### 2022-08-18 src/tex/ms.tex
[showyourwork] first commit

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

% Begin!
\begin{document}

% Title
\title{An open source scientific article}

% Author list
\author{@ekaterinailin}

% Abstract with filler text
\begin{abstract}
    Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
    Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
    Phasellus eu tellus sit amet tortor gravida placerat. 
    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
    Praesent eget sem vel leo ultrices bibendum. 
    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
    Curabitur auctor semper nulla donec varius orci eget risus. 
    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
    Duis eget orci sit amet orci dignissim rutrum.
\end{abstract}

% Main body with filler text
\section{Introduction}
\label{sec:intro}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
Phasellus eu tellus sit amet tortor gravida placerat. 
Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
Praesent eget sem vel leo ultrices bibendum. 
Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
Curabitur auctor semper nulla donec varius orci eget risus. 
Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi. 
Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae. 
Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna. 
Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante. 
Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient. 
Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis. 
Pellentesque cursus luctus mauris \citep{Luger2021}.

\bibliography{bib}

\end{document}

### 2022-08-18 src/scripts/random_numbers.py
added a new figure

@@ -1,0 +1,14 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import paths
+
+# Generate some data
+random_numbers = np.random.randn(100, 10)
+
+# Plot and save
+fig = plt.figure(figsize=(7, 6))
+plt.plot(random_numbers)
+plt.xlabel("x")
+plt.ylabel("y")
+fig.savefig(paths.figures / "random_numbers.pdf", bbox_inches="tight", dpi=300)
+

### 2022-09-27 src/tex/ms.tex
added a new figure
removed  new figure
[showyourwork] same as overleaf

@@
 Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis. 
-Pellentesque cursus luctus mauris \citep{Luger2021}.
+Pellentesque cursus luctus mauris .
+
+\begin{figure}[ht!]
+    \script{paper_cumdist_individual.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/PAPER_flares_phase_hist.png}
+        \caption{
+            Plot showing a bunch of random numbers.
+        }
+        \label{fig:random_numbers}
+    \end{centering}
+\end{figure}
+
+\section{Data}
+\label{sec:methods}
+\subsection{Star-Planet Systems}
+%Catalogs
+% as of January 2021
+We started our sample selection with the Planetary Systems Composite Parameters Table (PSCP)\footnote{ \url{https://exoplanetarchive.ipac.caltech.edu/cgi-bin/TblView/nph-tblView?app=ExoTbls&config=PSCompPars}} from which we removed controversial planet detections (``pl\_controv\_flag'' set to 1), i.e.
+detections with existing literature questioning the result.
+The catalog then contained XXXX unique systems.
+
+We complemented the PSCP with the TESS TOI Table~\citep[TT][]{guerrero2021arxiv}\footnote{\url{https://tev.mit.edu/data/collection/193/}}.
+We filtered the catalog by requiring the confirmed planet (CP) or known planet (KP) flags to be set in the ``TOI Disposition''.
+This added XXXX star-planet systems to the sample.
+
+%Transit information
+%Full sample statistics
+\subsection{Kepler and TESS photometry}
+Between 2009 and 2013, the Kepler space telescope~\citep{koch2010} nearly continuously observed a patch of the sky in the Cygnus-Lyra region.
+Each of the 18 observing Quarters contains nearly uninterrupted $\sim 90$ days of observations, totaling over 100000 stars monitored in 2-min cadence.
+% 100000 from here: https://exoplanetarchive.ipac.caltech.edu/docs/KeplerMission.html
+
+The Transiting Exoplanet Survey Satellite~(TESS,~\citealt{ricker2014}) is an all-sky mission that began operations in 2018, completed two sky scans until summer 2022.
+It is observing at the time of writing, collecting nearly continuous photometric time series in the 600-1000 nm band for $\sim 27 days$ in each observing Sector.
+About $200\,000$ stars have been observed in 2-min cadence in the first two years of operations with about 20000 targets per Sector.
+Out of these, from Sector 27 on, 1000 targets were observed at even higher 20-s cadence in each Sector.
+% 20000 per sector does not add up, because of stars observed in multiple sectors, the 20000 and 1000 figures can be found here: https://tess.mit.edu/observations/target-lists/
+% extended TESS mission https://heasarc.gsfc.nasa.gov/docs/tess/extended.html
+
+Based on the filtered PSCP and TT tables, we queried the full Kepler archive (quarters Q0-Q17, Data Release 25) and most recent TESS catalog (July 2022) for their respective 1-min and 2-min/20-s cadence light curves, accounting for systems that appeared in both catalogs.
+In total, we obtained XXXX Kepler light curves and XXXX TESS light curves.
+XXXX systems were observed only by the primary Kepler mission, XXXX only by TESS, and XXXX by both missions.
+
+\section{Methods}
+\label{sec:methods}
+same as in \cite{ilin2022searching}
+
+\section{Results}
+\label{sec:results}
+
+\subsection{Individual Stars}
+
+\subsection{Combined Sample}
+
+\begin{table}[ht!]
+    \script{paper_latex_flare_table.py}
+            \caption{
+            Table showing the head of the flare table.
+        }
+    \input{output/flare_table.tex}
+        \label{fig:random_numbers}
+\end{table}
+
+\section{Discussion}
+\label{sec:discussion}
 

### 2022-09-27 src/scripts/paper_cumdist_individual.py
load mplstyle

@@ -10,7 +10,11 @@ import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib.lines import Line2D
 
+
 if __name__ == "__main__":
+
+    # get matplotlib style
+    plt.style.use('./images/presentation.mplstyle')
 
     # read in flare table
     df = pd.read_csv(paths.data / "PAPER_flare_table.csv")

### 2022-09-27 src/scripts/paper_cumdist_individual.py
load mplstyle

@@ -14,7 +14,7 @@ from matplotlib.lines import Line2D
 if __name__ == "__main__":
 
     # get matplotlib style
-    plt.style.use('./images/presentation.mplstyle')
+    plt.style.use('.paper.mplstyle')
 
     # read in flare table
     df = pd.read_csv(paths.data / "PAPER_flare_table.csv")

### 2022-09-27 src/scripts/paper_cumdist_individual.py
load mplstyle

@@ -14,7 +14,7 @@ from matplotlib.lines import Line2D
 if __name__ == "__main__":
 
     # get matplotlib style
-    plt.style.use('.paper.mplstyle')
+    plt.style.use('paper.mplstyle')
 
     # read in flare table
     df = pd.read_csv(paths.data / "PAPER_flare_table.csv")

### 2022-12-27 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Title
-\title{An open source scientific article}
+\title{Searching for flaring star-planet interactions in star-planet systems in Kepler and TESS}
 
 % Author list
-\author{@ekaterinailin}
+\author{Ekaterina Ilin}
+\author{Katja Poppenh\"ager}
 
@@
 \begin{abstract}
-    Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
-    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
-    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
-    Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
-    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
-    Phasellus eu tellus sit amet tortor gravida placerat. 
-    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
-    Praesent eget sem vel leo ultrices bibendum. 
-    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
-    Curabitur auctor semper nulla donec varius orci eget risus. 
-    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
-    Duis eget orci sit amet orci dignissim rutrum.
+    Star-planet system we have found so far are nothing like the Solar System.
+Many stars host planets in orbits much closer than Mercury, where it takes them mere days to complete a full revolution.
+In some of these systems, the planets are so close that they plow through the extended magnetosphere of the star, and are expected to trigger flares on their surfaces.
+So far, however, these flaring star-planet interactions escape our detection methods.
+If found, the planets and the flare they cause become localized probes of the parts of the stellar magnetosphere that extends from the location of one to the other.
+A measurement of these interactions constrains mass loss from the star, and potentially also the magnetic field of the planet.
+
+    In this work, we searched star-planet systems observed by Kepler and TESS for flaring star-planet interactions.
+We compiled a catalog of all flaring star-planet systems known to date, and characterized the detected flares detected.
+We then searched for flares in excess of the intrinsic flaring of the star, i.e., flares triggered by the interaction with the planet in phase with its orbit.
+
+    We find XXXX star-planet systems with > XXXX flares.
+For XXXX of them, we can calculate the expected amplitude of interaction based on the system's magnetic field strength, orbital parameters, rotation and planet radius.
+We find that the trend of higher interaction signal agrees with the expected strength, but also shows signs of intermittency, both for individual systems, and in comparison between ones with similar expected amplitude.
+HIP 67522, a 17 Myr young Sun with a Jupiter in a 9 day orbit, shows both one of the highest expected and the highest measured interaction amplitudes, albeit only at the $2.5\sigma$ level.
 \end{abstract}
@@
 \label{sec:intro}
+Star-planet system we have found so far are nothing like the Solar System.
 
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
-Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
-Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
-Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
-Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
-Phasellus eu tellus sit amet tortor gravida placerat. 
-Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
-Praesent eget sem vel leo ultrices bibendum. 
-Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
-Curabitur auctor semper nulla donec varius orci eget risus. 
-Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
-Duis eget orci sit amet orci dignissim rutrum.
+What is SPI?
 
-Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi. 
-Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae. 
-Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna. 
-Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante. 
-Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient. 
-Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis. 
-Pellentesque cursus luctus mauris .
-
-\begin{figure}[ht!]
-    \script{paper_cumdist_individual.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/PAPER_flares_phase_hist.png}
-        \caption{
-            Plot showing a bunch of random numbers.
-        }
-        \label{fig:random_numbers}
-    \end{centering}
-\end{figure}
+Why look for SPI?
+Use planets as probes stellar magnetic fields at a defined orbit, e.g., stellar wind conditions.
+SPI can only occur if the planet is orbiting within the Alfv\'en radius of the star for a sizable period of time.
+The Alfv\'en radius is the radius at which the stellar wind velocity, which increases with increasing distance from the star because of XXXX, exceed the Alfv\'en velocity of the magnetized plasma.
+Beyond this radius, this plasma is disconnected from the star.
+Alfv\'en waves cannot propagate back to the star because the wind is carrying the plasma away faster than these waves can travel.
 
@@
 This added XXXX star-planet systems to the sample.
+\subsection{Orbital periods}
+Either Kepler/TESS or from RVs.
+
+\subsection{Semi-major axes}
+
+\subsection{Planetary radii}
+NASA table?
+
+\subsection{Stellar magnetic fields}
+\cite{foster2022identifying} and \cite{reiners2022magnetism}
 
@@
 \subsection{Kepler and TESS photometry}
-Between 2009 and 2013, the Kepler space telescope~\citep{koch2010} nearly continuously observed a patch of the sky in the Cygnus-Lyra region.
+Between 2009 and 2013, the Kepler space telescope~\citep{koch2010kepler} nearly continuously observed a patch of the sky in the Cygnus-Lyra region.
 Each of the 18 observing Quarters contains nearly uninterrupted $\sim 90$ days of observations, totaling over 100000 stars monitored in 2-min cadence.
@@
 
-The Transiting Exoplanet Survey Satellite~(TESS,~\citealt{ricker2014}) is an all-sky mission that began operations in 2018, completed two sky scans until summer 2022.
+The Transiting Exoplanet Survey Satellite~(TESS,~\cite{ricker2015transiting}) is an all-sky mission that began operations in 2018, completed two sky scans until summer 2022.
 It is observing at the time of writing, collecting nearly continuous photometric time series in the 600-1000 nm band for $\sim 27 days$ in each observing Sector.
@@
 
+\subsection{Transit mid-times}
+
 \section{Methods}
 \label{sec:methods}
-same as in \cite{ilin2022searching}
+We measure flaring star-planet interactions (SPI) as the presence of excess flares triggered by the orbiting planet.
+These excess flares manifest as a deviation of flare timing from a random Poisson process with orbital phase.
+That means that in the absence of flaring SPI, flare peak time will be distributed randomly in orbital phase.
+In the presence of flaring SPI, we measure a phase dependent deviation from this randomness.
+
+The main data for this analysis are flare times.
+To obtain them, we gather the Kepler and TESS light curves for all star-planet systems, remove rotational variability trends, search the de-trended light curves for flares, and convert the flare times to orbital phases.
+We then perform a customized Anderson-Darling test on the flare peak time distribution, which yields a p-value for the significance of the SPI signal.
+We compare these results to theoretical SPI power $P_{SPI}$ using the scaling relations in~\cite{lanza2012starplanet}, where $P_{SPI}$ is proportional to
+
+\begin{equation}
+    P_{SPI} \sim B_p^{2/3} B_*^{4/3} v_{rel} R_p^2.
+\end{equation}
+
+$B_p$ and $B_*$ are the total planetary and stellar surface field strengths, respectively; $v_{rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis; and $R_p$ is the planetary radius.
+
+The methods for light curve de-trending and flare finding in Kepler and TESS light curves, as well as the Anderson-Darling test, are the same as detailed in~\citep{ilin2022searching}.
+We therefore only briefly recap the techniques here:
+
+To remove trends and rotational variability from the light curve without losing the flare signal, we use an empirically derived multistep process.
+First, we apply spline fit with a coarse sampling of 30h mean values to capture slow rotation with periods above multiple days and non-periodic trends.
+Then, we iteratively fit a series of sines to capture rotational signal on time scales down to about half a day, close to the fastest rotational signals measured in low mass stars.
+Eventually, we apply two Savitzky-Golay filters in sequence, with decreasing periods at each step.
+At this stage, we mask all data points above a 2.5 sigma (or 1.5 sigma for very active stars) threshold as flare candidates to prevent the filter from ironing out the flares.
+
+Flare finding here. Manual vetting
+
+Orbital phase finding. Check coherence times. Orbital period is enough.
+Use transit mid-times from the same mission if possible.
+
+Anderson-Darling test here. Used four equidistant start phases instead of 20, because it does not change much.
+
+\cite{foster2022identifying} and \cite{reiners2022magnetism} to get Lx and then B.
 
@@
 
-\subsection{Individual Stars}
+\subsection{Flare catalog}
+
+\begin{table*}
+    \script{paper_latex_flare_table.py}
+    \centering
+            \caption{
+            Flare catalog of all star-planet systems observed by Kepler and TESS.
+In transiting multi-planet systems, the orbital phase refers to the innermost planet, with the transit mid-time at phase zero.
+        }
+    \input{output/flare_table.tex}
+        \label{fig:random_numbers}
+\end{table*}
+
+\subsection{Orbital coherence times}
+
+divide the coherence time of the orbital period by the observing baseline of the combined Kepler and TESS observations for each star.
+
+Do the same for the mid-times.
+
+\subsection{Flare phase distributions}
+
+For details on AU Mic results, see~\citep{ilin2022searching}.
+
+\begin{figure*}[ht!]
+    \script{paper_cumdist_individual.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/PAPER_flares_phase_hist.png}
+        \caption{
+            Cumulative distributions of orbital phases of flares in the hosts observed by Kepler and TESS that had the most flares detected per star.
+        }
+        \label{fig:cumdist_active}
+    \end{centering}
+\end{figure*}
+
+\subsection{Flaring star-planet interaction signal}
+We use the custom Anderson-Darling test detailed in \cite{ilin2022searching} to look for flaring SPI in all system with three flares or more.
+We do not find $>3\sigma$ signal of star-planet interaction in any of the star-planet systems in this sample.
+
+Table XXXX shows
+
+\subsection{Individual stars}
+
+\subsubsection{Proxima Cen}
+tentative detection of another planet further in, at 0.029 au, or 5 day orbital period~\citep{faria2022candidate, artigau2022linebyline}
+
+\subsubsection{HIP 67522}
+HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest signs of flaring SPI, albeit with only 6 flares in the sample.
+These flares are distributed across two Sectors in TESS.
+In Sector 11, two flares occur at orbital phases $\sim 0.6$ and $\sim 0.8$.
+Two years later, in Sector 38, four flares occur, but this time, all of them take place at orbital phases $0.00-0.05$, that is, up to a few hours after transit.
+
+HIP 67522 is young Sun, currently contracting onto the main sequence.
+It is a Sco-Cen member (10-20 Myr old), which was discovered to host a close-in Jupiter, HIP 67522 b, in 2020~\citep{rizzuto2020tess}.
+It was found with low obliquity, consistent with XXXX~\citep{heitzmann2021obliquity}.
+Tentative third planet transiting.
+
+HIP 67522 will be observed again with TESS in spring 2023.
+
+\subsection{TAP 26}
+
+\subsubsection{Excluded flaring star-planet systems}
+\paragraph{LTT 1445}
+ LTT 1445 is a hierarchical triple wherein LTT 1445 A hosts two close-in planets, and LTT 1445 B and C are a tight binary system separated by about 7 arcsec, that is, blended in one TESS pixel~\citep{winters2019three}.
+Both the binary and LTT 1445 A have been detected with flares in X-ray~\citep{brown2022xray}.
+Recently, LTT 1445 A was found to host a second plant LTT 1445 Ac inwards of LTT 1445 Ab~\citep{lavie2022planetary}
+
+\paragraph{HD 41004 B}
+Hierarchical system, composed of HD 41004 A and its Jupiter HD 41004 Ab, and HD 41004 B. an M dwarf, and its brown dwarf companion HD 41004 Bb.
 
@@
 
-\begin{table}[ht!]
-    \script{paper_latex_flare_table.py}
-            \caption{
-            Table showing the head of the flare table.
-        }
-    \input{output/flare_table.tex}
-        \label{fig:random_numbers}
-\end{table}
-
+For those stars with given transit mid-time and 
 \section{Discussion}
 \label{sec:discussion}
+
+\subsection{Similar work that puts ours in context}
+
+\subsection{Rotational variability}
+Hard to measure, because it de-phases much faster than orbital variability due to differential rotation and spot evolution. We could use single light curves within which coherence is given...
+
+\subsection{Intermittency}
+
+TAP 26 vs. HIP 67522, also different sectors for HIP 67522, see \cite{shkolnik2008nature}
+
+\subsection{Spin-orbit alignment}
 

### 2022-12-28 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-\subsection{Orbital coherence times}
+\subsection{Period coherence times}
 
@@
 Do the same for the mid-times.
+
+\begin{figure*}[ht!]
+    \script{paper_coherence_histogram.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/PAPER_coherence_histogram.png}
+        \caption{
+           Time span of observation vs.
+coherence time or the orbital and rotational periods, respectively.
+Orbital periods are all known precisely enough, so that the phase uncertainty at the last observed flare is of the order of $10^{-2}$.
+In contrast, in stars with known rotation periods, the precision is often too low, so that the phase of the last flare is often undetermined (ratio on x-axis $\sim 1$.
+        }
+        \label{fig:coherence_hist}
+    \end{centering}
+\end{figure*}
 

### 2023-01-31 src/scripts/paper_adtext_vs_value_scatterplots.py
adding main table

@@ -34,6 +34,40 @@ def get_sigma_values():
     return sigmas, sigma_label
 
 
+
+def colorcode_dist(dist):
+    """Define color code and symbol marker for rotation period.
+
+    Parameters
+    ----------
+    dist : float
+        Distance in pc.
+
+    Returns
+    -------
+    color : str
+        Color code.
+    marker : str
+        Symbol marker.
+    """
+    if dist < 50.:
+        color = "green"
+        symbol = "o"
+
+    elif (dist >= 50.) & (dist < 100.):
+        color = "blue"
+        symbol = "x"
+
+    elif (dist >= 100.) & (dist < 150.):
+        color = "black"
+        symbol = "d"
+
+    else:
+        color = "lightgrey"
+        symbol = "s"
+
+    return color, symbol
+
 def colorcode_rotation(st_rotp):
     """Define color code and symbol marker for rotation period.
 
@@ -68,8 +102,66 @@ def colorcode_rotation(st_rotp):
     return color, symbol
 
 
+def colorcode_multiplicity(snum):
+    """Define color code and symbol marker for rotation period.
 
-def make_adtest_figure(df, value, valuelabel, legend, labels):
+    Parameters
+    ----------
+    snum : float
+        Number of stars in the system.
+
+    Returns
+    -------
+    color : str
+        Color code.
+    marker : str
+        Symbol marker.
+    """
+    if snum == 1.:
+        color = "green"
+        symbol = "o"
+
+    elif snum>1:
+        color = "blue"
+        symbol = "x"
+
+    else:
+        color = "lightgrey"
+        symbol = "s"
+
+    return color, symbol
+
+def colorcode_Lx(lx):
+    """Define color code and symbol marker for available X-ray luminosity.
+
+    Parameters
+    ----------
+    lx : float
+        X-ray luminosity in erg/s.
+
+    Returns
+    -------
+    color : str
+        Color code.
+    marker : str
+        Symbol marker.
+    """
+    if np.isnan(lx):
+        color = "blue"
+        symbol = "o"
+
+    elif np.isfinite(lx):
+        color = "green"
+        symbol = "x"
+
+    else:
+        color = "lightgrey"
+        symbol = "s"
+
+    return color, symbol
+
+
+def make_adtest_figure(df, value, valuelabel, legend, labels, ext):
[…]

### 2023-01-31 src/scripts/paper_main_table.py

@@ -1,0 +1,320 @@
+"""
+Python 3.8 -- UTF-8
+
+Ekaterina Ilin, 2022, MIT License
+
+Script that generates the main table of the paper, showing the
+AD test results for the orbital period all stellar and planetary
+parameters.
+"""
+
+import numpy as np
+import pandas as pd
+import paths
+
+def citation_from_bibkey(bibkey):
+    """Create a LaTeX citation from a bibkey.
+    
+    Parameters
+    ----------
+    bibkey : str
+        The bibkey to use for the citation.
+    
+    Returns
+    -------
+    str
+        The LaTeX citation.
+    """
+    return r" \citet{" + bibkey + "}"
+
+def max_array(a, b):
+    """Compute the maximum of two arrays. """
+    a = a.astype(float)
+    b = b.astype(float)
+    return np.where(a > b, a, b)
+
+def min_array(a, b):
+    """Compute the minimum of two arrays. """
+    a = a.astype(float)
+    b = b.astype(float)
+    return np.where(a < b, a, b)
+
+def get_len_decimals(df, col, err, err2=None, typ="err"):
+    """Get the number of decimals to round to.
+    
+    Parameters
+    ----------
+    df : pd.DataFrame
+        The DataFrame containing the data.
+    col : str
+        The column name of the value.
+    err : str
+        The column name of the error.
+    err2 : str, optional    
+        The column name of the second error.
+    typ : str, optional
+        The type of error. Can be "err" or "high-low".
+
+    Returns
+    -------
+    int
+        The number of decimals to round to.
+    """
+    if err2 is None:
+        mr = max_array(np.abs(np.log10(np.abs(df[col])).astype(int).values)+2, 
+                        np.abs(np.log10(np.abs(df[col] / df[err]))).astype(int).values + 2)
+
+        return mr
+    else:
+    
+        if typ=="err":
+            minarr = min_array(df[err].values, -df[err2].values)
+            mr = max_array(np.abs(np.log10(np.abs(df[col])).astype(int).values)+2, 
+                         np.abs(np.log10(np.abs(df[col] / minarr)).astype(int).values) +2)
+            return mr
+        elif typ=="high-low":
+            minarr = min_array((df[err]-df[col]).values, (df[col]-df[err]).values)
+            
[…]

### 2023-01-31 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \section{Data}
-\label{sec:methods}
+\label{sec:data}
 \subsection{Star-Planet Systems}
@@
 This added XXXX star-planet systems to the sample.
+\subsection{Multiplicity}
+We flag all multiple stars except for Proxima Cen (whose companion are well separated both physically and on the sky), but kept them in for the analysis.
+In addition to noting the multiplicity of some well-known stars, we also use the Robo-AO catalog of nearby companions to Kepler planet candidates from ~\cite{ziegler2018measuring}
+
 \subsection{Orbital periods}
@@
 \subsection{Semi-major axes}
+\label{sec:data:a}
+The critical parameter is the distance between the star and the planet, not the semi-major axis itself.
+This varies if the orbit is eccentric.
+To account for varying distance, we adopt the mean semi-major axes from the literature, but use a custom estimate for the uncertainty that includes the eccentricity.
+If the eccentricity is known, then the range of the distance is set to either the error on the semi-major axis or half of the difference between the semi-major and semi-minor axis, as calculated from the eccentricity -- whichever is larger.
+If eccentricity is NOT known, then the range of the distance is either the 25\% error on the semi-major axis, that is, assuming e=0.5 or the uncertainty on the semi-major axis -- whichever is larger.
+
+\subsection{Rotation periods}
+We adopt available rotation period values from the literature. When uncertainties are not given, we assume 10\% uncertainty.% _09_
 
 \subsection{Planetary radii}
-NASA table?
+NASA table, see references in table, or using the planetary mass to calculate the radius using the empirical relations derived in \cite{chen2007} using their open source \texttt{forecaster} tool, upgraded to \texttt{astro-forecaster}\footnote{https://pypi.org/project/astro-forecaster/} by Ben Cassesse.
 
-\subsection{Stellar magnetic fields}
-\cite{foster2022identifying} and \cite{reiners2022magnetism}
+\subsection{Relative velocity}
+
+We calculate the relative velocity between the magnetic field of the star, assumed to be co-rotating, at the planetary orbit, as
+
+\begin{equation}
+    v_{rel} = 2 \pi a \left(\dfrac{1}{P_{orb}} - \dfrac{1}{P_{rot}}\right) 
+\end{equation}
+
+We use quadratic error propagation to estimate the uncertainty in $v_{rel}$ with the mean of the upper and lower uncertainty values on the orbital period and rotation period, if both are given, and the uncertainty on semi-major axis as derived in Sec.~\ref{sec:data:a}.
 
@@
 
+\subsection{X-ray luminosity}
+We take the \cite{foster2022exoplanet} X-ray luminosity catalog as the basis for our calculation, assuming an uncertainty of 30\% in the reported values, covering typical intrinsic variability among stars of similar rotation periods in studies like ~\cite{wright2011stellaractivityrotation, wright2018stellar}.
+
+\subsection{Stellar magnetic fields}
+\cite{foster2022identifying} and \cite{reiners2022magnetism}
+
+The intrinsic scatter in Eq.
+4 in \cite{reiners2022magnetism} dominates the uncertainty in B over the uncertainty in stellar radius and $L_X$.
+We use the $+/-1\sigma$ values for the latter two for the final uncertainty estimate $\sigma B$
+
+The estimate is consistent with existing Zeeman broadening for, e.g. AU Mic (3010 G~\cite{reiners2022magnetism})
 \subsection{Transit mid-times}
@@
 
-\begin{figure*}[ht!]
+\begin{figure}[ht!]
     \script{paper_coherence_histogram.py}
@@
     \end{centering}
-\end{figure*}
+\end{figure}
 
@@
 
+\begin{figure*}[ht!]
+    \script{paper_adtext_vs_value_scatterplots.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_p_spi_erg_s_bp0.png}
+        \caption{
+            Expected power of SPI vs.
+AD test results, assuming an unmagnetized planet.
+These results are mainly dominated by the X-ray luminosity of the host star, see Fig.~\ref{fig:adtest_xray_flux_erg_s}.
+Assuming a magnetized planet with $B_p=1$ G has only minor influence on the results shown in this figure, see Appendix.
+        }
+        \label{fig:adtest_p_spi_erg_s_bp0}
+    \end{centering}
+\end{figure*}
+
+\begin{figure*}[ht!]
+    \script{paper_adtext_vs_value_scatterplots.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_xray_flux_erg_s.png}
+        \caption{X-ray luminosity of the host star~\cite{foster2022identifying} vs. AD test results.
+        }
+        \label{fig:adtest_xray_flux_erg_s}
+    \end{centering}
+\end{figure*}
+
 \subsection{Individual stars}
@@
 tentative detection of another planet further in, at 0.029 au, or 5 day orbital period~\citep{faria2022candidate, artigau2022linebyline}
+Although Proxima Cen is part of a triple stellar system, we treat it a single star here because of the large angular separation to its two companions.
+
+Proxima Cen b has an eccentricity upper limit of 0.35~\cite{anglada-escude2016terrestrial}
 
@@
 
+HIP 67522 is in close spin-orbit commensurability -- $P_{rot}/P_{orb}=5/1$. The system's $a/R_*\approx11.7$, eccentricity below .25~\cite{rizzuto2020tess}, so that
+
+\cite{wood2021characterizing} rule out stellar companions for HIP 67522 based on RV, high-resolution imaging, and Gaia data.
+
 HIP 67522 will be observed again with TESS in spring 2023.
+\subsubsection{GJ 3323}
 
-\subsection{TAP 26}
+GJ 3323 b is a non-transiting, likely rocky planet.
+We adopted the mean radius between assuming pure iron through pure ice composition in \cite{lovos2022null} Table A1, and took the difference from this mean to either of the extremes as uncertainty estimate
+
+\subsubsection{GJ 1061}
+GJ 1061 b is a non-transiting, likely rocky planet.
+We adopted the mean radius between assuming pure iron through pure ice composition in \cite{lovos2022null} Table A1, and took the difference from this mean to either of the extremes as uncertainty estimate
+
+\subsubsection{TAP 26}
+Likely low eccentricity given in \cite{yu2017hot}
+
+\subsubsection{GJ 393}
+Eccentricity likely low, but not quantified in \cite{amado2021carmenes}, so we treat it as unconstrained (set e=0.5)
+
+\subsubsection{Kepler-42}
+ 	KOI-961 in the detection paper \cite{muirhead2012characterizing}, low eccentricity constrained by \cite{mann2017gold}
+
+\subsubsection{GJ 674}
+Has hot UV flares~\cite{froning2019hot}
+The mass estimates in \cite{bonfils2007harps} and \cite{boisse2011disentangling} do not quote errors, but differ by 0.3MEarth, so we assume that as the uncertainty on $M_p\sin i$
+
+\subsubsection{K2-354}
+Found under EPIC 211314705 and K2-329 in \cite{bouma2020cluster}, who refer to the detection paper \cite{pope2016transiting}, also TIC 468989066.
+
+\subsubsection{DS Tuc A}
+It's a multiple
+\subsubsection{Kepler-1651}
+It's a multiple
 
@@
 Both the binary and LTT 1445 A have been detected with flares in X-ray~\citep{brown2022xray}.
-Recently, LTT 1445 A was found to host a second plant LTT 1445 Ac inwards of LTT 1445 Ab~\citep{lavie2022planetary}
+Recently, LTT 1445 A was found to host a second planet LTT 1445 Ac inwards of LTT 1445 Ab~\citep{lavie2022planetary}.
+The rotation periods are not known, so it does not appear in the final figure.
 
 \paragraph{HD 41004 B}
-Hierarchical system, composed of HD 41004 A and its Jupiter HD 41004 Ab, and HD 41004 B. an M dwarf, and its brown dwarf companion HD 41004 Bb.
+Hierarchical system, composed of HD 41004 A and its Jupiter HD 41004 Ab, and HD 41004 B.
+an M dwarf, and its brown dwarf companion HD 41004 Bb.
+The rotation periods are not well-known, so it does not appear at all in the final figure.
 
@@
 
+\appendix
+\section{Expected $P_{SPI}$ vs. measure flaring SPI with a magnetized planet}
+
+\begin{figure*}[ht!]
+    \script{paper_adtext_vs_value_scatterplots.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_p_spi_erg_s.png}
+        \caption{
+            Expected power of SPI vs. AD test results, same as Fig.~\ref{fig:adtest_p_spi_erg_s_bp0}, but assuming a magnetized planet with $B_p=1$ G. 
+        }
+        \label{appendix:fig:adtest_p_spi_erg_s}
+    \end{centering}
+\end{figure*}
+
 \end{document}

### 2023-01-31 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-\begin{figure*}[ht!]
-    \script{paper_adtext_vs_value_scatterplots.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_p_spi_erg_s_bp0.png}
-        \caption{
-            Expected power of SPI vs.
+% \begin{figure*}[ht!]
+%     \script{paper_adtext_vs_value_scatterplots.py}
+%     \begin{centering}
+%         \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_p_spi_erg_s_bp0.png}
+%         \caption{
+%             Expected power of SPI vs.
 AD test results, assuming an unmagnetized planet.
@@
 Assuming a magnetized planet with $B_p=1$ G has only minor influence on the results shown in this figure, see Appendix.
-        }
-        \label{fig:adtest_p_spi_erg_s_bp0}
-    \end{centering}
-\end{figure*}
+%         }
+%         \label{fig:adtest_p_spi_erg_s_bp0}
+%     \end{centering}
+% \end{figure*}
 
-\begin{figure*}[ht!]
-    \script{paper_adtext_vs_value_scatterplots.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_xray_flux_erg_s.png}
-        \caption{X-ray luminosity of the host star~\cite{foster2022identifying} vs. AD test results.
-        }
-        \label{fig:adtest_xray_flux_erg_s}
-    \end{centering}
-\end{figure*}
+% \begin{figure*}[ht!]
+%     \script{paper_adtext_vs_value_scatterplots.py}
+%     \begin{centering}
+%         \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_xray_flux_erg_s.png}
+%         \caption{X-ray luminosity of the host star~\cite{foster2022identifying} vs. AD test results.
+%         }
+%         \label{fig:adtest_xray_flux_erg_s}
+%     \end{centering}
+% \end{figure*}
 
@@
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_p_spi_erg_s.png}
+        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_p_spi_erg_s_sab_wBp_colorcode_dist.png}
         \caption{
-            Expected power of SPI vs. AD test results, same as Fig.~\ref{fig:adtest_p_spi_erg_s_bp0}, but assuming a magnetized planet with $B_p=1$ G. 
+            Expected power of SPI from stretch and break vs. AD test results, assuming a magnetized planet with $B_p=1$ G. 
         }

### 2023-01-31 src/scripts/paper_main_table.py
added abbreviated version of the paper main table

@@ -281,6 +281,8 @@ if __name__ == "__main__":
     singles = singles[singles.TIC != 67646988 ]
     singles = singles[singles.TIC != 236387002 ]
 
+    fulltable = singles.copy()
+
     # convert the singles table to latex after converting the values to tex format
     print("Converting each parameter to a latex formatted column.")
     for col in cols:
@@ -306,7 +308,7 @@ if __name__ == "__main__":
 
     # layout
     string = string.replace("\citet{[*]}","[*]")
-    string = string.replace("rllllllllllll","c"*14)
+    # string = string.replace("rllllllllllll","c"*14)
     string = string.replace("midrule","hline")
     string = string.replace("toprule","hline")
     string = string.replace("bottomrule","hline")
@@ -318,3 +320,29 @@ if __name__ == "__main__":
     with open(path, "w") as f:
         f.write(string)
 
+
+    # Get all bibkeys from singles table
+    bibkeys = fulltable.st_rotp_bibkey.unique()
+    bibkeys = np.append(bibkeys, fulltable.pl_orbper_bibkey.unique())
+    bibkeys = np.append(bibkeys, fulltable.st_rad_bibkey.unique())
+    bibkeys = np.append(bibkeys, fulltable.pl_radj_bibkey.unique())
+    bibkeys = np.append(bibkeys, fulltable.pl_orbsmax_bibkey.unique())
+    bibkeys = np.append(bibkeys, fulltable.st_lum_bibkey.unique())
+
+    # enumerate the bibkeys
+    bibkeys = np.unique(bibkeys)
+
+    # make a dictionary with the bibkeys and the corresponding index
+    bibkeys = {bibkeys[i]:i+1 for i in range(len(bibkeys))}
+
+    # replace the bibkeys with the index in the string table
+    for key in bibkeys.keys():
+        replace = "\citet{"+key+"}"
+        string = string.replace(replace, "(" + str(bibkeys[key]) + ")")
+
+    # write to file
+    path = paths.output / "fit_parameters_bibkeys.tex"
+    print("Write to file: ", path)
+
+    with open(path, "w") as f:
+        f.write(string)

### 2023-02-01 src/scripts/paper_main_table.py
split table in two

@@ -234,7 +234,7 @@ if __name__ == "__main__":
         "st_rad":"$R_{*}$ [R$_\odot$]",
         "pl_radj":"$R_{p}$ [R$_J$]",
         "a_au":"$a$ [au]",
-        "st_lum":"$L_{*}$ [L$_\odot$]",
+        "st_lum":"log${10} L_{*}$ [L$_\odot$]",
         "Ro":"Ro",
         "B_G":"$B$ [G]",
         "p_spi_erg_s":"log$_{10} P_{SPI,sb}$ [erg s$^{-1}$]",
@@ -299,26 +299,25 @@ if __name__ == "__main__":
     del singles["orbits_covered"]
 
     # make TeX table
-    print("Converting table to TeX format.")
+    # print("Converting table to TeX format.")
 
-    # make the default string length longer
-    pd.set_option('display.max_colwidth', 1000)
+    # # make the default string length longer
+    # pd.set_option('display.max_colwidth', 1000)
 
-    string = singles.to_latex(escape=False,index=False)
+    # string = singles.to_latex(escape=False,index=False)
 
-    # layout
-    string = string.replace("\citet{[*]}","[*]")
-    # string = string.replace("rllllllllllll","c"*14)
-    string = string.replace("midrule","hline")
-    string = string.replace("toprule","hline")
-    string = string.replace("bottomrule","hline")
+    # # layout
+    # string = string.replace("\citet{[*]}","[*]")
+    # string = string.replace("midrule","hline")
+    # string = string.replace("toprule","hline")
+    # string = string.replace("bottomrule","hline")
 
-    # write to file
-    path = paths.output / "fit_parameters.tex"
-    print("Write to file: ", path)
+    # # write to file
+    # path = paths.output / "fit_parameters.tex"
+    # print("Write to file: ", path)
 
-    with open(path, "w") as f:
-        f.write(string)
+    # with open(path, "w") as f:
+    #     f.write(string)
 
 
     # Get all bibkeys from singles table
@@ -335,14 +334,63 @@ if __name__ == "__main__":
     # make a dictionary with the bibkeys and the corresponding index
     bibkeys = {bibkeys[i]:i+1 for i in range(len(bibkeys))}
 
-    # replace the bibkeys with the index in the string table
-    for key in bibkeys.keys():
-        replace = "\citet{"+key+"}"
-        string = string.replace(replace, "(" + str(bibkeys[key]) + ")")
[…]

### 2023-02-01 src/scripts/paper_main_table.py
edited table header

@@ -237,8 +237,8 @@ if __name__ == "__main__":
         "st_lum":"log${10} L_{*}$ [L$_\odot$]",
         "Ro":"Ro",
         "B_G":"$B$ [G]",
-        "p_spi_erg_s":"log$_{10} P_{SPI,sb}$ [erg s$^{-1}$]",
-        "p_spi_kav22":"log$_{10} P_{SPI,aw}$ [erg s$^{-1}$]",
+        "p_spi_erg_s":"log$_{10} P_{sb}$ [erg s$^{-1}$]",
+        "p_spi_kav22":"log$_{10} P_{aw}$ [erg s$^{-1}$]",
         "v_rel_km_s":"$v_{rel}$ [km s$^{-1}$]",
         "mean":"p-value",
         }
@@ -298,26 +298,6 @@ if __name__ == "__main__":
     del singles["multiple_star_source"]
     del singles["orbits_covered"]
 
-    # make TeX table
-    # print("Converting table to TeX format.")
-
-    # # make the default string length longer
-    # pd.set_option('display.max_colwidth', 1000)
-
-    # string = singles.to_latex(escape=False,index=False)
-
-    # # layout
-    # string = string.replace("\citet{[*]}","[*]")
-    # string = string.replace("midrule","hline")
-    # string = string.replace("toprule","hline")
-    # string = string.replace("bottomrule","hline")
-
-    # # write to file
-    # path = paths.output / "fit_parameters.tex"
-    # print("Write to file: ", path)
-
-    # with open(path, "w") as f:
-    #     f.write(string)
 
 
     # Get all bibkeys from singles table
@@ -334,26 +314,13 @@ if __name__ == "__main__":
     # make a dictionary with the bibkeys and the corresponding index
     bibkeys = {bibkeys[i]:i+1 for i in range(len(bibkeys))}
 
-    # # replace the bibkeys with the index in the string table
-    # for key in bibkeys.keys():
-    #     replace = "\citet{"+key+"}"
-    #     string = string.replace(replace, "(" + str(bibkeys[key]) + ")")
-
-    # # write to file
-    # path = paths.output / "fit_parameters_bibkeys.tex"
-    # print("Write to file: ", path)
-
-    # with open(path, "w") as f:
-    #     f.write(string)
[…]

### 2023-02-01 src/scripts/paper_main_table.py
added scientific notation for small values

@@ -159,7 +159,8 @@ def tex_one_err(val, err):
     str
         The LaTeX string.
     """
-    return val.astype(str) + "[" + err.astype(str) + "]"
+
+    return val.astype(str) + "[" + err.apply(lambda x: f"{x:.1e}" if x<1e-2 else x).astype(str) + "]"
 
 # for each type of value cols, define a function that
 # converts them into one list of strings for latex
@@ -254,6 +255,8 @@ if __name__ == "__main__":
     for col in makelog:
         df[col] = np.log10(df[col])
 
+    # convert to scientific notation
+
     # select only the columns we want
     sel = df[["ID","TIC",
                 'st_rotp','st_rotp_err','st_rotp_source', 
@@ -298,7 +301,7 @@ if __name__ == "__main__":
     del singles["multiple_star_source"]
     del singles["orbits_covered"]
 
-
+    
 
     # Get all bibkeys from singles table
     bibkeys = fulltable.st_rotp_bibkey.unique()

### 2023-02-01 src/scripts/paper_main_table.py
convert to 0.01 au unit

@@ -234,7 +234,7 @@ if __name__ == "__main__":
         "orbper_d":"$P_{orb}$ [d]",
         "st_rad":"$R_{*}$ [R$_\odot$]",
         "pl_radj":"$R_{p}$ [R$_J$]",
-        "a_au":"$a$ [au]",
+        "a_au":"$a$ [$10^{-2}$ au]",
         "st_lum":"log${10} L_{*}$ [L$_\odot$]",
         "Ro":"Ro",
         "B_G":"$B$ [G]",
@@ -255,7 +255,9 @@ if __name__ == "__main__":
     for col in makelog:
         df[col] = np.log10(df[col])
 
-    # convert to scientific notation
+    # convert au and au_err to 10^-2 au
+    df["a_au"] = df["a_au"] * 100
+    df["a_au_err"] = df["a_au_err"] * 100
 
     # select only the columns we want
     sel = df[["ID","TIC",
@@ -319,7 +321,7 @@ if __name__ == "__main__":
 
     # literature parameters table columns
     lit_cols = ["ID", "$P_{rot}$ [d]", "$P_{orb}$ [d]", "$R_{*}$ [R$_\odot$]",
-            "$R_{p}$ [R$_J$]", "$a$ [au]", "log${10} L_{*}$ [L$_\odot$]"]
+            "$R_{p}$ [R$_J$]", "$a$ [$10^{-2}$ au]", "log${10} L_{*}$ [L$_\odot$]"]
 
     # derived parameters table columns
     der_cols = ["ID", "Ro", "$B$ [G]", "log$_{10} P_{sb}$ [erg s$^{-1}$]",

### 2023-02-01 src/scripts/paper_main_table.py
make bibstring

@@ -365,4 +365,19 @@ if __name__ == "__main__":
         with open(path, "w") as f:
             f.write(string)
 
+    # generate a bibkey string to put in the footnote of the tex table
+    bibstring = ""
+    for key in bibkeys.keys():
+        bibstring += "(" + str(bibkeys[key]) + ") \citet{" + key + "}, "
+
+    # replace [*] with 10% error assumed
+    bibstring = bibstring.replace(r"\citet{[*]}","$10\%$ error assumed")
+   
+    # write the bibstring to a file
+    path = paths.output / "lit_table_bibstring.tex"
+    print("Write footnote list to file: ", path)
+
+    with open(path, "w") as f:
+        f.write(bibstring)
+
             

### 2023-02-01 src/scripts/paper_main_table.py
added string of excluded multiple and contaminated stars

@@ -3,9 +3,10 @@ Python 3.8 -- UTF-8
 
 Ekaterina Ilin, 2022, MIT License
 
-Script that generates the main table of the paper, showing the
-AD test results for the orbital period all stellar and planetary
-parameters.
+Script that generates the main tables of the paper, showing 1. all stellar and 
+planetary parameters necessary for analysis (and producing a string of 
+references for the footnote), and 2. derived parameters and AD test results 
+for the orbital period. 
 """
 
 import numpy as np

### 2023-02-01 src/scripts/paper_string_multiple_stars.py

@@ -1,0 +1,33 @@
+"""
+Python 3.8 -- UTF-8
+
+Ekaterina Ilin, 2022, MIT License
+
+Script that generates a list of excluded stars based on multiplicity and
+contamination, with reference to where the multiplicity info was found.
+"""
+
+import pandas as pd
+
+import paths
+
+if __name__ == "__main__":
+
+    # read table
+    print("[UP ]Read results table ", paths.data / "results.csv")
+    df = pd.read_csv(paths.data / "results.csv")
+
+    # select only multiple or contaminated stars
+    multiples = df[~df.multiple_star.isnull()]
+
+    # make a string of IDs with multiple_star_source attached in \cite{}
+    multiples["multiple_star_source"] = multiples.multiple_star_source.apply(lambda x: f"~\\citep{{{x}}}")
+
+    # append the multiple_star_source to the ID and give one comma separated big string
+    multiples = multiples.ID + multiples.multiple_star_source
+    multiples = ", ".join(multiples)
+
+    # write to file
+    print("Write to file ", paths.data / "multiples_string.tex")
+    with open(paths.data / "multiples_string.tex", "w") as f:
+        f.write(multiples)

### 2023-02-01 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 This added XXXX star-planet systems to the sample.
-\subsection{Multiplicity}
-We flag all multiple stars except for Proxima Cen (whose companion are well separated both physically and on the sky), but kept them in for the analysis.
-In addition to noting the multiplicity of some well-known stars, we also use the Robo-AO catalog of nearby companions to Kepler planet candidates from ~\cite{ziegler2018measuring}
+\subsection{Multiplicity and contamination}
+We drop all multiple stars except for Proxima Cen (whose companion are well separated both physically and on the sky), and all stars with nearby objects that contaminate our analysis, e.g., from ~\citet{ziegler2018measuring}.
+
+Quoting the references for multiplicity/contamination, we dropped the following targets: \input{output/multiples_string.tex}
 
@@
 
-\subsection{X-ray luminosity}
-We take the \cite{foster2022exoplanet} X-ray luminosity catalog as the basis for our calculation, assuming an uncertainty of 30\% in the reported values, covering typical intrinsic variability among stars of similar rotation periods in studies like ~\cite{wright2011stellaractivityrotation, wright2018stellar}.
+\subsection{Bolometric luminosity}
+
+We take bolometric luminosity values as given in the NASA Table if given with uncertainties, and supplement missing values and entries without quoted uncertainties with Gaia DR3 FLAME~\citep{fouesneau2022gaia} solutions.
+
+% \subsection{X-ray luminosity}
+% We take the \cite{foster2022exoplanet} X-ray luminosity catalog as the basis for our calculation, assuming an uncertainty of 30\% in the reported values, covering typical intrinsic variability among stars of similar rotation periods in studies like ~\cite{wright2011stellaractivityrotation, wright2018stellar}.
 
@@
 
-Table XXXX shows
+\begin{table*}
+\movetableright=-20mm
+\footnotesize
+    \script{paper_main_table.py}
+    \caption{Star-planet systems.}
+    \input{output/table_lit_vals.tex}
+        \label{tab:maintable_lit}
+    \tablerefs{\input{output/lit_table_bibstring.tex}}
+\end{table*}
+
+\begin{table*}
+\movetableright=-20mm
+    \script{paper_main_table.py}
+    \caption{Flaring SPI results.}
+    \input{output/table_der_vals.tex}
+        \label{tab:maintable_der}
+
+\end{table*}
 

### 2023-02-01 src/scripts/paper_string_multiple_stars.py
fixed the output location

@@ -28,6 +28,6 @@ if __name__ == "__main__":
     multiples = ", ".join(multiples)
 
     # write to file
-    print("Write to file ", paths.data / "multiples_string.tex")
-    with open(paths.data / "multiples_string.tex", "w") as f:
+    print("Write to file ", paths.output / "multiples_string.tex")
+    with open(paths.output / "multiples_string.tex", "w") as f:
         f.write(multiples)

### 2023-02-01 src/scripts/paper_adtext_vs_value_scatterplots.py
adding BP1 and BP0 scenarios to the main table and scatterplots

@@ -313,17 +313,23 @@ if __name__ == "__main__":
     # read in results table
     df = pd.read_csv(paths.data / "results.csv")
 
-    # define the colors and symbols for the different Lx
+
+
+    # ------------------------------------------------------------
+    # DISTANCE
+    # ------------------------------------------------------------
+
+    # define the colors and symbols for the different distance bins
     df["color"], df["symbol"] = zip(*df.sy_dist.apply(colorcode_dist))
     valuelegend = legend[-7:-3]
     valuelabels = labels[-7:-3]
 
 
     # ------------------------------------------------------------
-    # P-VALUE VS. P_SPI with Bp=1G
+    # STRETCH AND BREAK with Bp=1G
 
     value = "p_spi_erg_s"
-    valuelabel = r"$\sim$ P$_{SPI}$  @ B$_p$=1G"
+    valuelabel = r"$\sim$ P$_{sb}$  @ B$_p$=1G"
 
     make_adtest_figure(df, value, valuelabel, valuelegend, valuelabels, "sab_wBp_colorcode_dist")
 
@@ -342,33 +348,24 @@ if __name__ == "__main__":
     # P-VALUE VS. P_SPI with Bp=1G with Kavanagh+2022
 
     value = "p_spi_kav22"
-    valuelabel = r"$\sim$ P$_{SPI}$ @ B$_p$=1G"
+    valuelabel = r"$\sim$ P$_{aw}$ @ B$_p$=1G"
   
 
     make_adtest_figure(df, value, valuelabel, valuelegend, valuelabels, "aw_wBp_colorcode_dist")
 
+    
     # ------------------------------------------------------------
-    # P-VALUE VS. L_X
-
-    # value = "xray_flux_erg_s"
-    # valuelabel = r"$L_X$ [erg/s]"
-
-    # valuelegend = legend[1:]
-    # valuelabels = labels[1:]
-
-
-    # make_adtest_figure(df, value, valuelabel,  valuelegend, valuelabels)
-
+    # MULTIPICITY
     # ------------------------------------------------------------
 
-    # define the colors and symbols for the different Lx
+    # define the colors and symbols for the different multiplicity
     df["color"], df["symbol"] = zip(*df.sy_snum.apply(colorcode_multiplicity))
 
     # ------------------------------------------------------------
     # P-VALUE VS. P_SPI with Bp=1G
 
[…]

### 2023-02-01 src/scripts/paper_main_table.py

@@ -124,6 +124,22 @@ def round_to_decimals(df, col, err, err2=None, typ="err"):
         del df["_"]
         return val, err, err2
 
+def convert_to_scinote(series, rel_err=1e-2):
+    """Convert a series to scientific notation.
+
+    Parameters
+    ----------
+    series : pd.Series
+        The series to convert.
+
+    Returns
+    -------
+    pd.Series
+        The converted series of strings.
+    """
+
+    return series.apply(lambda x: f"{x:.1e}" if np.abs(x)<rel_err else x).astype(str)
+
 
 def tex_up_low(val, err, err2):
     """Convert a value and two errors into a LaTeX string.
@@ -143,7 +159,12 @@ def tex_up_low(val, err, err2):
         The LaTeX string.
     """
 
-    return "$" + val.astype(str) + r"^{" + err.astype(str) + "}_{" + err2.astype(str) + "}$"
+    return ("$" +
+            convert_to_scinote(val) +
+            r"^{" + 
+            convert_to_scinote(err) + 
+            "}_{" +
+            convert_to_scinote(err2) + "}$")
 
 def tex_one_err(val, err):
     """Convert a value and one error into a LaTeX string.
@@ -161,7 +182,10 @@ def tex_one_err(val, err):
         The LaTeX string.
     """
 
-    return val.astype(str) + "[" + err.apply(lambda x: f"{x:.1e}" if x<1e-2 else x).astype(str) + "]"
+    return (convert_to_scinote(val) +
+            "[" +
+            convert_to_scinote(err) +
+            "]")
 
 # for each type of value cols, define a function that
 # converts them into one list of strings for latex
@@ -222,8 +246,10 @@ if __name__ == "__main__":
 
             ("Ro","Ro_high","Ro_low", 'high-low'),
             ("B_G","B_G_high","B_G_low", 'high-low'),
-            ("p_spi_erg_s","p_spi_erg_s_high","p_spi_erg_s_low",'high-low'),
-            ('p_spi_kav22', 'p_spi_kav22_high','p_spi_kav22_low', 'high-low'),
[…]

### 2023-02-01 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+\subsection{Kepler and TESS photometry}
+Between 2009 and 2013, the Kepler space telescope~\citep{koch2010kepler} nearly continuously observed a patch of the sky in the Cygnus-Lyra region.
+Each of the 18 observing Quarters contains nearly uninterrupted $\sim 90$ days of observations, totaling over 100000 stars monitored in 2-min cadence.
+% 100000 from here: https://exoplanetarchive.ipac.caltech.edu/docs/KeplerMission.html
+
+The Transiting Exoplanet Survey Satellite~(TESS,~\cite{ricker2015transiting}) is an all-sky mission that began operations in 2018, completed two sky scans until summer 2022.
+It is observing at the time of writing, collecting nearly continuous photometric time series in the 600-1000 nm band for $\sim 27 days$ in each observing Sector.
+About $200\,000$ stars have been observed in 2-min cadence in the first two years of operations with about 20000 targets per Sector.
+Out of these, from Sector 27 on, 1000 targets were observed at even higher 20-s cadence in each Sector.
+% 20000 per sector does not add up, because of stars observed in multiple sectors, the 20000 and 1000 figures can be found here: https://tess.mit.edu/observations/target-lists/
+% extended TESS mission https://heasarc.gsfc.nasa.gov/docs/tess/extended.html
+
+Based on the filtered PSCP and TT tables, we queried the full Kepler archive (quarters Q0-Q17, Data Release 25) and most recent TESS catalog (July 2022) for their respective 1-min and 2-min/20-s cadence light curves, accounting for systems that appeared in both catalogs.
+In total, we obtained XXXX Kepler light curves and XXXX TESS light curves.
+XXXX systems were observed only by the primary Kepler mission, XXXX only by TESS, and XXXX by both missions.
+
 \subsection{Orbital periods}
@@
 
-\subsection{Relative velocity}
-
-We calculate the relative velocity between the magnetic field of the star, assumed to be co-rotating, at the planetary orbit, as
-
-\begin{equation}
-    v_{rel} = 2 \pi a \left(\dfrac{1}{P_{orb}} - \dfrac{1}{P_{rot}}\right) 
-\end{equation}
-
-We use quadratic error propagation to estimate the uncertainty in $v_{rel}$ with the mean of the upper and lower uncertainty values on the orbital period and rotation period, if both are given, and the uncertainty on semi-major axis as derived in Sec.~\ref{sec:data:a}.
-
 %Transit information
 %Full sample statistics
-\subsection{Kepler and TESS photometry}
-Between 2009 and 2013, the Kepler space telescope~\citep{koch2010kepler} nearly continuously observed a patch of the sky in the Cygnus-Lyra region.
-Each of the 18 observing Quarters contains nearly uninterrupted $\sim 90$ days of observations, totaling over 100000 stars monitored in 2-min cadence.
-% 100000 from here: https://exoplanetarchive.ipac.caltech.edu/docs/KeplerMission.html
-
-The Transiting Exoplanet Survey Satellite~(TESS,~\cite{ricker2015transiting}) is an all-sky mission that began operations in 2018, completed two sky scans until summer 2022.
-It is observing at the time of writing, collecting nearly continuous photometric time series in the 600-1000 nm band for $\sim 27 days$ in each observing Sector.
-About $200\,000$ stars have been observed in 2-min cadence in the first two years of operations with about 20000 targets per Sector.
-Out of these, from Sector 27 on, 1000 targets were observed at even higher 20-s cadence in each Sector.
-% 20000 per sector does not add up, because of stars observed in multiple sectors, the 20000 and 1000 figures can be found here: https://tess.mit.edu/observations/target-lists/
-% extended TESS mission https://heasarc.gsfc.nasa.gov/docs/tess/extended.html
-
-Based on the filtered PSCP and TT tables, we queried the full Kepler archive (quarters Q0-Q17, Data Release 25) and most recent TESS catalog (July 2022) for their respective 1-min and 2-min/20-s cadence light curves, accounting for systems that appeared in both catalogs.
-In total, we obtained XXXX Kepler light curves and XXXX TESS light curves.
-XXXX systems were observed only by the primary Kepler mission, XXXX only by TESS, and XXXX by both missions.
 
@@
 % We take the \cite{foster2022exoplanet} X-ray luminosity catalog as the basis for our calculation, assuming an uncertainty of 30\% in the reported values, covering typical intrinsic variability among stars of similar rotation periods in studies like ~\cite{wright2011stellaractivityrotation, wright2018stellar}.
-
-\subsection{Stellar magnetic fields}
-\cite{foster2022identifying} and \cite{reiners2022magnetism}
-
-The intrinsic scatter in Eq.
-4 in \cite{reiners2022magnetism} dominates the uncertainty in B over the uncertainty in stellar radius and $L_X$.
-We use the $+/-1\sigma$ values for the latter two for the final uncertainty estimate $\sigma B$
-
-The estimate is consistent with existing Zeeman broadening for, e.g. AU Mic (3010 G~\cite{reiners2022magnetism})
-\subsection{Transit mid-times}
 
@@
 We then perform a customized Anderson-Darling test on the flare peak time distribution, which yields a p-value for the significance of the SPI signal.
-We compare these results to theoretical SPI power $P_{SPI}$ using the scaling relations in~\cite{lanza2012starplanet}, where $P_{SPI}$ is proportional to
-
-\begin{equation}
-    P_{SPI} \sim B_p^{2/3} B_*^{4/3} v_{rel} R_p^2.
-\end{equation}
-
-$B_p$ and $B_*$ are the total planetary and stellar surface field strengths, respectively; $v_{rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis; and $R_p$ is the planetary radius.
+We compare these results to theoretical SPI power $P_{SPI}$
 
@@
 Use transit mid-times from the same mission if possible.
-
+\subsection{Custom Anderson-Darlin test}
 Anderson-Darling test here. Used four equidistant start phases instead of 20, because it does not change much.
 
-\cite{foster2022identifying} and \cite{reiners2022magnetism} to get Lx and then B.
+\subsection{Relative velocity}
+
+We calculate the relative velocity between the magnetic field of the star, assumed to be co-rotating, at the planetary orbit, as
+
+\begin{equation}
+    v_{rel} = 2 \pi a \left(\dfrac{1}{P_{orb}} - \dfrac{1}{P_{rot}}\right) 
+\end{equation}
+
+We use quadratic error propagation to estimate the uncertainty in $v_{rel}$ with the mean of the upper and lower uncertainty values on the orbital period and rotation period, if both are given, and the uncertainty on semi-major axis as derived in Sec.~\ref{sec:data:a}.
+
+\subsection{Stellar magnetic fields}
+We derive B from Ro using Eq. XXX in \cite{reiners2022magnetism}:
+
+The estimate is consistent with existing Zeeman broadening for, e.g. AU Mic (3010 G~\cite{reiners2022magnetism})
+\subsection{Power of star-planet interaction}
+
+We estimate the power of star-planet interaction generated by the strech-and-break mechanism using the scaling relations in~\cite{lanza2012starplanet} (their Eqn.
+45), where $P_{sb}$ is proportional to
+
+\begin{equation}
+    P_{sb} \sim B_p^{2/3} B_*^{4/3} v_{rel} R_p^2 a^{-4} R_*^4.
+\end{equation}
+
+$B_p$ and $B_*$ are the total planetary and stellar surface field strengths, respectively; $v_{rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis; and $R_*$ and $R_p$ are the stellar and planetary radii, respectively; and $a$ is the semi-major axis.
+
+We also consider the case of an unmagnetized planet with $B_p=0$, in which case Eq.~45 in~\cite{lanza2012starplanet} reduces to
+
+\begin{equation}
+    P_{sb0} \sim B^2 v_{rel}  R_p^2  a^{-4} R_*^4
+\end{equation}
+
+For comparison, we estimate the power of star-planet interaction generated by the Alfv\'en wing mechanism ~\cite{saur2013magnetic,kavanagh2022radio}, combining Eqs.~8~and~11 in \cite{kavanagh2022radio} to give
+
+\begin{equation}
+    P_{aw} \sim R_{p}^2  B_p^{2/3}  B^{1/3}  v_{rel}^2 * a^{-2}  
+\end{equation}
+where we approximate the stellar wind density $\rho_W$ with $a^{-2}$ and stellar wind magnetic field at the planetary radius $B_W$ with the surface field strength $B a^{-3}$, which result in the total $a^{-2}$ factor.
+
+Here, we also consider the case of an unmagnetized planet with $B_p=0$, in which case Eq.~8 in \cite{kavanagh2022radio} reduces to
+
+\begin{equation}
+    P_{aw0} \sim R_p^2  B  v_{rel}^2  a^{-4}
+\end{equation}
 
@@
 
-\subsubsection{DS Tuc A}
-It's a multiple
-\subsubsection{Kepler-1651}
-It's a multiple
-
-\subsubsection{Excluded flaring star-planet systems}
-\paragraph{LTT 1445}
- LTT 1445 is a hierarchical triple wherein LTT 1445 A hosts two close-in planets, and LTT 1445 B and C are a tight binary system separated by about 7 arcsec, that is, blended in one TESS pixel~\citep{winters2019three}.
-Both the binary and LTT 1445 A have been detected with flares in X-ray~\citep{brown2022xray}.
-Recently, LTT 1445 A was found to host a second planet LTT 1445 Ac inwards of LTT 1445 Ab~\citep{lavie2022planetary}.
-The rotation periods are not known, so it does not appear in the final figure.
-
-\paragraph{HD 41004 B}
-Hierarchical system, composed of HD 41004 A and its Jupiter HD 41004 Ab, and HD 41004 B.
-an M dwarf, and its brown dwarf companion HD 41004 Bb.
-The rotation periods are not well-known, so it does not appear at all in the final figure.
-
 \subsection{Combined Sample}
@@
 
+\subsection{Eccentricity}
+The star-planet systems in this work do not have notably eccentric orbits.
 \bibliography{bib}

### 2023-02-01 src/scripts/paper_main_table.py
formatting

@@ -374,6 +374,8 @@ if __name__ == "__main__":
         string = string.replace("midrule","hline")
         string = string.replace("toprule","hline")
         string = string.replace("bottomrule","hline")
+        for n in range(1,10):
+            string = string.replace(fr"e-0{n}",fr"\cdot 10^{{-{n}}}")
 
         # replace the bibkeys with the index in the string table
         for key in bibkeys.keys():

### 2023-02-01 src/scripts/paper_main_table.py
still fixing table

@@ -108,7 +108,7 @@ def round_to_decimals(df, col, err, err2=None, typ="err"):
     """
 
     df["_"] = get_len_decimals(df, col, err, err2=err2,typ=typ).astype(int)
-    val = df.apply(lambda x: np.round(x[col], x._) if np.abs(x[err])<1 else  np.round(x[col],0).astype(int), axis=1)
+    val = df.apply(lambda x: np.round(x[col], x._) if np.abs(x[col])<1 else  np.round(x[col],0).astype(int), axis=1)
     
     if err2 is None:
         err = df.apply(lambda x: np.round(x[err], x._) if x[err]<1 else np.round(x[err],0).astype(int), axis=1)
@@ -137,8 +137,8 @@ def convert_to_scinote(series, rel_err=1e-2):
     pd.Series
         The converted series of strings.
     """
-
-    return series.apply(lambda x: f"{x:.1e}" if np.abs(x)<rel_err else x).astype(str)
+    print(rel_err)
+    return series.apply(lambda x: f"{x:.1e}" if np.abs(x)<rel_err else f"{x:.2f}").astype(str)
 
 
 def tex_up_low(val, err, err2):
@@ -160,11 +160,11 @@ def tex_up_low(val, err, err2):
     """
 
     return ("$" +
-            convert_to_scinote(val,rel_err=1e-9) +
-            r"^{" + 
-            convert_to_scinote(err,rel_err=1e-9) + 
+            convert_to_scinote(val) +
+            "^{" + 
+            convert_to_scinote(err) + 
             "}_{" +
-            convert_to_scinote(err2,rel_err=1e-9) + "}$")
+            convert_to_scinote(err2) + "}$")
 
 def tex_one_err(val, err):
     """Convert a value and one error into a LaTeX string.
@@ -209,24 +209,27 @@ def to_tex(df, col):
    
         if col[2][-6:] == "bibkey":
 
-            val, err = round_to_decimals(df, col[0], col[1],typ=col[3])
-            tex = tex_one_err(val, err) + citation_from_bibkey(df[col[2]])
-   
+            # val, err = round_to_decimals(df, col[0], col[1],typ=col[3])
+            # tex = tex_one_err(val, err) + citation_from_bibkey(df[col[2]])
+            tex = tex_one_err(df[col[0]], df[col[1]]) + citation_from_bibkey(df[col[2]])
         else:
    
[…]

### 2023-02-01 src/scripts/paper_adtext_vs_value_scatterplots.py
4er figure

@@ -160,8 +160,46 @@ def colorcode_Lx(lx):
 
     return color, symbol
 
+def colorcode_B_G(bg):
+    """Define color code and symbol marker for B_G.
 
-def make_adtest_figure(df, value, valuelabel, legend, labels, ext):
+    Parameters
+    ----------
+    bg : float
+        Magnetic field strength in Gauss.
+
+    Returns
+    -------
+    color : str
+        Color code.
+    marker : str
+        Symbol marker.
+    """
+    if bg < 100.:
+        color = "lightgrey"
+        symbol = "s"
+
+    elif 100 <= bg < 1000.:
+        color = "blue"
+        symbol = "x"
+
+    elif 1000 <= bg < 2000.:
+        color = "black"
+        symbol = "d"
+
+    elif bg >= 2000.:
+        color = "green"
+        symbol = "o"
+
+    else:
+        color = "r"
+        symbol = "*"
+    
+
+    return color, symbol
+
+
+def make_adtest_figure(df, value, valuelabel, legend, labels, ext, ax, leg=False):
     """Create an AD test vs. value figure.
     
     Parameters
@@ -178,6 +216,8 @@ def make_adtest_figure(df, value, valuelabel, legend, labels, ext):
         List of legend labels.
     ext : str
         Extension for the figure name.
+    ax : matplotlib.axes._subplots.AxesSubplot
+        Axes to plot on.
     
     Returns
     -------
@@ -189,15 +229,9 @@ def make_adtest_figure(df, value, valuelabel, legend, labels, ext):
     # get reference sigma values
     sigmas, sigma_labels = get_sigma_values()
 
-    # set up figure
-    fig, ax = plt.subplots(figsize=(10, 6.5))
 
     data = df[df[value].notnull()]
-    norm = data.loc[data.ID=="AU Mic",value].values[0]
-    
-    data[value] = data[value] / norm
-    data[f"{value}_high"] = data[f"{value}_high"] / norm
-    data[f"{value}_low"] = data[f"{value}_low"] / norm
+
     texts = []
 
     # plot the data
@@ -205,51 +239,47 @@ def make_adtest_figure(df, value, valuelabel, legend, labels, ext):
 
         # make the scatter plot
         x = group[value]
-        xhigh = group[f"{value}_high"]
-        xlow = group[f"{value}_low"]
-        plt.errorbar(x, group["mean"], 
+        xhigh = group[value]
+        xlow = group[value]
[…]

### 2023-02-01 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Use transit mid-times from the same mission if possible.
-\subsection{Custom Anderson-Darlin test}
+\subsection{Custom Anderson-Darling test}
 Anderson-Darling test here. Used four equidistant start phases instead of 20, because it does not change much.
@@
 \begin{table*}
+\footnotesize
 \movetableright=-20mm
@@
 
-% \begin{figure*}[ht!]
-%     \script{paper_adtext_vs_value_scatterplots.py}
-%     \begin{centering}
-%         \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_p_spi_erg_s_bp0.png}
-%         \caption{
-%             Expected power of SPI vs.
-AD test results, assuming an unmagnetized planet.
-These results are mainly dominated by the X-ray luminosity of the host star, see Fig.~\ref{fig:adtest_xray_flux_erg_s}.
-Assuming a magnetized planet with $B_p=1$ G has only minor influence on the results shown in this figure, see Appendix.
-%         }
-%         \label{fig:adtest_p_spi_erg_s_bp0}
-%     \end{centering}
-% \end{figure*}
+\begin{figure*}[ht!]
+    \script{paper_adtext_vs_value_scatterplots.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_bg.png}
+        \caption{
+            Expected power of SPI vs. AD test results, assuming four different scenarios, colorcoded but stellar surface field strength.
+        }
+        \label{fig:adtest_bp}
+    \end{centering}
+\end{figure*}
 
@@
 
-\begin{figure*}[ht!]
-    \script{paper_adtext_vs_value_scatterplots.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_p_spi_erg_s_sab_wBp_colorcode_dist.png}
-        \caption{
-            Expected power of SPI from stretch and break vs. AD test results, assuming a magnetized planet with $B_p=1$ G. 
-        }
-        \label{appendix:fig:adtest_p_spi_erg_s}
-    \end{centering}
-\end{figure*}
-
 \end{document}

### 2023-02-14 src/scripts/paper_adtext_vs_value_scatterplots.py
improved figure styles, added cumdist for transiting and RV targets

@@ -239,8 +239,8 @@ def make_adtest_figure(df, value, valuelabel, legend, labels, ext, ax, leg=False
 
         # make the scatter plot
         x = group[value]
-        xhigh = group[value]
-        xlow = group[value]
+        xhigh = group[value + "_high"]
+        xlow = group[value + "_low"]
         ax.errorbar(x, group["mean"], 
                         xerr=[x - xlow, xhigh - x],
                          yerr=group["std"],

### 2023-02-14 src/scripts/paper_cumdist_individual_rv.py

@@ -1,0 +1,106 @@
+"""
+Python 3.8 -- UTF-8
+
+Ekaterina Ilin, 2022, MIT License
+
+Script that generates the individual cumulative distribution 
+plot for the paper using the final flare table.
+"""
+
+import paths
+
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.lines import Line2D
+
+
+if __name__ == "__main__":
+
+    # get matplotlib style
+    plt.style.use(paths.scripts / 'paper.mplstyle')
+
+    # read in flare table
+    df = pd.read_csv(paths.data / "PAPER_flare_table.csv")
+
+    # pick only real flares
+    df = df[(~df.tstart.isnull()) & (df.orbital_phase==-1)]
+
+    # only use the systems that appear in the results table
+    res = pd.read_csv(paths.data / "results.csv")
+
+    tics = res[(res.multiple_star.isnull()) & (res.multiple_star_source != "BD")]
+    tics = tics.sort_values(by="number_of_flares", ascending=False).TIC.astype(str)
+
+    tics = tics.values
+
+    # make a plot for 15 panels
+    fig, ax = plt.subplots(nrows=3, ncols=3, figsize=(14,11), sharex=True)
+
+    # linearize the axes
+    ax = [_1 for _0 in ax for _1 in _0]
+
+    # create a subplot for each star
+    for tic in tics:
+
+        # print(g.shape)
+        g = df[df.TIC.astype(str) == tic]
+        print(tic, g.shape, len(ax))
+        # pick only stars with more than 0 flares
+        if ((g.shape[0]>3) & (len(ax)>0)):
+            
+            # pick an axis
+            a = ax.pop()
+            
+            # gey the ID
+            ID = g.ID.iloc[0]
+            
+            # if no ID, use TIC instead
+            if str(ID)=="nan":
+                print(ID)
+                ID = f"TIC {g.TIC.iloc[0]}"
+
+            # get the orbital period
+            orbper = res[res.TIC.astype(str) == tic].orbper_d.values[0]
+            
+            # calculate the phases
+            phases = g.tstart.values / orbper % 1.
+
+            # sort the phases
+            phases = np.sort(phases)
+            
+            # define the bins
+            bins = np.linspace(0,1,len(phases))
+    
+            # plot the histogram
+            a.hist(phases, bins=bins, histtype="step",
+                cumulative=True,)
+            
[…]

### 2023-02-14 src/scripts/paper_cumdist_individual_transiting.py

@@ -26,29 +26,28 @@ if __name__ == "__main__":
     # pick only real flares
     df = df[df.orbital_phase != -1]
 
-    # get the 15 stars with the most flares as a sorted list
-    tics = df.groupby("TIC").count().sort_values("ED", ascending=False)
-    tics = tics.head(15).reset_index().TIC.values
+    # only use the systems that appear in the results table
+    tics = pd.read_csv(paths.data / "results.csv")
 
-    # get the subsample of most active stars
-    new_df = df[df.TIC.isin(tics)]
+    tics = tics[(tics.multiple_star.isnull()) & (tics.multiple_star_source != "BD")]
+    tics = tics.sort_values(by="number_of_flares", ascending=False).TIC.astype(str)
 
-    # defined categorical index for tics
-    new_df['TIC'] = pd.Categorical(new_df['TIC'], tics)
-
-    # sort by new categorical index
-    new_df = new_df.sort_values("TIC", ascending=False)
+    tics = tics.values
 
     # make a plot for 15 panels
-    fig, ax = plt.subplots(nrows=5, ncols=3, figsize=(14,18))
+    fig, ax = plt.subplots(nrows=6, ncols=3, figsize=(14,19), sharex=True)
 
     # linearize the axes
     ax = [_1 for _0 in ax for _1 in _0]
 
     # create a subplot for each star
-    for i, g in new_df.groupby("TIC"):
-        # pick only stars with more than 8 flares
-        if ((g.shape[0]>8) & (len(ax)>0)):
+    for tic in tics:
+
+        # print(g.shape)
+        g = df[df.TIC.astype(str) == tic]
+        print(tic, g.shape, len(ax))
+        # pick only stars with more than 0 flares
+        if ((g.shape[0]>=3) & (len(ax)>0)):
             
             # pick an axis
             a = ax.pop()
@@ -63,13 +62,13 @@ if __name__ == "__main__":
 
             # ge the phases
             phases = g.orbital_phase.sort_values(ascending=True).values
-        
+            # print(phases)
             # define the bins
             bins = np.linspace(0,1,len(phases))
     
             # plot the histogram
             a.hist(phases, bins=bins, histtype="step",
-                cumulative=True,);
+                cumulative=True,)
             
             # make a line for the legend
             line = Line2D([0], [0], color='w', linestyle='-', 
@@ -86,11 +85,16 @@ if __name__ == "__main__":
[…]

### 2023-02-14 src/scripts/paper_rename_trappist.py

@@ -1,0 +1,41 @@
+"""
+Python 3.8 -- UTF-8
+
+Ekaterina Ilin, 2022, MIT License
+
+Script that renames EPIC 200164267 to TRAPPIST-1, and drops Kepler-411(c) 
+in the tables.
+
+"""
+
+import paths
+
+import pandas as pd
+
+if __name__ == "__main__":
+
+    # read in flare table
+    df = pd.read_csv(paths.data / "PAPER_flare_table.csv")
+
+    # rename the star
+    df.loc[df.ID == "EPIC 200164267", "ID"] = "TRAPPIST-1"
+
+    # drop Kepler-411(c) from the flare table
+    df = df[df.ID != "Kepler-411(c)"]
+
+    # write to file
+    df.to_csv(paths.data / "PAPER_flare_table.csv", index=False)
+
+    # read in results table
+    df = pd.read_csv(paths.data / "results.csv")
+
+    # rename the star
+    df.loc[df.ID == "EPIC 200164267", "ID"] = "TRAPPIST-1"
+
+    # drop Kepler-411(c) from the results table
+    df = df[df.ID != "Kepler-411(c)"]
+
+    # write to file
+    df.to_csv(paths.data / "results.csv", index=False)
+
+    

### 2023-02-14 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \label{sec:data}
-\subsection{Star-Planet Systems}
-%Catalogs
-% as of January 2021
-We started our sample selection with the Planetary Systems Composite Parameters Table (PSCP)\footnote{ \url{https://exoplanetarchive.ipac.caltech.edu/cgi-bin/TblView/nph-tblView?app=ExoTbls&config=PSCompPars}} from which we removed controversial planet detections (``pl\_controv\_flag'' set to 1), i.e.
+\subsection{Star-planet systems}
+
+ction with the Planetary Systems Composite Parameters Table (PSCP)\footnote{ \url{https://exoplanetarchive.ipac.caltech.edu/cgi-bin/TblView/nph-tblView?app=ExoTbls&config=PSCompPars}} from which we removed controversial planet detections (``pl\_controv\_flag'' set to 1), i.e.
 detections with existing literature questioning the result.
@@
            Time span of observation vs.
-coherence time or the orbital and rotational periods, respectively.
+coherence time of the orbital and rotational periods, respectively.
 Orbital periods are all known precisely enough, so that the phase uncertainty at the last observed flare is of the order of $10^{-2}$.
@@
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/PAPER_flares_phase_hist.png}
+        \includegraphics[width=\linewidth]{figures/PAPER_flares_phase_hist_transiting.png}
         \caption{
-            Cumulative distributions of orbital phases of flares in the hosts observed by Kepler and TESS that had the most flares detected per star. 
+            Cumulative distributions of orbital phases of flares in the transiting planet hosts observed by Kepler and TESS with 4 or more flares each. 
         }
-        \label{fig:cumdist_active}
+        \label{fig:cumdist_transiting}
+    \end{centering}
+\end{figure*}
+
+\begin{figure*}[ht!]
+    \script{paper_cumdist_individual.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/PAPER_flares_phase_hist_rv.png}
+        \caption{
+            Cumulative distributions of orbital phases of flares in the RV planet hosts observed by Kepler and TESS with 4 or more flares each. 
+        }
+        \label{fig:cumdist_transiting}
     \end{centering}
@@
     \script{paper_main_table.py}
-    \caption{Star-planet systems.}
+    \caption{Flaring single star-planet system parameters.}
     \input{output/table_lit_vals.tex}
@@
 \script{paper_main_table.py}
-    \caption{Flaring SPI results.}
+\caption{Flaring star-planet interaction.
+$Ro$, $B$, and $v_{rel}$, are derived from literature values (Table~\ref{tab:maintable_lit}).
+$P_{xx}$ stands for the power of stretch-and-break ($sb$) and ALfv\'en wing ($aw$) interaction mechanisms, assuming the planet has a magnetic field strength of 1 G.
+$P_{xx0}$ is the same, but assuming an unmagnetized planet.
+All powers are normalized to AU Mic.
+The p-value of the Anderson-Darling test is lower when the system shows more flares periodic with the planetary orbit.}
 \input{output/table_der_vals.tex}
@@
         \caption{
-            Expected power of SPI vs. AD test results, assuming four different scenarios, colorcoded but stellar surface field strength.
+            Expected power of SPI vs. AD test results, assuming four different scenarios, color-coded by stellar surface field strength.
         }
@@
 \subsection{Individual stars}
+
+\subsubsection{Excluded targets}
+Kepler-808 (KOI 1300) has a $\sim0.4$ Msun \cite{kraus2016impact}companion that is about 1.8 mag fainter than the primary at a separation of .78 arcsec~\cite{baranec2016roboao}.
+
+TOI-837 has co-moving M dwarf a few arcsec away in the same young cluster, 5 mag fainter, but the primary is an F9-G0 star, so flare could come from both stars~\cite{bouma2020cluster}
+
+HD 41004 B and DS Tuc A and LTT 1445
+
+\subsubsection{Kepler-411}
+Kepler-411 has 3 mag fainter companion~\cite{wang2014influence,ziegler2018measuring}.
+It was observed in Kepler short cadence by \cite{jackman2021stellara} and both the planet host, and the companion flare.
+\cite{jackman2021stellara} disentangle the contributions on a pixel level.
+According to \cite{morton2016false, sun2019kepler411} the planets orbit the primary companion.
+In fact, the fainter companion of Kepler-411 appears to cause the majority of flares (41), whereas Kepler-411 causes only 7.
+We adopt the 7 flares from \cite{jackman2021stellara} for our analysis.
+
+\subsubsection{HAT-P-11}
+\cite{miskovetz2022resolving}  found background stars that were not co-moving HAT-P-11.
+HAT-P-11 rotates nearly pole-on, and HAT-P-11 b is transiting in a near-polar orbit~\citep{bourrier2023dream}.
+This may be the reason for absent SPI
 
@@
 \subsection{Spin-orbit alignment}
-
+or more broadly system architecture including misalignment of the magnetic axis. See HAT-P-11, or instance, and the many polar orbits in \cite{bourrier2023dream}
 \subsection{Eccentricity}
@@
 \appendix
-\section{Expected $P_{SPI}$ vs. measure flaring SPI with a magnetized planet}
+\section{Expected $P$ vs. measured flaring SPI}
 

### 2023-03-02 src/scripts/paper_flare_table_values.py
added flare catalog numbers

@@ -1,0 +1,45 @@
+"""
+
+Script that produces a LaTeX table with the 
+results of the flare finding and characterization.
+
+"""
+
+import paths
+import pandas as pd
+
+if __name__ == "__main__":
+
+    # Load the data
+    flare_table = pd.read_csv(paths.data / "PAPER_flare_table.csv")
+
+    # define total number of flares and write to file
+    total_number_of_flares = flare_table[~flare_table["tstart"].isnull()].shape[0]
+    print("Total number of flares: ", total_number_of_flares)
+
+    with open(paths.output / "PAPER_total_number_of_flares.txt", "w") as f:
+        f.write(f"{total_number_of_flares}")
+
+
+    # total number of systems with flares
+    total_number_of_systems_with_flares = flare_table[~flare_table["tstart"].isnull()]["TIC"].unique().shape[0]
+    print("Total number of systems with flares: ", total_number_of_systems_with_flares)
+
+    with open(paths.output / "PAPER_total_number_of_systems_with_flares.txt", "w") as f:
+        f.write(f"{total_number_of_systems_with_flares}")
+
+    # table contains only systems that flare
+    assert flare_table["TIC"].unique().shape[0] == total_number_of_systems_with_flares
+
+    # total number of light curves searched
+    total_number_of_light_curves = flare_table.groupby(["TIC", "quarter_or_sector"]).size().shape[0]
+    print("Total number of light curves: ", total_number_of_light_curves)
+
+    with open(paths.output / "PAPER_total_number_of_light_curves.txt", "w") as f:
+        f.write(f"{total_number_of_light_curves}")
+
+    # total number of light curves without flares
+    light_curves_without_flares = flare_table[flare_table["tstart"].isnull()].groupby(["TIC", "quarter_or_sector"]).size().shape[0]
+    print("Total number of light curves without flares: ", light_curves_without_flares)
+ 
+    assert flare_table.shape[0] == total_number_of_flares + light_curves_without_flares

### 2023-03-02 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+Stretch and break
+
+Alfven wing
+
 \section{Data}
@@
 Either Kepler/TESS or from RVs.
-
+\subsection{Transit mid-times}
+Use transit mid-times from the same mission if possible.
 \subsection{Semi-major axes}
@@
 We measure flaring star-planet interactions (SPI) as the presence of excess flares triggered by the orbiting planet.
-These excess flares manifest as a deviation of flare timing from a random Poisson process with orbital phase.
-That means that in the absence of flaring SPI, flare peak time will be distributed randomly in orbital phase.
+In the absence of flaring SPI, flare peak times will be distributed randomly in orbital phase.
 In the presence of flaring SPI, we measure a phase dependent deviation from this randomness.
@@
 We then perform a customized Anderson-Darling test on the flare peak time distribution, which yields a p-value for the significance of the SPI signal.
-We compare these results to theoretical SPI power $P_{SPI}$
+Finally, we compare these results to the theoretically expected SPI power $P_{SPI}$ in each system.
 
-The methods for light curve de-trending and flare finding in Kepler and TESS light curves, as well as the Anderson-Darling test, are the same as detailed in~\citep{ilin2022searching}.
-We therefore only briefly recap the techniques here:
+The methods for light curve de-trending and flare finding in Kepler and TESS light curves, as well as the Anderson-Darling test, are the same as detailed in~\citet{ilin2022searching}.
+We briefly recap the techniques in Sections~\ref{methods:flaresearch} and \ref{methods:adtest}.
+The expected power of SPI depends on the relative velocity between the planet and the magnetic field strength in its orbit, the derivation of which we explain in
+Sections~\ref{methods:relvel} and \ref{methods:bfield}, respectively.
+With relative velocity and magnetic field strength derived, we can combine them with stellar radius, planetary radius, and semi-major axis to estimate the power of SPI.
+We use the scaling laws from two different magnetic SPI models, which we introduce in Section~\ref{methods:pspi}.
 
+\subsection{Light curve de-trending and flare search}
+\label{methods:flaresearch}
 To remove trends and rotational variability from the light curve without losing the flare signal, we use an empirically derived multistep process.
@@
 Then, we iteratively fit a series of sines to capture rotational signal on time scales down to about half a day, close to the fastest rotational signals measured in low mass stars.
-Eventually, we apply two Savitzky-Golay filters in sequence, with decreasing periods at each step.
-At this stage, we mask all data points above a 2.5 sigma (or 1.5 sigma for very active stars) threshold as flare candidates to prevent the filter from ironing out the flares.
+Eventually, we apply two Savitzky-Golay~\cite{savitzky1964smoothing} filters in sequence, with window sizes of 6h and 3h each.
+At this stage, we mask all data points above a $2.5 \sigma$ (or $1.5 \sigma$ for very active stars like AU Mic or Proxima Cen) threshold as flare candidates to prevent the filter from ironing out the flares.
+As a final step, we fit exponential functions to the edges of the light curves, if there are data points that deviate more than one standard deviation from the median value, while keeping the flare candidates masked.
 
-Flare finding here. Manual vetting
+In these light curves, we then search for flares as series of at least three consecutive data points $3\sigma$ above the noise level, implemented in AltaiPony~\cite{ilin2021altaipony}.
+We estimate the noise
+level as the standard deviation in a rolling window of two hours, while masking deviation above $2.5\sigma$ (or $1.5$ sigma for active stars).
+To capture the exponential tail of the flare, we use the \texttt{addtail} flag to continue adding data points to the end of the flare as long as they are $2\sigma$ above the noise threshold.
+For these flares, we calculate the relative amplitude $a$ and equivalent duration $ED$, defined as the integrated flare flux $F_{flare}$ over the duration of the flare, divided by the median flux $F_0$ of the star, integrated over the flare duration~\citep{gershberg1972results}:
+\begin{equation}
+\label{eq:ED}
+ED=\displaystyle \int \mathrm dt\, \frac{F_{flare}(t)}{F_0}.
+\end{equation}
+Equivalent duration is the time during which the non-flaring star releases as much energy as the flare.
 
-Orbital phase finding. Check coherence times. Orbital period is enough.
-Use transit mid-times from the same mission if possible.
 \subsection{Custom Anderson-Darling test}
-Anderson-Darling test here. Used four equidistant start phases instead of 20, because it does not change much.
+\label{methods:adtest}
+For each star-planet system with three or more flares in their Kepler and/or TESS light curves, we test for deviations from a random distribution of flares with orbital phase.
+We use the same customized Anderson-Darling test as in \cite{ilin2022searching}.
+In brief, we first take the number of flares observed in the TESS and Kepler data, calculate a base flare rate for each light curve.
+We then calculate how often each orbital phase has been covered by the data, again for each light curve.
+With the phase coverage and base flare rate combined, we can tell how many flares we would expect to see in any given phase bin if flares were randomly distributed.
+This number of expected flares per bin can be aggregated into one expected distribution by summing over all available light curves.
+As a last step, this distribution is then compared to the observed one using an Anderson-Darling test.
+We repeat this test with different phase offsets to account for potential biases in sensitivity of the test at different phases.
+
+The only adjustment to the procedure in \cite{ilin2022searching} is that we use four equidistant start phases (i.e., 0, 0.25, 0.5 and 0.75) compared to the 20 used in~\cite{ilin2022searching} to save time, and because the range of derived $p$-values is already well-sampled using four.
+We adopt the standard deviation of these four $p$-values as the uncertainty on the flaring SPI measurement.
+
+% \subsection{Orbital phase}
+% \label{methods:orbitalphase}
+
+% For the star-planet system that have transiting innermost planets, we use the transit mid-time to signify orbital phase zero.
+For non-transiting planets, we use arbitrary phase zero.
+The inferior conjunction time from the orbital parameters of planets that only have radial velocity measurements is usually either very uncertain, of the order of $10\%$ of the orbital duration~(XXXX), or cannot be derived because the eccentricity is poorly constrained~(XXXX).
 
 \subsection{Relative velocity}
-
-We calculate the relative velocity between the magnetic field of the star, assumed to be co-rotating, at the planetary orbit, as
+\label{methods:relvel}
+We calculate the relative velocity between the magnetic field of the star, which we assume is co-rotating with the stellar rotation period $P_{rot}$, at the planetary orbit, where the planet moves with a period $P_{orb}$:
 
 \begin{equation}
-    v_{rel} = 2 \pi a \left(\dfrac{1}{P_{orb}} - \dfrac{1}{P_{rot}}\right) 
+    v_{rel} = 2 \pi a \left(\frac{1}{P_{orb}} - \frac{1}{P_{rot}}\right).
 \end{equation}
 
-We use quadratic error propagation to estimate the uncertainty in $v_{rel}$ with the mean of the upper and lower uncertainty values on the orbital period and rotation period, if both are given, and the uncertainty on semi-major axis as derived in Sec.~\ref{sec:data:a}.
+We use quadratic error propagation to estimate the uncertainty in $v_{rel}$ with the mean of the upper and lower uncertainty values on the orbital period and rotation period, if both are given, and the uncertainty on semi-major axis $a$ as derived in Sec.~\ref{sec:data:a}.
 
 \subsection{Stellar magnetic fields}
-We derive B from Ro using Eq. XXX in \cite{reiners2022magnetism}:
+\label{methods:bfield}
+We derive the average magnetic field strength $B$ from $Ro$ using the empirical relation derived in \cite{reiners2022magnetism},  Table 2, in the unsaturated and saturated regimes, respectively:
+
+\begin{eqnarray}
+    B &= 199\,\text{G} \cdot Ro^{-1.26\pm 0.1} \;(\text{if}\; Ro > 0.13) \\
+    B &= 2050\,\text{G} \cdot Ro^{-0.11\pm 0.03} \;(\text{if}\; Ro < 0.13) 
+\end{eqnarray}
 
@@
 \subsection{Power of star-planet interaction}
+\label{methods:pspi}
+We consider two theories for the mechanism behind flaring star-planet interactions, the stretch-and-break and the Alfv\'en wing mechanisms.
+For both of them, we include the case of a magnetized and an unmagnetized planet, for a total of estimates of the expected power of magnetic star-planet interaction.
 
-We estimate the power of star-planet interaction generated by the strech-and-break mechanism using the scaling relations in~\cite{lanza2012starplanet} (their Eqn.
+First, we estimate the power of star-planet interaction generated by the stretch-and-break mechanism using the scaling relations in~\cite{lanza2012starplanet} (their Eqn.
 45), where $P_{sb}$ is proportional to
@@
 
-We also consider the case of an unmagnetized planet with $B_p=0$, in which case Eq.~45 in~\cite{lanza2012starplanet} reduces to
+Second, we also consider the case of an unmagnetized planet with $B_p=0$, in which case Eq.~45 in~\cite{lanza2012starplanet} reduces to
 
 \begin{equation}
-    P_{sb0} \sim B^2 v_{rel}  R_p^2  a^{-4} R_*^4
+    P_{sb0} \sim B_*^2 v_{rel}  R_p^2  a^{-4} R_*^4
 \end{equation}
 
-For comparison, we estimate the power of star-planet interaction generated by the Alfv\'en wing mechanism ~\cite{saur2013magnetic,kavanagh2022radio}, combining Eqs.~8~and~11 in \cite{kavanagh2022radio} to give
+Third, for comparison, we estimate the power of star-planet interaction generated by the Alfv\'en wing mechanism ~\cite{saur2013magnetic,kavanagh2022radio}, combining Eqs.~8~and~11 in \cite{kavanagh2022radio} to give
 
 \begin{equation}
-    P_{aw} \sim R_{p}^2  B_p^{2/3}  B^{1/3}  v_{rel}^2 * a^{-2}  
+    P_{aw} \sim R_{p}^2  B_p^{2/3}  B^{1/3}  v_{rel}^2 a^{-2}  
 \end{equation}
@@
 
-Here, we also consider the case of an unmagnetized planet with $B_p=0$, in which case Eq.~8 in \cite{kavanagh2022radio} reduces to
+And fourth, we finally consider the case of an unmagnetized planet with $B_p=0$, in which case Eq.~8 in \cite{kavanagh2022radio} reduces to
 
@@
 
+Our goal was to measure magnetic star-planet interaction as the presence of excess flares in phase with the innermost planet's orbit.
+We searched all star-planet systems that were observed with Kepler and TESS at 1 or 2 min cadence, respectively, for flares.
+For the star-planet systems in the resulting flare catalog~(Section~\ref{sec:results:catalog}), we confirmed that the orbital phase could be known well enough for the entire observing baseline of the system~(Section~\ref{sec:results:coherence}).
+Knowing that, we could move on to calculate the orbital phases of each flare, and calculate distributions for each system in the catalog~(Section \ref{sec:results:phasedist}).
+We then applied the custom Anderson-Darling test to check how likely it is that some of the flares were triggered by the planet.
+Comparing the test results with the expected power of magnetic star-planet interaction, we found that the probability of observing planet induced flares increases with the expected power in all considered scenarios~(Section~\ref{sec:results:spi}).
+However, not all systems with high expected power show signs of flaring SPI, which appears as a branching in the distribution of test results, and could be due to the intermittency of the interaction.
+Finally, we provide additional context for the most interesting systems in our sample, and explain why we had to exclude some systems from the analysis in Section~\ref{sec:results:individualstars}.
 \subsection{Flare catalog}
+\label{sec:results:catalog}
+We searched a total of XXXX light curves of XXXX star-planet systems for flares.
+We inspected all candidates manually, and added flares observed by K2 on TRAPPIST-1~\cite{paudel2018k2}, and flares from the planet hosting primary in the Kepler-411 binary~\cite{jackman2021stellara}.
+The final table contains a total of \input{output/PAPER_total_number_of_flares.txt} flares in \input{output/PAPER_total_number_of_systems_with_flares.txt} systems.
+In Table~\ref{tab:flares}, we list all the flares and their characteristics.
+To identify each event, we provide the name of the system in which the flare was found, along with its TIC, whether it was observed with Kepler or TESS, and during what Quarter or Sector, respectively.
+For each flare, we also give the start and finish time, relative amplitude $a$ and equivalent duration $ED$.
+If the transit midtime is known for the innermost planet, we also give the orbital phase at which the flare occurred.
 
@@
     \input{output/flare_table.tex}
-        \label{fig:random_numbers}
+        \label{tab:flares}
 \end{table*}
@@
 \subsection{Period coherence times}
-
+\label{sec:results:coherence}
 divide the coherence time of the orbital period by the observing baseline of the combined Kepler and TESS observations for each star.
@@
 \subsection{Flare phase distributions}
-
+\label{sec:results:phasedist}
 For details on AU Mic results, see~\citep{ilin2022searching}.
@@
 \begin{figure*}[ht!]
-    \script{paper_cumdist_individual.py}
+    \script{paper_cumdist_individual_transiting.py}
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/PAPER_flares_phase_hist_transiting.png}
+        \includegraphics[width=.95\linewidth]{figures/PAPER_flares_phase_hist_transiting.png}
         \caption{
             Cumulative distributions of orbital phases of flares in the transiting planet hosts observed by Kepler and TESS with 4 or more flares each.
+Phase zero corresponds to the transit mid-time of the planet.
         }
@@
 \begin{figure*}[ht!]
-    \script{paper_cumdist_individual.py}
+    \script{paper_cumdist_individual_rv.py}
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/PAPER_flares_phase_hist_rv.png}
+        \includegraphics[width=0.95\linewidth]{figures/PAPER_flares_phase_hist_rv.png}
         \caption{
-            Cumulative distributions of orbital phases of flares in the RV planet hosts observed by Kepler and TESS with 4 or more flares each. 
+            Cumulative distributions of orbital phases of flares in the RV planet hosts observed by Kepler and TESS with 4 or more flares each. Phase zero is chosen arbitrarily.
         }
@@
 \subsection{Flaring star-planet interaction signal}
+\label{sec:results:spi}
 We use the custom Anderson-Darling test detailed in \cite{ilin2022searching} to look for flaring SPI in all system with three flares or more.
@@
 \subsection{Individual stars}
-
+\label{sec:results:individualstars}
 \subsubsection{Excluded targets}
@@
 
+Any indication of flaring SPI anywhere else? Any reason to think there should be any?
+Why does HIP 67522 stick out so much? -- spin-orbit alignment
+
 \subsection{Rotational variability}
@@
 \subsection{Intermittency}
-
+\label{sec:discussion:intermittency}
 TAP 26 vs. HIP 67522, also different sectors for HIP 67522, see \cite{shkolnik2008nature}

### 2023-03-03 src/scripts/paper_cumdist_individual_rv.py
updated cumdist plots with expected distribution

@@ -21,10 +21,10 @@ if __name__ == "__main__":
     plt.style.use(paths.scripts / 'paper.mplstyle')
 
     # read in flare table
-    df = pd.read_csv(paths.data / "PAPER_flare_table.csv")
+    flares = pd.read_csv(paths.data / "PAPER_flare_table.csv")
 
     # pick only real flares
-    df = df[(~df.tstart.isnull()) & (df.orbital_phase==-1)]
+    flares = flares[(~flares.tstart.isnull()) & (flares.orbital_phase==-1)]
 
     # only use the systems that appear in the results table
     res = pd.read_csv(paths.data / "results.csv")
@@ -44,7 +44,7 @@ if __name__ == "__main__":
     for tic in tics:
 
         # print(g.shape)
-        g = df[df.TIC.astype(str) == tic]
+        g = flares[flares.TIC.astype(str) == tic]
         print(tic, g.shape, len(ax))
         # pick only stars with more than 0 flares
         if ((g.shape[0]>3) & (len(ax)>0)):
@@ -60,6 +60,13 @@ if __name__ == "__main__":
                 print(ID)
                 ID = f"TIC {g.TIC.iloc[0]}"
 
+            # read in file with phase distribution
+            df = pd.read_csv(paths.data / f"TIC_{tic}_cumhist.csv")
+            
+            # plot the distribution
+            a.plot(df.p, df.f, color="blue", linewidth=1.5)
+
+
             # get the orbital period
             orbper = res[res.TIC.astype(str) == tic].orbper_d.values[0]
             
@@ -69,23 +76,27 @@ if __name__ == "__main__":
             # sort the phases
             phases = np.sort(phases)
             
-            # define the bins
-            bins = np.linspace(0,1,len(phases))
-    
             # plot the histogram
-            a.hist(phases, bins=bins, histtype="step",
-                cumulative=True,)
-            
+            hist = np.cumsum(np.ones_like(phases))
+            hist = hist/hist[-1]
+            # insert 1 and 0 at the beginning and the end
+            hist = np.append(hist, 1)
+            hist = np.insert(hist, 0, 0)
+            phases = np.append(phases, 1)
+            phases = np.insert(phases, 0, 0)
+           
+            a.plot(phases, hist, color="k", linewidth=1.5)
+
             # make a line for the legend
             line = Line2D([0], [0], color='w', linestyle='-', 
                             linewidth=1, alpha=0.)
[…]

### 2023-03-03 src/scripts/paper_cumdist_individual_transiting.py

@@ -21,18 +21,17 @@ if __name__ == "__main__":
     plt.style.use(paths.scripts / 'paper.mplstyle')
 
     # read in flare table
-    df = pd.read_csv(paths.data / "PAPER_flare_table.csv")
+    flares = pd.read_csv(paths.data / "PAPER_flare_table.csv")
 
     # pick only real flares
-    df = df[df.orbital_phase != -1]
+    flares = flares[flares.orbital_phase != -1]
 
     # only use the systems that appear in the results table
     tics = pd.read_csv(paths.data / "results.csv")
+    tics = tics[tics.TIC != '399954349(c)']
 
     tics = tics[(tics.multiple_star.isnull()) & (tics.multiple_star_source != "BD")]
-    tics = tics.sort_values(by="number_of_flares", ascending=False).TIC.astype(str)
-
-    tics = tics.values
+    tics = tics.sort_values(by="number_of_flares", ascending=False)
 
     # make a plot for 15 panels
     fig, ax = plt.subplots(nrows=6, ncols=3, figsize=(14,19), sharex=True)
@@ -41,45 +40,45 @@ if __name__ == "__main__":
     ax = [_1 for _0 in ax for _1 in _0]
 
     # create a subplot for each star
-    for tic in tics:
+    for id_, row in tics.iterrows():
 
-        # print(g.shape)
-        g = df[df.TIC.astype(str) == tic]
-        print(tic, g.shape, len(ax))
-        # pick only stars with more than 0 flares
-        if ((g.shape[0]>=3) & (len(ax)>0)):
-            
-            # pick an axis
+        # get the orbital phases
+        phases = flares[flares.TIC.astype(str) == str(row.TIC)].orbital_phase.values
+
+        if (len(phases) > 2) & (len(ax) > 0):
             a = ax.pop()
-            
-            # gey the ID
-            ID = g.ID.iloc[0]
-            
-            # if no ID, use TIC instead
-            if str(ID)=="nan":
-                print(ID)
-                ID = f"TIC {g.TIC.iloc[0]}"
 
-            # ge the phases
-            phases = g.orbital_phase.sort_values(ascending=True).values
-            # print(phases)
-            # define the bins
-            bins = np.linspace(0,1,len(phases))
-    
-            # plot the histogram
-            a.hist(phases, bins=bins, histtype="step",
-                cumulative=True,)
+            # read in file with phase distribution
+            df = pd.read_csv(paths.data / f"TIC_{row.TIC}_cumhist.csv")
             
+            # plot the distribution
[…]

### 2023-03-03 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \label{sec:results:catalog}
-We searched a total of XXXX light curves of XXXX star-planet systems for flares.
+We searched a total of 3032 Kepler Quarters and 4181 TESS Sectors of a total of 1811 star-planet systems for flares.
 We inspected all candidates manually, and added flares observed by K2 on TRAPPIST-1~\cite{paudel2018k2}, and flares from the planet hosting primary in the Kepler-411 binary~\cite{jackman2021stellara}.
@@
 If the transit midtime is known for the innermost planet, we also give the orbital phase at which the flare occurred.
+The full table is provided with the supplementary material and via Zenodo (see Data Availability).
 
@@
 \label{sec:results:coherence}
-divide the coherence time of the orbital period by the observing baseline of the combined Kepler and TESS observations for each star.
+In many cases, the observing baseline covered by Kepler and TESS for a given system can span multiple years.
+In these cases, the orbital period of the innermost planet must be known very precisely so that we can assign accurate orbital phases to the flare events.
+We test this by dividing the timespan between the first and the last flare in the combined Kepler and TESS observations by the coherence time $\tau$ of the orbital period for each system.
+We calculate the coherence time as
 
-Do the same for the mid-times.
+\begin{equation}
+    \tau = P^2 / \sigma_P,
+\end{equation}
+where $P$ is the orbital period, and $\sigma_P$ is its uncertainty.
+The resulting ratio should be $<<1$.
+The bottom panel in Figure~\ref{fig:coherence_hist} shows a histogram of these ratios in our sample.
+The orbital period is known sufficiently well for our analysis in most cases with ratios $<0.02$.
+The three cases where the ratio is highest with $0.05$, $0.12$, $0.24$ deviation are TAP 26, GJ 3082, and GJ 674, respectively.
+We keep these systems in our sample, but caution that the measured absence of flaring SPI might be due to the uncertain orbital period of the planet in these cases.
+
+We repeated the coherence calculation for $P_{rot}$, and found that the ratio is $>.1$ for most stars~(Figure~\ref{fig:coherence_hist}, top panel).
+There are three reasons for this: First, the uncertainty for the rotation was not always provided.
+Second, rotation period is more difficult to ascertain from a light curves' variability than the orbital period, particularly if the modulation is weak and or rapidly evolving.
+And third, differential rotation causes spots at different latitudes to move at different speeds, so it becomes difficult to even define a rotation period, as long as we don't know at which latitude(s) the flares occur.
 
@@
 Orbital periods are all known precisely enough, so that the phase uncertainty at the last observed flare is of the order of $10^{-2}$.
-In contrast, in stars with known rotation periods, the precision is often too low, so that the phase of the last flare is often undetermined (ratio on x-axis $\sim 1$.
+In contrast, in stars with known rotation periods, the precision is often too low, so that the phase of the last flare is often undetermined (ratio on x-axis $\sim 1$).
         }
@@
 \label{sec:results:phasedist}
-For details on AU Mic results, see~\citep{ilin2022searching}.
+The Anderson-Darling test we use compares the measured distribution of orbital phases of the flares to the expected distribution, and return the significance of the deviation between the two.
+In the expected distribution, the same number of flares would be distributed randomly across the observing time.
+Figures~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv} show the flare phase distributions along with the corresponding expected distributions.
+The latter is not a straight line from zero to 1 because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different detection thresholds in each light curve.
 
@@
         }
-        \label{fig:cumdist_transiting}
+        \label{fig:cumdist_rv}
     \end{centering}

### 2023-03-03 src/scripts/paper_cumdist_individual_rv.py
more plots

@@ -35,7 +35,7 @@ if __name__ == "__main__":
     tics = tics.values
 
     # make a plot for 15 panels
-    fig, ax = plt.subplots(nrows=3, ncols=3, figsize=(14,11), sharex=True)
+    fig, ax = plt.subplots(nrows=3, ncols=3, figsize=(14,9), sharex=True)
 
     # linearize the axes
     ax = [_1 for _0 in ax for _1 in _0]

### 2023-03-03 src/scripts/paper_cumdist_individual_transiting.py

@@ -34,7 +34,7 @@ if __name__ == "__main__":
     tics = tics.sort_values(by="number_of_flares", ascending=False)
 
     # make a plot for 15 panels
-    fig, ax = plt.subplots(nrows=6, ncols=3, figsize=(14,19), sharex=True)
+    fig, ax = plt.subplots(nrows=7, ncols=3, figsize=(14,21), sharex=True)
 
     # linearize the axes
     ax = [_1 for _0 in ax for _1 in _0]

### 2023-03-03 src/scripts/paper_cumdist_individual_rv.py
adjusting plots

@@ -35,7 +35,7 @@ if __name__ == "__main__":
     tics = tics.values
 
     # make a plot for 15 panels
-    fig, ax = plt.subplots(nrows=3, ncols=3, figsize=(14,9), sharex=True)
+    fig, ax = plt.subplots(nrows=3, ncols=3, figsize=(14,7.5), sharex=True)
 
     # linearize the axes
     ax = [_1 for _0 in ax for _1 in _0]
@@ -93,7 +93,7 @@ if __name__ == "__main__":
             label = f"{ID}, {len(phases)-2} flares"
 
             # add the legend
-            a.legend([line], [label], loc=(-.1,.87), fontsize=13)
+            a.legend([line], [label], loc=(-.1,.85), fontsize=13)
             
             # plot a 1-1 line
             a.plot([0,1],[0,1], linestyle="dotted")
@@ -110,7 +110,7 @@ if __name__ == "__main__":
     plt.tight_layout(h_pad=0.1)
 
     # make sure y-axis labels are visible
-    plt.subplots_adjust(left=0.07, right=0.97, top=0.97, bottom=0.05)
+    plt.subplots_adjust(left=0.07, right=0.97, top=0.97, bottom=0.07)
 
 
     # save the figure

### 2023-03-03 src/scripts/paper_cumdist_individual_transiting.py

@@ -34,7 +34,7 @@ if __name__ == "__main__":
     tics = tics.sort_values(by="number_of_flares", ascending=False)
 
     # make a plot for 15 panels
-    fig, ax = plt.subplots(nrows=7, ncols=3, figsize=(14,21), sharex=True)
+    fig, ax = plt.subplots(nrows=7, ncols=3, figsize=(14,18.5), sharex=True)
 
     # linearize the axes
     ax = [_1 for _0 in ax for _1 in _0]
@@ -84,7 +84,7 @@ if __name__ == "__main__":
             a.set_xlim(0,1)
 
             # set the axis labels
-            if len(ax) >14:
+            if len(ax) >17:
                 a.set_xlabel("orbital phase")
             a.set_ylabel("number of flares")
 
@@ -92,7 +92,7 @@ if __name__ == "__main__":
     plt.tight_layout(h_pad=0.1)
 
     # make sure y-axis labels are visible
-    plt.subplots_adjust(left=0.07, right=0.99, top=0.99, bottom=0.05)
+    plt.subplots_adjust(left=0.07, right=0.99, top=0.99, bottom=0.03)
 
 
     # save the figure

### 2023-03-03 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \begin{centering}
-        \includegraphics[width=.95\linewidth]{figures/PAPER_flares_phase_hist_transiting.png}
+        \includegraphics[width=.9\linewidth]{figures/PAPER_flares_phase_hist_transiting.png}
         \caption{
@@
     \begin{centering}
-        \includegraphics[width=0.95\linewidth]{figures/PAPER_flares_phase_hist_rv.png}
+        \includegraphics[width=0.9\linewidth]{figures/PAPER_flares_phase_hist_rv.png}
         \caption{
@@
 
+GJ 1061 is lacking a stellar rotation period estimate, which we to calculate the magnetic field, and $v_{rel}$.
+\cite{dreizler2020reddots} estimate that it is a fairly slow rotator with a period between 50 and 200 days.
+
 \subsubsection{Kepler-411}
@@
 GJ 3323 b is a non-transiting, likely rocky planet.
-We adopted the mean radius between assuming pure iron through pure ice composition in \cite{lovos2022null} Table A1, and took the difference from this mean to either of the extremes as uncertainty estimate
-
-\subsubsection{GJ 1061}
-GJ 1061 b is a non-transiting, likely rocky planet.
 We adopted the mean radius between assuming pure iron through pure ice composition in \cite{lovos2022null} Table A1, and took the difference from this mean to either of the extremes as uncertainty estimate

### 2023-03-06 src/scripts/paper_main_table.py
sorted table

@@ -319,6 +319,9 @@ if __name__ == "__main__":
     # GJ 1061
     singles = singles[singles.TIC != "79611981" ]
 
+    # sort table by p-value
+    singles = singles.sort_values(by="mean", ascending=False)
+
     fulltable = singles.copy()
 
     # convert the singles table to latex after converting the values to tex format
@@ -362,6 +365,7 @@ if __name__ == "__main__":
 
     # make a list of tuples with the two column lists
     splitcols = [("lit", lit_cols), ("der", der_cols)]
+
 
     # SPLIT TABLE IN TWO
 

### 2023-03-06 src/tex/ms.tex
[showyourwork] overleaf sync

--- 2023-03-03 src/tex/ms.tex
@@
 \subsection{Light curve de-trending and flare search}
-\label{methods:flaresearch}
+\label{sec:methods:flaresearch}
 To remove trends and rotational variability from the light curve without losing the flare signal, we use an empirically derived multistep process.
@@
 \subsection{Custom Anderson-Darling test}
-\label{methods:adtest}
+\label{sec:methods:adtest}
 For each star-planet system with three or more flares in their Kepler and/or TESS light curves, we test for deviations from a random distribution of flares with orbital phase.
@@
 \subsection{Relative velocity}
-\label{methods:relvel}
+\label{sec:methods:relvel}
 We calculate the relative velocity between the magnetic field of the star, which we assume is co-rotating with the stellar rotation period $P_{rot}$, at the planetary orbit, where the planet moves with a period $P_{orb}$:
@@
 \subsection{Stellar magnetic fields}
-\label{methods:bfield}
+\label{sec:methods:bfield}
 We derive the average magnetic field strength $B$ from $Ro$ using the empirical relation derived in \cite{reiners2022magnetism},  Table 2, in the unsaturated and saturated regimes, respectively:
@@
 \subsection{Power of star-planet interaction}
-\label{methods:pspi}
+\label{sec:methods:pspi}
 We consider two theories for the mechanism behind flaring star-planet interactions, the stretch-and-break and the Alfv\'en wing mechanisms.
-For both of them, we include the case of a magnetized and an unmagnetized planet, for a total of estimates of the expected power of magnetic star-planet interaction.
+For both of them, we include the case of a magnetized and an unmagnetized planet, for a total of four estimates of the expected power of magnetic star-planet interaction.
 
@@
 Figures~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv} show the flare phase distributions along with the corresponding expected distributions.
-The latter is not a straight line from zero to 1 because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different detection thresholds in each light curve.
+The latter usually deviate from a straight line from zero to 1 because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different detection thresholds in each light curve.
 
@@
         \caption{
-            Cumulative distributions of orbital phases of flares in the transiting planet hosts observed by Kepler and TESS with 4 or more flares each.
+            Cumulative distributions of orbital phases of flares in the transiting planet hosts observed by Kepler and TESS.
+The bisector line is dotted, the expected distribution is solid blue, and the observed distribution is solid black.
 Phase zero corresponds to the transit mid-time of the planet.
@@
         \caption{
-            Cumulative distributions of orbital phases of flares in the RV planet hosts observed by Kepler and TESS with 4 or more flares each. Phase zero is chosen arbitrarily.
+            Cumulative distributions of orbital phases of flares in the RV planet hosts observed by Kepler and TESS.
+The bisector line is dotted, the expected distribution is solid blue, and the observed distribution is solid black.
+Phase zero is chosen arbitrarily.
         }
@@
 \label{sec:results:spi}
-We use the custom Anderson-Darling test detailed in \cite{ilin2022searching} to look for flaring SPI in all system with three flares or more.
-We do not find $>3\sigma$ signal of star-planet interaction in any of the star-planet systems in this sample.
+We used the custom Anderson-Darling test introduced in  \citet{ilin2022searching} and Section~\ref{methods:adtest} to look for flaring SPI in all systems with three  or more flares detected in their Kepler and TESS observations.
+Table~\ref{tab:maintable_der} lists the $p$-value results for each star-planet system.
+We do not find any $>3\sigma$ signal of star-planet interaction in our sample.
+However, the significance of the deviation increases with higher expected power of interaction.
+Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with or without planetary magnetic field), the significance of the measured interaction is correlated with the expected power $P$.
+Table~\ref{tab:maintable_der} lists the values for the four different powers $P$, calculated with the scaling laws introduced in Section~\ref{sec:methods:pspi} and normalized to AU Mic, along with the derived parameters for these scaling laws, i.e., Rossby number R$_o$, surface magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{rel}$.
 

### 2023-03-06 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \subsection{Planetary radii}
-NASA table, see references in table, or using the planetary mass to calculate the radius using the empirical relations derived in \cite{chen2007} using their open source \texttt{forecaster} tool, upgraded to \texttt{astro-forecaster}\footnote{https://pypi.org/project/astro-forecaster/} by Ben Cassesse.
+NASA table, see references in table, or using the planetary mass to calculate the radius using the empirical relations derived in \cite{chen2017probabilistic} using their open source \texttt{forecaster} tool, upgraded to \texttt{astro-forecaster}\footnote{https://pypi.org/project/astro-forecaster/} by Ben Cassesse.
 
@@
 The methods for light curve de-trending and flare finding in Kepler and TESS light curves, as well as the Anderson-Darling test, are the same as detailed in~\citet{ilin2022searching}.
-We briefly recap the techniques in Sections~\ref{methods:flaresearch} and \ref{methods:adtest}.
+We briefly recap the techniques in Sections~\ref{sec:methods:flaresearch} and \ref{sec:methods:adtest}.
 The expected power of SPI depends on the relative velocity between the planet and the magnetic field strength in its orbit, the derivation of which we explain in
-Sections~\ref{methods:relvel} and \ref{methods:bfield}, respectively.
+Sections~\ref{sec:methods:relvel} and \ref{sec:methods:bfield}, respectively.
 With relative velocity and magnetic field strength derived, we can combine them with stellar radius, planetary radius, and semi-major axis to estimate the power of SPI.
-We use the scaling laws from two different magnetic SPI models, which we introduce in Section~\ref{methods:pspi}.
+We use the scaling laws from two different magnetic SPI models, which we introduce in Section~\ref{sec:methods:pspi}.
 
@@
 In the expected distribution, the same number of flares would be distributed randomly across the observing time.
-Figures~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv} show the flare phase distributions along with the corresponding expected distributions.
-The latter usually deviate from a straight line from zero to 1 because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different detection thresholds in each light curve.
+Figures~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv} show the flare phase distributions along with the corresponding expected distributions for transiting and non-transiting systems, respectively.
+The expected distributions usually deviate from a straight line because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different detection thresholds in each light curve.
 
@@
 \label{sec:results:spi}
-We used the custom Anderson-Darling test introduced in  \citet{ilin2022searching} and Section~\ref{methods:adtest} to look for flaring SPI in all systems with three  or more flares detected in their Kepler and TESS observations.
+We used the custom Anderson-Darling test introduced in  \citet{ilin2022searching} and Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three  or more flares detected in their Kepler and TESS observations.
 Table~\ref{tab:maintable_der} lists the $p$-value results for each star-planet system.
@@
 Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with or without planetary magnetic field), the significance of the measured interaction is correlated with the expected power $P$.
-Table~\ref{tab:maintable_der} lists the values for the four different powers $P$, calculated with the scaling laws introduced in Section~\ref{sec:methods:pspi} and normalized to AU Mic, along with the derived parameters for these scaling laws, i.e., Rossby number R$_o$, surface magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{rel}$.
+Table~\ref{tab:maintable_der} lists the values for the four different powers $P$, calculated with the scaling laws introduced in Section~\ref{sec:methods:pspi} and normalized to AU Mic, along with the derived parameters for these scaling laws, i.e., Rossby number R$_o$, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{rel}$.
+
+We observe the highest interaction strength for
 
@@
 All powers are normalized to AU Mic.
-The p-value of the Anderson-Darling test is lower when the system shows more flares periodic with the planetary orbit.}
+The $p$-value of the Anderson-Darling test is lower when the system shows more flares periodic with the planetary orbit.}
 \input{output/table_der_vals.tex}

### 2023-03-06 src/scripts/paper_adtest_vs_value_scatterplots.py
remove contaminated and excluded targets

@@ -328,6 +328,16 @@ if __name__ == "__main__":
     # read in results table
     df = pd.read_csv(paths.data / "results.csv")
 
+    # remove GJ 1061 because it does not have a rotation period
+    df = df[df["ID"] != "GJ 1061"]
+
+    # drop rows with TIC 67646988 and 236387002, the brown dwarfs
+    df = df[df.TIC != "67646988" ]
+    df = df[df.TIC != "236387002" ]
+
+    # the old Kepler-411 instance
+    df = df[df.TIC != "399954349(c)" ]
+
     # FOUR SCENARIO PLOTS
 
     columns = ["p_spi_sb_bp1_norm", "p_spi_sb_bp0_norm",

### 2023-03-06 src/scripts/paper_cumdist_individual_transiting.py

@@ -28,13 +28,23 @@ if __name__ == "__main__":
 
     # only use the systems that appear in the results table
     tics = pd.read_csv(paths.data / "results.csv")
+
+    # remove old Kepler-411 instance
     tics = tics[tics.TIC != '399954349(c)']
+
+    # remove GJ 1061 because it does not have a rotation period
+    tics = tics[tics["ID"] != "GJ 1061"]
+
+    # drop rows with TIC 67646988 and 236387002, the brown dwarfs
+    tics = tics[tics.TIC != "67646988" ]
+    tics = tics[tics.TIC != "236387002" ]
+
 
     tics = tics[(tics.multiple_star.isnull()) & (tics.multiple_star_source != "BD")]
     tics = tics.sort_values(by="number_of_flares", ascending=False)
 
     # make a plot for 15 panels
-    fig, ax = plt.subplots(nrows=7, ncols=3, figsize=(14,18.5), sharex=True)
+    fig, ax = plt.subplots(nrows=6, ncols=3, figsize=(14,17), sharex=True)
 
     # linearize the axes
     ax = [_1 for _0 in ax for _1 in _0]

### 2023-03-06 src/scripts/paper_main_table.py

@@ -316,8 +316,9 @@ if __name__ == "__main__":
     # the old Kepler-411 instance
     singles = singles[singles.TIC != "399954349(c)" ]
 
-    # GJ 1061
+    # GJ 1061 because rotation is unclear
     singles = singles[singles.TIC != "79611981" ]
+
 
     # sort table by p-value
     singles = singles.sort_values(by="mean", ascending=False)

### 2023-03-06 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 This added XXXX star-planet systems to the sample.
-\subsection{Multiplicity and contamination}
-We drop all multiple stars except for Proxima Cen (whose companion are well separated both physically and on the sky), and all stars with nearby objects that contaminate our analysis, e.g., from ~\citet{ziegler2018measuring}.
-
-Quoting the references for multiplicity/contamination, we dropped the following targets: \input{output/multiples_string.tex}
 
@@
 \subsection{Planetary radii}
-NASA table, see references in table, or using the planetary mass to calculate the radius using the empirical relations derived in \cite{chen2017probabilistic} using their open source \texttt{forecaster} tool, upgraded to \texttt{astro-forecaster}\footnote{https://pypi.org/project/astro-forecaster/} by Ben Cassesse.
+NASA table, see references in table, or using the planetary mass $M_p$ or $M_p\sin i$ to calculate the radius or a lower limit for the radius using the empirical relations derived in \cite{chen2017probabilistic} using their open source \texttt{forecaster} tool, upgraded to \texttt{astro-forecaster}\footnote{https://pypi.org/project/astro-forecaster/} by Ben Cassesse.
 
-%Transit information
-%Full sample statistics
+We note that for GJ 674, the mass estimates in \cite{bonfils2007harps} and \cite{boisse2011disentangling} do not quote uncertainties, but differ by 0.3MEarth, so we assumed that value as the uncertainty on $M_p\sin i$.
 
@@
 We take bolometric luminosity values as given in the NASA Table if given with uncertainties, and supplement missing values and entries without quoted uncertainties with Gaia DR3 FLAME~\citep{fouesneau2022gaia} solutions.
-
-% \subsection{X-ray luminosity}
-% We take the \cite{foster2022exoplanet} X-ray luminosity catalog as the basis for our calculation, assuming an uncertainty of 30\% in the reported values, covering typical intrinsic variability among stars of similar rotation periods in studies like ~\cite{wright2011stellaractivityrotation, wright2018stellar}.
 
@@
 \label{sec:results:spi}
-We used the custom Anderson-Darling test introduced in  \citet{ilin2022searching} and Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three  or more flares detected in their Kepler and TESS observations.
+We used the custom Anderson-Darling test introduced in  \citet{ilin2022searching} and Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three  or more flares with equivalent duration $ED>1\,$s, detected in their Kepler and TESS observations.
 Table~\ref{tab:maintable_der} lists the $p$-value results for each star-planet system.
 We do not find any $>3\sigma$ signal of star-planet interaction in our sample.
-However, the significance of the deviation increases with higher expected power of interaction.
-Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with or without planetary magnetic field), the significance of the measured interaction is correlated with the expected power $P$.
+However, overall, the significance of the deviation increases with higher expected power of interaction.
+
+Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with or without planetary magnetic field), there are two branches.
+On one branch, the significance of the measured interaction is correlated with the expected power $P$.
+On the other branch, no interaction is measured regardless of the expected power $P$.
+
 Table~\ref{tab:maintable_der} lists the values for the four different powers $P$, calculated with the scaling laws introduced in Section~\ref{sec:methods:pspi} and normalized to AU Mic, along with the derived parameters for these scaling laws, i.e., Rossby number R$_o$, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{rel}$.
-
-We observe the highest interaction strength for
 
@@
 \begin{figure*}[ht!]
-    \script{paper_adtext_vs_value_scatterplots.py}
+    \script{paper_adtest_vs_value_scatterplots.py}
     \begin{centering}
@@
 
-% \begin{figure*}[ht!]
-%     \script{paper_adtext_vs_value_scatterplots.py}
-%     \begin{centering}
-%         \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_xray_flux_erg_s.png}
-%         \caption{X-ray luminosity of the host star~\cite{foster2022identifying} vs. AD test results.
-%         }
-%         \label{fig:adtest_xray_flux_erg_s}
-%     \end{centering}
-% \end{figure*}
-
 \subsection{Individual stars}
 \label{sec:results:individualstars}
+The properties of star-planet systems in this work are diverse, including both very young and old systems (with slowly rotating host stars); systems with super-Earths, Neptunes, and Hot Jupiters; and spectral types covering the lower main sequence from early G to late M dwarfs.
+
+For our analysis, it is important to know that the observed flares indeed occurred on the planet host star.
+We therefore excluded some systems due to documented contamination from nearby (bound or co-moving) companions~(Section~\ref{sec:results:individualstars:excluded}).
+One exception to this rule is Kepler-411, a binary system for which the flare contributions from each component could be separated~(Section~\ref{sec:results:individualstars:kep411}).
+We also dropped GJ 1061 from the sample because its rotation period was unconstrained.
+Another uncertainty in our analysis is the possibility of additional planets at even shorter orbits than the currently known innermost planet, such as might be the case for Proxima Cen~(Section~\ref{sec:results:individualstars:proxima}).
+
+The bulk of the systems in our sample are neither expected to show high power of magnetic star-planet interaction, nor do they show any deviation from intrinsic stellar flaring that could be indicative of flaring star-planet interaction.
+In the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring star-planet interaction with increasing expected power $P$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522~(Sections \ref{sec:results:individualstars:aumic}-\ref{sec:results:individualstars:hip67522}).
+Then we consider those systems where high power was expected in all scenarios, but not measured, i.e., TAP 26 and KOI-12~(Sections \ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}).
 \subsubsection{Excluded targets}
-Kepler-808 (KOI 1300) has a $\sim0.4$ Msun \cite{kraus2016impact}companion that is about 1.8 mag fainter than the primary at a separation of .78 arcsec~\cite{baranec2016roboao}.
+\label{sec:results:individualstars:excluded}
 
-TOI-837 has co-moving M dwarf a few arcsec away in the same young cluster, 5 mag fainter, but the primary is an F9-G0 star, so flare could come from both stars~\cite{bouma2020cluster}
+While they appear in Table~\ref{tab:flares}, we excluded a number of systems from further analysis.
+We drop all multiple stars except for Proxima Cen (whose components are well separated both physically and on the sky), and all stars with nearby objects that contaminate our analysis, e.g., from ~\citet{ziegler2018measuring}: \input{output/multiples_string.tex}
 
-HD 41004 B and DS Tuc A and LTT 1445
+For instance, Kepler-808 (KOI 1300) has a $\sim0.4M_\odot$ \citep{kraus2016impact} companion that is about 1.8 mag fainter than the primary at a separation of .78 arcsec~\citep{baranec2016roboao}.
+TOI-837 has co-moving M dwarf a few arcsec away in the same young cluster, 5 mag fainter, but the primary is an F9-G0 star, so flares could still originate come from both stars~\citep{bouma2020cluster}.
+HD 41004 B, DS Tuc A, and LTT 1445 are known multiple systems where all components contribute significantly to the total flux.
 
-GJ 1061 is lacking a stellar rotation period estimate, which we to calculate the magnetic field, and $v_{rel}$.
-\cite{dreizler2020reddots} estimate that it is a fairly slow rotator with a period between 50 and 200 days.
+The only single star system excluded is GJ 1061.
+The star is lacking a stellar rotation period estimate, which we need to calculate the magnetic field, and $v_{rel}$.
+\citet{dreizler2020reddots} estimate that it is a fairly slow rotator with a period between 50 and 200 days, so we do not expect it to have a strong magnetic field anyway.
 
 \subsubsection{Kepler-411}
-Kepler-411 has 3 mag fainter companion~\cite{wang2014influence,ziegler2018measuring}.
-It was observed in Kepler short cadence by \cite{jackman2021stellara} and both the planet host, and the companion flare.
-\cite{jackman2021stellara} disentangle the contributions on a pixel level.
-According to \cite{morton2016false, sun2019kepler411} the planets orbit the primary companion.
-In fact, the fainter companion of Kepler-411 appears to cause the majority of flares (41), whereas Kepler-411 causes only 7.
-We adopt the 7 flares from \cite{jackman2021stellara} for our analysis.
-
-\subsubsection{HAT-P-11}
-\cite{miskovetz2022resolving}  found background stars that were not co-moving HAT-P-11.
-HAT-P-11 rotates nearly pole-on, and HAT-P-11 b is transiting in a near-polar orbit~\citep{bourrier2023dream}.
-This may be the reason for absent SPI
+\label{sec:results:individualstars:kep411}
+Kepler-411 has 3 mag fainter companion~\cite{wang2014influence,ziegler2018measuring}, but we do not exclude it from the analysis.
+The system was observed in Kepler short cadence by \citet{jackman2021stellara} and both the planet host, and the companion star flare.
+\citet{jackman2021stellara} disentangle the contributions from each component on a pixel level.
+According to \citet{morton2016false, sun2019kepler411}, Kepler-411's planets orbit the primary companion.
+The fainter companion of Kepler-411 appears to cause the majority of flares (41), whereas the planet host causes only 7.
+We adopt the 7 flares from \cite{jackman2021stellara} in our analysis.
 
 \subsubsection{Proxima Cen}
-tentative detection of another planet further in, at 0.029 au, or 5 day orbital period~\citep{faria2022candidate, artigau2022linebyline}
-Although Proxima Cen is part of a triple stellar system, we treat it a single star here because of the large angular separation to its two companions.
+\label{sec:results:individualstars:proxima}
+We do not detect a deviation from intrinsic flaring on Proxima Cen, consistent with numerical models that place Proxima Cen b well outside the sub-Alfv\'enic zone~\citep{kavanagh2021planetinduced}.
+However, this might not entirely exclude Proxima Cen from the search for flaring star-planet interaction.
+The tentatively detected Proxima Cen d, a planet further in, at 0.029 au, or 5 day orbital period~\citep{faria2022candidate, artigau2022linebyline} could still cause flaring star-planet interactions.
+However, the orbital period of the tentative planet is so uncertain at this point that its coherence time is shorter than the roughly 2yr observing baseline of Proxima Cen, preventing us from accurately measuring the flare phases.
 
-Proxima Cen b has an eccentricity upper limit of 0.35~\cite{anglada-escude2016terrestrial}
+\subsubsection{AU Mic}
+\label{sec:results:individualstars:aumic}
+
+AU Mic is a 16-29 Myr old pre-main sequence M0-M1 dwarf with a strong magnetic field of about $3010\pm220\,$G obtained from Zeeman broadening measurements~\citep{reiners2022magnetism}.
+The innermost Neptune-sized planet, AU Mic b, could be both inside the sub-Alfv\'enic zone if the star's mass loss rate is relatively low at about 30 times the solar value or lower.
+If the mass loss rate is high, exceeding the solar value by a factor of several hundreds, AU Mic b could orbit in the super-Alfv\'enic zone, and become unable to experience any planet-induced flaring.
+Recently, \citet{klein2022one} found tentative periodicity with the orbital period of AU Mic b in the chromospheric He I D line, which increases if the contribution from flares is included in the calculation.
+Overall, our marginal signal of flaring star-planet interaction in the AU Mic system supports the idea that this young, magnetically active M dwarf system with a close-in Neptune could exhibit planet=induced flaring.
+For a detailed discussion of AU Mic and its flaring star-planet interaction, we refer to~\cite{ilin2022searching}, where we also estimate that an additional 50–100 days of TESS-like monitoring of AU Mic would yield a $3\sigma$ detection if the marginal signal in our data is real.
+
+\subsubsection{K2-25}
+\label{sec:results:individualstars:k225}
+\subsubsection{TOI-540}
+\label{sec:results:individualstars:toi540}
 
 \subsubsection{HIP 67522}
+\label{sec:results:individualstars:hip67522}
 HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest signs of flaring SPI, albeit with only 6 flares in the sample.
@@
 HIP 67522 will be observed again with TESS in spring 2023.
-\subsubsection{GJ 3323}
-
-GJ 3323 b is a non-transiting, likely rocky planet.
-We adopted the mean radius between assuming pure iron through pure ice composition in \cite{lovos2022null} Table A1, and took the difference from this mean to either of the extremes as uncertainty estimate
 
 \subsubsection{TAP 26}
-Likely low eccentricity given in \cite{yu2017hot}
+\label{sec:results:individualstars:tap26}
 
-\subsubsection{GJ 393}
-Eccentricity likely low, but not quantified in \cite{amado2021carmenes}, so we treat it as unconstrained (set e=0.5)
+\subsubsection{KOI-12}
+\label{sec:results:individualstars:koi12}
 
-\subsubsection{Kepler-42}
- 	KOI-961 in the detection paper \cite{muirhead2012characterizing}, low eccentricity constrained by \cite{mann2017gold}
+%\subsection{Combined Sample}
 
-\subsubsection{GJ 674}
-Has hot UV flares~\cite{froning2019hot}
-The mass estimates in \cite{bonfils2007harps} and \cite{boisse2011disentangling} do not quote errors, but differ by 0.3MEarth, so we assume that as the uncertainty on $M_p\sin i$
+%For those stars with given transit mid-time and
 
-\subsubsection{K2-354}
-Found under EPIC 211314705 and K2-329 in \cite{bouma2020cluster}, who refer to the detection paper \cite{pope2016transiting}, also TIC 468989066.
-
-\subsection{Combined Sample}
-
-For those stars with given transit mid-time and 
 \section{Discussion}
@@
 \subsection{Spin-orbit alignment}
+nother relevant factor is the geometry of the system.
+If we assume that the magnetic dipole axis and the rotation axis of the star are relatively well-aligned, the spin-orbit alignment may have an influence on interaction strength.
+
 or more broadly system architecture including misalignment of the magnetic axis. See HAT-P-11, or instance, and the many polar orbits in \cite{bourrier2023dream}
+
+\cite{miskovetz2022resolving}  found background stars that were not co-moving HAT-P-11.
+HAT-P-11 rotates nearly pole-on, and HAT-P-11 b is transiting in a near-polar orbit~\citep{bourrier2023dream}.
+This may be the reason for absent SPI.
 \subsection{Eccentricity}
 The star-planet systems in this work do not have notably eccentric orbits.
+
+\section{Summary and Conclusions}
+
 \bibliography{bib}
@@
 \appendix
-\section{Expected $P$ vs. measured flaring SPI}
+\section{Notes on individual stars}
+\subsection{Proxima Cen}
+Although Proxima Cen is part of a triple stellar system, we treat it a single star in this work because of the large angular separation to its two companions.
+Proxima Cen b has an eccentricity upper limit of 0.35~\cite{anglada-escude2016terrestrial}.
+\subsection{TAP 26}
+Likely low eccentricity given in \cite{yu2017hot}.
 
+\subsection{GJ 393}
+Eccentricity likely low, but not quantified in \cite{amado2021carmenes}, so we treat it as unconstrained (set e=0.5)
+
+\subsection{Kepler-42}
+ KOI-961 in the detection paper \cite{muirhead2012characterizing}, low eccentricity constrained by \cite{mann2017gold}
+
+\subsection{K2-354}
+We note that we found K2-354 under EPIC 211314705 and K2-329(!) in \cite{bouma2020cluster}, who refer to the detection paper \cite{pope2016transiting}, and also under TIC 468989066.
 \end{document}

### 2023-03-07 src/scripts/paper_latex_flare_table.py
ordering the flare table, adding the wrapper bash script

@@ -14,7 +14,7 @@ if __name__ == "__main__":
     flare_table = pd.read_csv(paths.data / "PAPER_flare_table.csv")
 
     # Sort the data by orbital phase
-    flare_table = flare_table.sort_values(by="orbital_phase", ascending=True)
+    flare_table = flare_table.sort_values(by="tstart", ascending=True)
 
     # Get ED with uncertainties in one expression
     flare_table[r"$ED$ [s]"] = flare_table.apply(lambda x: fr"${x.ED:.2f} \pm {x.ED_err:.2f}$",

### 2023-03-07 src/scripts/run_all.sh

@@ -1,0 +1,10 @@
+source /home/ekaterina/Documents/000_envs/python38forall/bin/activate
+python paper_rename_trappist.py
+python paper_string_multiple_stars.py
+python paper_adtest_vs_value_scatterplots.py
+python paper_coherence_diagram.py
+python paper_cumdist_individual_rv.py
+python paper_cumdist_individual_transiting.py
+python paper_flare_table_values.py 
+python paper_latex_flare_table.py 
+python paper_main_table.py 

### 2023-03-07 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 The bulk of the systems in our sample are neither expected to show high power of magnetic star-planet interaction, nor do they show any deviation from intrinsic stellar flaring that could be indicative of flaring star-planet interaction.
-In the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring star-planet interaction with increasing expected power $P$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522~(Sections \ref{sec:results:individualstars:aumic}-\ref{sec:results:individualstars:hip67522}).
+In the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring star-planet interaction with increasing expected power $P$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522~(Sections \ref{sec:results:individualstars:aumic} and \ref{sec:results:individualstars:hip67522}).
 Then we consider those systems where high power was expected in all scenarios, but not measured, i.e., TAP 26 and KOI-12~(Sections \ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}).
@@
 
-\subsubsection{AU Mic}
+\subsubsection{AU Mic, K2-25, and TOI-540}
 \label{sec:results:individualstars:aumic}
@@
 
-\subsubsection{K2-25}
-\label{sec:results:individualstars:k225}
-\subsubsection{TOI-540}
-\label{sec:results:individualstars:toi540}
+K2-25 is a multiplanet system around a fast rotating ($<2\,$d) mid-M dwarf in the Hyades open cluster, that is, 600-800 Myr old~\citep{stefansson2020habitable}.
+Both the expected power of interaction, and the measured deviation, are remarkably similar to the AU Mic system.
+Moreover, K2-25 b is in a presumably similar environment to GJ 436 b, but does not show the atmospheric escape in Ly$\alpha$ that the latter famously exhibits~\citep{rockcliffe2021lya}.
+This might at least in part be due to the stellar wind conditions around K2-25 b.
+Further investigation of magnetic star-planet interactions, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius.
 
+In Figure~\ref{fig:adtest_bp}, TOI-540 clusters with K2-25 and AU Mic -- a fast rotating M dwarf with its innermost planet in a $1.24\,$d orbit~\citep{ment2021toi}.
+Compared to the other two systems, its innermost planet is not a Neptune, but a rocky planet slightly smaller than Earth~\citep{ment2021toi}.
+It is a relatively smaller obstacle in the host's magnetic field, yet the interaction is expected to be of a similar magnitude due to the strongest inferred magnetic field and closest orbit among the three systems.
+
+In the scenario wherein the stretch-and-break mechanism drives the interaction, the three system cluster together most distinctly. In this scenario, they 
 \subsubsection{HIP 67522}

### 2023-03-07 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 The fainter companion of Kepler-411 appears to cause the majority of flares (41), whereas the planet host causes only 7.
-We adopt the 7 flares from \cite{jackman2021stellara} in our analysis.
+Adopting the 7 flares from \cite{jackman2021stellara} in our analysis, we find that they all have equivalent duration $<1\,$s, which excludes Kepler-411 from our analysis.
 
@@
 
-In the scenario wherein the stretch-and-break mechanism drives the interaction, the three system cluster together most distinctly. In this scenario, they 
+In the scenario wherein the stretch-and-break mechanism drives the interaction, the three system cluster together most distinctly.
+In this scenario, most, but not all systems that do not show elevated interaction, have a weaker magnetic field~(top row in Figure\ref{fig:adtest_bp}).
+An excep
 \subsubsection{HIP 67522}

### 2023-03-10 src/scripts/paper_spin_orbit_commensurability.py
spin-orbt commensurability plot added

@@ -1,0 +1,173 @@
+"""
+Python 3.8 -- UTF-8
+
+Ekaterina Ilin, 2022, MIT License
+
+Script that generates the spin-orbit commensurability plot for the paper.
+"""
+
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.lines import Line2D
+import paths
+
+
+def build_ratios_table(tol:float=1e-5)->dict:
+    """
+    Create a table of small integer ratios 
+    with a tolerance used to determine if the ratio between two 
+    periods is close to a small integer ratio.
+
+    Parameters:
+        tol (float): 
+        The tolerance used to determine if the ratio between 
+        the two periods is close to a small integer ratio.
+        Default is 1e-5
+
+    Returns:
+        dict: A dictionary of ratios with the key as the ratio
+        and value as a tuple of numerator and denominator
+    """
+
+    ratios = {}
+    
+    for i in range(1, int(np.sqrt(1/tol))):
+        for j in range(1, int(np.sqrt(1/tol))):
+            ratio = round(i/j, int(-np.log10(tol)))
+            if ratio not in ratios:
+                ratios[ratio] = (i,j)
+    return ratios
+
+
+def is_spin_orbit_commensurable(period1:float, period2:float,  ratios:dict, 
+                                tol:float=1e-5,)->tuple:
+    """
+    Check for spin-orbit commensurability between two periods.
+    Spin-orbit commensurability occurs when the ratio between the rotation period
+    of a celestial body and its orbital period around another body is close to a 
+    small integer ratio.
+
+    Parameters:
+    ----------
+        period1 (float):
+            The rotation period of a celestial body.
+        period2 (float): 
+            The orbital period around another body.
+        tol (float): 
+            The tolerance used to determine if the ratio between 
+            the two periods is close to a small integer ratio.
+            Default is 1e-5
+        ratios (dict):
+            A dictionary of ratios with the key as the ratio
+            and value as a tuple of numerator and denominator
+
+
+    Returns:
+    -------
+        tuple:  A tuple containing,
+                A boolean value indicating whether the ratio is close to small integer ratio
[…]

### 2023-03-10 src/tex/ms.tex
[showyourwork] overleaf sync

--- 2023-03-07 src/tex/ms.tex
@@
 \label{sec:intro}
-Star-planet system we have found so far are nothing like the Solar System.
+One of the most surprising results in exoplanet research is the diversity of star-planet system architectures.
+In particular, the past two decades revealed that planets can occur in orbits so close to their host star that they could be considered to live inside the stellar atmosphere.
+At this proximity, the planet exerts force, gravitational and magnetic, both short- and long-term, on its host -- a phenomenon unknown to the Solar System.
+The individual processes are typically subsumed under the term star-planet interactions that emphasizes that they are bidirectional, affecting both planet, and star.
 
-What is SPI?
+Understanding short-term, magnetic star-planet interactions holds promise to provide important insights into the habitability of the entire system.
+Planets involved in such interactions can be viewed as in-situ probes of the system's space weather, and could prospectively reveal otherwise difficult to measure planetary properties such as the strength and extent of their magnetic fields.
 
-Why look for SPI?
-Use planets as probes stellar magnetic fields at a defined orbit, e.g., stellar wind conditions.
-SPI can only occur if the planet is orbiting within the Alfv\'en radius of the star for a sizable period of time.
-The Alfv\'en radius is the radius at which the stellar wind velocity, which increases with increasing distance from the star because of XXXX, exceed the Alfv\'en velocity of the magnetized plasma.
+Magnetic star-planet interactions can only occur if the planet is orbiting within the Alfv\'en radius of the star longer than it takes for the effects of the planet to travel to the surface of the star.
+The Alfv\'en radius is the radius at which the stellar wind velocity, which increases with increasing distance from the star, exceed the Alfv\'en velocity of the magnetized plasma.
 Beyond this radius, this plasma is disconnected from the star.
-Alfv\'en waves cannot propagate back to the star because the wind is carrying the plasma away faster than these waves can travel.
+Alfv\'en waves set off by the planet within the magnetic field they cross cannot propagate back to the star if the wind carries the plasma away faster than these waves can travel.
+In the sub-Alfv\'enic regime, the wave can reach the star, and deposit its energy in some way.
+\citet{lanza2012starplanet, lanza2018closeby} and \citet{zarka2007plasma, saur2013magnetic} suggest different mechanisms for when and how the energy dissipation takes place, and how much energy can be transferred and dissipated at all.
 
-Stretch and break
+One way of dissipating the energy in the magnetic field is through flares. 
+Flares are explosions in stellar atmospheres that occur in the stellar corona as a way to dissipate energy stored in the magnetic field by the motion of footpoints of coronal loops.
+They are strong and impulsive eruptions released by reconnection and subsequent relaxation of field lines~\citep{svestka1976solar,priest2002magnetic}.
+We can observe flares in nearly all electromagnetic bands -- from radio to X-ray~\citep{benz2010physical}.
+In contrast to solar flares, stellar flares often are extremely energetic, sometimes enhancing the stellar flux by orders of magnitude~\citep{maehara2012superflares, shibayama2013superflares, paudel2018k2}.
+But since they occur randomly in time, individual events can be hard to catch.
 
-Alfven wing
+In the 2010s, a wealth of flare observations from space missions like Kepler~\citep{borucki2010kepler} and K2~\citep{howell2014k2} have been catalogued~\citep{davenport2016kepler, paudel2018k2, ilin2021flares}.
+We now have access to long-term stellar monitoring data suitable for flare hunting.
+Currently, the Transiting Exoplanet Survey Satellite~\citep{ricker2015transiting} is rapidly expanding the treasury~\citep{gunther2020stellar}, which will grow even further after the launch of the PLATO mission in 2026~\citep{rauer2014plato}.
+As will become clear in the following paragraphs, the key advantage of these missions is their quasi uninterrupted monitoring of star-planet systems that covers all phases of their planets' orbits.
+
+The absolute power of flaring star-planet interactions is difficult to constrain, so we do not know how energetic planet-induced flares can be.
+The estimates of the maximum dissipated power~\citep{lanza2018closeby} are well within the regime of superflares typically observed by Kepler and TESS.
+However, on the one hand that power is an upper limit, so the observed energies might be lower.
+The planet might for instance be triggering flares prematurely, leading an overabundance of low energy flares~\citep{loyd2023flares}.
+On the other hand, the energy need not be dissipated continuously, particularly in the stretch-and-break mechanism, so it might be higher.
+We also do not know whether flares triggered by interactions with a companion would have different properties than intrinsic flares.
+We assume that, since they would be caused by magnetic reconnection triggered by the planet in the stellar corona, they should follow the same process as intrinsic flares.
+
+Since planet-induced flares are not expected to look any different from intrinsic flares, and we do not know how their energies will be distributed, we require a method to distinguish them without referring to their individual properties.
+Instead, we can look at the statistical distribution of flares in time:
+
+If we picture the magnetic field lines connecting the planet to the star in the sub-Alfv\'enic zone, we expect that the stellar footpoint of these lines will move along with the planet.
+Flares triggered by the planet will occur at a preferred orbital phase, namely whenever the footpoint is visible to the observer.
+Depending on the system's architecture and magnetic situation, i.e., the inclination of the rotation axis, the spin-orbit (mis-)alignment, and the extent and configuration of the large scale magnetic field -- the footpoint could be always in view, or never.
+In expectation, however, in star-planet systems with favorable architectures and magnetic field states, the footpoint visibility will be modulated in phase with the planetary orbit.
+The resulting phase preference of planet-induced flares introduces a deviation from a random distribution of flares.
+Space missions like Kepler and TESS provide light curves that cover all phases of the planet's orbit, so that phase-correlated planet-induced flares can be detected against a background of uncorrelated intrinsic flaring.
+
+\citet{fischer2019timevariable} and \citet{howard2021evryflare}
+
+In this work, we searched for excess flaring in all available Kepler and TESS short cadence light curves of confirmed star-planet systems~(Section~\ref{sec:data}).
+We scoured the light curves for flares, and tested their observed phases for departures from a uniform distribution in phase with the innermost planet's orbit~(Section~\ref{sec:methods}).
+We present the catalog of all flares found in our sample of star-planet systems, and compare the test results with the expected power of interaction for each system~(Section~\ref{sec:results}).
+We discuss the results for the most interesting star-planet systems individually~(Section~\ref{sec:results:individualstars}, and take a look at the more general patterns emerging from our systematic analysis~(Section~\ref{sec:discussion}).
+Finally, we summarize our findings, and suggest future observations that could uncover the star-planet interaction mechanisms operating behind the observed trends~(Section~\ref{sec:summary}).
+
+%Short intro to SaB mechanism
+
+%Short intro to AW mechanism
+
+% ----------------------------------------------------------------------------------
+
+% In both models, the radius of the perturbing body, and its proximity increase the power of interaction. Would it not be more reasonable to search for star-brown dwarf or star-star interactions?
+
+% Flares caused by magnetic interactions in close binary systems were previously observed.
+Flares detected on the young eccentric binary system V 773 Tau could be attributed to colliding magnetospheres~\citep{massi2002periodic, massi2008interacting}, while other promising systems, like DQ Tau, another young equal-mass binary system in a strongly eccentric orbit, did not live up to the expectations~\citep{salter2008captured,salter2010recurring,getman2011young,getman2016search, kospal2018spots}.
+In these systems, it is, however, unclear whether it is mass transfer or reconnection that drive excess coronal emission and flares at periastron.
+Substellar objects can orbit the star much closer than a stellar companion without filling the Roche lobe.
+Gravitationally, a rocky planet can go unnoticed by its host even if it orbits at ultrashort periods of less than a day.
+% Interactions in systems with brown dwarf companions are less likely than binary systems
 
@@
 We used the custom Anderson-Darling test introduced in  \citet{ilin2022searching} and Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three or more flares with equivalent duration $ED>1\,$s, detected in their Kepler and TESS observations.
+We choose the $ED$ cutoff to make sure that we are comparing similar flares regardless of spectral type, that is, flares with the same energy relative to stellar luminosity.
+We show the results that include all flares regardless of $ED$ in the appendix (XXXX TBD).
+
 Table~\ref{tab:maintable_der} lists the $p$-value results for each star-planet system.
@@
 The fainter companion of Kepler-411 appears to cause the majority of flares (41), whereas the planet host causes only 7.
-We adopt the 7 flares from \cite{jackman2021stellara} in our analysis.
+Adopting the 7 flares from \cite{jackman2021stellara} in our analysis, we find that they all have equivalent duration $<1\,$s, which excludes Kepler-411 from further analysis.
 
@@
 
-In the scenario wherein the stretch-and-break mechanism drives the interaction, the three system cluster together most distinctly. In this scenario, they 
+In the scenario wherein the stretch-and-break mechanism drives the interaction, the three system cluster together most distinctly.
+In this scenario, all systems that do not show elevated interaction, have a weaker magnetic field below $2000\,$G~(top row in Figure\ref{fig:adtest_bp}).
+In the Alfv\'en wing scenario~(bottom row in Figure\ref{fig:adtest_bp}), the distinction is less clear, and systems with strong fields and similar expected power of interaction do not show any excess flaring.
+In both cases, the absence of interaction could be due to the Alfv\'en radius being within the planetary orbit (note that the scaling laws assume that the planet is sub-Alfv\'enic, but make no statement about it).
+All else equal, this is more likely if the stellar magnetic field strength is weaker.
+Another explanation is the possible intermittency, or 'on-off nature' of the interaction~\citep{shkolnik2008nature}, which may be at play here, but particularly in cases where the expected power is very strong, such as in the comparison between HIP 67522 and TAP 26 that we address in the following Section.
+
 \subsubsection{HIP 67522}
 \label{sec:results:individualstars:hip67522}
-HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest signs of flaring SPI, albeit with only 6 flares in the sample.
+HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest sign of flaring SPI at $>2\sigma$ level, albeit with only 6 flares in the sample.
 These flares are distributed across two Sectors in TESS.
@@
 
-HIP 67522 is young Sun, currently contracting onto the main sequence.
+HIP 67522 is a young Sun, currently contracting onto the main sequence.
 It is a Sco-Cen member (10-20 Myr old), which was discovered to host a close-in Jupiter, HIP 67522 b, in 2020~\citep{rizzuto2020tess}.
-It was found with low obliquity, consistent with XXXX~\citep{heitzmann2021obliquity}.
-Tentative third planet transiting.
+Curiously, the planet is in close spin-orbit commensurability -- $P_{rot}/P_{orb}=5/1$, closer than any other system in our sample.
+Therefore, we cannot completely rule out that the observed periodicity is in fact a rotational periodicity, and not related to the planet.
+However, if we calculate the $p$-value of AD test using the rotational period instead of the orbital period, we find HIP 67522 consistent with uniform flaring in time within $1\sigma$.
+Fortunately, HIP 67522 will be observed again with TESS in April 2023, which may resolve the puzzle.
 
-HIP 67522 is in close spin-orbit commensurability -- $P_{rot}/P_{orb}=5/1$. The system's $a/R_*\approx11.7$, eccentricity below .25~\cite{rizzuto2020tess}, so that
-
-\cite{wood2021characterizing} rule out stellar companions for HIP 67522 based on RV, high-resolution imaging, and Gaia data.
-
-HIP 67522 will be observed again with TESS in spring 2023.
+%It was found with low obliquity, consistent with XXXX~\citep{heitzmann2021obliquity}. Tentative third planet transiting.
+%The system's $a/R_*\approx11.7$, eccentricity below .25~\cite{rizzuto2020tess}, so that  
+ %\cite{wood2021characterizing} rule out stellar companions for HIP 67522 based on RV, high-resolution imaging, and Gaia data.
 
@@
 \label{sec:results:individualstars:tap26}
+TAP 26 is a weak-line T-Tauri star with a strong magnetic field~\citep{yu2017hot}.
+\citet{lanza2018closeby} estimate that the system can release more energy in magnetic star-planet interaction than other  systems with Hot Jupiters, such as HD 179949, that has previously been detected with chromospheric variability in phase with the planet's orbit~\citep{shkolnik2008nature}.
+However, for TAP 26 b, the orbital period might is not well-constrained.
+\citet{yu2017hot} apply several methods to derive $P_{orb}$ from the radial velocity data: While the $10.8\,$d orbit we adopted is the most likely according to \citet{yu2017hot}, a $9.0\,$d orbit is also likely, and some of their applied methods favored a $13.4\,$d period.
+The absence of interaction could hence be a consequence of uncertain orbital period.
+However, intermittent interactions and the viewing geometry of TAP 26 could also explain the absence of phase-correlated flaring~(see Sections~\ref{sec:discussion:intermittency} and \ref{sec:discussion:viewing}).
 
@@
 \label{sec:results:individualstars:koi12}
+KOI-12, also known as Kepler-448, is a young two-planet system with an eccentric outer planet KOI-12 c, and an inner Hot Jupiter planet KOI-12 b in a $17.8\,$d orbit~\citep{masuda2017eccentric}.
+With respect to rotation rate, stellar and planetary radius, the KOI-12/KOI-12 b system is similar to HIP~67522 and TAP~26 (although for the those young stars the radii are large because the stars are still contracting onto the main sequence).
+Yet, despite its high expected power of interaction, we detect no excess flaring in phase with KOI-12 b.
+Here, the reason could be that KOI-12 b is in fact super-Alfv\'enic due to the relatively wide orbit compared to TAP 26 and HIP 67522.
+Intermittent interaction might play a role here as well, and could be favored if future observations capture episodes during which the interaction is 'on'.
 
@@
 
-\subsection{Similar work that puts ours in context}
+\subsection{Rotational and synodic variability}
+\citet{fischer2019timevariable} argue that the synodic period, at which the sub-planetary point crosses the same (magnetic) surface element on the star, may result in a clearer interaction signal, because a magnetically active region that is prone to planet-induced flares, will be passed only once per period.
+However, this assumes that the landscape of active regions on the star is stable throughout the entire observing time, and that the number of such regions in the footpoint passageway is low enough to produce a periodic modulation.
 
-Any indication of flaring SPI anywhere else? Any reason to think there should be any?
-Why does HIP 67522 stick out so much? -- spin-orbit alignment
+In our sample, the observing baseline is multiple years long for many systems.
+Even the most rigidly rotating late M dwarfs show variability in their spot modulation on such long timescales.
+Even if differential rotation was absent and active regions were extremely stable, we will not be able to observe the passage of the sub-planetary point over the flare-prone region every synodic period.
+For a fraction of the time, this will happen on the back of the star relative to the observer.
+The true period will therefore be additionally modulated by the visibility, resulting in an intermittency of the signal.
+As a consequence, to detect a modulation with the synodic period, a significantly longer observing baseline is needed than to detect a modulation with the orbital period.
+Additionally, if there are multiple active regions that produce flares when the sub-planetary footpoint passes across, the effect with the synodic period is further diluted.
 
-\subsection{Rotational variability}
-Hard to measure, because it de-phases much faster than orbital variability due to differential rotation and spot evolution. We could use single light curves within which coherence is given...
+In summary: Even for the few stars, for which the rotational period is known precisely enough~(see Fig.~\ref{fig:coherence_hist}), we need to make assumptions about the number of active regions crossed by the footpoint of interaction, differential rotation, spot evolution, and a significant correlation between the location of the planet and the location of the planet-induced flare on the stellar surface.
+For modulation with the orbital period, we require only that last correlation between footpoint location and orbital phase.
+Any realistic number of active regions (one or more), a wide range of degrees of differential rotation (from rigid rotator to solar-type), and half-life duration of active regions (day to years) are acceptable, because the observed effect depends predominantly on the visibility of the footpoint, which is governed by orbital motion.
+And except for extreme circumstances, the latter will be much more stable over long periods of time than the intrinsically dynamic magnetic field configuration.
 
@@
 \label{sec:discussion:intermittency}
-TAP 26 vs. HIP 67522, also different sectors for HIP 67522, see \cite{shkolnik2008nature}
+Magnetic star-planet interactions in a given system may sometimes be turned off for episodes of time, and turned on for others.
+HD 179949 is the prototype example, wherein the orbital modulation of chromospheric indicators was observable for XXXX out of XXXXX epochs~\citep{shkolnik2003evidence,shkolnik2008nature}.
+It is not clear how long a continuous epoch of interaction or non-interaction might be.
+This leaves room for many different explanations.
+Long-term monitoring is needed to investigate the reasons for the temporary cessation of interaction.
+Candidate mechanisms include: The Alfv\'en radius moving in- and outside the planet's orbit, either over the course of an activity cycle, or through short-term variations in the magnetic field and wind properties caused by, e.g., coronal mass ejections; visibility of the interacting footpoint changing as the magnetic field evolves; the active latitude moving away from the magnetic footpoints passageway, the available magnetic energy decreasing such that the flares or other magnetic interaction indicators still occur but fall below the detection threshold for a period of time.
 
-\subsection{Spin-orbit alignment}
-nother relevant factor is the geometry of the system.
+If the magnetic field of the planet changes or disappears, this might also reduce the intensity of interaction below the detection threshold.
+
+The location of active regions within the passageway of the magnetic footpoints may be such that the interaction occurs only when the region faces away from the observer.
+This could span multiple orbits of the planet, particularly when the surface is populated by few stable active regions, and the orbital and rotational periods are similar.
+The flip-flop behavior of active longitudes could then cause a relatively sudden quenching of interaction by moving the interacting region out of view for a period of time.
+
+In our results in Fig.~\ref{fig:adtest_bp}, we can interpret the two branches emerging at high expected power of interaction as due to the intermittency of the phenomenon.
+TAP 26 and KOI-12 do not show any sign of excess flaring in our data, despite similar expected powers as in HIP 67522 with its $>2\sigma$ signal.
+In Sections~\ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}, the absence of interaction in TAP 26 and KOI-12 could be explained by an uncertainty in orbital period that smears out the signal, and a super-Alfv\'enic orbit, respectively.
+Yet intermittency cannot be ruled out.
+The case HIP 67522 may be more informative.
+In our data, we combine the observation from two TESS Sectors that are almost 2 years apart.
+The four phase-correlated flares all occur in the later Sector, while the earlier one contains only two flares, both of them at orbital phases different from each other and the four phase-aligned flares.
+This can be interpreted as a tentative sign of intermittency of flaring star-planet interactions in this system.
+
+\subsection{Viewing geometry}
+\label{sec:discussion:viewing}
+The visibility of the magnetic interaction footpoint is crucial for the detection of flaring star-planet interactions in our analysis.
+The viewing geometry of the star-planet system is therefore important to consider.
+Assuming for the sake of the argument that the sub-planetary point is close to the magnetic interaction footpoint in longitude, two factors will determine whether the footpoint's visibility will be modulated with the planetary orbit or not: the orbital inclination and the footpoint's latitude relative to it.
+If the footpoint's latitude is low, i.e., close to the orbital plane, the orbital plane can be inclined to a high degree, and the footpoint will still periodically move in and out of view.
+However, if the footpoint's latitude is high, we need to observe the star-planet system nearly edge-on to be able to measure a modulation of activity with the planet's orbital phase.
+The latter can be the case when the dipole axis of the stellar large scale field is well-aligned with the orbital axis.
+In that case, assuming the dipole field dominates at the distance of the planet, the footpoint will be close to the pole, similar to the hot spot created by Io and the other moons in the polar cap of Jupiter.
+In this scenario, many non-transiting systems may experience flaring star-planet interaction, but those would not show up as correlation of flare timing with the orbital phase in our data.
+
+Most of our systems are transiting, and for those we can expect this scenario to be a minor problem.
+Of the systems that have high expected power but do not show any, only TAP 26 is a planet detected in radial velocity, and is expected to have a relatively high orbital inclination of about $55\pm10$ deg inferred from Zeeman Doppler measurements~\citep{yu2017hot}.
+The ZD map reveals magnetic field concentrations close to the rotational pole.
+If the orbital plane is aligned with the stellar rotation axis, the absence of phase-correlated flaring in TAP 26 could be explained by the footpoint of interaction being always in view and therefore never modulated.
+
+\subsection{(Mis-)alignment between orbital, rotational and stellar magnetic axis}
+\label{sec:discussion:misalignment}
+Another relevant factor is the geometry of the system.
 If we assume that the magnetic dipole axis and the rotation axis of the star are relatively well-aligned, the spin-orbit alignment may have an influence on interaction strength.
@@
 This may be the reason for absent SPI.
+
+HD 179949 has a strong misalignment of about 70 deg between rotational and magnetic axis.
+Time-resolved X-ray observations~\citep{acharya2022xray} suggest that the magnetic interaction footpoint is close to the stellar rotational pole, which would be close to the magnetic equator of the strongly dipolar field of HD 179949
+
 \subsection{Eccentricity}
-The star-planet systems in this work do not have notably eccentric orbits.
+If the planetary orbit is highly eccentric, the difference between the semi-major and semi-minor axis can be significantly larger than the variability of the Alfv\'en radius.
+If then apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, namely during the planet's rapid periastron passage.
+This was exploited in magnetic star-star interaction~(XXXX), and also star-planet interaction~(XXXX).
+In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e<XXXX$.
+There are therefore no planets where we would expect a strongly preferred orbital phase for interaction.
+
+\subsection{Spin-orbit commensurability}
+\begin{figure}[ht!]
+    \script{paper_spin_orbit_commensurability.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/PAPER_spin_orbit_commensurable.png}
+        \caption{
+           caption
+        }
+        \label{fig:spinorbit}
+    \end{centering}
+\end{figure}
+
+\subsection{Tidal or magnetic interaction?}
+
+The tight spin-orbit commensurability in some systems may give rise to spots on the star that rotate with the commensurable period~\citep{lanza2022model, lanza2022tidal}.
+HIP 67522 is in very close 1:5 spin-orbit commensurability with HIP 67522 b.
+It is possible that the periodicity seen with the orbital period in our flare data is an effect of tidally created spots that happen to produce flares.
 
 \section{Summary and Conclusions}
+\label{sec:summary}
 

### 2023-03-17 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Title
-\title{Searching for flaring star-planet interactions in star-planet systems in Kepler and TESS}
+\title{Flaring star-planet interactions in star-planet systems in Kepler and TESS}
 
@@
     Star-planet system we have found so far are nothing like the Solar System.
-Many stars host planets in orbits much closer than Mercury, where it takes them mere days to complete a full revolution.
+Many stars host planets in orbits much closer than Mercury, where it takes them mere days or even hours to complete a full revolution.
 In some of these systems, the planets are so close that they plow through the extended magnetosphere of the star, and are expected to trigger flares on their surfaces.
@@
     We find XXXX star-planet systems with > XXXX flares.
-For XXXX of them, we can calculate the expected amplitude of interaction based on the system's magnetic field strength, orbital parameters, rotation and planet radius.
-We find that the trend of higher interaction signal agrees with the expected strength, but also shows signs of intermittency, both for individual systems, and in comparison between ones with similar expected amplitude.
+For XXXX of them, we can quantify both the intensity of excess flaring, and the expected amplitude of interaction based on the system's magnetic field strength, orbital parameters, rotation and planet radius.
+Most systems are neither expected to show interactions, nor do they show any excess flaring.
+Among those systems that have high expected power of interaction, we see two branches.
+An inactive one, where no signs of excess flaring appear, and an active one %We find that the trend of higher interaction signal agrees with the expected strength, but also shows signs of intermittency, both for individual systems, and in comparison between ones with similar expected amplitude.
 HIP 67522, a 17 Myr young Sun with a Jupiter in a 9 day orbit, shows both one of the highest expected and the highest measured interaction amplitudes, albeit only at the $2.5\sigma$ level.
@@
 
+K2-25 is eccentric, see Eike Günther?
+
 In Figure~\ref{fig:adtest_bp}, TOI-540 clusters with K2-25 and AU Mic -- a fast rotating M dwarf with its innermost planet in a $1.24\,$d orbit~\citep{ment2021toi}.
@@
 \label{sec:discussion}
+Eccentricity is almost controlled for in our sample~(Section~\ref{sec:discussion:eccentricity}), while rotation is not well enough constrained to investigate the presence of flaring modulation with $P_{rot}$, or the synodic period~(Section~\ref{sec:discussion:rotsyn}).
+In the remainder of the discussion, we lay out different reasons for the emerging shape of the distribution in our results in Fig.~\ref{fig:adtest_bp}, in particular the inactive and active branches at high expected power of interaction.
+We begin with the possible intermittency of the interaction that could be caused by the planet regularly moving in and out of the sub-Alfv\'enic zone for extended periods of time~(Section~\ref{sec:discussion:intermittency}).
+In Section~\ref{sec:discussion:viewing}, we suggest that the absence of interaction at high expected power could be due to unfavorable viewing geometry of the system, e.g., a face-on orbital plane.
+In Section~\ref{sec:discussion:misalignment}, we discuss whether (mis-)alignment between spin, orbit and magnetic dipole can increase or decrease the chances of flaring star-planet interaction.
+In Section~\ref{sec:discussion:commensurability}, we note that systems on the inactive branch are further away from spin-orbit commensurability than stars on the active branch.
+This leads us to conjecture a possible influence of tidal interactions on the occurrence of orbital phase correlated flaring.
+We conclude our discussion by following this line of reasoning, and consider ways to disentangle tidal from magnetic interactions~(Section~\ref{sec:discussion:tidalmagnetic}).
+
+\subsection{Eccentricity}
+\label{sec:discussion:eccentricity}
+If the planetary orbit is highly eccentric, the difference between the semi-major and semi-minor axis can be significantly larger than the variability of the Alfv\'en radius.
+If then apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, namely during the planet's rapid periastron passage.
+This was exploited in magnetic star-star interaction~(XXXX), and also star-planet interaction~(XXXX).
+In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e<XXXX$.
+The exception is K2-25, with a moderate $e=0.45$, which may contribute to the increased contrast of excess flares.
+All else equal, closer proximity increases the strength of interaction.
+Perhaps, K2-25 even moves in and out of the sub-Alfv\'enic zone between periastron and apoastron, turning interaction on and off every single orbit.
+Otherwise, there are therefore no planets where we would expect a strongly preferred orbital phase for interaction.
 
 \subsection{Rotational and synodic variability}
+\label{sec:discussion:rotsyn}
 \citet{fischer2019timevariable} argue that the synodic period, at which the sub-planetary point crosses the same (magnetic) surface element on the star, may result in a clearer interaction signal, because a magnetically active region that is prone to planet-induced flares, will be passed only once per period.
@@
 
-\subsection{Eccentricity}
-If the planetary orbit is highly eccentric, the difference between the semi-major and semi-minor axis can be significantly larger than the variability of the Alfv\'en radius.
-If then apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, namely during the planet's rapid periastron passage.
-This was exploited in magnetic star-star interaction~(XXXX), and also star-planet interaction~(XXXX).
-In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e<XXXX$.
-There are therefore no planets where we would expect a strongly preferred orbital phase for interaction.
+\subsection{Spin-orbit commensurability}
+\label{sec:discussion:commensurability}
+In Fig.~\ref{fig:spinorbit}, we split our sample into three categories.
+The first contains the systems where the expected interaction is lower than that in TOI-540.
+The second includes the systems where a high power of interaction is expected, but none is measured (e.g., TAP 26, KOI-12).
+The final third category contains all system where the data suggest a correlation between expected power of interaction and measured flaring star-planet interaction signal (e.g., HIP 67522, AU Mic).
+We search for spin-orbit commensurability with integers $<10$ in each system, and plot the relative difference between the closest ratio and the actual spin-orbit ratio.
+Systems with low expected power of interaction span both very close spin-orbit commensurability to none.
+Systems with high expected power are divided: Stars that show a correlation between excess flaring and expected power tend to have closer spin-orbit commensurability than systems that are far away from any low-integer ratio between rotational and orbital period.
 
-\subsection{Spin-orbit commensurability}
-\begin{figure}[ht!]
+While chance alignment is possible, the division invokes the idea that spin-orbit commensurability and magnetic star-planet interaction are related.
+Either something about our observing method favors the measurement of excess flaring in systems with close spin-orbit commensurability, or there is physical causation at play.
+In the latter case, the spin-orbit commensurability could be either an effect, or a cause, of measured magnetic star-planet interaction.
+
+Our method favors systems in which the deviation from uniform flare timing is concentrated in a narrow phase bracket of the planet's orbit.
+This might be the case in HIP 67522.
+Due to its low-order, 5:1 resonance, the sub-planetary point passes the same magnetic features at the same orbital phase each orbit.
+This is no longer the case for m:n ratios, where $n>1$.
+In those systems, the same surface feature is passed by the sub-planetary point at the same orbital phase every $m \cdot n$ orbits, if $m>n$ (which is true for all our systems with high expected power of interaction).
+For HIP 67522, the interaction signal may therefore be more strongly confined to certain orbital phases, while for systems with less and less commensurability, this effect dilutes.
+
+There could also be physical reasons for increased flaring interaction-in systems with close spin-orbit commensurability.
+\citet{lanza2022model} suggest that tidal torque of the planet on the star excites resonant oscillations in the interior stellar magnetic field, which in turn leads to a resonance between stellar spin and planetary orbit.
+These oscillations can lead to a surface pattern of emerging magnetic field that rotates with the spin-orbit commensurable period.
+This can explain the clearer interaction signal in the systems with spin-orbit resonance, because it would stabilize the pattern of regions with strong magnetic field that favor planet-induced flaring, and thereby counterbalance the diluting effect of differential rotation.
+This model requires tidal interaction, which may be too weak in systems like AU Mic, where the planet is too small and distant for the proposed effect~\citet{lanza2022model}, but that still show spin-orbit commensurability and signs of flaring star-planet interaction.
+However, for systems with $m=1$, like HIP~67522, or $\tau$ Boo~\citep[which is not in our sample]{walker2008nature, cauley2019magnetic}, this model would directly favor active regions that rotate with the orbital period instead of the rotational one.
+
+While in~\citet{lanza2022model}, resonant oscillations favor flaring star-planet interaction observability, there might also be physical effects where the magnetic torque causes the spin-orbit resonance in the first place.
+The connection here is: Where there is strong enough magnetic torque to cause spin-orbit resonance, there would also be flaring star-planet interaction.
+
+\citet{szabo2021changing} note that many systems within the sparsely populated region of close-in planets around rapid rotators~\citep{mcquillan2013stellar} seem close to low-integer spin-orbit resonance.
+The systems with consistently high expected power of interaction (TAP 26, TOI-540, KOI-12, HIP 67522, K2-25, and AU Mic) are all found within that region, even if KOI-12 and AU Mic lie rather close to its edge.
+Of these six systems, those that show signs of star-planet interaction, are also in close-spin orbit resonance.
+We may speculate, that at least some of the mechanisms that explain the dearth of close-in planets around rapidly rotating stars also explain the presence of star-planet magnetic interaction in those systems that are still found there.
+One may think that planets that remain in the desert are held there by being trapped in the resonance, while for the others, the magnetic torque cause rapid migration out of this region.
+
+\begin{figure}[t]
     \script{paper_spin_orbit_commensurability.py}
@@
         \caption{
-           caption
+           Spin-orbit commensurability compared to flaring star-planet interaction signal.
+The lower the p-value of the AD test, the stronger the interaction signal.
+Lower relative difference between the measured spin-orbit ratio and the integer ratio closest to it indicates a tighter spin-orbit commensurability.
+We include only ratios of integers $<10$.
+\textbf{Black diamonds:} All systems with p-values lower than that of K2-25, and expected power of interaction equal or higher than TOI-540's, the active 'SPI on' branch~(see top left panel in Fig.~\ref{fig:adtest_bp}).
+\textbf{Red crosses:} The complementary 'SPI off' branch includes all systems with expected power of interaction above that of TOI-540, but with p-values below that of K2-25.
+\textbf{Blue circles:} The remaining systems include all with expected power of interaction below that of TOI-540.
+Among the systems with high expected power, those with higher interaction signal ('SPI on') show closer spin-orbit commensurability than those on the inactive 'SPI off' branch.
         }
@@
 \subsection{Tidal or magnetic interaction?}
+\label{sec:discussion:tidalmagnetic}
+The tight spin-orbit commensurability in some systems may give rise to spots on the star that rotate with the commensurable period~\citep{lanza2022model}.
+HIP~67522 is in very close 5:1 spin-orbit commensurability with HIP~67522~b.
+It is possible that the periodicity seen with the orbital period in our flare data is an effect of such tidally created spots that happen to produce flares.
+On the other hand, magnetic interactions, wherein the direct perturbation of stellar field by the planetary obstacle cannot be ruled out~\citep{lanza2018closeby, saur2013magnetic}.
 
-The tight spin-orbit commensurability in some systems may give rise to spots on the star that rotate with the commensurable period~\citep{lanza2022model, lanza2022tidal}.
-HIP 67522 is in very close 1:5 spin-orbit commensurability with HIP 67522 b.
-It is possible that the periodicity seen with the orbital period in our flare data is an effect of tidally created spots that happen to produce flares.
+Both mechanisms may play a role, but to understand their respective contribution, we require approaches that can unambiguously discriminate between the two.
+
+While suggestive, our data are statistically insufficient to conclude whether the flaring interaction is driven only by magnetic interaction, or whether tidal effects, and more specifically spin-orbit resonances, play a role.
+Further monitoring of the systems in our sample will clarify whether the interaction is statistically significant for individual systems, whether the branching is caused by intrinsic intermittency of the effect.
+If the branching persists over time, and systems do not switch from the inactive to the active branch or vice versa, the distinction may be due to tidal effects.
+
+Another possibility is that the branching disappears in favor of a continuous distribution. This would put in question the on-off nature of magnetic interactions.
+
+Another hint is the onset of the branching.
+If it persists in a larger sample, it may mark the transition of star-planet systems from the super- to the sub-Alfv\'enic regime.
+If it disappears in favor of a more continuous distribution, tidal effects are favored because their intensity has no such threshold at a particular radius, but increases continuously with decreasing semi-major axis and increasing companion mass.
+
+Ways to investigate which mechanisms play a role using flaring:
+
+Search for flaring star-planet interactions in rapidly rotating fully convective stars with close-in planets or brown dwarfs.
+There are very few such systems, TOI-540 among them.
+These systems have only negligible differential rotation so that the rotation period of surface features can be precisely known.
+In those cases, we may figure out whether interaction occurs with the synodic period.
+
+Search for ECMI emission in radio from systems that have high expected power of interaction.
+If periodic radio emission is seen predominantly in the systems that also show flaring star-planet interactions, magnetic interaction is relevant because coherent radio emission stems from large scale fields, and not from resonantly emerging patterns of active regions as suggested by~\citet{lanza2022model}.
+
+spetral type dependence of tidal interaction
 

### 2023-03-17 src/scripts/paper_cumdist_individual_rv.py

@@ -29,16 +29,25 @@ if __name__ == "__main__":
     # only use the systems that appear in the results table
     res = pd.read_csv(paths.data / "results.csv")
 
-    tics = res[(res.multiple_star.isnull()) & (res.multiple_star_source != "BD")]
+    tics = res[(res.multiple_star.isnull()) & (res.multiple_star_source != "BD") & (res.TIC != "399954349(c)")]
     tics = tics.sort_values(by="number_of_flares", ascending=False).TIC.astype(str)
 
     tics = tics.values
+
+    # Add the number of flares to the TICs
+    n_flares = []
+    for tic in tics:
+        n_flares.append(pd.read_csv(paths.data / f"TIC_{tic}_cumhist.csv").shape[0])
+    
+    # sort the TICs by the number of flares
+    tics = [x for _,x in sorted(zip(n_flares, tics), reverse=True)]
 
     # make a plot for 15 panels
     fig, ax = plt.subplots(nrows=3, ncols=3, figsize=(14,7.5), sharex=True)
 
     # linearize the axes
     ax = [_1 for _0 in ax for _1 in _0]
+    ax = ax[::-1]
 
     # create a subplot for each star
     for tic in tics:
@@ -102,9 +111,14 @@ if __name__ == "__main__":
             a.set_xlim(0,1)
 
             # set the axis labels
-            if len(ax) > 5:
+            if len(ax) <5:
                 a.set_xlabel("orbital phase")
-            a.set_ylabel("number of flares")
+            
+            a.set_ylabel("fraction of flares")
+
+    if len(ax) > 0:
+        for a in ax:
+            a.remove()
 
     # layout the figure
     plt.tight_layout(h_pad=0.1)

### 2023-03-17 src/scripts/paper_cumdist_individual_transiting.py

@@ -43,11 +43,22 @@ if __name__ == "__main__":
     tics = tics[(tics.multiple_star.isnull()) & (tics.multiple_star_source != "BD")]
     tics = tics.sort_values(by="number_of_flares", ascending=False)
 
+
+    # Add the number of flares to the TICs
+    n_flares = []
+    for tic in tics.TIC:
+        n_flares.append(pd.read_csv(paths.data / f"TIC_{tic}_cumhist.csv").shape[0])
+    
+    # sort the TICs by the number of flares
+    tics["n_flares"] = n_flares
+    tics = tics.sort_values(by="n_flares", ascending=False)
+
     # make a plot for 15 panels
     fig, ax = plt.subplots(nrows=6, ncols=3, figsize=(14,17), sharex=True)
 
     # linearize the axes
     ax = [_1 for _0 in ax for _1 in _0]
+    ax = ax[::-1]
 
     # create a subplot for each star
     for id_, row in tics.iterrows():
@@ -94,7 +105,7 @@ if __name__ == "__main__":
             a.set_xlim(0,1)
 
             # set the axis labels
-            if len(ax) >17:
+            if len(ax) <3:
                 a.set_xlabel("orbital phase")
             a.set_ylabel("number of flares")
 

### 2023-03-17 src/scripts/paper_spin_orbit_commensurability.py

@@ -131,12 +131,12 @@ if __name__ == "__main__":
 
 
     # Make plot
-    plt.figure(figsize=(7,5.5))
+    plt.figure(figsize=(8,5.5))
 
     # plot each group
     for marker, group in df.groupby("marker"):
         plt.scatter(group["ratio_error"], group["mean"],
-                    color=group["color"], alpha=1., marker=marker)
+                    color=group["color"], alpha=1., marker=marker, s=60)
 
     # define legend
     valuelegend = [Line2D([0], [0], marker='o', color='w',
@@ -148,8 +148,8 @@ if __name__ == "__main__":
 
     # define legend labels
     valuelabels = [ r"low expected power",
-                        r"high expected power / SPI off",
-                        r"high expected power / SPI on"]
+                    r"high expected power / SPI off",
+                    r"high expected power / SPI on"]
 
     # annotate points with high expected power and SPI on
     for i, row in df.iterrows():
@@ -158,11 +158,13 @@ if __name__ == "__main__":
                         (row.ratio_error*1.1, row["mean"]*.95))
 
     # plot legend
-    plt.legend(valuelegend, valuelabels, loc=4, fontsize=12, frameon=False)
+    plt.legend(valuelegend, valuelabels, loc=4, fontsize=14, frameon=False)
 
     # label axes
-    plt.xlabel("relative difference to closest spin-orbit commensurable ratio")
-    plt.ylabel(r"$p$-value of AD test")
+    plt.xlabel("relative difference to closest spin-orbit commensurable ratio",
+               fontsize=14)
+    plt.ylabel(r"$p$-value of AD test",
+               fontsize=14)
 
     # set log scale
     plt.xscale("log")
@@ -171,3 +173,49 @@ if __name__ == "__main__":
     # save figure to figures folder
     plt.tight_layout()
     plt.savefig(paths.figures / "PAPER_spin_orbit_commensurable.png", dpi=300)
+
+
+    # Corresponding AD test vs. SPI plot
+
+    # Make plot
+    plt.figure(figsize=(8,5.5))
+
+    # plot each group
+    for marker, group in df.groupby("marker"):
+        plt.errorbar(group["p_spi_sb_bp1_norm"], group["mean"], yerr=group["std"],
+                     xerr=[group["p_spi_sb_bp1_norm"]-group["p_spi_sb_bp1_norm_low"],
+                           group["p_spi_sb_bp1_norm_high"] - group["p_spi_sb_bp1_norm"]],
[…]

### 2023-03-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 If the eccentricity is known, then the range of the distance is set to either the error on the semi-major axis or half of the difference between the semi-major and semi-minor axis, as calculated from the eccentricity -- whichever is larger.
-If eccentricity is NOT known, then the range of the distance is either the 25\% error on the semi-major axis, that is, assuming e=0.5 or the uncertainty on the semi-major axis -- whichever is larger.
+If eccentricity is not known, then the range of the distance is either the 25\% error on the semi-major axis, that is, assuming e=0.25 or the uncertainty on the semi-major axis -- whichever is larger.
 
@@
 We adopt available rotation period values from the literature. When uncertainties are not given, we assume 10\% uncertainty.% _09_
+
+Sources of rotation periods are XXXX
 
@@
 If then apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, namely during the planet's rapid periastron passage.
-This was exploited in magnetic star-star interaction~(XXXX), and also star-planet interaction~(XXXX).
+This was previously exploited in the case of HD 189733, and also for binary interaction in the V 773 Tau system.
 In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e<XXXX$.

### 2023-03-22 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \begin{abstract}
-    Star-planet system we have found so far are nothing like the Solar System.
+    The star-planet systems discovered so far are nothing like the Solar System.
 Many stars host planets in orbits much closer than Mercury, where it takes them mere days or even hours to complete a full revolution.
@@
 \label{sec:data}
+In this study, we wanted to compile the largest possible sample to search for flaring star-planet interactions, so took the entire Planetary Systems Composite Parameters Table (PSCP, Section~\ref{sec:data:sps})\footnote{ \url{https://exoplanetarchive.ipac.caltech.edu/cgi-bin/TblView/nph-tblView?app=ExoTbls&config=PSCompPars}} from the NASA Exoplanet Archive, and scanned the systems for available Kepler and TESS light curves~(Section~\ref{sec:data:photometry}).
+We ended up searching a total of 1812 systems and over 7200 light curves from both missions for flares.
+To calculate the amount of excess flaring from star-planet interaction, we then required the orbital periods of each system~(Section~\ref{sec:data:orbitalperiod}).
+To compare our measurements to theory, we also wanted to estimate the expected power of interaction for each system with at least three flares.
+For this, we required further system parameters -- distance between planet and star, stellar rotation periods, planetary radii, and stellar luminosity~(Sections~\ref{sec:data:orbitalperiod}-\ref{sec:data:lum}).
+We started compiling the table of system parameters with the PSCP, but verified, supplemented and updated the table from the literature.
+The literature parameters for the systems in the final sample of systems, for which we performed the full analysis, is shown in Table~\ref{tab:maintable_lit}.
+
 \subsection{Star-planet systems}
-
-ction with the Planetary Systems Composite Parameters Table (PSCP)\footnote{ \url{https://exoplanetarchive.ipac.caltech.edu/cgi-bin/TblView/nph-tblView?app=ExoTbls&config=PSCompPars}} from which we removed controversial planet detections (``pl\_controv\_flag'' set to 1), i.e.
+\label{sec:data:sps}
+We compiled our sample of star-planet systems from the PSCP, from which we removed controversial planet detections (``pl\_controv\_flag'' set to 1), i.e.
 detections with existing literature questioning the result.
-The catalog then contained XXXX unique systems.
-
-We complemented the PSCP with the TESS TOI Table~\citep[TT][]{guerrero2021arxiv}\footnote{\url{https://tev.mit.edu/data/collection/193/}}.
-We filtered the catalog by requiring the confirmed planet (CP) or known planet (KP) flags to be set in the ``TOI Disposition''.
-This added XXXX star-planet systems to the sample.
+The catalog then contained 2993 transiting and 191 non-transiting systems, from which we picked the innermost known planet in each system.
 
 \subsection{Kepler and TESS photometry}
+\label{sec:data:photometry}
+The Kepler and TESS missions are unbeatable with respect to long-term optical monitoring of stellar flares.
+Their excellent coverage of orbital phases makes the light curves ideal for our search for orbital phase dependent flare timing.
+
 Between 2009 and 2013, the Kepler space telescope~\citep{koch2010kepler} nearly continuously observed a patch of the sky in the Cygnus-Lyra region.
@@
 
-Based on the filtered PSCP and TT tables, we queried the full Kepler archive (quarters Q0-Q17, Data Release 25) and most recent TESS catalog (July 2022) for their respective 1-min and 2-min/20-s cadence light curves, accounting for systems that appeared in both catalogs.
-In total, we obtained XXXX Kepler light curves and XXXX TESS light curves.
-XXXX systems were observed only by the primary Kepler mission, XXXX only by TESS, and XXXX by both missions.
+Based on the filtered PSCP table, we queried the full Kepler archive (quarters Q0-Q17, Data Release 25), and the most recent TESS catalog (July 2022) for their respective 1-min and 2-min/20-s cadence light curves.
+In total, we searched 7258 light curves for flares -- 3030 Kepler Quarters, and 4228 TESS Sectors.
+We found and analyzed light curves for a total of 1811 systems, 344 of which were observed only by the primary Kepler mission, 1205 only by TESS, and 262 by both missions.
+We did not use K2 light curves because of the many systematics, and consequently the high costs of de-trending them.
+But we included the flare list obtained by~\citet{paudel2018k2} for TRAPPIST-1 K2 flares, since this system is a potential candidate for sub-Alfv\'enic interactions~\citep{fischer2019timevariable}.
 
-\subsection{Orbital periods}
-Either Kepler/TESS or from RVs.
-\subsection{Transit mid-times}
-Use transit mid-times from the same mission if possible.
-\subsection{Semi-major axes}
+\subsection{Orbital periods and transit mid-times}
+\label{sec:data:orbitalperiod}
+We adopt the orbital periods from the PSCP, which were either obtained from Kepler or TESS transits, or from radial velocity measurements.
+For the transiting systems, we use the transit mid-times given in the PSCP to set orbital phase zero.
+If possible, we do this for each mission separately to reduce the uncertainties on orbital phase.
+For the non-transiting system, phase zero is set arbitrarily.
+\subsection{Semi-major axes and eccentricities}
 \label{sec:data:a}
@@
 To account for varying distance, we adopt the mean semi-major axes from the literature, but use a custom estimate for the uncertainty that includes the eccentricity.
-If the eccentricity is known, then the range of the distance is set to either the error on the semi-major axis or half of the difference between the semi-major and semi-minor axis, as calculated from the eccentricity -- whichever is larger.
-If eccentricity is not known, then the range of the distance is either the 25\% error on the semi-major axis, that is, assuming e=0.25 or the uncertainty on the semi-major axis -- whichever is larger.
+
+If the eccentricity is known, then the uncertainty on the distance is set to either the error on the semi-major axis, or to half of the difference between periastron and apoastron -- whichever is larger.
+If eccentricity is not known, then the uncertainty on the distance is either the 25\% error on the semi-major axis, that is, assuming $e=0.25$, or the uncertainty on the semi-major axis -- whichever is larger.
+We chose $e=0.25$ because it is both a typical value within our sample~(see Table~\ref{tab:maintable_lit}), and in the literature~\citep{eylen2019orbital}.
 
 \subsection{Rotation periods}
-We adopt available rotation period values from the literature. When uncertainties are not given, we assume 10\% uncertainty.% _09_
-
-Sources of rotation periods are XXXX
+\label{sec:data:rotationperiods}
+We adopt available rotation period values from the literature.
+Almost all stem from light curve variability~\citep{angus2018inferring, mazeh2015photometric, mcquillan2013stellar, mcquillan2014rotation, luger2017sevenplanet, stock2020carmenes, deleon202137, torres2017validation, stefansson2020habitable, zicher2022one, ment2021toi, rizzuto2020tess}, and only one from periodic variation in chromospheric lines~\citep{demangeon2021warm}.
+When uncertainties are not given, we conservatively assume $10\%$ uncertainty, WHERE ARE THE PERIODS FROM.
 
 \subsection{Planetary radii}
-NASA table, see references in table, or using the planetary mass $M_p$ or $M_p\sin i$ to calculate the radius or a lower limit for the radius using the empirical relations derived in \cite{chen2017probabilistic} using their open source \texttt{forecaster} tool, upgraded to \texttt{astro-forecaster}\footnote{https://pypi.org/project/astro-forecaster/} by Ben Cassesse.
-
+\label{sec:data:planetradii}
+For the transiting planets, we adopt the literature values for planet radius $R_p$, and uncertainties, from the PSCP.
+For the non-transiting radial velocity detected planets we use the planetary mass $M_p$ or $M_p\sin i$ to calculate the radius or a lower limit for the radius using the empirical relations derived in \cite{chen2017probabilistic} using their open source \texttt{forecaster} tool, upgraded to \texttt{astro-forecaster}\footnote{https://pypi.org/project/astro-forecaster/} by Ben Cassesse.
 We note that for GJ 674, the mass estimates in \cite{bonfils2007harps} and \cite{boisse2011disentangling} do not quote uncertainties, but differ by 0.3MEarth, so we assumed that value as the uncertainty on $M_p\sin i$.
@@
 \subsection{Bolometric luminosity}
+\label{sec:data:lum}
 
-We take bolometric luminosity values as given in the NASA Table if given with uncertainties, and supplement missing values and entries without quoted uncertainties with Gaia DR3 FLAME~\citep{fouesneau2022gaia} solutions.
+We take bolometric luminosity values as given in the PSCP whenever they are given with uncertainties.
+We supplement missing values, and replace entries without quoted uncertainties with Gaia DR3 FLAME~\citep{fouesneau2022gaia} solutions~(\texttt{lum\_flame}).
 
@@
 
-% \subsection{Orbital phase}
-% \label{methods:orbitalphase}
-
-% For the star-planet system that have transiting innermost planets, we use the transit mid-time to signify orbital phase zero.
-For non-transiting planets, we use arbitrary phase zero.
-The inferior conjunction time from the orbital parameters of planets that only have radial velocity measurements is usually either very uncertain, of the order of $10\%$ of the orbital duration~(XXXX), or cannot be derived because the eccentricity is poorly constrained~(XXXX).
-
 \subsection{Relative velocity}
@@
 
-The estimate is consistent with existing Zeeman broadening for, e.g. AU Mic (3010 G~\cite{reiners2022magnetism})
+The estimate is consistent with existing Zeeman broadening for, e.g. AU Mic (3010 G~\cite{reiners2022magnetism}).
 \subsection{Power of star-planet interaction}
@@
 \label{sec:discussion:tidalmagnetic}
-The tight spin-orbit commensurability in some systems may give rise to spots on the star that rotate with the commensurable period~\citep{lanza2022model}.
-HIP~67522 is in very close 5:1 spin-orbit commensurability with HIP~67522~b.
-It is possible that the periodicity seen with the orbital period in our flare data is an effect of such tidally created spots that happen to produce flares.
-On the other hand, magnetic interactions, wherein the direct perturbation of stellar field by the planetary obstacle cannot be ruled out~\citep{lanza2018closeby, saur2013magnetic}.
+The tight spin-orbit commensurability in some systems may give rise to stable spot patterns on the star that rotate with the commensurable period~\citep{lanza2022model}, and perhaps appear preferentially in the orbital plane of the tidally interacting planet.
+It is possible that the enhanced periodicity seen with the orbital period in systems close to a low integer spin-orbit commensurability is an effect of such tidally created spots that lie along the passageway of the planet's magnetic footpoint.% On the other hand, magnetic interactions, wherein the direct perturbation of stellar field by the planetary obstacle cannot be ruled out~\citep{lanza2018closeby, saur2013magnetic}.
 
@@
 While suggestive, our data are statistically insufficient to conclude whether the flaring interaction is driven only by magnetic interaction, or whether tidal effects, and more specifically spin-orbit resonances, play a role.
-Further monitoring of the systems in our sample will clarify whether the interaction is statistically significant for individual systems, whether the branching is caused by intrinsic intermittency of the effect.
-If the branching persists over time, and systems do not switch from the inactive to the active branch or vice versa, the distinction may be due to tidal effects.
+Further monitoring of the systems in our sample will clarify whether the interaction is statistically significant for individual systems, or whether the branching is caused by intrinsic intermittency of the effect.
+If the branching persists over time, and systems do not switch from the inactive to the active branch or vice versa, the distinction may more likely be due to spin-orbit resonance.
 
 Another possibility is that the branching disappears in favor of a continuous distribution. This would put in question the on-off nature of magnetic interactions.
-
-Another hint is the onset of the branching.
-If it persists in a larger sample, it may mark the transition of star-planet systems from the super- to the sub-Alfv\'enic regime.
-If it disappears in favor of a more continuous distribution, tidal effects are favored because their intensity has no such threshold at a particular radius, but increases continuously with decreasing semi-major axis and increasing companion mass.
 

### 2023-03-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \begin{abstract}
-    The star-planet systems discovered so far are nothing like the Solar System.
-Many stars host planets in orbits much closer than Mercury, where it takes them mere days or even hours to complete a full revolution.
-In some of these systems, the planets are so close that they plow through the extended magnetosphere of the star, and are expected to trigger flares on their surfaces.
-So far, however, these flaring star-planet interactions escape our detection methods.
-If found, the planets and the flare they cause become localized probes of the parts of the stellar magnetosphere that extends from the location of one to the other.
-A measurement of these interactions constrains mass loss from the star, and potentially also the magnetic field of the planet.
+    In many of the star-planet systems discovered so far, most planets orbit far within Mercury's orbit, and many are so close to their host that they plow through its extended magnetosphere.
+In these systems, planets become in-situ probes of the dynamic magnetic fields in their orbits, able to trigger flares on the stellar surface.
+Until recently, however, these flaring star-planet interactions suffered from small sample sizes, and poor orbital phase coverage.
 
-    In this work, we searched star-planet systems observed by Kepler and TESS for flaring star-planet interactions.
-We compiled a catalog of all flaring star-planet systems known to date, and characterized the detected flares detected.
-We then searched for flares in excess of the intrinsic flaring of the star, i.e., flares triggered by the interaction with the planet in phase with its orbit.
+    In this work, we used the excellent phase coverage of Kepler and TESS to search their entire archives for star-planet systems with flaring star-planet interactions.
+We compiled a catalog of all star-planet systems with flares, and searched for planet-induced flares, i.e., flares clustering in phase with the planet's orbit.
 
-    We find XXXX star-planet systems with > XXXX flares.
-For XXXX of them, we can quantify both the intensity of excess flaring, and the expected amplitude of interaction based on the system's magnetic field strength, orbital parameters, rotation and planet radius.
-Most systems are neither expected to show interactions, nor do they show any excess flaring.
+    Out of 1811 searched systems, 26 are single star systems that show three or more flares each.
+For these, we quantified the intensity of excess flaring, and compared it against the expected amplitude of interaction based on the system's parameters.
+Most systems are neither expected to interact, nor do they show excess flaring.
 Among those systems that have high expected power of interaction, we see two branches.
-An inactive one, where no signs of excess flaring appear, and an active one %We find that the trend of higher interaction signal agrees with the expected strength, but also shows signs of intermittency, both for individual systems, and in comparison between ones with similar expected amplitude.
-HIP 67522, a 17 Myr young Sun with a Jupiter in a 9 day orbit, shows both one of the highest expected and the highest measured interaction amplitudes, albeit only at the $2.5\sigma$ level.
+An inactive one, where no signs of excess flaring appear regardless of favorable conditions, and an active one where expected power and excess flaring are correlated.
+While this trend is tentative, we also found that the two branches form two distinct populations in spin-orbit commensurability.
+The active branch is closer to low-integer ratios between rotational and orbital period than the inactive branch.
+While viewing geometry and intermittency of interaction remain possible explanations, spin-orbit resonances hint at a physical link worth exploring to better understand the underlying mechanisms of star-planet interactions.
+    %magnetic field strength (using $Ro$-$B$ relations), orbital parameters, and planet radius.
 \end{abstract}
@@
 In particular, the past two decades revealed that planets can occur in orbits so close to their host star that they could be considered to live inside the stellar atmosphere.
-At this proximity, the planet exerts force, gravitational and magnetic, both short- and long-term, on its host -- a phenomenon unknown to the Solar System.
-The individual processes are typically subsumed under the term star-planet interactions that emphasizes that they are bidirectional, affecting both planet, and star.
+At this proximity, the planet exerts force, tidal and magnetic, both short- and long-term, on its host -- a phenomenon largely unknown to the Solar System.
+These forces are typically subsumed under the term star-planet interactions that emphasizes that they are bidirectional, affecting both planet, and star.
 
-Understanding short-term, magnetic star-planet interactions holds promise to provide important insights into the habitability of the entire system.
-Planets involved in such interactions can be viewed as in-situ probes of the system's space weather, and could prospectively reveal otherwise difficult to measure planetary properties such as the strength and extent of their magnetic fields.
+On the one hand, a close-in planet that changes the star's rotation and activity makes it more difficult for us to model the system's evolution, as it affects fundamental stellar parameters.
+Inferring stellar age from rotation may be biased, if the star is spun up or spun down relative to stars without close-in companions~(XXXX).
+Analogously, altered activity levels may mimic an older or younger host than it actually is~\citep{ilic2022tidal}.
 
-Magnetic star-planet interactions can only occur if the planet is orbiting within the Alfv\'en radius of the star longer than it takes for the effects of the planet to travel to the surface of the star.
-The Alfv\'en radius is the radius at which the stellar wind velocity, which increases with increasing distance from the star, exceed the Alfv\'en velocity of the magnetized plasma.
+On the other hand, understanding short-term, magnetic star-planet interactions -- the focus of this work -- holds promise to provide important insights into the habitability of the entire system~(XXXX).
+Planets involved in such interactions are in-situ probes of the system's space weather~(XXXX), and could prospectively reveal otherwise difficult to measure planetary properties such as the strength and extent of their magnetic field~\citep{cauley2019magnetic}.
+
+\subsection{Magnetic star-planet interactions}
+
+Magnetic star-planet interactions can only occur if the planet is orbiting within the Alfv\'en radius of the star.
+It does not need to be there all the time, but for a time period that is longer than it takes for the effects of the planet to travel to the surface of the star.
+The Alfv\'en radius is the radius at which the stellar wind velocity, which increases with increasing distance from the star, exceeds the Alfv\'en velocity of the magnetized plasma.
 Beyond this radius, this plasma is disconnected from the star.
 Alfv\'en waves set off by the planet within the magnetic field they cross cannot propagate back to the star if the wind carries the plasma away faster than these waves can travel.
-In the sub-Alfv\'enic regime, the wave can reach the star, and deposit its energy in some way.
-\citet{lanza2012starplanet, lanza2018closeby} and \citet{zarka2007plasma, saur2013magnetic} suggest different mechanisms for when and how the energy dissipation takes place, and how much energy can be transferred and dissipated at all.
+In the sub-Alfv\'enic regime, the wave can reach the star, and deposit its energy in some way in its atmosphere.
+\citet{lanza2012starplanet, lanza2018closeby} and \citet{zarka2007plasma, saur2013magnetic} suggest different mechanisms for when and how the energy transport and dissipation takes place, and how much energy can be transferred and dissipated at all.
 
-One way of dissipating the energy in the magnetic field is through flares. 
-Flares are explosions in stellar atmospheres that occur in the stellar corona as a way to dissipate energy stored in the magnetic field by the motion of footpoints of coronal loops.
+\subsection{Searching for global changes in actvity}
+
+Measuring magnetic star planet-interaction is notoriously difficult in individual systems because a non-detection may not mean an absence of the interaction, but just a temporary cessation~\citep{shkolnik2005hot, shkolnik2008nature}.
+Statistical studies searching for changes in global chromospheric and coronal activity indicators in star-planet systems with close-in planets relative to planet-less stars are inconclusive~\citep{kashyap2008extrasolar,scharf2010possible,poppenhaeger2011correlation, shkolnik2013ultraviolet, france2018farultraviolet, viswanath2020statistical, krejcova2012evidence, miller2015comprehensive}.
+In these studies, it is challenging both to define a control sample to measure the activity against, and to quantify how the way we detect planets introduces a bias in the activity measure.
+It is, for instance, easier to detect a planet around a magnetically inactive star, because both radial velocity and transit detections will be less affected by stellar variability.
+
+\subsection{Flares}
+
+In this study, we will look at flares as another way of dissipating the energy deposited in the magnetic field.
+Flares are explosions that occur in the stellar corona as a way to dissipate energy stored in the magnetic field by the motion of footpoints of coronal loops.
 They are strong and impulsive eruptions released by reconnection and subsequent relaxation of field lines~\citep{svestka1976solar,priest2002magnetic}.
-We can observe flares in nearly all electromagnetic bands -- from radio to X-ray~\citep{benz2010physical}.
-In contrast to solar flares, stellar flares often are extremely energetic, sometimes enhancing the stellar flux by orders of magnitude~\citep{maehara2012superflares, shibayama2013superflares, paudel2018k2}.
+In contrast to solar flares, stellar flares often are extremely energetic, sometimes enhancing the stellar flux by orders of magnitude~\citep{maehara2012superflares, shibayama2013superflares, paudel2018k2} so that they can be detected in stars up to hundreds of parsecs away~(XXXX).
 But since they occur randomly in time, individual events can be hard to catch.
+%We can observe flares in nearly all electromagnetic bands -- from radio to X-ray~\citep{benz2010physical}.
 
 In the 2010s, a wealth of flare observations from space missions like Kepler~\citep{borucki2010kepler} and K2~\citep{howell2014k2} have been catalogued~\citep{davenport2016kepler, paudel2018k2, ilin2021flares}.
-We now have access to long-term stellar monitoring data suitable for flare hunting.
-Currently, the Transiting Exoplanet Survey Satellite~\citep{ricker2015transiting} is rapidly expanding the treasury~\citep{gunther2020stellar}, which will grow even further after the launch of the PLATO mission in 2026~\citep{rauer2014plato}.
-As will become clear in the following paragraphs, the key advantage of these missions is their quasi uninterrupted monitoring of star-planet systems that covers all phases of their planets' orbits.
+We now have access to long-term stellar monitoring data available for flare hunting.
+Currently, the Transiting Exoplanet Survey Satellite~\citep{ricker2015transiting} is rapidly growing the archive~\citep{gunther2020stellar}.
+The key advantage of these missions for this work is their quasi uninterrupted monitoring of star-planet systems that covers all phases of their planets' orbits, as will become clear in the following.
+
+\subsection{Flaring star-planet interactions}
 
@@
 The estimates of the maximum dissipated power~\citep{lanza2018closeby} are well within the regime of superflares typically observed by Kepler and TESS.
-However, on the one hand that power is an upper limit, so the observed energies might be lower.
-The planet might for instance be triggering flares prematurely, leading an overabundance of low energy flares~\citep{loyd2023flares}.
+However, on the one hand, that power is an upper limit, so the observed energies might be lower.
+The planet might for instance be triggering flares prematurely, leading to an overabundance of low energy flares~\citep{loyd2023flares}.
 On the other hand, the energy need not be dissipated continuously, particularly in the stretch-and-break mechanism, so it might be higher.
@@
 Flares triggered by the planet will occur at a preferred orbital phase, namely whenever the footpoint is visible to the observer.
-Depending on the system's architecture and magnetic situation, i.e., the inclination of the rotation axis, the spin-orbit (mis-)alignment, and the extent and configuration of the large scale magnetic field -- the footpoint could be always in view, or never.
+Depending on the system's viewing geometry, i.e., the inclination of the rotation axis, the spin-orbit (mis-)alignment, and the extent and configuration of the large scale magnetic field -- the footpoint could be always in view, or never.
 In expectation, however, in star-planet systems with favorable architectures and magnetic field states, the footpoint visibility will be modulated in phase with the planetary orbit.
@@
 
-\citet{fischer2019timevariable} and \citet{howard2021evryflare}
+\subsection{Searching for local changes in activity}
+
+Phase correlated activity, flaring and otherwise, has been searched for in individual systems.
+After eight years of monitoring of HD 189733, an X-ray active Hot Jupiter host, the observed slight clustering of flaring in orbital phase remains tentative~\citep{pillitteri2022xray}.
+\citet{maggio2015coordinated} observed a flare-up in X-ray when the Jupiter-sized companion was in periastron on its highly eccentric orbit around its host HD 17156.
+However, a similar study using chromospheric indicators in the eccentric system HD 80606 found no variation between periastron and apoastron~\citep{figueira2016activity}.
+In the above cases, non-detection can at least partly be attributed to poor orbital phase coverage, which also limits the significance of any positive detection.
+Realizing this, \citet{fischer2019timevariable} used K2 data with excellent phase coverage of the orbits of the inner TRAPPIST-1 planets to look for clustered flaring in phase, but found none.
+Similarly, in \citet{ilin2022searching}, we found hints of excess flaring in the TESS light curves of the young AU Mic system.
+This mixed picture of individual object studies calls for a more comprehensive and systematic approach.
 
@@
 We adopt available rotation period values from the literature.
-Almost all stem from light curve variability~\citep{angus2018inferring, mazeh2015photometric, mcquillan2013stellar, mcquillan2014rotation, luger2017sevenplanet, stock2020carmenes, deleon202137, torres2017validation, stefansson2020habitable, zicher2022one, ment2021toi, rizzuto2020tess}, and only one from periodic variation in chromospheric lines~\citep{demangeon2021warm}.
-When uncertainties are not given, we conservatively assume $10\%$ uncertainty, WHERE ARE THE PERIODS FROM.
+Almost all stem from light curve variability~\citep{angus2018inferring, mazeh2015photometric, mcquillan2013stellar, mcquillan2014rotation, luger2017sevenplanet, stock2020carmenes, deleon202137, torres2017validation, stefansson2020habitable, zicher2022one, ment2021toi, rizzuto2020tess, gunther2020stellar}, and only one from periodic variation in chromospheric lines~\citep{demangeon2021warm}.
+When uncertainties are not given, we conservatively assume $10\%$ uncertainty.
+Uncertainties are missing usually when periods were detected using Lomb-Scargle~\citep{lomb1976leastsquares, scargle1982studies}, or similar, periodogram peaks only~\citep{gunther2020stellar, kiraga2007agerotationactivity, grankin2013magnetically, burt2014lickcarnegie}, but also when the measurement is indirect using activity-rotation relations~(only in the case of GJ 3323).
+
+GJ 3082 periods were measured and are consistent both in TESS and in KELT light curves~\citep{gunther2020stellar} to below 1\,s precision.
+GJ 674 periods are consistent between light curve periodograms~\citep{kiraga2007agerotationactivity} and activity-rotation relations~\citep{boisse2011disentangling} at a $<10\%$ level.
+GJ 3323 only has measured rotation from activity measurements~\citep{astudillo-defru2017magnetic}, without any periodicities detected in the activity indicators themselves~\citep{astudillo-defru2017harps}.
+The rotation period for Proxima Cen is very slow, but consistent between different datasets~\citep{anglada-escude2016terrestrial, kiraga2007agerotationactivity}.
+In general, among the stars without given uncertainties on the rotation period, the period is either
+\begin{itemize}
+    \item short, leaving a clear peak in the periodogram, and little doubt about the period after ruling out aliases with $P/2$, as with GJ 3082, or
+    \item longer than the Sun's, that is, in the regime where rotation-activity relations are reliable because the stars are in the unsaturated activity regime, as in the case of GJ 674.
+\end{itemize}
 
@@
 
-The estimate is consistent with existing Zeeman broadening for, e.g. AU Mic (3010 G~\cite{reiners2022magnetism}).
+The estimate is consistent with existing Zeeman broadening for, e.g. AU~Mic (3010 G~\cite{reiners2022magnetism}).
 \subsection{Power of star-planet interaction}
@@
 \label{sec:discussion:eccentricity}
-If the planetary orbit is highly eccentric, the difference between the semi-major and semi-minor axis can be significantly larger than the variability of the Alfv\'en radius.
+If the planetary orbit is highly eccentric, the difference between periastron and apoastron can be significantly larger than the variability of the Alfv\'en radius.
 If then apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, namely during the planet's rapid periastron passage.
-This was previously exploited in the case of HD 189733, and also for binary interaction in the V 773 Tau system.
-In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e<XXXX$.
-The exception is K2-25, with a moderate $e=0.45$, which may contribute to the increased contrast of excess flares.
+This was previously exploited in the case of HD 189733~(XXXX), and also for binary interaction in the V 773 Tau system~(XXXX).
+In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e\leq 0.35$.
+The exception is K2-25, with a relative high $e=0.45$, which may contribute to the increased contrast of excess flares.
 All else equal, closer proximity increases the strength of interaction.
 Perhaps, K2-25 even moves in and out of the sub-Alfv\'enic zone between periastron and apoastron, turning interaction on and off every single orbit.
-Otherwise, there are therefore no planets where we would expect a strongly preferred orbital phase for interaction.
+If periastron passage occurs when the planet is in front of the star relative to the observer, the visibility effect of the interaction footpoint moving in and out of view as the planet orbits is further enhanced by the narrow phase range of the periastron passage.
 
@@
 \label{sec:discussion:rotsyn}
+Our analysis is the most comprehensive search for flaring star-planet interactions to date, using the full Kepler and most recent TESS archives of light curves.
+We considered exploiting it beyond the search for variations with orbital period, and additionally look for variability with rotation period, and synodic period.
+Here, we explain why we ultimately decided not to do so.
+
+Even for the few stars, for which the rotational period is known precisely enough~(see Fig.~\ref{fig:coherence_hist}) for our analysis, we need to make a large number of assumptions.
+These include the number of active regions crossed by the footpoint of interaction, differential rotation, spot evolution, and a significant correlation between the location of the planet and the location of the planet-induced flare on the stellar surface.
+For modulation with the orbital period, we require only that last correlation between footpoint location and orbital phase.
+Any realistic number of active regions (one or more), a wide range of degrees of differential rotation (from rigid rotator to solar-type), and half-life duration of active regions (day to years) are acceptable, because the observed effect depends predominantly on the visibility of the footpoint, which is governed by orbital motion.
+The latter is much more stable over long periods of time than the intrinsically dynamic magnetic field configuration.
+
 \citet{fischer2019timevariable} argue that the synodic period, at which the sub-planetary point crosses the same (magnetic) surface element on the star, may result in a clearer interaction signal, because a magnetically active region that is prone to planet-induced flares, will be passed only once per period.
 However, this assumes that the landscape of active regions on the star is stable throughout the entire observing time, and that the number of such regions in the footpoint passageway is low enough to produce a periodic modulation.
+Note that this is a different effect from the geometrical modulation of visibility we look for in modulation with the orbital period in this study.
 
@@
 Even if differential rotation was absent and active regions were extremely stable, we will not be able to observe the passage of the sub-planetary point over the flare-prone region every synodic period.
-For a fraction of the time, this will happen on the back of the star relative to the observer.
+If the planet's rotational axis is inclined, then the passage will regularly occur on the back of the star relative to the observer.
 The true period will therefore be additionally modulated by the visibility, resulting in an intermittency of the signal.
 As a consequence, to detect a modulation with the synodic period, a significantly longer observing baseline is needed than to detect a modulation with the orbital period.
-Additionally, if there are multiple active regions that produce flares when the sub-planetary footpoint passes across, the effect with the synodic period is further diluted.
-
-In summary: Even for the few stars, for which the rotational period is known precisely enough~(see Fig.~\ref{fig:coherence_hist}), we need to make assumptions about the number of active regions crossed by the footpoint of interaction, differential rotation, spot evolution, and a significant correlation between the location of the planet and the location of the planet-induced flare on the stellar surface.
-For modulation with the orbital period, we require only that last correlation between footpoint location and orbital phase.
-Any realistic number of active regions (one or more), a wide range of degrees of differential rotation (from rigid rotator to solar-type), and half-life duration of active regions (day to years) are acceptable, because the observed effect depends predominantly on the visibility of the footpoint, which is governed by orbital motion.
-And except for extreme circumstances, the latter will be much more stable over long periods of time than the intrinsically dynamic magnetic field configuration.
+Additionally, if there are many active regions that produce flares when the sub-planetary footpoint passes across, the effect with the synodic period is further diluted.
 
@@
 \label{sec:discussion:intermittency}
-Magnetic star-planet interactions in a given system may sometimes be turned off for episodes of time, and turned on for others.
-HD 179949 is the prototype example, wherein the orbital modulation of chromospheric indicators was observable for XXXX out of XXXXX epochs~\citep{shkolnik2003evidence,shkolnik2008nature}.
+Magnetic star-planet interaction power in a given system may sometimes be low for episodes of time, and high for others.
+HD 179949 is the prototype example for this phenomenon, wherein the orbital modulation of chromospheric indicators was observable for XXXX out of XXXXX epochs on XXXX years baseline~\citep{shkolnik2003evidence,shkolnik2008nature}.
 It is not clear how long a continuous epoch of interaction or non-interaction might be.
@@
 Long-term monitoring is needed to investigate the reasons for the temporary cessation of interaction.
-Candidate mechanisms include: The Alfv\'en radius moving in- and outside the planet's orbit, either over the course of an activity cycle, or through short-term variations in the magnetic field and wind properties caused by, e.g., coronal mass ejections; visibility of the interacting footpoint changing as the magnetic field evolves; the active latitude moving away from the magnetic footpoints passageway, the available magnetic energy decreasing such that the flares or other magnetic interaction indicators still occur but fall below the detection threshold for a period of time.
+Candidate mechanisms for the star include:
+\begin{itemize}
+    \item the Alfv\'en radius moving in- and outside the planet's orbit, either over the course of an activity cycle, or through short-term variations in the magnetic field and wind properties caused by, e.g., coronal mass ejections;
+    \item visibility of the interacting footpoint changing as the magnetic field evolves;
+    \item the active latitude moving away from the magnetic footpoints passageway; or
+    \item the available magnetic energy decreasing such that the flares or other magnetic interaction indicators still occur but fall below the detection threshold for a period of time.
+\end{itemize}
 
-If the magnetic field of the planet changes or disappears, this might also reduce the intensity of interaction below the detection threshold.
+If the magnetic field of the planet changes or disappears as well, this might also reduce the intensity of interaction below the detection threshold.
 
@@
 This could span multiple orbits of the planet, particularly when the surface is populated by few stable active regions, and the orbital and rotational periods are similar.
-The flip-flop behavior of active longitudes could then cause a relatively sudden quenching of interaction by moving the interacting region out of view for a period of time.
+The flip-flop behavior of active longitudes seen in young solar-like stars~(XXXX) could then cause a relatively sudden quenching of interaction by moving the interacting region out of view for a period of time.
 
-In our results in Fig.~\ref{fig:adtest_bp}, we can interpret the two branches emerging at high expected power of interaction as due to the intermittency of the phenomenon.
-TAP 26 and KOI-12 do not show any sign of excess flaring in our data, despite similar expected powers as in HIP 67522 with its $>2\sigma$ signal.
+In our results in Fig.~\ref{fig:adtest_bp}, we can interpret the two branches emerging at high expected power of interaction as due to intermittency.
+TAP 26 and KOI-12 do not show any sign of excess flaring in our data, despite similar expected powers as in HIP 67522 with its $2-3\sigma$ signal.
 In Sections~\ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}, the absence of interaction in TAP 26 and KOI-12 could be explained by an uncertainty in orbital period that smears out the signal, and a super-Alfv\'enic orbit, respectively.
 Yet intermittency cannot be ruled out.
-The case HIP 67522 may be more informative.
+The case HIP~67522 may be more informative.
 In our data, we combine the observation from two TESS Sectors that are almost 2 years apart.
-The four phase-correlated flares all occur in the later Sector, while the earlier one contains only two flares, both of them at orbital phases different from each other and the four phase-aligned flares.
+The four phase-correlated flares all occur in the later Sector, while the earlier one contains only two flares, both of them at orbital phases different both from each other and the four phase-aligned flares~(see Fig.~\ref{fig:cumdist_transiting}).
 This can be interpreted as a tentative sign of intermittency of flaring star-planet interactions in this system.
@@
 Of the systems that have high expected power but do not show any, only TAP 26 is a planet detected in radial velocity, and is expected to have a relatively high orbital inclination of about $55\pm10$ deg inferred from Zeeman Doppler measurements~\citep{yu2017hot}.
-The ZD map reveals magnetic field concentrations close to the rotational pole.
+The ZD map reveals magnetic field concentrations close to the rotational pole, and the brightness maps also show a dark spot in the same location.
 If the orbital plane is aligned with the stellar rotation axis, the absence of phase-correlated flaring in TAP 26 could be explained by the footpoint of interaction being always in view and therefore never modulated.
 
-\subsection{(Mis-)alignment between orbital, rotational and stellar magnetic axis}
-\label{sec:discussion:misalignment}
-Another relevant factor is the geometry of the system.
-If we assume that the magnetic dipole axis and the rotation axis of the star are relatively well-aligned, the spin-orbit alignment may have an influence on interaction strength.
+%If we assume that the magnetic dipole axis and the rotation axis of the star are relatively well-aligned, the spin-orbit alignment may have an influence on interaction strength.
+For instance,  HAT-P-11 rotates nearly pole-on, and HAT-P-11 b is transiting in a near-polar orbit~\citep{bourrier2023dream}.
 
-or more broadly system architecture including misalignment of the magnetic axis. See HAT-P-11, or instance, and the many polar orbits in \cite{bourrier2023dream}
+% \subsection{(Mis-)alignment between orbital, rotational and stellar magnetic axis}
+% \label{sec:discussion:misalignment}
 
-\cite{miskovetz2022resolving}  found background stars that were not co-moving HAT-P-11.
-HAT-P-11 rotates nearly pole-on, and HAT-P-11 b is transiting in a near-polar orbit~\citep{bourrier2023dream}.
-This may be the reason for absent SPI.
+%  Relaxing the assumption of alignment between rotational and magnetic dipole axis, we introduce a further complication that is not only due to viewing geometry.
 
-HD 179949 has a strong misalignment of about 70 deg between rotational and magnetic axis.
+% or more broadly system architecture including misalignment of the magnetic axis. See HAT-P-11, or instance, and the many polar orbits in \cite{bourrier2023dream}
+
+% \cite{miskovetz2022resolving}  found background stars that were not co-moving HAT-P-11.
+
+% HD 179949 has a strong misalignment of about 70 deg between rotational and magnetic axis.
 Time-resolved X-ray observations~\citep{acharya2022xray} suggest that the magnetic interaction footpoint is close to the stellar rotational pole, which would be close to the magnetic equator of the strongly dipolar field of HD 179949
@@
 \label{sec:discussion:commensurability}
+Curiously, in our analysis, systems with high expected power are divided: Stars that show a correlation between excess flaring and expected power tend to have closer spin-orbit commensurability than systems that are far away from any low-integer ratio between rotational and orbital period.
+
 In Fig.~\ref{fig:spinorbit}, we split our sample into three categories.
@@
 The second includes the systems where a high power of interaction is expected, but none is measured (e.g., TAP 26, KOI-12).
-The final third category contains all system where the data suggest a correlation between expected power of interaction and measured flaring star-planet interaction signal (e.g., HIP 67522, AU Mic).
+The final third category contains all system where the data suggest a correlation between expected power of interaction and measured flaring star-planet interaction signal (i.e., K2-25, TOI-540, HIP 67522, and AU Mic).
 We search for spin-orbit commensurability with integers $<10$ in each system, and plot the relative difference between the closest ratio and the actual spin-orbit ratio.
 Systems with low expected power of interaction span both very close spin-orbit commensurability to none.
-Systems with high expected power are divided: Stars that show a correlation between excess flaring and expected power tend to have closer spin-orbit commensurability than systems that are far away from any low-integer ratio between rotational and orbital period.
+However, the second and third group form two separate populations.
+Non-interacting systems are further away from low-integer commensurability, than interacting ones, even though both have high expected power.
 
-While chance alignment is possible, the division invokes the idea that spin-orbit commensurability and magnetic star-planet interaction are related.
+While chance alignment is possible, the division suggests that spin-orbit commensurability and magnetic star-planet interaction are related.
 Either something about our observing method favors the measurement of excess flaring in systems with close spin-orbit commensurability, or there is physical causation at play.
@@
 This model requires tidal interaction, which may be too weak in systems like AU Mic, where the planet is too small and distant for the proposed effect~\citet{lanza2022model}, but that still show spin-orbit commensurability and signs of flaring star-planet interaction.
-However, for systems with $m=1$, like HIP~67522, or $\tau$ Boo~\citep[which is not in our sample]{walker2008nature, cauley2019magnetic}, this model would directly favor active regions that rotate with the orbital period instead of the rotational one.
 
@@
 
-\citet{szabo2021changing} note that many systems within the sparsely populated region of close-in planets around rapid rotators~\citep{mcquillan2013stellar} seem close to low-integer spin-orbit resonance.
+\citet{szabo2021changing} conjecture that many systems within the sparsely populated region of close-in planets around rapid rotators~\citep{mcquillan2013stellar} seem close to low-integer spin-orbit resonance.
 The systems with consistently high expected power of interaction (TAP 26, TOI-540, KOI-12, HIP 67522, K2-25, and AU Mic) are all found within that region, even if KOI-12 and AU Mic lie rather close to its edge.
@@
 We may speculate, that at least some of the mechanisms that explain the dearth of close-in planets around rapidly rotating stars also explain the presence of star-planet magnetic interaction in those systems that are still found there.
-One may think that planets that remain in the desert are held there by being trapped in the resonance, while for the others, the magnetic torque cause rapid migration out of this region.
+One may think that planets that remain in the desert are held there by being trapped in the resonance, while for the others, the magnetic torque causes rapid evolution out of this region through spin-down of the star throug both magnetic braking and star-planet interaction, and the planet's migration to higher orbital periods through the latter mechanism.
 
@@
 
-\subsection{Tidal or magnetic interaction?}
-\label{sec:discussion:tidalmagnetic}
-The tight spin-orbit commensurability in some systems may give rise to stable spot patterns on the star that rotate with the commensurable period~\citep{lanza2022model}, and perhaps appear preferentially in the orbital plane of the tidally interacting planet.
-It is possible that the enhanced periodicity seen with the orbital period in systems close to a low integer spin-orbit commensurability is an effect of such tidally created spots that lie along the passageway of the planet's magnetic footpoint.% On the other hand, magnetic interactions, wherein the direct perturbation of stellar field by the planetary obstacle cannot be ruled out~\citep{lanza2018closeby, saur2013magnetic}.
-
-Both mechanisms may play a role, but to understand their respective contribution, we require approaches that can unambiguously discriminate between the two.
-
-While suggestive, our data are statistically insufficient to conclude whether the flaring interaction is driven only by magnetic interaction, or whether tidal effects, and more specifically spin-orbit resonances, play a role.
-Further monitoring of the systems in our sample will clarify whether the interaction is statistically significant for individual systems, or whether the branching is caused by intrinsic intermittency of the effect.
-If the branching persists over time, and systems do not switch from the inactive to the active branch or vice versa, the distinction may more likely be due to spin-orbit resonance.
-
-Another possibility is that the branching disappears in favor of a continuous distribution. This would put in question the on-off nature of magnetic interactions.
-
-Ways to investigate which mechanisms play a role using flaring:
-
-Search for flaring star-planet interactions in rapidly rotating fully convective stars with close-in planets or brown dwarfs.
-There are very few such systems, TOI-540 among them.
-These systems have only negligible differential rotation so that the rotation period of surface features can be precisely known.
-In those cases, we may figure out whether interaction occurs with the synodic period.
-
-Search for ECMI emission in radio from systems that have high expected power of interaction.
-If periodic radio emission is seen predominantly in the systems that also show flaring star-planet interactions, magnetic interaction is relevant because coherent radio emission stems from large scale fields, and not from resonantly emerging patterns of active regions as suggested by~\citet{lanza2022model}.
-
-spetral type dependence of tidal interaction
-
 \section{Summary and Conclusions}
 \label{sec:summary}
+
+We have conducted the so far largest search for flaring star-planet interactions.
+Using over 7000 Quarters and Sectors of photometric monitoring from Kepler and TESS archives, we found searched for flares in over 1800 systems of the over 3000 listed in the NASA Exoplanet Archive.
+In those systems that were single stars, where flares could be unambiguously attributed to the planet host, and showed three or more energetic events in the data, we searched for flares that clustered in orbital phase.
+Our final sample consisted of 26 systems, among them well-known flaring hosts like Proxima Cen, AU Mic, and TRAPPIST-1.
+
+Applying both the stretch-and-break and Alfv\'en wing mechanisms discussed for magnetic interaction, we found evidence for a correlation between the expected power of interaction, and the presence of excess flaring in phase with the orbital period.
+In particular, we found that there may be two branches at high expected power -- one where the measured excess flaring is correlated with the expected power, and one where this is not the case.
+This may be an effect of intermittency in the interaction, but viewing geometry may also play a major role, and orbital eccentricity a minor one.
+
+Although no individual system shows flaring star-planet interaction on a significant level, the ensemble result is still curious.
+In particular, the two branches form two separate populations on another dimension.
+Systems on the correlated branch are closer to spin-orbit commensurability with low-integer ratios than their non-interacting counterparts.
+If this interaction is causal, either magnetic-star planet interaction traps star-planet systems in these resonances, or the excitement of these resonances -- tidally or magnetically -- favors the presence of flaring clustered in orbital phase.
+
+Our study is the first that systematically searched for flaring star-planet interactions, and is not limited by sampling biases in the way earlier ensemble based searches for this effect have been~(XXXX).
+While our results remain tentative due to the small final sample, future studies using our technique will accumulate more and more data.
+The TESS mission continues to produce high precision light curves for many nearby active planet hosts, and the PLATO mission will join in late 2026.
+For AU Mic, we may be only a few TESS Sectors away from a $3\sigma$ level confirmation~\citep{ilin2022searching} of the tentative interaction signal observed here and in other work~\citep{klein2022one}.
+HIP 67522, the system with the strongest individual signal, will be re-observed by TESS as soon as April 2023.
+
+Close-in planets around young, active stars are being explored as in-situ probes of the dynamic magnetic~(XXXX), and stellar mass loss~\citep{vidotto2017exoplanets} conditions in their orbit.
+Together, mass loss and magnetism form two key components of the space weather that a potentially habitable planet will encounter.
+The orbits where sub-Alfv\'enic interaction, of the kind we searched for in this work, can take place are usually closer to the star than its habitable zone.
+However, in late M dwarfs like TRAPPIST-1, these two regions overlap~\citep{strugarek2021physics}, and information from closer in is still crucial (or else why would we send probes to the Sun?).
+We only begin to uncover the invaluable information that close-in planets can provide about the ever-changing environment of habitable-zone terrestrial planets.
 
@@
 
-\subsection{GJ 393}
-Eccentricity likely low, but not quantified in \cite{amado2021carmenes}, so we treat it as unconstrained (set e=0.5)
-
 \subsection{Kepler-42}

### 2023-03-23 src/scripts/paper_main_table.py

@@ -393,6 +393,7 @@ if __name__ == "__main__":
         string = string.replace(r"$nan^{nan}_{nan}$",r"--")
         string = string.replace(r"nan",r"-")
         string = string.replace(r"NaN",r"-") 
+        string = string.replace(r"0.0e+00",r"0.0")
         string = string.replace("midrule","hline")
         string = string.replace("toprule","hline")
         string = string.replace("bottomrule","hline")

### 2023-03-23 src/scripts/paper_spin_orbit_commensurability.py

@@ -95,6 +95,9 @@ if __name__ == "__main__":
     # GJ 1061 because rotation is unclear
     df = df[df.TIC != "79611981" ]
 
+    # pick only single systems
+    df = df[df["multiple_star"].isnull()]
+
     # set tolerance to ratios with values <10 each
     tol = 0.01
 
@@ -199,3 +202,6 @@ if __name__ == "__main__":
     fig.savefig(paths.figures / "PAPER_spin_orbit_commensurable.png", dpi=300)
 
 
+    # save table to data folder
+
+    df.to_csv(paths.data / "results_spin_orbit_commensurable.csv", index=False)

### 2023-03-24 src/scripts/paper_main_table.py
edit bad format of zero in paper_main_table

@@ -393,7 +393,7 @@ if __name__ == "__main__":
         string = string.replace(r"$nan^{nan}_{nan}$",r"--")
         string = string.replace(r"nan",r"-")
         string = string.replace(r"NaN",r"-") 
-        string = string.replace(r"0.0e+00",r"0.0")
+        string = string.replace("0.0e+00",r"0.0")
         string = string.replace("midrule","hline")
         string = string.replace("toprule","hline")
         string = string.replace("bottomrule","hline")

### 2023-03-24 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 One of the most surprising results in exoplanet research is the diversity of star-planet system architectures.
-In particular, the past two decades revealed that planets can occur in orbits so close to their host star that they could be considered to live inside the stellar atmosphere.
+The past two decades revealed that planets can occur in orbits so close to their host star that they could almost be considered to live inside the stellar atmosphere.
 At this proximity, the planet exerts force, tidal and magnetic, both short- and long-term, on its host -- a phenomenon largely unknown to the Solar System.
-These forces are typically subsumed under the term star-planet interactions that emphasizes that they are bidirectional, affecting both planet, and star.
+These forces are typically subsumed under the term star-planet interactions (SPI) that emphasizes that they are bidirectional, affecting both planet, and star.
+Their effects pose challenges, but also opportunities for our understanding of star-planet systems:
 
@@
 
+The search for magnetic SPI (Section~\ref{sec:intro:mspi}) in the form of changes in global activity indicators~(Section~\ref{sec:intro:local}), has so far been a series of detections and non-detections, often due to selection bias in the studied systems.
+Looking for local changes that trace the magnetic footpoint that connects planet to star mitigates this bias, but introduces another -- sampling bias due to poor orbital phase coverage.
+Flares~(Section~\ref{sec:intro:flares}) are activity markers that can be caused by SPI~(Section~\ref{sec:intro:fspi}), and be monitored more easily with high phase coverage than chromospheric lines or coronal brightness over long periods of time with missions like Kepler and TESS.
+Thanks to their enormous archives of hundreds of cumulative years of stellar monitoring, we can overcome the limitations of individual system studies~(Section~\ref{sec:intro:local}), and now look for flaring SPI more comprehensively, and systematically.
+
 \subsection{Magnetic star-planet interactions}
-
+\label{sec:intro:mspi}
 Magnetic star-planet interactions can only occur if the planet is orbiting within the Alfv\'en radius of the star.
-It does not need to be there all the time, but for a time period that is longer than it takes for the effects of the planet to travel to the surface of the star.
 The Alfv\'en radius is the radius at which the stellar wind velocity, which increases with increasing distance from the star, exceeds the Alfv\'en velocity of the magnetized plasma.
@@
 \citet{lanza2012starplanet, lanza2018closeby} and \citet{zarka2007plasma, saur2013magnetic} suggest different mechanisms for when and how the energy transport and dissipation takes place, and how much energy can be transferred and dissipated at all.
+All suffer from a lack of observational constraints for calibration.
 
 \subsection{Searching for global changes in actvity}
-
+\label{sec:intro:global}
 Measuring magnetic star planet-interaction is notoriously difficult in individual systems because a non-detection may not mean an absence of the interaction, but just a temporary cessation~\citep{shkolnik2005hot, shkolnik2008nature}.
-Statistical studies searching for changes in global chromospheric and coronal activity indicators in star-planet systems with close-in planets relative to planet-less stars are inconclusive~\citep{kashyap2008extrasolar,scharf2010possible,poppenhaeger2011correlation, shkolnik2013ultraviolet, france2018farultraviolet, viswanath2020statistical, krejcova2012evidence, miller2015comprehensive}.
-In these studies, it is challenging both to define a control sample to measure the activity against, and to quantify how the way we detect planets introduces a bias in the activity measure.
-It is, for instance, easier to detect a planet around a magnetically inactive star, because both radial velocity and transit detections will be less affected by stellar variability.
+Statistical studies searching for changes in global chromospheric and coronal activity indicators in star-planet systems with close-in planets relative to planet-less stars are inconclusive~\citep{kashyap2008extrasolar,scharf2010possible, shkolnik2013ultraviolet, france2018farultraviolet, viswanath2020statistical, krejcova2012evidence, miller2015comprehensive}.
+In these studies, it is challenging both to define a control sample to measure the activity against, and to quantify how the way we detect planets introduces selection bias in the activity measure.
+It is, for instance, easier to detect a planet around a magnetically inactive star, because both radial velocity and transit detections will be less affected by stellar variability~\citep{poppenhaeger2011correlation}.
 
 \subsection{Flares}
-
-In this study, we will look at flares as another way of dissipating the energy deposited in the magnetic field.
-Flares are explosions that occur in the stellar corona as a way to dissipate energy stored in the magnetic field by the motion of footpoints of coronal loops.
-They are strong and impulsive eruptions released by reconnection and subsequent relaxation of field lines~\citep{svestka1976solar,priest2002magnetic}.
+\label{sec:intro:flares}
+In this study, we will look at stellar flares as another way of dissipating the energy deposited in the magnetic field.
+Flares are strong and impulsive eruptions released by reconnection and subsequent relaxation of field lines in the corona~\citep{svestka1976solar,priest2002magnetic}.
 In contrast to solar flares, stellar flares often are extremely energetic, sometimes enhancing the stellar flux by orders of magnitude~\citep{maehara2012superflares, shibayama2013superflares, paudel2018k2} so that they can be detected in stars up to hundreds of parsecs away~(XXXX).
@@
 Currently, the Transiting Exoplanet Survey Satellite~\citep{ricker2015transiting} is rapidly growing the archive~\citep{gunther2020stellar}.
-The key advantage of these missions for this work is their quasi uninterrupted monitoring of star-planet systems that covers all phases of their planets' orbits, as will become clear in the following.
+As will become clear in the following Section, their key advantage for this work is the quasi uninterrupted monitoring of star-planet systems that covers all phases of a close-in planet's orbit.
 
 \subsection{Flaring star-planet interactions}
-
+\label{sec:intro:fspi}
 The absolute power of flaring star-planet interactions is difficult to constrain, so we do not know how energetic planet-induced flares can be.
@@
 \subsection{Searching for local changes in activity}
-
+\label{sec:intro:local}
 Phase correlated activity, flaring and otherwise, has been searched for in individual systems.
@@
 We present the catalog of all flares found in our sample of star-planet systems, and compare the test results with the expected power of interaction for each system~(Section~\ref{sec:results}).
-We discuss the results for the most interesting star-planet systems individually~(Section~\ref{sec:results:individualstars}, and take a look at the more general patterns emerging from our systematic analysis~(Section~\ref{sec:discussion}).
-Finally, we summarize our findings, and suggest future observations that could uncover the star-planet interaction mechanisms operating behind the observed trends~(Section~\ref{sec:summary}).
+We discuss the results for the most interesting star-planet systems individually~(Section~\ref{sec:results:individualstars}), and take a look at the patterns emerging from our analysis~(Section~\ref{sec:discussion}).
+We summarize our findings in Section~\ref{sec:summary}.
 
@@
 \label{sec:data}
-In this study, we wanted to compile the largest possible sample to search for flaring star-planet interactions, so took the entire Planetary Systems Composite Parameters Table (PSCP, Section~\ref{sec:data:sps})\footnote{ \url{https://exoplanetarchive.ipac.caltech.edu/cgi-bin/TblView/nph-tblView?app=ExoTbls&config=PSCompPars}} from the NASA Exoplanet Archive, and scanned the systems for available Kepler and TESS light curves~(Section~\ref{sec:data:photometry}).
-We ended up searching a total of 1812 systems and over 7200 light curves from both missions for flares.
+In this study, we wanted to compile the largest possible sample to search for flaring star-planet interactions.
+We took the entire Planetary Systems Composite Parameters Table (PSCP, Section~\ref{sec:data:sps})\footnote{ \url{https://exoplanetarchive.ipac.caltech.edu/cgi-bin/TblView/nph-tblView?app=ExoTbls&config=PSCompPars}} from the NASA Exoplanet Archive, as of July 2022, and scanned the systems for available Kepler and TESS light curves~(Section~\ref{sec:data:photometry}).
+We searched a total of 1811 systems and over 7200 light curves from both missions for flares.
 To calculate the amount of excess flaring from star-planet interaction, we then required the orbital periods of each system~(Section~\ref{sec:data:orbitalperiod}).
-To compare our measurements to theory, we also wanted to estimate the expected power of interaction for each system with at least three flares.
-For this, we required further system parameters -- distance between planet and star, stellar rotation periods, planetary radii, and stellar luminosity~(Sections~\ref{sec:data:orbitalperiod}-\ref{sec:data:lum}).
-We started compiling the table of system parameters with the PSCP, but verified, supplemented and updated the table from the literature.
+To compare our measurements to theory, we estimated the expected power of interaction for each system with at least three flares.
+For this, we required further system parameters -- distance between planet and star, stellar rotation period, planetary radius, and stellar luminosity~(Sections~\ref{sec:data:orbitalperiod}-\ref{sec:data:lum}).
+We began by compiling the table of system parameters with the PSCP, but verified, supplemented and updated the table from the literature.
 The literature parameters for the systems in the final sample of systems, for which we performed the full analysis, is shown in Table~\ref{tab:maintable_lit}.
+
+\begin{table*}
+\movetableright=-20mm
+\footnotesize
+    \script{paper_main_table.py}
+    \caption{Flaring single star-planet system parameters.}
+    \input{output/table_lit_vals.tex}
+        \label{tab:maintable_lit}
+    \tablerefs{\input{output/lit_table_bibstring.tex}}
+\end{table*}
 
@@
 \label{sec:data:photometry}
-The Kepler and TESS missions are unbeatable with respect to long-term optical monitoring of stellar flares.
+The Kepler and TESS missions are unbeaten with respect to long-term optical monitoring of stellar flares.
 Their excellent coverage of orbital phases makes the light curves ideal for our search for orbital phase dependent flare timing.
@@
 Between 2009 and 2013, the Kepler space telescope~\citep{koch2010kepler} nearly continuously observed a patch of the sky in the Cygnus-Lyra region.
-Each of the 18 observing Quarters contains nearly uninterrupted $\sim 90$ days of observations, totaling over 100000 stars monitored in 2-min cadence.
+Each of the 18 observing Quarters contains nearly uninterrupted $\sim 90$ days of observations, totaling over $100\,000$ stars monitored in 2-min cadence in a broad $400-850\,$nm bandpass.
 % 100000 from here: https://exoplanetarchive.ipac.caltech.edu/docs/KeplerMission.html
@@
 The Transiting Exoplanet Survey Satellite~(TESS,~\cite{ricker2015transiting}) is an all-sky mission that began operations in 2018, completed two sky scans until summer 2022.
-It is observing at the time of writing, collecting nearly continuous photometric time series in the 600-1000 nm band for $\sim 27 days$ in each observing Sector.
-About $200\,000$ stars have been observed in 2-min cadence in the first two years of operations with about 20000 targets per Sector.
-Out of these, from Sector 27 on, 1000 targets were observed at even higher 20-s cadence in each Sector.
+It is observing at the time of writing, collecting nearly continuous photometric time series in the $600-1000\,$nm band for $\sim 27\,$d in each observing Sector.
+About $200\,000$ stars have been observed in 2-min cadence in the first two years of operations alone, with about $20,000$ targets per Sector.
+Out of these, from Sector 27 on, $1,000$ targets were observed at even higher 20-s cadence in each Sector.
 % 20000 per sector does not add up, because of stars observed in multiple sectors, the 20000 and 1000 figures can be found here: https://tess.mit.edu/observations/target-lists/
@@
 
-Based on the filtered PSCP table, we queried the full Kepler archive (quarters Q0-Q17, Data Release 25), and the most recent TESS catalog (July 2022) for their respective 1-min and 2-min/20-s cadence light curves.
+Based on the filtered PSCP table, we use the \texttt{lightkurve}~\citep{lightkurvecollaboration2018lightkurve} software to query the full Kepler archive (quarters Q0-Q17, Data Release 25), and the most recent TESS catalog (July 2022) for their respective 1-min and 2-min/20-s cadence light curves.
 In total, we searched 7258 light curves for flares -- 3030 Kepler Quarters, and 4228 TESS Sectors.
@@
 For the transiting systems, we use the transit mid-times given in the PSCP to set orbital phase zero.
-If possible, we do this for each mission separately to reduce the uncertainties on orbital phase.
+If possible, we use the transit mid-times determined in each mission separately to reduce the uncertainties on orbital phase.
 For the non-transiting system, phase zero is set arbitrarily.
@@
 
-GJ 3082 periods were measured and are consistent both in TESS and in KELT light curves~\citep{gunther2020stellar} to below 1\,s precision.
-GJ 674 periods are consistent between light curve periodograms~\citep{kiraga2007agerotationactivity} and activity-rotation relations~\citep{boisse2011disentangling} at a $<10\%$ level.
-GJ 3323 only has measured rotation from activity measurements~\citep{astudillo-defru2017magnetic}, without any periodicities detected in the activity indicators themselves~\citep{astudillo-defru2017harps}.
-The rotation period for Proxima Cen is very slow, but consistent between different datasets~\citep{anglada-escude2016terrestrial, kiraga2007agerotationactivity}.
+The rotation of GJ 3082 was measured and are consistent both in TESS and in KELT light curves to below 1\,s precision~\citep{gunther2020stellar}.
+The rotation of GJ 674 is consistent between light curve periodograms~\citep{kiraga2007agerotationactivity}, and activity-rotation relations~\citep{boisse2011disentangling} at a $<10\%$ level.
+GJ 3323 only has rotation periods inferred from activity indicators~\citep{astudillo-defru2017magnetic}, without any periodicity detected in the activity indicators themselves~\citep{astudillo-defru2017harps}.
+The rotation of Proxima Cen is very slow, but consistent between different datasets~\citep{anglada-escude2016terrestrial, kiraga2007agerotationactivity}.
 In general, among the stars without given uncertainties on the rotation period, the period is either
@@
 For the non-transiting radial velocity detected planets we use the planetary mass $M_p$ or $M_p\sin i$ to calculate the radius or a lower limit for the radius using the empirical relations derived in \cite{chen2017probabilistic} using their open source \texttt{forecaster} tool, upgraded to \texttt{astro-forecaster}\footnote{https://pypi.org/project/astro-forecaster/} by Ben Cassesse.
-We note that for GJ 674, the mass estimates in \cite{bonfils2007harps} and \cite{boisse2011disentangling} do not quote uncertainties, but differ by 0.3MEarth, so we assumed that value as the uncertainty on $M_p\sin i$.
+We note that for GJ 674, the mass estimates in \cite{bonfils2007harps} and \cite{boisse2011disentangling} do not quote uncertainties, but differ by $0.3M_\oplus$, so we assumed that value as the uncertainty on $M_p\sin i$.
 
@@
 We take bolometric luminosity values as given in the PSCP whenever they are given with uncertainties.
-We supplement missing values, and replace entries without quoted uncertainties with Gaia DR3 FLAME~\citep{fouesneau2022gaia} solutions~(\texttt{lum\_flame}).
+We supplement missing values, and replace entries without quoted uncertainties with Gaia DR3 FLAME~\citep{fouesneau2022gaia} solutions~(\texttt{lum\_flame, lum\_flame\_upper, lum\_flame\_lower}).
 
@@
 We then perform a customized Anderson-Darling test on the flare peak time distribution, which yields a p-value for the significance of the SPI signal.
-Finally, we compare these results to the theoretically expected SPI power $P_{SPI}$ in each system.
+Finally, we compare these results to the theoretically expected SPI power $P$ in each system.
 
@@
 Sections~\ref{sec:methods:relvel} and \ref{sec:methods:bfield}, respectively.
-With relative velocity and magnetic field strength derived, we can combine them with stellar radius, planetary radius, and semi-major axis to estimate the power of SPI.
+We can then combine them with stellar radius, planetary radius, and semi-major axis to estimate the power of SPI.
 We use the scaling laws from two different magnetic SPI models, which we introduce in Section~\ref{sec:methods:pspi}.
@@
 To remove trends and rotational variability from the light curve without losing the flare signal, we use an empirically derived multistep process.
-First, we apply spline fit with a coarse sampling of 30h mean values to capture slow rotation with periods above multiple days and non-periodic trends.
+First, we apply a spline fit with a coarse sampling of 30h-averaged values to capture slow rotation with periods above multiple days and non-periodic trends.
 Then, we iteratively fit a series of sines to capture rotational signal on time scales down to about half a day, close to the fastest rotational signals measured in low mass stars.
-Eventually, we apply two Savitzky-Golay~\cite{savitzky1964smoothing} filters in sequence, with window sizes of 6h and 3h each.
+Eventually, we apply two Savitzky-Golay~\citep{savitzky1964smoothing} filters in sequence, with window sizes of 6h and 3h each.
 At this stage, we mask all data points above a $2.5 \sigma$ (or $1.5 \sigma$ for very active stars like AU Mic or Proxima Cen) threshold as flare candidates to prevent the filter from ironing out the flares.
@@
 
-In these light curves, we then search for flares as series of at least three consecutive data points $3\sigma$ above the noise level, implemented in AltaiPony~\cite{ilin2021altaipony}.
-We estimate the noise
-level as the standard deviation in a rolling window of two hours, while masking deviation above $2.5\sigma$ (or $1.5$ sigma for active stars).
-To capture the exponential tail of the flare, we use the \texttt{addtail} flag to continue adding data points to the end of the flare as long as they are $2\sigma$ above the noise threshold.
-For these flares, we calculate the relative amplitude $a$ and equivalent duration $ED$, defined as the integrated flare flux $F_{flare}$ over the duration of the flare, divided by the median flux $F_0$ of the star, integrated over the flare duration~\citep{gershberg1972results}:
+In the de-trended light curves, we search for flares as series of at least three consecutive data points $3\sigma$ above the noise level, implemented in AltaiPony~\cite{ilin2021altaipony}.
+We estimate the noise level as the standard deviation in a rolling window of two hours, while masking deviation above $2.5\sigma$ (or $1.5$ sigma for active stars).
+To capture the exponential tail of the flare, we use the \texttt{addtail} flag in the \texttt{find\_flares} method to continue adding data points to the end of the flare as long as they are $2\sigma$ above the noise threshold.
+
+We vet all flare candidates by eye, and exclude instrumental false positives and physical one like Solar System Objects.
+For each confirmed flare candidate, we calculate the relative amplitude $a$ and equivalent duration $ED$, defined as the integrated flare flux $F_{flare}$ over the duration of the flare, divided by the median flux $F_0$ of the star, integrated over the flare duration~\citep{gershberg1972results}:
 \begin{equation}
@@
 \label{sec:methods:adtest}
-For each star-planet system with three or more flares in their Kepler and/or TESS light curves, we test for deviations from a random distribution of flares with orbital phase.
+For each star-planet system with three or more flares in their light curves, we test for deviations from a random distribution of flares with orbital phase.
 We use the same customized Anderson-Darling test as in \cite{ilin2022searching}.
-In brief, we first take the number of flares observed in the TESS and Kepler data, calculate a base flare rate for each light curve.
-We then calculate how often each orbital phase has been covered by the data, again for each light curve.
+In brief, we first take the number of flares observed in the TESS and Kepler data to calculate a base flare rate for each light curve.
+We then calculate how often each orbital phase has been covered by the data, also for each light curve separately.
 With the phase coverage and base flare rate combined, we can tell how many flares we would expect to see in any given phase bin if flares were randomly distributed.
-This number of expected flares per bin can be aggregated into one expected distribution by summing over all available light curves.
-As a last step, this distribution is then compared to the observed one using an Anderson-Darling test.
+We then aggregate this number of expected flares per time bin into one expected distribution by summing over all available light curves.
+As a last step, we compare this distribution to the observed one using an Anderson-Darling test.
 We repeat this test with different phase offsets to account for potential biases in sensitivity of the test at different phases.
@@
 \label{sec:methods:relvel}
-We calculate the relative velocity between the magnetic field of the star, which we assume is co-rotating with the stellar rotation period $P_{rot}$, at the planetary orbit, where the planet moves with a period $P_{orb}$:
+We calculate the relative velocity between the magnetic field of the star and the planet using stellar rotation period $P_{rot}$, orbital period $P_{orb}$, and semi-major axis $a$.
+We assume that the large scale magnetic field is co-rotating with the stellar surface, and calculate the relative velocity at the planet's orbital distance:
 
@@
 \begin{equation}
-    P_{sb} \sim B_p^{2/3} B_*^{4/3} v_{rel} R_p^2 a^{-4} R_*^4.
+    P_{sb} \sim B_p^{2/3} R_p^2 B_*^{4/3} R_*^4 v_{rel} a^{-4} .
 \end{equation}
 
-$B_p$ and $B_*$ are the total planetary and stellar surface field strengths, respectively; $v_{rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis; and $R_*$ and $R_p$ are the stellar and planetary radii, respectively; and $a$ is the semi-major axis.
+$B_p$ and $B_*$ are the total planetary and stellar surface field strengths, respectively; $v_{rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis $a$; and $R_*$ and $R_p$ are the stellar and planetary radii, respectively.
 
@@
 \begin{equation}
-    P_{sb0} \sim B_*^2 v_{rel}  R_p^2  a^{-4} R_*^4
+    P_{sb0} \sim R_p^2 R_*^4 B_*^2 v_{rel}    a^{-4} 
 \end{equation}
 
-Third, for comparison, we estimate the power of star-planet interaction generated by the Alfv\'en wing mechanism ~\cite{saur2013magnetic,kavanagh2022radio}, combining Eqs.~8~and~11 in \cite{kavanagh2022radio} to give
+Third, for comparison, we estimate the power of star-planet interaction generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio}, combining Eqs.~8~and~11 in \citet{kavanagh2022radio} to give
 
 \begin{equation}
-    P_{aw} \sim R_{p}^2  B_p^{2/3}  B^{1/3}  v_{rel}^2 a^{-2}  
+    P_{aw} \sim B_p^{2/3} R_{p}^2    B_*^{1/3}  v_{rel}^2 a^{-2}  
 \end{equation}
-where we approximate the stellar wind density $\rho_W$ with $a^{-2}$ and stellar wind magnetic field at the planetary radius $B_W$ with the surface field strength $B a^{-3}$, which result in the total $a^{-2}$ factor.
+where we approximate the stellar wind density $\rho_W$ with $a^{-2}$ and stellar wind magnetic field at the planetary radius $B_W$ with the surface field strength $B_* a^{-3}$, which result in the total $a^{-2}$ factor.
 
@@
 \begin{equation}
-    P_{aw0} \sim R_p^2  B  v_{rel}^2  a^{-4}
+    P_{aw0} \sim R_p^2  B_*  v_{rel}^2  a^{-4}
 \end{equation}
@@
 For the star-planet systems in the resulting flare catalog~(Section~\ref{sec:results:catalog}), we confirmed that the orbital phase could be known well enough for the entire observing baseline of the system~(Section~\ref{sec:results:coherence}).
-Knowing that, we could move on to calculate the orbital phases of each flare, and calculate distributions for each system in the catalog~(Section \ref{sec:results:phasedist}).
-We then applied the custom Anderson-Darling test to check how likely it is that some of the flares were triggered by the planet.
-Comparing the test results with the expected power of magnetic star-planet interaction, we found that the probability of observing planet induced flares increases with the expected power in all considered scenarios~(Section~\ref{sec:results:spi}).
-However, not all systems with high expected power show signs of flaring SPI, which appears as a branching in the distribution of test results, and could be due to the intermittency of the interaction.
-Finally, we provide additional context for the most interesting systems in our sample, and explain why we had to exclude some systems from the analysis in Section~\ref{sec:results:individualstars}.
+Knowing that, we could calculate the orbital phases of each flare, and the flare phase distributions for each system~(Section \ref{sec:results:phasedist}).
+We then applied the custom Anderson-Darling test to check how much each distribution was different from randomly distributed intrinsic flaring.
+Comparing the test results with the expected power of magnetic star-planet interaction, we found that the amount of excess flaring tentatively increases with the expected power in all considered scenarios~(Section~\ref{sec:results:spi}).
+However, not all systems with high expected power show signs of flaring SPI, which appears as a branching in the distribution of test results.
+To prepare the subsequent discussion, we provide additional context for the most interesting systems in our sample, and explain why we had to exclude some systems from the analysis in Section~\ref{sec:results:individualstars}.
 \subsection{Flare catalog}
@@
 If the transit midtime is known for the innermost planet, we also give the orbital phase at which the flare occurred.
-The full table is provided with the supplementary material and via Zenodo (see Data Availability).
+The full table is provided with the supplementary material, and via Zenodo (see Data Availability Statement).
 
@@
         }
+    \footnote{Full catalog is available online (see Data Availability Statement).}
     \input{output/flare_table.tex}
@@
 where $P$ is the orbital period, and $\sigma_P$ is its uncertainty.
-The resulting ratio should be $<<1$.
+If the orbital period is well-known, the resulting ratio should be $<<1$.
 The bottom panel in Figure~\ref{fig:coherence_hist} shows a histogram of these ratios in our sample.
-The orbital period is known sufficiently well for our analysis in most cases with ratios $<0.02$.
+The orbital period is known sufficiently well for our analysis in most cases with ratios $<0.02$, that is, the orbital phase of last flare is at most $2\%$ off, compared to the first.
 The three cases where the ratio is highest with $0.05$, $0.12$, $0.24$ deviation are TAP 26, GJ 3082, and GJ 674, respectively.
@@
 
-We repeated the coherence calculation for $P_{rot}$, and found that the ratio is $>.1$ for most stars~(Figure~\ref{fig:coherence_hist}, top panel).
-There are three reasons for this: First, the uncertainty for the rotation was not always provided.
-Second, rotation period is more difficult to ascertain from a light curves' variability than the orbital period, particularly if the modulation is weak and or rapidly evolving.
-And third, differential rotation causes spots at different latitudes to move at different speeds, so it becomes difficult to even define a rotation period, as long as we don't know at which latitude(s) the flares occur.
+We repeated the coherence calculation for $P_{rot}$, and found that the ratio is $>0.1$ for most stars~(Figure~\ref{fig:coherence_hist}, top panel).
+There are three reasons for this: First, the uncertainty for the rotation was not always provided, in which case we assigned a $10\%$ error.
+Second, rotation period is more difficult to ascertain from a light curves' variability than the orbital period, particularly if the modulation is weak and/or rapidly evolving.
+And third, differential rotation causes spots at different latitudes to move at different speeds, so it becomes difficult to even define a rotation period, as long as we don't know at which latitude(s) the flares occur~(see also Section~\ref{sec:discussion:rotsyn}).
 
@@
            Time span of observation vs.
-coherence time of the orbital and rotational periods, respectively.
+coherence time of the rotational (\textbf{top panel}) and orbital (\textbf{bottom panel}) periods, respectively.
 Orbital periods are all known precisely enough, so that the phase uncertainty at the last observed flare is of the order of $10^{-2}$.
@@
 \label{sec:results:phasedist}
-The Anderson-Darling test we use compares the measured distribution of orbital phases of the flares to the expected distribution, and return the significance of the deviation between the two.
-In the expected distribution, the same number of flares would be distributed randomly across the observing time.
+Our custom Anderson-Darling test compares the measured distribution of orbital phases of the flares to the expected distribution, and return the significance of the deviation between the two.
+In the expected distribution, the same number of flares would be distributed randomly across all phases, as the overwhelming majority of studies looking for variation with rotational phase suggest~\citep[e.g.]{doyle2018investigating,howard2021evryflare}.
 Figures~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv} show the flare phase distributions along with the corresponding expected distributions for transiting and non-transiting systems, respectively.
-The expected distributions usually deviate from a straight line because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different detection thresholds in each light curve.
+The expected distributions usually deviate from a straight line because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different flare rates in each light curve.
 
@@
     \begin{centering}
-        \includegraphics[width=.95\linewidth]{figures/PAPER_flares_phase_hist_transiting.png}
+        \includegraphics[width=\linewidth]{figures/PAPER_flares_phase_hist_transiting.png}
         \caption{
@@
     \begin{centering}
-        \includegraphics[width=0.95\linewidth]{figures/PAPER_flares_phase_hist_rv.png}
+        \includegraphics[width=\linewidth]{figures/PAPER_flares_phase_hist_rv.png}
         \caption{
-            Cumulative distributions of orbital phases of flares in the RV planet hosts observed by Kepler and TESS.
+            Cumulative distributions of orbital phases of flares in the non-transiting planet hosts observed by Kepler and TESS.
 The bisector line is dotted, the expected distribution is solid blue, and the observed distribution is solid black.
@@
 
-Table~\ref{tab:maintable_der} lists the $p$-value results for each star-planet system.
+Table~\ref{tab:maintable_der} lists the $p$-values for each star-planet system.
 We do not find any $>3\sigma$ signal of star-planet interaction in our sample.
-However, overall, the significance of the deviation increases with higher expected power of interaction.
+However, overall, the significance of the deviation increases with higher expected power of interaction, which is also listed for the four different powers $P$, calculated with the scaling laws introduced in Section~\ref{sec:methods:pspi} and normalized to AU Mic, along with the derived parameters for these scaling laws, i.e., Rossby number R$_o$, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{rel}$.
 
-Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with or without planetary magnetic field), there are two branches.
+Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with or without planetary magnetic field), there are two branches on the high end of expected powers.
 On one branch, the significance of the measured interaction is correlated with the expected power $P$.
 On the other branch, no interaction is measured regardless of the expected power $P$.
-
-Table~\ref{tab:maintable_der} lists the values for the four different powers $P$, calculated with the scaling laws introduced in Section~\ref{sec:methods:pspi} and normalized to AU Mic, along with the derived parameters for these scaling laws, i.e., Rossby number R$_o$, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{rel}$.
-
-\begin{table*}
-\movetableright=-20mm
-\footnotesize
-    \script{paper_main_table.py}
-    \caption{Flaring single star-planet system parameters.}
-    \input{output/table_lit_vals.tex}
-        \label{tab:maintable_lit}
-    \tablerefs{\input{output/lit_table_bibstring.tex}}
-\end{table*}
 
@@
 We therefore excluded some systems due to documented contamination from nearby (bound or co-moving) companions~(Section~\ref{sec:results:individualstars:excluded}).
-One exception to this rule is Kepler-411, a binary system for which the flare contributions from each component could be separated~(Section~\ref{sec:results:individualstars:kep411}).
+One exception to this rule is Kepler-411, a binary system for which the flare contributions from each component could be separated, but was excluded for other reasons~(Section~\ref{sec:results:individualstars:kep411}).
 We also dropped GJ 1061 from the sample because its rotation period was unconstrained.
@@
 While they appear in Table~\ref{tab:flares}, we excluded a number of systems from further analysis.
-We drop all multiple stars except for Proxima Cen (whose components are well separated both physically and on the sky), and all stars with nearby objects that contaminate our analysis, e.g., from ~\citet{ziegler2018measuring}: \input{output/multiples_string.tex}
+We drop all multiple stars except for Proxima Cen (whose components are well separated both physically, and on the sky), and all stars with nearby objects that contaminate our analysis, e.g., from Gaia DR2 and ground-based adaptive optics~\citep{ziegler2018measuring}: \input{output/multiples_string.tex}.
 
@@
 \label{sec:results:individualstars:kep411}
-Kepler-411 has 3 mag fainter companion~\cite{wang2014influence,ziegler2018measuring}, but we do not exclude it from the analysis.
+Kepler-411 has a 3 mag fainter companion~\citep{wang2014influence,ziegler2018measuring}, but we do not exclude it from the analysis initially.
 The system was observed in Kepler short cadence by \citet{jackman2021stellara} and both the planet host, and the companion star flare.
@@
 The fainter companion of Kepler-411 appears to cause the majority of flares (41), whereas the planet host causes only 7.
-Adopting the 7 flares from \cite{jackman2021stellara} in our analysis, we find that they all have equivalent duration $<1\,$s, which excludes Kepler-411 from further analysis.
+Adopting the 7 flares from \cite{jackman2021stellara} in our analysis, we find that they all have equivalent duration $ED<1\,$s, which excludes Kepler-411 from further analysis.
 

### 2023-05-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 On the one hand, a close-in planet that changes the star's rotation and activity makes it more difficult for us to model the system's evolution, as it affects fundamental stellar parameters.
-Inferring stellar age from rotation may be biased, if the star is spun up or spun down relative to stars without close-in companions~(XXXX).
+Inferring stellar age from rotation may be biased, if the star is spun up or spun down relative to stars without close-in companions~\citep{tejadaarevalo2021further, brown2014discrepancies, maxted2015comparison}.
 Analogously, altered activity levels may mimic an older or younger host than it actually is~\citep{ilic2022tidal}.
 
-On the other hand, understanding short-term, magnetic star-planet interactions -- the focus of this work -- holds promise to provide important insights into the habitability of the entire system~(XXXX).
-Planets involved in such interactions are in-situ probes of the system's space weather~(XXXX), and could prospectively reveal otherwise difficult to measure planetary properties such as the strength and extent of their magnetic field~\citep{cauley2019magnetic}.
+On the other hand, understanding short-term, magnetic star-planet interactions -- the focus of this work -- can provide important insights into the habitability of the entire system~\citep{shkolnik2018signatures}.
+Even if they orbit far inside the habitable, planets involved in such interactions are in-situ probes of the system's space weather and mass loss by revealing the extent of the Alfv\'en zone~\citep{kavanagh2021planetinduced, chebly2022destination}.
+Prospectively, planet-induced stellar activity could reveal otherwise difficult to measure planetary properties such as the strength and extent of their magnetic field~\citep{cauley2019magnetic}.
 
@@
 Measuring magnetic star planet-interaction is notoriously difficult in individual systems because a non-detection may not mean an absence of the interaction, but just a temporary cessation~\citep{shkolnik2005hot, shkolnik2008nature}.
-Statistical studies searching for changes in global chromospheric and coronal activity indicators in star-planet systems with close-in planets relative to planet-less stars are inconclusive~\citep{kashyap2008extrasolar,scharf2010possible, shkolnik2013ultraviolet, france2018farultraviolet, viswanath2020statistical, krejcova2012evidence, miller2015comprehensive}.
+Statistical studies searching for changes in global chromospheric and coronal activity indicators in star-planet systems with close-in planets relative to planet-less stars are inconclusive~\citep{kashyap2008extrasolar,scharf2010possible, shkolnik2013ultraviolet, france2018farultraviolet, viswanath2020statistical, krejcova2012evidence, miller2015comprehensive, poppenhaeger2010coronal}.
 In these studies, it is challenging both to define a control sample to measure the activity against, and to quantify how the way we detect planets introduces selection bias in the activity measure.
 It is, for instance, easier to detect a planet around a magnetically inactive star, because both radial velocity and transit detections will be less affected by stellar variability~\citep{poppenhaeger2011correlation}.
+Tidal interactions can also induce global increase in activity~\citep{ilic2022tidal}, which adds further ambiguity to the interpretation.
 
@@
 Flares are strong and impulsive eruptions released by reconnection and subsequent relaxation of field lines in the corona~\citep{svestka1976solar,priest2002magnetic}.
-In contrast to solar flares, stellar flares often are extremely energetic, sometimes enhancing the stellar flux by orders of magnitude~\citep{maehara2012superflares, shibayama2013superflares, paudel2018k2} so that they can be detected in stars up to hundreds of parsecs away~(XXXX).
+In contrast to solar flares, stellar flares often are extremely energetic, sometimes enhancing the stellar flux by orders of magnitude~\citep{maehara2012superflares, shibayama2013superflares, paudel2018k2} so that they can be detected in stars over 1kpc away~\citep{chang2015}.
 But since they occur randomly in time, individual events can be hard to catch.
@@
 \label{sec:intro:local}
-Phase correlated activity, flaring and otherwise, has been searched for in individual systems.
+Phase-correlated activity, flaring and otherwise, has been searched for in individual systems.
 After eight years of monitoring of HD 189733, an X-ray active Hot Jupiter host, the observed slight clustering of flaring in orbital phase remains tentative~\citep{pillitteri2022xray}.
-\citet{maggio2015coordinated} observed a flare-up in X-ray when the Jupiter-sized companion was in periastron on its highly eccentric orbit around its host HD 17156.
+\citet{maggio2015coordinated} observed an eruption of X-ray emissionwhen the Jupiter-sized companion was in periastron on its highly eccentric orbit around its host HD 17156.
 However, a similar study using chromospheric indicators in the eccentric system HD 80606 found no variation between periastron and apoastron~\citep{figueira2016activity}.
@@
 Realizing this, \citet{fischer2019timevariable} used K2 data with excellent phase coverage of the orbits of the inner TRAPPIST-1 planets to look for clustered flaring in phase, but found none.
-Similarly, in \citet{ilin2022searching}, we found hints of excess flaring in the TESS light curves of the young AU Mic system.
+\citet{ilin2022searching} and \citet{klein2022one} found hints of excess flaring, and chromospheric Helium emission in the young AU Mic system, respectively.
 This mixed picture of individual object studies calls for a more comprehensive and systematic approach.
@@
 We found and analyzed light curves for a total of 1811 systems, 344 of which were observed only by the primary Kepler mission, 1205 only by TESS, and 262 by both missions.
-We did not use K2 light curves because of the many systematics, and consequently the high costs of de-trending them.
+We did not use K2 light curves because of the many systematics, and consequently the high time investment of de-trending them.
 But we included the flare list obtained by~\citet{paudel2018k2} for TRAPPIST-1 K2 flares, since this system is a potential candidate for sub-Alfv\'enic interactions~\citep{fischer2019timevariable}.
@@
 \label{sec:methods:flaresearch}
-To remove trends and rotational variability from the light curve without losing the flare signal, we use an empirically derived multistep process.
+To remove trends and rotational variability from the light curve without losing the flare signal, we use an empirically derived multistep process, implemented as the \texttt{custom\_detrending} method in \texttt{AltaiPony}, a flare science package for light curve analysis~\citep{ilin2021altaipony}.
 First, we apply a spline fit with a coarse sampling of 30h-averaged values to capture slow rotation with periods above multiple days and non-periodic trends.
@@
 
-In the de-trended light curves, we search for flares as series of at least three consecutive data points $3\sigma$ above the noise level, implemented in AltaiPony~\cite{ilin2021altaipony}.
+In the de-trended light curves, we search for flares as series of at least three consecutive data points $3\sigma$ above the noise level using the \texttt{AltaiPony} method \texttt{find\_flares}.
 We estimate the noise level as the standard deviation in a rolling window of two hours, while masking deviation above $2.5\sigma$ (or $1.5$ sigma for active stars).
@@
         \caption{
-            Cumulative distributions of orbital phases of flares in the transiting planet hosts observed by Kepler and TESS.
+            Cumulative distributions of orbital phases of flares in the \textit{transiting} planet hosts observed by Kepler and TESS, sorted by number of flares from top to bottom.
 The bisector line is dotted, the expected distribution is solid blue, and the observed distribution is solid black.
@@
         \caption{
-            Cumulative distributions of orbital phases of flares in the non-transiting planet hosts observed by Kepler and TESS.
+            Cumulative distributions of orbital phases of flares in the \textit{non-transiting} planet hosts observed by Kepler and TESS, sorted by number of flares from top to bottom.
 The bisector line is dotted, the expected distribution is solid blue, and the observed distribution is solid black.
@@
 \label{sec:results:spi}
-We used the custom Anderson-Darling test introduced in  \citet{ilin2022searching} and Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three or more flares with equivalent duration $ED>1\,$s, detected in their Kepler and TESS observations.
+We used the custom Anderson-Darling test introduced in~\citet{ilin2022searching} and Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three or more flares with equivalent duration $ED>1\,$s, detected in their Kepler and TESS observations.
 We choose the $ED$ cutoff to make sure that we are comparing similar flares regardless of spectral type, that is, flares with the same energy relative to stellar luminosity.
@@
 Table~\ref{tab:maintable_der} lists the $p$-values for each star-planet system.
-We do not find any $>3\sigma$ signal of star-planet interaction in our sample.
+There is no star-planet system for which we find a $>3\sigma$ signal of star-planet interaction in our sample.
 However, overall, the significance of the deviation increases with higher expected power of interaction, which is also listed for the four different powers $P$, calculated with the scaling laws introduced in Section~\ref{sec:methods:pspi} and normalized to AU Mic, along with the derived parameters for these scaling laws, i.e., Rossby number R$_o$, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{rel}$.
@@
         \caption{
-            Expected power of SPI vs. AD test results, assuming four different scenarios, color-coded by stellar surface field strength.
+            Expected power of SPI vs.
+AD test results, assuming four different scenarios, color-coded by stellar surface field strength.
+Top row: Stretch-and-break scenario.
+Bottom row: Alfv\'en wing scenario.
+Left column: assuming $B_p=1\,$G.
+Right column: assuming $B_p=1\,$G.
+While the distribution of $p$-values is consistent with no interaction, all scenarios indicate lower $p$-values only for high expected powers of interaction.
         }
@@
 Recently, \citet{klein2022one} found tentative periodicity with the orbital period of AU Mic b in the chromospheric He I D line, which increases if the contribution from flares is included in the calculation.
-Overall, our marginal signal of flaring star-planet interaction in the AU Mic system supports the idea that this young, magnetically active M dwarf system with a close-in Neptune could exhibit planet=induced flaring.
+Overall, our marginal signal of flaring star-planet interaction in the AU Mic system supports the idea that this young, magnetically active M dwarf system with a close-in Neptune could exhibit planet-induced flaring.
 For a detailed discussion of AU Mic and its flaring star-planet interaction, we refer to~\cite{ilin2022searching}, where we also estimate that an additional 50–100 days of TESS-like monitoring of AU Mic would yield a $3\sigma$ detection if the marginal signal in our data is real.
 
-K2-25 is a multiplanet system around a fast rotating ($<2\,$d) mid-M dwarf in the Hyades open cluster, that is, 600-800 Myr old~\citep{stefansson2020habitable}.
+K2-25 is a multiplanet system around a fast rotating ($P_{rot}<2\,$d) mid-M dwarf in the Hyades open cluster, that is, 600-800 Myr old~\citep{stefansson2020habitable}.
 Both the expected power of interaction, and the measured deviation, are remarkably similar to the AU Mic system.
-Moreover, K2-25 b is in a presumably similar environment to GJ 436 b, but does not show the atmospheric escape in Ly$\alpha$ that the latter famously exhibits~\citep{rockcliffe2021lya}.
-This might at least in part be due to the stellar wind conditions around K2-25 b.
-Further investigation of magnetic star-planet interactions, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius.
-
-K2-25 is eccentric, see Eike Günther?
+Interestingly, K2-25 b is in a presumably similar environment to GJ 436 b, but does not show the atmospheric escape in Ly$\alpha$ that the latter famously exhibits~\citep{rockcliffe2021lya}.
+This might in part be due to the stellar wind conditions around K2-25 b.
+Further investigation of magnetic star-planet interactions, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius, especially accounting for its moderately high eccentricity~(see also Section~\ref{sec:discussion:eccentricity}).
 
@@
 Compared to the other two systems, its innermost planet is not a Neptune, but a rocky planet slightly smaller than Earth~\citep{ment2021toi}.
-It is a relatively smaller obstacle in the host's magnetic field, yet the interaction is expected to be of a similar magnitude due to the strongest inferred magnetic field and closest orbit among the three systems.
+It is a relatively smaller obstacle in the host's magnetic field, yet the interaction is expected to be of a similar magnitude due to the strongest inferred magnetic field, and closest orbit among the three systems.
 
-In the scenario wherein the stretch-and-break mechanism drives the interaction, the three system cluster together most distinctly.
-In this scenario, all systems that do not show elevated interaction, have a weaker magnetic field below $2000\,$G~(top row in Figure\ref{fig:adtest_bp}).
-In the Alfv\'en wing scenario~(bottom row in Figure\ref{fig:adtest_bp}), the distinction is less clear, and systems with strong fields and similar expected power of interaction do not show any excess flaring.
-In both cases, the absence of interaction could be due to the Alfv\'en radius being within the planetary orbit (note that the scaling laws assume that the planet is sub-Alfv\'enic, but make no statement about it).
+In the scenario wherein the stretch-and-break mechanism drives the interaction, the three systems cluster together most distinctly~(top row in Figure~\ref{fig:adtest_bp}).
+In the Alfv\'en wing scenario~(bottom row in Figure~\ref{fig:adtest_bp}), the distinction is less clear, and systems with strong fields and similar expected power of interaction do not show any excess flaring.
+In both cases, the absence of interaction could be due to the Alfv\'en radius being within the planetary orbit.
+It is important to note that the scaling laws assume that the planet is sub-Alfv\'enic, but make no statement about it, because the mass loss of these stars is largely unconstrained.
 All else equal, this is more likely if the stellar magnetic field strength is weaker.
-Another explanation is the possible intermittency, or 'on-off nature' of the interaction~\citep{shkolnik2008nature}, which may be at play here, but particularly in cases where the expected power is very strong, such as in the comparison between HIP 67522 and TAP 26 that we address in the following Section.
+Another explanation is the possible intermittency, or 'on-off nature' of the interaction~\citep{shkolnik2008nature}, which may be at play here, but particularly in cases where the expected power is very strong, such as in the comparison between HIP 67522 and TAP 26 that we address in the following two Sections.
 
@@
 These flares are distributed across two Sectors in TESS.
-In Sector 11, two flares occur at orbital phases $\sim 0.6$ and $\sim 0.8$.
+In Sector 11, two flares occur at orbital phases $\sim 0.61$ and $\sim 0.81$.
 Two years later, in Sector 38, four flares occur, but this time, all of them take place at orbital phases $0.00-0.05$, that is, up to a few hours after transit.
@@
 It is a Sco-Cen member (10-20 Myr old), which was discovered to host a close-in Jupiter, HIP 67522 b, in 2020~\citep{rizzuto2020tess}.
-Curiously, the planet is in close spin-orbit commensurability -- $P_{rot}/P_{orb}=5/1$, closer than any other system in our sample.
+Curiously, the planet is in close spin-orbit commensurability -- $P_{rot}/P_{orb}=5/1$.
 Therefore, we cannot completely rule out that the observed periodicity is in fact a rotational periodicity, and not related to the planet.
-However, if we calculate the $p$-value of AD test using the rotational period instead of the orbital period, we find HIP 67522 consistent with uniform flaring in time within $1\sigma$.
-Fortunately, HIP 67522 will be observed again with TESS in April 2023, which may resolve the puzzle.
+However, if we calculate the $p$-value of the AD test using the rotational period instead of the orbital period, we find HIP 67522 consistent with uniform flaring in time within $1\sigma$, which is likely due to the not sufficiently low uncertainty in rotation period.% Fortunately, HIP 67522 will be observed again with TESS in April 2023, which may resolve the puzzle.
 
@@
 \citet{lanza2018closeby} estimate that the system can release more energy in magnetic star-planet interaction than other  systems with Hot Jupiters, such as HD 179949, that has previously been detected with chromospheric variability in phase with the planet's orbit~\citep{shkolnik2008nature}.
-However, for TAP 26 b, the orbital period might is not well-constrained.
+However, for TAP 26 b, the orbital period might not be well-constrained.
 \citet{yu2017hot} apply several methods to derive $P_{orb}$ from the radial velocity data: While the $10.8\,$d orbit we adopted is the most likely according to \citet{yu2017hot}, a $9.0\,$d orbit is also likely, and some of their applied methods favored a $13.4\,$d period.
@@
 \label{sec:results:individualstars:koi12}
-KOI-12, also known as Kepler-448, is a young two-planet system with an eccentric outer planet KOI-12 c, and an inner Hot Jupiter planet KOI-12 b in a $17.8\,$d orbit~\citep{masuda2017eccentric}.
-With respect to rotation rate, stellar and planetary radius, the KOI-12/KOI-12 b system is similar to HIP~67522 and TAP~26 (although for the those young stars the radii are large because the stars are still contracting onto the main sequence).
+KOI-12, also known as Kepler-448, is a two-planet system with an eccentric outer planet KOI-12 c, and an inner Warm Jupiter planet KOI-12 b in a $17.8\,$d orbit~\citep{masuda2017eccentric}.
+With respect to rotation rate, stellar and planetary radius, the KOI-12 system is similar to HIP~67522 and TAP~26 (although for the those young stars the radii are large because the stars are still contracting onto the main sequence).
+In constrast, KOI-12 is $1.4\pm0.3\,$Gyr old~\citep{bourrier2015sophie}, an F5 subgiant~\citep{frasca2016activity}, which is already evolving off the main sequence.
 Yet, despite its high expected power of interaction, we detect no excess flaring in phase with KOI-12 b.
@@
 In Section~\ref{sec:discussion:viewing}, we suggest that the absence of interaction at high expected power could be due to unfavorable viewing geometry of the system, e.g., a face-on orbital plane.
-In Section~\ref{sec:discussion:misalignment}, we discuss whether (mis-)alignment between spin, orbit and magnetic dipole can increase or decrease the chances of flaring star-planet interaction.
 In Section~\ref{sec:discussion:commensurability}, we note that systems on the inactive branch are further away from spin-orbit commensurability than stars on the active branch.
-This leads us to conjecture a possible influence of tidal interactions on the occurrence of orbital phase correlated flaring.
-We conclude our discussion by following this line of reasoning, and consider ways to disentangle tidal from magnetic interactions~(Section~\ref{sec:discussion:tidalmagnetic}).
+This leads us to conjecture a possible link between spin-orbit resonance and flaring SPI.
 
@@
 If the planetary orbit is highly eccentric, the difference between periastron and apoastron can be significantly larger than the variability of the Alfv\'en radius.
-If then apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, namely during the planet's rapid periastron passage.
-This was previously exploited in the case of HD 189733~(XXXX), and also for binary interaction in the V 773 Tau system~(XXXX).
+If then the apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, during the planet's rapid periastron passage.
+This was previously exploited in the case of HD 17156~\citep{maggio2015coordinated}, and analogously for the colliding magnetospheres in binary systems~\citep{massi2002periodic,getman2016search}.
 In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e\leq 0.35$.
-The exception is K2-25, with a relative high $e=0.45$, which may contribute to the increased contrast of excess flares.
-All else equal, closer proximity increases the strength of interaction.
-Perhaps, K2-25 even moves in and out of the sub-Alfv\'enic zone between periastron and apoastron, turning interaction on and off every single orbit.
-If periastron passage occurs when the planet is in front of the star relative to the observer, the visibility effect of the interaction footpoint moving in and out of view as the planet orbits is further enhanced by the narrow phase range of the periastron passage.
+The exception is K2-25, with a relatively high $e=0.45$.
+If periastron passage in K2-25 occurs when the planet is in front of the star relative to the observer, the visibility effect of the interaction footpoint moving in and out of view as the planet orbits is further increased by the narrow phase range of the periastron passage.
+\citet{stefansson2020habitable} estimated the argument of periastron $\omega=120^{+12}_{-14}\,$deg for K2-25 (with longitude of the ascending node chosen such that $\omega$ is the same as the longitude of periastron, with $\omega=90\,$deg being periastron passage during transit,~\citealt{kipping2010investigations,dawson2012photoeccentric}).
+We can therefore conjecture that the tentative signal of flaring SPI in K2-25 is enhanced by eccentricity.
 
@@
 
-Even for the few stars, for which the rotational period is known precisely enough~(see Fig.~\ref{fig:coherence_hist}) for our analysis, we need to make a large number of assumptions.
+Even for the few stars, for which the rotational period is known precisely enough~(see Fig.~\ref{fig:coherence_hist}) for our analysis, we need to make numerous assumptions.
 These include the number of active regions crossed by the footpoint of interaction, differential rotation, spot evolution, and a significant correlation between the location of the planet and the location of the planet-induced flare on the stellar surface.
@@
 The latter is much more stable over long periods of time than the intrinsically dynamic magnetic field configuration.
+\textcolor{red}{add some references}
 
@@
 Even if differential rotation was absent and active regions were extremely stable, we will not be able to observe the passage of the sub-planetary point over the flare-prone region every synodic period.
-If the planet's rotational axis is inclined, then the passage will regularly occur on the back of the star relative to the observer.
+If the planet's rotational axis inclination is high, then the passage will regularly occur on the back of the star relative to the observer.
 The true period will therefore be additionally modulated by the visibility, resulting in an intermittency of the signal.
@@
     \item the Alfv\'en radius moving in- and outside the planet's orbit, either over the course of an activity cycle, or through short-term variations in the magnetic field and wind properties caused by, e.g., coronal mass ejections;
-    \item visibility of the interacting footpoint changing as the magnetic field evolves;
-    \item the active latitude moving away from the magnetic footpoints passageway; or
+    \item visibility of the interacting footpoint changing as the magnetic field evolves (more visibility is less modulation with orbital period);
+    \item an active latitude moving away from the magnetic footpoints passageway; or
     \item the available magnetic energy decreasing such that the flares or other magnetic interaction indicators still occur but fall below the detection threshold for a period of time.
@@
 
-If the magnetic field of the planet changes or disappears as well, this might also reduce the intensity of interaction below the detection threshold.
+If the magnetic field of the planet also changes over time, this might modulate the intensity as well~[e.g.]\citep{turnpenney2018exoplanetinduced}.
 
@@
 Yet intermittency cannot be ruled out.
-The case HIP~67522 may be more informative.
+The case of HIP~67522 may be more informative.
 In our data, we combine the observation from two TESS Sectors that are almost 2 years apart.
@@
 \label{sec:discussion:viewing}
+\textcolor{red}{needs to be contrasted more with intermittency}
 The visibility of the magnetic interaction footpoint is crucial for the detection of flaring star-planet interactions in our analysis.
@@
 In that case, assuming the dipole field dominates at the distance of the planet, the footpoint will be close to the pole, similar to the hot spot created by Io and the other moons in the polar cap of Jupiter.
-In this scenario, many non-transiting systems may experience flaring star-planet interaction, but those would not show up as correlation of flare timing with the orbital phase in our data.
+In this scenario, many, especially non-transiting, systems may experience flaring star-planet interaction, but those would not show up as correlation of flare timing with the orbital phase in our data.
 
-Most of our systems are transiting, and for those we can expect this scenario to be a minor problem.
-Of the systems that have high expected power but do not show any, only TAP 26 is a planet detected in radial velocity, and is expected to have a relatively high orbital inclination of about $55\pm10$ deg inferred from Zeeman Doppler measurements~\citep{yu2017hot}.
+Most of our systems are transiting, and for those we can expect this scenario to be a minor problem unless the latitude of the footpoint is very high.
+Of the systems that have high expected power but do not show any, only TAP 26 b is a planet detected in radial velocity, and has a relatively high orbital inclination of about $55\pm10$ deg inferred from Zeeman Doppler measurements~\citep{yu2017hot}.
 The ZD map reveals magnetic field concentrations close to the rotational pole, and the brightness maps also show a dark spot in the same location.
 If the orbital plane is aligned with the stellar rotation axis, the absence of phase-correlated flaring in TAP 26 could be explained by the footpoint of interaction being always in view and therefore never modulated.
+Note that alignment between orbital, rotational and magnetic dipole axis is not generally given, with many pole-on orbiting planets~(XXXX), and stars with heavily mislaligned magnetic axes~(XXXX).
+So interpreting non-detections as effects of viewing geometry comes with a caveat.
 
@@
 In Fig.~\ref{fig:spinorbit}, we split our sample into three categories.
-The first contains the systems where the expected interaction is lower than that in TOI-540.
+The first contains the systems where the expected interaction is lower than that in TOI-540, the system with the lowest power of interaction among those with relatively high flaring star-planet interaction signal (i.e., K2-25, TOI-540, HIP 67522, and AU Mic).
 The second includes the systems where a high power of interaction is expected, but none is measured (e.g., TAP 26, KOI-12).
-The final third category contains all system where the data suggest a correlation between expected power of interaction and measured flaring star-planet interaction signal (i.e., K2-25, TOI-540, HIP 67522, and AU Mic).
+The final third category contains all system where the data suggest a correlation between expected power of interaction, but do not belong in the first category.
 We search for spin-orbit commensurability with integers $<10$ in each system, and plot the relative difference between the closest ratio and the actual spin-orbit ratio.
-Systems with low expected power of interaction span both very close spin-orbit commensurability to none.
+Systems with low expected power of interaction span a wide range of spin-orbit commensurability.
 However, the second and third group form two separate populations.
 Non-interacting systems are further away from low-integer commensurability, than interacting ones, even though both have high expected power.
+A similar picture arises when the same sample split is applied to the other interaction scenarios.
 
@@
 In those systems, the same surface feature is passed by the sub-planetary point at the same orbital phase every $m \cdot n$ orbits, if $m>n$ (which is true for all our systems with high expected power of interaction).
-For HIP 67522, the interaction signal may therefore be more strongly confined to certain orbital phases, while for systems with less and less commensurability, this effect dilutes.
+For HIP 67522, the interaction signal may therefore be more strongly confined to certain orbital phases, while for systems with higher order commensurability, this effect dilutes.
 
@@
 These oscillations can lead to a surface pattern of emerging magnetic field that rotates with the spin-orbit commensurable period.
-This can explain the clearer interaction signal in the systems with spin-orbit resonance, because it would stabilize the pattern of regions with strong magnetic field that favor planet-induced flaring, and thereby counterbalance the diluting effect of differential rotation.
-This model requires tidal interaction, which may be too weak in systems like AU Mic, where the planet is too small and distant for the proposed effect~\citet{lanza2022model}, but that still show spin-orbit commensurability and signs of flaring star-planet interaction.
+Systems with spin-orbit resonance would then show clearer interaction signal, because the resonance would stabilize the pattern of regions with strong magnetic field that favor planet-induced flaring.
+The stable active regions might withstand the diluting effect of differential rotation~(see Section~\ref{sec:discussion:rotsyn}).
+However, the \citet{lanza2022model} requires tidal interaction, which may be too weak in systems like AU Mic, where the planet is too small and distant for the proposed effect, but that still show spin-orbit commensurability and signs of flaring star-planet interaction.
 
 While in~\citet{lanza2022model}, resonant oscillations favor flaring star-planet interaction observability, there might also be physical effects where the magnetic torque causes the spin-orbit resonance in the first place.
-The connection here is: Where there is strong enough magnetic torque to cause spin-orbit resonance, there would also be flaring star-planet interaction.
+The connection here is: In regions where there is strong enough magnetic torque that causes spin-orbit resonance, there would also be flaring star-planet interaction.
 
 \citet{szabo2021changing} conjecture that many systems within the sparsely populated region of close-in planets around rapid rotators~\citep{mcquillan2013stellar} seem close to low-integer spin-orbit resonance.
-The systems with consistently high expected power of interaction (TAP 26, TOI-540, KOI-12, HIP 67522, K2-25, and AU Mic) are all found within that region, even if KOI-12 and AU Mic lie rather close to its edge.
-Of these six systems, those that show signs of star-planet interaction, are also in close-spin orbit resonance.
-We may speculate, that at least some of the mechanisms that explain the dearth of close-in planets around rapidly rotating stars also explain the presence of star-planet magnetic interaction in those systems that are still found there.
-One may think that planets that remain in the desert are held there by being trapped in the resonance, while for the others, the magnetic torque causes rapid evolution out of this region through spin-down of the star throug both magnetic braking and star-planet interaction, and the planet's migration to higher orbital periods through the latter mechanism.
+However, proximity to spin-orbit resonance is sensitive to the highest integer included in the calculation.
+If we choose the maximum low integer for m or n to be smaller than 10 the pattern in Fig.~\ref{fig:spinorbit} disappears.
+If we choose it to be larger than 10, XXXX.
 
@@
         \caption{
-           Spin-orbit commensurability compared to flaring star-planet interaction signal.
+           \textbf{Top panel}: Same as the bottom left panel in Fig.~\ref{fig:adtest_bp}, but color coded as below.
+\textbf{Bottom panel:} Spin-orbit commensurability compared to flaring star-planet interaction signal.
 The lower the p-value of the AD test, the stronger the interaction signal.
@@
 
+\subsection{Tidal interaction}
+\begin{figure*}[t]
+    \script{paper_tidal_interaction.py}
+    \begin{centering}
+        \includegraphics[width=\hsize]{figures/PAPER_tidal_AD_test.png}
+        \caption{
+           \textbf{Left panel}: Blue color indicates that the star rotates slower than the planet orbits, so that angular momentum is transferred from the orbit to the spin of the star.
+Grey color is the reverse.
+\textbf{Middle panel}: \textbf{Right panel}:
+        }
+        \label{fig:tidal}
+    \end{centering}
+\end{figure*}
+
+Tidal interaction can also lead to enhanced activity, globally, and locally.
+Locally, we expect to see periodicity with half the orbital period of the planet, corresponding to the two tidal bulges forming in the stellar envelope.
+
+We cannot tell whether an additional individual flare is produced by tidal or magnetic interaction, but as with magnetic interaction, we can look for deviations from a random distribution of flare times in phase with the relevant period.
+In this case, the relevant period is $P_{orb}/2$.
+
+We applied the same technique as described in Section~\ref{sec:methods:adtest} to determine the significance of a local tidal SPI signal.
+Following~\citet{ilic2022tidal}, we compare the resulting $p$-values with three different models of tidal interaction in Fig.~\ref{fig:tidal} and list the derived values in Table~(XXXX).
+The first model measures the torque $\partial L / \partial t$, exerted by angular momentum transfer from star to planet or from planet to star~(\citealt{penev2012constraining}, their Eqns.
+1 and 2).
+We choose the tidal quality factor $Q_*=10^7$, but our results do not depend on the choice of $Q_*$.
+We also make the simplifying assumption that the rotation period of the convective envelope is the same as the surface rotation period measured as described in Section~\ref{sec:data:rotationperiods}, ignoring differential rotation effects.
+\textcolor{red}{Why doesn't the torque depend on the stellar rotation velocity, except for the sign of interaction?}.
+The second model considers the tidal dissipation timescale -- the shorter the timescale, the higher the power of the interaction~\citep{albrecht2012obliquities}.
+The third model uses the gravitational perturbation as a proxy for the interaction~\citep{cuntz2000stellar}.
+
+We find that no single system shows significant signs of tidal star-planet interaction.
+Overall, the signal in phase with $P_{orb}/2$ is smaller than with $P_{orb}$.
+However, in all three scenarios, the deviation from random flare timing increases with expected tidal interaction strength.
+
+Among the systems, HIP 67522 appears with tentative signs of both tidal and magnetic interaction (measured and expected in the different scenarios).
+KOI-12, which lacks signal with $P_{orb}$ despite high expected power of magnetic interaction, shows more consistency between expected and measured tidal interaction.
+This could be interpreted as KOI-12 b orbiting outside the ALfv\'en radius, unable to interact magnetically, but tidally.
+We note that KOI may be evolving off the main sequence, so that the tidal interaction estimates might not be accurate for this star.
+Finally, Kepler-42 is neither expected to interact magnetically, nor did it show any deviation from random flare timing in phase with $P_{orb}$.
+However, since it is the system with the shortest planetary orbit in our sample, it is both expected to and does show marginal signal of tidal interaction.
+Kepler-42 is very similar to TOI-540, which also is a small M dwarf with a likely terrestrial planet in a very short orbit.
+The key difference may be that Kepler-42 is rotating at about 70 days, and therefore expected to have a relatively weak magnetic field, whereas TOI-540 is a young star with a rotation period $<1\,$d.
+TOI-540 is expected to have lower tidal interaction strength than Kepler-42 due to TOI-540 b's wider orbit, and also shows a weaker tidal SPI signal in all three scenarios.
+
+The results here, as with magnetic SPI, are suggestive, as they are consistent with theoretical expectation, albeit at low significance.
+Further observations, underway with TESS and soon PLATO, may confirm or reject the trends seen for both types of interaction.
+As multiple observations can be combined regardless of the gaps in time between individual campaigns with our method, we will become able to sensitively constrain the magnitude of interaction, and the relative contributions from tidal and magnetic SPI.
+
 \section{Summary and Conclusions}
@@
 We have conducted the so far largest search for flaring star-planet interactions.
-Using over 7000 Quarters and Sectors of photometric monitoring from Kepler and TESS archives, we found searched for flares in over 1800 systems of the over 3000 listed in the NASA Exoplanet Archive.
-In those systems that were single stars, where flares could be unambiguously attributed to the planet host, and showed three or more energetic events in the data, we searched for flares that clustered in orbital phase.
+Using over 7200 Quarters and Sectors of photometric monitoring from Kepler and TESS archives, we searched for flares in over 1800 systems of the about 3000 listed in the NASA Exoplanet Archive.
+In the single star systems, where flares could be unambiguously attributed to the planet host, and showed three or more energetic events in the data, we searched for flares that clustered in orbital phase.
 Our final sample consisted of 26 systems, among them well-known flaring hosts like Proxima Cen, AU Mic, and TRAPPIST-1.
 
-Applying both the stretch-and-break and Alfv\'en wing mechanisms discussed for magnetic interaction, we found evidence for a correlation between the expected power of interaction, and the presence of excess flaring in phase with the orbital period.
+Applying both the stretch-and-break and Alfv\'en wing mechanisms discussed for magnetic interaction, we found tentative evidence for a correlation between the expected power of interaction, and the presence of excess flaring in phase with the orbital period.
 In particular, we found that there may be two branches at high expected power -- one where the measured excess flaring is correlated with the expected power, and one where this is not the case.
-This may be an effect of intermittency in the interaction, but viewing geometry may also play a major role, and orbital eccentricity a minor one.
+This may be an effect of the extent of the Alfv\'en surface, the intermittency in the interaction, or of the viewing geometry of the systems.
 
@@
 
-Our study is the first that systematically searched for flaring star-planet interactions, and is not limited by sampling biases in the way earlier ensemble based searches for this effect have been~(XXXX).
-While our results remain tentative due to the small final sample, future studies using our technique will accumulate more and more data.
-The TESS mission continues to produce high precision light curves for many nearby active planet hosts, and the PLATO mission will join in late 2026.
+Our study is the first that systematically searched for flaring star-planet interactions, and is not limited by sampling or selection bias in the way earlier studies of this effect have been~(XXXX).
+While our results remain tentative, future studies using our technique will benefit from accumulating data.
+The TESS mission continues to produce high precision light curves for many nearby active planet hosts, and the PLATO~\citep{rauer2014plato} mission will join in late 2026.
 For AU Mic, we may be only a few TESS Sectors away from a $3\sigma$ level confirmation~\citep{ilin2022searching} of the tentative interaction signal observed here and in other work~\citep{klein2022one}.
@@
 
-Close-in planets around young, active stars are being explored as in-situ probes of the dynamic magnetic~(XXXX), and stellar mass loss~\citep{vidotto2017exoplanets} conditions in their orbit.
-Together, mass loss and magnetism form two key components of the space weather that a potentially habitable planet will encounter.
-The orbits where sub-Alfv\'enic interaction, of the kind we searched for in this work, can take place are usually closer to the star than its habitable zone.
-However, in late M dwarfs like TRAPPIST-1, these two regions overlap~\citep{strugarek2021physics}, and information from closer in is still crucial (or else why would we send probes to the Sun?).
+Close-in planets around young, active stars are being explored as in-situ probes of the dynamic magnetic field~(XXXX), and stellar mass loss~\citep{vidotto2017exoplanets} conditions in their orbit.
+They are two key components of the space weather that a potentially habitable planet will encounter.
+The orbital distances where sub-Alfv\'enic interaction can take place, are usually closer to the star than its habitable zone.
+However, in late M dwarfs like TRAPPIST-1, these two regions overlap~\citep{strugarek2021physics}, and information from closer in for earlier spectral types is still crucial (or else why would we send probes to the Sun?).
 We only begin to uncover the invaluable information that close-in planets can provide about the ever-changing environment of habitable-zone terrestrial planets.
@@
 Proxima Cen b has an eccentricity upper limit of 0.35~\cite{anglada-escude2016terrestrial}.
-\subsection{TAP 26}
-Likely low eccentricity given in \cite{yu2017hot}.
-
-\subsection{Kepler-42}
- KOI-961 in the detection paper \cite{muirhead2012characterizing}, low eccentricity constrained by \cite{mann2017gold}
 

### 2023-05-08 src/scripts/paper_cumdist_individual_rv.py
added spin-orbit plots for other scenarios, added tidal interaction plot

@@ -53,7 +53,7 @@ if __name__ == "__main__":
     for tic in tics:
 
         # print(g.shape)
-        g = flares[flares.TIC.astype(str) == tic]
+        g = flares[(flares.TIC.astype(str) == tic)]
         print(tic, g.shape, len(ax))
         # pick only stars with more than 0 flares
         if ((g.shape[0]>3) & (len(ax)>0)):

### 2023-05-08 src/scripts/paper_spin_orbit_commensurability.py

@@ -116,90 +116,99 @@ if __name__ == "__main__":
 
     # Color-code the points
 
-    # baseline color coding
-    df["color"] = "blue"
-    df["marker"] = "o"
+
+    power_names = ["p_spi_sb_bp1_norm", "p_spi_sb_bp0_norm", 
+                   "p_spi_aw_bp1_norm", "p_spi_aw_bp0_norm"]
 
 
-    # label all that are expected with higher power than TOI-540 but SPI off
-    toi540 = df.loc[df.ID=="TOI-540","p_spi_sb_bp1_norm"].values[0]
-    cond = ((df["p_spi_sb_bp1_norm"]>toi540) & (df["mean"]>.3))
-    df.loc[cond, "color"] = "red"
-    df.loc[cond, "marker"] = "X"
+    for power_name in power_names:
 
-    # label all that are expected with higher power than TOI-540 and SPI on
-    cond = df["mean"] < .2
-    df.loc[cond, "color"] = "k"
-    df.loc[cond, "marker"] = "d"
+        # baseline color coding
+        df["color"] = "blue"
+        df["marker"] = "o"
 
 
-    # Make plot
-    fig, (ax2, ax1) = plt.subplots(nrows=2, ncols=1, figsize=(8,10.5))
+        # label all that are expected with higher power than lowest for low p-values
+        #  but SPI off
+        cutoff = df.loc[df["mean"] < 0.2 , power_name].min()
+        cond = ((df[power_name]>cutoff) & (df["mean"]>.2))
+        df.loc[cond, "color"] = "red"
+        df.loc[cond, "marker"] = "X"
 
-    # plot each group
-    for marker, group in df.groupby("marker"):
-        ax1.scatter(group["ratio_error"], group["mean"],
-                    color=group["color"], alpha=1., marker=marker, s=60)
-
-    # annotate points with high expected power and SPI on
-    for i, row in df.iterrows():
-        if (row["mean"] < 2e-1):
-            ax1.annotate(f"{row.ID} ({row.closest_ratio_den}:{row.closest_ratio_num})",
-                        (row.ratio_error*1.1, row["mean"]*.95))
-
-    # label axes
-    ax1.set_xlabel("relative difference to closest spin-orbit commensurable ratio",
-               fontsize=14)
-    ax1.set_ylabel(r"$p$-value of AD test",
-               fontsize=14)
-
-    # set log scale
-    ax1.set_xscale("log")
[…]

### 2023-05-08 src/scripts/paper_tidal_interaction.py

@@ -1,0 +1,88 @@
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import paths
+
+
+from adjustText import adjust_text
+
+def get_sigma_values():
+    """Define the sigma values."""
+
+    # define sigma values
+    onesigma = 1 - .342*2
+    twosigma = 1 - .342*2 - .136*2
+    threesigma = 1 - .342*2 - .136*2 - .021*2
+    
+    # put them in a list
+    sigmas = [onesigma, twosigma, threesigma]
+    sigma_label = [r"$1\sigma$", r"$2\sigma$", r"$3\sigma$"]
+
+    return sigmas, sigma_label
+
+
+if __name__ == "__main__":
+
+
+    # read the tidal interaction strength table with the AD test results
+    res = pd.read_csv(paths.data / "TIS_with_ADtests.csv", index_col=0)
+
+    # blue when convective envelope is spinning faster, and transferring angular momentum to the planet
+    res["color_conv"] = ["blue" if np.sign(torque)==1 else "grey" for torque in res["torque_conv"].values]
+    res["torque_conv"] = res["torque_conv"].abs()
+
+    # initialize the figure
+    fig, axes = plt.subplots(1,3, figsize=(15,5), sharey=True)
+    axes = list(axes) 
+
+    # define the models and labels
+    models = ["grav_pert", "tidal_disip_timescale", "torque_conv"]
+    labels = [r"gravitational perturbation $\Delta g / g$",
+            r"tidal dissipation timescale $\tau_{\rm tide}$ [yr]",
+            r"tidal torque $\partial L_{conv}/\partial t$ $\left[M_\odot \left(\frac{km}{s}\right)^2\right]$"]
+
+    # define shared axis label
+    axes[0].set_ylabel("p-value of AD test", fontsize=12)
+
+    # loop over the models
+    for model, label in zip(models, labels):
+
+        # pick an axis
+        ax = axes.pop()
+        
+        # plot the data
+        # torque conv is the model, use appropriate color, otherwise grey
+        if model == "torque_conv":
+            ax.scatter(res[model],res["mean"], label=model, 
+                       color=res["color_conv"], marker="x", s=50)
+        else:
+            ax.scatter(res[model],res["mean"], label=model, 
+                       color="grey", marker="x", s=50)
+
+        # add the ID of the systems with low p-values
+        texts = []
[…]

### 2023-05-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/PAPER_spin_orbit_commensurable.png}
+        \includegraphics[width=\linewidth]{figures/PAPER_spin_orbit_commensurable_p_spi_sb_bp1_norm.png}
         \caption{
@@
 Among the systems, HIP 67522 appears with tentative signs of both tidal and magnetic interaction (measured and expected in the different scenarios).
-KOI-12, which lacks signal with $P_{orb}$ despite high expected power of magnetic interaction, shows more consistency between expected and measured tidal interaction.
-This could be interpreted as KOI-12 b orbiting outside the ALfv\'en radius, unable to interact magnetically, but tidally.
+KOI-12, which lacks signal with $P_{orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction.
+This could be interpreted as KOI-12 b orbiting outside the Alfv\'en radius, unable to interact magnetically, but tidally.
 We note that KOI may be evolving off the main sequence, so that the tidal interaction estimates might not be accurate for this star.

### 2023-05-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Most systems are neither expected to interact, nor do they show excess flaring.
-Among those systems that have high expected power of interaction, we see two branches.
+Among those systems that have high expected power of magnetic interaction, we see two branches.
 An inactive one, where no signs of excess flaring appear regardless of favorable conditions, and an active one where expected power and excess flaring are correlated.
-While this trend is tentative, we also found that the two branches form two distinct populations in spin-orbit commensurability.
-The active branch is closer to low-integer ratios between rotational and orbital period than the inactive branch.
-While viewing geometry and intermittency of interaction remain possible explanations, spin-orbit resonances hint at a physical link worth exploring to better understand the underlying mechanisms of star-planet interactions.
+While this trend is tentative, it is consistent across all investigated models for magnetic interaction.
+Finally, we searched for signs of tidal interaction, that is, excess flaring in phase with the tidal bulges ($P_{orb}/2$), and found a similar trend with different expected powers of tidal interaction.
+Our results support the view that young systems with close in planets are likely to interact both tidally and magnetically, whereas star-planet interactions in old, slowly rotating systems lack the extended magnetosphere, and interact predominantly tidally.
     %magnetic field strength (using $Ro$-$B$ relations), orbital parameters, and planet radius.
@@
 We cannot tell whether an additional individual flare is produced by tidal or magnetic interaction, but as with magnetic interaction, we can look for deviations from a random distribution of flare times in phase with the relevant period.
-In this case, the relevant period is $P_{orb}/2$.
+In the case of tidal interactions, the relevant period is $P_{orb}/2$.
 
@@
 \textcolor{red}{Why doesn't the torque depend on the stellar rotation velocity, except for the sign of interaction?}.
-The second model considers the tidal dissipation timescale -- the shorter the timescale, the higher the power of the interaction~\citep{albrecht2012obliquities}.
+The second model considers the tidal dissipation timescale -- the shorter the timescale, the higher the power of the interaction~\citep{zahn1977tidal}.
+Following~\citet{ilic2022tidal}, we adopt Eqn.2 from~\citep{albrecht2012obliquities} for the tidal dissipation timescale in the convective envelope.
+We assume that all stars in our sample have a convective envelope because they flare, and flaring requires a dynamo-generated magnetic field, which can only operate in stars with convective envelopes.
+Most of our stars are clearly below the Kraft break at spectral type F5~(XXXX), above which stars have a radiative envelope, except for KOI-12, which is an F5 sub-giant~\citep{frasca2016activity}.
 The third model uses the gravitational perturbation as a proxy for the interaction~\citep{cuntz2000stellar}.
+All models require the planetary and stellar mass to be known, which we collect from the literature.
+For missing planetary masses, radii are known, so we can use the mass-radius relations in~\citet{chen2017probabilistic}.
+We list the masses in Table~(XXXX).
 
@@
 However, in all three scenarios, the deviation from random flare timing increases with expected tidal interaction strength.
+We can now compare the magnetic interaction measurements to the tidal ones in some of the conspicuous systems:
 
 Among the systems, HIP 67522 appears with tentative signs of both tidal and magnetic interaction (measured and expected in the different scenarios).
+On the one hand, since the flares in HIP 67522 mostly appear close to the transit phase, and not during eclipse, this may favor magnetic interaction, and the tidal signal would only be an artifact.
+On the other hand, the narrow range in which most of the flares on HIP 67522 occurred favor a well-located tidal bulge.
+It is conceivable that both effects play a role at the same time.
+
 KOI-12, which lacks signal with $P_{orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction.
@@
 We note that KOI may be evolving off the main sequence, so that the tidal interaction estimates might not be accurate for this star.
-Finally, Kepler-42 is neither expected to interact magnetically, nor did it show any deviation from random flare timing in phase with $P_{orb}$.
+TAP 26, which shows no signs of magnetic SPI, does not show any sign of tidal interaction despite both being high as expected from models.
+This could again be due to the inclination of TAP 26's orbit, but only if the flares caused by the tidal bulge are not too close to the equator.
+In that case, TAP 26's tidally induced flares should be more modulated than the magnetically induced ones.
+
+Kepler-42 is neither expected to interact magnetically, nor did it show any deviation from random flare timing in phase with $P_{orb}$.
 However, since it is the system with the shortest planetary orbit in our sample, it is both expected to and does show marginal signal of tidal interaction.
@@
 TOI-540 is expected to have lower tidal interaction strength than Kepler-42 due to TOI-540 b's wider orbit, and also shows a weaker tidal SPI signal in all three scenarios.
+K2-25 and AU Mic are similar, but differ from TOI-540 -- both show tentative signs of magnetic SPI, but are consistent within $1\sigma$ with no observable tidal interaction.
 
-The results here, as with magnetic SPI, are suggestive, as they are consistent with theoretical expectation, albeit at low significance.
+%The results here, as with magnetic SPI, are suggestive, as they are consistent with theoretical expectation, albeit at low significance.
 Further observations, underway with TESS and soon PLATO, may confirm or reject the trends seen for both types of interaction.

### 2023-05-10 src/scripts/paper_table_tidal.py
added table with tidal parameters

@@ -1,0 +1,111 @@
+"""
+Python 3.8 -- UTF-8
+
+Ekaterina Ilin, 2022, MIT License
+
+Script that generates the tidal interaction of the paper, showing stellar and 
+planetary mass which are necessary for analysis (and producing a string of 
+references for the footnote), and 2. derived interaction, and AD test results 
+for the Porb/2 (i.e., in phase with tidal bulges). 
+"""
+
+import pandas as pd
+import numpy as np
+import paths
+
+
+
+if __name__ == "__main__":
+
+    # read in the tidal results
+    df = pd.read_csv(paths.data / "TIS_with_ADtests.csv")
+
+    # sort by p-value
+    df = df.sort_values(by="mean", ascending=False)
+
+    # convert to latex readable entries 
+    new_cols =  [r"$M_*$ [$M_\odot$]",
+                r"$M_p$ [$M_\oplus$]",
+                r"$10^{-8} \Delta g / g$",
+                r"$\tau_{\rm tide}$ [Gyr]",
+                r"$10^{-20} \partial L_{conv}/\partial t$"
+                r" $\left[M_\odot \left(\frac{km}{s}\right)^2\right]$",
+                ]
+
+    factor = [1., 317.907, 1e8, 1e-8, 1e20, 1]
+    n = [2, 1, 2, 1, 1, 3]
+    fs = ["f", "f", "f", "e", "e", "f"]
+    old_cols = ["M_star", "M_pl", "grav_pert", 
+                "tidal_disip_timescale", "torque_conv"]
+
+
+    for ocol, fac, n, f,  ncol in zip(old_cols, factor, n, fs, new_cols):
+        df[ncol] = df.apply(lambda row: f"${row[ocol] * fac:.{n}{f}}" + 
+                                        r"^{" + 
+                                        f"{row[ocol + '_up_err'] * fac:.{n}{f}}" + 
+                                        r"}_{" + 
+                                        f" {row[ocol + '_low_err'] * fac:.{n}{f}}" + 
+                                        r"}$", 
+                                        axis=1)
+    
+
+    g = lambda row: f"{row['mean']:.2f} [{row['std']:.2f}]"  
+    df[r"$p$-value"] = df.apply(g, axis=1)
+
+    # add ID column and p-value column
+    new_cols.insert(0, "ID")
+    new_cols.append(r"$p$-value")
+
+
+    # Get all bibkeys from singles table
[…]

### 2023-05-10 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+\begin{table*}
+\footnotesize
+\movetableright=-20mm
+\script{paper_table_tidal.py}
+\caption{Flaring tidal star-planet interaction.}
+\input{output/table_tidal.tex}
+    \label{tab:maintable_der}
+ \tablerefs{\input{output/table_tidal_bibstring.tex}}
+\end{table*}
+
 Tidal interaction can also lead to enhanced activity, globally, and locally.
 Locally, we expect to see periodicity with half the orbital period of the planet, corresponding to the two tidal bulges forming in the stellar envelope.
+XXXX tidal theory here XXXX
 
@@
 We applied the same technique as described in Section~\ref{sec:methods:adtest} to determine the significance of a local tidal SPI signal.
-Following~\citet{ilic2022tidal}, we compare the resulting $p$-values with three different models of tidal interaction in Fig.~\ref{fig:tidal} and list the derived values in Table~(XXXX).
+Following~\citet{ilic2022tidal}, we compare the resulting $p$-values with three different models of tidal interaction as proxies for expected excess flaring due to tides in Fig.~\ref{fig:tidal}.
+We list the derived values in Table~(XXXX).
+
 The first model measures the torque $\partial L / \partial t$, exerted by angular momentum transfer from star to planet or from planet to star~(\citealt{penev2012constraining}, their Eqns.
 1 and 2).
-We choose the tidal quality factor $Q_*=10^7$, but our results do not depend on the choice of $Q_*$.
+We choose the tidal quality factor $Q_*=10^7$.
+Our results do not depend on the choice of $Q_*$, as we only need to know the tidal torque down to a proportionality factor.
 We also make the simplifying assumption that the rotation period of the convective envelope is the same as the surface rotation period measured as described in Section~\ref{sec:data:rotationperiods}, ignoring differential rotation effects.
 \textcolor{red}{Why doesn't the torque depend on the stellar rotation velocity, except for the sign of interaction?}.
+
 The second model considers the tidal dissipation timescale -- the shorter the timescale, the higher the power of the interaction~\citep{zahn1977tidal}.
@@
 Most of our stars are clearly below the Kraft break at spectral type F5~(XXXX), above which stars have a radiative envelope, except for KOI-12, which is an F5 sub-giant~\citep{frasca2016activity}.
+
 The third model uses the gravitational perturbation as a proxy for the interaction~\citep{cuntz2000stellar}.
-All models require the planetary and stellar mass to be known, which we collect from the literature.
-For missing planetary masses, radii are known, so we can use the mass-radius relations in~\citet{chen2017probabilistic}.
+All models require the planetary and stellar mass to be known which we collect from the literature.
+For missing planetary masses, radii are known, so we can use the mass-radius relations implemented in \texttt{forecaster}~\citep{chen2017probabilistic}.
+GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute Ks magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}.
 We list the masses in Table~(XXXX).
@@
 On the one hand, since the flares in HIP 67522 mostly appear close to the transit phase, and not during eclipse, this may favor magnetic interaction, and the tidal signal would only be an artifact.
-On the other hand, the narrow range in which most of the flares on HIP 67522 occurred favor a well-located tidal bulge.
+On the other hand, the narrow range in which most of the flares on HIP 67522 occurred might favor a well-located tidal bulge.
 It is conceivable that both effects play a role at the same time.

### 2023-05-11 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Flares are strong and impulsive eruptions released by reconnection and subsequent relaxation of field lines in the corona~\citep{svestka1976solar,priest2002magnetic}.
-In contrast to solar flares, stellar flares often are extremely energetic, sometimes enhancing the stellar flux by orders of magnitude~\citep{maehara2012superflares, shibayama2013superflares, paudel2018k2} so that they can be detected in stars over 1kpc away~\citep{chang2015}.
+In contrast to solar flares, stellar flares often are extremely energetic, sometimes enhancing the stellar flux by orders of magnitude~\citep{maehara2012superflares, shibayama2013superflares, paudel2018k2} so that they can be detected in stars over 1kpc away~\citep{chang2015photometric}.
 But since they occur randomly in time, individual events can be hard to catch.
@@
 The stable active regions might withstand the diluting effect of differential rotation~(see Section~\ref{sec:discussion:rotsyn}).
-However, the \citet{lanza2022model} requires tidal interaction, which may be too weak in systems like AU Mic, where the planet is too small and distant for the proposed effect, but that still show spin-orbit commensurability and signs of flaring star-planet interaction.
+However, the \citet{lanza2022model} requires tidal interaction, which may be too weak in systems like AU Mic~(see also Section~\ref{sec:discussion:tidal}), where the planet is too small and distant for the proposed effect, but that still show spin-orbit commensurability and signs of flaring star-planet interaction.
 
@@
 \subsection{Tidal interaction}
+\label{sec:discussion:tidal}
 \begin{figure*}[t]
@@
         \includegraphics[width=\hsize]{figures/PAPER_tidal_AD_test.png}
-        \caption{
-           \textbf{Left panel}: Blue color indicates that the star rotates slower than the planet orbits, so that angular momentum is transferred from the orbit to the spin of the star.
+        \caption{Deviation from random flare times in phase with $P_{orb}/2$, i.e., in phase with tidal bulges raised on the star, compared to different models of tidal interaction.
+           \textbf{Left panel}: The tidal torque in the system for stars with a convective envelope.
+Blue color indicates that the star rotates slower than the planet orbits, so that angular momentum is transferred from the orbit to the spin of the star.
 Grey color is the reverse.
-\textbf{Middle panel}: \textbf{Right panel}:
-        }
+\textbf{Middle panel}: The tidal dissipation timescale.
+\textbf{Right panel}:  Relative gravitational perturbation in the star.}
         \label{fig:tidal}
@@
 \script{paper_table_tidal.py}
-\caption{Flaring tidal star-planet interaction.}
+\caption{Flaring tidal star-planet interaction. }
 \input{output/table_tidal.tex}
-    \label{tab:maintable_der}
+    \label{tab:tidal}
  \tablerefs{\input{output/table_tidal_bibstring.tex}}
@@
 Tidal interaction can also lead to enhanced activity, globally, and locally.
-Locally, we expect to see periodicity with half the orbital period of the planet, corresponding to the two tidal bulges forming in the stellar envelope.
-XXXX tidal theory here XXXX
+Locally, we expect to see periodicity with half the orbital period of the planet, corresponding to the two tidal bulges forming in the stellar envelope~\citep{cuntz2000stellar}.
+There are neither models to describe how that process leads to enhanced activity, or excess flaring, in star-planet systems, nor are there existing observations.
+However, in the extreme case of RS CVn binaries, starspots have been observed modulated with half the orbital period of the stellar companion~\citep{ozavci2018recurrent, kriskovics2023ei}.
+A similar effect was measured when the companion was likely a very low mass star or a brown dwarf~\citep{donati1995activity, frasca2008spots, parks2021interferometric}, and in the case of a K dwarf/white dwarf binary~\citep{hussain2006spot, watson2007roche}.
+In ellipsoidal binaries, a modulation of flares beyond geometrical effects was observed with Kepler~\citep{gao2016whitelight}, suggesting flaring regions at the location of the extreme tidal bulges in these stars.
+However, these systems are synchronized, $P_{rot}=P_{orb}$, so that intrinsic active longitudes~\citep{usoskin2007longterm, weber2013theory} cannot be disambiguated from the result of tidal star-star interaction ~\citep{holzwarth2003dynamics}.
+We can decrease the companion mass further to arrive at local, tidal star-planet interaction, for which, in our sample, spin and orbit are not synchronized.
+In analogy to~\citet{holzwarth2003dynamics}, we can picture an asymmetry induced in the stellar dynamo by the tidal disturbance, which would lead to a preference for flares at longitudes about $180\,$deg apart from each other.
 
@@
 Following~\citet{ilic2022tidal}, we compare the resulting $p$-values with three different models of tidal interaction as proxies for expected excess flaring due to tides in Fig.~\ref{fig:tidal}.
-We list the derived values in Table~(XXXX).
+We list the derived values in Table~\ref{tab:tidal}.
 
-The first model measures the torque $\partial L / \partial t$, exerted by angular momentum transfer from star to planet or from planet to star~(\citealt{penev2012constraining}, their Eqns.
+The first model measures the torque $\partial L / \partial t$, exerted by angular momentum transfer from star to planet or from planet to star, assumin the star has a convective envelope~(\citealt{penev2012constraining}, their Eqns.
 1 and 2).
 We choose the tidal quality factor $Q_*=10^7$.
-Our results do not depend on the choice of $Q_*$, as we only need to know the tidal torque down to a proportionality factor.
+Our results in Fig~\ref{fig:tidal} (left panel) do not depend on the choice of $Q_*$, as we only need to know the tidal torque down to a proportionality factor.
 We also make the simplifying assumption that the rotation period of the convective envelope is the same as the surface rotation period measured as described in Section~\ref{sec:data:rotationperiods}, ignoring differential rotation effects.
-\textcolor{red}{Why doesn't the torque depend on the stellar rotation velocity, except for the sign of interaction?}.
 
@@
 We assume that all stars in our sample have a convective envelope because they flare, and flaring requires a dynamo-generated magnetic field, which can only operate in stars with convective envelopes.
-Most of our stars are clearly below the Kraft break at spectral type F5~(XXXX), above which stars have a radiative envelope, except for KOI-12, which is an F5 sub-giant~\citep{frasca2016activity}.
+Most of our stars are dwarf stars below the Kraft break at spectral type F5, except for KOI-12, which is an F5 sub-giant~\citep{frasca2016activity}.
 
-The third model uses the gravitational perturbation as a proxy for the interaction~\citep{cuntz2000stellar}.
+The third model uses the gravitational perturbation as a proxy for the interaction~\citep{cuntz2000stellar}, originally proposed for star-planet interactions.
+Their Eqn.
+1 proposes a gravitational perturbation proportional to the mass ratio between planet and star, and $a^{-3}$.
+
 All models require the planetary and stellar mass to be known which we collect from the literature.
@@
 GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute Ks magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}.
-We list the masses in Table~(XXXX).
+We list the masses in Table~\ref{tab:tidal}.
 

### 2023-05-11 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \author{Katja Poppenh\"ager}
+\author{Nikoleta Ilic}
 
@@
 Locally, we expect to see periodicity with half the orbital period of the planet, corresponding to the two tidal bulges forming in the stellar envelope~\citep{cuntz2000stellar}.
-There are neither models to describe how that process leads to enhanced activity, or excess flaring, in star-planet systems, nor are there existing observations.
-However, in the extreme case of RS CVn binaries, starspots have been observed modulated with half the orbital period of the stellar companion~\citep{ozavci2018recurrent, kriskovics2023ei}.
-A similar effect was measured when the companion was likely a very low mass star or a brown dwarf~\citep{donati1995activity, frasca2008spots, parks2021interferometric}, and in the case of a K dwarf/white dwarf binary~\citep{hussain2006spot, watson2007roche}.
+There are neither detailed models to describe how that process leads to enhanced activity, or excess flaring, in star-planet systems, nor are there existing observations.
+However, in the extreme case of RS CVn binaries, starspots often appear modulated with half the orbital period of the system~\citep{olah2002time, ozavci2018recurrent, kriskovics2023ei}.
+A similar effect was measured when the companion was likely a very low mass star or a brown dwarf~\citep{donati1995activity, frasca2008spots, parks2021interferometric}, and in the case of a white dwarf companion~\citep{hussain2006spot, watson2007roche}.
 In ellipsoidal binaries, a modulation of flares beyond geometrical effects was observed with Kepler~\citep{gao2016whitelight}, suggesting flaring regions at the location of the extreme tidal bulges in these stars.
-However, these systems are synchronized, $P_{rot}=P_{orb}$, so that intrinsic active longitudes~\citep{usoskin2007longterm, weber2013theory} cannot be disambiguated from the result of tidal star-star interaction ~\citep{holzwarth2003dynamics}.
-We can decrease the companion mass further to arrive at local, tidal star-planet interaction, for which, in our sample, spin and orbit are not synchronized.
-In analogy to~\citet{holzwarth2003dynamics}, we can picture an asymmetry induced in the stellar dynamo by the tidal disturbance, which would lead to a preference for flares at longitudes about $180\,$deg apart from each other.
+However, all these systems are synchronized, $P_{rot}=P_{orb}$, so that intrinsic active longitudes~\citep{usoskin2007longterm, weber2013theory, jarvinen2005spots, lanza2009corot} cannot be disambiguated from the result of tidal star-star interaction ~\citep{holzwarth2003dynamics}.
+In that framework, we can decrease the companion mass to arrive at local, tidal star-planet interaction, for which, in our sample, spin and orbit are not synchronized.
+In analogy to~\citet{holzwarth2003dynamics}, we can picture an asymmetry induced in the stellar dynamo by the tidal disturbance, which leads to a preference for flares at longitudes about $P_{orb}/2$ apart from each other.
 
-We cannot tell whether an additional individual flare is produced by tidal or magnetic interaction, but as with magnetic interaction, we can look for deviations from a random distribution of flare times in phase with the relevant period.
-In the case of tidal interactions, the relevant period is $P_{orb}/2$.
+We cannot tell whether an additional individual flare is produced by tidal or magnetic interaction, but we can look for deviations from a random distribution of flare times in phase with the relevant period, i.e., $P_{orb}/2$.
 
 We applied the same technique as described in Section~\ref{sec:methods:adtest} to determine the significance of a local tidal SPI signal.
-Following~\citet{ilic2022tidal}, we compare the resulting $p$-values with three different models of tidal interaction as proxies for expected excess flaring due to tides in Fig.~\ref{fig:tidal}.
+Since we lack a model to relate tidally induced flaring to the systems' properties, we follow~\citet{ilic2022tidal}, and compare the resulting $p$-values with three different models of tidal interaction as proxies for expected excess flaring due to tides in Fig.~\ref{fig:tidal}.
 We list the derived values in Table~\ref{tab:tidal}.
 
-The first model measures the torque $\partial L / \partial t$, exerted by angular momentum transfer from star to planet or from planet to star, assumin the star has a convective envelope~(\citealt{penev2012constraining}, their Eqns.
+The first model measures the torque $\partial L / \partial t$, exerted by angular momentum transfer from star to planet or from planet to star, assuming the star has a convective envelope~(\citealt{penev2012constraining}, their Eqns.
 1 and 2).
@@
 The second model considers the tidal dissipation timescale -- the shorter the timescale, the higher the power of the interaction~\citep{zahn1977tidal}.
-Following~\citet{ilic2022tidal}, we adopt Eqn.2 from~\citep{albrecht2012obliquities} for the tidal dissipation timescale in the convective envelope.
+Following~\citet{ilic2022tidal}, we adopt Eqn.
+2 in~\citep{albrecht2012obliquities} for the tidal dissipation timescale in the convective envelope.
 We assume that all stars in our sample have a convective envelope because they flare, and flaring requires a dynamo-generated magnetic field, which can only operate in stars with convective envelopes.
@@
 
-The third model uses the gravitational perturbation as a proxy for the interaction~\citep{cuntz2000stellar}, originally proposed for star-planet interactions.
+The third model uses the gravitational perturbation as a proxy for the interaction~\citep{cuntz2000stellar}, originally derived for star-planet interactions.
 Their Eqn.
@@
 
-All models require the planetary and stellar mass to be known which we collect from the literature.
-For missing planetary masses, radii are known, so we can use the mass-radius relations implemented in \texttt{forecaster}~\citep{chen2017probabilistic}.
+We collect the planetary and stellar masses from the literature~(Table~\ref{tab:tidal}).
+For missing planetary masses, the radii were known, so used the mass-radius relations implemented in \texttt{forecaster}~\citep{chen2017probabilistic}.
 GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute Ks magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}.

### 2023-05-11 src/scripts/paper_correlation_coefficients.py

@@ -1,0 +1,66 @@
+"""
+Python 3.8 -- UTF-8
+
+Ekaterina Ilin, 2022, MIT License
+
+Script that calculates the Spearman and Pearson correlation coefficients for
+the tidal and magnetic interaction results.
+"""
+
+import pandas as pd
+import numpy as np
+import paths
+
+from scipy.stats import spearmanr, pearsonr
+
+if __name__ == "__main__":
+
+    # read in the tidal results
+    df = pd.read_csv(paths.data / "TIS_with_ADtests.csv")
+
+    # calculate the Spearman and Pearson correlation coefficients
+    for model in ["torque_conv", "tidal_disip_timescale", "grav_pert"]:
+        d = df[[model, "mean"]]
+        coeff = spearmanr(np.abs(d[model]), d["mean"])
+        pcoeff = pearsonr(np.abs(d[model]), d["mean"])
+        logcoeff = spearmanr(np.log10(np.abs(d[model])), np.log10(d["mean"]))
+        plogcoeff = pearsonr(np.log10(np.abs(d[model])), np.log10(d["mean"]))
+        print(model)
+        print(coeff)
+        print(logcoeff)
+        print(pcoeff)
+        print(plogcoeff)
+        print("")
+
+    # read magnetic SPI table
+    df = pd.read_csv(paths.data / "results.csv")
+
+    # select only the single stars
+    singles = df[df.multiple_star.isnull()]
+
+    # rename the column with the source of the rotation period
+    singles = singles.rename(columns={"st_rotp_source":"st_rotp_bibkey"})
+
+    # drop rows with TIC 67646988 and 236387002, the brown dwarfs
+    singles = singles[singles.TIC != "67646988" ]
+    singles = singles[singles.TIC != "236387002" ]
+
+    # the old Kepler-411 instance
+    singles = singles[singles.TIC != "399954349(c)" ]
+
+    # GJ 1061 because rotation is unclear
+    singles = singles[singles.TIC != "79611981" ]
+
+    # calculate the Spearman and Pearson correlation coefficients
+    for model in ["p_spi_sb_bp1_norm","p_spi_sb_bp0_norm",
+                "p_spi_aw_bp1_norm","p_spi_aw_bp0_norm"]:
+        
+        d = df[[model, "mean"]].dropna(how="any")
+        pcoeff = pearsonr(np.abs(d[model]), d["mean"])
[…]

### 2023-05-11 src/scripts/paper_table_tidal.py

@@ -62,6 +62,8 @@ if __name__ == "__main__":
     g = lambda row: f"{row['mean']:.2f} [{row['std']:.2f}]"  
     df[r"$p$-value"] = df.apply(g, axis=1)
 
+    print(df)
+
     # add ID column and p-value column
     new_cols.insert(0, "ID")
     new_cols.append(r"$p$-value")

### 2023-05-11 src/scripts/paper_tidal_interaction.py

@@ -53,11 +53,15 @@ if __name__ == "__main__":
         # plot the data
         # torque conv is the model, use appropriate color, otherwise grey
         if model == "torque_conv":
-            ax.scatter(res[model],res["mean"], label=model, 
-                       color=res["color_conv"], marker="x", s=50)
+            for color, g in res.groupby("color_conv"):
+                ax.errorbar(g[model],g["mean"], xerr=(g[model + "_up_err"], g[model + "_low_err"]),
+                            yerr=g["std"], label=color, 
+                        color=color, fmt="x", markersize=10)
+          
         else:
-            ax.scatter(res[model],res["mean"], label=model, 
-                       color="grey", marker="x", s=50)
+            ax.errorbar(res[model],res["mean"], xerr=(res[model + "_up_err"], res[model + "_low_err"]),
+                        yerr=res["std"], label=model, 
+                       color="grey", fmt="x", markersize=10)
 
         # add the ID of the systems with low p-values
         texts = []

### 2023-05-12 src/scripts/paper_table_tidal.py
improving masses and table layout

@@ -13,6 +13,12 @@ import pandas as pd
 import numpy as np
 import paths
 
+def round_to_1(x):
+    if x == 0:
+        return 0
+    else:
+        return np.round(x, -int(np.floor(np.log10(np.abs(x)))))
+
 
 
 if __name__ == "__main__":
@@ -50,11 +56,12 @@ if __name__ == "__main__":
 
 
     for ocol, fac, n, f,  ncol in zip(old_cols, factor, n, fs, new_cols):
-        df[ncol] = df.apply(lambda row: f"${row[ocol] * fac:.{n}{f}}" + 
+        print(ncol)
+        df[ncol] = df.apply(lambda row: f"${round_to_1(row[ocol] * fac):.0{f}}" + 
                                         r"^{" + 
-                                        f"{row[ocol + '_up_err'] * fac:.{n}{f}}" + 
+                                        f"{round_to_1(row[ocol + '_up_err'] * fac):.0{f}}" + 
                                         r"}_{" + 
-                                        f" {row[ocol + '_low_err'] * fac:.{n}{f}}" + 
+                                        f" {round_to_1(row[ocol + '_low_err'] * fac):.0{f}}" + 
                                         r"}$", 
                                         axis=1)
     

### 2023-05-12 src/scripts/paper_tidal_interaction.py

@@ -54,14 +54,20 @@ if __name__ == "__main__":
         # torque conv is the model, use appropriate color, otherwise grey
         if model == "torque_conv":
             for color, g in res.groupby("color_conv"):
-                ax.errorbar(g[model],g["mean"], xerr=(g[model + "_up_err"], g[model + "_low_err"]),
+                xerr = np.abs(np.asarray([g[model + "_low_err"], np.abs(g[model + "_up_err"])]))
+                print(xerr)
+                ax.errorbar(g[model],g["mean"], xerr=xerr,
                             yerr=g["std"], label=color, 
-                        color=color, fmt="x", markersize=10)
+                        color=color, fmt="X", markersize=7, elinewidth=0.3)
           
         else:
-            ax.errorbar(res[model],res["mean"], xerr=(res[model + "_up_err"], res[model + "_low_err"]),
+            xerr = np.abs(np.asarray([res[model + "_low_err"], np.abs(res[model + "_up_err"])]))
+            print(model)
+            print(xerr)
+
+            ax.errorbar(res[model],res["mean"], xerr=xerr,
                         yerr=res["std"], label=model, 
-                       color="grey", fmt="x", markersize=10)
+                       color="grey", fmt="X", markersize=7, elinewidth=0.3)
 
         # add the ID of the systems with low p-values
         texts = []
@@ -76,13 +82,13 @@ if __name__ == "__main__":
 
         minx, maxx = res[model].min(), res[model].max()
 
-        ax.set_xlim(minx*0.8, maxx*1.3)
+        ax.set_xlim(minx*0.1, maxx*10)
 
         # add the sigma lines
         sigmas, sigma_label = get_sigma_values()
         for sigma, l in zip(sigmas, sigma_label):
             ax.axhline(sigma, color="k", linestyle="--", alpha=.5)
-            ax.text(maxx*1.4, sigma, l, fontsize=10)
+            ax.text(maxx*12, sigma, l, fontsize=10)
 
         # adjust label positions
         adjust_text(texts, ax=ax)

### 2023-05-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+\subsubsection{Comparison to tidal interaction scaling laws}
+
 We cannot tell whether an additional individual flare is produced by tidal or magnetic interaction, but we can look for deviations from a random distribution of flare times in phase with the relevant period, i.e., $P_{orb}/2$.
@@
 We applied the same technique as described in Section~\ref{sec:methods:adtest} to determine the significance of a local tidal SPI signal.
-Since we lack a model to relate tidally induced flaring to the systems' properties, we follow~\citet{ilic2022tidal}, and compare the resulting $p$-values with three different models of tidal interaction as proxies for expected excess flaring due to tides in Fig.~\ref{fig:tidal}.
+Since we lack a model to relate tidally induced flaring to the systems' properties, we follow~\citet{ilic2022tidal}, and compare the resulting $p$-values with three different scaling laws for tidal interaction as proxies for expected excess flaring due to tides in Fig.~\ref{fig:tidal}.
 We list the derived values in Table~\ref{tab:tidal}.
@@
 
+\subsubsection{Planetary and stellar masses}
+
 We collect the planetary and stellar masses from the literature~(Table~\ref{tab:tidal}).
@@
 We list the masses in Table~\ref{tab:tidal}.
+For Kepler-42 b, we used  $M_p=0.1-2.06M_\oplus$ that covers pure rock to pure iron compositions in \citet{muirhead2012characterizing}.
+
+\subsection{Tidal vs. magnetic flaring star planet interaction}
 
@@
 Overall, the signal in phase with $P_{orb}/2$ is smaller than with $P_{orb}$.
-However, in all three scenarios, the deviation from random flare timing increases with expected tidal interaction strength.
-We can now compare the magnetic interaction measurements to the tidal ones in some of the conspicuous systems:
+However, in all three scenarios, the sample's deviation from random flare timing increases with expected tidal interaction strength.
+We can compare the magnetic interaction measurements to the tidal ones in some of the conspicuous systems:
 

### 2023-05-12 src/scripts/paper_table_tidal.py
added better mass estimate for Kepler-1558 and formatting table

@@ -17,7 +17,7 @@ def round_to_1(x):
     if x == 0:
         return 0
     else:
-        return np.round(x, -int(np.floor(np.log10(np.abs(x)))))
+        return np.round(x, -int(1 + np.floor(np.log10(np.abs(x)))))
 
 
 

### 2023-05-12 src/scripts/paper_tidal_interaction.py

@@ -62,8 +62,6 @@ if __name__ == "__main__":
           
         else:
             xerr = np.abs(np.asarray([res[model + "_low_err"], np.abs(res[model + "_up_err"])]))
-            print(model)
-            print(xerr)
 
             ax.errorbar(res[model],res["mean"], xerr=xerr,
                         yerr=res["std"], label=model, 

### 2023-05-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-\subsection{Tidal vs. magnetic flaring star planet interaction}
+\subsubsection{Tidal vs. magnetic flaring star planet interaction}
 
@@
 
-Among the systems, HIP 67522 appears with tentative signs of both tidal and magnetic interaction (measured and expected in the different scenarios).
+\paragraph{HIP 67522} appears with tentative signs of both tidal and magnetic interaction (measured and expected in the different scenarios).
 On the one hand, since the flares in HIP 67522 mostly appear close to the transit phase, and not during eclipse, this may favor magnetic interaction, and the tidal signal would only be an artifact.
 On the other hand, the narrow range in which most of the flares on HIP 67522 occurred might favor a well-located tidal bulge.
-It is conceivable that both effects play a role at the same time.
+Conceivably, both effects play a role at the same time.
 
-KOI-12, which lacks signal with $P_{orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction.
+\paragraph{KOI-12}, which lacks signal with $P_{orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction.
 This could be interpreted as KOI-12 b orbiting outside the Alfv\'en radius, unable to interact magnetically, but tidally.
 We note that KOI may be evolving off the main sequence, so that the tidal interaction estimates might not be accurate for this star.
-TAP 26, which shows no signs of magnetic SPI, does not show any sign of tidal interaction despite both being high as expected from models.
-This could again be due to the inclination of TAP 26's orbit, but only if the flares caused by the tidal bulge are not too close to the equator.
-In that case, TAP 26's tidally induced flares should be more modulated than the magnetically induced ones.
 
+\paragraph{TAP 26,} which shows no signs of magnetic SPI, does not show any sign of tidal interaction despite both being high according to the scaling laws.
+This could again be due to the inclination of TAP 26's orbit, but only if the flares caused by the tidal bulge are not close to the equator.
+Otherwise, TAP 26's tidally induced flares should be more modulated than the magnetically induced ones.
+
+\paragraph{Kepler-42 and TOI-540}.
 Kepler-42 is neither expected to interact magnetically, nor did it show any deviation from random flare timing in phase with $P_{orb}$.
@@
 Kepler-42 is very similar to TOI-540, which also is a small M dwarf with a likely terrestrial planet in a very short orbit.
-The key difference may be that Kepler-42 is rotating at about 70 days, and therefore expected to have a relatively weak magnetic field, whereas TOI-540 is a young star with a rotation period $<1\,$d.
-TOI-540 is expected to have lower tidal interaction strength than Kepler-42 due to TOI-540 b's wider orbit, and also shows a weaker tidal SPI signal in all three scenarios.
+A key difference is that Kepler-42 is rotating at about 70 days, and therefore expected to have a relatively weak magnetic field, whereas TOI-540 is a young star with a rotation period $<1\,$d.
+TOI-540 is expected to have lower tidal interaction strength than Kepler-42 due to TOI-540 b's wider orbit, and also shows a weaker tidal flaring SPI signal in all three scenarios.
 K2-25 and AU Mic are similar, but differ from TOI-540 -- both show tentative signs of magnetic SPI, but are consistent within $1\sigma$ with no observable tidal interaction.

### 2023-05-12 src/scripts/paper_table_tidal.py
perhaps now it looks better

@@ -17,7 +17,7 @@ def round_to_1(x):
     if x == 0:
         return 0
     else:
-        return np.round(x, -int(1 + np.floor(np.log10(np.abs(x)))))
+        return np.round(x, -int(np.floor(np.log10(np.abs(x)))))
 
 
 
@@ -57,11 +57,11 @@ if __name__ == "__main__":
 
     for ocol, fac, n, f,  ncol in zip(old_cols, factor, n, fs, new_cols):
         print(ncol)
-        df[ncol] = df.apply(lambda row: f"${round_to_1(row[ocol] * fac):.0{f}}" + 
+        df[ncol] = df.apply(lambda row: f"${round_to_1(row[ocol] * fac)}" + 
                                         r"^{" + 
-                                        f"{round_to_1(row[ocol + '_up_err'] * fac):.0{f}}" + 
+                                        f"{round_to_1(row[ocol + '_up_err'] * fac)}" + 
                                         r"}_{" + 
-                                        f" {round_to_1(row[ocol + '_low_err'] * fac):.0{f}}" + 
+                                        f" {round_to_1(row[ocol + '_low_err'] * fac)}" + 
                                         r"}$", 
                                         axis=1)
     

### 2023-05-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 We list the masses in Table~\ref{tab:tidal}.
-For Kepler-42 b, we used  $M_p=0.1-2.06M_\oplus$ that covers pure rock to pure iron compositions in \citet{muirhead2012characterizing}.
+For Kepler-42 b, we used  $M_p=0.1-2.06M_\oplus$ that covers pure rock to pure iron compositions in \citet{muirhead2012characterizing}, and adopted the logarithmic mean for our estimate.
+Kepler-1558 c has a similar radius to Kepler-42 b, i.e., most likely a bare core planet, so we proceeded analogously to estimate its mass.
 

### 2023-05-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Kepler-1558 c has a similar radius to Kepler-42 b, i.e., most likely a bare core planet, so we proceeded analogously to estimate its mass.
+We also adopt the upper limit of $5M_J$ for HIP 67522, but use the lower error from \citet{chen2017probabilistic}.
 
@@
 
-\paragraph{KOI-12}, which lacks signal with $P_{orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction.
+\paragraph{KOI-12,} which lacks signal with $P_{orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction.
 This could be interpreted as KOI-12 b orbiting outside the Alfv\'en radius, unable to interact magnetically, but tidally.
-We note that KOI may be evolving off the main sequence, so that the tidal interaction estimates might not be accurate for this star.
+We note that KOI-12 may be evolving off the main sequence, so that the tidal interaction estimates might not be accurate for this star.
 
-\paragraph{TAP 26,} which shows no signs of magnetic SPI, does not show any sign of tidal interaction despite both being high according to the scaling laws.
+\paragraph{TAP 26,} which shows no signs of magnetic SPI, does not show any sign of tidal interaction, either, despite both being high according to the scaling laws.
 This could again be due to the inclination of TAP 26's orbit, but only if the flares caused by the tidal bulge are not close to the equator.
@@
 
-\paragraph{Kepler-42 and TOI-540}.
-Kepler-42 is neither expected to interact magnetically, nor did it show any deviation from random flare timing in phase with $P_{orb}$.
+\paragraph{Kepler-42 and TOI-540} Kepler-42 is neither expected to interact magnetically, nor did it show any deviation from random flare timing in phase with $P_{orb}$.
 However, since it is the system with the shortest planetary orbit in our sample, it is both expected to and does show marginal signal of tidal interaction.

### 2023-05-17 src/scripts/paper_cumdist_individual_rv.py
changed phase histograms to ED above 1s as in the paper

@@ -23,6 +23,9 @@ if __name__ == "__main__":
     # read in flare table
     flares = pd.read_csv(paths.data / "PAPER_flare_table.csv")
 
+    # pick only flares above 1 s in ED
+    flares = flares[flares.ED > 1]
+
     # pick only real flares
     flares = flares[(~flares.tstart.isnull()) & (flares.orbital_phase==-1)]
 
@@ -30,17 +33,18 @@ if __name__ == "__main__":
     res = pd.read_csv(paths.data / "results.csv")
 
     tics = res[(res.multiple_star.isnull()) & (res.multiple_star_source != "BD") & (res.TIC != "399954349(c)")]
-    tics = tics.sort_values(by="number_of_flares", ascending=False).TIC.astype(str)
+    tics = tics.sort_values(by="number_of_flares", ascending=False)
 
-    tics = tics.values
 
     # Add the number of flares to the TICs
     n_flares = []
-    for tic in tics:
-        n_flares.append(pd.read_csv(paths.data / f"TIC_{tic}_cumhist.csv").shape[0])
+    for tic in tics.TIC:
+        n_flares.append(flares[flares.TIC.astype(str) == str(tic)].shape[0])
+    
     
     # sort the TICs by the number of flares
-    tics = [x for _,x in sorted(zip(n_flares, tics), reverse=True)]
+    tics["n_flares"] = n_flares
+    tics = tics.sort_values(by="n_flares", ascending=False)
 
     # make a plot for 15 panels
     fig, ax = plt.subplots(nrows=3, ncols=3, figsize=(14,9.5), sharex=True)
@@ -50,7 +54,7 @@ if __name__ == "__main__":
     ax = ax[::-1]
 
     # create a subplot for each star
-    for tic in tics:
+    for tic in tics.TIC:
 
         # print(g.shape)
         g = flares[(flares.TIC.astype(str) == tic)]

### 2023-05-17 src/scripts/paper_cumdist_individual_transiting.py

@@ -23,6 +23,9 @@ if __name__ == "__main__":
     # read in flare table
     flares = pd.read_csv(paths.data / "PAPER_flare_table.csv")
 
+    # pick only flares above 1 s in ED
+    flares = flares[flares.ED > 1]
+
     # pick only real flares
     flares = flares[flares.orbital_phase != -1]
 
@@ -47,7 +50,7 @@ if __name__ == "__main__":
     # Add the number of flares to the TICs
     n_flares = []
     for tic in tics.TIC:
-        n_flares.append(pd.read_csv(paths.data / f"TIC_{tic}_cumhist.csv").shape[0])
+        n_flares.append(flares[flares.TIC.astype(str) == str(tic)].shape[0])
     
     # sort the TICs by the number of flares
     tics["n_flares"] = n_flares

### 2023-05-17 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \begin{abstract}
-    In many of the star-planet systems discovered so far, most planets orbit far within Mercury's orbit, and many are so close to their host that they plow through its extended magnetosphere.
-In these systems, planets become in-situ probes of the dynamic magnetic fields in their orbits, able to trigger flares on the stellar surface.
-Until recently, however, these flaring star-planet interactions suffered from small sample sizes, and poor orbital phase coverage.
+    In many of the star-planet systems discovered so far, the innermost planets orbit extremely close to their host, that is, within its extended magnetosphere.
+In these systems, the planets become in-situ probes of the stellar magnetic fields.
+As they move, they may trigger flares on the stellar surface.
+Until recently, searches for such flaring star-planet interactions suffered from small sample sizes, and poor orbital phase coverage.
 
@@
 
-    Out of 1811 searched systems, 26 are single star systems that show three or more flares each.
-For these, we quantified the intensity of excess flaring, and compared it against the expected amplitude of interaction based on the system's parameters.
-Most systems are neither expected to interact, nor do they show excess flaring.
-Among those systems that have high expected power of magnetic interaction, we see two branches.
-An inactive one, where no signs of excess flaring appear regardless of favorable conditions, and an active one where expected power and excess flaring are correlated.
-While this trend is tentative, it is consistent across all investigated models for magnetic interaction.
-Finally, we searched for signs of tidal interaction, that is, excess flaring in phase with the tidal bulges ($P_{orb}/2$), and found a similar trend with different expected powers of tidal interaction.
-Our results support the view that young systems with close in planets are likely to interact both tidally and magnetically, whereas star-planet interactions in old, slowly rotating systems lack the extended magnetosphere, and interact predominantly tidally.
+    In the 1811 searched systems, we found 26 single stars with three or more flares each.
+We quantified the significance of their excess flaring, and compared it against the theoretically expected amplitude of magnetic interaction.
+Most systems are neither expected to, nor do they show excess flaring.
+Among the systems that we can expect to interact, we see two branches.
+An inactive one, where no signs of excess flaring appear, and an active one, where expected power and excess flaring are correlated.
+This trend is tentative, but consistent for all scaling laws for magnetic interaction.
+
+    Finally, we searched the same data for signs of locally expressed tidal interaction, that is, excess flaring in phase with the tidal bulges ($P_{\rm orb}/2$).
+We found a similar trend with different scaling laws of tidal interaction, albeit at even lower significance.
+Our system-by-system comparison suggests that young systems may interact both tidally and magnetically, whereas old, magnetically inactive systems might mostly interact tidally.
     %magnetic field strength (using $Ro$-$B$ relations), orbital parameters, and planet radius.
@@
 These forces are typically subsumed under the term star-planet interactions (SPI) that emphasizes that they are bidirectional, affecting both planet, and star.
-Their effects pose challenges, but also opportunities for our understanding of star-planet systems:
+Specifically, the effects on the star pose challenges, but also opportunities for our understanding of star-planet systems:
 
 On the one hand, a close-in planet that changes the star's rotation and activity makes it more difficult for us to model the system's evolution, as it affects fundamental stellar parameters.
-Inferring stellar age from rotation may be biased, if the star is spun up or spun down relative to stars without close-in companions~\citep{tejadaarevalo2021further, brown2014discrepancies, maxted2015comparison}.
+Ages inferred from rotation will be biased, if the star is spun up or spun down relative to stars without close-in companions~\citep{tejadaarevalo2021further, brown2014discrepancies, maxted2015comparison}.
 Analogously, altered activity levels may mimic an older or younger host than it actually is~\citep{ilic2022tidal}.
+On the other hand, measuring in what ways and how much close-in planets alter their hosts' behavior can provide important insights into the habitability of the entire system~\citep{shkolnik2018signatures}.
+Even if they orbit far inside the habitable zone, such planets probe the system's space weather and mass loss by revealing the extent of the Alfv\'en zone~\citep{kavanagh2021planetinduced, chebly2022destination}.
+% Prospectively, planet-induced stellar activity could quantify otherwise difficult to measure planetary properties such as the strength and extent of their magnetic field~\citep{cauley2019magnetic}.
 
-On the other hand, understanding short-term, magnetic star-planet interactions -- the focus of this work -- can provide important insights into the habitability of the entire system~\citep{shkolnik2018signatures}.
-Even if they orbit far inside the habitable, planets involved in such interactions are in-situ probes of the system's space weather and mass loss by revealing the extent of the Alfv\'en zone~\citep{kavanagh2021planetinduced, chebly2022destination}.
-Prospectively, planet-induced stellar activity could reveal otherwise difficult to measure planetary properties such as the strength and extent of their magnetic field~\citep{cauley2019magnetic}.
-
-The search for magnetic SPI (Section~\ref{sec:intro:mspi}) in the form of changes in global activity indicators~(Section~\ref{sec:intro:local}), has so far been a series of detections and non-detections, often due to selection bias in the studied systems.
+The search for magnetic SPI (Section~\ref{sec:intro:mspi}) in the form of changes in global activity indicators~(Section~\ref{sec:intro:global}), has so far been a series of detections and non-detections, often due to selection bias in the studied systems.
 Looking for local changes that trace the magnetic footpoint that connects planet to star mitigates this bias, but introduces another -- sampling bias due to poor orbital phase coverage.
-Flares~(Section~\ref{sec:intro:flares}) are activity markers that can be caused by SPI~(Section~\ref{sec:intro:fspi}), and be monitored more easily with high phase coverage than chromospheric lines or coronal brightness over long periods of time with missions like Kepler and TESS.
-Thanks to their enormous archives of hundreds of cumulative years of stellar monitoring, we can overcome the limitations of individual system studies~(Section~\ref{sec:intro:local}), and now look for flaring SPI more comprehensively, and systematically.
+Flares~(Section~\ref{sec:intro:flares}) are activity markers that can be caused by SPI~(Section~\ref{sec:intro:fspi}).
+They can be monitored with high phase coverage over long periods of time with missions like Kepler and TESS.
+Thanks to their large archives of hundreds of cumulative years of stellar monitoring, we can overcome the limitations of individual system studies~(Section~\ref{sec:intro:local}), and now look for flaring SPI more comprehensively, and systematically.
 
@@
 Alfv\'en waves set off by the planet within the magnetic field they cross cannot propagate back to the star if the wind carries the plasma away faster than these waves can travel.
-In the sub-Alfv\'enic regime, the wave can reach the star, and deposit its energy in some way in its atmosphere.
-\citet{lanza2012starplanet, lanza2018closeby} and \citet{zarka2007plasma, saur2013magnetic} suggest different mechanisms for when and how the energy transport and dissipation takes place, and how much energy can be transferred and dissipated at all.
-All suffer from a lack of observational constraints for calibration.
+In the sub-Alfv\'enic regime, the wave can reach the star, and deposit its energy in its atmosphere.
+\citet{lanza2012starplanet, lanza2018closeby}, and \citet{zarka2007plasma} and \citet{saur2013magnetic} suggest different mechanisms for when and how the energy transport and dissipation takes place, and how much energy can be transferred and dissipated at all.
+They all lack observational constraints for calibration, which we aim to provide in this work.
 
-\subsection{Searching for global changes in actvity}
+\subsection{Searching for global changes in activity}
 \label{sec:intro:global}
-Measuring magnetic star planet-interaction is notoriously difficult in individual systems because a non-detection may not mean an absence of the interaction, but just a temporary cessation~\citep{shkolnik2005hot, shkolnik2008nature}.
+Measuring magnetic star planet-interaction is notoriously difficult in individual systems because a non-detection may not mean an absence of the interaction, but merely a temporary cessation~\citep{shkolnik2005hot, shkolnik2008nature}.
 Statistical studies searching for changes in global chromospheric and coronal activity indicators in star-planet systems with close-in planets relative to planet-less stars are inconclusive~\citep{kashyap2008extrasolar,scharf2010possible, shkolnik2013ultraviolet, france2018farultraviolet, viswanath2020statistical, krejcova2012evidence, miller2015comprehensive, poppenhaeger2010coronal}.
@@
 Currently, the Transiting Exoplanet Survey Satellite~\citep{ricker2015transiting} is rapidly growing the archive~\citep{gunther2020stellar}.
-As will become clear in the following Section, their key advantage for this work is the quasi uninterrupted monitoring of star-planet systems that covers all phases of a close-in planet's orbit.
+Their key advantage for this work is the nearly uninterrupted monitoring of star-planet systems that covers all phases of a close-in planet's orbit.
 
@@
 \label{sec:intro:fspi}
-The absolute power of flaring star-planet interactions is difficult to constrain, so we do not know how energetic planet-induced flares can be.
+The absolute power of flaring star-planet interactions is difficult to constrain.
+We do not know how energetic planet-induced flares can be.
 The estimates of the maximum dissipated power~\citep{lanza2018closeby} are well within the regime of superflares typically observed by Kepler and TESS.
 However, on the one hand, that power is an upper limit, so the observed energies might be lower.
-The planet might for instance be triggering flares prematurely, leading to an overabundance of low energy flares~\citep{loyd2023flares}.
-On the other hand, the energy need not be dissipated continuously, particularly in the stretch-and-break mechanism, so it might be higher.
+The planet might, for instance, be triggering flares prematurely, leading to an overabundance of low energy flares~\citep{loyd2023flares}.
+On the other hand, the energy need not be dissipated continuously, particularly in the stretch-and-break mechanism proposed by~\citep{lanza2012starplanet}, so an individual flare's energy might be higher.
 We also do not know whether flares triggered by interactions with a companion would have different properties than intrinsic flares.
@@
 Depending on the system's viewing geometry, i.e., the inclination of the rotation axis, the spin-orbit (mis-)alignment, and the extent and configuration of the large scale magnetic field -- the footpoint could be always in view, or never.
-In expectation, however, in star-planet systems with favorable architectures and magnetic field states, the footpoint visibility will be modulated in phase with the planetary orbit.
+In expectation, however, in star-planet systems with favorable viewing geometries and magnetic field states, the footpoint visibility will be modulated in phase with the planetary orbit.
 The resulting phase preference of planet-induced flares introduces a deviation from a random distribution of flares.
@@
 \label{sec:intro:local}
+In contrast with global SPI, local SPI effects are easier to tell apart from intrinsic stellar behavior because they are tied to the planet's orbital period. 
 Phase-correlated activity, flaring and otherwise, has been searched for in individual systems.
 After eight years of monitoring of HD 189733, an X-ray active Hot Jupiter host, the observed slight clustering of flaring in orbital phase remains tentative~\citep{pillitteri2022xray}.
-\citet{maggio2015coordinated} observed an eruption of X-ray emissionwhen the Jupiter-sized companion was in periastron on its highly eccentric orbit around its host HD 17156.
+\citet{maggio2015coordinated} observed an eruption of X-ray emission when the Jupiter-sized companion was in periastron on its highly eccentric orbit around its host HD 17156.
 However, a similar study using chromospheric indicators in the eccentric system HD 80606 found no variation between periastron and apoastron~\citep{figueira2016activity}.
@@
 
+\subsection{Overview}
 In this work, we searched for excess flaring in all available Kepler and TESS short cadence light curves of confirmed star-planet systems~(Section~\ref{sec:data}).
@@
 We present the catalog of all flares found in our sample of star-planet systems, and compare the test results with the expected power of interaction for each system~(Section~\ref{sec:results}).
-We discuss the results for the most interesting star-planet systems individually~(Section~\ref{sec:results:individualstars}), and take a look at the patterns emerging from our analysis~(Section~\ref{sec:discussion}).
+We discuss the results for the most interesting star-planet systems individually~(Section~\ref{sec:results:individualstars}), and take a look at the patterns emerging from our analysis~(Section~\ref{sec:discussion}), particularly at the possible role of tidal flaring SPI in our observations~(Section~\ref{sec:discussion:tidal}).
 We summarize our findings in Section~\ref{sec:summary}.
@@
 \label{sec:data}
-In this study, we wanted to compile the largest possible sample to search for flaring star-planet interactions.
-We took the entire Planetary Systems Composite Parameters Table (PSCP, Section~\ref{sec:data:sps})\footnote{ \url{https://exoplanetarchive.ipac.caltech.edu/cgi-bin/TblView/nph-tblView?app=ExoTbls&config=PSCompPars}} from the NASA Exoplanet Archive, as of July 2022, and scanned the systems for available Kepler and TESS light curves~(Section~\ref{sec:data:photometry}).
+In this study, we compiled the largest possible sample to search for flaring star-planet interactions.
+We took the entire Planetary Systems Composite Parameters Table (PSCP\footnote{ \url{https://exoplanetarchive.ipac.caltech.edu/cgi-bin/TblView/nph-tblView?app=ExoTbls&config=PSCompPars}}, Section~\ref{sec:data:sps}) from the NASA Exoplanet Archive, as of July 2022, and scanned the systems for available Kepler and TESS light curves~(Section~\ref{sec:data:photometry}).
 We searched a total of 1811 systems and over 7200 light curves from both missions for flares.
-To calculate the amount of excess flaring from star-planet interaction, we then required the orbital periods of each system~(Section~\ref{sec:data:orbitalperiod}).
+To calculate the amount of excess flaring from star-planet interaction, we then sought out the orbital periods of each system from the literature~(Section~\ref{sec:data:orbitalperiod}).
 To compare our measurements to theory, we estimated the expected power of interaction for each system with at least three flares.
-For this, we required further system parameters -- distance between planet and star, stellar rotation period, planetary radius, and stellar luminosity~(Sections~\ref{sec:data:orbitalperiod}-\ref{sec:data:lum}).
-We began by compiling the table of system parameters with the PSCP, but verified, supplemented and updated the table from the literature.
-The literature parameters for the systems in the final sample of systems, for which we performed the full analysis, is shown in Table~\ref{tab:maintable_lit}.
+For this, we required further system parameters -- distance between planet and star, stellar rotation period, planetary radius, and stellar luminosity~(Sections~\ref{sec:data:a}-\ref{sec:data:lum}), which we also mostly found in the literature.
+We began by compiling the table of system parameters with the PSCP, but verified, supplemented and updated the table with more up-to-date results.
+The parameters for the systems in the final sample of systems are shown in Table~\ref{tab:maintable_lit}.
 
@@
 \label{sec:data:sps}
-We compiled our sample of star-planet systems from the PSCP, from which we removed controversial planet detections (``pl\_controv\_flag'' set to 1), i.e.
-detections with existing literature questioning the result.
-The catalog then contained 2993 transiting and 191 non-transiting systems, from which we picked the innermost known planet in each system.
+We compiled our sample of star-planet systems from the PSCP, from which we removed controversial planet detections (``pl\_controv\_flag'' set to 1), i.e., detections with existing literature questioning the result.
+The resulting catalog contained 2993 transiting and 191 non-transiting systems, from which we picked the innermost known planet in each system.
 
@@
 Their excellent coverage of orbital phases makes the light curves ideal for our search for orbital phase dependent flare timing.
-
 Between 2009 and 2013, the Kepler space telescope~\citep{koch2010kepler} nearly continuously observed a patch of the sky in the Cygnus-Lyra region.
@@
 If the eccentricity is known, then the uncertainty on the distance is set to either the error on the semi-major axis, or to half of the difference between periastron and apoastron -- whichever is larger.
-If eccentricity is not known, then the uncertainty on the distance is either the 25\% error on the semi-major axis, that is, assuming $e=0.25$, or the uncertainty on the semi-major axis -- whichever is larger.
+If eccentricity is not known, then the uncertainty on the distance is set to either the 25\% error on the semi-major axis, that is, assuming $e=0.25$, or the uncertainty on the semi-major axis -- whichever is larger.
 We chose $e=0.25$ because it is both a typical value within our sample~(see Table~\ref{tab:maintable_lit}), and in the literature~\citep{eylen2019orbital}.
@@
 
-The rotation of GJ 3082 was measured and are consistent both in TESS and in KELT light curves to below 1\,s precision~\citep{gunther2020stellar}.
+Among the stars without given uncertainties, the rotation of GJ 3082 was measured and is consistent both in TESS and in KELT light curves to below 1\,s precision~\citep{gunther2020stellar}.
 The rotation of GJ 674 is consistent between light curve periodograms~\citep{kiraga2007agerotationactivity}, and activity-rotation relations~\citep{boisse2011disentangling} at a $<10\%$ level.
-GJ 3323 only has rotation periods inferred from activity indicators~\citep{astudillo-defru2017magnetic}, without any periodicity detected in the activity indicators themselves~\citep{astudillo-defru2017harps}.
+GJ 3323 only has rotation periods inferred from activity indicators~\citep{Astudillo-defru2017magnetic}, without any periodicity detected in the activity indicators themselves~\citep{astudillo-defru2017harps}.
 The rotation of Proxima Cen is very slow, but consistent between different datasets~\citep{anglada-escude2016terrestrial, kiraga2007agerotationactivity}.
@@
 As a final step, we fit exponential functions to the edges of the light curves, if there are data points that deviate more than one standard deviation from the median value, while keeping the flare candidates masked.
+Transits are usually too shallow to affect either light curve de-trending or flare finding.
+The light curve portions around deep transits were inspected manually.
 
@@
 \label{sec:methods:adtest}
-For each star-planet system with three or more flares in their light curves, we test for deviations from a random distribution of flares with orbital phase.
+For each star-planet system with three or more flares in its light curves, we test for deviations from a random distribution of flares with orbital phase.
 We use the same customized Anderson-Darling test as in \cite{ilin2022searching}.
@@
 \label{sec:methods:relvel}
-We calculate the relative velocity between the magnetic field of the star and the planet using stellar rotation period $P_{rot}$, orbital period $P_{orb}$, and semi-major axis $a$.
+We calculate the relative velocity between the magnetic field of the star and the planet using stellar rotation period $P_{rot}$, orbital period $P_{\rm orb}$, and semi-major axis $a$.
 We assume that the large scale magnetic field is co-rotating with the stellar surface, and calculate the relative velocity at the planet's orbital distance:
@@
 \begin{equation}
-    v_{rel} = 2 \pi a \left(\frac{1}{P_{orb}} - \frac{1}{P_{rot}}\right).
+    v_{rel} = 2 \pi a \left(\frac{1}{P_{\rm orb}} - \frac{1}{P_{rot}}\right).
 \end{equation}
@@
 \label{sec:methods:bfield}
-We derive the average magnetic field strength $B$ from $Ro$ using the empirical relation derived in \cite{reiners2022magnetism},  Table 2, in the unsaturated and saturated regimes, respectively:
+We derive the average magnetic field strength $B$ from $R$o using the empirical relation derived in \citet{reiners2022magnetism},  Table 2, in the unsaturated and saturated regimes, respectively:
 
 \begin{eqnarray}
-    B &= 199\,\text{G} \cdot Ro^{-1.26\pm 0.1} \;(\text{if}\; Ro > 0.13) \\
-    B &= 2050\,\text{G} \cdot Ro^{-0.11\pm 0.03} \;(\text{if}\; Ro < 0.13) 
+    B &= 199\,\text{G} \cdot R\rm o^{-1.26\pm 0.1} \;(\text{if}\; Ro > 0.13) \\
+    B &= 2050\,\text{G} \cdot R\rm o^{-0.11\pm 0.03} \;(\text{if}\; Ro < 0.13) 
 \end{eqnarray}
 
-The estimate is consistent with existing Zeeman broadening for, e.g. AU~Mic (3010 G~\cite{reiners2022magnetism}).
+The convective turnover time $\tau$ in  $R \rm o=P_{rot}/\tau$ is derived using bolometric luminosity~(Section~\ref{sec:data:lum}), following~\citet{reiners2014generalized, reiners2022magnetism}:
+
+\begin{equation}
+    \tau = 12.3\, \rm d \cdot (L_{\rm bol}/L_\odot)^{-1/2}
+\end{equation}
+
 \subsection{Power of star-planet interaction}
@@
 
-$B_p$ and $B_*$ are the total planetary and stellar surface field strengths, respectively; $v_{rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis $a$; and $R_*$ and $R_p$ are the stellar and planetary radii, respectively.
+$B_p$ and $B_*$ are the planetary and stellar field strengths at their poles, respectively; $v_{rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis $a$; and $R_*$ and $R_p$ are the stellar and planetary radii, respectively.
+Since the planetary fields are unknown, we ignore it in the calculations.
+Since we also do not know the stellar field strength at the pole for the vast majority of the stars, we adopt the surface field strength~(Section~\ref{sec:methods:bfield}) as a proxy.
 
@@
 
-Third, for comparison, we estimate the power of star-planet interaction generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio}, combining Eqs.~8~and~11 in \citet{kavanagh2022radio} to give
+Third, for comparison, we estimate the power of star-planet interaction generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio}, combining Eqs.~8~and~11 in \citet{kavanagh2022radio} to arrive at
 
@@
 \end{equation}
+
+Lacking $B_p$ and various additional factors that appear in $P_{sb},P_{sb0},P_{aw}$, and  $P_{aw0}$, such as the angle between the wind and the
 
@@
 In transiting multi-planet systems, the orbital phase refers to the innermost planet, with the transit mid-time at phase zero.
+The full catalog is available online (see Data Availability Statement).
         }
-    \footnote{Full catalog is available online (see Data Availability Statement).}
     \input{output/flare_table.tex}
@@
 Our custom Anderson-Darling test compares the measured distribution of orbital phases of the flares to the expected distribution, and return the significance of the deviation between the two.
-In the expected distribution, the same number of flares would be distributed randomly across all phases, as the overwhelming majority of studies looking for variation with rotational phase suggest~\citep[e.g.]{doyle2018investigating,howard2021evryflare}.
+In the expected distribution, the same number of flares would be distributed randomly across all phases, as the overwhelming majority of studies looking for variation with rotational phase suggest~\citep[e.g.][]{doyle2018investigating,howard2021evryflare}.
 Figures~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv} show the flare phase distributions along with the corresponding expected distributions for transiting and non-transiting systems, respectively.
@@
 We used the custom Anderson-Darling test introduced in~\citet{ilin2022searching} and Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three or more flares with equivalent duration $ED>1\,$s, detected in their Kepler and TESS observations.
-We choose the $ED$ cutoff to make sure that we are comparing similar flares regardless of spectral type, that is, flares with the same energy relative to stellar luminosity.
-We show the results that include all flares regardless of $ED$ in the appendix (XXXX TBD).
+We choose the $ED$ cutoff to make sure that we are comparing similar flares regardless of spectral type, that is, flares above the same energy relative to stellar luminosity, without losing too many flares.
+In~\citet{ilin2022}, AU Mic appeared to be more modulated with orbital period in the high energy flares above $1\,$s than below.
+It is also the only star in our sample, for which the threshold makes a difference in the significance of the Anderson-Darling test.
+However, we note that we lose four systems by applying this threshold -- GJ 393, Kepler-411, Kepler-138, and Kepler-1084.
+The flares (with $ED<1\,$s) in all of these systems are consistent with random flare phases within $1\sigma$.
 
@@
 It is a Sco-Cen member (10-20 Myr old), which was discovered to host a close-in Jupiter, HIP 67522 b, in 2020~\citep{rizzuto2020tess}.
-Curiously, the planet is in close spin-orbit commensurability -- $P_{rot}/P_{orb}=5/1$.
+Curiously, the planet is in close spin-orbit commensurability -- $P_{rot}/P_{\rm orb}=5/1$.
 Therefore, we cannot completely rule out that the observed periodicity is in fact a rotational periodicity, and not related to the planet.
@@
 However, for TAP 26 b, the orbital period might not be well-constrained.
-\citet{yu2017hot} apply several methods to derive $P_{orb}$ from the radial velocity data: While the $10.8\,$d orbit we adopted is the most likely according to \citet{yu2017hot}, a $9.0\,$d orbit is also likely, and some of their applied methods favored a $13.4\,$d period.
+\citet{yu2017hot} apply several methods to derive $P_{\rm orb}$ from the radial velocity data: While the $10.8\,$d orbit we adopted is the most likely according to \citet{yu2017hot}, a $9.0\,$d orbit is also likely, and some of their applied methods favored a $13.4\,$d period.
 The absence of interaction could hence be a consequence of uncertain orbital period.
@@
 \label{sec:discussion:viewing}
-\textcolor{red}{needs to be contrasted more with intermittency}
 The visibility of the magnetic interaction footpoint is crucial for the detection of flaring star-planet interactions in our analysis.
-The viewing geometry of the star-planet system is therefore important to consider.
+The viewing geometry of the star-planet system is therefore important to consider as an alternative to, or explanation for, the intermittency discussed above.
 Assuming for the sake of the argument that the sub-planetary point is close to the magnetic interaction footpoint in longitude, two factors will determine whether the footpoint's visibility will be modulated with the planetary orbit or not: the orbital inclination and the footpoint's latitude relative to it.
+
+Consider a system, where orbit, and stellar spin and stellar magnetic dipole are aligned.
 If the footpoint's latitude is low, i.e., close to the orbital plane, the orbital plane can be inclined to a high degree, and the footpoint will still periodically move in and out of view.
 However, if the footpoint's latitude is high, we need to observe the star-planet system nearly edge-on to be able to measure a modulation of activity with the planet's orbital phase.
-The latter can be the case when the dipole axis of the stellar large scale field is well-aligned with the orbital axis.
-In that case, assuming the dipole field dominates at the distance of the planet, the footpoint will be close to the pole, similar to the hot spot created by Io and the other moons in the polar cap of Jupiter.
+Assuming the dipole field dominates at the distance of the planet, the footpoint will be close to the pole, similar to the hot spot created by Io and the other moons in the polar cap of Jupiter~().
 In this scenario, many, especially non-transiting, systems may experience flaring star-planet interaction, but those would not show up as correlation of flare timing with the orbital phase in our data.
@@
 If the orbital plane is aligned with the stellar rotation axis, the absence of phase-correlated flaring in TAP 26 could be explained by the footpoint of interaction being always in view and therefore never modulated.
-Note that alignment between orbital, rotational and magnetic dipole axis is not generally given, with many pole-on orbiting planets~(XXXX), and stars with heavily mislaligned magnetic axes~(XXXX).
-So interpreting non-detections as effects of viewing geometry comes with a caveat.
+
+Alignment between orbital, rotational and magnetic dipole axis is not generally given.
+Many planets orbit their hosts nearly pole-on~\citep{albrecht2012obliquities, albrecht2022stellar, bourrier2023dream}.
+T Tauri stars show somewhat misaligned magnetic axes relative to their spin~\citep{mcginnis2020magnetic}.
+Moreover, the magnetic dipole axis location changes throughout the activity cycles of Sun-like stars~\citep{petit2009polarity,borosaikia2018direct}, which may cause temporary cessation of visibility.
+Orbital precession of misaligned planets can also cause such intermittency, if it periodically brings the footpoints trajectory on the stellar surface fully into view so that it is no longer modulated.
+Interpreting non-detections as effects of viewing geometry in fully aligned systems ignores this caveat.
 
@@
 
-\subsection{Spin-orbit commensurability}
-\label{sec:discussion:commensurability}
-Curiously, in our analysis, systems with high expected power are divided: Stars that show a correlation between excess flaring and expected power tend to have closer spin-orbit commensurability than systems that are far away from any low-integer ratio between rotational and orbital period.
-
-In Fig.~\ref{fig:spinorbit}, we split our sample into three categories.
-The first contains the systems where the expected interaction is lower than that in TOI-540, the system with the lowest power of interaction among those with relatively high flaring star-planet interaction signal (i.e., K2-25, TOI-540, HIP 67522, and AU Mic).
-The second includes the systems where a high power of interaction is expected, but none is measured (e.g., TAP 26, KOI-12).
-The final third category contains all system where the data suggest a correlation between expected power of interaction, but do not belong in the first category.
-We search for spin-orbit commensurability with integers $<10$ in each system, and plot the relative difference between the closest ratio and the actual spin-orbit ratio.
-Systems with low expected power of interaction span a wide range of spin-orbit commensurability.
-However, the second and third group form two separate populations.
-Non-interacting systems are further away from low-integer commensurability, than interacting ones, even though both have high expected power.
-A similar picture arises when the same sample split is applied to the other interaction scenarios.
-
-While chance alignment is possible, the division suggests that spin-orbit commensurability and magnetic star-planet interaction are related.
-Either something about our observing method favors the measurement of excess flaring in systems with close spin-orbit commensurability, or there is physical causation at play.
-In the latter case, the spin-orbit commensurability could be either an effect, or a cause, of measured magnetic star-planet interaction.
-
-Our method favors systems in which the deviation from uniform flare timing is concentrated in a narrow phase bracket of the planet's orbit.
-This might be the case in HIP 67522.
-Due to its low-order, 5:1 resonance, the sub-planetary point passes the same magnetic features at the same orbital phase each orbit.
-This is no longer the case for m:n ratios, where $n>1$.
-In those systems, the same surface feature is passed by the sub-planetary point at the same orbital phase every $m \cdot n$ orbits, if $m>n$ (which is true for all our systems with high expected power of interaction).
-For HIP 67522, the interaction signal may therefore be more strongly confined to certain orbital phases, while for systems with higher order commensurability, this effect dilutes.
-
-There could also be physical reasons for increased flaring interaction-in systems with close spin-orbit commensurability.
-\citet{lanza2022model} suggest that tidal torque of the planet on the star excites resonant oscillations in the interior stellar magnetic field, which in turn leads to a resonance between stellar spin and planetary orbit.
-These oscillations can lead to a surface pattern of emerging magnetic field that rotates with the spin-orbit commensurable period.
-Systems with spin-orbit resonance would then show clearer interaction signal, because the resonance would stabilize the pattern of regions with strong magnetic field that favor planet-induced flaring.
-The stable active regions might withstand the diluting effect of differential rotation~(see Section~\ref{sec:discussion:rotsyn}).
-However, the \citet{lanza2022model} requires tidal interaction, which may be too weak in systems like AU Mic~(see also Section~\ref{sec:discussion:tidal}), where the planet is too small and distant for the proposed effect, but that still show spin-orbit commensurability and signs of flaring star-planet interaction.
-
-While in~\citet{lanza2022model}, resonant oscillations favor flaring star-planet interaction observability, there might also be physical effects where the magnetic torque causes the spin-orbit resonance in the first place.
-The connection here is: In regions where there is strong enough magnetic torque that causes spin-orbit resonance, there would also be flaring star-planet interaction.
-
-\citet{szabo2021changing} conjecture that many systems within the sparsely populated region of close-in planets around rapid rotators~\citep{mcquillan2013stellar} seem close to low-integer spin-orbit resonance.
-However, proximity to spin-orbit resonance is sensitive to the highest integer included in the calculation.
-If we choose the maximum low integer for m or n to be smaller than 10 the pattern in Fig.~\ref{fig:spinorbit} disappears.
-If we choose it to be larger than 10, XXXX.
-
-\begin{figure}[t]
-    \script{paper_spin_orbit_commensurability.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/PAPER_spin_orbit_commensurable_p_spi_sb_bp1_norm.png}
-        \caption{
-           \textbf{Top panel}: Same as the bottom left panel in Fig.~\ref{fig:adtest_bp}, but color coded as below.
-\textbf{Bottom panel:} Spin-orbit commensurability compared to flaring star-planet interaction signal.
-The lower the p-value of the AD test, the stronger the interaction signal.
-Lower relative difference between the measured spin-orbit ratio and the integer ratio closest to it indicates a tighter spin-orbit commensurability.
-We include only ratios of integers $<10$.
-\textbf{Black diamonds:} All systems with p-values lower than that of K2-25, and expected power of interaction equal or higher than TOI-540's, the active 'SPI on' branch~(see top left panel in Fig.~\ref{fig:adtest_bp}).
-\textbf{Red crosses:} The complementary 'SPI off' branch includes all systems with expected power of interaction above that of TOI-540, but with p-values below that of K2-25.
-\textbf{Blue circles:} The remaining systems include all with expected power of interaction below that of TOI-540.
-Among the systems with high expected power, those with higher interaction signal ('SPI on') show closer spin-orbit commensurability than those on the inactive 'SPI off' branch.
-        }
-        \label{fig:spinorbit}
-    \end{centering}
-\end{figure}
-
 \subsection{Tidal interaction}
@@
         \includegraphics[width=\hsize]{figures/PAPER_tidal_AD_test.png}
-        \caption{Deviation from random flare times in phase with $P_{orb}/2$, i.e., in phase with tidal bulges raised on the star, compared to different models of tidal interaction.
+        \caption{Deviation from random flare times in phase with $P_{\rm orb}/2$, i.e., in phase with tidal bulges raised on the star, compared to different models of tidal interaction.
            \textbf{Left panel}: The tidal torque in the system for stars with a convective envelope.
@@
 \script{paper_table_tidal.py}
-\caption{Flaring tidal star-planet interaction. }
+\caption{Flaring tidal star-planet interaction parameters and $p$-value of the custom Anderson-Darling test. }
 \input{output/table_tidal.tex}
@@
 
+\subsubsection{Locally expressed tidal interaction}
 Tidal interaction can also lead to enhanced activity, globally, and locally.
-Locally, we expect to see periodicity with half the orbital period of the planet, corresponding to the two tidal bulges forming in the stellar envelope~\citep{cuntz2000stellar}.
-There are neither detailed models to describe how that process leads to enhanced activity, or excess flaring, in star-planet systems, nor are there existing observations.
+Locally, we expect to see a periodicity with half the orbital period of the planet, corresponding to the two tidal bulges forming in the stellar envelope~\citep{cuntz2000stellar}.
+\citet{holzwarth2003dynamics} suggest an asymmetry induced in the stellar dynamo by the tidal disturbance, which leads to a preference for active (flaring) regions at longitudes about $P_{\rm orb}/2$ apart from each other.
+
+No observations of local tidal star-planet interaction exist yet.
 However, in the extreme case of RS CVn binaries, starspots often appear modulated with half the orbital period of the system~\citep{olah2002time, ozavci2018recurrent, kriskovics2023ei}.
 A similar effect was measured when the companion was likely a very low mass star or a brown dwarf~\citep{donati1995activity, frasca2008spots, parks2021interferometric}, and in the case of a white dwarf companion~\citep{hussain2006spot, watson2007roche}.
-In ellipsoidal binaries, a modulation of flares beyond geometrical effects was observed with Kepler~\citep{gao2016whitelight}, suggesting flaring regions at the location of the extreme tidal bulges in these stars.
-However, all these systems are synchronized, $P_{rot}=P_{orb}$, so that intrinsic active longitudes~\citep{usoskin2007longterm, weber2013theory, jarvinen2005spots, lanza2009corot} cannot be disambiguated from the result of tidal star-star interaction ~\citep{holzwarth2003dynamics}.
-In that framework, we can decrease the companion mass to arrive at local, tidal star-planet interaction, for which, in our sample, spin and orbit are not synchronized.
-In analogy to~\citet{holzwarth2003dynamics}, we can picture an asymmetry induced in the stellar dynamo by the tidal disturbance, which leads to a preference for flares at longitudes about $P_{orb}/2$ apart from each other.
+In ellipsoidal binaries, a modulation of flares with $P_{\rm orb}/2$ beyond geometrical effects was observed with Kepler~\citep{gao2016whitelight}, suggesting flaring regions at the location of the extreme tidal bulges in these stars.
+However, all these systems are synchronized, $P_{rot}=P_{\rm orb}$, so that intrinsic active longitudes~\citep{usoskin2007longterm, weber2013theory, jarvinen2005spots, lanza2009corot} cannot be disambiguated from the result of tidal star-star interaction ~\citep{holzwarth2003dynamics}.
 
-\subsubsection{Comparison to tidal interaction scaling laws}
+If the observed effects are due to the tidally interacting companion, planets should do the same to their host, albeit at a smaller magnitude.
+Fortunately, spin and orbit are not synchronized in our sample, so confusion with intrinsic effects is less likely.
 
-We cannot tell whether an additional individual flare is produced by tidal or magnetic interaction, but we can look for deviations from a random distribution of flare times in phase with the relevant period, i.e., $P_{orb}/2$.
+\subsubsection{Tidal interaction scaling laws}
+
+We cannot tell whether an additional individual flare is produced by tidal or magnetic interaction, but we can look for deviations from a random distribution of flare times in phase with the relevant period, i.e., $P_{\rm orb}/2$.
 
@@
 
-The first model measures the torque $\partial L / \partial t$, exerted by angular momentum transfer from star to planet or from planet to star, assuming the star has a convective envelope~(\citealt{penev2012constraining}, their Eqns.
+The first model measures the torque $\partial L_{\rm conv} / \partial t$, exerted by angular momentum transfer from star to planet or from planet to star, assuming the star has a convective envelope~(\citealt{penev2012constraining}, their Eqns.
 1 and 2).
@@
 We find that no single system shows significant signs of tidal star-planet interaction.
-Overall, the signal in phase with $P_{orb}/2$ is smaller than with $P_{orb}$.
+Overall, the signal in phase with $P_{\rm orb}/2$ is smaller than with $P_{\rm orb}$.
 However, in all three scenarios, the sample's deviation from random flare timing increases with expected tidal interaction strength.
@@
 
-\paragraph{KOI-12,} which lacks signal with $P_{orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction.
+\paragraph{KOI-12,} which lacks signal with $P_{\rm orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction.
 This could be interpreted as KOI-12 b orbiting outside the Alfv\'en radius, unable to interact magnetically, but tidally.
@@
 
-\paragraph{Kepler-42 and TOI-540} Kepler-42 is neither expected to interact magnetically, nor did it show any deviation from random flare timing in phase with $P_{orb}$.
+\paragraph{Kepler-42 and TOI-540} Kepler-42 is neither expected to interact magnetically, nor did it show any deviation from random flare timing in phase with $P_{\rm orb}$.
 However, since it is the system with the shortest planetary orbit in our sample, it is both expected to and does show marginal signal of tidal interaction.
@@
 As multiple observations can be combined regardless of the gaps in time between individual campaigns with our method, we will become able to sensitively constrain the magnitude of interaction, and the relative contributions from tidal and magnetic SPI.
+
+\subsection{Spin-orbit commensurability}
+\label{sec:discussion:commensurability}
+Curiously, in our analysis, systems with high expected power are divided: Stars that show a correlation between excess flaring and expected power tend to have closer spin-orbit commensurability than systems that are far away from any low-integer ratio between rotational and orbital period.
+
+In Fig.~\ref{fig:spinorbit}, we split our sample into three categories.
+The first contains the systems where the expected interaction is lower than that in TOI-540, the system with the lowest power of interaction among those with relatively high flaring star-planet interaction signal (i.e., K2-25, TOI-540, HIP 67522, and AU Mic).
+The second includes the systems where a high power of interaction is expected, but none is measured (e.g., TAP 26, KOI-12).
+The final third category contains all system where the data suggest a correlation between expected power of interaction, but do not belong in the first category.
+We search for spin-orbit commensurability with integers $<10$ in each system, and plot the relative difference between the closest ratio and the actual spin-orbit ratio.
+Systems with low expected power of interaction span a wide range of spin-orbit commensurability.
+However, the second and third group form two separate populations.
+Non-interacting systems are further away from low-integer commensurability, than interacting ones, even though both have high expected power.
+A similar picture arises when the same sample split is applied to the other interaction scenarios.
+
+While chance alignment is possible, the division suggests that spin-orbit commensurability and magnetic star-planet interaction are related.
+Either something about our observing method favors the measurement of excess flaring in systems with close spin-orbit commensurability, or there is physical causation at play.
+
+In the latter case, the spin-orbit commensurability could be either an effect, or a cause, of measured magnetic star-planet interaction.
+\citet{lanza2022model} suggest that tidal torque of the planet on the star excites resonant oscillations in the interior stellar magnetic field, which in turn leads to a resonance between stellar spin and planetary orbit.
+These oscillations can lead to a surface pattern of emerging magnetic field that rotates with the spin-orbit commensurable period.
+Systems with spin-orbit resonance would then show clearer interaction signal, because the resonance would stabilize the pattern of regions with strong magnetic field that favor planet-induced flaring.
+\citet{szabo2021changing} conjecture that many systems within the sparsely populated region of close-in planets around rapid rotators~\citep{mcquillan2013stellar} seem close to low-integer spin-orbit resonance.
+However, proximity to spin-orbit resonance is sensitive to the highest integer included in the calculation.
+If we choose the maximum low integer for m or n to be smaller than 10 the pattern in Fig.~\ref{fig:spinorbit} disappears.
+
+We therefore favor the observational bias explanation: Only fast rotating stars can be close to a low integer spin-orbit commensurability with a planet in a few days long orbit.
+Incidentally, only fast rotating stars can have strong enough magnetic fields to put their planets in the sub-Alfv\'enic zone.
+A comparison with the tidal interaction scenarios, where we do not expect to be biased towards fast rotating stars, further supports this conclusion: No clustering in spin-orbit commensurability appears for any tidal interaction scenario.
+
+\begin{figure}[t]
+    \script{paper_spin_orbit_commensurability.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/PAPER_spin_orbit_commensurable_p_spi_sb_bp1_norm.png}
+        \caption{
+           \textbf{Top panel}: Same as the bottom left panel in Fig.~\ref{fig:adtest_bp}, but color coded as below.
+\textbf{Bottom panel:} Spin-orbit commensurability compared to flaring star-planet interaction signal.
+The lower the p-value of the AD test, the stronger the interaction signal.
+Lower relative difference between the measured spin-orbit ratio and the integer ratio closest to it indicates a tighter spin-orbit commensurability.
+We include only ratios of integers $<10$.
+\textbf{Black diamonds:} All systems with p-values lower than that of K2-25, and expected power of interaction equal or higher than TOI-540's, the active 'SPI on' branch~(see top left panel in Fig.~\ref{fig:adtest_bp}).
+\textbf{Red crosses:} The complementary 'SPI off' branch includes all systems with expected power of interaction above that of TOI-540, but with p-values below that of K2-25.
+\textbf{Blue circles:} The remaining systems include all with expected power of interaction below that of TOI-540.
+Among the systems with high expected power, those with higher interaction signal ('SPI on') show closer spin-orbit commensurability than those on the inactive 'SPI off' branch.
+        }
+        \label{fig:spinorbit}
+    \end{centering}
+\end{figure}
 
@@
 
-Although no individual system shows flaring star-planet interaction on a significant level, the ensemble result is still curious.
-In particular, the two branches form two separate populations on another dimension.
-Systems on the correlated branch are closer to spin-orbit commensurability with low-integer ratios than their non-interacting counterparts.
-If this interaction is causal, either magnetic-star planet interaction traps star-planet systems in these resonances, or the excitement of these resonances -- tidally or magnetically -- favors the presence of flaring clustered in orbital phase.
+We also searched the same data for signs of locally expressed tidal interaction, that is, excess flaring in phase with the tidal bulges ($P_{\rm orb}/2$).
+We found a similar trend with different scaling laws of tidal interaction, albeit at even lower significance.
+Our system-by-system comparison suggests that young systems, like HIP 67522, may interact both tidally and magnetically, whereas old, magnetically inactive systems, like Kepler-42, might mostly interact tidally.
 
-Our study is the first that systematically searched for flaring star-planet interactions, and is not limited by sampling or selection bias in the way earlier studies of this effect have been~(XXXX).
+Our study is the first that systematically searched for flaring star-planet interactions, and is not limited by sampling or selection bias in the way earlier studies of this effect have often been.
 While our results remain tentative, future studies using our technique will benefit from accumulating data.
@@
 
-Close-in planets around young, active stars are being explored as in-situ probes of the dynamic magnetic field~(XXXX), and stellar mass loss~\citep{vidotto2017exoplanets} conditions in their orbit.
+Close-in planets are being explored as in-situ probes of the dynamic magnetic field~\citep{trigilio2023starplanet}, and stellar mass loss~\citep{vidotto2017exoplanets} conditions in their orbit.
 They are two key components of the space weather that a potentially habitable planet will encounter.
-The orbital distances where sub-Alfv\'enic interaction can take place, are usually closer to the star than its habitable zone.
-However, in late M dwarfs like TRAPPIST-1, these two regions overlap~\citep{strugarek2021physics}, and information from closer in for earlier spectral types is still crucial (or else why would we send probes to the Sun?).
+The orbital distances, where sub-Alfv\'enic interaction can take place, are usually closer to the star than its habitable zone.
+However, in late M dwarfs like TRAPPIST-1, these two regions overlap~\citep{strugarek2021physics}, and information from closer in for earlier spectral types is still crucial to reliably model the magnetic environment of further out terrestrial planets.
 We only begin to uncover the invaluable information that close-in planets can provide about the ever-changing environment of habitable-zone terrestrial planets.
+
+\section*{Acknowledgements}
+This paper includes data collected by the TESS mission, which are publicly available from the Mikulski Archive for Space Telescopes (MAST).
+Funding for the TESS mission is provided by NASA’s Science Mission directorate. 
+This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
+Funding for the DPAC
+has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
+%follow instructions here https://gea.esac.esa.int/archive/documentation/GEDR3/Miscellaneous/sec_credit_and_citation_instructions/
+\section*{Data Availability}
+All analysis script can be found under https://github.com/ekaterinailin/flaring-spi/. All data and scripts used to creat the tables and figures in this paper can be found under
 

### 2023-05-17 src/scripts/paper_adtest_vs_value_scatterplots.py
ro vs. pvalue and correct error bar in main table

@@ -68,6 +68,40 @@ def colorcode_dist(dist):
 
     return color, symbol
 
+
+def colorcode_rossby(ro):
+    """Define color code and symbol marker for rotation period.
+
+    Parameters
+    ----------
+    ro : float
+        Rossby number.
+
+    Returns
+    -------
+    color : str
+        Color code.
+    marker : str
+        Symbol marker.
+    """
+    if ro < 1e-2:
+        color = "green"
+        symbol = "o"
+
+    elif (ro >= 1e-2) & (ro < 0.3):
+        color = "blue"
+        symbol = "x"
+
+    elif (ro >= 0.3) & (ro < 1.):
+        color = "black"
+        symbol = "d"
+
+    elif (ro >= 1.):
+        color = "lightgrey"
+        symbol = "s"
+
+    return color, symbol
+
 def colorcode_rotation(st_rotp):
     """Define color code and symbol marker for rotation period.
 
@@ -425,6 +459,47 @@ if __name__ == "__main__":
 
     # save the figure
     plt.savefig(paths.figures / f"PAPER_ADtest_bg.png", dpi=300)
+
+
+
+
+    # ------------------------------------------------------------
+    # ROSSBY NUMBER
+    # ------------------------------------------------------------
+
+    # define the colors and symbols for the different distance bins
+    df["color"], df["symbol"] = zip(*df.Ro.apply(colorcode_rossby))
+    
+    valuelegend = [Line2D([0], [0], marker='o', color='w',
+                   markerfacecolor='green', markersize=10),
+                   Line2D([0], [0], marker='X', color='w',
+                   markerfacecolor='blue', markersize=10),
+                   Line2D([0], [0], marker='d', color='w',
+                   markerfacecolor='black', markersize=10),
+                   Line2D([0], [0], marker='s', color='w',
+                   markerfacecolor='lightgrey', markersize=10),]
+
+    valuelabels = [ "Ro < .01","0.01 < Ro < 0.3","0.3 < Ro < 1","Ro > 1",]
+
+    # set up figure
+    fig, axes = plt.subplots(nrows=2, ncols=2, figsize=(16, 10))
+
+    # make one list of all axes
+    axes = axes.flatten()
+
+    for value, valuelabel, ax in list(zip(columns, xlabels, axes)):
+        if value=="p_spi_sb_bp1_norm":
+            leg = True
+        else:
+            leg = False
[…]

### 2023-05-17 src/scripts/paper_main_table.py

@@ -163,9 +163,9 @@ def tex_up_low(val, err, err2):
     return ("$" +
             convert_to_scinote(val) +
             "^{" + 
-            convert_to_scinote(err) + 
+            convert_to_scinote(err - val) + 
             "}_{" +
-            convert_to_scinote(err2) + "}$")
+            convert_to_scinote(val - np.abs(err2)) + "}$")
 
 def tex_one_err(val, err):
     """Convert a value and one error into a LaTeX string.

### 2023-05-17 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-%It was found with low obliquity, consistent with XXXX~\citep{heitzmann2021obliquity}. Tentative third planet transiting.
+%It was found with low obliquity, consistent with ~\citep{heitzmann2021obliquity}. Tentative third planet transiting.
 %The system's $a/R_*\approx11.7$, eccentricity below .25~\cite{rizzuto2020tess}, so that  
@@
 Any realistic number of active regions (one or more), a wide range of degrees of differential rotation (from rigid rotator to solar-type), and half-life duration of active regions (day to years) are acceptable, because the observed effect depends predominantly on the visibility of the footpoint, which is governed by orbital motion.
-The latter is much more stable over long periods of time than the intrinsically dynamic magnetic field configuration.
-\textcolor{red}{add some references}
+The latter is much more stable over long periods of time than the intrinsically dynamic magnetic field configuration~(see e.g., various works on spot lifetimes in low mass stars~\citealt{giles2017kepler,davenport2015spots, namekata2019lifetimes}).
 
@@
 Magnetic star-planet interaction power in a given system may sometimes be low for episodes of time, and high for others.
-HD 179949 is the prototype example for this phenomenon, wherein the orbital modulation of chromospheric indicators was observable for XXXX out of XXXXX epochs on XXXX years baseline~\citep{shkolnik2003evidence,shkolnik2008nature}.
+HD 179949 is the prototype example for this phenomenon, wherein the orbital modulation of chromospheric indicators was observable for four out of six epochs on a five year baseline~\citep{shkolnik2003evidence,shkolnik2008nature}.
 It is not clear how long a continuous epoch of interaction or non-interaction might be.
@@
 
-If the magnetic field of the planet also changes over time, this might modulate the intensity as well~[e.g.]\citep{turnpenney2018exoplanetinduced}.
+If the magnetic field of the planet also changes over time, this might modulate the intensity as well~\citep[e.g.][]{turnpenney2018exoplanetinduced}.
 
@@
 This could span multiple orbits of the planet, particularly when the surface is populated by few stable active regions, and the orbital and rotational periods are similar.
-The flip-flop behavior of active longitudes seen in young solar-like stars~(XXXX) could then cause a relatively sudden quenching of interaction by moving the interacting region out of view for a period of time.
+The flip-flop behavior of active longitudes seen in young solar-like stars~\citep{berdyugina2005starspots} could then cause a relatively sudden quenching of interaction by moving the interacting region out of view for a period of time.
 

### 2023-05-17 src/scripts/paper_lx_plots.py
Lx plots added

@@ -1,0 +1,85 @@
+"""
+Python 3.8 -- UTF-8
+
+Ekaterina Ilin, 2023, MIT License
+
+Script that generates the figures that compare the X-ray luminosity of the
+sources in the sample to the Rossby number and magnetic field strength.
+"""
+
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+from astropy.constants import L_sun
+
+import paths
+
+import adjustText as aT
+
+if __name__ == "__main__":
+
+    # convert L_sun to erg/s
+    L_sun = L_sun.to('erg/s').value
+
+    # read in the data
+    df = pd.read_csv(paths.data / 'results.csv')
+
+    # calculate Lx/Lbol
+    lxlbol = df.xray_flux_erg_s/10**df.st_lum/L_sun
+
+    # error propagation
+    lxlbol_err = lxlbol * np.sqrt((df.xray_flux_err_erg_s/df.xray_flux_erg_s)**2 +
+                                  ((df.st_lumerr1-df.st_lumerr2)/2./df.st_lum)**2)
+    
+    # make the plot
+    fig, [ax1, ax2] = plt.subplots(ncols=1, nrows=2, figsize=(6,9))
+
+
+    # ---------------------------------------------------------------------
+    # Upper panel: Lx vs Ro
+
+    ax1.errorbar(df.Ro, lxlbol, xerr=[df.Ro - df.Ro_low, df.Ro_high - df.Ro],
+                yerr=lxlbol_err, markersize=8, fmt="d")
+    
+    # annotate with ID
+    txts = []
+    for i, row in df.iterrows():
+        txt = ax1.annotate(row.ID, (row.Ro, lxlbol[i]), fontsize=11)
+        txts.append(txt)
+
+    # layout
+    ax1.set_xlabel('Rossby number', fontsize=14)
+    ax1.set_ylabel(r'$L_X/L_{bol}$', fontsize=14)
+    ax1.set_xscale('log')
+    ax1.set_yscale('log')
+
+    # adjust text positions
+    aT.adjust_text(txts, arrowprops=dict(arrowstyle="-", color='k', lw=0.5),
+                   ax=ax1)
+
+    # ---------------------------------------------------------------------
+    # Lower panel: Lx vs B
+
+    ax2.errorbar(df.B_G, lxlbol, markersize=8, 
[…]

### 2023-05-17 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \end{equation}
+
+We compared our derived values for $Ro$ and $B$ with existing estimates of coronal emission from~\citet{foster2022exoplanet}.
+We show $L_X/L_{\rm bol}$ as a function of $Ro$ and $B$ in Fig.~\ref{fig:lx}.
+The X-ray emission relation to Rossby number in our sample follows that of stars that are not known to host close-in planets~\citep{wright2011stellaractivityrotation}, spanning both the saturated and unsaturated regime.
+The X-ray emission and our estimated magnetic field closely follow each other, also consistent with stars without known close-in planets~(XXXX).
+There are two exceptions: GJ 3082 appears underluminous in X-ray compared to its Rossby number and expected magnetic field strength.
+AU Mic is slightly overluminous, falling somewhat above the saturated level of $L_X/L_{\rm bol}$.
+However, the star still follows the $B-L_X/L_{\rm bol}$ relation.
+
+\begin{figure}[ht!]
+    \script{paper_lxl_plots.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/PAPER_lxlbol.png}
+        \caption{
+           X-ray luminosity over bolometric luminosity compared to Rossby number (\textbf{upper panel}), and surface magnetic field strength (\textbf{lower panel}).
+Both relations follow those of stars not selected for hosting close-in planets, except for GJ 3323, which is underluminous for its Rossby number, and hence also its estimated magnetic field strength.
+        }
+        \label{fig:coherence_hist}
+    \end{centering}
+\end{figure}
 
@@
 We note that we found K2-354 under EPIC 211314705 and K2-329(!) in \cite{bouma2020cluster}, who refer to the detection paper \cite{pope2016transiting}, and also under TIC 468989066.
+
+\section{Expected power vs. AD test, colorcoded by Rossby number}
+\begin{figure*}[ht!]
+    \script{paper_adtest_vs_value_scatterplots.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_bg.png}
+        \caption{
+        Expected power of SPI vs.
+AD test results, assuming the same four different scenarios as in Fig.~\ref{fig:adtest_bp}, color-coded by Rossby number.
+$R\rm o=0.3$ is chosen to mark the transition from the saturated ($R\rm o < 0.3$) to the unsaturated ($R\rm o > 0.3$) activity regime.
+        }
+        \label{fig:adtest_bp}
+    \end{centering}
+\end{figure*}
+
 \end{document}

### 2023-05-19 src/scripts/paper_lx_plots.py
added wright and reiners data, and some string formatting

@@ -11,10 +11,54 @@ import numpy as np
 import matplotlib.pyplot as plt
 import pandas as pd
 from astropy.constants import L_sun
+from astropy.table import Table
 
 import paths
 
 import adjustText as aT
+
+
+def tau_wright2018(V, Ks, err=False, eV=None, eKs=None):
+    """Convective turnover time from Wright et al. 2018 using
+    Eq. 5 from that paper.
+
+    Parameters
+    ----------
+    V : float
+        The V magnitude of the star.
+    Ks : float
+        The Ks magnitude of the star.
+    err : bool, optional
+        If True, return the error on the Rossby number.
+        The default is False.
+    eV : float, optional
+        The error on the V magnitude of the star.
+        The default is None.
+    eKs : float, optional
+        The error on the Ks magnitude of the star.
+        The default is None.
+
+    Returns 
+    -------
+    tau : float
+        The convective turnover time of the star.
+    tau_err_high : float
+        The upper error on the convective turnover time.
+    tau_err_low : float
+        The lower error on the convective turnover time.
+
+    """
+
+    tau = 0.64 + 0.25 * (V - Ks)
+
+    if err:
+        tau_err_high = 0.74 + 0.33 * (V + eV - Ks + eKs)
+        tau_err_low = 0.54 + 0.17 * (V - eV - Ks - eKs)
+        return 10**tau, 10**tau_err_high, 10**tau_err_low
+    else:
+        return 10**tau
+
+
 
 if __name__ == "__main__":
 
@@ -38,6 +82,17 @@ if __name__ == "__main__":
     # ---------------------------------------------------------------------
     # Upper panel: Lx vs Ro
 
+
+    # read Wright et al. 2011 data
+    wright2011 = Table.read(paths.data / "wright2011.fit")
+    wright2011["tau"] = tau_wright2018(wright2011["Vmag"], wright2011["Vmag"] - wright2011["V-K"])
+    wright2011["Ro"] = wright2011["Prot"] / wright2011["tau"]   
+
+        
+    # Wright et al. 2011 data
+    ax1.scatter(wright2011["Ro"].value, 10**wright2011["Lx_bol"].value,
+                label="Wright et al. 2011", c="grey", zorder=-10, marker="x", alpha=0.2)
+
[…]

### 2023-05-19 src/scripts/paper_main_table.py

@@ -420,6 +420,7 @@ if __name__ == "__main__":
     for key in bibkeys.keys():
         bibstring += "(" + str(bibkeys[key]) + ") \citet{" + key + "}, "
     
+    bibstring = bibstring[:-2] + "."
    
     # write the bibstring to a file
     path = paths.output / "lit_table_bibstring.tex"

### 2023-05-19 src/scripts/paper_string_multiple_stars.py

@@ -27,6 +27,8 @@ if __name__ == "__main__":
     multiples = multiples.ID + multiples.multiple_star_source
     multiples = ", ".join(multiples)
 
+    multiples = multiples[:-2] + "."
+
     # write to file
     print("Write to file ", paths.output / "multiples_string.tex")
     with open(paths.output / "multiples_string.tex", "w") as f:

### 2023-05-19 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Title
-\title{Flaring star-planet interactions in star-planet systems in Kepler and TESS}
+\title{Flaring star-planet interactions in Kepler and TESS}
 
@@
 
-Our goal was to measure magnetic star-planet interaction as the presence of excess flares in phase with the innermost planet's orbit.
+Our goal was to measure magnetic star-planet interaction as the statistical clustering of flares in phase with the innermost planet's orbit.
 We searched all star-planet systems that were observed with Kepler and TESS at 1 or 2 min cadence, respectively, for flares.
 For the star-planet systems in the resulting flare catalog~(Section~\ref{sec:results:catalog}), we confirmed that the orbital phase could be known well enough for the entire observing baseline of the system~(Section~\ref{sec:results:coherence}).
-Knowing that, we could calculate the orbital phases of each flare, and the flare phase distributions for each system~(Section \ref{sec:results:phasedist}).
-We then applied the custom Anderson-Darling test to check how much each distribution was different from randomly distributed intrinsic flaring.
+We calculated the orbital phases of each flare, and the flare phase distributions for each system~(Section \ref{sec:results:phasedist}).
+We then applied the custom Anderson-Darling test to assess how much each distribution was different from randomly distributed intrinsic flaring.
 Comparing the test results with the expected power of magnetic star-planet interaction, we found that the amount of excess flaring tentatively increases with the expected power in all considered scenarios~(Section~\ref{sec:results:spi}).
-However, not all systems with high expected power show signs of flaring SPI, which appears as a branching in the distribution of test results.
-To prepare the subsequent discussion, we provide additional context for the most interesting systems in our sample, and explain why we had to exclude some systems from the analysis in Section~\ref{sec:results:individualstars}.
+However, not all systems with high expected power show signs of flaring SPI, which creates two branches in the distribution of test results.
+Finally, in Section~\ref{sec:results:individualstars}, we provide additional context for the most interesting systems in our sample, and explain why we had to exclude others from the analysis.
+
 \subsection{Flare catalog}
@@
 We searched a total of 3032 Kepler Quarters and 4181 TESS Sectors of a total of 1811 star-planet systems for flares.
-We inspected all candidates manually, and added flares observed by K2 on TRAPPIST-1~\cite{paudel2018k2}, and flares from the planet hosting primary in the Kepler-411 binary~\cite{jackman2021stellara}.
-The final table contains a total of \input{output/PAPER_total_number_of_flares.txt} flares in \input{output/PAPER_total_number_of_systems_with_flares.txt} systems.
-In Table~\ref{tab:flares}, we list all the flares and their characteristics.
+We inspected all candidates manually, and added flares observed by K2 on TRAPPIST-1~\citep{paudel2018k2}, and flares from the planet hosting primary in the Kepler-411 binary~\citep{jackman2021stellara}.
+The final table contains a total of \input{output/PAPER_total_number_of_flares.txt}flares in \input{output/PAPER_total_number_of_systems_with_flares.txt}systems.
+In Table~\ref{tab:flares}, we list the flares and their characteristics.
 To identify each event, we provide the name of the system in which the flare was found, along with its TIC, whether it was observed with Kepler or TESS, and during what Quarter or Sector, respectively.
@@
 In these cases, the orbital period of the innermost planet must be known very precisely so that we can assign accurate orbital phases to the flare events.
-We test this by dividing the timespan between the first and the last flare in the combined Kepler and TESS observations by the coherence time $\tau$ of the orbital period for each system.
+We test this by dividing the timespan $\Delta T$ between the first and the last flare in the combined Kepler and TESS observations by the coherence time $\tau$ of the orbital period for each system.
 We calculate the coherence time as
@@
 where $P$ is the orbital period, and $\sigma_P$ is its uncertainty.
-If the orbital period is well-known, the resulting ratio should be $<<1$.
-The bottom panel in Figure~\ref{fig:coherence_hist} shows a histogram of these ratios in our sample.
-The orbital period is known sufficiently well for our analysis in most cases with ratios $<0.02$, that is, the orbital phase of last flare is at most $2\%$ off, compared to the first.
+If the orbital period is well-known, the resulting ratio $\Delta T/\tau$ should be $<<1$.
+The bottom panel in Figure~\ref{fig:coherence_hist} shows a histogram of $\Delta T/\tau$ in our sample.
+The orbital period is known sufficiently well for our analysis in most cases with ratios $<0.02$, that is, the orbital phase of the last flare is at most $2\%$ off, compared to the first.
 The three cases where the ratio is highest with $0.05$, $0.12$, $0.24$ deviation are TAP 26, GJ 3082, and GJ 674, respectively.
@@
 
-We repeated the coherence calculation for $P_{rot}$, and found that the ratio is $>0.1$ for most stars~(Figure~\ref{fig:coherence_hist}, top panel).
-There are three reasons for this: First, the uncertainty for the rotation was not always provided, in which case we assigned a $10\%$ error.
+We repeated the coherence calculation for $P_{rot}$, and found that the ratio is $>0.1$ for most stars~(Figure~\ref{fig:coherence_hist}, top panel), so that a statistical analysis of rotational flare modulation is not feasible.
+
+\citet{fischer2019timevariable} argue that the synodic period, at which the sub-planetary point crosses the same (magnetic) surface element on the star, may result in a clearer interaction signal, because a magnetically active region that is prone to planet-induced flares, will be passed only once per that period.
+However, the uncertainty in $P_{\rm rot}$ does not allow us to search for modulation with synodic period.
+We argue, however, that in a transiting system with high orbital inclination, the effect with synodic period reduces to modulation with the orbital period:
+
+If the orbital axis inclination is high, then the passage will regularly occur on the back of the star relative to the observer.
+The true period will therefore be additionally modulated by the visibility, resulting in an intermittency of the signal.
+As a consequence, to detect a modulation with the synodic period, a significantly longer observing baseline is needed than to detect a modulation with the orbital period.
+Additionally, if there are many active regions (at the same time, or in sequence) that produce flares when the sub-planetary footpoint passes across, the effect with the synodic period further converges to a modulation with orbital period.
+In our sample, the observing baseline is multiple years long for many systems.
+Most stars, even the most rigidly rotating late M dwarfs, show variability in their spot modulation on such long timescales~\citep[e.g.,][]{giles2017kepler,davenport2015spots, namekata2019lifetimes}).
+
+% Even if differential rotation was absent and active regions were extremely stable, we would likely be unable to observe the passage of the sub-planetary point over the flare-prone region every synodic period.
+
+%However, this assumes that the landscape of active regions on the star is stable throughout the entire observing time, and that the number of such regions in the footpoint passageway is low enough to produce a periodic modulation.
+Note that this is a different effect from the geometrical modulation of visibility we look for in modulation with the orbital period in this study.
+
+%Even for the few stars, for which the rotational period is known precisely enough, we need to make numerous assumptions.
+These include the number of active regions crossed by the footpoint of interaction, differential rotation, spot evolution, and a significant correlation between the location of the planet and the location of the planet-induced flare on the stellar surface.
+For modulation with the orbital period, we require only that last correlation between footpoint location and orbital phase.
+
+%There are three reasons for this: First, the uncertainty for the rotation was not always provided, in which case we assigned a $10\%$ error.
 Second, rotation period is more difficult to ascertain from a light curves' variability than the orbital period, particularly if the modulation is weak and/or rapidly evolving.
@@
 \label{sec:results:phasedist}
-Our custom Anderson-Darling test compares the measured distribution of orbital phases of the flares to the expected distribution, and return the significance of the deviation between the two.
-In the expected distribution, the same number of flares would be distributed randomly across all phases, as the overwhelming majority of studies looking for variation with rotational phase suggest~\citep[e.g.][]{doyle2018investigating,howard2021evryflare}.
+Our custom Anderson-Darling test compares the measured distribution of orbital phases of the flares to the expected distribution, and returns the significance of the deviation between the two.
+In the expected distribution, the same number of flares would be distributed randomly across all phases, as the overwhelming majority of studies looking for variation with rotational phase suggest~\citep[see, e.g.,][]{doyle2018investigating,howard2021evryflare}.
 Figures~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv} show the flare phase distributions along with the corresponding expected distributions for transiting and non-transiting systems, respectively.
-The expected distributions usually deviate from a straight line because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different flare rates in each light curve.
+The expected distributions usually deviate from a straight line because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different flare rates in each light curve, which arise due to varying noise levels between individual Quarter/Sectors, and Kepler and TESS.
 
@@
 \label{sec:results:spi}
-We used the custom Anderson-Darling test introduced in~\citet{ilin2022searching} and Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three or more flares with equivalent duration $ED>1\,$s, detected in their Kepler and TESS observations.
+We used the custom Anderson-Darling test introduced in Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three or more flares with equivalent duration $ED>1\,$s, detected in their Kepler and TESS observations.
 We choose the $ED$ cutoff to make sure that we are comparing similar flares regardless of spectral type, that is, flares above the same energy relative to stellar luminosity, without losing too many flares.
-In~\citet{ilin2022}, AU Mic appeared to be more modulated with orbital period in the high energy flares above $1\,$s than below.
-It is also the only star in our sample, for which the threshold makes a difference in the significance of the Anderson-Darling test.
+In~\citet{ilin2022searching}, AU Mic appeared to be more modulated with orbital period in the high energy flares above $1\,$s than below.
+It is also the only star in our sample, for which this threshold makes a difference in the significance of the Anderson-Darling test.
 However, we note that we lose four systems by applying this threshold -- GJ 393, Kepler-411, Kepler-138, and Kepler-1084.
-The flares (with $ED<1\,$s) in all of these systems are consistent with random flare phases within $1\sigma$.
+We note that the flares (with $ED<1\,$s) in all of these systems are consistent with random flare phases within $1\sigma$.
 
@@
 There is no star-planet system for which we find a $>3\sigma$ signal of star-planet interaction in our sample.
-However, overall, the significance of the deviation increases with higher expected power of interaction, which is also listed for the four different powers $P$, calculated with the scaling laws introduced in Section~\ref{sec:methods:pspi} and normalized to AU Mic, along with the derived parameters for these scaling laws, i.e., Rossby number R$_o$, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{rel}$.
+However, overall, the significance of the deviation increases with higher expected power $P_{xx}$ of interaction, where the subscript denotes different scenarios  introduced in Section~\ref{sec:methods:pspi}.
+Table~\ref{tab:maintable_der} also lists the derived parameters required in these scaling laws, i.e., Rossby number $R$o, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{\rm rel}$.
 
 Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with or without planetary magnetic field), there are two branches on the high end of expected powers.
-On one branch, the significance of the measured interaction is correlated with the expected power $P$.
-On the other branch, no interaction is measured regardless of the expected power $P$.
+On one branch, the significance of the measured interaction is correlated with the expected power $P_{xx}$.
+On the other branch, no interaction is measured regardless of the expected power $P_{xx}$.
 
@@
 \label{sec:results:individualstars}
-The properties of star-planet systems in this work are diverse, including both very young and old systems (with slowly rotating host stars); systems with super-Earths, Neptunes, and Hot Jupiters; and spectral types covering the lower main sequence from early G to late M dwarfs.
+The properties of star-planet systems in this work are diverse, including both very fast and very slowly rotating host stars; systems with super-Earths, Neptunes, and Hot Jupiters; and spectral types covering the lower main sequence from mid-F to late M.
 
@@
 We therefore excluded some systems due to documented contamination from nearby (bound or co-moving) companions~(Section~\ref{sec:results:individualstars:excluded}).
-One exception to this rule is Kepler-411, a binary system for which the flare contributions from each component could be separated, but was excluded for other reasons~(Section~\ref{sec:results:individualstars:kep411}).
+One exception to this rule is Kepler-411, a binary system for which the flare contributions from each component could be separated, but which was excluded for other reasons~(Section~\ref{sec:results:individualstars:kep411}).
 We also dropped GJ 1061 from the sample because its rotation period was unconstrained.
@@
 
-The bulk of the systems in our sample are neither expected to show high power of magnetic star-planet interaction, nor do they show any deviation from intrinsic stellar flaring that could be indicative of flaring star-planet interaction.
-In the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring star-planet interaction with increasing expected power $P$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522~(Sections \ref{sec:results:individualstars:aumic} and \ref{sec:results:individualstars:hip67522}).
-Then we consider those systems where high power was expected in all scenarios, but not measured, i.e., TAP 26 and KOI-12~(Sections \ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}).
+The bulk of the systems in our sample are neither expected to show high power of magnetic star-planet interaction, nor do they show any deviation from intrinsic stellar flaring.
+In the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring star-planet interaction with increasing expected power $P_{xx}$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522~(Sections \ref{sec:results:individualstars:aumic} and \ref{sec:results:individualstars:hip67522}).
+Then we consider those systems where high power was expected in all scenarios, but not measured, i.e., TAP~26 and KOI-12~(Sections \ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}).
 \subsubsection{Excluded targets}
@@
 
-While they appear in Table~\ref{tab:flares}, we excluded a number of systems from further analysis.
-We drop all multiple stars except for Proxima Cen (whose components are well separated both physically, and on the sky), and all stars with nearby objects that contaminate our analysis, e.g., from Gaia DR2 and ground-based adaptive optics~\citep{ziegler2018measuring}: \input{output/multiples_string.tex}.
+While they appear in the flare catalog~(Table~\ref{tab:flares}), we excluded a number of systems from further analysis.
+We drop all multiple stars except for Proxima Cen (whose components are well separated both physically, and on the sky), and all stars with nearby objects that contaminate our analysis, e.g., from Gaia DR2 and ground-based adaptive optics~\citep{ziegler2018measuring}: \input{output/multiples_string.tex}
 
-For instance, Kepler-808 (KOI 1300) has a $\sim0.4M_\odot$ \citep{kraus2016impact} companion that is about 1.8 mag fainter than the primary at a separation of .78 arcsec~\citep{baranec2016roboao}.
+For instance, Kepler-808 (KOI-1300) has a $\sim0.4M_\odot$ \citep{kraus2016impact} companion that is about 1.8 mag fainter than the primary at a separation of .78 arcsec~\citep{baranec2016roboao}.
 TOI-837 has co-moving M dwarf a few arcsec away in the same young cluster, 5 mag fainter, but the primary is an F9-G0 star, so flares could still originate come from both stars~\citep{bouma2020cluster}.
@@
 Adopting the 7 flares from \cite{jackman2021stellara} in our analysis, we find that they all have equivalent duration $ED<1\,$s, which excludes Kepler-411 from further analysis.
+Note that we do not find the low energy flares to cluster in orbital phase, either.
 
@@
 The tentatively detected Proxima Cen d, a planet further in, at 0.029 au, or 5 day orbital period~\citep{faria2022candidate, artigau2022linebyline} could still cause flaring star-planet interactions.
-However, the orbital period of the tentative planet is so uncertain at this point that its coherence time is shorter than the roughly 2yr observing baseline of Proxima Cen, preventing us from accurately measuring the flare phases.
+However, the orbital period of the tentative planet is so uncertain at this point that its coherence time~(Section~\ref{sec:results:coherence}) is shorter than the roughly 2yr observing baseline of Proxima Cen, preventing us from accurately measuring the flare phases.
 
@@
 
-K2-25 is a multiplanet system around a fast rotating ($P_{rot}<2\,$d) mid-M dwarf in the Hyades open cluster, that is, 600-800 Myr old~\citep{stefansson2020habitable}.
+K2-25 is a multiplanet system around a fast rotating ($P_{\rm rot}<2\,$d) mid-M dwarf in the Hyades open cluster~\citep[600-800 Myr, ][]{stefansson2020habitable}.
 Both the expected power of interaction, and the measured deviation, are remarkably similar to the AU Mic system.
@@
 In the scenario wherein the stretch-and-break mechanism drives the interaction, the three systems cluster together most distinctly~(top row in Figure~\ref{fig:adtest_bp}).
-In the Alfv\'en wing scenario~(bottom row in Figure~\ref{fig:adtest_bp}), the distinction is less clear, and systems with strong fields and similar expected power of interaction do not show any excess flaring.
-In both cases, the absence of interaction could be due to the Alfv\'en radius being within the planetary orbit.
-It is important to note that the scaling laws assume that the planet is sub-Alfv\'enic, but make no statement about it, because the mass loss of these stars is largely unconstrained.
-All else equal, this is more likely if the stellar magnetic field strength is weaker.
+In the Alfv\'en wing scenario~(bottom row in Figure~\ref{fig:adtest_bp}), the distinction is less clear.
+In both cases, the low level (or possible absence) of interaction could be due to the Alfv\'en radius being within the planetary orbit.
+It is important to note that the scaling laws introduced in Section~\ref{sec:methods:pspi} assume that the planet is sub-Alfv\'enic, but make no statement about it, because the mass loss of these stars is largely unconstrained.
+All else equal, a planet is more likely sub-Alfv\'enic if the stellar magnetic field is strong.
 Another explanation is the possible intermittency, or 'on-off nature' of the interaction~\citep{shkolnik2008nature}, which may be at play here, but particularly in cases where the expected power is very strong, such as in the comparison between HIP 67522 and TAP 26 that we address in the following two Sections.
@@
 In Sector 11, two flares occur at orbital phases $\sim 0.61$ and $\sim 0.81$.
-Two years later, in Sector 38, four flares occur, but this time, all of them take place at orbital phases $0.00-0.05$, that is, up to a few hours after transit.
+Two years later, in Sector 38, four flares occur, but this time, all of them take place at orbital phases $0.00-0.05$, that is, within 10 hours after mid-transit.
 
@@
 It is a Sco-Cen member (10-20 Myr old), which was discovered to host a close-in Jupiter, HIP 67522 b, in 2020~\citep{rizzuto2020tess}.
-Curiously, the planet is in close spin-orbit commensurability -- $P_{rot}/P_{\rm orb}=5/1$.
+Curiously, the planet is in close spin-orbit commensurability -- $P_{\rm rot}/P_{\rm orb}\approx 1/5$.
 Therefore, we cannot completely rule out that the observed periodicity is in fact a rotational periodicity, and not related to the planet.
-However, if we calculate the $p$-value of the AD test using the rotational period instead of the orbital period, we find HIP 67522 consistent with uniform flaring in time within $1\sigma$, which is likely due to the not sufficiently low uncertainty in rotation period.% Fortunately, HIP 67522 will be observed again with TESS in April 2023, which may resolve the puzzle.
+However, if we calculate the $p$-value of the AD test using the rotational period instead of the orbital period, we find HIP 67522 consistent with uniform flaring in time within $1\sigma$, which is likely due to the not sufficiently low uncertainty in rotation period.
+So we cannot rule out rotational modulation yet, although the clustering close to transit is suggestive.% Fortunately, HIP 67522 will be observed again with TESS in April 2023, which may resolve the puzzle.
 
@@
 \label{sec:discussion}
-Eccentricity is almost controlled for in our sample~(Section~\ref{sec:discussion:eccentricity}), while rotation is not well enough constrained to investigate the presence of flaring modulation with $P_{rot}$, or the synodic period~(Section~\ref{sec:discussion:rotsyn}).
-In the remainder of the discussion, we lay out different reasons for the emerging shape of the distribution in our results in Fig.~\ref{fig:adtest_bp}, in particular the inactive and active branches at high expected power of interaction.
-We begin with the possible intermittency of the interaction that could be caused by the planet regularly moving in and out of the sub-Alfv\'enic zone for extended periods of time~(Section~\ref{sec:discussion:intermittency}).
-In Section~\ref{sec:discussion:viewing}, we suggest that the absence of interaction at high expected power could be due to unfavorable viewing geometry of the system, e.g., a face-on orbital plane.
-In Section~\ref{sec:discussion:commensurability}, we note that systems on the inactive branch are further away from spin-orbit commensurability than stars on the active branch.
-This leads us to conjecture a possible link between spin-orbit resonance and flaring SPI.
+
+Our results in Fig.~\ref{fig:adtest_bp} are tentative, yet the trend between expected power of interaction and measured clustering of flares in orbital phase is suggestive, as is the appearance of an active and an inactive branch at high expected powers.
+We can now consider additional facts about the systems, as well as processes, that may explain the observed trends.
+Beyond the extent of the Alfv\'en radius that decides over the possibility of magnetic interaction in the first place~(Section~\ref{sec:intro:mspi}), orbital eccentricity can further enhance magnetic SPI signal, but is low for most systems in our sample except for K2-25~(Section~\ref{sec:discussion:eccentricity}).
+The observed branching might also be explained by intermittent SPI~(Section~\ref{sec:discussion:intermittency}), but its possible causes are not well known.
+As an easier to test alternative explanation, we highlight the important influence of viewing geometry on the observability of flaring SPI, which might explain the absence of magnetic SPI in TAP~26~(Section~\ref{sec:discussion:viewing}).
+
+Magnetic and tidal SPI are difficult to disentangle by their global effects on stellar activity indicators~(Section~\ref{sec:intro:global}).
+Locally, however, we can discriminate between the two by their relevant periods, that is, $P_{\rm orb}$ and $P_{\rm orb /2}$.
+In Section~\ref{sec:discussion:tidal}, we repeat the analysis in this paper with $P_{orb}/2$, and find yet more tentative trends in line with scaling laws for tidal interaction.
+In a system-by-system comparison, we find consistency with the expectation that slowly rotating, likely old, systems can only show local tidal interaction, while rapidly rotating systems with strong magnetic fields can experience both.
 
@@
 \label{sec:discussion:eccentricity}
+Orbital eccentricity can affect magnetic SPI by modulating the planet's distance to the star.
 If the planetary orbit is highly eccentric, the difference between periastron and apoastron can be significantly larger than the variability of the Alfv\'en radius.
-If then the apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, during the planet's rapid periastron passage.
+If then apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, during the planet's rapid periastron passage.
 This was previously exploited in the case of HD 17156~\citep{maggio2015coordinated}, and analogously for the colliding magnetospheres in binary systems~\citep{massi2002periodic,getman2016search}.
@@
 The exception is K2-25, with a relatively high $e=0.45$.
-If periastron passage in K2-25 occurs when the planet is in front of the star relative to the observer, the visibility effect of the interaction footpoint moving in and out of view as the planet orbits is further increased by the narrow phase range of the periastron passage.
+If periastron passage in K2-25 occurs when the planet is in front of the star relative to the observer, the visibility effect of the interaction footpoint is further increased by the narrow phase range of the periastron passage.
 \citet{stefansson2020habitable} estimated the argument of periastron $\omega=120^{+12}_{-14}\,$deg for K2-25 (with longitude of the ascending node chosen such that $\omega$ is the same as the longitude of periastron, with $\omega=90\,$deg being periastron passage during transit,~\citealt{kipping2010investigations,dawson2012photoeccentric}).
 We can therefore conjecture that the tentative signal of flaring SPI in K2-25 is enhanced by eccentricity.
+Statistically, we are more likely to observe a planetary transit close to periastron, since periastron permits more orbital inclinations than apoastron.
+So, overall, we expect eccentric transiting systems to experience elevated SPI signal.
 
-\subsection{Rotational and synodic variability}
-\label{sec:discussion:rotsyn}
-Our analysis is the most comprehensive search for flaring star-planet interactions to date, using the full Kepler and most recent TESS archives of light curves.
+% \subsection{Rotational and synodic variability}
+% \label{sec:discussion:rotsyn}
+% Our analysis is the most comprehensive search for flaring star-planet interactions to date, using the full Kepler and most recent TESS archives of light curves.
 We considered exploiting it beyond the search for variations with orbital period, and additionally look for variability with rotation period, and synodic period.
@@
 
-Even for the few stars, for which the rotational period is known precisely enough~(see Fig.~\ref{fig:coherence_hist}) for our analysis, we need to make numerous assumptions.
+% Even for the few stars, for which the rotational period is known precisely enough~(see Fig.~\ref{fig:coherence_hist}) for our analysis, we need to make numerous assumptions.
 These include the number of active regions crossed by the footpoint of interaction, differential rotation, spot evolution, and a significant correlation between the location of the planet and the location of the planet-induced flare on the stellar surface.
@@
 
-\citet{fischer2019timevariable} argue that the synodic period, at which the sub-planetary point crosses the same (magnetic) surface element on the star, may result in a clearer interaction signal, because a magnetically active region that is prone to planet-induced flares, will be passed only once per period.
+% \citet{fischer2019timevariable} argue that the synodic period, at which the sub-planetary point crosses the same (magnetic) surface element on the star, may result in a clearer interaction signal, because a magnetically active region that is prone to planet-induced flares, will be passed only once per period.
 However, this assumes that the landscape of active regions on the star is stable throughout the entire observing time, and that the number of such regions in the footpoint passageway is low enough to produce a periodic modulation.
@@
 
-In our sample, the observing baseline is multiple years long for many systems.
+% In our sample, the observing baseline is multiple years long for many systems.
 Even the most rigidly rotating late M dwarfs show variability in their spot modulation on such long timescales.
@@
 Magnetic star-planet interaction power in a given system may sometimes be low for episodes of time, and high for others.
-HD 179949 is the prototype example for this phenomenon, wherein the orbital modulation of chromospheric indicators was observable for four out of six epochs on a five year baseline~\citep{shkolnik2003evidence,shkolnik2008nature}.
+HD 179949 is the prototype example for this phenomenon.
+The orbital modulation of its chromospheric indicators was observable for four out of six epochs on a five-year baseline~\citep{shkolnik2003evidence,shkolnik2008nature}.
 It is not clear how long a continuous epoch of interaction or non-interaction might be.
 This leaves room for many different explanations.
-Long-term monitoring is needed to investigate the reasons for the temporary cessation of interaction.
+Uninterrupted, long-term monitoring of individual systems is required to investigate the reasons for the temporary cessation of interaction.
 Candidate mechanisms for the star include:
 \begin{itemize}
-    \item the Alfv\'en radius moving in- and outside the planet's orbit, either over the course of an activity cycle, or through short-term variations in the magnetic field and wind properties caused by, e.g., coronal mass ejections;
-    \item visibility of the interacting footpoint changing as the magnetic field evolves (more visibility is less modulation with orbital period);
-    \item an active latitude moving away from the magnetic footpoints passageway; or
+    \item the Alfv\'en radius moving in- and out the planet's orbit, either over the course of an activity cycle, or through short-term variations in the magnetic field and wind properties caused by, e.g., coronal mass ejections;
+    \item the interacting footpoint moving to higher latitudes due to changes in the large scale field, which reduces the modulation of its visibility 
+    \item an active latitude (i.e., small scale field) moving away from the magnetic footpoints passageway; or
     \item the available magnetic energy decreasing such that the flares or other magnetic interaction indicators still occur but fall below the detection threshold for a period of time.
@@
 TAP 26 and KOI-12 do not show any sign of excess flaring in our data, despite similar expected powers as in HIP 67522 with its $2-3\sigma$ signal.
-In Sections~\ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}, the absence of interaction in TAP 26 and KOI-12 could be explained by an uncertainty in orbital period that smears out the signal, and a super-Alfv\'enic orbit, respectively.
+However, other explanations cannot be ruled out yet (see Sections~\ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}, and the following).
+
+%In Sections~\ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}, the absence of interaction in TAP 26 and KOI-12 could be explained by an uncertainty in orbital period that smears out the signal, and a super-Alfv\'enic orbit, respectively.
 Yet intermittency cannot be ruled out.
@@
 \label{sec:discussion:viewing}
-The visibility of the magnetic interaction footpoint is crucial for the detection of flaring star-planet interactions in our analysis.
+Modulated visibility of the magnetic interaction footpoint is crucial for the detection of flaring star-planet interactions in our analysis.
 The viewing geometry of the star-planet system is therefore important to consider as an alternative to, or explanation for, the intermittency discussed above.
@@
 However, if the footpoint's latitude is high, we need to observe the star-planet system nearly edge-on to be able to measure a modulation of activity with the planet's orbital phase.
-Assuming the dipole field dominates at the distance of the planet, the footpoint will be close to the pole, similar to the hot spot created by Io and the other moons in the polar cap of Jupiter~().
+Assuming the dipole field dominates at the distance of the planet, the footpoint will be close to the pole, similar to the UV spot created by Io and the other moons in the polar cap of Jupiter~\citep{clarke1996farultraviolet, prange1996rapid}.
 In this scenario, many, especially non-transiting, systems may experience flaring star-planet interaction, but those would not show up as correlation of flare timing with the orbital phase in our data.
@@
 Most of our systems are transiting, and for those we can expect this scenario to be a minor problem unless the latitude of the footpoint is very high.
-Of the systems that have high expected power but do not show any, only TAP 26 b is a planet detected in radial velocity, and has a relatively high orbital inclination of about $55\pm10$ deg inferred from Zeeman Doppler measurements~\citep{yu2017hot}.
-The ZD map reveals magnetic field concentrations close to the rotational pole, and the brightness maps also show a dark spot in the same location.
-If the orbital plane is aligned with the stellar rotation axis, the absence of phase-correlated flaring in TAP 26 could be explained by the footpoint of interaction being always in view and therefore never modulated.
+Of the systems that have high expected power but do not show any excess flaring, only TAP 26 b is a planet detected in radial velocity, and has a relatively high orbital inclination of about $55\pm10$ deg inferred from photometry, spectroscopy, and Zeeman Doppler measurements~\citep{yu2017hot}.
+Their ZD map reveals magnetic field concentrations close to the rotational pole, and the brightness maps also show a dark spot in the same location.
+If the orbital plane is aligned with the stellar rotation axis, the absence of phase-correlated flaring in TAP 26 could be explained by the footpoint of interaction being always in view, and therefore never modulated.
 
-Alignment between orbital, rotational and magnetic dipole axis is not generally given.
+However, alignment between orbital, rotational and magnetic dipole axis is not generally given.
 Many planets orbit their hosts nearly pole-on~\citep{albrecht2012obliquities, albrecht2022stellar, bourrier2023dream}.
 T Tauri stars show somewhat misaligned magnetic axes relative to their spin~\citep{mcginnis2020magnetic}.
-Moreover, the magnetic dipole axis location changes throughout the activity cycles of Sun-like stars~\citep{petit2009polarity,borosaikia2018direct}, which may cause temporary cessation of visibility.
+In Sun-like stars, the magnetic dipole axis location changes throughout the activity cycle~\citep{petit2009polarity,borosaikia2018direct}, which may also cause temporary cessation of visibility.
 Orbital precession of misaligned planets can also cause such intermittency, if it periodically brings the footpoints trajectory on the stellar surface fully into view so that it is no longer modulated.
-Interpreting non-detections as effects of viewing geometry in fully aligned systems ignores this caveat.
+
+%Interpreting non-detections as effects of viewing geometry in fully aligned systems ignores this caveat.
 
@@
 
-If the observed effects are due to the tidally interacting companion, planets should do the same to their host, albeit at a smaller magnitude.
+If the observed effects are due to the tidally interacting stellar companion, planetary companions should do the same, albeit at a smaller magnitude.
 Fortunately, spin and orbit are not synchronized in our sample, so confusion with intrinsic effects is less likely.
@@
 
-The first model measures the torque $\partial L_{\rm conv} / \partial t$, exerted by angular momentum transfer from star to planet or from planet to star, assuming the star has a convective envelope~(\citealt{penev2012constraining}, their Eqns.
+The first model measures the torque $\partial L_{\rm conv} / \partial t$, exerted by angular momentum transfer between star and planet, assuming the star has a convective envelope~(\citealt{penev2012constraining}, their Eqns.
 1 and 2).
@@
 Following~\citet{ilic2022tidal}, we adopt Eqn.
-2 in~\citep{albrecht2012obliquities} for the tidal dissipation timescale in the convective envelope.
+2 in~\citet{albrecht2012obliquities} for the tidal dissipation timescale in the convective envelope.
 We assume that all stars in our sample have a convective envelope because they flare, and flaring requires a dynamo-generated magnetic field, which can only operate in stars with convective envelopes.
-Most of our stars are dwarf stars below the Kraft break at spectral type F5, except for KOI-12, which is an F5 sub-giant~\citep{frasca2016activity}.
+Most of our stars are dwarf stars below the Kraft break at spectral type F5~\citep{kraft1967studies}, except for KOI-12, which is an F5 sub-giant~\citep{frasca2016activity}.
 
@@
 We collect the planetary and stellar masses from the literature~(Table~\ref{tab:tidal}).
-For missing planetary masses, the radii were known, so used the mass-radius relations implemented in \texttt{forecaster}~\citep{chen2017probabilistic}.
+For missing planetary masses, the radii were known, so we used the mass-radius relations implemented in \texttt{astro-forecaster}~[Ben Cassesse's implementation of \texttt{forecaster}][]\citep{chen2017probabilistic}.
 GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute Ks magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}.
-We list the masses in Table~\ref{tab:tidal}.
 For Kepler-42 b, we used  $M_p=0.1-2.06M_\oplus$ that covers pure rock to pure iron compositions in \citet{muirhead2012characterizing}, and adopted the logarithmic mean for our estimate.
-Kepler-1558 c has a similar radius to Kepler-42 b, i.e., most likely a bare core planet, so we proceeded analogously to estimate its mass.
+Kepler-1558 c has a similar radius to Kepler-42 b, i.e., most likely a bare core planet, so we used the same density range to estimate its mass.
 We also adopt the upper limit of $5M_J$ for HIP 67522, but use the lower error from \citet{chen2017probabilistic}.
@@
 On the one hand, since the flares in HIP 67522 mostly appear close to the transit phase, and not during eclipse, this may favor magnetic interaction, and the tidal signal would only be an artifact.
-On the other hand, the narrow range in which most of the flares on HIP 67522 occurred might favor a well-located tidal bulge.
+On the other hand, the narrow range in which most of the flares on HIP 67522 occurred~(see Fig.~\ref{fig:cumdist_transiting} and Section~\ref{sec:results:individualstars:hip67522}) might favor a well-localized active region in the vicinity of the tidal bulge.
 Conceivably, both effects play a role at the same time.
@@
 \paragraph{KOI-12,} which lacks signal with $P_{\rm orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction.
-This could be interpreted as KOI-12 b orbiting outside the Alfv\'en radius, unable to interact magnetically, but tidally.
-We note that KOI-12 may be evolving off the main sequence, so that the tidal interaction estimates might not be accurate for this star.
+This could be interpreted as KOI-12 b orbiting outside the Alfv\'en radius, so that it can still interact tidally, but not magnetically.
+However, we note that KOI-12 may be evolving off the main sequence, so that the tidal interaction scaling laws may not apply for this star.
 
@@
 Kepler-42 is very similar to TOI-540, which also is a small M dwarf with a likely terrestrial planet in a very short orbit.
-A key difference is that Kepler-42 is rotating at about 70 days, and therefore expected to have a relatively weak magnetic field, whereas TOI-540 is a young star with a rotation period $<1\,$d.
+A key difference is that Kepler-42 is rotating at about 70 days, and therefore expected to have a relatively weak magnetic field, whereas TOI-540 is a young star with $P_{\rm rot}<1\,$d.
 TOI-540 is expected to have lower tidal interaction strength than Kepler-42 due to TOI-540 b's wider orbit, and also shows a weaker tidal flaring SPI signal in all three scenarios.
-K2-25 and AU Mic are similar, but differ from TOI-540 -- both show tentative signs of magnetic SPI, but are consistent within $1\sigma$ with no observable tidal interaction.
+
+\paragraph{K2-25 and AU Mic} cluster with TOI-540 in magnetic SPI -- all three show tentative signs of magnetic interaction and similar expected powers.
+But in contrast to TOI-540, both K2-25 and AU Mic are consistent within $1\sigma$ with no observable tidal interaction.
+
+Overall, tidal interaction, if at all present, is less pronounced than magnetic SPI in our sample.
+However, if the observed deviations from intrinsic flaring do in fact represent low level tidal interaction signal, we can conclude that close-in planets can interact both magnetically and tidally.
+In line with theoretical considerations~\citep{strugarek2017fate}, our results tentatively suggest that magnetic interaction is more pronounced for planets with fast rotating, active hosts, while tidal interactions affect both systems with slowly and rapidly rotating stars.
 
@@
 
-\subsection{Spin-orbit commensurability}
-\label{sec:discussion:commensurability}
-Curiously, in our analysis, systems with high expected power are divided: Stars that show a correlation between excess flaring and expected power tend to have closer spin-orbit commensurability than systems that are far away from any low-integer ratio between rotational and orbital period.
+%\subsection{Spin-orbit commensurability}
+%\label{sec:discussion:commensurability}
+%Curiously, in our analysis, systems with high expected power are divided: Stars that show a correlation between excess flaring and expected power tend to have closer spin-orbit commensurability than systems that are far away from any low-integer ratio between rotational and orbital period.
 
-In Fig.~\ref{fig:spinorbit}, we split our sample into three categories.
+%In Fig.~\ref{fig:spinorbit}, we split our sample into three categories.
 The first contains the systems where the expected interaction is lower than that in TOI-540, the system with the lowest power of interaction among those with relatively high flaring star-planet interaction signal (i.e., K2-25, TOI-540, HIP 67522, and AU Mic).
@@
 
-While chance alignment is possible, the division suggests that spin-orbit commensurability and magnetic star-planet interaction are related.
+%While chance alignment is possible, the division suggests that spin-orbit commensurability and magnetic star-planet interaction are related.
 Either something about our observing method favors the measurement of excess flaring in systems with close spin-orbit commensurability, or there is physical causation at play.
 
-In the latter case, the spin-orbit commensurability could be either an effect, or a cause, of measured magnetic star-planet interaction.
+%In the latter case, the spin-orbit commensurability could be either an effect, or a cause, of measured magnetic star-planet interaction.
 \citet{lanza2022model} suggest that tidal torque of the planet on the star excites resonant oscillations in the interior stellar magnetic field, which in turn leads to a resonance between stellar spin and planetary orbit.
@@
 
-We therefore favor the observational bias explanation: Only fast rotating stars can be close to a low integer spin-orbit commensurability with a planet in a few days long orbit.
+%We therefore favor the observational bias explanation: Only fast rotating stars can be close to a low integer spin-orbit commensurability with a planet in a few days long orbit.
 Incidentally, only fast rotating stars can have strong enough magnetic fields to put their planets in the sub-Alfv\'enic zone.
@@
 
-\begin{figure}[t]
-    \script{paper_spin_orbit_commensurability.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/PAPER_spin_orbit_commensurable_p_spi_sb_bp1_norm.png}
-        \caption{
-           \textbf{Top panel}: Same as the bottom left panel in Fig.~\ref{fig:adtest_bp}, but color coded as below.
+% \begin{figure}[t]
+%     \script{paper_spin_orbit_commensurability.py}
+%     \begin{centering}
+%         \includegraphics[width=\linewidth]{figures/PAPER_spin_orbit_commensurable_p_spi_sb_bp1_norm.png}
+%         \caption{
+%            \textbf{Top panel}: Same as the bottom left panel in Fig.~\ref{fig:adtest_bp}, but color coded as below.
 \textbf{Bottom panel:} Spin-orbit commensurability compared to flaring star-planet interaction signal.
@@
 Among the systems with high expected power, those with higher interaction signal ('SPI on') show closer spin-orbit commensurability than those on the inactive 'SPI off' branch.
-        }
-        \label{fig:spinorbit}
-    \end{centering}
-\end{figure}
+%         }
+%         \label{fig:spinorbit}
+%     \end{centering}
+% \end{figure}
 
@@
 
-We have conducted the so far largest search for flaring star-planet interactions.
+We conducted the so far largest search for flaring star-planet interactions.
 Using over 7200 Quarters and Sectors of photometric monitoring from Kepler and TESS archives, we searched for flares in over 1800 systems of the about 3000 listed in the NASA Exoplanet Archive.
 In the single star systems, where flares could be unambiguously attributed to the planet host, and showed three or more energetic events in the data, we searched for flares that clustered in orbital phase.
-Our final sample consisted of 26 systems, among them well-known flaring hosts like Proxima Cen, AU Mic, and TRAPPIST-1.
+Our final sample consisted of 25 systems, among them well-known flaring hosts like Proxima Cen, AU Mic, and TRAPPIST-1.
 
-Applying both the stretch-and-break and Alfv\'en wing mechanisms discussed for magnetic interaction, we found tentative evidence for a correlation between the expected power of interaction, and the presence of excess flaring in phase with the orbital period.
-In particular, we found that there may be two branches at high expected power -- one where the measured excess flaring is correlated with the expected power, and one where this is not the case.
+Applying both the stretch-and-break and Alfv\'en wing mechanisms for magnetic interaction, we found a tentative evidence trend between the expected power of interaction, and the presence of excess flaring in phase with the orbital period $P_{\rm orb$.
+In particular, we found that there may be two branches at high expected power -- one where the measured excess flaring is correlated with the expected power, and one where excess flaring is absent.
 This may be an effect of the extent of the Alfv\'en surface, the intermittency in the interaction, or of the viewing geometry of the systems.
@@
 For AU Mic, we may be only a few TESS Sectors away from a $3\sigma$ level confirmation~\citep{ilin2022searching} of the tentative interaction signal observed here and in other work~\citep{klein2022one}.
-HIP 67522, the system with the strongest individual signal, will be re-observed by TESS as soon as April 2023.
+Several systems in our sample are already scheduled for further observing with TESS, including HIP 67522, Kepler-42, and KOI-12.
 
-Close-in planets are being explored as in-situ probes of the dynamic magnetic field~\citep{trigilio2023starplanet}, and stellar mass loss~\citep{vidotto2017exoplanets} conditions in their orbit.
+%Close-in planets are being explored as in-situ probes of the dynamic magnetic field~\citep{trigilio2023starplanet}, and stellar mass loss~\citep{vidotto2017exoplanets} conditions in their orbit.
 They are two key components of the space weather that a potentially habitable planet will encounter.

### 2023-05-19 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-Applying both the stretch-and-break and Alfv\'en wing mechanisms for magnetic interaction, we found a tentative evidence trend between the expected power of interaction, and the presence of excess flaring in phase with the orbital period $P_{\rm orb$.
+Applying both the stretch-and-break and Alfv\'en wing mechanisms for magnetic interaction, we found a tentative evidence trend between the expected power of interaction, and the presence of excess flaring in phase with the orbital period $P_{\rm orb}$.
 In particular, we found that there may be two branches at high expected power -- one where the measured excess flaring is correlated with the expected power, and one where excess flaring is absent.

### 2023-05-23 src/scripts/paper_adtest_vs_value_scatterplots.py
layouting figures

@@ -287,7 +287,7 @@ def make_adtest_figure(df, value, valuelabel, legend, labels, ext, ax, leg=False
         for star, row in group.iterrows():
             if (row["mean"]<=.2) :# | (row[value]>=1.):
                 texts.append(ax.text(x=row[value], y=row["mean"], s=row["ID"],
-                        fontsize=11, ha="right", va="top", rotation=0))
+                        fontsize=12, ha="right", va="top", rotation=0))
 
     # log scale
     ax.set_yscale("log")
@@ -300,8 +300,8 @@ def make_adtest_figure(df, value, valuelabel, legend, labels, ext, ax, leg=False
                 color="k", verticalalignment="center")
 
     # labels
-    ax.set_ylabel("p-value of AD test")
-    ax.set_xlabel(valuelabel)
+    ax.set_ylabel("p-value of AD test", fontsize=13)
+    ax.set_xlabel(valuelabel, fontsize=13)
 
     # legend
     if leg == True:

### 2023-05-23 src/scripts/paper_cumdist_individual_transiting.py

@@ -110,7 +110,7 @@ if __name__ == "__main__":
             # set the axis labels
             if len(ax) <3:
                 a.set_xlabel("orbital phase")
-            a.set_ylabel("number of flares")
+            a.set_ylabel("fraction of flares")
 
     # layout the figure
     plt.tight_layout(h_pad=0.1)

### 2023-05-23 src/scripts/paper_tidal_interaction.py

@@ -49,7 +49,7 @@ if __name__ == "__main__":
             r"tidal torque $\partial L_{conv}/\partial t$ $\left[M_\odot \left(\frac{km}{s}\right)^2\right]$"]
 
     # define shared axis label
-    axes[0].set_ylabel("p-value of AD test", fontsize=12)
+    axes[0].set_ylabel("p-value of AD test", fontsize=13)
 
     # loop over the models
     for model, label in zip(models, labels):
@@ -79,11 +79,11 @@ if __name__ == "__main__":
         _ = res[(res['mean']<.19) | (res["torque_conv"]>1e-15)]
         for i, row in _.iterrows():
             texts.append(ax.annotate(row["ID"], (row[model], row["mean"]), 
-                                     fontsize=10,))
+                                     fontsize=11,))
         # layout
         ax.set_xscale("log")
         ax.set_yscale("log")
-        ax.set_xlabel(label, fontsize=12)
+        ax.set_xlabel(label, fontsize=13)
 
         minx, maxx = res[model].min(), res[model].max()
 

### 2023-05-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \author{Katja Poppenh\"ager}
+\author{Judy Chebly}
 \author{Nikoleta Ilic}
@@
 \begin{abstract}
-    In many of the star-planet systems discovered so far, the innermost planets orbit extremely close to their host, that is, within its extended magnetosphere.
-In these systems, the planets become in-situ probes of the stellar magnetic fields.
-As they move, they may trigger flares on the stellar surface.
-Until recently, searches for such flaring star-planet interactions suffered from small sample sizes, and poor orbital phase coverage.
-
-    In this work, we used the excellent phase coverage of Kepler and TESS to search their entire archives for star-planet systems with flaring star-planet interactions.
-We compiled a catalog of all star-planet systems with flares, and searched for planet-induced flares, i.e., flares clustering in phase with the planet's orbit.
-
-    In the 1811 searched systems, we found 26 single stars with three or more flares each.
+    In many of the star-planet systems discovered so far, the innermost planets orbit within only a few stellar radii.
+In these systems, the planets become in-situ probes of the extended stellar magnetic field.
+As they move, they can trigger flares on the stellar surface.
+Until recently, however, searches for such planet-induced flaring suffered from small sample sizes, and poor orbital phase coverage.
+
+    In this work, we used the excellent phase coverage of the archives of Kepler and the Transiting Exoplanet Survey Satellite to search for star-planet systems with flaring star-planet interactions.
+We compiled a catalog of all their flares, and searched for planet-induced flaring, i.e., flares clustering in phase with the planet's orbit.
+
+    In the 1811 searched systems, we found 25 single stars with three or more flares each.
 We quantified the significance of their excess flaring, and compared it against the theoretically expected amplitude of magnetic interaction.
-Most systems are neither expected to, nor do they show excess flaring.
-Among the systems that we can expect to interact, we see two branches.
-An inactive one, where no signs of excess flaring appear, and an active one, where expected power and excess flaring are correlated.
-This trend is tentative, but consistent for all scaling laws for magnetic interaction.
-
-    Finally, we searched the same data for signs of locally expressed tidal interaction, that is, excess flaring in phase with the tidal bulges ($P_{\rm orb}/2$).
-We found a similar trend with different scaling laws of tidal interaction, albeit at even lower significance.
-Our system-by-system comparison suggests that young systems may interact both tidally and magnetically, whereas old, magnetically inactive systems might mostly interact tidally.
+As we did not select for short orbits, most systems do not show excess flaring, as expected.
+Those we expect to interact fall on two branches.
+An inactive one, without any signs of excess flaring, and an active one, where expected power and excess flaring are correlated.
+This trend is tentative, but consistent for several scaling laws for magnetic interaction.
+
+    Finally, we searched our data for locally expressed tidal interaction, i.e., excess flaring in phase with the tidal bulges ($P_{\rm orb}/2$).
+We find a marginal trend with different scaling laws of tidal interaction.
+Our system-by-system comparison tentatively suggests that young systems can interact both tidally and magnetically, whereas old, magnetically inactive systems mostly interact tidally.
     %magnetic field strength (using $Ro$-$B$ relations), orbital parameters, and planet radius.
@@
 One of the most surprising results in exoplanet research is the diversity of star-planet system architectures.
-The past two decades revealed that planets can occur in orbits so close to their host star that they could almost be considered to live inside the stellar atmosphere.
+The past two decades revealed that planets can occur in orbits of only a few stellar radii~[e.g., ][]\citep{sanchis-ojeda2014study} that they could almost be considered to live inside the stellar atmosphere.
 At this proximity, the planet exerts force, tidal and magnetic, both short- and long-term, on its host -- a phenomenon largely unknown to the Solar System.
@@
 On the other hand, measuring in what ways and how much close-in planets alter their hosts' behavior can provide important insights into the habitability of the entire system~\citep{shkolnik2018signatures}.
-Even if they orbit far inside the habitable zone, such planets probe the system's space weather and mass loss by revealing the extent of the Alfv\'en zone~\citep{kavanagh2021planetinduced, chebly2022destination}.
+Even if they orbit far inside the habitable zone, such planets probe the system's space weather and mass loss by revealing the extent of the Alfv\'en zone through SPI~\citep{kavanagh2021planetinduced, chebly2022destination}.
 % Prospectively, planet-induced stellar activity could quantify otherwise difficult to measure planetary properties such as the strength and extent of their magnetic field~\citep{cauley2019magnetic}.
@@
 \label{sec:intro:mspi}
-Magnetic star-planet interactions can only occur if the planet is orbiting within the Alfv\'en radius of the star.
+Magnetic star-planet interactions can occur if the planet is orbiting within the Alfv\'en radius of the star at least part of the time~\citep{preusse2006magnetic, cohen2011dynamics}.
 The Alfv\'en radius is the radius at which the stellar wind velocity, which increases with increasing distance from the star, exceeds the Alfv\'en velocity of the magnetized plasma.
@@
 \citet{lanza2012starplanet, lanza2018closeby}, and \citet{zarka2007plasma} and \citet{saur2013magnetic} suggest different mechanisms for when and how the energy transport and dissipation takes place, and how much energy can be transferred and dissipated at all.
-They all lack observational constraints for calibration, which we aim to provide in this work.
+They all lack observational constraints from large samples for calibration, which we aim to provide in this work.
 
@@
 We now have access to long-term stellar monitoring data available for flare hunting.
-Currently, the Transiting Exoplanet Survey Satellite~\citep{ricker2015transiting} is rapidly growing the archive~\citep{gunther2020stellar}.
-Their key advantage for this work is the nearly uninterrupted monitoring of star-planet systems that covers all phases of a close-in planet's orbit.
+Since 2018, the Transiting Exoplanet Survey Satellite~\citep{ricker2015transiting} is rapidly growing the archive~\citep{gunther2020stellar}.
+The key advantage of both missions for this work is the nearly uninterrupted monitoring of star-planet systems that covers all phases of a close-in planet's orbit.
 
@@
 We do not know how energetic planet-induced flares can be.
-The estimates of the maximum dissipated power~\citep{lanza2018closeby} are well within the regime of superflares typically observed by Kepler and TESS.
-However, on the one hand, that power is an upper limit, so the observed energies might be lower.
-The planet might, for instance, be triggering flares prematurely, leading to an overabundance of low energy flares~\citep{loyd2023flares}.
+The estimates for dissipated energy~\citep{lanza2018closeby} are in the ballpark of the regime of superflares observed by Kepler and TESS.
+However, on the one hand, the planet might be triggering flares prematurely, which would be of lower energy~\citep{loyd2023flares}, and end up below our detection threshold.
 On the other hand, the energy need not be dissipated continuously, particularly in the stretch-and-break mechanism proposed by~\citep{lanza2012starplanet}, so an individual flare's energy might be higher.
 We also do not know whether flares triggered by interactions with a companion would have different properties than intrinsic flares.
-We assume that, since they would be caused by magnetic reconnection triggered by the planet in the stellar corona, they should follow the same process as intrinsic flares.
-
-Since planet-induced flares are not expected to look any different from intrinsic flares, and we do not know how their energies will be distributed, we require a method to distinguish them without referring to their individual properties.
+We will assume that, since they would be caused by magnetic reconnection triggered by the planet in the stellar corona, they should still have the same physics as intrinsic flares.
+
+Since planet-induced flares might not look any different from intrinsic flares, and we do not know how their energies will be distributed, we require a method to distinguish them without referring to their individual properties.
 Instead, we can look at the statistical distribution of flares in time:
@@
 Depending on the system's viewing geometry, i.e., the inclination of the rotation axis, the spin-orbit (mis-)alignment, and the extent and configuration of the large scale magnetic field -- the footpoint could be always in view, or never.
-In expectation, however, in star-planet systems with favorable viewing geometries and magnetic field states, the footpoint visibility will be modulated in phase with the planetary orbit.
+In expectation, however, in star-planet systems with favorable viewing geometries and magnetic field strengths and configurations, the footpoint visibility will be modulated in phase with the planetary orbit.
 The resulting phase preference of planet-induced flares introduces a deviation from a random distribution of flares.
@@
 \label{sec:intro:local}
-In contrast with global SPI, local SPI effects are easier to tell apart from intrinsic stellar behavior because they are tied to the planet's orbital period. 
+In contrast to global SPI, local SPI effects are easier to tell apart from intrinsic stellar behavior because they are tied to the planet's orbital period. 
 Phase-correlated activity, flaring and otherwise, has been searched for in individual systems.
-After eight years of monitoring of HD 189733, an X-ray active Hot Jupiter host, the observed slight clustering of flaring in orbital phase remains tentative~\citep{pillitteri2022xray}.
-\citet{maggio2015coordinated} observed an eruption of X-ray emission when the Jupiter-sized companion was in periastron on its highly eccentric orbit around its host HD 17156.
+After eight years of monitoring of HD 189733, an active Hot Jupiter host, higher X-ray energy flares seem only marginally clustered in orbital phase than lower energy ones~\citep{pillitteri2022xray}.
+\citet{maggio2015coordinated} observed an eruption of X-ray emission when the Jupiter-sized companion was in periastron on the highly eccentric orbit around its host HD 17156.
 However, a similar study using chromospheric indicators in the eccentric system HD 80606 found no variation between periastron and apoastron~\citep{figueira2016activity}.
 In the above cases, non-detection can at least partly be attributed to poor orbital phase coverage, which also limits the significance of any positive detection.
-Realizing this, \citet{fischer2019timevariable} used K2 data with excellent phase coverage of the orbits of the inner TRAPPIST-1 planets to look for clustered flaring in phase, but found none.
+Realizing this, \citet{fischer2019timevariable} used K2 data with excellent phase coverage of the orbits of the inner \mbox{TRAPPIST-1} planets to look for clustered flaring in phase, but found none.
 \citet{ilin2022searching} and \citet{klein2022one} found hints of excess flaring, and chromospheric Helium emission in the young AU Mic system, respectively.
@@
 We present the catalog of all flares found in our sample of star-planet systems, and compare the test results with the expected power of interaction for each system~(Section~\ref{sec:results}).
-We discuss the results for the most interesting star-planet systems individually~(Section~\ref{sec:results:individualstars}), and take a look at the patterns emerging from our analysis~(Section~\ref{sec:discussion}), particularly at the possible role of tidal flaring SPI in our observations~(Section~\ref{sec:discussion:tidal}).
+We discuss the results for the most interesting star-planet systems individually~(Section~\ref{sec:results:individualstars}), and take a look at the patterns emerging from our analysis~(Section~\ref{sec:discussion}), and the possible role of tidal flaring SPI in our observations~(Section~\ref{sec:discussion:tidal}).
 We summarize our findings in Section~\ref{sec:summary}.
@@
 \label{sec:data}
-In this study, we compiled the largest possible sample to search for flaring star-planet interactions.
+In this study, we aimed at compiling the largest possible sample to search for flaring star-planet interactions.
 We took the entire Planetary Systems Composite Parameters Table (PSCP\footnote{ \url{https://exoplanetarchive.ipac.caltech.edu/cgi-bin/TblView/nph-tblView?app=ExoTbls&config=PSCompPars}}, Section~\ref{sec:data:sps}) from the NASA Exoplanet Archive, as of July 2022, and scanned the systems for available Kepler and TESS light curves~(Section~\ref{sec:data:photometry}).
 We searched a total of 1811 systems and over 7200 light curves from both missions for flares.
-To calculate the amount of excess flaring from star-planet interaction, we then sought out the orbital periods of each system from the literature~(Section~\ref{sec:data:orbitalperiod}).
+To calculate the amount of excess flaring from star-planet interaction, we further required the orbital periods of each system~(Section~\ref{sec:data:orbitalperiod}).
 To compare our measurements to theory, we estimated the expected power of interaction for each system with at least three flares.
-For this, we required further system parameters -- distance between planet and star, stellar rotation period, planetary radius, and stellar luminosity~(Sections~\ref{sec:data:a}-\ref{sec:data:lum}), which we also mostly found in the literature.
+For this, we required further system parameters -- distance between planet and star, stellar rotation period, planetary radius, and stellar luminosity~(Sections~\ref{sec:data:a}-\ref{sec:data:lum}), which we mostly took from the literature.
 We began by compiling the table of system parameters with the PSCP, but verified, supplemented and updated the table with more up-to-date results.
-The parameters for the systems in the final sample of systems are shown in Table~\ref{tab:maintable_lit}.
+The parameters for the systems in the final sample of 25 systems are shown in Table~\ref{tab:maintable_lit}.
 
@@
 \label{sec:data:sps}
-We compiled our sample of star-planet systems from the PSCP, from which we removed controversial planet detections (``pl\_controv\_flag'' set to 1), i.e., detections with existing literature questioning the result.
+We compiled our sample of star-planet systems from the PSCP, from which we removed controversial planet detections (``pl\_controv\_flag'' must be 0), i.e., detections with existing literature questioning the result.
 The resulting catalog contained 2993 transiting and 191 non-transiting systems, from which we picked the innermost known planet in each system.
@@
 The Kepler and TESS missions are unbeaten with respect to long-term optical monitoring of stellar flares.
-Their excellent coverage of orbital phases makes the light curves ideal for our search for orbital phase dependent flare timing.
+Their excellent coverage of orbital phases makes the light curves ideal for our search for orbital phase dependent flaring.
 Between 2009 and 2013, the Kepler space telescope~\citep{koch2010kepler} nearly continuously observed a patch of the sky in the Cygnus-Lyra region.
@@
 
-The Transiting Exoplanet Survey Satellite~(TESS,~\cite{ricker2015transiting}) is an all-sky mission that began operations in 2018, completed two sky scans until summer 2022.
+The Transiting Exoplanet Survey Satellite~[TESS, ][]\citep{ricker2015transiting} is an all-sky mission that began operations in 2018, completed two sky scans until summer 2022.
 It is observing at the time of writing, collecting nearly continuous photometric time series in the $600-1000\,$nm band for $\sim 27\,$d in each observing Sector.
@@
 
-Based on the filtered PSCP table, we use the \texttt{lightkurve}~\citep{lightkurvecollaboration2018lightkurve} software to query the full Kepler archive (quarters Q0-Q17, Data Release 25), and the most recent TESS catalog (July 2022) for their respective 1-min and 2-min/20-s cadence light curves.
+Based on the filtered PSCP table, we use the \texttt{lightkurve}~\citep{lightkurvecollaboration2018lightkurve} Python software to query the full Kepler archive (quarters Q0-Q17, Data Release 25), and the most recent TESS catalog (July 2022) for their respective 1-min and 2-min/20-s cadence light curves.
 In total, we searched 7258 light curves for flares -- 3030 Kepler Quarters, and 4228 TESS Sectors.
@@
 \label{sec:data:a}
-The critical parameter is the distance between the star and the planet, not the semi-major axis itself.
+A critical parameter for the possibility of magnetic SPI and its power is the distance between the star and the planet, not the semi-major axis itself.
 This varies if the orbit is eccentric.
-To account for varying distance, we adopt the mean semi-major axes from the literature, but use a custom estimate for the uncertainty that includes the eccentricity.
+We therefore adopt the mean semi-major axes from the literature, but use a custom estimate for the uncertainty that includes the eccentricity:
 
@@
 The rotation of GJ 674 is consistent between light curve periodograms~\citep{kiraga2007agerotationactivity}, and activity-rotation relations~\citep{boisse2011disentangling} at a $<10\%$ level.
-GJ 3323 only has rotation periods inferred from activity indicators~\citep{Astudillo-defru2017magnetic}, without any periodicity detected in the activity indicators themselves~\citep{astudillo-defru2017harps}.
+GJ 3323 only has rotation periods inferred from activity indicators~\citep{astudillo-defru2017magnetic}, without any periodicity detected in the activity indicators themselves~\citep{astudillo-defru2017harps}.
 The rotation of Proxima Cen is very slow, but consistent between different datasets~\citep{anglada-escude2016terrestrial, kiraga2007agerotationactivity}.
@@
     \item short, leaving a clear peak in the periodogram, and little doubt about the period after ruling out aliases with $P/2$, as with GJ 3082, or
-    \item longer than the Sun's, that is, in the regime where rotation-activity relations are reliable because the stars are in the unsaturated activity regime, as in the case of GJ 674.
+    \item longer than the Sun's, that is, in the regime where rotation-activity relations are reliable because the stars are in the unsaturated activity regime, as in the case of GJ 674, and GJ 3323.
 \end{itemize}
@@
 To obtain them, we gather the Kepler and TESS light curves for all star-planet systems, remove rotational variability trends, search the de-trended light curves for flares, and convert the flare times to orbital phases.
-We then perform a customized Anderson-Darling test on the flare peak time distribution, which yields a p-value for the significance of the SPI signal.
-Finally, we compare these results to the theoretically expected SPI power $P$ in each system.
+We then perform a customized Anderson-Darling test on the flare peak time distribution, which yields a $p$-value for the significance of the SPI signal.
+Finally, we compare these results to the theoretically expected SPI power $P_{xx}$ in each system.
 
@@
 We can then combine them with stellar radius, planetary radius, and semi-major axis to estimate the power of SPI.
-We use the scaling laws from two different magnetic SPI models, which we introduce in Section~\ref{sec:methods:pspi}.
+We use the scaling laws for two different magnetic SPI models, which we introduce in Section~\ref{sec:methods:pspi}.
 
@@
 \label{sec:methods:flaresearch}
-To remove trends and rotational variability from the light curve without losing the flare signal, we use an empirically derived multistep process, implemented as the \texttt{custom\_detrending} method in \texttt{AltaiPony}, a flare science package for light curve analysis~\citep{ilin2021altaipony}.
+To remove trends and rotational variability from the light curve without losing the flare signal, we use an empirically derived multistep process, implemented as the \texttt{custom\_detrending} method in \texttt{AltaiPony}, a flare science Python package for light curve analysis~\citep{ilin2021altaipony}.
 First, we apply a spline fit with a coarse sampling of 30h-averaged values to capture slow rotation with periods above multiple days and non-periodic trends.
@@
 Eventually, we apply two Savitzky-Golay~\citep{savitzky1964smoothing} filters in sequence, with window sizes of 6h and 3h each.
-At this stage, we mask all data points above a $2.5 \sigma$ (or $1.5 \sigma$ for very active stars like AU Mic or Proxima Cen) threshold as flare candidates to prevent the filter from ironing out the flares.
+At this stage, we mask all data points above a $2.5 \sigma$ (or $1.5 \sigma$ for stars like AU Mic or Proxima Cen, which are very active or have very low noise levels, or both) threshold as flare candidates to prevent the filter from ironing out the flares.
 As a final step, we fit exponential functions to the edges of the light curves, if there are data points that deviate more than one standard deviation from the median value, while keeping the flare candidates masked.
@@
 In the de-trended light curves, we search for flares as series of at least three consecutive data points $3\sigma$ above the noise level using the \texttt{AltaiPony} method \texttt{find\_flares}.
-We estimate the noise level as the standard deviation in a rolling window of two hours, while masking deviation above $2.5\sigma$ (or $1.5$ sigma for active stars).
+We estimate the noise level as the standard deviation in a rolling window of two hours, while masking deviation above $2.5\sigma$ (or $1.5\sigma$  for stars like AU Mic and Proxima Cen).
 To capture the exponential tail of the flare, we use the \texttt{addtail} flag in the \texttt{find\_flares} method to continue adding data points to the end of the flare as long as they are $2\sigma$ above the noise threshold.
 
-We vet all flare candidates by eye, and exclude instrumental false positives and physical one like Solar System Objects.
-For each confirmed flare candidate, we calculate the relative amplitude $a$ and equivalent duration $ED$, defined as the integrated flare flux $F_{flare}$ over the duration of the flare, divided by the median flux $F_0$ of the star, integrated over the flare duration~\citep{gershberg1972results}:
+We vet all flare candidates by eye, and exclude instrumental false positives and physical ones like passing Solar System Objects.
+For each confirmed flare candidate, we calculate the relative amplitude $a$ and equivalent duration $ED$, defined as the integrated flare flux $F_{\rm flare}$ over the duration of the flare, divided by the median flux $F_0$ of the star, integrated over the flare duration~\citep{gershberg1972results}:
 \begin{equation}
 \label{eq:ED}
-ED=\displaystyle \int \mathrm dt\, \frac{F_{flare}(t)}{F_0}.
+ED=\displaystyle \int \mathrm dt\, \frac{F_{\rm flare}(t)}{F_0}.
 \end{equation}
-Equivalent duration is the time during which the non-flaring star releases as much energy as the flare.
+Equivalent duration is equal to the time during which the non-flaring star releases as much energy as the flare.
 
@@
 In brief, we first take the number of flares observed in the TESS and Kepler data to calculate a base flare rate for each light curve.
-We then calculate how often each orbital phase has been covered by the data, also for each light curve separately.
+We then calculate how often each orbital phase has been observed, also for each light curve separately.
 With the phase coverage and base flare rate combined, we can tell how many flares we would expect to see in any given phase bin if flares were randomly distributed.
 We then aggregate this number of expected flares per time bin into one expected distribution by summing over all available light curves.
-As a last step, we compare this distribution to the observed one using an Anderson-Darling test.
+As a last step, we compare the expected distribution to the observed one using an Anderson-Darling test.
 We repeat this test with different phase offsets to account for potential biases in sensitivity of the test at different phases.
 
-The only adjustment to the procedure in \cite{ilin2022searching} is that we use four equidistant start phases (i.e., 0, 0.25, 0.5 and 0.75) compared to the 20 used in~\cite{ilin2022searching} to save time, and because the range of derived $p$-values is already well-sampled using four.
+The only adjustment to the procedure in \cite{ilin2022searching} is that we use four equidistant start phases (i.e., 0, 0.25, 0.5 and 0.75) compared to the 20 used in~\cite{ilin2022searching} to save time, because the range of derived $p$-values is already well-sampled using four.
 We adopt the standard deviation of these four $p$-values as the uncertainty on the flaring SPI measurement.
@@
 \label{sec:methods:relvel}
-We calculate the relative velocity between the magnetic field of the star and the planet using stellar rotation period $P_{rot}$, orbital period $P_{\rm orb}$, and semi-major axis $a$.
+We calculate the relative velocity between the magnetic field of the star and the planet using stellar rotation period $P_{\rm rot}$, orbital period $P_{\rm orb}$, and semi-major axis $a$.
 We assume that the large scale magnetic field is co-rotating with the stellar surface, and calculate the relative velocity at the planet's orbital distance:
@@
 \begin{equation}
-    v_{rel} = 2 \pi a \left(\frac{1}{P_{\rm orb}} - \frac{1}{P_{rot}}\right).
+    v_{\rm rel} = 2 \pi a \left(\frac{1}{P_{\rm orb}} - \frac{1}{P_{\rm rot}}\right).
 \end{equation}
 
-We use quadratic error propagation to estimate the uncertainty in $v_{rel}$ with the mean of the upper and lower uncertainty values on the orbital period and rotation period, if both are given, and the uncertainty on semi-major axis $a$ as derived in Sec.~\ref{sec:data:a}.
+We use quadratic error propagation to estimate the uncertainty in $v_{\rm rel}$ with the mean of the upper and lower uncertainty values on the orbital period and rotation period, if both are given, and the uncertainty on semi-major axis $a$ as derived in Sec.~\ref{sec:data:a}.
 
@@
 
-We compared our derived values for $Ro$ and $B$ with existing estimates of coronal emission from~\citet{foster2022exoplanet}.
+We compared our derived values for $R$o and $B$ with existing estimates of coronal emission from~\citet{foster2022exoplanet}.
 We show $L_X/L_{\rm bol}$ as a function of $Ro$ and $B$ in Fig.~\ref{fig:lx}.
 The X-ray emission relation to Rossby number in our sample follows that of stars that are not known to host close-in planets~\citep{wright2011stellaractivityrotation}, spanning both the saturated and unsaturated regime.
-The X-ray emission and our estimated magnetic field closely follow each other, also consistent with stars without known close-in planets~(XXXX).
+The X-ray emission and our estimated magnetic field closely follow each other, also consistent with stars not selected for close-in planets~\citep{reiners2022magnetism}.
 There are two exceptions: GJ 3082 appears underluminous in X-ray compared to its Rossby number and expected magnetic field strength.
@@
         \caption{
-           X-ray luminosity over bolometric luminosity compared to Rossby number (\textbf{upper panel}), and surface magnetic field strength (\textbf{lower panel}).
-Both relations follow those of stars not selected for hosting close-in planets, except for GJ 3323, which is underluminous for its Rossby number, and hence also its estimated magnetic field strength.
+           X-ray luminosity over bolometric luminosity compared to Rossby number (\textbf{upper panel}), and average surface magnetic field strength (\textbf{lower panel}).
+Both relations follow those of stars not selected for hosting close-in planets, except for GJ 3082, which is underluminous for its Rossby number, and hence also its estimated magnetic field strength.
         }
-        \label{fig:coherence_hist}
+        \label{fig:lx}
     \end{centering}
@@
 $B_p$ and $B_*$ are the planetary and stellar field strengths at their poles, respectively; $v_{rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis $a$; and $R_*$ and $R_p$ are the stellar and planetary radii, respectively.
-Since the planetary fields are unknown, we ignore it in the calculations.
-Since we also do not know the stellar field strength at the pole for the vast majority of the stars, we adopt the surface field strength~(Section~\ref{sec:methods:bfield}) as a proxy.
+Since the planetary fields are unknown, we ignore them in the calculation.
+We also do not know the stellar field strength at the pole for the vast majority of the stars, so we adopt the surface field strength~(Section~\ref{sec:methods:bfield}) as a proxy.
 
@@
 
-Third, for comparison, we estimate the power of star-planet interaction generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio}, combining Eqs.~8~and~11 in \citet{kavanagh2022radio} to arrive at
+Third, we estimate the power of star-planet interaction generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio}, combining Eqns.~8~and~11 in \citet{kavanagh2022radio} to arrive at
 
@@
 \end{equation}
-where we approximate the stellar wind density $\rho_W$ with $a^{-2}$ and stellar wind magnetic field at the planetary radius $B_W$ with the surface field strength $B_* a^{-3}$, which result in the total $a^{-2}$ factor.
-
-And fourth, we finally consider the case of an unmagnetized planet with $B_p=0$, in which case Eq.~8 in \cite{kavanagh2022radio} reduces to
+where we replace the stellar wind density $\rho_W$ with its proportionality to $a^{-2}$, and stellar wind magnetic field at the planetary radius $B_W$ with the surface field strength $B_* a^{-3}$, which result in the total $a^{-2}$ factor in the above equation.
+
+And fourth, we also consider the case of an unmagnetized planet with $B_p=0$, in which case Eq.~8 in \cite{kavanagh2022radio} reduces to
 
@@
 
-Lacking $B_p$ and various additional factors that appear in $P_{sb},P_{sb0},P_{aw}$, and  $P_{aw0}$, such as the angle between the wind and the
+Lacking $B_p$, and various additional factors that appear in $P_{sb},P_{sb0},P_{aw}$, and  $P_{aw0}$, such as the angle between the relative velocity and magnetic field of the stellar wind~\citep{kavanagh2022radio}, or the force-free parameter~\citep{lanza2012starplanet}, we restrict ourselves to differential estimates, and normalize all $P_{xx}$ to AU Mic.
 
@@
             \caption{
-            Flare catalog of all star-planet systems observed by Kepler and TESS.
+            Flare catalog of all star-planet systems observed by Kepler and TESS (as of July 2022).
 In transiting multi-planet systems, the orbital phase refers to the innermost planet, with the transit mid-time at phase zero.
@@
            Time span of observation vs.
-coherence time of the rotational (\textbf{top panel}) and orbital (\textbf{bottom panel}) periods, respectively.
-Orbital periods are all known precisely enough, so that the phase uncertainty at the last observed flare is of the order of $10^{-2}$.
-In contrast, in stars with known rotation periods, the precision is often too low, so that the phase of the last flare is often undetermined (ratio on x-axis $\sim 1$).
+coherence time of the rotational (\textbf{upper panel}) and orbital (\textbf{lower panel}) periods, respectively.
+Orbital periods are typically known precisely enough, so that the phase uncertainty at the last observed flare is of the order of $10^{-2}$.
+In contrast, rotation periods are usually less well constrained, so that the phase of the last flare is often undetermined (ratio on x-axis $\geq 1$).
         }
@@
 $Ro$, $B$, and $v_{rel}$, are derived from literature values (Table~\ref{tab:maintable_lit}).
-$P_{xx}$ stands for the power of stretch-and-break ($sb$) and ALfv\'en wing ($aw$) interaction mechanisms, assuming the planet has a magnetic field strength of 1 G.
+$P_{xx}$ stands for the power of stretch-and-break ($sb$) and Alfv\'en wing ($aw$) interaction mechanisms, assuming the planet has a magnetic field strength of 1 G.
 $P_{xx0}$ is the same, but assuming an unmagnetized planet.
@@
 While the distribution of $p$-values is consistent with no interaction, all scenarios indicate lower $p$-values only for high expected powers of interaction.
+See Fig.~\ref{fig:adtest_ro} in the Appendix for the same figure, color-coded by Rossby number.
         }
@@
 We can now consider additional facts about the systems, as well as processes, that may explain the observed trends.
-Beyond the extent of the Alfv\'en radius that decides over the possibility of magnetic interaction in the first place~(Section~\ref{sec:intro:mspi}), orbital eccentricity can further enhance magnetic SPI signal, but is low for most systems in our sample except for K2-25~(Section~\ref{sec:discussion:eccentricity}).
+We consider the extent of the Alfv\'en radius that decides over the possibility of magnetic interaction in the first place~(Section~\ref{sec:discussion:as}), and how orbital eccentricity can further enhance magnetic SPI signal~(Section~\ref{sec:discussion:eccentricity}).
 The observed branching might also be explained by intermittent SPI~(Section~\ref{sec:discussion:intermittency}), but its possible causes are not well known.
@@
 In a system-by-system comparison, we find consistency with the expectation that slowly rotating, likely old, systems can only show local tidal interaction, while rapidly rotating systems with strong magnetic fields can experience both.
+\subsection{Alfv\'en surface}
+\label{sec:discussion:as}
+
+reference \ref{sec:intro:mspi}
+
+how we estimated the AS (Judy's part)
+
+what we think about it (E and J contributions, comments from others  welcome)
 
@@
         \includegraphics[width=\hsize]{figures/PAPER_tidal_AD_test.png}
-        \caption{Deviation from random flare times in phase with $P_{\rm orb}/2$, i.e., in phase with tidal bulges raised on the star, compared to different models of tidal interaction.
+    \caption{Deviation from random flare times in phase with $P_{\rm orb}/2$, i.e., in phase with tidal bulges raised on the star, compared to different models of tidal interaction~(Section~\ref{sec:discussion:tidal}).
            \textbf{Left panel}: The tidal torque in the system for stars with a convective envelope.
@@
 \subsection{Proxima Cen}
-Although Proxima Cen is part of a triple stellar system, we treat it a single star in this work because of the large angular separation to its two companions.
-Proxima Cen b has an eccentricity upper limit of 0.35~\cite{anglada-escude2016terrestrial}.
+Although Proxima Cen is part of a triple stellar system, we treat it a single star in this work because of the large angular separation of over 2 deg to its companions, $\alpha$ Cen AB.
 
@@
 
-\section{Expected power vs. AD test, colorcoded by Rossby number}
+\section{Expected power vs. AD test, color-coded by Rossby number}
 \begin{figure*}[ht!]
@@
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_bg.png}
+        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_Ro.png}
         \caption{
@@
         }
-        \label{fig:adtest_bp}
+        \label{fig:adtest_ro}
     \end{centering}

### 2023-05-23 src/scripts/paper_as_vs_ad.py
add AS figure

@@ -1,0 +1,65 @@
+"""
+Python 3.8 -- UTF-8
+
+Ekaterina Ilin, 2023, MIT License
+
+Script that generates a figure of AD test p-values vs. star-planet distance
+minus Alfvén surface radius for the discussion of whether the AS is larger
+than the planet's orbit.
+"""
+
+
+import pandas as pd
+import matplotlib.pyplot as plt
+import paths
+
+import adjustText as aT
+
+if __name__ == "__main__":
+
+    # read results
+    df = pd.read_csv(paths.data / 'results.csv')
+
+    # read AS
+    AS = pd.read_csv(paths.data / 'AS_estimation_table.csv')
+
+    # merge tables
+    df = df.merge(AS, on='ID')
+
+    # pick only valid values
+    d = df[["ID","a_au",'a_au_err','AS_AU','mean','std']].dropna(how='any')
+
+    # plot
+    plt.figure(figsize=(6.5,5))
+
+    plt.errorbar(d.a_au -  d.AS_AU, d["mean"], 
+                xerr=d.a_au_err, yerr = d["std"],
+                fmt='d', color='olive',markersize=8, elinewidth=0.5)
+
+    txts = []
+    for i, row in d.iterrows():
+        if (row['mean'] < 0.2) | (row['a_au'] - row['AS_AU'] < -0.05):
+            txts.append(plt.annotate(row.ID, (row.a_au - row.AS_AU, row["mean"]),
+                                    fontsize=12))
+
+    # vertical dashed line at 0
+    plt.axvline(0, color='k', linestyle='--', lw=2)
+
+    # shade region where AS is larger than a
+    plt.axvspan(0, -0.3, alpha=0.2, color='orange')
+
+    # plt.xscale('log')
+    plt.yscale('log')
+
+    # adjust texts
+    aT.adjust_text(txts, arrowprops=dict(arrowstyle="-", color='k', lw=0.5))
+
+    plt.xlim(-0.28,0.22)
+    plt.ylim(5e-3,1)
+
+    plt.xlabel('planet-star distance - Alfvén surface radius [au]', fontsize=14)
+    plt.ylabel('p-value of AD test', fontsize=14)
+
+    plt.tight_layout()
+
+    plt.savefig(paths.figures / 'paper_AS_vs_AD.png', dpi=300)

### 2023-05-24 src/scripts/paper_table_tidal.py
one more try

@@ -45,6 +45,8 @@ def g(row, col, oneerr=False):
         except:
             n = 1
      
+        if n==0:
+            n=1
         if n < 0:
             # convert values in row to int
             
@@ -85,8 +87,11 @@ if __name__ == "__main__":
     # take absolute value of pl_bmassjerr2
     # df.M_pl_low_err = np.abs(df.M_pl_low_err)
 
-    # take absolute value of st_masserr2
-    # df.M_star_low_err = np.abs(df.M_star_low_err)
+    # take neg value of st_masserr2
+    df.M_star_low_err = - df.M_star_low_err
+
+    # take neg value of pl_bmassjerr2
+    df.M_pl_low_err = - df.M_pl_low_err
 
     # take absolute value of torque_conv_up_err and torque_conv_low_err
     # df.torque_conv_up_err = np.abs(df.torque_conv_up_err)
@@ -97,20 +102,27 @@ if __name__ == "__main__":
                 r"$M_p$ [$M_\oplus$]",
                 r"log$_{10} 10^{-8} \Delta g / g$",
                 r"log$_{10} \tau_{\rm tide}$ [yr]",
-                r"$10^{-20} \frac{\partial L_{conv}}{\partial t}$"
+                r"$10^{-18} \frac{\partial L_{conv}}{\partial t}$"
                 r" $\left[M_\odot \left(\frac{km}{s}\right)^2\right]$",
                 ]
 
-    # convert "grav_pert",  "tidal_disip_timescale", "torque_conv" and errors to log10
-    df["grav_pert"] = np.log10(df["grav_pert"] * 1e8)
-    df["grav_pert_up_err"] = np.log10(df["grav_pert_up_err"] * 1e8)
-    df["grav_pert_low_err"] = np.log10(df["grav_pert_low_err"] * 1e8)
+    
+
+    df["grav_pert"] = df["grav_pert"] * 1e8
+    df["grav_pert_up_err"] = df["grav_pert_up_err"] * 1e8
+    df["grav_pert_low_err"] = df["grav_pert_low_err"] * 1e8
+    df["grav_pert_up_err"] = np.log10(df["grav_pert"] + df["grav_pert_up_err"]) - np.log10(df["grav_pert"])
+    df["grav_pert_low_err"] = np.log10(df["grav_pert"] - df["grav_pert_low_err"]) - np.log10(df["grav_pert"])
[…]

### 2023-05-24 src/scripts/paper_as_vs_ad.py
new figure with uncertainties on AS estimate

@@ -10,6 +10,7 @@ than the planet's orbit.
 
 
 import pandas as pd
+import numpy as np
 import matplotlib.pyplot as plt
 import paths
 
@@ -27,13 +28,19 @@ if __name__ == "__main__":
     df = df.merge(AS, on='ID')
 
     # pick only valid values
-    d = df[["ID","a_au",'a_au_err','AS_AU','mean','std']].dropna(how='any')
+    d = df[["ID", "a_au", 'a_au_err', 'AS_AU', 'AS_error_upper_AU',
+            'AS_error_lower_AU', 'mean', 'std']].dropna(how='any')
+
+    print(d.shape)
 
     # plot
     plt.figure(figsize=(6.5,5))
 
+    d["error_up"] = np.sqrt(d.a_au_err**2 + d.AS_error_upper_AU**2)
+    d["error_low"] = np.sqrt(d.a_au_err**2 + d.AS_error_lower_AU**2)
+
     plt.errorbar(d.a_au -  d.AS_AU, d["mean"], 
-                xerr=d.a_au_err, yerr = d["std"],
+                xerr=[d.error_low, d.error_up], yerr = d["std"],
                 fmt='d', color='olive',markersize=8, elinewidth=0.5)
 
     txts = []

### 2023-05-30 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Author list
-\author{Ekaterina Ilin}
-\author{Katja Poppenh\"ager}
-\author{Judy Chebly}
-\author{Nikoleta Ilic}
+\author[0000-0002-6299-7542]{Ekaterina Ilin }
+\affiliation{Leibniz Insitute for Astrophysics Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany}
+
+\author[0000-0003-1231-2194]{Katja Poppenh\"ager}
+\affiliation{Leibniz Insitute for Astrophysics Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany}
+\affiliation{Institute for Physics and Astronomy, University of Potsdam, Karl-Liebknecht-Strasse 24/25, 14476 Potsdam, Germany}
+
+\author[0000-0003-0695-6487]{Judy Chebly}
+\affiliation{Leibniz Insitute for Astrophysics Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany}
+\affiliation{Institute for Physics and Astronomy, University of Potsdam, Karl-Liebknecht-Strasse 24/25, 14476 Potsdam, Germany}
+
+\author[0000-0001-7579-3728]{Nikoleta Ilic}
+\affiliation{Leibniz Insitute for Astrophysics Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany}
+\affiliation{Institute for Physics and Astronomy, University of Potsdam, Karl-Liebknecht-Strasse 24/25, 14476 Potsdam, Germany}
+
+\author[0000-0001-5052-3473]{Juli\'an D. Alvarado-G\'omez}
+\affiliation{Leibniz Insitute for Astrophysics Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany}
 
@@
 One of the most surprising results in exoplanet research is the diversity of star-planet system architectures.
-The past two decades revealed that planets can occur in orbits of only a few stellar radii~[e.g., ][]\citep{sanchis-ojeda2014study} that they could almost be considered to live inside the stellar atmosphere.
+The past two decades revealed that planets can occur in orbits of only a few stellar radii~\citep[e.g., ][]{sanchis-ojeda2014study} that they could almost be considered to live inside the stellar atmosphere.
 At this proximity, the planet exerts force, tidal and magnetic, both short- and long-term, on its host -- a phenomenon largely unknown to the Solar System.
@@
 \begin{figure}[ht!]
-    \script{paper_lxl_plots.py}
+    \script{paper_lx_plots.py}
     \begin{centering}
@@
 
-reference \ref{sec:intro:mspi}
-
-how we estimated the AS (Judy's part)
+\begin{figure}[t]
+    \script{paper_as_vs_ad.py}
+    \begin{centering}
+        \includegraphics[width=\hsize]{figures/PAPER_AS_vs_AD.png}
+    \caption{Magnetic flaring star-planet interaction strength ($p$-value of AD-test) vs.
+the innermost planet's location relative to the Alfv\'en surface radius.
+The innermost planets in the systems left of the dashed line (\textbf{shaded region}) are likely in the sub-Alfv\'enic regime.
+Only these planets can induce flares in the stellar atmosphere.
+See Section~\ref{sec:discussion:as} for the procedure we used to estimate the Alfv\'en surface radius.
+}
+        \label{fig:as}
+    \end{centering}
+\end{figure}
+
+Magnetic star-planet interaction can only take place if the planet spends at least a part of its orbit in the sub-Alfv\'enic regime~(see Section~\ref{sec:intro:mspi}).
+
+Fig.~\ref{fig:as}
+
+The average Alfv\'en surface size ($\overline{AS}_{R}$) was estimated using the power law  (Eq.~\ref{AS_estimation}) established by Chebly et al. (under revision):
+
+\begin{equation}
+    \log \overline{AS_{\rm R}} = (0.44 \pm 0.05) \log B_{\rm r}^{\rm max} + (0.54 \pm 0.08)\label{AS_estimation}
+\end{equation}
+
+This relation links the mean AS size with the maximum large-scale radial magnetic field ($B_{\rm r}^{\rm max}$) obtained in Zeeman-Doppler Imaging reconstructions  \textcolor{red}{(references here)}.
+The relation was derived from 3D~MHD stellar wind simulations cool main sequence stars (F, G, K, and M), which incorporated observed ZDI maps as boundary condition for the stellar radial magnetic field (for more details on the models see Chebly et al.
+2023).
+However, the stellar magnetic field~($B$) in this work (Table XX), derived from the Rossby number of each star (Eq.
+XX), corresponds to the total, unsigned magnetic field strength on the stellar surface.
+As such, it is necessary to estimate how $B_{\rm r}^{\rm max}$ relates to $B$.
+
+In \cite{reiners2022magnetism}, it was reported that for Sun-like stars with a total magnetic field strength of up to 2000~G, the longitudinal magnetic field derived from Stokes V spectropolarimetric observations ($B_{\rm V}$) accounts for $\sim$\,$10$\% of the total magnetic field.
+\textbf{add ref.} showed that this trend also holds for M-dwarfs with magnetic fields up to 4000~G.
+Therefore, as a first assumption, we consider that the longitudinal magnetic field of our stars would reach 15\% of the total magnetic field (i.e.
+$B_{\rm V} = 0.15B$), given that most systems in our sample have B~$>$~2000 G.
+
+The second assumption is that $B_{\rm V}$ can be equal to or lower than the maximum radial magnetic field strength.
+This is because, unlike the maximum radial magnetic field, which is measured at a specific location on the stellar surface, $B_{\rm V}$ may suffer from cancellation as it is measured across a specific area.
+In this context, the maximum radial magnetic field strength can be considered as the upper limit of $B_{\rm V}$ (15\%~of~B~=~$B_{\rm r}^{\rm max}$).
+Under these two assumptions, we will be estimating  an upper limit on $\overline{AS}_{R}$.
 
 what we think about it (E and J contributions, comments from others  welcome)
+TAP 26 and KOI-12 appear sub-Alfv\'enic in our estimate. So it seems unlikely that the absence of interaction is caused by the planets orbiting outside the Alfv\'en radius.
 
@@
 For Kepler-42 b, we used  $M_p=0.1-2.06M_\oplus$ that covers pure rock to pure iron compositions in \citet{muirhead2012characterizing}, and adopted the logarithmic mean for our estimate.
-Kepler-1558 c has a similar radius to Kepler-42 b, i.e., most likely a bare core planet, so we used the same density range to estimate its mass.
+Kepler-1558 c has a similar radius to Kepler-42 b, i.e., most likely a bare core planet, so we used density ranging from Earth bulk density to pure rock to estimate its mass.
 We also adopt the upper limit of $5M_J$ for HIP 67522, but use the lower error from \citet{chen2017probabilistic}.
@@
 \section*{Acknowledgements}
+
 This paper includes data collected by the TESS mission, which are publicly available from the Mikulski Archive for Space Telescopes (MAST).
@@
 \section*{Data Availability}
-All analysis script can be found under https://github.com/ekaterinailin/flaring-spi/. All data and scripts used to creat the tables and figures in this paper can be found under
-
+All data used in this study are publicly available in their respective archives.
+This study used the reproducibility software \href{https://github.com/showyourwork/showyourwork}{\showyourwork}
+\citep{luger2021mappinga} to create all figures, format all tables, and compile the manuscript.
+Each figure links to the dataset stored on Zenodo (\url{ZENODO LINK} and XXXX integration TBD), and to the script that produced the figure in the git repository~\url{https://github.com/ekaterinailin/flaring-spi-paper}.
+The git repository that produces the data stored on Zenodo is publicly available at \url{https://github.com/ekaterinailin/flaring-spi}.
 \bibliography{bib}

### 2023-05-31 src/scripts/paper_adtest_vs_value_scatterplots.py
update figures with correct sigma-levels and some layout changes

@@ -23,9 +23,9 @@ def get_sigma_values():
     """Define the sigma values."""
 
     # define sigma values
-    onesigma = 1 - .342*2
-    twosigma = 1 - .342*2 - .136*2
-    threesigma = 1 - .342*2 - .136*2 - .021*2
+    onesigma = 0.3173
+    twosigma = 0.0455
+    threesigma = 0.0027
     
     # put them in a list
     sigmas = [onesigma, twosigma, threesigma]
@@ -305,11 +305,11 @@ def make_adtest_figure(df, value, valuelabel, legend, labels, ext, ax, leg=False
 
     # legend
     if leg == True:
-        ax.legend(legend, labels, loc=(0, 0.07), fontsize=15)
+        ax.legend(legend, labels, loc=(0, 0.08), fontsize=15)
 
     # limits
     ax.set_xlim(data[f"{value}_low"].min() * 0.85, data[f"{value}_high"].max() * 1.15)
-    ax.set_ylim(1.5e-3, 1)
+    ax.set_ylim(2e-3, 1)
 
     # adjust label positions
     adjust_text(texts, arrowprops=dict(arrowstyle="-", color='k', lw=0.5), ax=ax)
@@ -379,10 +379,10 @@ if __name__ == "__main__":
 
     columns = ["p_spi_sb_bp1_norm", "p_spi_sb_bp0_norm",
               "p_spi_aw_bp1_norm", "p_spi_aw_bp0_norm"]
-    xlabels = [r"$\sim$ P$_{sb}$  @ B$_p$=1G",
-              r"$\sim$ P$_{sb}$  @ B$_p$=0G",
-              r"$\sim$ P$_{aw}$  @ B$_p$=1G",
-              r"$\sim$ P$_{aw}$  @ B$_p$=0G"]
+    xlabels = [r"$\sim$ P$_{sb}$ (stretch-and-break interaction with magnetized planet)",
+              r"$\sim$ P$_{sb0}$  (stretch-and-break interaction with unmagnetized planet)",
+              r"$\sim$ P$_{aw}$  (Alfvén wing interaction with magnetized planet)",
+              r"$\sim$ P$_{aw0}$  (Alfvén wing interaction with unmagnetized planet)"]
 
     # ------------------------------------------------------------
     # DISTANCE

### 2023-05-31 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 In these systems, the planets become in-situ probes of the extended stellar magnetic field.
-As they move, they can trigger flares on the stellar surface.
+As they move, they are expected to trigger flares on the stellar surface.
 Until recently, however, searches for such planet-induced flaring suffered from small sample sizes, and poor orbital phase coverage.
@@
     In this work, we used the excellent phase coverage of the archives of Kepler and the Transiting Exoplanet Survey Satellite to search for star-planet systems with flaring star-planet interactions.
-We compiled a catalog of all their flares, and searched for planet-induced flaring, i.e., flares clustering in phase with the planet's orbit.
+We compiled a catalog of all their flares, and searched for planet-induced flaring, i.e., flares clustering in phase with the planet's orbital phase.
 
@@
 On the other hand, measuring in what ways and how much close-in planets alter their hosts' behavior can provide important insights into the habitability of the entire system~\citep{shkolnik2018signatures}.
-Even if they orbit far inside the habitable zone, such planets probe the system's space weather and mass loss by revealing the extent of the Alfv\'en zone through SPI~\citep{kavanagh2021planetinduced, chebly2022destination}.
+Even if they orbit far inside the habitable zone, such planets probe the system's space weather and mass loss~~\citep{cohen2011dynamics, cohen2015interaction, hazra2022impact} by revealing the extent of the Alfv\'en zone through SPI~\citep{kavanagh2021planetinduced, chebly2022destination}.
 % Prospectively, planet-induced stellar activity could quantify otherwise difficult to measure planetary properties such as the strength and extent of their magnetic field~\citep{cauley2019magnetic}.
@@
 \label{sec:intro:flares}
-In this study, we will look at stellar flares as another way of dissipating the energy deposited in the magnetic field.
+In this study, we will look at stellar flares as another way of dissipating the energy stored in the magnetic field.
 Flares are strong and impulsive eruptions released by reconnection and subsequent relaxation of field lines in the corona~\citep{svestka1976solar,priest2002magnetic}.
@@
 Depending on the system's viewing geometry, i.e., the inclination of the rotation axis, the spin-orbit (mis-)alignment, and the extent and configuration of the large scale magnetic field -- the footpoint could be always in view, or never.
-In expectation, however, in star-planet systems with favorable viewing geometries and magnetic field strengths and configurations, the footpoint visibility will be modulated in phase with the planetary orbit.
+In expectation, however, in star-planet systems with favorable viewing geometries and magnetic field strengths and configurations, the footpoint visibility will be modulated in phase with the planetary orbit~(see, e.g., Fig.~4 in \citet{strugarek2019chasing} for an illustration XXXX maybe make my own sketch?
+XXXX).
 The resulting phase preference of planet-induced flares introduces a deviation from a random distribution of flares.
@@
 In brief, we first take the number of flares observed in the TESS and Kepler data to calculate a base flare rate for each light curve.
-We then calculate how often each orbital phase has been observed, also for each light curve separately.
+We then calculate how often each orbital phase has been observed, also for each light curve separately, to ensure that the different detection thresholds for TESS and Kepler do not bias the base rate.
 With the phase coverage and base flare rate combined, we can tell how many flares we would expect to see in any given phase bin if flares were randomly distributed.
@@
 \begin{eqnarray}
-    B &= 199\,\text{G} \cdot R\rm o^{-1.26\pm 0.1} \;(\text{if}\; Ro > 0.13) \\
-    B &= 2050\,\text{G} \cdot R\rm o^{-0.11\pm 0.03} \;(\text{if}\; Ro < 0.13) 
+    B &= 199\,\text{G} \cdot R\rm o^{-1.26\pm 0.1} \;(\text{if}\; Ro > 0.13) \label{Eq3}\\
+    B &= 2050\,\text{G} \cdot R\rm o^{-0.11\pm 0.03} \;(\text{if}\; Ro < 0.13) \label{Eq4}
 \end{eqnarray}
@@
 
-We compared our derived values for $R$o and $B$ with existing estimates of coronal emission from~\citet{foster2022exoplanet}.
-We show $L_X/L_{\rm bol}$ as a function of $Ro$ and $B$ in Fig.~\ref{fig:lx}.
+We compared our derived values for $R$o and $B$ with existing estimates of coronal emission.
+We show $L_X/L_{\rm bol}$ obtained from~\citet{foster2022exoplanet} as a function of $Ro$ and $B$ in Fig.~\ref{fig:lx}.
 The X-ray emission relation to Rossby number in our sample follows that of stars that are not known to host close-in planets~\citep{wright2011stellaractivityrotation}, spanning both the saturated and unsaturated regime.
@@
 
-We repeated the coherence calculation for $P_{rot}$, and found that the ratio is $>0.1$ for most stars~(Figure~\ref{fig:coherence_hist}, top panel), so that a statistical analysis of rotational flare modulation is not feasible.
-
 \citet{fischer2019timevariable} argue that the synodic period, at which the sub-planetary point crosses the same (magnetic) surface element on the star, may result in a clearer interaction signal, because a magnetically active region that is prone to planet-induced flares, will be passed only once per that period.
-However, the uncertainty in $P_{\rm rot}$ does not allow us to search for modulation with synodic period.
-We argue, however, that in a transiting system with high orbital inclination, the effect with synodic period reduces to modulation with the orbital period:
-
-If the orbital axis inclination is high, then the passage will regularly occur on the back of the star relative to the observer.
+However, we repeated the coherence calculation for $P_{rot}$, and found that the ratio is $>0.1$ for most stars~(Figure~\ref{fig:coherence_hist}, top panel), so that a statistical analysis of rotational flare modulation is not feasible.
+%We argue, however, that in a transiting system with high orbital inclination, the effect with synodic period reduces to modulation with the orbital period:
+
+%If the orbital axis inclination is high, then the passage will regularly occur on the back of the star relative to the observer.
 The true period will therefore be additionally modulated by the visibility, resulting in an intermittency of the signal.
@@
 Additionally, if there are many active regions (at the same time, or in sequence) that produce flares when the sub-planetary footpoint passes across, the effect with the synodic period further converges to a modulation with orbital period.
-In our sample, the observing baseline is multiple years long for many systems.
+%In our sample, the observing baseline is multiple years long for many systems.
 Most stars, even the most rigidly rotating late M dwarfs, show variability in their spot modulation on such long timescales~\citep[e.g.,][]{giles2017kepler,davenport2015spots, namekata2019lifetimes}).
@@
 \label{sec:results:phasedist}
-Our custom Anderson-Darling test compares the measured distribution of orbital phases of the flares to the expected distribution, and returns the significance of the deviation between the two.
+Our custom Anderson-Darling test compares the measured distribution of orbital phases of the flares to the expected distribution~(see Section~\ref{sec:methods:adtest}), and returns the significance of the deviation between the two.
 In the expected distribution, the same number of flares would be distributed randomly across all phases, as the overwhelming majority of studies looking for variation with rotational phase suggest~\citep[see, e.g.,][]{doyle2018investigating,howard2021evryflare}.
@@
 Table~\ref{tab:maintable_der} lists the $p$-values for each star-planet system.
-There is no star-planet system for which we find a $>3\sigma$ signal of star-planet interaction in our sample.
+There is no star-planet system for which we find a $>3\sigma$ ($p<0.0027$) signal of star-planet interaction in our sample.
 However, overall, the significance of the deviation increases with higher expected power $P_{xx}$ of interaction, where the subscript denotes different scenarios introduced in Section~\ref{sec:methods:pspi}.
@@
 
-Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with or without planetary magnetic field), there are two branches on the high end of expected powers.
+Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with magnetized or unmagnetized planets), there are two branches on the high end of expected powers.
 On one branch, the significance of the measured interaction is correlated with the expected power $P_{xx}$.
@@
 AD test results, assuming four different scenarios, color-coded by stellar surface field strength.
-Top row: Stretch-and-break scenario.
-Bottom row: Alfv\'en wing scenario.
-Left column: assuming $B_p=1\,$G.
-Right column: assuming $B_p=1\,$G.
+\textbf{Top panels}: stretch-and-break scenario.
+\textbf{Bottom panels}: Alfv\'en wing scenario.
+\textbf{Left panels}: assuming a magnetized planet.
+\textbf{Right panels}: assuming an unmagnetized planet.
 While the distribution of $p$-values is consistent with no interaction, all scenarios indicate lower $p$-values only for high expected powers of interaction.
@@
 2023).
-However, the stellar magnetic field~($B$) in this work (Table XX), derived from the Rossby number of each star (Eq.
-XX), corresponds to the total, unsigned magnetic field strength on the stellar surface.
-As such, it is necessary to estimate how $B_{\rm r}^{\rm max}$ relates to $B$.
-
-In \cite{reiners2022magnetism}, it was reported that for Sun-like stars with a total magnetic field strength of up to 2000~G, the longitudinal magnetic field derived from Stokes V spectropolarimetric observations ($B_{\rm V}$) accounts for $\sim$\,$10$\% of the total magnetic field.
+However, the stellar magnetic field~($B$) in this work (Table~\ref{tab:maintable_der}), derived from the Rossby number of each star (Eq.~\ref{Eq3}, \ref{Eq4}), corresponds to the total, unsigned magnetic field strength on the stellar surface.
+As such, it is necessary to estimate how $B_{\rm r}^{\rm max}$ could be related to $B$.
+
+In \cite{reiners2022magnetism} it was reported that for Sun-like stars with a total magnetic field strength of up to 2000~G, the longitudinal magnetic field derived from Stokes V spectropolarimetric observations ($B_{\rm V}$) accounts for $\sim$\,$10$\% of the total magnetic field.
 \textbf{add ref.} showed that this trend also holds for M-dwarfs with magnetic fields up to 4000~G.
@@
 
-The second assumption is that $B_{\rm V}$ can be equal to or lower than the maximum radial magnetic field strength.
-This is because, unlike the maximum radial magnetic field, which is measured at a specific location on the stellar surface, $B_{\rm V}$ may suffer from cancellation as it is measured across a specific area.
-In this context, the maximum radial magnetic field strength can be considered as the upper limit of $B_{\rm V}$ (15\%~of~B~=~$B_{\rm r}^{\rm max}$).
-Under these two assumptions, we will be estimating  an upper limit on $\overline{AS}_{R}$.
-
-what we think about it (E and J contributions, comments from others  welcome)
-TAP 26 and KOI-12 appear sub-Alfv\'enic in our estimate. So it seems unlikely that the absence of interaction is caused by the planets orbiting outside the Alfv\'en radius.
+The second assumption is that $B_{\rm V}$ will match the maximum radial magnetic field in a ZDI reconstruction.
+Since $B_{\rm V}$ is integrated over the visible surface of the star, this assumption will only hold if for an observing phase containing the strongest large-scale radial magnetic region, the effect from cancellation of opposite polarities is small.
+As such, in all other rotational phases we expect $B_{\rm V} < B_{\rm r}^{\rm max}$.
+Therefore, by assuming $B_{\rm V} = B_{\rm r}^{\rm max}$ we are effectively taking an upper limit on the longitudinal magnetic field strength, which will be translated\footnote[3]{Naturally this will also depend on how good our $15$\% match between $B$ and $B_{\rm V}$ is to reality.} in our estimated values of $\overline{AS}_{R}$.
+
+\textcolor{blue}{what we think about it (E and J contributions, comments from others  welcome)
+TAP 26 and KOI-12 appear sub-Alfv\'enic in our estimate.
+So it seems unlikely that the absence of interaction is caused by the planets orbiting outside the Alfv\'en radius.} \textcolor{red}{JDAG: Thats a good point.
+However, I think being inside the AS is a required but not sufficient condition for the type of SPI that you are looking for.
+Because you are searching for flares, you need reconnection + particle acceleration (which are the precursors/drivers of the flare emission observed on different wavelengths).
+While the coronal material is expected to provide the particles (at least in closed-field Active Regions -- if the reconnection takes place in open-field line regions, the plasma density there is usually low which would also yield weak EM signatures as those are typically a function of $\rho$), one of the difficulties I see is that in the star-planet system, the reconnection of the magnetic field is more likely to occur in the planet end rather than on the stellar end (simply because the AR field strength is probably larger than the planetary field).
+As such, the field topology will be more 'resistant' closer to the star than to the planet, facilitating the re-organization in the latter case compared to the former.
+Planetary outflows falling back to the star could help to trigger some instabilities, but those would depend on whether or not the planet is losing any significant mass (which we probably don't know for these targets).
+There's of course more to it than just field strength or accretion, with things like the torsion and helicity of the field among others (which is why the likelihood of a solar AR to host a flare is not only determined by field strength but also by its topology/complexity), but all of that is too complicated or even impossible to estimate here.
+The bottom line is that there are multiple reasons that could explain why those two stars that lie deep in the sub-Alfv\'enic regime show no signs of flaring SPI which, without a better characterization of each individual system + some 3D modelling, are very hard to ascertain.}
 

### 2023-05-31 src/scripts/paper_tidal_interaction.py
marked mpsini

@@ -26,6 +26,13 @@ if __name__ == "__main__":
     # read the tidal interaction strength table with the AD test results
     res = pd.read_csv(paths.data / "TIS_with_ADtests.csv", index_col=0)
 
+
+    # RV IDs
+    rvs = ["Proxima Cen", "TAP 26", "GJ 3082", "GJ 3323", "GJ 687" , "YZ Cet", "GJ 674"]
+
+    # add a column that is 1 for RV stars and 0 for others
+    res["RV"] = [1 if ID in rvs else 0 for ID in res.ID.values]
+
     # blue when convective envelope is spinning faster, and transferring angular momentum to the planet
     res["color_conv"] = ["blue" if np.sign(torque)==1 else "grey" for torque in res["torque_conv"].values]
     
@@ -59,19 +66,41 @@ if __name__ == "__main__":
         # plot the data
         # torque conv is the model, use appropriate color, otherwise grey
         if model == "torque_conv":
-            for color, g in res.groupby("color_conv"):
-                xerr = np.abs(np.asarray([g[model + "_low_err"], np.abs(g[model + "_up_err"])]))
-                print(xerr)
-                ax.errorbar(g[model],g["mean"], xerr=xerr,
-                            yerr=g["std"], label=color, 
-                        color=color, fmt="X", markersize=7, elinewidth=0.3)
+            for color, h in res.groupby("color_conv"):
+                
+                # group by RV and non-RV
+                for rv, g in h.groupby("RV"):
+
+                    xerr = np.abs(np.asarray([g[model + "_low_err"], np.abs(g[model + "_up_err"])]))
+                   
+                    if rv == 1:
+                        ax.errorbar(g[model],g["mean"], xerr=xerr,
+                                    yerr=g["std"], label=color, 
+                                color=color, fmt="X", markersize=7, elinewidth=0.3)
+                    else:
+                        ax.errorbar(g[model],g["mean"], xerr=xerr,
+                                    yerr=g["std"], label=color, 
+                                color=color, fmt="o", markersize=7, elinewidth=0.3)
+                
           
         else:
-            xerr = np.abs(np.asarray([res[model + "_low_err"], np.abs(res[model + "_up_err"])]))
+            
 
-            ax.errorbar(res[model],res["mean"], xerr=xerr,
-                        yerr=res["std"], label=model, 
-                       color="grey", fmt="X", markersize=7, elinewidth=0.3)
+            # group by RV and non-RV
+            for rv, g in res.groupby("RV"):
[…]

### 2023-05-31 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 It is also the only star in our sample, for which this threshold makes a difference in the significance of the Anderson-Darling test.
-However, we note that we lose four systems by applying this threshold -- GJ 393, Kepler-411, Kepler-138, and Kepler-1084.
+However, we note that we lose five systems by applying this threshold -- GJ 393, Kepler-411, Kepler-138, GJ 1061, and Kepler-1084.
 We note that the flares (with $ED<1\,$s) in all of these systems are consistent with random flare phases within $1\sigma$.
@@
 
-The only single star system excluded is GJ 1061.
+%The only single star system excluded is GJ 1061.
 The star is lacking a stellar rotation period estimate, which we need to calculate the magnetic field, and $v_{rel}$.
 \citet{dreizler2020reddots} estimate that it is a fairly slow rotator with a period between 50 and 200 days, so we do not expect it to have a strong magnetic field anyway.
+TURNS OUT IT DOES NOT HAVE ENOUGH FLARES FOR THE ANALYSIS
 
@@
 \label{sec:results:individualstars:proxima}
-We do not detect a deviation from intrinsic flaring on Proxima Cen, consistent with numerical models that place Proxima Cen b well outside the sub-Alfv\'enic zone~\citep{kavanagh2021planetinduced}.
+We do not detect a deviation from intrinsic flaring on Proxima Cen, consistent with numerical models that place Proxima Cen b well outside the sub-Alfv\'enic zone~\citep{gomez2020earthlike, kavanagh2021planetinduced, garraffo2022revisiting}.
 However, this might not entirely exclude Proxima Cen from the search for flaring star-planet interaction.
 The tentatively detected Proxima Cen d, a planet further in, at 0.029 au, or 5 day orbital period~\citep{faria2022candidate, artigau2022linebyline} could still cause flaring star-planet interactions.
+Depending on the phase of the activity cycle, Proxima Cen d may be in the sub-Alf\'enic regime during Proxima Cen's activity maximum~\citep{gomez2020earthlike}.
 However, the orbital period of the tentative planet is so uncertain at this point that its coherence time~(Section~\ref{sec:results:coherence}) is shorter than the roughly 2yr observing baseline of Proxima Cen, preventing us from accurately measuring the flare phases.
@@
 AU Mic is a 16-29 Myr old pre-main sequence M0-M1 dwarf with a strong magnetic field of about $3010\pm220\,$G obtained from Zeeman broadening measurements~\citep{reiners2022magnetism}.
-The innermost Neptune-sized planet, AU Mic b, could be both inside the sub-Alfv\'enic zone if the star's mass loss rate is relatively low at about 30 times the solar value or lower.
+The innermost Neptune-sized planet, AU Mic b, could be both inside the sub-Alfv\'enic zone if the star's mass loss rate is relatively low at about 30 times the solar value or lower~\citep{alvarado-gomez2022simulating}.
 If the mass loss rate is high, exceeding the solar value by a factor of several hundreds, AU Mic b could orbit in the super-Alfv\'enic zone, and become unable to experience any planet-induced flaring.
@@
 Both the expected power of interaction, and the measured deviation, are remarkably similar to the AU Mic system.
-Interestingly, K2-25 b is in a presumably similar environment to GJ 436 b, but does not show the atmospheric escape in Ly$\alpha$ that the latter famously exhibits~\citep{rockcliffe2021lya}.
-This might in part be due to the stellar wind conditions around K2-25 b.
+Interestingly, K2-25 b is in a presumably similar environment to GJ 436 b, but does not show the atmospheric escape in Ly$\alpha$ that the latter famously exhibits, which might be due to high speed stellar winds that suppress atmospheric escape~\citep{rockcliffe2021lya, carolan2020dichotomy, vidotto2020stellar}.
 Further investigation of magnetic star-planet interactions, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius, especially accounting for its moderately high eccentricity~(see also Section~\ref{sec:discussion:eccentricity}).
 
-In Figure~\ref{fig:adtest_bp}, TOI-540 clusters with K2-25 and AU Mic -- a fast rotating M dwarf with its innermost planet in a $1.24\,$d orbit~\citep{ment2021toi}.
+In Figure~\ref{fig:adtest_bp}, K2-25 and AU Mic form a cluster with TOI-540 -- a fast rotating M dwarf with its innermost planet in a $1.24\,$d orbit~\citep{ment2021toi}.
 Compared to the other two systems, its innermost planet is not a Neptune, but a rocky planet slightly smaller than Earth~\citep{ment2021toi}.
-It is a relatively smaller obstacle in the host's magnetic field, yet the interaction is expected to be of a similar magnitude due to the strongest inferred magnetic field, and closest orbit among the three systems.
+It is a relatively smaller obstacle in the host's magnetic field, yet the interaction is expected to be of a similar magnitude due to the strongest inferred stellar magnetic field, and closest orbit among the three systems.
 
@@
 Here, the reason could be that KOI-12 b is in fact super-Alfv\'enic due to the relatively wide orbit compared to TAP 26 and HIP 67522.
+However, our estimate of the Alf\'en radius place KOI-12 b in the sub-Alfv\'enic regime~(see Fig.~\ref{fig:as}), although the scaling law applied there may be inaccurate for post-main sequence stars.
 Intermittent interaction might play a role here as well, and could be favored if future observations capture episodes during which the interaction is 'on'.
@@
 In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e\leq 0.35$.
-The exception is K2-25, with a relatively high $e=0.45$.
+The exception is K2-25, with a relatively high $e\approx0.43$.
 If periastron passage in K2-25 occurs when the planet is in front of the star relative to the observer, the visibility effect of the interaction footpoint is further increased by the narrow phase range of the periastron passage.
@@
 Consider a system, where orbit, and stellar spin and stellar magnetic dipole are aligned.
-If the footpoint's latitude is low, i.e., close to the orbital plane, the orbital plane can be inclined to a high degree, and the footpoint will still periodically move in and out of view.
+If the magnetic footpoint's latitude is low, i.e., close to the orbital plane, the orbital plane can be inclined to a high degree, and the footpoint will still periodically move in and out of view.
 However, if the footpoint's latitude is high, we need to observe the star-planet system nearly edge-on to be able to measure a modulation of activity with the planet's orbital phase.
@@
 Their ZD map reveals magnetic field concentrations close to the rotational pole, and the brightness maps also show a dark spot in the same location.
-If the orbital plane is aligned with the stellar rotation axis, the absence of phase-correlated flaring in TAP 26 could be explained by the footpoint of interaction being always in view, and therefore never modulated.
+If the orbital plane axis is aligned with the stellar rotation axis, the absence of phase-correlated flaring in TAP 26 could be explained by the footpoint of interaction being always in view, and therefore never modulated.
 
@@
     \caption{Deviation from random flare times in phase with $P_{\rm orb}/2$, i.e., in phase with tidal bulges raised on the star, compared to different models of tidal interaction~(Section~\ref{sec:discussion:tidal}).
+\textbf{Cross symbols} mark planets with $M_p \sin i$ measurements.
+\textbf{Round symbols} mark planets with measured  or estimated $M_p$ (see Section~\ref{sec:discussion:mpms}).
            \textbf{Left panel}: The tidal torque in the system for stars with a convective envelope.
@@
 \subsubsection{Locally expressed tidal interaction}
-Tidal interaction can also lead to enhanced activity, globally, and locally.
-Locally, we expect to see a periodicity with half the orbital period of the planet, corresponding to the two tidal bulges forming in the stellar envelope~\citep{cuntz2000stellar}.
-\citet{holzwarth2003dynamics} suggest an asymmetry induced in the stellar dynamo by the tidal disturbance, which leads to a preference for active (flaring) regions at longitudes about $P_{\rm orb}/2$ apart from each other.
+Tidal interaction can also lead to enhanced stellar activity, globally, and locally, e.g., higher coronal emission~\citep{ilic2022tidal}, or excess flaring.
+Locally, we expect to see a periodicity of activity with half the orbital period of the planet, corresponding to the two tidal bulges forming in the stellar envelope~\citep{cuntz2000stellar}.
+\citet{holzwarth2003dynamics} suggest an asymmetry induced in the stellar dynamo by the tidal disturbance, which could lead to a preference for active regions (potentially flaring) at longitudes about $P_{\rm orb}/2$ apart from each other.
 
@@
 
-We cannot tell whether an additional individual flare is produced by tidal or magnetic interaction, but we can look for deviations from a random distribution of flare times in phase with the relevant period, i.e., $P_{\rm orb}/2$.
+We cannot tell whether an additional individual flare is triggered by tidal or magnetic interaction, but we can look for deviations from a random distribution of flare times in phase with the relevant period, i.e., $P_{\rm orb}/2$.
 
@@
 2 in~\citet{albrecht2012obliquities} for the tidal dissipation timescale in the convective envelope.
-We assume that all stars in our sample have a convective envelope because they flare, and flaring requires a dynamo-generated magnetic field, which can only operate in stars with convective envelopes.
+We assume that all stars in our sample have a convective envelope because they flare, and flaring requires a dynamo-generated magnetic field, which can only operate in stars with convective envelopes or fully convective stars.
 Most of our stars are dwarf stars below the Kraft break at spectral type F5~\citep{kraft1967studies}, except for KOI-12, which is an F5 sub-giant~\citep{frasca2016activity}.
@@
 \subsubsection{Planetary and stellar masses}
-
+\label{sec:discussion:mpms}
 We collect the planetary and stellar masses from the literature~(Table~\ref{tab:tidal}).
@@
 We also adopt the upper limit of $5M_J$ for HIP 67522, but use the lower error from \citet{chen2017probabilistic}.
+The assumptions we made here are conservative, and the estimates based on \citet{chen2017probabilistic} use a broad sample of planets, so we consider the planetary mass estimates with their respective uncertainties robust.
+We note, however, that the mass estimates for RV-detected planets are $M_p \sin i$, so that their expected interaction may be stronger than indicated in Fig.~\ref{fig:tidal}.
 
@@
 \paragraph{KOI-12,} which lacks signal with $P_{\rm orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction.
-This could be interpreted as KOI-12 b orbiting outside the Alfv\'en radius, so that it can still interact tidally, but not magnetically.
 However, we note that KOI-12 may be evolving off the main sequence, so that the tidal interaction scaling laws may not apply for this star.
@@
 In line with theoretical considerations~\citep{strugarek2017fate}, our results tentatively suggest that magnetic interaction is more pronounced for planets with fast rotating, active hosts, while tidal interactions affect both systems with slowly and rapidly rotating stars.
+Finally, exceptions such as TAP 26 exemplify that the simple scaling laws we applied here may not capture the complexity of the interaction.
 
@@
 In particular, we found that there may be two branches at high expected power -- one where the measured excess flaring is correlated with the expected power, and one where excess flaring is absent.
-This may be an effect of the extent of the Alfv\'en surface, the intermittency in the interaction, or of the viewing geometry of the systems.
+This may be, among others, an effect of the extent of the Alfv\'en surface, the intermittency in the interaction, or of the viewing geometry of the systems.
 

### 2023-06-02 src/scripts/paper_illustrative_sketch_of_system_geometries.py
sketch of systems

@@ -1,0 +1,228 @@
+"""
+UTF-8, Python 3
+
+------------------
+Flaring SPI
+------------------
+
+Ekaterina Ilin, 2023, MIT License
+
+
+Simplified magnetic star-planet interaction geometries. Panel a: Fully aligned 
+system along the line of sight. Magnetic, rotational, and orbital axis are 
+aligned. The interaction footpoint moves along the black line, and is visible 
+on the red line, i.e. during 50% of the planet's orbit. Flares induced along 
+this line will result in excess flares when the planet is in front of the star. 
+Panel b: Orbital misalignment. The rotational and magnetic axis are aligned, 
+but the planet is highly misaligned. The footpoint of interaction moves between 
+the two horizontal black lines, and is still visible 50% of the time, resulting 
+in modulated flaring with orbital phase. However, the footpoint passes different 
+latitudes on the star, which correspond to different dipole field strengths, 
+which may influence the power of interaction. Panel c: Inclined fully aligned 
+system. The red interaction footpoint line is visible 100% of the time. No 
+modulation due to SPI can observed, even if flares are triggered by the planet. 
+The sketch only shows the interaction footpoint region on the Northern 
+hemisphere of the star, but they may appear on both. 
+"""
+
+import numpy as np
+import matplotlib.pyplot as plt
+import paths
+
+
+if __name__ == "__main__":
+
+    # init two figure panels next to each other
+    fig, (ax1, ax2, ax3) = plt.subplots(1, 3, figsize=(15, 5))
+
+    # Central star
+    for ax in [ax1, ax2, ax3]:
+        ax.add_patch(plt.Circle((0, 0), 1.0, color='w', fill=True))
+        ax.add_patch(plt.Circle((0, 0), 1.03, color='k', fill=False))
+        ax.add_patch(plt.Circle((0, 0), 1, color='grey', fill=True, alpha=0.5))
+
+
+    # -----------------------------------------------------------------------------
+    # PANEL 1
+
+    req = 2 # field apex
+    aplanet = 2 # semi-major axis
+
+    # plot a dipole field line from the big circle
[…]

### 2023-06-02 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Depending on the system's viewing geometry, i.e., the inclination of the rotation axis, the spin-orbit (mis-)alignment, and the extent and configuration of the large scale magnetic field -- the footpoint could be always in view, or never.
-In expectation, however, in star-planet systems with favorable viewing geometries and magnetic field strengths and configurations, the footpoint visibility will be modulated in phase with the planetary orbit~(see, e.g., Fig.~4 in \citet{strugarek2019chasing} for an illustration XXXX maybe make my own sketch?
-XXXX).
+In expectation, however, in star-planet systems with favorable viewing geometries and magnetic field strengths and configurations, the footpoint visibility will be modulated in phase with the planetary orbit~(Fig.~\ref{}).
 The resulting phase preference of planet-induced flares introduces a deviation from a random distribution of flares.
 Space missions like Kepler and TESS provide light curves that cover all phases of the planet's orbit, so that phase-correlated planet-induced flares can be detected against a background of uncorrelated intrinsic flaring.
+
+\begin{figure*}[ht!]
+\script{paper_illustrative_sketch_of_system_geometries.py}
+    \begin{centering}
+        \includegraphics[width=\hsize]{figures/system_geometries.png}
+        \caption{
+         Simplified magnetic star-planet interaction geometries.\textbf{ Panel a: Fully aligned system along the line of sight.
+}Magnetic, rotational, and orbital axis are aligned.
+The interaction footpoint moves along the black line, and is visible on the red line, i.e.
+during $50\%$ of the planet's orbit.
+Flares induced along this line will result in excess flares when the planet is in front of the star.
+\textbf{Panel b: Orbital misalignment.} The rotational and magnetic axis are aligned, but the planet is highly misaligned.
+The footpoint of interaction moves between the two horizontal black lines, and is still visible $50\%$ of the time, resulting in modulated flaring with orbital phase.
+However, the footpoint passes different latitudes on the star, which correspond to different dipole field strengths, which may influence the power of interaction.
+\textbf{Panel c: Inclined fully aligned system.} The red interaction footpoint line is visible $100\%$ of the time.
+No modulation due to SPI can observed, even if flares are triggered by the planet.
+The sketch only shows the interaction footpoint region on the Northern hemisphere of the star, but they may appear on both.
+        }
+        \label{fig:sketch}
+    \end{centering}
+\end{figure*}
 
@@
 
-The average Alfv\'en surface size ($\overline{AS}_{R}$) was estimated using the power law  (Eq.~\ref{AS_estimation}) established by Chebly et al. (under revision):
+The average Alfv\'en surface size ($\overline{AS}_{R}$) was estimated using the power law  (Eq.~\ref{AS_estimation}) established by \citet{Chebly2023}:
 
@@
 
-This relation links the mean AS size with the maximum large-scale radial magnetic field ($B_{\rm r}^{\rm max}$) obtained in Zeeman-Doppler Imaging reconstructions  \textcolor{red}{(references here)}.
-The relation was derived from 3D~MHD stellar wind simulations cool main sequence stars (F, G, K, and M), which incorporated observed ZDI maps as boundary condition for the stellar radial magnetic field (for more details on the models see Chebly et al.
-2023).
+This relation links the mean AS size with the maximum large-scale radial magnetic field ($B_{\rm r}^{\rm max}$) obtained in Zeeman-Doppler Imaging reconstructions (\citealt{donati2006surprising, morin2008largescale, fares2009magnetic, alvarado-gomez2015activity, hussain2016spectropolarimetric, kochukhov2020mapping}).
+The relation was derived from 3D~MHD stellar wind simulations cool main sequence stars (F, G, K, and M), which incorporated observed ZDI maps as boundary condition for the stellar radial magnetic field (for more details on the models see \citealt{Chebly2023}).
 However, the stellar magnetic field~($B$) in this work (Table~\ref{tab:maintable_der}), derived from the Rossby number of each star (Eq.~\ref{Eq3}, \ref{Eq4}), corresponds to the total, unsigned magnetic field strength on the stellar surface.
@@
     \item the available magnetic energy decreasing such that the flares or other magnetic interaction indicators still occur but fall below the detection threshold for a period of time.
+    \item the availability of a sufficient amount of plasma in the vicinity of the magnetic interaction region to yield significant observable flare emission in the stellar atmosphere (in analogy to the Jupiter-Io system, wherein Io's volcanism provides the plasma that eventually produces an interaction hotspot on Jupiter,~\citealt{clarke1996farultraviolet, prange1996rapid})
 \end{itemize}
@@
 1 and 2).
-We choose the tidal quality factor $Q_*=10^7$.
+We choose the tidal quality factor $Q_*=10^7$, i.e., low efficiency of tidal dissipation, as a conservative estimate.
 Our results in Fig~\ref{fig:tidal} (left panel) do not depend on the choice of $Q_*$, as we only need to know the tidal torque down to a proportionality factor.

### 2023-06-03 src/scripts/paper_illustrative_sketch_of_system_geometries.py
tight layout

@@ -221,6 +221,7 @@ if __name__ == "__main__":
         ax.text(0., 0.97, label + ".", transform=ax.transAxes,
                 fontsize=18, fontweight='bold', va='top', ha='right')
         
+    plt.tight_layout()
 
     # --------------------------------------------------------------------------
     # SAVE

### 2023-06-03 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Depending on the system's viewing geometry, i.e., the inclination of the rotation axis, the spin-orbit (mis-)alignment, and the extent and configuration of the large scale magnetic field -- the footpoint could be always in view, or never.
-In expectation, however, in star-planet systems with favorable viewing geometries and magnetic field strengths and configurations, the footpoint visibility will be modulated in phase with the planetary orbit~(Fig.~\ref{}).
+In expectation, however, in star-planet systems with favorable viewing geometries and magnetic field strengths and configurations, the footpoint visibility will be modulated in phase with the planetary orbit~(Fig.~\ref{fig:sketch}).
 The resulting phase preference of planet-induced flares introduces a deviation from a random distribution of flares.
@@
     \begin{centering}
-        \includegraphics[width=\hsize]{figures/system_geometries.png}
+        \includegraphics[width=\linewidth]{figures/system_geometries.png}
         \caption{
@@
 \textbf{Panel c: Inclined fully aligned system.} The red interaction footpoint line is visible $100\%$ of the time.
-No modulation due to SPI can observed, even if flares are triggered by the planet.
+No modulation due to SPI can be observed, even if flares are triggered by the planet.
 The sketch only shows the interaction footpoint region on the Northern hemisphere of the star, but they may appear on both.

### 2023-06-08 src/scripts/paper_correlation_coefficients.py
legibility and completeness

@@ -18,6 +18,8 @@ if __name__ == "__main__":
     # read in the tidal results
     df = pd.read_csv(paths.data / "TIS_with_ADtests.csv")
 
+    print("TIDAL INTERACTION corr-coeffs")
+
     # calculate the Spearman and Pearson correlation coefficients
     for model in ["torque_conv", "tidal_disip_timescale", "grav_pert"]:
         d = df[[model, "mean"]]
@@ -50,6 +52,8 @@ if __name__ == "__main__":
 
     # GJ 1061 because rotation is unclear
     singles = singles[singles.TIC != "79611981" ]
+
+    print("MAGNETIC INTERACTION corr-coeffs")
 
     # calculate the Spearman and Pearson correlation coefficients
     for model in ["p_spi_sb_bp1_norm","p_spi_sb_bp0_norm",

### 2023-06-08 src/scripts/run_all.sh

@@ -2,10 +2,17 @@ source /home/ekaterina/Documents/000_envs/python38forall/bin/activate
 python paper_rename_trappist.py
 python paper_string_multiple_stars.py
 python paper_adtest_vs_value_scatterplots.py
-python paper_coherence_diagram.py
+python paper_coherence_histogram.py
 python paper_cumdist_individual_rv.py
 python paper_cumdist_individual_transiting.py
 python paper_flare_table_values.py 
 python paper_latex_flare_table.py 
 python paper_main_table.py 
+python paper_table_tidal.py
 python paper_tidal_interaction.py
+python paper_illustrative_sketch_of_system_geometries.py
+python paper_lx_plots.py
+python paper_as_vs_ad.py
+python paper_correlation_coefficients.py
+
+

### 2023-06-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \label{sec:intro:fspi}
+
+\begin{figure*}[ht!]
+\script{paper_illustrative_sketch_of_system_geometries.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/system_geometries.png}
+        \caption{
+         Simplified magnetic star-planet interaction (SPI) geometries.\textbf{ Panel a: Fully aligned system along the line of sight (LOS).
+}Magnetic, rotational, and orbital axis are aligned.
+The interaction footpoint moves along the black line, and is visible to the observer on the red line, i.e.
+during $50\%$ of the planet's orbit.
+Flares induced along this line will result in excess flares when the planet is in front of the star.
+\textbf{Panel b: Orbital misalignment.} Same a panel a., but the planet's orbit is misaligned.
+The footpoint of interaction is again visible $50\%$ of the time, resulting in modulated flaring with orbital phase.
+However, it passes different latitudes on the star, which correspond to different dipole field strengths and coronal regions, which may affect the power of interaction.
+\textbf{Panel c: Inclined fully aligned system.} The red interaction footpoint line is visible $100\%$ of the time.
+No modulation due to magnetic SPI can be observed, even if flares are triggered by the planet.
+The sketches only show the interaction on one hemisphere of the star, but they may appear on both.
+        }
+        \label{fig:sketch}
+    \end{centering}
+\end{figure*}
+
 The absolute power of flaring star-planet interactions is difficult to constrain.
@@
 Space missions like Kepler and TESS provide light curves that cover all phases of the planet's orbit, so that phase-correlated planet-induced flares can be detected against a background of uncorrelated intrinsic flaring.
-
-\begin{figure*}[ht!]
-\script{paper_illustrative_sketch_of_system_geometries.py}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/system_geometries.png}
-        \caption{
-         Simplified magnetic star-planet interaction geometries.\textbf{ Panel a: Fully aligned system along the line of sight.
-}Magnetic, rotational, and orbital axis are aligned.
-The interaction footpoint moves along the black line, and is visible on the red line, i.e.
-during $50\%$ of the planet's orbit.
-Flares induced along this line will result in excess flares when the planet is in front of the star.
-\textbf{Panel b: Orbital misalignment.} The rotational and magnetic axis are aligned, but the planet is highly misaligned.
-The footpoint of interaction moves between the two horizontal black lines, and is still visible $50\%$ of the time, resulting in modulated flaring with orbital phase.
-However, the footpoint passes different latitudes on the star, which correspond to different dipole field strengths, which may influence the power of interaction.
-\textbf{Panel c: Inclined fully aligned system.} The red interaction footpoint line is visible $100\%$ of the time.
-No modulation due to SPI can be observed, even if flares are triggered by the planet.
-The sketch only shows the interaction footpoint region on the Northern hemisphere of the star, but they may appear on both.
-        }
-        \label{fig:sketch}
-    \end{centering}
-\end{figure*}
 
@@
 \label{sec:results:individualstars:hip67522}
-HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest sign of flaring SPI at $>2\sigma$ level, albeit with only 6 flares in the sample.
-These flares are distributed across two Sectors in TESS.
-In Sector 11, two flares occur at orbital phases $\sim 0.61$ and $\sim 0.81$.
-Two years later, in Sector 38, four flares occur, but this time, all of them take place at orbital phases $0.00-0.05$, that is, within 10 hours after mid-transit.
+HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest sign of flaring SPI at $>2.5\sigma$ level, with 12 flares in the sample, distributed across three Sectors in TESS.
+In our original sample from July 2022, HIP 67522 was observed for two Sectors with a total of 6 flares, which yielded a $p$-value of $0.015$.
+In June 2023, observations from Sector 64 were released, which we used to follow up on this interesting target, increasing the number of flares by another 6, reducing the $p$-value further to $0.0057$.
 
@@
 Therefore, we cannot completely rule out that the observed periodicity is in fact a rotational periodicity, and not related to the planet.
-However, if we calculate the $p$-value of the AD test using the rotational period instead of the orbital period, we find HIP 67522 consistent with uniform flaring in time within $1\sigma$, which is likely due to the not sufficiently low uncertainty in rotation period.
-So we cannot rule out rotational modulation yet, although the clustering close to transit is suggestive.% Fortunately, HIP 67522 will be observed again with TESS in April 2023, which may resolve the puzzle.
+However, if we calculate the $p$-value of the AD test using the rotational period instead of the orbital period, we find HIP 67522 deviates from uniform flaring in time with $p=0.18$.
+So we cannot rule rotational modulation completely, since the rotational period is very uncertain relative to the total observing baseline, and the clustering close to transit is suggestive.% Fortunately, HIP 67522 will be observed again with TESS in April 2023, which may resolve the puzzle.
 
@@
 Magnetic star-planet interaction can only take place if the planet spends at least a part of its orbit in the sub-Alfv\'enic regime~(see Section~\ref{sec:intro:mspi}).
-
-Fig.~\ref{fig:as}
-
-The average Alfv\'en surface size ($\overline{AS}_{R}$) was estimated using the power law  (Eq.~\ref{AS_estimation}) established by \citet{Chebly2023}:
+We estimated the average Alfv\'en surface size ($\overline{AS}_{R}$) using the power law established by \citet{Chebly2023}:
 
@@
 In \cite{reiners2022magnetism} it was reported that for Sun-like stars with a total magnetic field strength of up to 2000~G, the longitudinal magnetic field derived from Stokes V spectropolarimetric observations ($B_{\rm V}$) accounts for $\sim$\,$10$\% of the total magnetic field.
-\textbf{add ref.} showed that this trend also holds for M-dwarfs with magnetic fields up to 4000~G.
+\cite{kochukhov2020hidden} showed that this trend also holds for M-dwarfs with magnetic fields up to 4000~G.
+In this case, however, the recovered longitudinal magnetic field accounts for about 20\% of the total magnetic field.
+Moreover, our star sample covers a wide range of magnetic fields, the weakest being 100~G and the strongest 3800~G.
 Therefore, as a first assumption, we consider that the longitudinal magnetic field of our stars would reach 15\% of the total magnetic field (i.e.
@@
 
-\textcolor{blue}{what we think about it (E and J contributions, comments from others  welcome)
-TAP 26 and KOI-12 appear sub-Alfv\'enic in our estimate.
-So it seems unlikely that the absence of interaction is caused by the planets orbiting outside the Alfv\'en radius.} \textcolor{red}{JDAG: Thats a good point.
+We show the difference between star-planet distance and $\overline{AS}_{R}$ in Fig.~\ref{fig:as}.
+HIP 67522 b falls most deeply into the sub-Alfv\'enic regime, consistent with the strongest signal of magnetic SPI in our sample.
+TAP 26 and KOI-12 also appear sub-Alfv\'enic, despite absent signal of magnetic SPI.
+From this follows that the absence of interaction is not caused by the planets orbiting outside the Alfv\'en radius.
+location inside $\overline{AS}_{R}$ is a required but not sufficient condition for magnetic SPI, as we will see in the following Sections.
+%\textcolor{red}{JDAG: Thats a good point.
 However, I think being inside the AS is a required but not sufficient condition for the type of SPI that you are looking for.
@@
 As such, the field topology will be more 'resistant' closer to the star than to the planet, facilitating the re-organization in the latter case compared to the former.
-Planetary outflows falling back to the star could help to trigger some instabilities, but those would depend on whether or not the planet is losing any significant mass (which we probably don't know for these targets).
+Planetary outflows falling back to the star could help to trigger some instabilities, but those would depend on whether the planet is losing any significant mass (which we probably don't know for these targets).
 There's of course more to it than just field strength or accretion, with things like the torsion and helicity of the field among others (which is why the likelihood of a solar AR to host a flare is not only determined by field strength but also by its topology/complexity), but all of that is too complicated or even impossible to estimate here.
@@
 \label{sec:discussion:viewing}
-Modulated visibility of the magnetic interaction footpoint is crucial for the detection of flaring star-planet interactions in our analysis.
+Modulated visibility of the magnetic interaction footpoint is crucial for the detection of flaring star-planet interactions in our analysis~(Fig.~\ref{fig:sketch}).
 The viewing geometry of the star-planet system is therefore important to consider as an alternative to, or explanation for, the intermittency discussed above.
@@
 
-Applying both the stretch-and-break and Alfv\'en wing mechanisms for magnetic interaction, we found a tentative evidence trend between the expected power of interaction, and the presence of excess flaring in phase with the orbital period $P_{\rm orb}$.
+Applying both the stretch-and-break and Alfv\'en wing mechanisms for magnetic interaction, we found a tentative trend between the expected power of interaction, and the presence of excess flaring in phase with the orbital period $P_{\rm orb}$.
 In particular, we found that there may be two branches at high expected power -- one where the measured excess flaring is correlated with the expected power, and one where excess flaring is absent.
-This may be, among others, an effect of the extent of the Alfv\'en surface, the intermittency in the interaction, or of the viewing geometry of the systems.
+While we can exclude the extent of the Alfv\'en surface as a reason, intermittency in the interaction, and the viewing geometry of the systems are candidates for explaining the branching.
 

### 2023-06-15 src/scripts/paper_main_table.py
added whitespace

@@ -219,7 +219,7 @@ if __name__ == "__main__":
             singles[newname] = singles.apply(g, axis=1)
 
         if "bibkey" in col[-2]:
-            singles[newname] = singles.apply(lambda x: str(x[newname]) + "\citet{" + str(x[col[-2]]) + "}", axis=1)
+            singles[newname] = singles.apply(lambda x: str(x[newname]) + " \citet{" + str(x[col[-2]]) + "}", axis=1)
  
         for c in col:
             if (c in singles.columns) & (newname != c):

### 2023-06-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Therefore, we cannot completely rule out that the observed periodicity is in fact a rotational periodicity, and not related to the planet.
-However, if we calculate the $p$-value of the AD test using the rotational period instead of the orbital period, we find HIP 67522 deviates from uniform flaring in time with $p=0.18$.
-So we cannot rule rotational modulation completely, since the rotational period is very uncertain relative to the total observing baseline, and the clustering close to transit is suggestive.% Fortunately, HIP 67522 will be observed again with TESS in April 2023, which may resolve the puzzle.
+The $p$-value of the AD test using the rotational period instead of the orbital period is $p=0.18$.
+However, the rotational period is very uncertain relative to the total observing baseline (coherence time of about 100 days, and observing baseline of several years), so this number is unreliable.
 
@@
 Yet, despite its high expected power of interaction, we detect no excess flaring in phase with KOI-12 b.
-Here, the reason could be that KOI-12 b is in fact super-Alfv\'enic due to the relatively wide orbit compared to TAP 26 and HIP 67522.
+The reason could be that KOI-12 b is in fact super-Alfv\'enic due to the relatively wide orbit compared to TAP 26 and HIP 67522.
 However, our estimate of the Alf\'en radius place KOI-12 b in the sub-Alfv\'enic regime~(see Fig.~\ref{fig:as}), although the scaling law applied there may be inaccurate for post-main sequence stars.
@@
 \cite{kochukhov2020hidden} showed that this trend also holds for M-dwarfs with magnetic fields up to 4000~G.
-In this case, however, the recovered longitudinal magnetic field accounts for about 20\% of the total magnetic field.
-Moreover, our star sample covers a wide range of magnetic fields, the weakest being 100~G and the strongest 3800~G.
+In this case, however, the recovered longitudinal magnetic field accounts for about $20\%$ of the total magnetic field.
+Moreover, our star sample covers a wide range of magnetic fields, the weakest being 100~G and the strongest $3800\,$G.
 Therefore, as a first assumption, we consider that the longitudinal magnetic field of our stars would reach 15\% of the total magnetic field (i.e.
-$B_{\rm V} = 0.15B$), given that most systems in our sample have B~$>$~2000 G.
+$B_{\rm V} = 0.15B$), given that most systems in our sample have $B>2000\,$G.
 
@@
 HIP 67522 b falls most deeply into the sub-Alfv\'enic regime, consistent with the strongest signal of magnetic SPI in our sample.
+K2-25, TOI-540 and AU Mic also fulfil the condition of sub-Alfv\'enic orbit of the innermost planet, consistent with their observed marginal deviation from uniform flaring with orbital phase.
+
 TAP 26 and KOI-12 also appear sub-Alfv\'enic, despite absent signal of magnetic SPI.
 From this follows that the absence of interaction is not caused by the planets orbiting outside the Alfv\'en radius.
-location inside $\overline{AS}_{R}$ is a required but not sufficient condition for magnetic SPI, as we will see in the following Sections.
+Location inside $\overline{AS}_{R}$ is a required but not sufficient condition for magnetic SPI, as we will see in the following Sections.
 %\textcolor{red}{JDAG: Thats a good point.
@@
 In our results in Fig.~\ref{fig:adtest_bp}, we can interpret the two branches emerging at high expected power of interaction as due to intermittency.
-TAP 26 and KOI-12 do not show any sign of excess flaring in our data, despite similar expected powers as in HIP 67522 with its $2-3\sigma$ signal.
+TAP 26 and KOI-12 do not show any sign of excess flaring in our data, despite similar expected powers as in HIP 67522 with its $>2.5\sigma$ signal.
 However, other explanations cannot be ruled out yet (see Sections~\ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}, and the following).
@@
 
-\paragraph{HIP 67522} appears with tentative signs of both tidal and magnetic interaction (measured and expected in the different scenarios).
-On the one hand, since the flares in HIP 67522 mostly appear close to the transit phase, and not during eclipse, this may favor magnetic interaction, and the tidal signal would only be an artifact.
-On the other hand, the narrow range in which most of the flares on HIP 67522 occurred~(see Fig.~\ref{fig:cumdist_transiting} and Section~\ref{sec:results:individualstars:hip67522}) might favor a well-localized active region in the vicinity of the tidal bulge.
-Conceivably, both effects play a role at the same time.
+\paragraph{HIP 67522} does not show signs of tidal interaction, despite a relatively high expected power.
+Conceivably, both effects play a role at the same time, but the tidal interaction is dominated by magnetic SPI.
+With more available observations in the future, and better constraints on the expected signal of each type of SPI, it will become possible to model both simultaneously.
+However, with only a total of 12 flares in this work, we cannot make any strong claims about the contribution of tidal SPI, except for it apparently being weaker than the magnetic aspect.
 
@@
 We found a similar trend with different scaling laws of tidal interaction, albeit at even lower significance.
-Our system-by-system comparison suggests that young systems, like HIP 67522, may interact both tidally and magnetically, whereas old, magnetically inactive systems, like Kepler-42, might mostly interact tidally.
+Our system-by-system comparison suggests that young systems, like HIP 67522, may be dominated by magnetic interaction, whereas old, magnetically inactive systems, like Kepler-42, might mostly interact tidally.
 
@@
 For AU Mic, we may be only a few TESS Sectors away from a $3\sigma$ level confirmation~\citep{ilin2022searching} of the tentative interaction signal observed here and in other work~\citep{klein2022one}.
-Several systems in our sample are already scheduled for further observing with TESS, including HIP 67522, Kepler-42, and KOI-12.
+Several systems in our sample are already scheduled for further observing with TESS, including Kepler-42, and KOI-12.
 

### 2023-06-21 src/scripts/paper_main_table.py
wrap note on k2-354

@@ -285,6 +285,14 @@ if __name__ == "__main__":
         string = string.replace("midrule","hline")
         string = string.replace("toprule","hline")
         string = string.replace("bottomrule","hline")
+
+        if label == "lit":
+            note = (r"We note that we found K2-354 under EPIC 211314705 and K2-329(!)"
+                    r" in \cite{bouma2020cluster}, who refer to the detection paper"
+                    r" \cite{pope2016transiting}, and also under TIC 468989066.")
+            
+            string = string.replace(r"K2-354",r"K2-354\footnote{" + note + "}")
+
         for n in range(1,10):
             string = string.replace(fr"e-0{n}",fr"\text{{e-}}{n}")
 

### 2023-06-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \begin{abstract}
-    In many of the star-planet systems discovered so far, the innermost planets orbit within only a few stellar radii.
-In these systems, the planets become in-situ probes of the extended stellar magnetic field.
-As they move, they are expected to trigger flares on the stellar surface.
-Until recently, however, searches for such planet-induced flaring suffered from small sample sizes, and poor orbital phase coverage.
-
-    In this work, we used the excellent phase coverage of the archives of Kepler and the Transiting Exoplanet Survey Satellite to search for star-planet systems with flaring star-planet interactions.
-We compiled a catalog of all their flares, and searched for planet-induced flaring, i.e., flares clustering in phase with the planet's orbital phase.
+    In many star-planet systems discovered so far, the innermost planet orbits within only a few stellar radii.
+In these systems, planets become in-situ probes of the extended stellar magnetic field.
+Because they disturb the field as they move, they are expected to trigger flares on the stellar surface.
+These flares are not expected to appear different from intrinsic stellar flares individually.
+
+    However, as we expect planet-induced flares to be associated with the planet's orbital period $P_{orb}$, we can identify their presence from a clustering of flares in phase with the planet's orbital phase.
+We used the excellent phase coverage obtained from Kepler and the Transiting Exoplanet Survey Satellite to find flaring star-planet systems, compile a catalog of all their flares, and measure how much they cluster in orbital phase.
 
     In the 1811 searched systems, we found 25 single stars with three or more flares each.
-We quantified the significance of their excess flaring, and compared it against the theoretically expected amplitude of magnetic interaction.
-As we did not select for short orbits, most systems do not show excess flaring, as expected.
-Those we expect to interact fall on two branches.
-An inactive one, without any signs of excess flaring, and an active one, where expected power and excess flaring are correlated.
-This trend is tentative, but consistent for several scaling laws for magnetic interaction.
-
-    Finally, we searched our data for locally expressed tidal interaction, i.e., excess flaring in phase with the tidal bulges ($P_{\rm orb}/2$).
+We quantified the significance of the clustering in each system, and compared it against the theoretically expected amplitude of magnetic interaction that leads to planet-induced flaring.
+Most systems do not show any clustering, as expected from their relatively wide orbits.
+Those we expect to show planet-induced flaring fall on two branches.
+An inactive one, without any signs of clustering, and a tentative active one, where the clustering becomes more pronounced as the expected amplitude of interaction increases.
+The flares in HIP 67522, a young Hot Jupiter system, are prominently clustered ($p<0.006$), identifying it as the most promising candidate for magnetic star-planet interaction in our sample.
+
+  %  In our results, HIP 67522, a 17 Myr old solar type star with a Hot Jupiter in a 7-day orbit, shows the most pronounced clustering with only a 0.006 probability of coincidence.
+While short of a $3\sigma$ detection,
+
+  %  We also searched our data for locally expressed tidal interaction, i.e., flares clustering in phase with the tidal bulges ($P_{\rm orb}/2$).
 We find a marginal trend with different scaling laws of tidal interaction.
@@
 
+We note that we found K2-354 under EPIC 211314705 and K2-329(!) in \cite{bouma2020cluster}, who refer to the detection paper \cite{pope2016transiting}, and also under TIC 468989066.
+
 \subsection{Star-planet systems}
@@
 We then perform a customized Anderson-Darling test on the flare peak time distribution, which yields a $p$-value for the significance of the SPI signal.
-Finally, we compare these results to the theoretically expected SPI power $P_{xx}$ in each system.
+Finally, we compare these results to the theoretically expected SPI power $P_{spi}$ in each system.
 
@@
 For each star-planet system with three or more flares in its light curves, we test for deviations from a random distribution of flares with orbital phase.
-We use the same customized Anderson-Darling test as in \cite{ilin2022searching}.
+We use the same customized Anderson-Darling test as in \cite{ilin2022searching}, which is more sensitive to deviations at both ends of the distribution than the widely used Kolmogorov-Smirnov test~\citep{feigelson2012statistical}.
 In brief, we first take the number of flares observed in the TESS and Kepler data to calculate a base flare rate for each light curve.
@@
            X-ray luminosity over bolometric luminosity compared to Rossby number (\textbf{upper panel}), and average surface magnetic field strength (\textbf{lower panel}).
-Both relations follow those of stars not selected for hosting close-in planets, except for GJ 3082, which is underluminous for its Rossby number, and hence also its estimated magnetic field strength.
+Both relations follow those of stars not selected for hosting close-in planets, except for GJ 3082, which is underluminous for its Rossby number, and hence also its estimated magnetic field appears too strong for its $L_X/L_{\rm bol}$.
         }
@@
 First, we estimate the power of star-planet interaction generated by the stretch-and-break mechanism using the scaling relations in~\cite{lanza2012starplanet} (their Eqn.
-45), where $P_{sb}$ is proportional to
+45), where $P_{spi,sb}$ is proportional to
 
 \begin{equation}
-    P_{sb} \sim B_p^{2/3} R_p^2 B_*^{4/3} R_*^4 v_{rel} a^{-4} .
+    P_{spi,sb} \sim B_p^{2/3} R_p^2 B_*^{4/3} R_*^4 v_{rel} a^{-4} .
 \end{equation}
@@
 \begin{equation}
-    P_{sb0} \sim R_p^2 R_*^4 B_*^2 v_{rel}    a^{-4} 
+    P_{spi,sb0} \sim R_p^2 R_*^4 B_*^2 v_{rel}    a^{-4} 
 \end{equation}
@@
 \begin{equation}
-    P_{aw} \sim B_p^{2/3} R_{p}^2    B_*^{1/3}  v_{rel}^2 a^{-2}  
+    P_{spi,aw} \sim B_p^{2/3} R_{p}^2    B_*^{1/3}  v_{rel}^2 a^{-2}  
 \end{equation}
@@
 \begin{equation}
-    P_{aw0} \sim R_p^2  B_*  v_{rel}^2  a^{-4}
+    P_{spi,aw0} \sim R_p^2  B_*  v_{rel}^2  a^{-4}
 \end{equation}
 
-Lacking $B_p$, and various additional factors that appear in $P_{sb},P_{sb0},P_{aw}$, and  $P_{aw0}$, such as the angle between the relative velocity and magnetic field of the stellar wind~\citep{kavanagh2022radio}, or the force-free parameter~\citep{lanza2012starplanet}, we restrict ourselves to differential estimates, and normalize all $P_{xx}$ to AU Mic.
+Lacking $B_p$, and various additional factors that appear in $P_{spi,sb},P_{spi,sb0},P_{spi,aw}$, and  $P_{spi,aw0}$, such as the angle between the relative velocity and magnetic field of the stellar wind~\citep{kavanagh2022radio}, or the force-free parameter~\citep{lanza2012starplanet}, we restrict ourselves to differential estimates, and normalize all $P_{spi}$ to AU Mic.
 
@@
 \label{sec:results:spi}
+The main result of this work is the comparison of the significance of flares clustering in orbital phase to the expected amplitude of magnetic SPI, and is shown in Figure~\ref{fig:adtest_bp}.
 We used the custom Anderson-Darling test introduced in Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three or more flares with equivalent duration $ED>1\,$s, detected in their Kepler and TESS observations.
-We choose the $ED$ cutoff to make sure that we are comparing similar flares regardless of spectral type, that is, flares above the same energy relative to stellar luminosity, without losing too many flares.
+
+Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with magnetized or unmagnetized planets), there are two branches on the high end of expected powers.
+On one branch, the significance of the measured interaction increases with the expected power $P_{spi}$.
+On the other branch, no interaction is measured regardless of $P_{spi}$.
+
+Table~\ref{tab:maintable_der} lists the $p$-values for each star-planet system.
+There is no star-planet system for which we find a $>3\sigma$ ($p<0.0027$) signal of star-planet interaction in our sample.
+However, overall, the significance of the deviation increases with higher expected power $P_{spi}$ of interaction, where additional subscripts denote different scenarios introduced in Section~\ref{sec:methods:pspi}.
+Table~\ref{tab:maintable_der} also lists the derived parameters required in these scaling laws, i.e., Rossby number $R$o, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{\rm rel}$.
+
+We choose the $ED>1\,$s cutoff to make sure that we are comparing similar flares regardless of spectral type, that is, flares above the same energy relative to stellar luminosity, without losing too many flares.
 In~\citet{ilin2022searching}, AU Mic appeared to be more modulated with orbital period in the high energy flares above $1\,$s than below.
@@
 We note that the flares (with $ED<1\,$s) in all of these systems are consistent with random flare phases within $1\sigma$.
-
-Table~\ref{tab:maintable_der} lists the $p$-values for each star-planet system.
-There is no star-planet system for which we find a $>3\sigma$ ($p<0.0027$) signal of star-planet interaction in our sample.
-However, overall, the significance of the deviation increases with higher expected power $P_{xx}$ of interaction, where the subscript denotes different scenarios introduced in Section~\ref{sec:methods:pspi}.
-Table~\ref{tab:maintable_der} also lists the derived parameters required in these scaling laws, i.e., Rossby number $R$o, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{\rm rel}$.
-
-Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with magnetized or unmagnetized planets), there are two branches on the high end of expected powers.
-On one branch, the significance of the measured interaction is correlated with the expected power $P_{xx}$.
-On the other branch, no interaction is measured regardless of the expected power $P_{xx}$.
 
@@
 $Ro$, $B$, and $v_{rel}$, are derived from literature values (Table~\ref{tab:maintable_lit}).
-$P_{xx}$ stands for the power of stretch-and-break ($sb$) and Alfv\'en wing ($aw$) interaction mechanisms, assuming the planet has a magnetic field strength of 1 G.
-$P_{xx0}$ is the same, but assuming an unmagnetized planet.
+$P_{spi,xx}$ stands for the power of stretch-and-break ($sb$) and Alfv\'en wing ($aw$) interaction mechanisms, assuming the planet has a magnetic field strength of $1\,$G.
+$P_{spi,xx0}$ is the same, but assuming an unmagnetized planet.
 All powers are normalized to AU Mic.
@@
 The bulk of the systems in our sample are neither expected to show high power of magnetic star-planet interaction, nor do they show any deviation from intrinsic stellar flaring.
-In the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring star-planet interaction with increasing expected power $P_{xx}$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522~(Sections \ref{sec:results:individualstars:aumic} and \ref{sec:results:individualstars:hip67522}).
+In the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring star-planet interaction with increasing expected power $P_{spi}$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522~(Sections \ref{sec:results:individualstars:aumic} and \ref{sec:results:individualstars:hip67522}).
 Then we consider those systems where high power was expected in all scenarios, but not measured, i.e., TAP~26 and KOI-12~(Sections \ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}).
@@
 
-For instance, Kepler-808 (KOI-1300) has a $\sim0.4M_\odot$ \citep{kraus2016impact} companion that is about 1.8 mag fainter than the primary at a separation of .78 arcsec~\citep{baranec2016roboao}.
+For instance, Kepler-808 (KOI-1300) has a $\sim0.4M_\odot$ \citep{kraus2016impact} companion that is about 1.8 mag fainter than the primary at a separation of $0.78\arcsec$~\citep{baranec2016roboao}.
 TOI-837 has co-moving M dwarf a few arcsec away in the same young cluster, 5 mag fainter, but the primary is an F9-G0 star, so flares could still originate come from both stars~\citep{bouma2020cluster}.
-HD 41004 B, DS Tuc A, and LTT 1445 are known multiple systems where all components contribute significantly to the total flux.
+HD 41004 B, DS Tuc A, and LTT 1445 are known multiple systems where all components contribute significantly to the total TESS flux.
 
@@
 
-\subsubsection{Kepler-411}
+\paragraph{Kepler-411}
 \label{sec:results:individualstars:kep411}
@@
 
-\subsubsection{Proxima Cen}
+\subsubsection{Prominent systems}
+\label{sec:prominensystems}
+\paragraph{Proxima Cen}
 \label{sec:results:individualstars:proxima}
+Although Proxima Cen is part of a triple stellar system, we treat it a single star in this work because of the large angular separation of over 2 deg to its companions, $\alpha$ Cen AB.
 We do not detect a deviation from intrinsic flaring on Proxima Cen, consistent with numerical models that place Proxima Cen b well outside the sub-Alfv\'enic zone~\citep{gomez2020earthlike, kavanagh2021planetinduced, garraffo2022revisiting}.
@@
 
-\subsubsection{AU Mic, K2-25, and TOI-540}
+\paragraph{AU Mic, K2-25, and TOI-540}
 \label{sec:results:individualstars:aumic}
@@
 
-\subsubsection{HIP 67522}
+\paragraph{HIP 67522}
 \label{sec:results:individualstars:hip67522}
@@
 
-\subsubsection{TAP 26}
+\paragraph{TAP 26}
 \label{sec:results:individualstars:tap26}
@@
 
-\subsubsection{KOI-12}
+\paragraph{KOI-12}
 \label{sec:results:individualstars:koi12}
@@
 From this follows that the absence of interaction is not caused by the planets orbiting outside the Alfv\'en radius.
-Location inside $\overline{AS}_{R}$ is a required but not sufficient condition for magnetic SPI, as we will see in the following Sections.
+Location inside $\overline{AS}_{R}$ is a required but not sufficient condition for magnetic SPI, as we will see in the following subsections.
 %\textcolor{red}{JDAG: Thats a good point.
@@
 has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
+KP, JC and NI acknowledge funding from the German \textit{Leibniz Community} under grant P67/2018.
 %follow instructions here https://gea.esac.esa.int/archive/documentation/GEDR3/Miscellaneous/sec_credit_and_citation_instructions/
@@
 \citep{luger2021mappinga} to create all figures, format all tables, and compile the manuscript.
-Each figure links to the dataset stored on Zenodo (\url{ZENODO LINK} and XXXX integration TBD), and to the script that produced the figure in the git repository~\url{https://github.com/ekaterinailin/flaring-spi-paper}.
+Each figure links to the dataset stored on Zenodo (link to be added after acceptance), and to the script that produced the figure in the git repository~\url{https://github.com/ekaterinailin/flaring-spi-paper}.
 The git repository that produces the data stored on Zenodo is publicly available at \url{https://github.com/ekaterinailin/flaring-spi}.
@@
 \appendix
-\section{Notes on individual stars}
-\subsection{Proxima Cen}
-Although Proxima Cen is part of a triple stellar system, we treat it a single star in this work because of the large angular separation of over 2 deg to its companions, $\alpha$ Cen AB.
-
-\subsection{K2-354}
+
+%\subsection{K2-354}
 We note that we found K2-354 under EPIC 211314705 and K2-329(!) in \cite{bouma2020cluster}, who refer to the detection paper \cite{pope2016transiting}, and also under TIC 468989066.

### 2023-06-21 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \label{sec:intro:mspi}
-Magnetic star-planet interactions can occur if the planet is orbiting within the Alfv\'en radius of the star at least part of the time~\citep{preusse2006magnetic, cohen2011dynamics}.
+Magnetic SPI can occur if the planet is orbiting within the Alfv\'en radius of the star at least part of the time~\citep{preusse2006magnetic, cohen2011dynamics}.
 The Alfv\'en radius is the radius at which the stellar wind velocity, which increases with increasing distance from the star, exceeds the Alfv\'en velocity of the magnetized plasma.
@@
 
-The absolute power of flaring star-planet interactions is difficult to constrain.
+The absolute power of flaring SPI is difficult to constrain.
 We do not know how energetic planet-induced flares can be.
@@
 \label{sec:data}
-In this study, we aimed at compiling the largest possible sample to search for flaring star-planet interactions.
+In this study, we aimed at compiling the largest possible sample to search for flaring SPI.
 We took the entire Planetary Systems Composite Parameters Table (PSCP\footnote{ \url{https://exoplanetarchive.ipac.caltech.edu/cgi-bin/TblView/nph-tblView?app=ExoTbls&config=PSCompPars}}, Section~\ref{sec:data:sps}) from the NASA Exoplanet Archive, as of July 2022, and scanned the systems for available Kepler and TESS light curves~(Section~\ref{sec:data:photometry}).
 We searched a total of 1811 systems and over 7200 light curves from both missions for flares.
-To calculate the amount of excess flaring from star-planet interaction, we further required the orbital periods of each system~(Section~\ref{sec:data:orbitalperiod}).
+To calculate the amount of excess flaring from SPI, we further required the orbital periods of each system~(Section~\ref{sec:data:orbitalperiod}).
 To compare our measurements to theory, we estimated the expected power of interaction for each system with at least three flares.
@@
 \label{sec:methods}
-We measure flaring star-planet interactions (SPI) as the presence of excess flares triggered by the orbiting planet.
+We measure flaring SPI as the presence of excess flares triggered by the orbiting planet.
 In the absence of flaring SPI, flare peak times will be distributed randomly in orbital phase.
@@
 We then perform a customized Anderson-Darling test on the flare peak time distribution, which yields a $p$-value for the significance of the SPI signal.
-Finally, we compare these results to the theoretically expected SPI power $P_{spi}$ in each system.
+Finally, we compare these results to the theoretically expected SPI power $P_{\rm spi}$ in each system.
 
@@
 For each star-planet system with three or more flares in its light curves, we test for deviations from a random distribution of flares with orbital phase.
-We use the same customized Anderson-Darling test as in \cite{ilin2022searching}, which is more sensitive to deviations at both ends of the distribution than the widely used Kolmogorov-Smirnov test~\citep{feigelson2012statistical}.
+We use the same customized Anderson-Darling test as in \cite{ilin2022searching}, which is more sensitive to deviations at both ends of the distribution than the widely used Kolmogorov-Smirnov test~\citep{feigelson2012modern}.
 In brief, we first take the number of flares observed in the TESS and Kepler data to calculate a base flare rate for each light curve.
@@
 \label{sec:methods:pspi}
-We consider two theories for the mechanism behind flaring star-planet interactions, the stretch-and-break and the Alfv\'en wing mechanisms.
-For both of them, we include the case of a magnetized and an unmagnetized planet, for a total of four estimates of the expected power of magnetic star-planet interaction.
-
-First, we estimate the power of star-planet interaction generated by the stretch-and-break mechanism using the scaling relations in~\cite{lanza2012starplanet} (their Eqn.
-45), where $P_{spi,sb}$ is proportional to
+We consider two theories for the mechanism behind flaring SPI, the stretch-and-break and the Alfv\'en wing mechanisms.
+For both of them, we include the case of a magnetized and an unmagnetized planet, for a total of four estimates of the expected power of magnetic SPI.
+
+First, we estimate the power of SPI generated by the stretch-and-break mechanism using the scaling relations in~\cite{lanza2012starplanet} (their Eqn. 45), where $P_{\rm spi,sb}$ is proportional to
 
 \begin{equation}
-    P_{spi,sb} \sim B_p^{2/3} R_p^2 B_*^{4/3} R_*^4 v_{rel} a^{-4} .
+    P_{\rm spi,sb} \sim B_p^{2/3} R_p^2 B_*^{4/3} R_*^4 v_{rel} a^{-4} .
 \end{equation}
@@
 \begin{equation}
-    P_{spi,sb0} \sim R_p^2 R_*^4 B_*^2 v_{rel}    a^{-4} 
+    P_{\rm spi,sb0} \sim R_p^2 R_*^4 B_*^2 v_{rel}    a^{-4} 
 \end{equation}
 
-Third, we estimate the power of star-planet interaction generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio}, combining Eqns.~8~and~11 in \citet{kavanagh2022radio} to arrive at
+Third, we estimate the power of SPI generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio}, combining Eqns.~8~and~11 in \citet{kavanagh2022radio} to arrive at
 
 \begin{equation}
-    P_{spi,aw} \sim B_p^{2/3} R_{p}^2    B_*^{1/3}  v_{rel}^2 a^{-2}  
+    P_{\rm spi,aw} \sim B_p^{2/3} R_{p}^2    B_*^{1/3}  v_{rel}^2 a^{-2}  
 \end{equation}
@@
 \begin{equation}
-    P_{spi,aw0} \sim R_p^2  B_*  v_{rel}^2  a^{-4}
+    P_{\rm spi,aw0} \sim R_p^2  B_*  v_{rel}^2  a^{-4}
 \end{equation}
 
-Lacking $B_p$, and various additional factors that appear in $P_{spi,sb},P_{spi,sb0},P_{spi,aw}$, and  $P_{spi,aw0}$, such as the angle between the relative velocity and magnetic field of the stellar wind~\citep{kavanagh2022radio}, or the force-free parameter~\citep{lanza2012starplanet}, we restrict ourselves to differential estimates, and normalize all $P_{spi}$ to AU Mic.
+Lacking $B_p$, and various additional factors that appear in $P_{\rm spi,sb},P_{\rm spi,sb0},P_{\rm spi,aw}$, and  $P_{\rm spi,aw0}$, such as the angle between the relative velocity and magnetic field of the stellar wind~\citep{kavanagh2022radio}, or the force-free parameter~\citep{lanza2012starplanet}, we restrict ourselves to differential estimates, and normalize all $P_{\rm spi}$ to AU Mic.
 
@@
 
-Our goal was to measure magnetic star-planet interaction as the statistical clustering of flares in phase with the innermost planet's orbit.
+Our goal was to measure magnetic SPI as the statistical clustering of flares in phase with the innermost planet's orbit.
 We searched all star-planet systems that were observed with Kepler and TESS at 1 or 2 min cadence, respectively, for flares.
@@
 We then applied the custom Anderson-Darling test to assess how much each distribution was different from randomly distributed intrinsic flaring.
-Comparing the test results with the expected power of magnetic star-planet interaction, we found that the amount of excess flaring tentatively increases with the expected power in all considered scenarios~(Section~\ref{sec:results:spi}).
+Comparing the test results with the expected power of magnetic SPI, we found our main result: The clustering of flares in orbital phase tentatively increases with the expected power in all considered scenarios of magnetic SPI~(Section~\ref{sec:results:spi}).
 However, not all systems with high expected power show signs of flaring SPI, which creates two branches in the distribution of test results.
@@
 Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with magnetized or unmagnetized planets), there are two branches on the high end of expected powers.
-On one branch, the significance of the measured interaction increases with the expected power $P_{spi}$.
-On the other branch, no interaction is measured regardless of $P_{spi}$.
+On one branch, the significance of the measured interaction increases with the expected power $P_{\rm spi}$.
+On the other branch, no interaction is measured regardless of $P_{\rm spi}$.
 
 Table~\ref{tab:maintable_der} lists the $p$-values for each star-planet system.
-There is no star-planet system for which we find a $>3\sigma$ ($p<0.0027$) signal of star-planet interaction in our sample.
-However, overall, the significance of the deviation increases with higher expected power $P_{spi}$ of interaction, where additional subscripts denote different scenarios introduced in Section~\ref{sec:methods:pspi}.
+There is no star-planet system for which we find a $>3\sigma$ ($p<0.0027$) signal of flaring SPI in our sample.
+However, overall, the significance of the deviation increases with higher expected power $P_{\rm spi}$ of interaction, where additional subscripts denote different scenarios introduced in Section~\ref{sec:methods:pspi}.
 Table~\ref{tab:maintable_der} also lists the derived parameters required in these scaling laws, i.e., Rossby number $R$o, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{\rm rel}$.
@@
 $Ro$, $B$, and $v_{rel}$, are derived from literature values (Table~\ref{tab:maintable_lit}).
-$P_{spi,xx}$ stands for the power of stretch-and-break ($sb$) and Alfv\'en wing ($aw$) interaction mechanisms, assuming the planet has a magnetic field strength of $1\,$G.
-$P_{spi,xx0}$ is the same, but assuming an unmagnetized planet.
+$P_{\rm spi,xx}$ stands for the power of stretch-and-break ($sb$) and Alfv\'en wing ($aw$) interaction mechanisms, assuming the planet has a magnetic field strength of $1\,$G.
+$P_{\rm spi,xx0}$ is the same, but assuming an unmagnetized planet.
 All powers are normalized to AU Mic.
@@
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_bg.png}
+        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_bg_main.png}
         \caption{
-            Expected power of SPI vs.
-AD test results, assuming four different scenarios, color-coded by stellar surface field strength.
-\textbf{Top panels}: stretch-and-break scenario.
-\textbf{Bottom panels}: Alfv\'en wing scenario.
-\textbf{Left panels}: assuming a magnetized planet.
-\textbf{Right panels}: assuming an unmagnetized planet.
+            Expected power of magnetic SPI vs.
+AD test results, assuming the stretch-and-break scenario.
 While the distribution of $p$-values is consistent with no interaction, all scenarios indicate lower $p$-values only for high expected powers of interaction.
@@
 
-\subsection{Individual stars}
+\begin{figure}[ht!]
+    \script{paper_adtest_vs_value_scatterplots.py}
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_bg_rest.png}
+        \caption{
+            Same as Fig.~\ref{fig:adtest_bp}, but for three other scenarios.
+\textbf{Top panel}: stretch-and-break scenario for an unmagnetized planet.
+\textbf{Middle panel}: Alfv\'en wing scenario, assuming a magnetized planet.
+\textbf{Bottom panel}: Alfv\'en wing scenario, assuming an unmagnetized planet.
+See Fig.~\ref{fig:adtest_ro} in the Appendix for the same figure, color-coded by Rossby number.
+        }
+        \label{fig:adtest_bp_rest}
+    \end{centering}
+\end{figure}
+
+\subsection{Individual systems}
 \label{sec:results:individualstars}
@@
 We therefore excluded some systems due to documented contamination from nearby (bound or co-moving) companions~(Section~\ref{sec:results:individualstars:excluded}).
-One exception to this rule is Kepler-411, a binary system for which the flare contributions from each component could be separated, but which was excluded for other reasons~(Section~\ref{sec:results:individualstars:kep411}).
-We also dropped GJ 1061 from the sample because its rotation period was unconstrained.
-Another uncertainty in our analysis is the possibility of additional planets at even shorter orbits than the currently known innermost planet, such as might be the case for Proxima Cen~(Section~\ref{sec:results:individualstars:proxima}).
-
-The bulk of the systems in our sample are neither expected to show high power of magnetic star-planet interaction, nor do they show any deviation from intrinsic stellar flaring.
-In the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring star-planet interaction with increasing expected power $P_{spi}$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522~(Sections \ref{sec:results:individualstars:aumic} and \ref{sec:results:individualstars:hip67522}).
-Then we consider those systems where high power was expected in all scenarios, but not measured, i.e., TAP~26 and KOI-12~(Sections \ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}).
+One exception to this rule is Kepler-411, a binary system for which the flare contributions from each component could be separated, but which was excluded for other reasons.
+We also dropped GJ 1061 from the final sample because its rotation period was unconstrained.
+Another uncertainty in our analysis is the possibility of additional planets at even shorter orbits than the currently known innermost planet, such as might be the case for Proxima Cen~(see Section~\ref{sec:prominensystems}).
+
+The bulk of the systems in our sample are neither expected to show high power of magnetic SPI, nor do they show any deviation from intrinsic stellar flaring.
+In Section~\ref{sec:prominensystems}, in the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring SPI with increasing expected power $P_{\rm spi}$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522.
+Then we consider those systems where high power was expected in all scenarios, but not measured, i.e., TAP~26 and KOI-12.
 \subsubsection{Excluded targets}
@@
 Although Proxima Cen is part of a triple stellar system, we treat it a single star in this work because of the large angular separation of over 2 deg to its companions, $\alpha$ Cen AB.
-We do not detect a deviation from intrinsic flaring on Proxima Cen, consistent with numerical models that place Proxima Cen b well outside the sub-Alfv\'enic zone~\citep{gomez2020earthlike, kavanagh2021planetinduced, garraffo2022revisiting}.
-However, this might not entirely exclude Proxima Cen from the search for flaring star-planet interaction.
-The tentatively detected Proxima Cen d, a planet further in, at 0.029 au, or 5 day orbital period~\citep{faria2022candidate, artigau2022linebyline} could still cause flaring star-planet interactions.
-Depending on the phase of the activity cycle, Proxima Cen d may be in the sub-Alf\'enic regime during Proxima Cen's activity maximum~\citep{gomez2020earthlike}.
+We do not detect a deviation from intrinsic flaring on Proxima Cen, consistent with numerical models that place Proxima Cen b well outside the sub-Alfv\'enic zone~\citep{alvarado-gomez2020earthlike, kavanagh2021planetinduced, garraffo2022revisiting}.
+However, this might not entirely rule out flaring SPI in Proxima Cen.
+The tentatively detected Proxima Cen d, a planet further in, at 0.029 au, or 5 day orbital period~\citep{faria2022candidate, artigau2022linebyline} could still cause flaring SPI.
+Depending on the phase of the activity cycle, Proxima Cen d may be in the sub-Alfv\'enic regime during Proxima Cen's activity maximum~\citep{alvarado-gomez2020earthlike}.
 However, the orbital period of the tentative planet is so uncertain at this point that its coherence time~(Section~\ref{sec:results:coherence}) is shorter than the roughly 2yr observing baseline of Proxima Cen, preventing us from accurately measuring the flare phases.
@@
 Recently, \citet{klein2022one} found tentative periodicity with the orbital period of AU Mic b in the chromospheric He I D line, which increases if the contribution from flares is included in the calculation.
-Overall, our marginal signal of flaring star-planet interaction in the AU Mic system supports the idea that this young, magnetically active M dwarf system with a close-in Neptune could exhibit planet-induced flaring.
-For a detailed discussion of AU Mic and its flaring star-planet interaction, we refer to~\cite{ilin2022searching}, where we also estimate that an additional 50–100 days of TESS-like monitoring of AU Mic would yield a $3\sigma$ detection if the marginal signal in our data is real.
+Overall, our marginal signal of flaring SPI in the AU Mic system supports the idea that this young, magnetically active M dwarf system with a close-in Neptune could exhibit planet-induced flaring.
+For a detailed discussion of AU Mic and its flaring SPI, we refer to~\cite{ilin2022searching}, where we also estimate that an additional 50–100 days of TESS-like monitoring of AU Mic would yield a $3\sigma$ detection if the marginal signal in our data is real.
 
@@
 Interestingly, K2-25 b is in a presumably similar environment to GJ 436 b, but does not show the atmospheric escape in Ly$\alpha$ that the latter famously exhibits, which might be due to high speed stellar winds that suppress atmospheric escape~\citep{rockcliffe2021lya, carolan2020dichotomy, vidotto2020stellar}.
-Further investigation of magnetic star-planet interactions, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius, especially accounting for its moderately high eccentricity~(see also Section~\ref{sec:discussion:eccentricity}).
+Further investigation of magnetic SPI, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius, especially accounting for its moderately high eccentricity~(see also Section~\ref{sec:discussion:eccentricity}).
 
@@
 TAP 26 is a weak-line T-Tauri star with a strong magnetic field~\citep{yu2017hot}.
-\citet{lanza2018closeby} estimate that the system can release more energy in magnetic star-planet interaction than other  systems with Hot Jupiters, such as HD 179949, that has previously been detected with chromospheric variability in phase with the planet's orbit~\citep{shkolnik2008nature}.
+\citet{lanza2018closeby} estimate that the system can release more energy in magnetic SPI than other  systems with Hot Jupiters, such as HD 179949, that has previously been detected with chromospheric variability in phase with the planet's orbit~\citep{shkolnik2008nature}.
 However, for TAP 26 b, the orbital period might not be well-constrained.
@@
 The reason could be that KOI-12 b is in fact super-Alfv\'enic due to the relatively wide orbit compared to TAP 26 and HIP 67522.
-However, our estimate of the Alf\'en radius place KOI-12 b in the sub-Alfv\'enic regime~(see Fig.~\ref{fig:as}), although the scaling law applied there may be inaccurate for post-main sequence stars.
+However, our estimate of the Alfv\'en radius place KOI-12 b in the sub-Alfv\'enic regime~(see Fig.~\ref{fig:as}), although the scaling law applied there may be inaccurate for post-main sequence stars.
 Intermittent interaction might play a role here as well, and could be favored if future observations capture episodes during which the interaction is 'on'.
@@
 
-Magnetic star-planet interaction can only take place if the planet spends at least a part of its orbit in the sub-Alfv\'enic regime~(see Section~\ref{sec:intro:mspi}).
+Magnetic SPI can only take place if the planet spends at least a part of its orbit in the sub-Alfv\'enic regime~(see Section~\ref{sec:intro:mspi}).
 We estimated the average Alfv\'en surface size ($\overline{AS}_{R}$) using the power law established by \citet{Chebly2023}:
@@
 \label{sec:discussion:intermittency}
-Magnetic star-planet interaction power in a given system may sometimes be low for episodes of time, and high for others.
+Magnetic SPI power in a given system may sometimes be low for episodes of time, and high for others.
 HD 179949 is the prototype example for this phenomenon.
@@
 \label{sec:discussion:viewing}
-Modulated visibility of the magnetic interaction footpoint is crucial for the detection of flaring star-planet interactions in our analysis~(Fig.~\ref{fig:sketch}).
+Modulated visibility of the magnetic interaction footpoint is crucial for the detection of flaring SPI in our analysis~(Fig.~\ref{fig:sketch}).
 The viewing geometry of the star-planet system is therefore important to consider as an alternative to, or explanation for, the intermittency discussed above.
@@
 Assuming the dipole field dominates at the distance of the planet, the footpoint will be close to the pole, similar to the UV spot created by Io and the other moons in the polar cap of Jupiter~\citep{clarke1996farultraviolet, prange1996rapid}.
-In this scenario, many, especially non-transiting, systems may experience flaring star-planet interaction, but those would not show up as correlation of flare timing with the orbital phase in our data.
+In this scenario, many, especially non-transiting, systems may experience flaring SPI, but those would not show up as correlation of flare timing with the orbital phase in our data.
 
@@
 
-No observations of local tidal star-planet interaction exist yet.
+No observations of local tidal SPI exist yet.
 However, in the extreme case of RS CVn binaries, starspots often appear modulated with half the orbital period of the system~\citep{olah2002time, ozavci2018recurrent, kriskovics2023ei}.
@@
 
-The third model uses the gravitational perturbation as a proxy for the interaction~\citep{cuntz2000stellar}, originally derived for star-planet interactions.
+The third model uses the gravitational perturbation as a proxy for the interaction~\citep{cuntz2000stellar}, originally derived for SPI.
 Their Eqn.
@@
 
-We find that no single system shows significant signs of tidal star-planet interaction.
+We find that no single system shows significant signs of tidal SPI.
 Overall, the signal in phase with $P_{\rm orb}/2$ is smaller than with $P_{\rm orb}$.
@@
 
-We conducted the so far largest search for flaring star-planet interactions.
+We conducted the so far largest search for flaring star-planet interactions (SPI).
 Using over 7200 Quarters and Sectors of photometric monitoring from Kepler and TESS archives, we searched for flares in over 1800 systems of the about 3000 listed in the NASA Exoplanet Archive.
@@
 
-Our study is the first that systematically searched for flaring star-planet interactions, and is not limited by sampling or selection bias in the way earlier studies of this effect have often been.
+Our study is the first that systematically searched for flaring SPI in a large sample of systems, and is not limited by sampling or selection bias in the way earlier studies of this effect have often been.
 While our results remain tentative, future studies using our technique will benefit from accumulating data.
@@
 
-%\subsection{K2-354}
-We note that we found K2-354 under EPIC 211314705 and K2-329(!) in \cite{bouma2020cluster}, who refer to the detection paper \cite{pope2016transiting}, and also under TIC 468989066.
-
 \section{Expected power vs. AD test, color-coded by Rossby number}
@@
         \caption{
-        Expected power of SPI vs.
-AD test results, assuming the same four different scenarios as in Fig.~\ref{fig:adtest_bp}, color-coded by Rossby number.
+        Expected power of flaring SPI vs.
+AD test results, assuming the same four different scenarios as in Fig.~\ref{fig:adtest_bp}, here color-coded by Rossby number.
 $R\rm o=0.3$ is chosen to mark the transition from the saturated ($R\rm o < 0.3$) to the unsaturated ($R\rm o > 0.3$) activity regime.

### 2023-06-21 src/scripts/paper_main_table.py

@@ -118,10 +118,10 @@ if __name__ == "__main__":
         "st_lum":"log$_{10} L_{*}$ [L$_\odot$]",
         "Ro":"Ro",
         "B_G":"$B$ [G]",
-        "p_spi_sb_bp1_norm":"log$_{10} P_{sb}$",
-        "p_spi_aw_bp1_norm":"log$_{10} P_{aw}$",
-        "p_spi_sb_bp0_norm":"log$_{10} P_{sb0}$",
-        "p_spi_aw_bp0_norm":"log$_{10} P_{aw0}$",
+        "p_spi_sb_bp1_norm":"log$_{10} P_{\rm spi,sb}$",
+        "p_spi_aw_bp1_norm":"log$_{10} P_{\rm spi,aw}$",
+        "p_spi_sb_bp0_norm":"log$_{10} P_{\rm spi,sb0}$",
+        "p_spi_aw_bp0_norm":"log$_{10} P_{\rm spi,aw0}$",
         "v_rel_km_s":"$v_{rel}$ [km s$^{-1}$]",
         "mean":"p-value",
         }
@@ -252,8 +252,8 @@ if __name__ == "__main__":
             "$R_{p}$ [R$_J$]", "$a$ [$10^{-2}$ au]", "$e$", "log$_{10} L_{*}$ [L$_\odot$]"]
 
     # derived parameters table columns
-    der_cols = ["ID", "Ro", "$B$ [G]", "$v_{rel}$ [km s$^{-1}$]", "log$_{10} P_{sb}$",
-                "log$_{10} P_{sb0}$", "log$_{10} P_{aw}$", "log$_{10} P_{aw0}$", "p-value",]
+    der_cols = ["ID", "Ro", "$B$ [G]", "$v_{rel}$ [km s$^{-1}$]", "log$_{10} P_{\rm spi,sb}$",
+                "log$_{10} P_{\rm spi,sb0}$", "log$_{10} P_{\rm spi,aw}$", "log$_{10} P_{\rm spi,aw0}$", "p-value",]
 
     # make a list of tuples with the two column lists
     splitcols = [("lit", lit_cols), ("der", der_cols)]
@@ -288,8 +288,8 @@ if __name__ == "__main__":
 
         if label == "lit":
             note = (r"We note that we found K2-354 under EPIC 211314705 and K2-329(!)"
-                    r" in \cite{bouma2020cluster}, who refer to the detection paper"
-                    r" \cite{pope2016transiting}, and also under TIC 468989066.")
[…]

### 2023-06-21 src/scripts/paper_adtest_vs_value_scatterplots.py
split up main figure into two

@@ -233,7 +233,8 @@ def colorcode_B_G(bg):
     return color, symbol
 
 
-def make_adtest_figure(df, value, valuelabel, legend, labels, ext, ax, leg=False):
+def make_adtest_figure(df, value, valuelabel, legend, labels, ext, ax, leg=False,
+                       fontsize=13):
     """Create an AD test vs. value figure.
     
     Parameters
@@ -252,6 +253,10 @@ def make_adtest_figure(df, value, valuelabel, legend, labels, ext, ax, leg=False
         Extension for the figure name.
     ax : matplotlib.axes._subplots.AxesSubplot
         Axes to plot on.
+    leg : bool
+        Whether to plot the legend.
+    fontsize : int
+        Font size for the x and y labels.
     
     Returns
     -------
@@ -300,8 +305,8 @@ def make_adtest_figure(df, value, valuelabel, legend, labels, ext, ax, leg=False
                 color="k", verticalalignment="center")
 
     # labels
-    ax.set_ylabel("p-value of AD test", fontsize=13)
-    ax.set_xlabel(valuelabel, fontsize=13)
+    ax.set_ylabel("p-value of AD test", fontsize=fontsize)
+    ax.set_xlabel(valuelabel, fontsize=fontsize)
 
     # legend
     if leg == True:
@@ -379,10 +384,10 @@ if __name__ == "__main__":
 
     columns = ["p_spi_sb_bp1_norm", "p_spi_sb_bp0_norm",
               "p_spi_aw_bp1_norm", "p_spi_aw_bp0_norm"]
-    xlabels = [r"$\sim$ P$_{sb}$ (stretch-and-break interaction with magnetized planet)",
-              r"$\sim$ P$_{sb0}$  (stretch-and-break interaction with unmagnetized planet)",
-              r"$\sim$ P$_{aw}$  (Alfvén wing interaction with magnetized planet)",
-              r"$\sim$ P$_{aw0}$  (Alfvén wing interaction with unmagnetized planet)"]
+    xlabels = [r"$\sim$ $P_{\rm spi,sb}$ (stretch-and-break interaction with magnetized planet)",
+              r"$\sim$ $P_{\rm spi,sb0}$  (stretch-and-break interaction with unmagnetized planet)",
+              r"$\sim$ $P_{\rm spi,aw}$  (Alfvén wing interaction with magnetized planet)",
[…]

### 2023-06-21 src/scripts/paper_adtest_vs_value_scatterplots.py
swapped scenarios

@@ -452,7 +452,7 @@ if __name__ == "__main__":
     axes = axes.flatten()
 
     for value, valuelabel, ax in list(zip(columns, xlabels, axes)):
-        if value=="p_spi_sb_bp1_norm":
+        if value=="p_spi_sb_bp0_norm":
             leg = True
         else:
             leg = False
@@ -478,8 +478,8 @@ if __name__ == "__main__":
     fig, axes = plt.subplots(nrows=3, ncols=1, figsize=(6.5, 13))
     axes = axes.flatten()
 
-    for value, valuelabel, ax in list(zip(columns[1:], xlabels[1:], axes)):
-        if value=="p_spi_sb_bp0_norm":
+    for value, valuelabel, ax in list(zip(np.array(columns)[[0,2,3]], np.array(xlabels)[[0,2,3]], axes)):
+        if value=="p_spi_sb_bp1_norm":
             leg = True
         else:
             leg = False

### 2023-06-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Title
-\title{Flaring star-planet interactions in Kepler and TESS}
+\title{Planetary perturbers, or: flaring star-planet interactions in Kepler and TESS}
 
@@
     In the 1811 searched systems, we found 25 single stars with three or more flares each.
-We quantified the significance of the clustering in each system, and compared it against the theoretically expected amplitude of magnetic interaction that leads to planet-induced flaring.
+We quantified the significance of the clustering in each system, and compared it against the theoretically expected power of magnetic interaction that leads to planet-induced flaring.
 Most systems do not show any clustering, as expected from their relatively wide orbits.
 Those we expect to show planet-induced flaring fall on two branches.
-An inactive one, without any signs of clustering, and a tentative active one, where the clustering becomes more pronounced as the expected amplitude of interaction increases.
+An inactive one, without any signs of clustering, and a tentative active one, where the clustering becomes more pronounced as the expected power of interaction increases.
 The flares in HIP 67522, a young Hot Jupiter system, are prominently clustered ($p<0.006$), identifying it as the most promising candidate for magnetic star-planet interaction in our sample.
@@
 On the one hand, a close-in planet that changes the star's rotation and activity makes it more difficult for us to model the system's evolution, as it affects fundamental stellar parameters.
-Ages inferred from rotation will be biased, if the star is spun up or spun down relative to stars without close-in companions~\citep{tejadaarevalo2021further, brown2014discrepancies, maxted2015comparison}.
+Ages inferred from rotation will be biased, if the star is spun up or down relative to stars without close-in companions~\citep{tejadaarevalo2021further, brown2014discrepancies, maxted2015comparison}.
 Analogously, altered activity levels may mimic an older or younger host than it actually is~\citep{ilic2022tidal}.
@@
 
-The search for magnetic SPI (Section~\ref{sec:intro:mspi}) in the form of changes in global activity indicators~(Section~\ref{sec:intro:global}), has so far been a series of detections and non-detections, often due to selection bias in the studied systems.
+The search for magnetic SPI (Section~\ref{sec:intro:mspi}) in the form of changes in global activity indicators~(Section~\ref{sec:intro:global}) has so far been a series of detections and non-detections, often due to selection bias in the studied systems.
 Looking for local changes that trace the magnetic footpoint that connects planet to star mitigates this bias, but introduces another -- sampling bias due to poor orbital phase coverage.
@@
 In these studies, it is challenging both to define a control sample to measure the activity against, and to quantify how the way we detect planets introduces selection bias in the activity measure.
-It is, for instance, easier to detect a planet around a magnetically inactive star, because both radial velocity and transit detections will be less affected by stellar variability~\citep{poppenhaeger2011correlation}.
-Tidal interactions can also induce global increase in activity~\citep{ilic2022tidal}, which adds further ambiguity to the interpretation.
+It is, for instance, easier to detect a planet around a magnetically inactive star, because both radial velocity and transit detections will be less affected by stellar variability~\citep{poppenhaeger2011correlation}, but that does not imply that SPI quenches activity.
+Further, tidal interactions can induce global increase in activity~\citep{ilic2022tidal}, which adds a physical ambiguity to the interpretation~(see also Section~\ref{sec:discussion:tidal}).
 
@@
 \label{sec:intro:flares}
-In this study, we will look at stellar flares as another way of dissipating the energy stored in the magnetic field.
+In this study, we look at stellar flares as another way of dissipating the energy stored in the magnetic field.
 Flares are strong and impulsive eruptions released by reconnection and subsequent relaxation of field lines in the corona~\citep{svestka1976solar,priest2002magnetic}.
@@
 In expectation, however, in star-planet systems with favorable viewing geometries and magnetic field strengths and configurations, the footpoint visibility will be modulated in phase with the planetary orbit~(Fig.~\ref{fig:sketch}).
-The resulting phase preference of planet-induced flares introduces a deviation from a random distribution of flares.
+The resulting phase preference of planet-induced flares introduces a deviation from the otherwise random distribution of flares~\citep[see, e.g.,][]{doyle2018investigating,feinstein2020flare,howard2021evryflare}.
 Space missions like Kepler and TESS provide light curves that cover all phases of the planet's orbit, so that phase-correlated planet-induced flares can be detected against a background of uncorrelated intrinsic flaring.
@@
 We present the catalog of all flares found in our sample of star-planet systems, and compare the test results with the expected power of interaction for each system~(Section~\ref{sec:results}).
-We discuss the results for the most interesting star-planet systems individually~(Section~\ref{sec:results:individualstars}), and take a look at the patterns emerging from our analysis~(Section~\ref{sec:discussion}), and the possible role of tidal flaring SPI in our observations~(Section~\ref{sec:discussion:tidal}).
+We discuss the results for the most interesting star-planet systems individually~(Section~\ref{sec:results:individualstars}), and take a look at the patterns emerging from our analysis~(Section~\ref{sec:discussion}), as well as the possible role of tidal flaring SPI in our observations~(Section~\ref{sec:discussion:tidal}).
 We summarize our findings in Section~\ref{sec:summary}.
@@
 We searched a total of 1811 systems and over 7200 light curves from both missions for flares.
-To calculate the amount of excess flaring from SPI, we further required the orbital periods of each system~(Section~\ref{sec:data:orbitalperiod}).
-To compare our measurements to theory, we estimated the expected power of interaction for each system with at least three flares.
+To calculate the clustering of in orbital phase, we further required the orbital periods of each system~(Section~\ref{sec:data:orbitalperiod}).
+We then estimated the theoretically expected power of interaction for each system with at least three flares.
 For this, we required further system parameters -- distance between planet and star, stellar rotation period, planetary radius, and stellar luminosity~(Sections~\ref{sec:data:a}-\ref{sec:data:lum}), which we mostly took from the literature.
-We began by compiling the table of system parameters with the PSCP, but verified, supplemented and updated the table with more up-to-date results.
-The parameters for the systems in the final sample of 25 systems are shown in Table~\ref{tab:maintable_lit}.
+We began by compiling the table of system parameters with the PSCP, but verified, supplemented and updated the table with more up-to-date measurements.
+The relevant properties of the final sample of 25 systems are shown in Table~\ref{tab:maintable_lit}.
 
@@
 \movetableright=-20mm
-\footnotesize
+
     \script{paper_main_table.py}
     \caption{Flaring single star-planet system parameters.}
+
     \input{output/table_lit_vals.tex}
@@
 
-We note that we found K2-354 under EPIC 211314705 and K2-329(!) in \cite{bouma2020cluster}, who refer to the detection paper \cite{pope2016transiting}, and also under TIC 468989066.
+%We note that we found K2-354 under EPIC 211314705 and K2-329(!) in \cite{bouma2020cluster}, who refer to the detection paper \cite{pope2016transiting}, and also under TIC 468989066.
 
@@
 
-The Transiting Exoplanet Survey Satellite~[TESS, ][]\citep{ricker2015transiting} is an all-sky mission that began operations in 2018, completed two sky scans until summer 2022.
+The Transiting Exoplanet Survey Satellite~\citep[TESS,][]{ricker2015transiting} is an all-sky mission that began operations in 2018, completed two sky scans until summer 2022.
 It is observing at the time of writing, collecting nearly continuous photometric time series in the $600-1000\,$nm band for $\sim 27\,$d in each observing Sector.
@@
 
-Based on the filtered PSCP table, we use the \texttt{lightkurve}~\citep{lightkurvecollaboration2018lightkurve} Python software to query the full Kepler archive (quarters Q0-Q17, Data Release 25), and the most recent TESS catalog (July 2022) for their respective 1-min and 2-min/20-s cadence light curves.
-In total, we searched 7258 light curves for flares -- 3030 Kepler Quarters, and 4228 TESS Sectors.
+Based on the filtered PSCP table, we used the \texttt{lightkurve}~\citep{lightkurvecollaboration2018lightkurve} Python software to query the full Kepler archive (quarters Q0-Q17, Data Release 25), and the most recent TESS catalog (July 2022) for their respective 1-min and 2-min/20-s cadence light curves.
+In total, we searched 7213 light curves for flares -- 3032 Kepler Quarters, and 4181 TESS Sectors.
 We found and analyzed light curves for a total of 1811 systems, 344 of which were observed only by the primary Kepler mission, 1205 only by TESS, and 262 by both missions.
@@
 If the eccentricity is known, then the uncertainty on the distance is set to either the error on the semi-major axis, or to half of the difference between periastron and apoastron -- whichever is larger.
-If eccentricity is not known, then the uncertainty on the distance is set to either the 25\% error on the semi-major axis, that is, assuming $e=0.25$, or the uncertainty on the semi-major axis -- whichever is larger.
+If eccentricity is not known, then the uncertainty on the distance is set to either a 25\% error on the semi-major axis, that is, assuming $e=0.25$, or the uncertainty on the semi-major axis -- whichever is larger.
 We chose $e=0.25$ because it is both a typical value within our sample~(see Table~\ref{tab:maintable_lit}), and in the literature~\citep{eylen2019orbital}.
@@
 For the transiting planets, we adopt the literature values for planet radius $R_p$, and uncertainties, from the PSCP.
-For the non-transiting radial velocity detected planets we use the planetary mass $M_p$ or $M_p\sin i$ to calculate the radius or a lower limit for the radius using the empirical relations derived in \cite{chen2017probabilistic} using their open source \texttt{forecaster} tool, upgraded to \texttt{astro-forecaster}\footnote{https://pypi.org/project/astro-forecaster/} by Ben Cassesse.
+For the non-transiting radial velocity detected planets we use  $M_p\sin i$ to calculate a lower limit for the radius using the empirical relations derived in \cite{chen2017probabilistic} using their open source \texttt{forecaster} tool, upgraded to \texttt{astro-forecaster}\footnote{https://pypi.org/project/astro-forecaster/} by Ben Cassesse.
 We note that for GJ 674, the mass estimates in \cite{bonfils2007harps} and \cite{boisse2011disentangling} do not quote uncertainties, but differ by $0.3M_\oplus$, so we assumed that value as the uncertainty on $M_p\sin i$.
@@
 \label{sec:methods}
-We measure flaring SPI as the presence of excess flares triggered by the orbiting planet.
+We measure flaring SPI as the presence of flares triggered by the orbiting planet.
 In the absence of flaring SPI, flare peak times will be distributed randomly in orbital phase.
@@
 
-We vet all flare candidates by eye, and exclude instrumental false positives and physical ones like passing Solar System Objects.
+We vet all flare candidates by eye, and exclude instrumental and physical false positives, such as Solar System Objects passing by the field of view.
 For each confirmed flare candidate, we calculate the relative amplitude $a$ and equivalent duration $ED$, defined as the integrated flare flux $F_{\rm flare}$ over the duration of the flare, divided by the median flux $F_0$ of the star, integrated over the flare duration~\citep{gershberg1972results}:
@@
 As a last step, we compare the expected distribution to the observed one using an Anderson-Darling test.
-We repeat this test with different phase offsets to account for potential biases in sensitivity of the test at different phases.
+We repeat this test with different phase offsets to account for remaining biases in sensitivity of the test at different phases.
 
@@
 We calculated the orbital phases of each flare, and the flare phase distributions for each system~(Section \ref{sec:results:phasedist}).
-We then applied the custom Anderson-Darling test to assess how much each distribution was different from randomly distributed intrinsic flaring.
+We then applied a custom Anderson-Darling test~(see Section~\ref{sec:methods:adtest}) to assess how much each distribution was different from randomly distributed intrinsic flaring.
 Comparing the test results with the expected power of magnetic SPI, we found our main result: The clustering of flares in orbital phase tentatively increases with the expected power in all considered scenarios of magnetic SPI~(Section~\ref{sec:results:spi}).
@@
 To identify each event, we provide the name of the system in which the flare was found, along with its TIC, whether it was observed with Kepler or TESS, and during what Quarter or Sector, respectively.
-For each flare, we also give the start and finish time, relative amplitude $a$ and equivalent duration $ED$.
+For each flare, we also give the start and finish time, relative amplitude $a$ and equivalent duration $ED$~(Eq.~\ref{eq:ED}).
 If the transit midtime is known for the innermost planet, we also give the orbital phase at which the flare occurred.
-The full table is provided with the supplementary material, and via Zenodo (see Data Availability Statement).
+The full table is available online (see Data Availability Statement).
 
@@
 where $P$ is the orbital period, and $\sigma_P$ is its uncertainty.
-If the orbital period is well-known, the resulting ratio $\Delta T/\tau$ should be $<<1$.
+If the orbital period is well-known, the resulting ratio $\Delta T/\tau$ should be $\ll 1$.
 The bottom panel in Figure~\ref{fig:coherence_hist} shows a histogram of $\Delta T/\tau$ in our sample.
@@
 The three cases where the ratio is highest with $0.05$, $0.12$, $0.24$ deviation are TAP 26, GJ 3082, and GJ 674, respectively.
-We keep these systems in our sample, but caution that the measured absence of flaring SPI might be due to the uncertain orbital period of the planet in these cases.
+We keep these systems in our sample, but caution that the measured absence of flaring SPI might be partly due to the uncertain orbital period of the planet in these cases.
 
@@
 
-Figure~\ref{fig:adtest_bp} shows that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with magnetized or unmagnetized planets), there are two branches on the high end of expected powers.
+Figures~\ref{fig:adtest_bp} and \ref{fig:adtest_bp_rest} show that in every scenario we considered (Alfv\'en wing or stretch-and-break mechanism, with magnetized or unmagnetized planets, see Section~\ref{sec:methods:pspi}), there are two branches on the high end of expected powers.
 On one branch, the significance of the measured interaction increases with the expected power $P_{\rm spi}$.
@@
 There is no star-planet system for which we find a $>3\sigma$ ($p<0.0027$) signal of flaring SPI in our sample.
-However, overall, the significance of the deviation increases with higher expected power $P_{\rm spi}$ of interaction, where additional subscripts denote different scenarios introduced in Section~\ref{sec:methods:pspi}.
+However, overall, the significance of the deviation increases with higher expected power $P_{\rm spi}$ of interaction, introduced in Section~\ref{sec:methods:pspi}.
 Table~\ref{tab:maintable_der} also lists the derived parameters required in these scaling laws, i.e., Rossby number $R$o, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{\rm rel}$.
@@
 All powers are normalized to AU Mic.
-The $p$-value of the Anderson-Darling test is lower when the system shows more flares periodic with the planetary orbit.}
+The $p$-value of the Anderson-Darling test is lower when the system shows a stronger clustering of flares in orbital phase.}
 \input{output/table_der_vals.tex}
@@
             Expected power of magnetic SPI vs.
-AD test results, assuming the stretch-and-break scenario.
-While the distribution of $p$-values is consistent with no interaction, all scenarios indicate lower $p$-values only for high expected powers of interaction.
+AD test results, assuming the stretch-and-break scenario with an unmagnetized planet.
+While no individual system amounts to a $>3\sigma$ detection, the global trend is intriguing: Systems with low expected power show no deviation from random intrinsic flaring (i.e.
+high $p$-values).
+In contrast, systems with high expected power show two branches.
+One where the significance of interaction increases with power, and one without such a trend.
 See Fig.~\ref{fig:adtest_ro} in the Appendix for the same figure, color-coded by Rossby number.
@@
         \caption{
-            Same as Fig.~\ref{fig:adtest_bp}, but for three other scenarios.
-\textbf{Top panel}: stretch-and-break scenario for an unmagnetized planet.
-\textbf{Middle panel}: Alfv\'en wing scenario, assuming a magnetized planet.
-\textbf{Bottom panel}: Alfv\'en wing scenario, assuming an unmagnetized planet.
+            Same as Fig.~\ref{fig:adtest_bp}, but for three other scenarios for magnetic SPI.
+While the distribution of $p$-values is consistent with no interaction, all scenarios indicate lower $p$-values only for high expected powers of interaction.
+\textbf{Top panel}: stretch-and-break scenario with a magnetized planet.
+\textbf{Middle panel}: Alfv\'en wing scenario with a magnetized planet.
+\textbf{Bottom panel}: Alfv\'en wing scenario with an unmagnetized planet.
 See Fig.~\ref{fig:adtest_ro} in the Appendix for the same figure, color-coded by Rossby number.
@@
 In Section~\ref{sec:prominensystems}, in the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring SPI with increasing expected power $P_{\rm spi}$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522.
-Then we consider those systems where high power was expected in all scenarios, but not measured, i.e., TAP~26 and KOI-12.
+Then we consider those systems where high power was expected in all scenarios, but not measured: TAP~26 and KOI-12.
 \subsubsection{Excluded targets}
@@
 For instance, Kepler-808 (KOI-1300) has a $\sim0.4M_\odot$ \citep{kraus2016impact} companion that is about 1.8 mag fainter than the primary at a separation of $0.78\arcsec$~\citep{baranec2016roboao}.
-TOI-837 has co-moving M dwarf a few arcsec away in the same young cluster, 5 mag fainter, but the primary is an F9-G0 star, so flares could still originate come from both stars~\citep{bouma2020cluster}.
+TOI-837 has co-moving M dwarf a few arcsec away in the same young cluster, 5 mag fainter, but the primary is an F9-G0 star, so flares could still originate from both stars~\citep{bouma2020cluster}.
 HD 41004 B, DS Tuc A, and LTT 1445 are known multiple systems where all components contribute significantly to the total TESS flux.
@@
 Kepler-411 has a 3 mag fainter companion~\citep{wang2014influence,ziegler2018measuring}, but we do not exclude it from the analysis initially.
-The system was observed in Kepler short cadence by \citet{jackman2021stellara} and both the planet host, and the companion star flare.
-\citet{jackman2021stellara} disentangle the contributions from each component on a pixel level.
+The system was observed in Kepler short cadence by \citet{jackman2021stellara}, who found that both the planet host, and the companion star flare.
+The authors were able to disentangle the contributions from each component on a pixel level.
 According to \citet{morton2016false, sun2019kepler411}, Kepler-411's planets orbit the primary companion.
@@
 Adopting the 7 flares from \cite{jackman2021stellara} in our analysis, we find that they all have equivalent duration $ED<1\,$s, which excludes Kepler-411 from further analysis.
-Note that we do not find the low energy flares to cluster in orbital phase, either.
+Note, however, that we did not find the low energy flares to cluster in orbital phase, either, after applying our AD test procedure to the 7 correctly attributed flares.
 
@@
 AU Mic is a 16-29 Myr old pre-main sequence M0-M1 dwarf with a strong magnetic field of about $3010\pm220\,$G obtained from Zeeman broadening measurements~\citep{reiners2022magnetism}.
-The innermost Neptune-sized planet, AU Mic b, could be both inside the sub-Alfv\'enic zone if the star's mass loss rate is relatively low at about 30 times the solar value or lower~\citep{alvarado-gomez2022simulating}.
+The innermost Neptune-sized planet, AU Mic b, could be inside the sub-Alfv\'enic zone if the star's mass loss rate is relatively low at about 30 times the solar value or lower~\citep{alvarado-gomez2022simulating}.
 If the mass loss rate is high, exceeding the solar value by a factor of several hundreds, AU Mic b could orbit in the super-Alfv\'enic zone, and become unable to experience any planet-induced flaring.
@@
 Interestingly, K2-25 b is in a presumably similar environment to GJ 436 b, but does not show the atmospheric escape in Ly$\alpha$ that the latter famously exhibits, which might be due to high speed stellar winds that suppress atmospheric escape~\citep{rockcliffe2021lya, carolan2020dichotomy, vidotto2020stellar}.
-Further investigation of magnetic SPI, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius, especially accounting for its moderately high eccentricity~(see also Section~\ref{sec:discussion:eccentricity}).
+As strong winds push the Alfv\'en surface to smaller radii, further investigation of magnetic SPI, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius, especially accounting for its moderately high eccentricity~(see also Section~\ref{sec:discussion:eccentricity}).
 
@@
 
-In the scenario wherein the stretch-and-break mechanism drives the interaction, the three systems cluster together most distinctly~(top row in Figure~\ref{fig:adtest_bp}).
-In the Alfv\'en wing scenario~(bottom row in Figure~\ref{fig:adtest_bp}), the distinction is less clear.
+In the scenario wherein the stretch-and-break mechanism drives the interaction, the three systems cluster together most distinctly~(Figure~\ref{fig:adtest_bp} and top panel in Figure~\ref{fig:adtest_bp_rest}).
+In the Alfv\'en wing scenario~(middle and bottom panels in Figure~\ref{fig:adtest_bp_rest}), the distinction is less clear.
 In both cases, the low level (or possible absence) of interaction could be due to the Alfv\'en radius being within the planetary orbit.
 It is important to note that the scaling laws introduced in Section~\ref{sec:methods:pspi} assume that the planet is sub-Alfv\'enic, but make no statement about it, because the mass loss of these stars is largely unconstrained.
-All else equal, a planet is more likely sub-Alfv\'enic if the stellar magnetic field is strong.
-Another explanation is the possible intermittency, or 'on-off nature' of the interaction~\citep{shkolnik2008nature}, which may be at play here, but particularly in cases where the expected power is very strong, such as in the comparison between HIP 67522 and TAP 26 that we address in the following two Sections.
+All else equal, a planet is more likely sub-Alfv\'enic if the stellar magnetic field is strong~(see Section~\ref{sec:discussion:as} to see that the three planets are likely sub-Alfv\'enic).
+Another explanation is the possible intermittency, or 'on-off nature' of the interaction~\citep{shkolnik2008nature}, which may be at play here, but particularly in cases where the expected power is very strong, such as in the comparison between HIP 67522 and TAP 26 that we address in the following two paragraphs.
 
@@
 \label{sec:results:individualstars:hip67522}
-HIP 67522 has one of the strongest expected SPI signals in our sample, and shows the clearest sign of flaring SPI at $>2.5\sigma$ level, with 12 flares in the sample, distributed across three Sectors in TESS.
+has one of the strongest expected SPI signals in our sample, and shows the clearest sign of flaring SPI at $>2.5\sigma$ level ($p<0.006$), with 12 flares in the sample, distributed across three Sectors in TESS.
 In our original sample from July 2022, HIP 67522 was observed for two Sectors with a total of 6 flares, which yielded a $p$-value of $0.015$.
@@
 \label{sec:results:individualstars:tap26}
-TAP 26 is a weak-line T-Tauri star with a strong magnetic field~\citep{yu2017hot}.
+is a weak-line T-Tauri star with a strong magnetic field~\citep{yu2017hot}.
 \citet{lanza2018closeby} estimate that the system can release more energy in magnetic SPI than other  systems with Hot Jupiters, such as HD 179949, that has previously been detected with chromospheric variability in phase with the planet's orbit~\citep{shkolnik2008nature}.
@@
 With respect to rotation rate, stellar and planetary radius, the KOI-12 system is similar to HIP~67522 and TAP~26 (although for the those young stars the radii are large because the stars are still contracting onto the main sequence).
-In constrast, KOI-12 is $1.4\pm0.3\,$Gyr old~\citep{bourrier2015sophie}, an F5 subgiant~\citep{frasca2016activity}, which is already evolving off the main sequence.
+In constrast, KOI-12 is $1.4\pm0.3\,$Gyr old~\citep{bourrier2015sophie}, an F5 sub-giant~\citep{frasca2016activity}, which is already evolving off of the main sequence.
 Yet, despite its high expected power of interaction, we detect no excess flaring in phase with KOI-12 b.
 The reason could be that KOI-12 b is in fact super-Alfv\'enic due to the relatively wide orbit compared to TAP 26 and HIP 67522.
-However, our estimate of the Alfv\'en radius place KOI-12 b in the sub-Alfv\'enic regime~(see Fig.~\ref{fig:as}), although the scaling law applied there may be inaccurate for post-main sequence stars.
+Our estimate of the Alfv\'en radius place KOI-12 b in the sub-Alfv\'enic regime~(see Fig.~\ref{fig:as}), but the scaling law applied there may be inaccurate for post-main sequence stars.
 Intermittent interaction might play a role here as well, and could be favored if future observations capture episodes during which the interaction is 'on'.
@@
 
-Our results in Fig.~\ref{fig:adtest_bp} are tentative, yet the trend between expected power of interaction and measured clustering of flares in orbital phase is suggestive, as is the appearance of an active and an inactive branch at high expected powers.
+Our results in Fig.~\ref{fig:adtest_bp} are tentative, yet the trend between expected power of interaction and measured clustering of flares in orbital phase is suggestive, as is the appearance of an active and an inactive branch at high expected powers of magnetic SPI.
 We can now consider additional facts about the systems, as well as processes, that may explain the observed trends.
@@
 In Section~\ref{sec:discussion:tidal}, we repeat the analysis in this paper with $P_{orb}/2$, and find yet more tentative trends in line with scaling laws for tidal interaction.
-In a system-by-system comparison, we find consistency with the expectation that slowly rotating, likely old, systems can only show local tidal interaction, while rapidly rotating systems with strong magnetic fields can experience both.
+In a system-by-system comparison, we find consistency with the expectation that slowly rotating, likely old, systems can only show local tidal interaction, while rapidly rotating systems with strong magnetic fields are dominated by magnetic forces.
 \subsection{Alfv\'en surface}
@@
         \includegraphics[width=\hsize]{figures/PAPER_AS_vs_AD.png}
-    \caption{Magnetic flaring star-planet interaction strength ($p$-value of AD-test) vs.
+    \caption{Magnetic flaring star-planet interaction strength ($p$-value of AD test) vs.
 the innermost planet's location relative to the Alfv\'en surface radius.
@@
 This relation links the mean AS size with the maximum large-scale radial magnetic field ($B_{\rm r}^{\rm max}$) obtained in Zeeman-Doppler Imaging reconstructions (\citealt{donati2006surprising, morin2008largescale, fares2009magnetic, alvarado-gomez2015activity, hussain2016spectropolarimetric, kochukhov2020mapping}).
-The relation was derived from 3D~MHD stellar wind simulations cool main sequence stars (F, G, K, and M), which incorporated observed ZDI maps as boundary condition for the stellar radial magnetic field (for more details on the models see \citealt{Chebly2023}).
-However, the stellar magnetic field~($B$) in this work (Table~\ref{tab:maintable_der}), derived from the Rossby number of each star (Eq.~\ref{Eq3}, \ref{Eq4}), corresponds to the total, unsigned magnetic field strength on the stellar surface.
-As such, it is necessary to estimate how $B_{\rm r}^{\rm max}$ could be related to $B$.
-
-In \cite{reiners2022magnetism} it was reported that for Sun-like stars with a total magnetic field strength of up to 2000~G, the longitudinal magnetic field derived from Stokes V spectropolarimetric observations ($B_{\rm V}$) accounts for $\sim$\,$10$\% of the total magnetic field.
+The relation was derived from 3D~MHD stellar wind simulations of cool main sequence stars (F, G, K, and M), which used observed ZDI maps as boundary condition for the stellar radial magnetic field (for more details on the models see \citealt{Chebly2023}).
+However, the stellar magnetic field~($B$, Table~\ref{tab:maintable_der}), derived from the Rossby number (Eq.~\ref{Eq3}, \ref{Eq4}), corresponds to the total, unsigned magnetic field strength on the stellar surface, so that it is necessary to estimate how $B_{\rm r}^{\rm max}$ is related to $B$.
+
+\citet{reiners2022magnetism} report that for Sun-like stars with a total magnetic field strength of up to 2000~G, the longitudinal magnetic field derived from Stokes V spectropolarimetric observations ($B_{\rm V}$) accounts for $\sim$\,$10$\% of the total magnetic field.
 \cite{kochukhov2020hidden} showed that this trend also holds for M-dwarfs with magnetic fields up to 4000~G.
@@
 Since $B_{\rm V}$ is integrated over the visible surface of the star, this assumption will only hold if for an observing phase containing the strongest large-scale radial magnetic region, the effect from cancellation of opposite polarities is small.
-As such, in all other rotational phases we expect $B_{\rm V} < B_{\rm r}^{\rm max}$.
+At all other rotational phases, we expect $B_{\rm V} < B_{\rm r}^{\rm max}$.
 Therefore, by assuming $B_{\rm V} = B_{\rm r}^{\rm max}$ we are effectively taking an upper limit on the longitudinal magnetic field strength, which will be translated\footnote[3]{Naturally this will also depend on how good our $15$\% match between $B$ and $B_{\rm V}$ is to reality.} in our estimated values of $\overline{AS}_{R}$.
@@
 If the planetary orbit is highly eccentric, the difference between periastron and apoastron can be significantly larger than the variability of the Alfv\'en radius.
-If then apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, during the planet's rapid periastron passage.
-This was previously exploited in the case of HD 17156~\citep{maggio2015coordinated}, and analogously for the colliding magnetospheres in binary systems~\citep{massi2002periodic,getman2016search}.
+If then apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only briefly, during the planet's rapid periastron passage.
+This was previously exploited in the case of HD 17156~\citep{maggio2015coordinated}, and analogously for the colliding magnetospheres in binary systems~\citep{massi2002periodic,getman2016search,das2023discovery}.
 In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e\leq 0.35$.
@@
 If periastron passage in K2-25 occurs when the planet is in front of the star relative to the observer, the visibility effect of the interaction footpoint is further increased by the narrow phase range of the periastron passage.
-\citet{stefansson2020habitable} estimated the argument of periastron $\omega=120^{+12}_{-14}\,$deg for K2-25 (with longitude of the ascending node chosen such that $\omega$ is the same as the longitude of periastron, with $\omega=90\,$deg being periastron passage during transit,~\citealt{kipping2010investigations,dawson2012photoeccentric}).
+\citet{stefansson2020habitable} estimated the argument of periastron $\omega=120^{+12}_{-14}\,$deg for K2-25 (with longitude of the ascending node chosen such that $\omega$ is the same as the longitude of periastron, with $\omega=90\,$deg being periastron passage during transit, see~\citealt{kipping2010investigations,dawson2012photoeccentric}).
 We can therefore conjecture that the tentative signal of flaring SPI in K2-25 is enhanced by eccentricity.
-Statistically, we are more likely to observe a planetary transit close to periastron, since periastron permits more orbital inclinations than apoastron.
-So, overall, we expect eccentric transiting systems to experience elevated SPI signal.
+Statistically, we are more likely to observe a planetary transit close to periastron, since periastron permits more orbital inclinations to transit than apoastron.
+Overall, we expect eccentric transiting systems to experience elevated SPI signal, which could be tested in the future when better constraints on eccentricity become available~(see Table~\ref{tab:maintable_lit}).
 
@@
 \label{sec:discussion:intermittency}
-Magnetic SPI power in a given system may sometimes be low for episodes of time, and high for others.
-HD 179949 is the prototype example for this phenomenon.
+Magnetic SPI power in a star-planet system may sometimes be low for episodes of time, and high for others.
+HD~179949 is the prototype example for this phenomenon.
 The orbital modulation of its chromospheric indicators was observable for four out of six epochs on a five-year baseline~\citep{shkolnik2003evidence,shkolnik2008nature}.
@@
 TAP 26 and KOI-12 do not show any sign of excess flaring in our data, despite similar expected powers as in HIP 67522 with its $>2.5\sigma$ signal.
-However, other explanations cannot be ruled out yet (see Sections~\ref{sec:results:individualstars:tap26} and \ref{sec:results:individualstars:koi12}, and the following).
+However, other explanations cannot be ruled out yet (see Section~\ref{sec:results:individualstars}, and the following).
 
@@
 
-Consider a system, where orbit, and stellar spin and stellar magnetic dipole are aligned.
+Consider a system, where orbit, and stellar spin and stellar magnetic dipole are aligned~(Fig.~\ref{fig:sketch}).
 If the magnetic footpoint's latitude is low, i.e., close to the orbital plane, the orbital plane can be inclined to a high degree, and the footpoint will still periodically move in and out of view.
@@
 Most of our systems are transiting, and for those we can expect this scenario to be a minor problem unless the latitude of the footpoint is very high.
-Of the systems that have high expected power but do not show any excess flaring, only TAP 26 b is a planet detected in radial velocity, and has a relatively high orbital inclination of about $55\pm10$ deg inferred from photometry, spectroscopy, and Zeeman Doppler measurements~\citep{yu2017hot}.
+Of the systems that have high expected power but do not show any excess flaring, only TAP 26 b is a planet detected in radial velocity, and has a relatively high orbital inclination of about $55\pm10$ deg inferred from photometry, spectroscopy, and Zeeman Doppler measurements in~\citet{yu2017hot}.
 Their ZD map reveals magnetic field concentrations close to the rotational pole, and the brightness maps also show a dark spot in the same location.
@@
 \textbf{Round symbols} mark planets with measured  or estimated $M_p$ (see Section~\ref{sec:discussion:mpms}).
-           \textbf{Left panel}: The tidal torque in the system for stars with a convective envelope.
+           \textbf{Left panel}: Tidal torque in the system for stars with a convective envelope.
 Blue color indicates that the star rotates slower than the planet orbits, so that angular momentum is transferred from the orbit to the spin of the star.
@@
 We collect the planetary and stellar masses from the literature~(Table~\ref{tab:tidal}).
-For missing planetary masses, the radii were known, so we used the mass-radius relations implemented in \texttt{astro-forecaster}~[Ben Cassesse's implementation of \texttt{forecaster}][]\citep{chen2017probabilistic}.
+For missing planetary masses, the radii were known, so we used the mass-radius relations implemented in \texttt{astro-forecaster}~\citep[Ben Cassesse's implementation of \texttt{forecaster}][]{chen2017probabilistic}.
 GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute Ks magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}.
@@
 Kepler-1558 c has a similar radius to Kepler-42 b, i.e., most likely a bare core planet, so we used density ranging from Earth bulk density to pure rock to estimate its mass.
-We also adopt the upper limit of $5M_J$ for HIP 67522, but use the lower error from \citet{chen2017probabilistic}.
+We also adopt the upper limit of $5M_J$ for HIP 67522 from~\citet{rizzuto2020tess}, but use the lower error from \citet{chen2017probabilistic}.
 The assumptions we made here are conservative, and the estimates based on \citet{chen2017probabilistic} use a broad sample of planets, so we consider the planetary mass estimates with their respective uncertainties robust.
@@
 Using over 7200 Quarters and Sectors of photometric monitoring from Kepler and TESS archives, we searched for flares in over 1800 systems of the about 3000 listed in the NASA Exoplanet Archive.
-In the single star systems, where flares could be unambiguously attributed to the planet host, and showed three or more energetic events in the data, we searched for flares that clustered in orbital phase.
+When flares could be unambiguously attributed to the planet host, and showed three or more energetic events in the data, we searched for flares that clustered in orbital phase.
 Our final sample consisted of 25 systems, among them well-known flaring hosts like Proxima Cen, AU Mic, and TRAPPIST-1.
@@
 Applying both the stretch-and-break and Alfv\'en wing mechanisms for magnetic interaction, we found a tentative trend between the expected power of interaction, and the presence of excess flaring in phase with the orbital period $P_{\rm orb}$.
-In particular, we found that there may be two branches at high expected power -- one where the measured excess flaring is correlated with the expected power, and one where excess flaring is absent.
-While we can exclude the extent of the Alfv\'en surface as a reason, intermittency in the interaction, and the viewing geometry of the systems are candidates for explaining the branching.
+In particular, we found that there may be two branches at high expected power -- one where the measured orbital clustering increases with power, and one without a trend.
+While it is unlikely that the extent of the Alfv\'en surface is a reason, intermittency in the interaction and the viewing geometry of the systems could explain the branching.
+Among the investigated systems, the flares in HIP 67522, a young Sun-like Hot Jupiter host, cluster most distinctly, consistent with its deep embedding in the sub-Alfv\'enic zone and its high expected power of interaction.
 
@@
 
-Our study is the first that systematically searched for flaring SPI in a large sample of systems, and is not limited by sampling or selection bias in the way earlier studies of this effect have often been.
+Our study is the first that systematically searched for flaring SPI in a large sample of systems with excellent phase coverage.
 While our results remain tentative, future studies using our technique will benefit from accumulating data.
 The TESS mission continues to produce high precision light curves for many nearby active planet hosts, and the PLATO~\citep{rauer2014plato} mission will join in late 2026.
-For AU Mic, we may be only a few TESS Sectors away from a $3\sigma$ level confirmation~\citep{ilin2022searching} of the tentative interaction signal observed here and in other work~\citep{klein2022one}.
+For AU Mic, we may be only a few TESS Sectors away from a $3\sigma$ level confirmation~\citep{ilin2022searching} of the tentative interaction signal observed here and in other work~\citep{klein2022one}, and similarly for HIP 67522.
 Several systems in our sample are already scheduled for further observing with TESS, including Kepler-42, and KOI-12.
@@
 All data used in this study are publicly available in their respective archives.
-This study used the reproducibility software \href{https://github.com/showyourwork/showyourwork}{\showyourwork}
+This study used the reproducibility software \href{https://github.com/showyourwork/showyourwork}{showyourwork}
 \citep{luger2021mappinga} to create all figures, format all tables, and compile the manuscript.
-Each figure links to the dataset stored on Zenodo (link to be added after acceptance), and to the script that produced the figure in the git repository~\url{https://github.com/ekaterinailin/flaring-spi-paper}.
-The git repository that produces the data stored on Zenodo is publicly available at \url{https://github.com/ekaterinailin/flaring-spi}.
+Each figure links to the dataset stored on Zenodo (link to be added after acceptance), and to the script that produced the figure in the git repository~\href{https://github.com/ekaterinailin/flaring-spi-paper}{github.com/ekaterinailin/flaring-spi-paper}.
+The git repository that produces the data stored on Zenodo is publicly available at \href{https://github.com/ekaterinailin/flaring-spi}{github.com/ekaterinailin/flaring-spi}.
 \bibliography{bib}
@@
         Expected power of flaring SPI vs.
-AD test results, assuming the same four different scenarios as in Fig.~\ref{fig:adtest_bp}, here color-coded by Rossby number.
+AD test results, assuming the same four different scenarios as in Figures~\ref{fig:adtest_bp} and \ref{fig:adtest_bp_rest}, here color-coded by Rossby number.
 $R\rm o=0.3$ is chosen to mark the transition from the saturated ($R\rm o < 0.3$) to the unsaturated ($R\rm o > 0.3$) activity regime.

### 2023-06-23 src/scripts/paper_illustrative_sketch_of_system_geometries.py
more tweaks

@@ -217,12 +217,7 @@ if __name__ == "__main__":
 
     axes = [ax1, ax3]
     for ax in axes:
-        # right to the small circle draw a small arrow to the right
-        arr = ax.arrow(2, 3, 0.7, 0, head_width=0.3,
-                    head_length=0.1, fc='k', ec='k')
 
-        # annotate the arrow with LOS
-        ax.annotate('LOS', xy=(2, 3), xytext=(2, 3.4), fontsize=16)
 
         # set axis extent correctly
         ax.set_xlim(-3, 3)
@@ -231,9 +226,27 @@ if __name__ == "__main__":
         # remove axes
         ax.set_axis_off()
 
+    # right to the small circle draw a small arrow to the right
+    arr = ax1.arrow(1.8, 1.6, 0.5, 0, head_width=0.1,
+                head_length=0.07, fc='k', ec='k')
+
+    # annotate the arrow with LOS
+    ax1.annotate('LOS', xy=(1.8, 1.8), xytext=(1.8, 1.7), fontsize=16)
+
+    # right to the small circle draw a small arrow to the right
+    arr = ax3.arrow(2, 1.9, 0.6, 0, head_width=0.15,
+                head_length=0.07, fc='k', ec='k')
+
+    # annotate the arrow with LOS
+    ax3.annotate('LOS', xy=(2, 2.1), xytext=(2, 2), fontsize=17)
+
+    # set axis extent correctly
+    ax1.set_xlim(-2.5, 2.5)
+    ax1.set_ylim(-2.5, 2.5)
+
     # label each panel with letter in upper left corner
-    for label, ax in zip(list("abc"), axes):
-        ax.text(0., 0.97, label + ".", transform=ax.transAxes,
+    for label, ax in zip(list("ab"), axes):
+        ax.text(0., 0.95, label + ".", transform=ax.transAxes,
                 fontsize=18, fontweight='bold', va='top', ha='right')
         
     plt.tight_layout()

### 2023-06-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/system_geometries.png}
+        \includegraphics[width=0.8\linewidth]{figures/system_geometries.png}
         \caption{
-         Simplified magnetic star-planet interaction (SPI) geometries.\textbf{ Panel a: Fully aligned system along the line of sight (LOS).
-}Magnetic, rotational, and orbital axis are aligned.
-The interaction footpoint moves along the black line, and is visible to the observer on the red line, i.e.
+         Simplified magnetic star-planet interaction (SPI) viewing geometries.
+The hatched hemisphere is visible to the observer.
+\textbf{ Panel a: Fully aligned system along the line of sight (LOS).
+} Magnetic, rotational, and orbital axis are aligned.
+The interaction footpoint moves along the black line, and is visible to the observer on the red latitude, i.e.
 during $50\%$ of the planet's orbit.
-Flares induced along this line will result in excess flares when the planet is in front of the star.
-\textbf{Panel b: Orbital misalignment.} Same a panel a., but the planet's orbit is misaligned.
-The footpoint of interaction is again visible $50\%$ of the time, resulting in modulated flaring with orbital phase.
-However, it passes different latitudes on the star, which correspond to different dipole field strengths and coronal regions, which may affect the power of interaction.
-\textbf{Panel c: Inclined fully aligned system.} The red interaction footpoint line is visible $100\%$ of the time.
+Flares induced along this latitude will result in excess flares when the planet is in front of the star \textbf{Panel b: Inclined fully aligned system.} The interaction footpoint latitude is visible $100\%$ of the time.
 No modulation due to magnetic SPI can be observed, even if flares are triggered by the planet.
 The sketches only show the interaction on one hemisphere of the star, but they may appear on both.
+More complicated geometries arise when orbital, rotational and magnetic axis are mutually misaligned.
+The two panels also illustrate how a planet in a closer orbit interacts at a lower latitude than a farther out planet.
 }

### 2023-06-23 src/scripts/paper_illustrative_sketch_of_system_geometries.py
restack

@@ -33,7 +33,7 @@ import paths
 if __name__ == "__main__":
 
     # init two figure panels next to each other
-    fig, (ax1, ax3) = plt.subplots(1, 2, figsize=(10, 5))
+    fig, (ax1, ax3) = plt.subplots(2, 1, figsize=(5, 9))
 
     # Central star
     for ax in [ax1, ax3]:
@@ -231,7 +231,7 @@ if __name__ == "__main__":
                 head_length=0.07, fc='k', ec='k')
 
     # annotate the arrow with LOS
-    ax1.annotate('LOS', xy=(1.8, 1.8), xytext=(1.8, 1.7), fontsize=16)
+    ax1.annotate('LOS', xy=(1.8, 1.8), xytext=(1.8, 1.7), fontsize=16.5)
 
     # right to the small circle draw a small arrow to the right
     arr = ax3.arrow(2, 1.9, 0.6, 0, head_width=0.15,

### 2023-06-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Title
-\title{Planetary perturbers, or: flaring star-planet interactions in Kepler and TESS}
+\title{Planetary perturbers: Flaring star-planet interactions in Kepler and TESS}
 
@@
     \begin{centering}
-        \includegraphics[width=0.8\linewidth]{figures/system_geometries.png}
+        \includegraphics[width=0.7\linewidth]{figures/system_geometries.png}
         \caption{
-         Simplified magnetic star-planet interaction (SPI) viewing geometries.
-The hatched hemisphere is visible to the observer.
-\textbf{ Panel a: Fully aligned system along the line of sight (LOS).
-} Magnetic, rotational, and orbital axis are aligned.
-The interaction footpoint moves along the black line, and is visible to the observer on the red latitude, i.e.
-during $50\%$ of the planet's orbit.
-Flares induced along this latitude will result in excess flares when the planet is in front of the star \textbf{Panel b: Inclined fully aligned system.} The interaction footpoint latitude is visible $100\%$ of the time.
-No modulation due to magnetic SPI can be observed, even if flares are triggered by the planet.
-The sketches only show the interaction on one hemisphere of the star, but they may appear on both.
-More complicated geometries arise when orbital, rotational and magnetic axis are mutually misaligned.
-The two panels also illustrate how a planet in a closer orbit interacts at a lower latitude than a farther out planet.
+         Simple magnetic star-planet interaction (SPI) viewing geometries.
+\textbf{a.: system aligned along the line of sight (LOS).
+} The interaction footpoint moves along the black line, and is on the visible hemisphere (hatched area) for $50\%$ of the  orbit (red line).
+Flaring SPI can be observed as modulation of flare occurrence times.
+\textbf{b.: Inclined system.} The interaction latitude is visible $100\%$ of the time, so no modulation can be observed.
+Interaction is shown on one hemisphere, but may appear on both.
+Complex geometries arise when orbital, rotational and magnetic axis are misaligned.
+The panels also illustrate how a planet in a closer orbit (a.) interacts at a lower latitude than a farther out planet (b.).
 }

### 2023-07-04 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-\author[0000-0001-7579-3728]{Nikoleta Ilic}
+\author[0000-0001-7579-3728]{Nikoleta Ili\'c}
 \affiliation{Leibniz Insitute for Astrophysics Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany}
@@
 These flares are not expected to appear different from intrinsic stellar flares individually.
-
 However, as we expect planet-induced flares to be associated with the planet's orbital period $P_{orb}$, we can identify their presence from a clustering of flares in phase with the planet's orbital phase.
@@
 We quantified the significance of the clustering in each system, and compared it against the theoretically expected power of magnetic interaction that leads to planet-induced flaring.
-Most systems do not show any clustering, as expected from their relatively wide orbits.
+Most systems do not show any clustering, in accordance with low expected power.
 Those we expect to show planet-induced flaring fall on two branches.
@@
 
-\begin{figure*}[ht!]
+\begin{figure}[ht!]
 \script{paper_illustrative_sketch_of_system_geometries.py}
     \begin{centering}
-        \includegraphics[width=0.7\linewidth]{figures/system_geometries.png}
+        \includegraphics[width=0.9\linewidth]{figures/system_geometries.png}
         \caption{
@@
 \begin{table*}
+\script{paper_main_table.py}
 \movetableright=-20mm
 
-    \script{paper_main_table.py}
     \caption{Flaring single star-planet system parameters.}
-
+\scriptsize
     \input{output/table_lit_vals.tex}
@@
         \includegraphics[width=\hsize]{figures/PAPER_tidal_AD_test.png}
-    \caption{Deviation from random flare times in phase with $P_{\rm orb}/2$, i.e., in phase with tidal bulges raised on the star, compared to different models of tidal interaction~(Section~\ref{sec:discussion:tidal}).
+    \caption{Deviation from random flare times in phase with $P_{\rm orb}/2$, i.e., in phase with the two tidal bulges raised on the star, compared to different models of tidal interaction~(Section~\ref{sec:discussion:tidal}).
 \textbf{Cross symbols} mark planets with $M_p \sin i$ measurements.
@@
 \begin{table*}
+\script{paper_table_tidal.py}
 \footnotesize
 \movetableright=-20mm
-\script{paper_table_tidal.py}
 \caption{Flaring tidal star-planet interaction parameters and $p$-value of the custom Anderson-Darling test. }
@@
         Expected power of flaring SPI vs.
-AD test results, assuming the same four different scenarios as in Figures~\ref{fig:adtest_bp} and \ref{fig:adtest_bp_rest}, here color-coded by Rossby number.
+AD test results, assuming the same four scenarios as in Figures~\ref{fig:adtest_bp} and \ref{fig:adtest_bp_rest}, here color-coded by Rossby number.
 $R\rm o=0.3$ is chosen to mark the transition from the saturated ($R\rm o < 0.3$) to the unsaturated ($R\rm o > 0.3$) activity regime.

### 2023-07-04 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Author list
-\author[0000-0002-6299-7542]{Ekaterina Ilin }
+\author[0000-0002-6299-7542]{Ekaterina Ilin}
 \affiliation{Leibniz Insitute for Astrophysics Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany}
@@
 These flares are not expected to appear different from intrinsic stellar flares individually.
-However, as we expect planet-induced flares to be associated with the planet's orbital period $P_{orb}$, we can identify their presence from a clustering of flares in phase with the planet's orbital phase.
+However, as we expect planet-induced flares to be associated with the planet's orbital period $P_{\rm orb}$, we can identify their presence from a clustering of flares in phase with the planet's orbital phase.
 We used the excellent phase coverage obtained from Kepler and the Transiting Exoplanet Survey Satellite to find flaring star-planet systems, compile a catalog of all their flares, and measure how much they cluster in orbital phase.
@@
 
-In the 2010s, a wealth of flare observations from space missions like Kepler~\citep{borucki2010kepler} and K2~\citep{howell2014k2} have been catalogued~\citep{davenport2016kepler, paudel2018k2, ilin2021flares}.
+In the 2010s, a wealth of flare observations from space missions like Kepler~\citep{borucki2010kepler} and K2~\citep{howell2014k2} have been cataloged~\citep{davenport2016kepler, paudel2018k2, ilin2021flares}.
 We now have access to long-term stellar monitoring data available for flare hunting.
@@
 
-%Short intro to SaB mechanism
-
-%Short intro to AW mechanism
-
-% ----------------------------------------------------------------------------------
-
-% In both models, the radius of the perturbing body, and its proximity increase the power of interaction. Would it not be more reasonable to search for star-brown dwarf or star-star interactions?
-
-% Flares caused by magnetic interactions in close binary systems were previously observed.
-Flares detected on the young eccentric binary system V 773 Tau could be attributed to colliding magnetospheres~\citep{massi2002periodic, massi2008interacting}, while other promising systems, like DQ Tau, another young equal-mass binary system in a strongly eccentric orbit, did not live up to the expectations~\citep{salter2008captured,salter2010recurring,getman2011young,getman2016search, kospal2018spots}.
-In these systems, it is, however, unclear whether it is mass transfer or reconnection that drive excess coronal emission and flares at periastron.
-Substellar objects can orbit the star much closer than a stellar companion without filling the Roche lobe.
-Gravitationally, a rocky planet can go unnoticed by its host even if it orbits at ultrashort periods of less than a day.
-% Interactions in systems with brown dwarf companions are less likely than binary systems
-
 \section{Data}
@@
 
-%We note that we found K2-354 under EPIC 211314705 and K2-329(!) in \cite{bouma2020cluster}, who refer to the detection paper \cite{pope2016transiting}, and also under TIC 468989066.
-
 \subsection{Star-planet systems}
@@
 Between 2009 and 2013, the Kepler space telescope~\citep{koch2010kepler} nearly continuously observed a patch of the sky in the Cygnus-Lyra region.
-Each of the 18 observing Quarters contains nearly uninterrupted $\sim 90$ days of observations, totaling over $100\,000$ stars monitored in 2-min cadence in a broad $400-850\,$nm bandpass.
+Each of the 18 observing Quarters contains nearly uninterrupted $\sim 90$ days of observations, totaling over $100\,000$ stars monitored in 2-min cadence in a broad $400-850\,$nm band pass.
 % 100000 from here: https://exoplanetarchive.ipac.caltech.edu/docs/KeplerMission.html
@@
 
-Among the stars without given uncertainties, the rotation of GJ 3082 was measured and is consistent both in TESS and in KELT light curves to below 1\,s precision~\citep{gunther2020stellar}.
-The rotation of GJ 674 is consistent between light curve periodograms~\citep{kiraga2007agerotationactivity}, and activity-rotation relations~\citep{boisse2011disentangling} at a $<10\%$ level.
-GJ 3323 only has rotation periods inferred from activity indicators~\citep{astudillo-defru2017magnetic}, without any periodicity detected in the activity indicators themselves~\citep{astudillo-defru2017harps}.
-The rotation of Proxima Cen is very slow, but consistent between different datasets~\citep{anglada-escude2016terrestrial, kiraga2007agerotationactivity}.
+Among the stars without given uncertainties, the rotation of GJ~3082 was measured and is consistent both in TESS and in KELT light curves to below 1\,s precision~\citep{gunther2020stellar}.
+The rotation of GJ~674 is consistent between light curve periodograms~\citep{kiraga2007agerotationactivity}, and activity-rotation relations~\citep{boisse2011disentangling} at a $<10\%$ level.
+GJ~3323 only has rotation periods inferred from activity indicators~\citep{astudillo-defru2017magnetic}, without any periodicity detected in the activity indicators themselves~\citep{astudillo-defru2017harps}.
+The rotation of Proxima~Cen is very slow, but consistent between different datasets~\citep{anglada-escude2016terrestrial, kiraga2007agerotationactivity}.
 In general, among the stars without given uncertainties on the rotation period, the period is either
 \begin{itemize}
-    \item short, leaving a clear peak in the periodogram, and little doubt about the period after ruling out aliases with $P/2$, as with GJ 3082, or
-    \item longer than the Sun's, that is, in the regime where rotation-activity relations are reliable because the stars are in the unsaturated activity regime, as in the case of GJ 674, and GJ 3323.
+    \item short, leaving a clear peak in the periodogram, and little doubt about the period after ruling out aliases with $P_{\rm rot}/2$, as with GJ~3082, or
+    \item longer than the Sun's, that is, in the regime where rotation-activity relations are reliable because the stars are in the unsaturated activity regime, as in the case of GJ~674, and GJ~3323.
 \end{itemize}
@@
 
-The convective turnover time $\tau$ in  $R \rm o=P_{rot}/\tau$ is derived using bolometric luminosity~(Section~\ref{sec:data:lum}), following~\citet{reiners2014generalized, reiners2022magnetism}:
+The convective turnover time $\tau$ in  $R \rm o=P_{\rm rot}/\tau$ is derived using bolometric luminosity~(Section~\ref{sec:data:lum}), following~\citet{reiners2014generalized, reiners2022magnetism}:
 
@@
 \citet{fischer2019timevariable} argue that the synodic period, at which the sub-planetary point crosses the same (magnetic) surface element on the star, may result in a clearer interaction signal, because a magnetically active region that is prone to planet-induced flares, will be passed only once per that period.
-However, we repeated the coherence calculation for $P_{rot}$, and found that the ratio is $>0.1$ for most stars~(Figure~\ref{fig:coherence_hist}, top panel), so that a statistical analysis of rotational flare modulation is not feasible.
-%We argue, however, that in a transiting system with high orbital inclination, the effect with synodic period reduces to modulation with the orbital period:
-
-%If the orbital axis inclination is high, then the passage will regularly occur on the back of the star relative to the observer.
-The true period will therefore be additionally modulated by the visibility, resulting in an intermittency of the signal.
-As a consequence, to detect a modulation with the synodic period, a significantly longer observing baseline is needed than to detect a modulation with the orbital period.
-Additionally, if there are many active regions (at the same time, or in sequence) that produce flares when the sub-planetary footpoint passes across, the effect with the synodic period further converges to a modulation with orbital period.
-%In our sample, the observing baseline is multiple years long for many systems.
-Most stars, even the most rigidly rotating late M dwarfs, show variability in their spot modulation on such long timescales~\citep[e.g.,][]{giles2017kepler,davenport2015spots, namekata2019lifetimes}).
-
-% Even if differential rotation was absent and active regions were extremely stable, we would likely be unable to observe the passage of the sub-planetary point over the flare-prone region every synodic period.
-
-%However, this assumes that the landscape of active regions on the star is stable throughout the entire observing time, and that the number of such regions in the footpoint passageway is low enough to produce a periodic modulation.
-Note that this is a different effect from the geometrical modulation of visibility we look for in modulation with the orbital period in this study.
-
-%Even for the few stars, for which the rotational period is known precisely enough, we need to make numerous assumptions.
-These include the number of active regions crossed by the footpoint of interaction, differential rotation, spot evolution, and a significant correlation between the location of the planet and the location of the planet-induced flare on the stellar surface.
-For modulation with the orbital period, we require only that last correlation between footpoint location and orbital phase.
-
-%There are three reasons for this: First, the uncertainty for the rotation was not always provided, in which case we assigned a $10\%$ error.
-Second, rotation period is more difficult to ascertain from a light curves' variability than the orbital period, particularly if the modulation is weak and/or rapidly evolving.
-And third, differential rotation causes spots at different latitudes to move at different speeds, so it becomes difficult to even define a rotation period, as long as we don't know at which latitude(s) the flares occur~(see also Section~\ref{sec:discussion:rotsyn}).
+However, we repeated the coherence calculation for $P_{\rm rot}$, and found that the ratio is $>0.1$ for most stars~(Figure~\ref{fig:coherence_hist}, top panel), so that a statistical analysis of rotational flare modulation is not feasible.
 
@@
 TOI-837 has co-moving M dwarf a few arcsec away in the same young cluster, 5 mag fainter, but the primary is an F9-G0 star, so flares could still originate from both stars~\citep{bouma2020cluster}.
-HD 41004 B, DS Tuc A, and LTT 1445 are known multiple systems where all components contribute significantly to the total TESS flux.
+HD~41004~B, DS~Tuc~A, and LTT~1445 are known multiple systems where all components contribute significantly to the total TESS flux.
 
@@
 With respect to rotation rate, stellar and planetary radius, the KOI-12 system is similar to HIP~67522 and TAP~26 (although for the those young stars the radii are large because the stars are still contracting onto the main sequence).
-In constrast, KOI-12 is $1.4\pm0.3\,$Gyr old~\citep{bourrier2015sophie}, an F5 sub-giant~\citep{frasca2016activity}, which is already evolving off of the main sequence.
+In contrast, KOI-12 is $1.4\pm0.3\,$Gyr old~\citep{bourrier2015sophie}, an F5 sub-giant~\citep{frasca2016activity}, which is already evolving off of the main sequence.
 Yet, despite its high expected power of interaction, we detect no excess flaring in phase with KOI-12 b.
@@
 Locally, however, we can discriminate between the two by their relevant periods, that is, $P_{\rm orb}$ and $P_{\rm orb /2}$.
-In Section~\ref{sec:discussion:tidal}, we repeat the analysis in this paper with $P_{orb}/2$, and find yet more tentative trends in line with scaling laws for tidal interaction.
+In Section~\ref{sec:discussion:tidal}, we repeat the analysis in this paper with $P_{\rm orb}/2$, and find yet more tentative trends in line with scaling laws for tidal interaction.
 In a system-by-system comparison, we find consistency with the expectation that slowly rotating, likely old, systems can only show local tidal interaction, while rapidly rotating systems with strong magnetic fields are dominated by magnetic forces.
@@
 If then apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only briefly, during the planet's rapid periastron passage.
-This was previously exploited in the case of HD 17156~\citep{maggio2015coordinated}, and analogously for the colliding magnetospheres in binary systems~\citep{massi2002periodic,getman2016search,das2023discovery}.
+This was previously exploited in the case of HD~17156~\citep{maggio2015coordinated}, and analogously for the colliding magnetospheres in binary systems~\citep{massi2002periodic,getman2016search,das2023discovery}.
 In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e\leq 0.35$.
@@
 This leaves room for many different explanations.
-Uninterrupted, long-term monitoring of individual systems is required to investigate the reasons for the temporary cessation of interaction.
 Candidate mechanisms for the star include:
@@
     \item the Alfv\'en radius moving in- and out the planet's orbit, either over the course of an activity cycle, or through short-term variations in the magnetic field and wind properties caused by, e.g., coronal mass ejections;
-    \item the interacting footpoint moving to higher latitudes due to changes in the large scale field, which reduces the modulation of its visibility 
-    \item an active latitude (i.e., small scale field) moving away from the magnetic footpoints passageway; or
-    \item the available magnetic energy decreasing such that the flares or other magnetic interaction indicators still occur but fall below the detection threshold for a period of time.
+    \item the interacting footpoint moving to higher latitudes due to changes in the large scale field, which reduces the modulation of its visibility; 
+    \item an active latitude (i.e., small scale field) moving away from the magnetic footpoints passageway;
+    \item the available magnetic energy decreasing such that the flares or other magnetic interaction indicators still occur but fall below the detection threshold for a period of time; or
     \item the availability of a sufficient amount of plasma in the vicinity of the magnetic interaction region to yield significant observable flare emission in the stellar atmosphere (in analogy to the Jupiter-Io system, wherein Io's volcanism provides the plasma that eventually produces an interaction hotspot on Jupiter,~\citealt{clarke1996farultraviolet, prange1996rapid})
@@
 Orbital precession of misaligned planets can also cause such intermittency, if it periodically brings the footpoints trajectory on the stellar surface fully into view so that it is no longer modulated.
-
-%Interpreting non-detections as effects of viewing geometry in fully aligned systems ignores this caveat.
-
-%If we assume that the magnetic dipole axis and the rotation axis of the star are relatively well-aligned, the spin-orbit alignment may have an influence on interaction strength.
-For instance,  HAT-P-11 rotates nearly pole-on, and HAT-P-11 b is transiting in a near-polar orbit~\citep{bourrier2023dream}.
-
-% \subsection{(Mis-)alignment between orbital, rotational and stellar magnetic axis}
-% \label{sec:discussion:misalignment}
-
-%  Relaxing the assumption of alignment between rotational and magnetic dipole axis, we introduce a further complication that is not only due to viewing geometry.
-
-% or more broadly system architecture including misalignment of the magnetic axis. See HAT-P-11, or instance, and the many polar orbits in \cite{bourrier2023dream}
-
-% \cite{miskovetz2022resolving}  found background stars that were not co-moving HAT-P-11.
-
-% HD 179949 has a strong misalignment of about 70 deg between rotational and magnetic axis.
-Time-resolved X-ray observations~\citep{acharya2022xray} suggest that the magnetic interaction footpoint is close to the stellar rotational pole, which would be close to the magnetic equator of the strongly dipolar field of HD 179949
 
@@
 In ellipsoidal binaries, a modulation of flares with $P_{\rm orb}/2$ beyond geometrical effects was observed with Kepler~\citep{gao2016whitelight}, suggesting flaring regions at the location of the extreme tidal bulges in these stars.
-However, all these systems are synchronized, $P_{rot}=P_{\rm orb}$, so that intrinsic active longitudes~\citep{usoskin2007longterm, weber2013theory, jarvinen2005spots, lanza2009corot} cannot be disambiguated from the result of tidal star-star interaction ~\citep{holzwarth2003dynamics}.
+However, all these systems are synchronized, $P_{\rm rot}=P_{\rm orb}$, so that intrinsic active longitudes~\citep{usoskin2007longterm, weber2013theory, jarvinen2005spots, lanza2009corot} cannot be disambiguated from the result of tidal star-star interaction ~\citep{holzwarth2003dynamics}.
 
@@
 
-The first model measures the torque $\partial L_{\rm conv} / \partial t$, exerted by angular momentum transfer between star and planet, assuming the star has a convective envelope~(\citealt{penev2012constraining}, their Eqns.
-1 and 2).
+The first model measures the torque $\partial L_{\rm conv} / \partial t$, exerted by angular momentum transfer between star and planet, assuming the star has a convective envelope~(\citealt{penev2012constraining}, their Eqns.~1~and~2).
 We choose the tidal quality factor $Q_*=10^7$, i.e., low efficiency of tidal dissipation, as a conservative estimate.
@@
 The second model considers the tidal dissipation timescale -- the shorter the timescale, the higher the power of the interaction~\citep{zahn1977tidal}.
-Following~\citet{ilic2022tidal}, we adopt Eqn.
-2 in~\citet{albrecht2012obliquities} for the tidal dissipation timescale in the convective envelope.
+Following~\citet{ilic2022tidal}, we adopt Eq.~2 in~\citet{albrecht2012obliquities} for the tidal dissipation timescale in the convective envelope.
 We assume that all stars in our sample have a convective envelope because they flare, and flaring requires a dynamo-generated magnetic field, which can only operate in stars with convective envelopes or fully convective stars.
@@
 The third model uses the gravitational perturbation as a proxy for the interaction~\citep{cuntz2000stellar}, originally derived for SPI.
-Their Eqn.
-1 proposes a gravitational perturbation proportional to the mass ratio between planet and star, and $a^{-3}$.
+Their Eq.~1 proposes a gravitational perturbation proportional to the mass ratio between planet and star, and $a^{-3}$.
 
@@
 We collect the planetary and stellar masses from the literature~(Table~\ref{tab:tidal}).
-For missing planetary masses, the radii were known, so we used the mass-radius relations implemented in \texttt{astro-forecaster}~\citep[Ben Cassesse's implementation of \texttt{forecaster}][]{chen2017probabilistic}.
-GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute Ks magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}.
+For missing planetary masses, the radii were known, so we used the mass-radius relations implemented in \texttt{astro-forecaster}~\citep[Ben Cassesse's implementation of \texttt{forecaster},][]{chen2017probabilistic}.
+GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute $K_s$ magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}.
 For Kepler-42 b, we used  $M_p=0.1-2.06M_\oplus$ that covers pure rock to pure iron compositions in \citet{muirhead2012characterizing}, and adopted the logarithmic mean for our estimate.
@@
 However, if the observed deviations from intrinsic flaring do in fact represent low level tidal interaction signal, we can conclude that close-in planets can interact both magnetically and tidally.
-In line with theoretical considerations~\citep{strugarek2017fate}, our results tentatively suggest that magnetic interaction is more pronounced for planets with fast rotating, active hosts, while tidal interactions affect both systems with slowly and rapidly rotating stars.
+In line with theoretical considerations~\citep{strugarek2017fate}, our results tentatively suggest that magnetic interaction is more pronounced for planets with fast rotating, active hosts, while tidal interactions dominate systems with slowly rotating, inactive stars.
 Finally, exceptions such as TAP 26 exemplify that the simple scaling laws we applied here may not capture the complexity of the interaction.
@@
 When flares could be unambiguously attributed to the planet host, and showed three or more energetic events in the data, we searched for flares that clustered in orbital phase.
-Our final sample consisted of 25 systems, among them well-known flaring hosts like Proxima Cen, AU Mic, and TRAPPIST-1.
-
-Applying both the stretch-and-break and Alfv\'en wing mechanisms for magnetic interaction, we found a tentative trend between the expected power of interaction, and the presence of excess flaring in phase with the orbital period $P_{\rm orb}$.
+Our final sample consisted of 25 systems, among them well-known flaring hosts like Proxima~Cen, AU~Mic, and TRAPPIST-1.
+
+Applying both the stretch-and-break and Alfv\'en wing mechanisms for magnetic star-planet interaction, we found a tentative trend between the expected power of interaction, and the presence of excess flaring in phase with the orbital period $P_{\rm orb}$.
 In particular, we found that there may be two branches at high expected power -- one where the measured orbital clustering increases with power, and one without a trend.
 While it is unlikely that the extent of the Alfv\'en surface is a reason, intermittency in the interaction and the viewing geometry of the systems could explain the branching.
-Among the investigated systems, the flares in HIP 67522, a young Sun-like Hot Jupiter host, cluster most distinctly, consistent with its deep embedding in the sub-Alfv\'enic zone and its high expected power of interaction.
+Among the investigated systems, the flares in HIP~67522, a young Sun-like Hot Jupiter host, cluster most distinctly in orbital phase, consistent with its deep embedding in the sub-Alfv\'enic zone and its high expected power of interaction.
 
@@
 We found a similar trend with different scaling laws of tidal interaction, albeit at even lower significance.
-Our system-by-system comparison suggests that young systems, like HIP 67522, may be dominated by magnetic interaction, whereas old, magnetically inactive systems, like Kepler-42, might mostly interact tidally.
+Our system-by-system comparison suggests that young systems, like HIP~67522, may be dominated by magnetic interaction, whereas old, magnetically inactive systems, like Kepler-42, might mostly interact tidally.
 

### 2023-08-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-  %  In our results, HIP 67522, a 17 Myr old solar type star with a Hot Jupiter in a 7-day orbit, shows the most pronounced clustering with only a 0.006 probability of coincidence.
-While short of a $3\sigma$ detection,
-
-  %  We also searched our data for locally expressed tidal interaction, i.e., flares clustering in phase with the tidal bulges ($P_{\rm orb}/2$).
-We find a marginal trend with different scaling laws of tidal interaction.
-Our system-by-system comparison tentatively suggests that young systems can interact both tidally and magnetically, whereas old, magnetically inactive systems mostly interact tidally.
-    %magnetic field strength (using $Ro$-$B$ relations), orbital parameters, and planet radius.
 \end{abstract}
@@
 As a last step, we compare the expected distribution to the observed one using an Anderson-Darling test.
-We repeat this test with different phase offsets to account for remaining biases in sensitivity of the test at different phases.
+\textcolor{red}{For this, we sample 10000 times from the expected distribution the same number of flares we observe in each system, e.g., for HIP 67522, we sample 12 flares distributed according to the blue curve in Fig.~\ref{fig:cumdist_transiting}.
+For each of the 10000 samples, we compute the Anderson-Darling statistic $A^2$, which yields a distribution of $A^2$ values.
+In a last step, we compute $A^2$ for the observed distribution, and compute the $p$-value.} We repeat this test with different phase offsets to account for remaining biases in sensitivity of the test at different phases.
 
@@
 \begin{equation}
-    P_{\rm spi,aw} \sim B_p^{2/3} R_{p}^2    B_*^{1/3}  v_{rel}^2 a^{-2}  
+    P_{\rm spi,aw} \sim B_p^{2/3} R_{p}^2  R_*^2  B_*^{1/3}  v_{rel}^2 a^{-2} \rho_*^{1/2} \sin^2 \theta
 \end{equation}
-where we replace the stellar wind density $\rho_W$ with its proportionality to $a^{-2}$, and stellar wind magnetic field at the planetary radius $B_W$ with the surface field strength $B_* a^{-3}$, which result in the total $a^{-2}$ factor in the above equation.
+\textcolor{red}{where we replace the stellar wind density $\rho_W$ with its proportionality to $\rho_* (R_* / a)^{2}$, and stellar wind magnetic field at the planetary radius $B_W$ with the surface field strength $B_* (R_* / a)^{3}$, which result in the total $R_*^2 a^{-2}$ factor in the above equation.
+Since the stellar wind density at the stellar surface $\rho_*$ is poorly constrained empirically~\citep{vidotto2021evolution}, we follow~\citet{alvarado-gomez2020tuning,kavanagh2021planetinduced}, and fix $\rho_*=2\cdot10^{-10}\rm{cm}^{-3}$.
+The angle between the wind magnetic field vector and the velocity vector of the planet $\theta$ is also unknown, so we set $\sin\theta=1$ to obtain an upper limit.
+In reality, $\theta$ will vary both between systems, and over time in any individual system.
+Omitting $\rho_*$ assumes that all stellar wind densities are the same in our sample, which is not true in reality.
+The dependence on $\rho_*$ is stronger than that on $B_*$, but weaker than on every other parameter, so it may dominate the magnetic field dependence.}
 
@@
 \begin{equation}
-    P_{\rm spi,aw0} \sim R_p^2  B_*  v_{rel}^2  a^{-4}
+    P_{\rm spi,aw0} \sim R_p^2 R_*^4 B_*  v_{rel}^2 a^{-4} \rho_*^{1/2} \sin^2 \theta
 \end{equation}
 
-Lacking $B_p$, and various additional factors that appear in $P_{\rm spi,sb},P_{\rm spi,sb0},P_{\rm spi,aw}$, and  $P_{\rm spi,aw0}$, such as the angle between the relative velocity and magnetic field of the stellar wind~\citep{kavanagh2022radio}, or the force-free parameter~\citep{lanza2012starplanet}, we restrict ourselves to differential estimates, and normalize all $P_{\rm spi}$ to AU Mic.
+Lacking $B_p$, and various additional factors that appear in $P_{\rm spi,sb},P_{\rm spi,sb0},P_{\rm spi,aw}$, and  $P_{\rm spi,aw0}$, such as the angle between the relative velocity and magnetic field of the stellar wind~\citep{kavanagh2022radio}, or the force-free parameter~\citep{lanza2012starplanet}, we restrict ourselves to differential estimates, and normalize all $P_{\rm spi}$ to AU Mic\textcolor{red}{'s value of $XXXX$.}
 
@@
 Magnetic SPI can only take place if the planet spends at least a part of its orbit in the sub-Alfv\'enic regime~(see Section~\ref{sec:intro:mspi}).
-We estimated the average Alfv\'en surface size ($\overline{AS}_{R}$) using the power law established by \citet{Chebly2023}:
+We estimated the average Alfv\'en surface size ($\overline{AS}_{R}$) using the power law established by \citet{chebly2023numerical}:
 
@@
 This relation links the mean AS size with the maximum large-scale radial magnetic field ($B_{\rm r}^{\rm max}$) obtained in Zeeman-Doppler Imaging reconstructions (\citealt{donati2006surprising, morin2008largescale, fares2009magnetic, alvarado-gomez2015activity, hussain2016spectropolarimetric, kochukhov2020mapping}).
-The relation was derived from 3D~MHD stellar wind simulations of cool main sequence stars (F, G, K, and M), which used observed ZDI maps as boundary condition for the stellar radial magnetic field (for more details on the models see \citealt{Chebly2023}).
+The relation was derived from 3D~MHD stellar wind simulations of cool main sequence stars (F, G, K, and M), which used observed ZDI maps as boundary condition for the stellar radial magnetic field (for more details on the models see \citealt{chebly2023numerical}).
 However, the stellar magnetic field~($B$, Table~\ref{tab:maintable_der}), derived from the Rossby number (Eq.~\ref{Eq3}, \ref{Eq4}), corresponds to the total, unsigned magnetic field strength on the stellar surface, so that it is necessary to estimate how $B_{\rm r}^{\rm max}$ is related to $B$.

### 2023-08-15 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-Third, we estimate the power of SPI generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio}, combining Eqns.~8~and~11 in \citet{kavanagh2022radio} to arrive at
+Third, we estimate the power of SPI generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio},\textcolor{red}{ combining Eqn.~8 for the power of interaction and Eqn.~11 for the magnetopause radius of the planet from\citet{kavanagh2022radio} to arrive at:}
 
@@
 \end{equation}
-\textcolor{red}{where we replace the stellar wind density $\rho_W$ with its proportionality to $\rho_* (R_* / a)^{2}$, and stellar wind magnetic field at the planetary radius $B_W$ with the surface field strength $B_* (R_* / a)^{3}$, which result in the total $R_*^2 a^{-2}$ factor in the above equation.
+
+\textcolor{red}{Here, we assume that the magnetopause radius extends to where the magnetic pressures of planet and stellar magnetic wind -- which is dominated by the magnetic field in de sub-Alf\'enic regime -- are equal.
+We also replace the stellar wind density $\rho_W$ with its proportionality to $\rho_* (R_* / a)^{2}$, and stellar wind magnetic field at the planetary radius $B_W$ with the surface field strength $B_* (R_* / a)^{3}$, which result in the total $R_*^2 a^{-2}$ factor in the above equation.
 Since the stellar wind density at the stellar surface $\rho_*$ is poorly constrained empirically~\citep{vidotto2021evolution}, we follow~\citet{alvarado-gomez2020tuning,kavanagh2021planetinduced}, and fix $\rho_*=2\cdot10^{-10}\rm{cm}^{-3}$.
@@
 
-And fourth, we also consider the case of an unmagnetized planet with $B_p=0$, in which case Eq.~8 in \cite{kavanagh2022radio} reduces to
+And fourth, we also consider the case of an unmagnetized planet\textcolor{red}{ where the magnetospheric radius is set equal to the planetary radius}, in which case Eq.~8 in \cite{kavanagh2022radio} reduces to
 
@@
 
-Lacking $B_p$, and various additional factors that appear in $P_{\rm spi,sb},P_{\rm spi,sb0},P_{\rm spi,aw}$, and  $P_{\rm spi,aw0}$, such as the angle between the relative velocity and magnetic field of the stellar wind~\citep{kavanagh2022radio}, or the force-free parameter~\citep{lanza2012starplanet}, we restrict ourselves to differential estimates, and normalize all $P_{\rm spi}$ to AU Mic\textcolor{red}{'s value of $XXXX$.}
+Lacking $B_p$, and various additional factors that appear in $P_{\rm spi,sb},P_{\rm spi,sb0},P_{\rm spi,aw}$, and  $P_{\rm spi,aw0}$, such as the angle between the relative velocity and magnetic field of the stellar wind~\citep{kavanagh2022radio}, or the force-free parameter~\citep{lanza2012starplanet}, we restrict ourselves to differential estimates, and normalize all $P_{\rm spi}$ to AU Mic.
 
@@
 On the other branch, no interaction is measured regardless of $P_{\rm spi}$.
+\textcolor{red}{For all powers of SPI, we normalize the values to AU Mic, and give an overview over the normalization values in Table~\ref{tab:aumic}}.
 
@@
 \end{figure}
+
+\begin{table}
+\script{paper_aumic_table.py}
+\caption{Powers of star-planet interaction calculated for AU Mic in the four different scenarios introduced in Section~\ref{sec:methods:pspi}.}
+\input{output/aumic_spi.tex}
+    \label{tab:aumic}
+\end{table}
 

### 2023-08-15 src/scripts/paper_aumic_table.py
fix missing dollar

@@ -21,10 +21,10 @@ if __name__ == "__main__":
     aumicspi = df.loc[df.TIC == "441420236"]
 
     # select SPI scenarios
-    vals = [("p_spi_erg_s", r"P_{\rm spi,sb}$", "stretch-and-break, magnetized planet"),
-            ("p_spi_erg_s_bp0", r"P_{\rm spi,sb0}$", "stretch-and-break, unmagnetized planet"),
-            ("p_spi_kav22", r"P_{\rm spi,aw}$", r"Alfv\'en wing, magnetized planet"),
-            ("p_spi_kav22_bp0", r"P_{\rm spi,aw0}$", r"Alfv\'en wing, unmagnetized planet")]
+    vals = [("p_spi_erg_s", r"$P_{\rm spi,sb}$", "stretch-and-break, magnetized planet"),
+            ("p_spi_erg_s_bp0", r"$P_{\rm spi,sb0}$", "stretch-and-break, unmagnetized planet"),
+            ("p_spi_kav22", r"$P_{\rm spi,aw}$", r"Alfv\'en wing, magnetized planet"),
+            ("p_spi_kav22_bp0", r"$P_{\rm spi,aw0}$", r"Alfv\'en wing, unmagnetized planet")]
 
     # init SPI tab
     aumictab = pd.DataFrame(columns=["SPI scenario","abbrev.","AU Mic power [erg/s]"])

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 % Begin!
+\usepackage{makecell}
 \begin{document}
@@
 For the non-transiting system, phase zero is set arbitrarily.
+
 \subsection{Semi-major axes and eccentricities}
@@
 \label{sec:data:planetradii}
-For the transiting planets, we adopt the literature values for planet radius $R_p$, and uncertainties, from the PSCP.
-For the non-transiting radial velocity detected planets we use  $M_p\sin i$ to calculate a lower limit for the radius using the empirical relations derived in \cite{chen2017probabilistic} using their open source \texttt{forecaster} tool, upgraded to \texttt{astro-forecaster}\footnote{https://pypi.org/project/astro-forecaster/} by Ben Cassesse.
-We note that for GJ 674, the mass estimates in \cite{bonfils2007harps} and \cite{boisse2011disentangling} do not quote uncertainties, but differ by $0.3M_\oplus$, so we assumed that value as the uncertainty on $M_p\sin i$.
+For the transiting planets, we adopt the literature values for planet radius $R_{\rm p}$, and uncertainties, from the PSCP.
+For the non-transiting radial velocity detected planets we use  $M_{\rm p}\sin i$ to calculate a lower limit for the radius using the empirical relations derived in \cite{chen2017probabilistic} using their open source \texttt{forecaster} tool, upgraded to \texttt{astro-forecaster}\footnote{https://pypi.org/project/astro-forecaster/} by Ben Cassesse.
+We note that for GJ 674, the mass estimates in \cite{bonfils2007harps} and \cite{boisse2011disentangling} do not quote uncertainties, but differ by $0.3M_\oplus$, so we assumed that value as the uncertainty on $M_{\rm p}\sin i$.
 
@@
 \begin{eqnarray}
-    B &= 199\,\text{G} \cdot R\rm o^{-1.26\pm 0.1} \;(\text{if}\; Ro > 0.13) \label{Eq3}\\
-    B &= 2050\,\text{G} \cdot R\rm o^{-0.11\pm 0.03} \;(\text{if}\; Ro < 0.13) \label{Eq4}
+    B &= 199\,\text{G} \cdot R\mathrm{o}^{-1.26\pm 0.1} \;(\text{if}\; R\mathrm{o} > 0.13) \label{Eq3}\\
+    B &= 2050\,\text{G} \cdot R\mathrm{o}^{-0.11\pm 0.03} \;(\text{if}\; R\mathrm{o} < 0.13) \label{Eq4}
 \end{eqnarray}
 
-The convective turnover time $\tau$ in  $R \rm o=P_{\rm rot}/\tau$ is derived using bolometric luminosity~(Section~\ref{sec:data:lum}), following~\citet{reiners2014generalized, reiners2022magnetism}:
+The convective turnover time $\tau$ in  $R \mathrm{o}=P_{\rm rot}/\tau$ is derived using bolometric luminosity~(Section~\ref{sec:data:lum}), following~\citet{reiners2014generalized, reiners2022magnetism}:
 
 \begin{equation}
-    \tau = 12.3\, \rm d \cdot (L_{\rm bol}/L_\odot)^{-1/2}
+    \tau = 12.3\, \mathrm{d} \cdot (L_{\rm bol}/L_\odot)^{-1/2}
 \end{equation}
@@
 We compared our derived values for $R$o and $B$ with existing estimates of coronal emission.
-We show $L_X/L_{\rm bol}$ obtained from~\citet{foster2022exoplanet} as a function of $Ro$ and $B$ in Fig.~\ref{fig:lx}.
+We show $L_X/L_{\rm bol}$ obtained from~\citet{foster2022exoplanet} as a function of $R$o and $B$ in Fig.~\ref{fig:lx}.
 The X-ray emission relation to Rossby number in our sample follows that of stars that are not known to host close-in planets~\citep{wright2011stellaractivityrotation}, spanning both the saturated and unsaturated regime.
@@
 \begin{equation}
-    P_{\rm spi,sb} \sim B_p^{2/3} R_p^2 B_*^{4/3} R_*^4 v_{rel} a^{-4} .
+    P_{\rm spi,sb} \sim B_{\rm p}^{2/3} R_{\rm p}^2 B_*^{4/3} R_*^4 v_{\rm rel} a^{-4} .
 \end{equation}
 
-$B_p$ and $B_*$ are the planetary and stellar field strengths at their poles, respectively; $v_{rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis $a$; and $R_*$ and $R_p$ are the stellar and planetary radii, respectively.
+$B_{\rm p}$ and $B_*$ are the planetary and stellar field strengths at their poles, respectively; $v_{\rm rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis $a$; and $R_*$ and $R_{\rm p}$ are the stellar and planetary radii, respectively.
 Since the planetary fields are unknown, we ignore them in the calculation.
@@
 
-Second, we also consider the case of an unmagnetized planet with $B_p=0$, in which case Eq.~45 in~\cite{lanza2012starplanet} reduces to
+Second, we also consider the case of an unmagnetized planet with $B_{\rm p}=0$, in which case Eq.~45 in~\cite{lanza2012starplanet} reduces to
 
 \begin{equation}
-    P_{\rm spi,sb0} \sim R_p^2 R_*^4 B_*^2 v_{rel}    a^{-4} 
+    P_{\rm spi,sb0} \sim R_{\rm p}^2 R_*^4 B_*^2 v_{\rm rel}    a^{-4} 
 \end{equation}
@@
 \begin{equation}
-    P_{\rm spi,aw} \sim B_p^{2/3} R_{p}^2  R_*^2  B_*^{1/3}  v_{rel}^2 a^{-2} \rho_*^{1/2} \sin^2 \theta
+    P_{\rm spi,aw} \sim B_{\rm p}^{2/3} R_{p}^2  R_*^2  B_*^{1/3}  v_{\rm rel}^2 a^{-2} \rho_*^{1/2} \sin^2 \theta
 \end{equation}
@@
 \begin{equation}
-    P_{\rm spi,aw0} \sim R_p^2 R_*^4 B_*  v_{rel}^2 a^{-4} \rho_*^{1/2} \sin^2 \theta
+    P_{\rm spi,aw0} \sim R_{\rm p}^2 R_*^4 B_*  v_{\rm rel}^2 a^{-4} \rho_*^{1/2} \sin^2 \theta
 \end{equation}
 
-Lacking $B_p$, and various additional factors that appear in $P_{\rm spi,sb},P_{\rm spi,sb0},P_{\rm spi,aw}$, and  $P_{\rm spi,aw0}$, such as the angle between the relative velocity and magnetic field of the stellar wind~\citep{kavanagh2022radio}, or the force-free parameter~\citep{lanza2012starplanet}, we restrict ourselves to differential estimates, and normalize all $P_{\rm spi}$ to AU Mic.
+Lacking $B_{\rm p}$, and various additional factors that appear in $P_{\rm spi,sb},P_{\rm spi,sb0},P_{\rm spi,aw}$, and  $P_{\rm spi,aw0}$, such as the angle between the relative velocity and magnetic field of the stellar wind~\citep{kavanagh2022radio}, or the force-free parameter~\citep{lanza2012starplanet}, we restrict ourselves to differential estimates, and normalize all $P_{\rm spi}$ to AU Mic.
 
@@
 If the orbital period is well-known, the resulting ratio $\Delta T/\tau$ should be $\ll 1$.
-The bottom panel in Figure~\ref{fig:coherence_hist} shows a histogram of $\Delta T/\tau$ in our sample.
+\textcolor{red}{Here, we are not interested in the absolute orbital phase, but only in the relative one.
+Therefore, we can ignore that the uncertainty on phase zero at transit midtime increases with the time passed since the transit midtime was measured.
+For non-transiting systems, this time can amount to several years, and the midtime is unconstrained by the time of the observation with Kepler or TESS.
+For transiting systems, the midtime is usually very well known.
+So in the following, we set phsae zero to an arbitrary time in non-transiting systems, and to the reported transit midtime for the rest.} The bottom panel in Figure~\ref{fig:coherence_hist} shows a histogram of $\Delta T/\tau$ in our sample.
 The orbital period is known sufficiently well for our analysis in most cases with ratios $<0.02$, that is, the orbital phase of the last flare is at most $2\%$ off, compared to the first.
@@
 \caption{Flaring star-planet interaction.
-$Ro$, $B$, and $v_{rel}$, are derived from literature values (Table~\ref{tab:maintable_lit}).
+$Ro$, $B$, and $v_{\rm rel}$, are derived from literature values (Table~\ref{tab:maintable_lit}).
 $P_{\rm spi,xx}$ stands for the power of stretch-and-break ($sb$) and Alfv\'en wing ($aw$) interaction mechanisms, assuming the planet has a magnetic field strength of $1\,$G.
@@
 \begin{table}
+\movetableright=-10mm
 \script{paper_aumic_table.py}
-\caption{Powers of star-planet interaction calculated for AU Mic in the four different scenarios introduced in Section~\ref{sec:methods:pspi}.}
+\caption{\textcolor{red}{Powers of star-planet interaction calculated for AU Mic in the four different scenarios introduced in Section~\ref{sec:methods:pspi}.}}
 \input{output/aumic_spi.tex}
@@
 %The only single star system excluded is GJ 1061.
-The star is lacking a stellar rotation period estimate, which we need to calculate the magnetic field, and $v_{rel}$.
+The star is lacking a stellar rotation period estimate, which we need to calculate the magnetic field, and $v_{\rm rel}$.
 \citet{dreizler2020reddots} estimate that it is a fairly slow rotator with a period between 50 and 200 days, so we do not expect it to have a strong magnetic field anyway.
@@
 Magnetic and tidal SPI are difficult to disentangle by their global effects on stellar activity indicators~(Section~\ref{sec:intro:global}).
-Locally, however, we can discriminate between the two by their relevant periods, that is, $P_{\rm orb}$ and $P_{\rm orb /2}$.
+Locally, however, we can discriminate between the two by their relevant periods, that is, $P_{\rm orb}$ and $P_{\rm orb} /2$.
 In Section~\ref{sec:discussion:tidal}, we repeat the analysis in this paper with $P_{\rm orb}/2$, and find yet more tentative trends in line with scaling laws for tidal interaction.
@@
     \caption{Deviation from random flare times in phase with $P_{\rm orb}/2$, i.e., in phase with the two tidal bulges raised on the star, compared to different models of tidal interaction~(Section~\ref{sec:discussion:tidal}).
-\textbf{Cross symbols} mark planets with $M_p \sin i$ measurements.
-\textbf{Round symbols} mark planets with measured  or estimated $M_p$ (see Section~\ref{sec:discussion:mpms}).
+\textbf{Cross symbols} mark planets with $M_{\rm p} \sin i$ measurements.
+\textbf{Round symbols} mark planets with measured  or estimated $M_{\rm p}$ (see Section~\ref{sec:discussion:mpms}).
            \textbf{Left panel}: Tidal torque in the system for stars with a convective envelope.
@@
 For missing planetary masses, the radii were known, so we used the mass-radius relations implemented in \texttt{astro-forecaster}~\citep[Ben Cassesse's implementation of \texttt{forecaster},][]{chen2017probabilistic}.
-GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute $K_s$ magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}.
-For Kepler-42 b, we used  $M_p=0.1-2.06M_\oplus$ that covers pure rock to pure iron compositions in \citet{muirhead2012characterizing}, and adopted the logarithmic mean for our estimate.
+GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute $K_{\rm s}$ magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}.
+For Kepler-42 b, we used  $M_{\rm p}=0.1-2.06M_\oplus$ that covers pure rock to pure iron compositions in \citet{muirhead2012characterizing}, and adopted the logarithmic mean for our estimate.
 Kepler-1558 c has a similar radius to Kepler-42 b, i.e., most likely a bare core planet, so we used density ranging from Earth bulk density to pure rock to estimate its mass.
-We also adopt the upper limit of $5M_J$ for HIP 67522 from~\citet{rizzuto2020tess}, but use the lower error from \citet{chen2017probabilistic}.
+We also adopt the upper limit of $5M_{\rm J}$ for HIP 67522 from~\citet{rizzuto2020tess}, but use the lower error from \citet{chen2017probabilistic}.
 The assumptions we made here are conservative, and the estimates based on \citet{chen2017probabilistic} use a broad sample of planets, so we consider the planetary mass estimates with their respective uncertainties robust.
-We note, however, that the mass estimates for RV-detected planets are $M_p \sin i$, so that their expected interaction may be stronger than indicated in Fig.~\ref{fig:tidal}.
+We note, however, that the mass estimates for RV-detected planets are $M_{\rm p} \sin i$, so that their expected interaction may be stronger than indicated in Fig.~\ref{fig:tidal}.
 

### 2023-10-03 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Sections~\ref{sec:methods:relvel} and \ref{sec:methods:bfield}, respectively.
-We can then combine them with stellar radius, planetary radius, and semi-major axis to estimate the power of SPI.
+We can then combine them with \textcolor{red}{the} stellar radius, planetary radius, and semi-major axis to estimate the power of SPI.
 We use the scaling laws for two different magnetic SPI models, which we introduce in Section~\ref{sec:methods:pspi}.
@@
 We use the same customized Anderson-Darling test as in \cite{ilin2022searching}, which is more sensitive to deviations at both ends of the distribution than the widely used Kolmogorov-Smirnov test~\citep{feigelson2012modern}.
-In brief, we first take the number of flares observed in the TESS and Kepler data to calculate a base flare rate for each light curve.
+In \textcolor{red}{short}, we first take the number of flares observed in the TESS and Kepler data to calculate a base flare rate for each light curve.
 We then calculate how often each orbital phase has been observed, also for each light curve separately, to ensure that the different detection thresholds for TESS and Kepler do not bias the base rate.
@@
 \label{sec:methods:bfield}
-We derive the average magnetic field strength $B$ from $R$o using the empirical relation derived in \citet{reiners2022magnetism},  Table 2, in the unsaturated and saturated regimes, respectively:
+We derive the average magnetic field strength $B$ from \textcolor{red}{Rossby number} $R$o using the empirical relation derived in \citet{reiners2022magnetism},  Table 2, in the unsaturated and saturated regimes, respectively:
 
@@
 
-First, we estimate the power of SPI generated by the stretch-and-break mechanism using the scaling relations in~\cite{lanza2012starplanet} (their Eqn. 45), where $P_{\rm spi,sb}$ is proportional to
+First, we estimate the power of SPI generated by the stretch-and-break mechanism using the scaling relations in~\cite{lanza2012starplanet}.
+\textcolor{red}{We adopt their Eqn.
+45 for non-linear and axisymmetric magnetic fields, because the non-linear formulation does not assume a constant force-free parameter, and because only axisymmetric fields are able to produce modulation of flaring activity in phase with the planetary orbit.
+We note that the axisymmetry of stellar magnetic fields varies across stars~\citep[e.g.,][]{donati2009magnetic, donati2008largescale, morin2008largescale, morin2010largescale}, and also with the stellar activity cycle of individual stars~\citep[e.g.,][]{borosaikia2016solarlike, lehmann2021identifying} In Eqn.
+45,} $P_{\rm spi,sb}$ is proportional to
 
 \begin{equation}
-    P_{\rm spi,sb} \sim B_{\rm p}^{2/3} R_{\rm p}^2 B_*^{4/3} R_*^4 v_{\rm rel} a^{-4} .
+    P_{\rm spi,sb} \propto B_{\rm p}^{2/3} R_{\rm p}^2 B_*^{4/3} R_*^{(n+11) / 3} v_{\rm rel} a^{-(n+11) / 3},
 \end{equation}
 
-$B_{\rm p}$ and $B_*$ are the planetary and stellar field strengths at their poles, respectively; $v_{\rm rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis $a$; and $R_*$ and $R_{\rm p}$ are the stellar and planetary radii, respectively.
-Since the planetary fields are unknown, we ignore them in the calculation.
-We also do not know the stellar field strength at the pole for the vast majority of the stars, so we adopt the surface field strength~(Section~\ref{sec:methods:bfield}) as a proxy.
+\textcolor{red}{ignoring factors of the order of 1.}  $B_{\rm p}$ and $B_*$ are the planetary and stellar field strengths at their poles, respectively; $v_{\rm rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis $a$; and $R_*$ and $R_{\rm p}$ are the stellar and planetary radii, respectively.
+\textcolor{red}{We choose $n=1$ to quantify the strongest possible dependence of the dissipated power on stellar radius and star-planet distance.} Since the planetary fields are unknown, we ignore them in the calculation.
+We also do not know the stellar field strength at the pole for the vast majority of the stars, so we adopt \textcolor{red}{an average value of 15 per cent of the} surface field strength~(see Section~\ref{sec:methods:bfield}) as a proxy.
 
@@
 \begin{equation}
-    P_{\rm spi,sb0} \sim R_{\rm p}^2 R_*^4 B_*^2 v_{\rm rel}    a^{-4} 
+    P_{\rm spi,sb0} \propto R_{\rm p}^2 R_*^{(n+11) / 3} B_*^2 v_{\rm rel}    a^{-(n+11) / 3} 
 \end{equation}
@@
 \begin{equation}
-    P_{\rm spi,aw} \sim B_{\rm p}^{2/3} R_{p}^2  R_*^2  B_*^{1/3}  v_{\rm rel}^2 a^{-2} \rho_*^{1/2} \sin^2 \theta
+    P_{\rm spi,aw} \propto B_{\rm p}^{2/3} R_{p}^2  R_*^2  B_*^{1/3}  v_{\rm rel}^2 a^{-2} \rho_*^{1/2} \sin^2 \theta
 \end{equation}
@@
 
-And fourth, we also consider the case of an unmagnetized planet\textcolor{red}{ where the magnetospheric radius is set equal to the planetary radius}, in which case Eq.~8 in \cite{kavanagh2022radio} reduces to
+And fourth, we also consider the case of an unmagnetized planet, \textcolor{red}{ where the magnetospheric radius is set equal to the planetary radius}, in which case Eq.~8 in \cite{kavanagh2022radio} reduces to
 
 \begin{equation}
-    P_{\rm spi,aw0} \sim R_{\rm p}^2 R_*^4 B_*  v_{\rm rel}^2 a^{-4} \rho_*^{1/2} \sin^2 \theta
+    P_{\rm spi,aw0} \propto R_{\rm p}^2 R_*^4 B_*  v_{\rm rel}^2 a^{-4} \rho_*^{1/2} \sin^2 \theta
 \end{equation}
@@
 \caption{Flaring star-planet interaction.
-$Ro$, $B$, and $v_{\rm rel}$, are derived from literature values (Table~\ref{tab:maintable_lit}).
+$R$o, $B$, and $v_{\rm rel}$, are derived from literature values (Table~\ref{tab:maintable_lit}).
 $P_{\rm spi,xx}$ stands for the power of stretch-and-break ($sb$) and Alfv\'en wing ($aw$) interaction mechanisms, assuming the planet has a magnetic field strength of $1\,$G.
@@
 The relation was derived from 3D~MHD stellar wind simulations of cool main sequence stars (F, G, K, and M), which used observed ZDI maps as boundary condition for the stellar radial magnetic field (for more details on the models see \citealt{chebly2023numerical}).
-However, the stellar magnetic field~($B$, Table~\ref{tab:maintable_der}), derived from the Rossby number (Eq.~\ref{Eq3}, \ref{Eq4}), corresponds to the total, unsigned magnetic field strength on the stellar surface, so that it is necessary to estimate how $B_{\rm r}^{\rm max}$ is related to $B$.
+However, the stellar magnetic field~($B$, Table~\ref{tab:maintable_der}), derived from the Rossby number (Eq.~\ref{Eq3}, \ref{Eq4}), corresponds to the total, unsigned magnetic field strength on the stellar surface so that it is necessary to estimate how $B_{\rm r}^{\rm max}$ is related to $B$.
+
+\textcolor{red}{It is important to note that in \citet{chebly2023numerical} they assume a consistent Poynting flux per unit magnetic field strength for all stars, using the value of the Sun as a reference.
+The size of the Alfvén surface depends strongly on this assumption.
+However, any variation in the value between different stars would lead to deviations from the law proposed in \citet{chebly2023numerical}, resulting in corresponding changes in the dimensions of the Alfvén surface.
+}
 

### 2023-10-05 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     In many star-planet systems discovered so far, the innermost planet orbits within only a few stellar radii.
-In these systems, planets become in-situ probes of the extended stellar magnetic field.
+In these systems, planets \textcolor{red}{could} become in-situ probes of the extended stellar magnetic field.
 Because they disturb the field as they move, they are expected to trigger flares on the stellar surface.
@@
 These forces are typically subsumed under the term star-planet interactions (SPI) that emphasizes that they are bidirectional, affecting both planet, and star.
-Specifically, the effects on the star pose challenges, but also opportunities for our understanding of star-planet systems:
+Specifically, the effects on the star pose challenges, but also opportunities for our understanding of star-planet systems.
 
@@
 \label{sec:intro:global}
-Measuring magnetic star planet-interaction is notoriously difficult in individual systems because a non-detection may not mean an absence of the interaction, but merely a temporary cessation~\citep{shkolnik2005hot, shkolnik2008nature}.
+\textcolor{red}{Even if the instrument's sensitivity is sufficiently high, measuring magnetic star planet-interaction remains notoriously difficult.
+In individual systems,} a non-detection may not mean an absence of the interaction, but merely a temporary cessation~\citep{shkolnik2005hot, shkolnik2008nature}.
 Statistical studies searching for changes in global chromospheric and coronal activity indicators in star-planet systems with close-in planets relative to planet-less stars are inconclusive~\citep{kashyap2008extrasolar,scharf2010possible, shkolnik2013ultraviolet, france2018farultraviolet, viswanath2020statistical, krejcova2012evidence, miller2015comprehensive, poppenhaeger2010coronal}.
@@
 It is, for instance, easier to detect a planet around a magnetically inactive star, because both radial velocity and transit detections will be less affected by stellar variability~\citep{poppenhaeger2011correlation}, but that does not imply that SPI quenches activity.
-Further, tidal interactions can induce global increase in activity~\citep{ilic2022tidal}, which adds a physical ambiguity to the interpretation~(see also Section~\ref{sec:discussion:tidal}).
+Further, tidal interactions can induce \textcolor{red}{a} global increase in activity~\citep{ilic2022tidal}, which adds a physical ambiguity to the interpretation~(see also Section~\ref{sec:discussion:tidal}).
 
@@
 \section*{Acknowledgements}
-
+\textcolor{red}{The authors thank the anonymous referee for their thorough criticism of the manuscript, and numerous valuable suggestions. EI would like to thank Antonino Lanza for helpful advice.}
 This paper includes data collected by the TESS mission, which are publicly available from the Mikulski Archive for Space Telescopes (MAST).

### 2023-10-05 src/scripts/paper_main_table.py
moved the units to the next line

@@ -109,22 +109,24 @@ if __name__ == "__main__":
     
     # define the latex column names
     map_col_names = {
-        "st_rotp":r"$P_{\rm rot}$ [d]",
-        "orbper_d":r"$P_{\rm orb}$ [d]",
-        "st_rad":r"$R_{*}$ [R$_\odot$]",
-        "pl_radj":r"$R_{\rm p}$ [R$_J$]",
-        "a_au":r"$a$ [$10^{-2}$ au]",
+        "st_rotp":r"$P_{\rm rot}$",
+        "orbper_d":r"$P_{\rm orb}$",
+        "st_rad":r"$R_{*}$",
+        "pl_radj":r"$R_{\rm p}$",
+        "a_au":r"$a$",
         "pl_orbeccen":"$e$",
-        "st_lum":"log$_{10} L_{*}$ [L$_\odot$]",
+        "st_lum":"log$_{10} L_{*}$",
         "Ro":r"$R$o",
-        "B_G":r"$B$ [G]",
-        "p_spi_sb_bp1_erg_s":r"log$_{10} P_{\rm spi,sb}$ [erg s$^{-1}$]",
-        "p_spi_aw_bp1_erg_s":r"log$_{10} P_{\rm spi,aw}$ [erg s$^{-1}$]",
-        "p_spi_sb_bp0_erg_s":r"log$_{10} P_{\rm spi,sb0}$ [erg s$^{-1}$]",
-        "p_spi_aw_bp0_erg_s":r"log$_{10} P_{\rm spi,aw0}$ [erg s$^{-1}$]",
-        "v_rel_km_s":r"$v_{\mathrm{rel}}$ [km s$^{-1}$]",
+        "B_G":r"$B$",
+        "p_spi_sb_bp1_erg_s":r"log$_{10} P_{\rm spi,sb}$",
+        "p_spi_aw_bp1_erg_s":r"log$_{10} P_{\rm spi,aw}$",
+        "p_spi_sb_bp0_erg_s":r"log$_{10} P_{\rm spi,sb0}$",
+        "p_spi_aw_bp0_erg_s":r"log$_{10} P_{\rm spi,aw0}$",
+        "v_rel_km_s":r"$v_{\mathrm{rel}}$",
         "mean":r"$p$-value",
         }
+    
+
 
     # read table to texify
     df = pd.read_csv(paths.data / "results.csv")
@@ -197,7 +199,6 @@ if __name__ == "__main__":
     # convert the singles table to latex after converting the values to tex format
[…]

### 2023-10-06 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 We also replace the stellar wind density $\rho_W$ with its proportionality to $\rho_* (R_* / a)^{2}$, and stellar wind magnetic field at the planetary radius $B_W$ with the surface field strength $B_* (R_* / a)^{3}$, which result in the total $R_*^2 a^{-2}$ factor in the above equation.
-Since the stellar wind density at the stellar surface $\rho_*$ is poorly constrained empirically~\citep{vidotto2021evolution}, we follow~\citet{alvarado-gomez2020tuning,kavanagh2021planetinduced}, and fix $\rho_*=2\cdot10^{-10}\rm{cm}^{-3}$.
+Since the stellar wind density at the stellar surface $\rho_*$ is poorly constrained empirically~\citep{vidotto2021evolution}, we follow~\citet{alvarado-gomez2020tuning,kavanagh2021planetinduced}, and fix $\rho_*=2\cdot10^{10}\rm{cm}^{-3}$.
 The angle between the wind magnetic field vector and the velocity vector of the planet $\theta$ is also unknown, so we set $\sin\theta=1$ to obtain an upper limit.
@@
 
-\begin{table}
-\movetableright=-10mm
-\script{paper_aumic_table.py}
-\caption{\textcolor{red}{Powers of star-planet interaction calculated for AU Mic in the four different scenarios introduced in Section~\ref{sec:methods:pspi}.}}
-\input{output/aumic_spi.tex}
-    \label{tab:aumic}
-\end{table}
+% \begin{table}
+% \movetableright=-10mm
+% \script{paper_aumic_table.py}
+% \caption{\textcolor{red}{Powers of star-planet interaction calculated for AU Mic in the four different scenarios introduced in Section~\ref{sec:methods:pspi}.}}
+% \input{output/aumic_spi.tex}
+%     \label{tab:aumic}
+% \end{table}
 

### 2023-10-06 src/scripts/paper_main_table.py
added total observing time to main table

@@ -124,6 +124,7 @@ if __name__ == "__main__":
         "p_spi_aw_bp0_erg_s":r"log$_{10} P_{\rm spi,aw0}$",
         "v_rel_km_s":r"$v_{\mathrm{rel}}$",
         "mean":r"$p$-value",
+        "obstime_d":"obs. time",
         }
     
 
@@ -136,7 +137,7 @@ if __name__ == "__main__":
     df["a_au_err"] = df["a_au_err"] * 100
 
     # select only the columns we want
-    sel = df[["ID","TIC",
+    sel = df[["ID","TIC",'obstime_d',
                 'st_rotp','st_rotp_err','st_rotp_source', 
                 "orbper_d","orbper_d_err", "pl_orbper_bibkey",
                 "pl_orbeccen", "pl_orbeccenerr1", "pl_orbeccenerr2", "pl_orbeccen_bibkey",
@@ -153,7 +154,9 @@ if __name__ == "__main__":
                'p_spi_aw_bp1_erg_s', 'p_spi_aw_bp1_erg_s_high','p_spi_aw_bp1_erg_s_low', 
                "p_spi_sb_bp0_erg_s","p_spi_sb_bp0_erg_s_high","p_spi_sb_bp0_erg_s_low",
                'p_spi_aw_bp0_erg_s', 'p_spi_aw_bp0_erg_s_high','p_spi_aw_bp0_erg_s_low',
-                "mean", "std"]]
+                "mean", "std",]]
+    
+
     
     # select only the single stars
     singles = sel[sel.multiple_star.isnull()]
@@ -172,7 +175,8 @@ if __name__ == "__main__":
 
 
     # rename the column with the source of the rotation period
-    singles = singles.rename(index=str, columns={"st_rotp_source":"st_rotp_bibkey"})
+    singles = singles.rename(index=str, columns={"st_rotp_source":"st_rotp_bibkey",
+                                                  "obstime_d":"obs. time"})
 
 
     # sort table by p-value
@@ -195,6 +199,10 @@ if __name__ == "__main__":
     singles["B_G"] = (singles["B_G"].round(0).values).astype(int)
     singles["B_G_high"] = (singles["B_G_high"].round(0).values).astype(int)
     singles["B_G_low"] = (singles["B_G_low"].round(0).values).astype(int)
+
+    # round obs. time to 1 decimal
[…]

### 2023-10-06 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 In transiting multi-planet systems, the orbital phase refers to the innermost planet, with the transit mid-time at phase zero.
-The full catalog is available online (see Data Availability Statement).
+\textcolor{red}{Qua./Sec.
+is the Quarter or Sector number of the observation in Kepler or TESS, respectively.
+The first and last data point of the flare are denoted $t_s$ and $t_f$.
+The orbital phase of the innermost planet is measured at $t_s$.
+Relative amplitude $a$, and equivalent duration $ED$ (see Eq.~\ref{eq:ED}) are given for each flare.} The full catalog is available online (see Data Availability Statement).
         }

### 2023-10-06 src/scripts/paper_main_table.py
first iteration a/R included

@@ -104,6 +104,7 @@ if __name__ == "__main__":
             ('p_spi_aw_bp0_erg_s', 'p_spi_aw_bp0_erg_s_high','p_spi_aw_bp0_erg_s_low', 'high-low'),
             
             ("v_rel_km_s", 'v_rel_err_km_s', 'err'),
+            ("a_rstar", "a_rstar_err", "err"),
 
             ("mean", "std","err")]
     
@@ -125,6 +126,7 @@ if __name__ == "__main__":
         "v_rel_km_s":r"$v_{\mathrm{rel}}$",
         "mean":r"$p$-value",
         "obstime_d":"obs. time",
+        "a_rstar":r"$a/R_*$",
         }
     
 
@@ -154,7 +156,7 @@ if __name__ == "__main__":
                'p_spi_aw_bp1_erg_s', 'p_spi_aw_bp1_erg_s_high','p_spi_aw_bp1_erg_s_low', 
                "p_spi_sb_bp0_erg_s","p_spi_sb_bp0_erg_s_high","p_spi_sb_bp0_erg_s_low",
                'p_spi_aw_bp0_erg_s', 'p_spi_aw_bp0_erg_s_high','p_spi_aw_bp0_erg_s_low',
-                "mean", "std",]]
+                "mean", "std","a_rstar", "a_rstar_err"]]
     
 
     
@@ -258,7 +260,7 @@ if __name__ == "__main__":
 
     # literature parameters table columns
     lit_cols = ["ID", r"$P_{\rm rot}$", r"$P_{\rm orb}$", "$R_{*}$",
-            r"$R_{\rm p}$", "$a$", "$e$", "log$_{10} L_{*}$", "obs. time"]
+            r"$R_{\rm p}$", "$a$", r"$a/R_*$", "$e$", "log$_{10} L_{*}$", "obs. time"]
 
     # derived parameters table columns
     der_cols = ["ID", r"$R$o", r"$B$", r"$v_{\mathrm{rel}}$", 
@@ -267,7 +269,7 @@ if __name__ == "__main__":
                 r"log$_{10} P_{\rm spi,aw}$", 
                 r"log$_{10} P_{\rm spi,aw0}$", r"$p$-value",]
     
-    lit_unit_row = ['', '[d]', '[d]', r'[R$_\odot$]', r'[R$_J$]', r'[$10^{-2}$ au]',
[…]

### 2023-10-09 src/scripts/paper_main_table.py
added SpT columns to table 1

@@ -139,7 +139,7 @@ if __name__ == "__main__":
     df["a_au_err"] = df["a_au_err"] * 100
 
     # select only the columns we want
-    sel = df[["ID","TIC",'obstime_d',
+    sel = df[["ID","TIC",'obstime_d',"st_spectype","st_spectype_bibkey",
                 'st_rotp','st_rotp_err','st_rotp_source', 
                 "orbper_d","orbper_d_err", "pl_orbper_bibkey",
                 "pl_orbeccen", "pl_orbeccenerr1", "pl_orbeccenerr2", "pl_orbeccen_bibkey",
@@ -205,6 +205,11 @@ if __name__ == "__main__":
     # round obs. time to 1 decimal
     singles["obs. time"] = singles.apply(lambda x: f"{x['obs. time']:.1f}", axis=1)
 
+    # convert st_spectype and st_spectype_bibkey to latex format
+    singles.st_spectype = singles.st_spectype.fillna("")
+    singles.st_spectype_bibkey = singles.st_spectype_bibkey.fillna("")
+    singles["SpT"] = singles.apply(lambda x: x["st_spectype"] + " \citet{" + x["st_spectype_bibkey"] + "}", axis=1)
+
 
     # convert the singles table to latex after converting the values to tex format
     print("Converting each parameter to a latex formatted column.")
@@ -251,6 +256,7 @@ if __name__ == "__main__":
     bibkeys = np.append(bibkeys, fulltable.pl_orbsmax_bibkey.dropna().unique())
     bibkeys = np.append(bibkeys, fulltable.st_lum_bibkey.dropna().unique())
     bibkeys = np.append(bibkeys, fulltable.pl_orbeccen_bibkey.dropna().unique())
+    bibkeys = np.append(bibkeys, fulltable.st_spectype_bibkey.dropna().unique())
 
     # enumerate the bibkeys
     bibkeys = np.unique(bibkeys)
@@ -259,7 +265,7 @@ if __name__ == "__main__":
     bibkeys = {bibkeys[i]:i+1 for i in range(len(bibkeys))}
 
     # literature parameters table columns
-    lit_cols = ["ID", r"$P_{\rm rot}$", r"$P_{\rm orb}$", "$R_{*}$",
[…]

### 2023-10-09 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-\begin{table*}
+\begin{longrotatetable}
 \script{paper_main_table.py}
 \movetableright=-20mm
-
-    \caption{Flaring single star-planet system parameters.}
-\scriptsize
+    % \caption{Flaring single star-planet system parameters. Obs. time is the total observing time with Kepler and TESS.}
+% \footnotesize
     \input{output/table_lit_vals.tex}
@@
     \tablerefs{\input{output/lit_table_bibstring.tex}}
-\end{table*}
+\end{longrotatetable}
 
@@
            X-ray luminosity over bolometric luminosity compared to Rossby number (\textbf{upper panel}), and average surface magnetic field strength (\textbf{lower panel}).
-Both relations follow those of stars not selected for hosting close-in planets, except for GJ 3082, which is underluminous for its Rossby number, and hence also its estimated magnetic field appears too strong for its $L_X/L_{\rm bol}$.
+\textcolor{red}{Blue lines denote the error bars, grey lines point to the IDs of the corresponding stars.} Both relations follow those of stars not selected for hosting close-in planets, except for GJ 3082, which is underluminous for its Rossby number, and hence also its estimated magnetic field appears too strong for its $L_X/L_{\rm bol}$.
         }
@@
 AD test results, assuming the stretch-and-break scenario with an unmagnetized planet.
-While no individual system amounts to a $>3\sigma$ detection, the global trend is intriguing: Systems with low expected power show no deviation from random intrinsic flaring (i.e.
+\textcolor{red}{The vertical and horizontal grey lines denote the uncertainties quoted in Table~\ref{tab:maintable_der}.} While no individual system amounts to a $>3\sigma$ detection, the global trend is intriguing: Systems with low expected power show no deviation from random intrinsic flaring (i.e.
 high $p$-values).

### 2023-10-09 src/scripts/paper_main_table.py
filled in missing ref an lum classes

@@ -258,8 +258,13 @@ if __name__ == "__main__":
     bibkeys = np.append(bibkeys, fulltable.pl_orbeccen_bibkey.dropna().unique())
     bibkeys = np.append(bibkeys, fulltable.st_spectype_bibkey.dropna().unique())
 
+    # split entries in bibkeys that are separated by a comma
+    bibkeys = np.concatenate([b.split(", ") for b in bibkeys])
+
     # enumerate the bibkeys
     bibkeys = np.unique(bibkeys)
+
+    print(bibkeys)
 
     # make a dictionary with the bibkeys and the corresponding index
     bibkeys = {bibkeys[i]:i+1 for i in range(len(bibkeys))}
@@ -342,8 +347,16 @@ if __name__ == "__main__":
 
         # replace the bibkeys with the index in the string table
         for key in bibkeys.keys():
-            replace = "\citet{"+key+"}"
-            string = string.replace(replace, "(" + str(bibkeys[key]) + ")")
+            # if the key has a comma, split a comma and replace both
+           
+                replace = "\citet{"+key+"}"
+                string = string.replace(replace, "(" + str(bibkeys[key]) + ")")
+           
+                replace = "\citet{"+key+","
+                string = string.replace(replace, "(" + str(bibkeys[key]) + ",")
+                
+                replace = key+"}"
+                string = string.replace(replace, str(bibkeys[key]) + ")")
 
         # substitute "--" with any " (*)"" behind it with just "-" using regex
         string = re.sub(r"-- \(.+?\)", "-", string)

### 2023-10-10 src/scripts/stringmanipulation.py
fixed a bug in error handling

@@ -16,7 +16,5 @@ def get_err_string(df,col,errcol, fillna=1, nalt=1):
     df.log10err = df.log10err.fillna(fillna).astype(int) 
 
     df[col] = df.apply(lambda x: np.round(x[col], x.log10err), axis=1)
-    df[errcol] = df.apply(lambda x: np.round(x[errcol], 0), axis=1)
-
 
     return df.apply(lambda x: trail(x, col, errcol, nalt), axis=1)

### 2023-10-10 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 Because they disturb the field as they move, they are expected to trigger flares on the stellar surface.
-These flares are not expected to appear different from intrinsic stellar flares individually.
-However, as we expect planet-induced flares to be associated with the planet's orbital period $P_{\rm orb}$, we can identify their presence from a clustering of flares in phase with the planet's orbital phase.
-We used the excellent phase coverage obtained from Kepler and the Transiting Exoplanet Survey Satellite to find flaring star-planet systems, compile a catalog of all their flares, and measure how much they cluster in orbital phase.
+\textcolor{red}{If and how their energy and morphology differs from intrinsic stellar flares is poorly constrained.} However, as we expect planet-induced flares to be associated with the planet's orbital period $P_{\rm orb}$, we can identify their presence from a clustering of flares in phase with the planet's orbital phase.
+We used the excellent phase coverage from Kepler and the Transiting Exoplanet Survey Satellite to find flaring star-planet systems, compile a catalog of all their flares, and measure how much they cluster in orbital phase.
 
@@
 We quantified the significance of the clustering in each system, and compared it against the theoretically expected power of magnetic interaction that leads to planet-induced flaring.
-Most systems do not show any clustering, in accordance with low expected power.
+Most systems do not show any clustering, consistent with low expected power.
 Those we expect to show planet-induced flaring fall on two branches.
 An inactive one, without any signs of clustering, and a tentative active one, where the clustering becomes more pronounced as the expected power of interaction increases.
-The flares in HIP 67522, a young Hot Jupiter system, are prominently clustered ($p<0.006$), identifying it as the most promising candidate for magnetic star-planet interaction in our sample.
+The flares in HIP 67522 are prominently clustered ($p<0.006$).
+This young Hot Jupiter system is the most promising candidate for magnetic star-planet interaction in our sample.
 
@@
 We do not know how energetic planet-induced flares can be.
-The estimates for dissipated energy~\citep{lanza2018closeby} are in the ballpark of the regime of superflares observed by Kepler and TESS.
+The estimates for dissipated energy~\citep{lanza2018closeby} are in the ballpark of the regime of superflares\textcolor{red}{, with energies released at optical wavelengths $\geq10^{33}\,$erg~\citep{schaefer2000superflares},} observed by Kepler and TESS.
 However, on the one hand, the planet might be triggering flares prematurely, which would be of lower energy~\citep{loyd2023flares}, and end up below our detection threshold.
 On the other hand, the energy need not be dissipated continuously, particularly in the stretch-and-break mechanism proposed by~\citep{lanza2012starplanet}, so an individual flare's energy might be higher.
-We also do not know whether flares triggered by interactions with a companion would have different properties than intrinsic flares.
-We will assume that, since they would be caused by magnetic reconnection triggered by the planet in the stellar corona, they should still have the same physics as intrinsic flares.
-
-Since planet-induced flares might not look any different from intrinsic flares, and we do not know how their energies will be distributed, we require a method to distinguish them without referring to their individual properties.
+We also do not know whether flares triggered by interactions with a companion would \textcolor{red}{unfold faster or slower than} intrinsic flares.
+We will assume that, since they would be caused by magnetic reconnection triggered by the planet in the stellar corona, they should still have the same physics as intrinsic flares\textcolor{red}{.
+They should then approximalety follow the fast-rise-exponential-decay morphology.
+Individual flares can deviate from this template, yet still be classified as flares because flares remain the best explanation for a sudden rise and drop in stellar brightness in most main sequence dwarf stars.
+Many of these deviations are unexplained today~\citep{howard2022no}, so that identifying SPI flares based on morphology is not possible without additional constraints.
+However, if we can statistically identify enough SPI flares, as we attempt in this work, we can infer the differences between intrinsic and SPI events from the two ensembles.}
+
+\textcolor{red}{In other words, s}ince planet-induced flares might not look any different from intrinsic flares, and we do not know how their energies will be distributed, we require a method to distinguish them without referring to their individual properties.
 Instead, we can look at the statistical distribution of flares in time:
@@
 In contrast to global SPI, local SPI effects are easier to tell apart from intrinsic stellar behavior because they are tied to the planet's orbital period.
-Phase-correlated activity, flaring and otherwise, has been searched for in individual systems.
+\textcolor{red}{Searches for star-planet interactions in polarized radio emission, i.e.
+at the wavelengths at which Jupiter-Io interaction is observed (scaled up to the high field strengths of stars) have produced promising, but tentative results.
+In some works, shorter radio wavelenths can still be confused with stellar activity~\citep{pineda2023coherent}.
+In others, the planet has not been detected (yet)~\citep{vedantham2020coherent}, the data do not cover multiple orbital periods to see the signal repeat~\citep{perez-torres2021monitoring}, or both \citep{callingham2021population}.} Phase-correlated activity, flaring and otherwise, has been searched for in individual systems.
 After eight years of monitoring of HD 189733, an active Hot Jupiter host, higher X-ray energy flares seem only marginally clustered in orbital phase than lower energy ones~\citep{pillitteri2022xray}.
@@
 
-\begin{longrotatetable}
+\begin{table*}
+\begin{rotatetable*}
 \script{paper_main_table.py}
-\movetableright=-20mm
-    % \caption{Flaring single star-planet system parameters. Obs. time is the total observing time with Kepler and TESS.}
-% \footnotesize
+% \rotate
+ \caption{Flaring single star-planet system parameters. Obs. time is the total observing time with Kepler and TESS.}
+\movetableright=-40mm
+
+\footnotesize
+
     \input{output/table_lit_vals.tex}
@@
     \tablerefs{\input{output/lit_table_bibstring.tex}}
-\end{longrotatetable}
+\end{rotatetable*}
+\end{table*}
 
@@
 \end{itemize}
+
+% \textcolor{red}{Mid-to-late M dwarfs follow this bimodal distribution }
 

### 2023-10-12 src/scripts/paper_false_positives.py
added figure for the appendix with FPs

@@ -1,0 +1,53 @@
+"""
+Python 3.8 -- UTF-8
+
+Ekaterina Ilin, 2023, MIT License
+
+Script that grabs two light curves of planet hosts that we found with 
+false positives, both physical (SSO) and instrumental (argabrightening),
+makes a two panel figure for the appendix.
+"""
+
+import lightkurve as lk
+import matplotlib.pyplot as plt
+
+import paths
+
+
+if __name__ == '__main__':
+
+
+    # get Kepler light curve of Kepler-235
+    lcskic = lk.search_lightcurve('Kepler-235', author='Kepler', cadence='short', quarter=14)
+    lckic = lcskic[2].download()
+    kictitle = 'Instrumental False Positive: Possible Argabrightening'
+    xlimkic = (1337.45, 1337.55)
+    ylimkic = (5100, 5600)
+
+    # get TESS light curve of TIC 435339847
+    lcstic = lk.search_lightcurve('TIC 435339847', cadence='short', sector=44)
+    lctic = lcstic[0].download()
+    tictitle = 'Physical False Positive: Solar System Object'
+    xlimtic = (2516.6, 2518.3)
+    ylimtic = (None, None)
+
+    # plot the light curves side by side in one figure
+    fig, ax = plt.subplots(1, 2, figsize=(12, 4))
+    lckic.plot(ax=ax[0], linewidth=1)
+    lctic.plot(ax=ax[1], linewidth=1)
+
+    # set the limits of the x and y axes separately for each light curve
+    ax[0].set_xlim(xlimkic)
+    ax[0].set_ylim(ylimkic)
+    ax[1].set_xlim(xlimtic)
+    ax[1].set_ylim(ylimtic)
+    ax[0].set_title(kictitle)
+    ax[1].set_title(tictitle)
+
+    for a in ax:
+        a.legend(frameon=False)
+
+    plt.tight_layout()
+
+    plt.savefig(paths.figures / 'systematics_false_positives.png', dpi=300)
+

### 2023-10-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 We used the excellent phase coverage from Kepler and the Transiting Exoplanet Survey Satellite to find flaring star-planet systems, compile a catalog of all their flares, and measure how much they cluster in orbital phase.
-
 In the 1811 searched systems, we found 25 single stars with three or more flares each.
@@
 
+\keywords{stars: flare, planet–star interactions, stars: magnetic field, stars: low-mass, stars: activity}
 \end{abstract}
@@
 \textcolor{red}{ignoring factors of the order of 1.}  $B_{\rm p}$ and $B_*$ are the planetary and stellar field strengths at their poles, respectively; $v_{\rm rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis $a$; and $R_*$ and $R_{\rm p}$ are the stellar and planetary radii, respectively.
-\textcolor{red}{We choose $n=1$ to quantify the strongest possible dependence of the dissipated power on stellar radius and star-planet distance.} Since the planetary fields are unknown, we ignore them in the calculation.
-We also do not know the stellar field strength at the pole for the vast majority of the stars, so we adopt \textcolor{red}{an average value of 15 per cent of the} surface field strength~(see Section~\ref{sec:methods:bfield}) as a proxy.
+\textcolor{red}{We choose $n=XXXX$, which best reproduces observations of XXXX in~\citet{lanza2012starplanet}.
+Since the planetary fields are unknown, we adopt $B_{\rm p}=1\,$G for simplicity.} We also do not know the stellar field strength at the pole for the vast majority of the stars, so we adopt \textcolor{red}{an average value of 15 per cent of the} surface field strength~(see Section~\ref{sec:methods:bfield}) as a proxy.
 
@@
 
-Third, we estimate the power of SPI generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio},\textcolor{red}{ combining Eqn.~8 for the power of interaction and Eqn.~11 for the magnetopause radius of the planet from\citet{kavanagh2022radio} to arrive at:}
+Third, we estimate the power of SPI generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio}, \textcolor{red}{ combining Eqn.~8 for the power of interaction and Eqn.~11 for the magnetopause radius of the planet from\citet{kavanagh2022radio} to arrive at:}
 
@@
 
-\textcolor{red}{Here, we assume that the magnetopause radius extends to where the magnetic pressures of planet and stellar magnetic wind -- which is dominated by the magnetic field in de sub-Alf\'enic regime -- are equal.
-We also replace the stellar wind density $\rho_W$ with its proportionality to $\rho_* (R_* / a)^{2}$, and stellar wind magnetic field at the planetary radius $B_W$ with the surface field strength $B_* (R_* / a)^{3}$, which result in the total $R_*^2 a^{-2}$ factor in the above equation.
-Since the stellar wind density at the stellar surface $\rho_*$ is poorly constrained empirically~\citep{vidotto2021evolution}, we follow~\citet{alvarado-gomez2020tuning,kavanagh2021planetinduced}, and fix $\rho_*=2\cdot10^{10}\rm{cm}^{-3}$.
+\textcolor{red}{Here, we assume that the magnetopause radius extends to where the magnetic pressures of planet and stellar magnetic wind are equal, and the wind is dominated by the magnetic field in de sub-Alf\'enic regime.
+We approximate the stellar wind density $\rho_W$ with a proportionality to $\rho_* (R_* / a)^{2}$, where $\rho_*$ is the stellar wind density at the base of the corona.
+For the stellar wind magnetic field at the planetary radius $B_W$, we insert $B_* (R_* / a)^{3}$, i.e., the field strength decreasing radially outward from the surface as a dipole.
+This produces an upper bound on the field strength at the planet's distance because more complex fields would drop off more steeply.
+The last two replacements result in the total $R_*^2 a^{-2}$ factor in the above equation.
+Since $\rho_*$ is poorly constrained empirically~\citep{vidotto2021evolution}, we adopt $\rho_*=2\cdot10^{10}\rm{cm}^{-3}$, a value often used for the Sun~(XXXX), and for stellar simulations~\citep{alvarado-gomez2020tuning,kavanagh2021planetinduced}.
 The angle between the wind magnetic field vector and the velocity vector of the planet $\theta$ is also unknown, so we set $\sin\theta=1$ to obtain an upper limit.
@@
 
-Lacking $B_{\rm p}$, and various additional factors that appear in $P_{\rm spi,sb},P_{\rm spi,sb0},P_{\rm spi,aw}$, and  $P_{\rm spi,aw0}$, such as the angle between the relative velocity and magnetic field of the stellar wind~\citep{kavanagh2022radio}, or the force-free parameter~\citep{lanza2012starplanet}, we restrict ourselves to differential estimates, and normalize all $P_{\rm spi}$ to AU Mic.
+% Lacking $B_{\rm p}$, and various additional factors that appear in $P_{\rm spi,sb},P_{\rm spi,sb0},P_{\rm spi,aw}$, and  $P_{\rm spi,aw0}$, such as the angle between the relative velocity and magnetic field of the stellar wind~\citep{kavanagh2022radio}, or the force-free parameter~\citep{lanza2012starplanet}, we restrict ourselves to differential estimates, and normalize all $P_{\rm spi}$ to AU Mic.
 
@@
 
-\textcolor{red}{It is important to note that in \citet{chebly2023numerical} they assume a consistent Poynting flux per unit magnetic field strength for all stars, using the value of the Sun as a reference.
-The size of the Alfvén surface depends strongly on this assumption.
-However, any variation in the value between different stars would lead to deviations from the law proposed in \citet{chebly2023numerical}, resulting in corresponding changes in the dimensions of the Alfvén surface.
-}
+\textcolor{red}{It is important to note that \citet{chebly2023numerical} assume a consistent Poynting flux per unit magnetic field strength for all stars, using the value of the Sun as a reference.
+The size of the Alfv\'en surface depends strongly on this assumption.
+However, any variation in the value between different stars would lead to deviations from the law proposed in \citet{chebly2023numerical}, resulting in corresponding changes in the dimensions of the Alfvén surface.}
 
@@
 \appendix
+\restartappendixnumbering
 

### 2023-10-12 src/scripts/paper_false_positives.py
added a flare light curve panel

@@ -18,6 +18,7 @@ if __name__ == '__main__':
 
 
     # get Kepler light curve of Kepler-235
+    kicname = 'Kepler-235'
     lcskic = lk.search_lightcurve('Kepler-235', author='Kepler', cadence='short', quarter=14)
     lckic = lcskic[2].download()
     kictitle = 'Instrumental False Positive: Possible Argabrightening'
@@ -25,24 +26,38 @@ if __name__ == '__main__':
     ylimkic = (5100, 5600)
 
     # get TESS light curve of TIC 435339847
+    ticname = 'K2-77'
     lcstic = lk.search_lightcurve('TIC 435339847', cadence='short', sector=44)
     lctic = lcstic[0].download()
     tictitle = 'Physical False Positive: Solar System Object'
     xlimtic = (2516.6, 2518.3)
     ylimtic = (None, None)
 
+    # Get flare light curve of GJ 3323
+    flcname = 'GJ 3323'
+    lcs = lk.search_lightcurve('GJ 3323', author='SPOC', exptime=120, sector=32)
+    flc = lcs[0].download()
+    ftitle = 'Flare Light Curve'
+    fxlim = (2175.5, 2176.2)
+    fylim = (13500, 14400)
+
     # plot the light curves side by side in one figure
-    fig, ax = plt.subplots(1, 2, figsize=(12, 4))
-    lckic.plot(ax=ax[0], linewidth=1)
-    lctic.plot(ax=ax[1], linewidth=1)
+    fig, ax = plt.subplots(1, 3, figsize=(15, 4))
+    flc.plot(ax=ax[0], linewidth=1, label=flcname)
+    lckic.plot(ax=ax[1], linewidth=1, label=kicname)
+    lctic.plot(ax=ax[2], linewidth=1, label=ticname)
+
 
     # set the limits of the x and y axes separately for each light curve
-    ax[0].set_xlim(xlimkic)
-    ax[0].set_ylim(ylimkic)
-    ax[1].set_xlim(xlimtic)
-    ax[1].set_ylim(ylimtic)
-    ax[0].set_title(kictitle)
-    ax[1].set_title(tictitle)
+    ax[1].set_xlim(xlimkic)
+    ax[1].set_ylim(ylimkic)
+    ax[2].set_xlim(xlimtic)
+    ax[2].set_ylim(ylimtic)
+    ax[0].set_xlim(fxlim)
+    ax[0].set_ylim(fylim)
[…]

### 2023-10-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
+\section{Flaring finding in Kepler and TESS: False positives}
+
+\begin{figure*}
+    \script{paper_false_positives.py}
+    \includegraphics[width=\linewidth]{figures/systematics_false_positives.png}
+    \caption{\textcolor{red}{False positive flare candidates in Kepler and TESS light curves.
+\textbf{Left panel}: Kepler-235 with a possible argabrightening in the 1-min cadence light curve in  Quarter 14.
+Argabrightenings are few-minutes long reflections of light off debris and onto the detector~\citep{vancleve2016kepler}.
+The reflections affect large parts of the detector, so that this event can be identified as a false positive by its common occurrence across many light curves.
+\textbf{Right panel:} K2-77 with a Solar System Object (SSO) moving across the TESS detector in the 2-min cadence light curve in Sector 44.
+SSOs produce smooth and nearly symmetrical brightenings as they move in and out of the aperture of the star.
+They can also (partially) be identified with known SSOs~\citep{berthier2006skybot, berthier2016prediction}.}}
+\end{figure*}
+
 \end{document}

### 2023-10-12 src/scripts/paper_false_positives.py
different flare, same star, some layouting

@@ -31,15 +31,15 @@ if __name__ == '__main__':
     lctic = lcstic[0].download()
     tictitle = 'Physical False Positive: Solar System Object'
     xlimtic = (2516.6, 2518.3)
-    ylimtic = (None, None)
+    ylimtic = (4500, None)
 
     # Get flare light curve of GJ 3323
     flcname = 'GJ 3323'
-    lcs = lk.search_lightcurve('GJ 3323', author='SPOC', exptime=120, sector=32)
+    lcs = lk.search_lightcurve('GJ 3323', author='SPOC', exptime=120, sector=5)
     flc = lcs[0].download()
     ftitle = 'Flare Light Curve'
-    fxlim = (2175.5, 2176.2)
-    fylim = (13500, 14400)
+    fxlim = (1445.5, 1445.9)
+    fylim = (13200, 15800)
 
     # plot the light curves side by side in one figure
     fig, ax = plt.subplots(1, 3, figsize=(15, 4))

### 2023-10-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     \script{paper_false_positives.py}
+    \begin{centering}
     \includegraphics[width=\linewidth]{figures/systematics_false_positives.png}
-    \caption{\textcolor{red}{False positive flare candidates in Kepler and TESS light curves.
-\textbf{Left panel}: Kepler-235 with a possible argabrightening in the 1-min cadence light curve in  Quarter 14.
+    \caption{\textcolor{red}{True and false positive flare candidates in Kepler and TESS light curves.
+\textbf{Left panel}: A flare in the TESS 2-min cadence light curve of GJ 3323 in Sector 5, with its characteristic fast-rise-exponential-decay shape.
+\textbf{Middle panel}: Kepler-235 with a possible argabrightening in the 1-min cadence light curve in  Quarter 14.
 Argabrightenings are few-minutes long reflections of light off debris and onto the detector~\citep{vancleve2016kepler}.
@@
 They can also (partially) be identified with known SSOs~\citep{berthier2006skybot, berthier2016prediction}.}}
+    \label{fig:flares_and_fps}
+        \end{centering}
 \end{figure*}

### 2023-10-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 
-We vet all flare candidates by eye, and exclude instrumental and physical false positives, such as Solar System Objects passing by the field of view.
+We vet all flare candidates by eye, and exclude instrumental and physical false positives, such as Solar System Objects passing by the field of view~(see Fig.~\ref{fig:flares_and_fps} in the Appendix for an example).
 For each confirmed flare candidate, we calculate the relative amplitude $a$ and equivalent duration $ED$, defined as the integrated flare flux $F_{\rm flare}$ over the duration of the flare, divided by the median flux $F_0$ of the star, integrated over the flare duration~\citep{gershberg1972results}:
@@
 \begin{equation}
-    P_{\rm spi,sb} \propto B_{\rm p}^{2/3} R_{\rm p}^2 B_*^{4/3} R_*^{(n+11) / 3} v_{\rm rel} a^{-(n+11) / 3},
+    P_{\rm spi,sb}=\underbrace{\frac{27\pi \lambda^2(n+1)}{16 \mu_0 n (\lambda^2 + n^2)^{1/3}}}_{\hat{C}} B_{\rm p}^{2/3} R_{\rm p}^2 B_*^{4/3}  v_{\rm rel} \left(\frac{R_*}{a}\right)^{\frac{n+11}{ 3}},
 \end{equation}
 
-\textcolor{red}{ignoring factors of the order of 1.}  $B_{\rm p}$ and $B_*$ are the planetary and stellar field strengths at their poles, respectively; $v_{\rm rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis $a$; and $R_*$ and $R_{\rm p}$ are the stellar and planetary radii, respectively.
-\textcolor{red}{We choose $n=XXXX$, which best reproduces observations of XXXX in~\citet{lanza2012starplanet}.
+\textcolor{red}{where $\mu_0$ is the magnetic permeability of the vacuum, and $n$ and $\lambda$ are dimensionless constants, all of which we subsume under $\hat{C}$ together with other constant factors}.
+$B_{\rm p}$ and $B_*$ are the planetary and stellar field strengths at their poles, respectively; $v_{\rm rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis $a$; and $R_*$ and $R_{\rm p}$ are the stellar and planetary radii, respectively.
+\textcolor{red}{We choose $n=0.25$ ($\lambda^2 = 1.01203$, which best reproduces observations of SPI candidate systems HD~179949, $\tau$ Boo, and HD~189733 in~\citet{lanza2012starplanet} (except for $\upsilon$ And).
 Since the planetary fields are unknown, we adopt $B_{\rm p}=1\,$G for simplicity.} We also do not know the stellar field strength at the pole for the vast majority of the stars, so we adopt \textcolor{red}{an average value of 15 per cent of the} surface field strength~(see Section~\ref{sec:methods:bfield}) as a proxy.
@@
 \begin{equation}
-    P_{\rm spi,sb0} \propto R_{\rm p}^2 R_*^{(n+11) / 3} B_*^2 v_{\rm rel}    a^{-(n+11) / 3} 
+    P_{\rm spi,sb0} =\hat{C} R_{\rm p}^2 B_*^2 v_{\rm rel}  \left(\frac{R_*}{a}\right)^{\frac{n+11}{ 3}}
 \end{equation}
@@
 \begin{equation}
-    P_{\rm spi,aw} \propto B_{\rm p}^{2/3} R_{p}^2  R_*^2  B_*^{1/3}  v_{\rm rel}^2 a^{-2} \rho_*^{1/2} \sin^2 \theta
+    P_{\rm spi,aw} = \pi^{1/2} B_{\rm p}^{2/3} R_{p}^2  R_*^2  B_*^{1/3}  v_{\rm rel}^2 a^{-2} \rho_*^{1/2} \sin^2 \theta
 \end{equation}
@@
 The last two replacements result in the total $R_*^2 a^{-2}$ factor in the above equation.
-Since $\rho_*$ is poorly constrained empirically~\citep{vidotto2021evolution}, we adopt $\rho_*=2\cdot10^{10}\rm{cm}^{-3}$, a value often used for the Sun~(XXXX), and for stellar simulations~\citep{alvarado-gomez2020tuning,kavanagh2021planetinduced}.
+Since $\rho_*$ is poorly constrained empirically~\citep{vidotto2021evolution}, we adopt $\rho_*=2\cdot10^{10}\rm{cm}^{-3}$, a value often used for the Sun~\citep{sokolov2013magnetohydrodynamic}, and for stellar simulations~\citep{alvarado-gomez2020tuning,kavanagh2021planetinduced}.
 The angle between the wind magnetic field vector and the velocity vector of the planet $\theta$ is also unknown, so we set $\sin\theta=1$ to obtain an upper limit.
@@
 On the other branch, no interaction is measured regardless of $P_{\rm spi}$.
-\textcolor{red}{For all powers of SPI, we normalize the values to AU Mic, and give an overview over the normalization values in Table~\ref{tab:aumic}}.
 
@@
 
+\newpage
 \section{Flaring finding in Kepler and TESS: False positives}
-
-\begin{figure*}
+\restartappendixnumbering
+
+\begin{figure*}[ht!]
     \script{paper_false_positives.py}
@@
     \caption{\textcolor{red}{True and false positive flare candidates in Kepler and TESS light curves.
-\textbf{Left panel}: A flare in the TESS 2-min cadence light curve of GJ 3323 in Sector 5, with its characteristic fast-rise-exponential-decay shape.
+\textbf{Left panel}: A flare in the TESS 2-min cadence light curve of GJ 3323 in Sector 5, with its characteristic fast-rise-exponential-decay shape, with additional substructure around the peak.
 \textbf{Middle panel}: Kepler-235 with a possible argabrightening in the 1-min cadence light curve in  Quarter 14.

### 2023-10-23 src/scripts/paper_adtest_vs_value_scatterplots.py
update figure and add appendix plot of A2 stats

@@ -388,10 +388,10 @@ if __name__ == "__main__":
 
     columns = ["p_spi_sb_bp1_erg_s", "p_spi_sb_bp0_erg_s",
               "p_spi_aw_bp1_erg_s", "p_spi_aw_bp0_erg_s"]
-    xlabels = [r"$\sim$ $P_{\rm spi,sb}$ (stretch-and-break interaction with magnetized planet)",
-              r"$\sim$ $P_{\rm spi,sb0}$  (stretch-and-break interaction with unmagnetized planet)",
-              r"$\sim$ $P_{\rm spi,aw}$  (Alfvén wing interaction with magnetized planet)",
-              r"$\sim$ $P_{\rm spi,aw0}$  (Alfvén wing interaction with unmagnetized planet)"]
+    xlabels = [r"$P_{\rm spi,sb}$ [erg/s] (stretch-and-break interaction with magnetized planet)",
+              r"$P_{\rm spi,sb0}$ [erg/s] (stretch-and-break interaction with unmagnetized planet)",
+              r"$P_{\rm spi,aw}$ [erg/s] (Alfvén wing interaction with magnetized planet)",
+              r"$P_{\rm spi,aw0}$ [erg/s] (Alfvén wing interaction with unmagnetized planet)"]
 
     # ------------------------------------------------------------
     # DISTANCE

### 2023-10-23 src/scripts/paper_example_ad_dist.py

@@ -1,0 +1,218 @@
+
+import lightkurve as lk
+import numpy as np
+import matplotlib.pyplot as plt 
+import emcee
+from scipy.stats import scoreatpercentile
+from scipy.interpolate import interp1d
+from scipy.misc import derivative
+import paths
+
+
+def sample_AD_for_custom_distribution(f, nobs, N):
+    """
+    
+    Parameters:
+    ------------
+    f : func
+        expected cum. dist. function (EDF)
+    nobs : int
+        size of data sample
+    N : int
+        number of samples to draw from the expected 
+        distribution of flare phases
+
+    Returns:
+    ---------
+    A2 : N-array
+    """
+
+   
+    def func(x):
+        if (x >= 1) | (x <= 0):
+            return -np.inf
+        else:
+            lp =  np.log(derivative(f, x, dx=np.min([1e-4, (1-x)/3, x/3])))
+            if np.isnan(lp):
+                return -np.inf
+            else:
+                
+                return lp[0]
+        
+
+    # Apply ensemble sampler from emcee
+    
+    # Sample from a 1-D distribution
+    # Sample nobs values from the distribution
+    # because the distrbution of the AD statistic
+    # crucially depends on the sample size
+    ndim, nwalkers = 1, nobs
+    
+    # initial state of the sampler is random values between 0 and 1
+    p0 = np.random.rand(nwalkers, ndim)
+    
+    # Define the sampler with func as the distribution to sample from
+    sampler = emcee.EnsembleSampler(nwalkers, ndim, func)
+    
+    # Run MCMC for N steps
+    sampler.run_mcmc(p0, N, progress=True)
+    
+    # Get the samples
+    samples = sampler.get_chain()
+
+    # replace infs
+    missing = np.where(~np.isfinite(samples))[0]
+    if len(missing) > 0:
+        samples[missing] = f(np.random.rand(*missing.shape))
+    c = samples.reshape((N,nobs))
+ 
+    # calculate the AD statistic for all samples
+    A2 = np.array([anderson_custom(c[i,:], f) for i in range(N)])
+    
+    # make sure that converting shapes and calculating the statistic
+    # preserved the number of samples correctly
+    assert len(A2) == N
+    
+    return A2
+
+
+
+def anderson_custom(x, dist):
+    """
+    Anderson-Darling test for data coming from a particular distribution
[…]

### 2023-10-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 In these systems, planets \textcolor{red}{could} become in-situ probes of the extended stellar magnetic field.
-Because they disturb the field as they move, they are expected to trigger flares on the stellar surface.
-\textcolor{red}{If and how their energy and morphology differs from intrinsic stellar flares is poorly constrained.} However, as we expect planet-induced flares to be associated with the planet's orbital period $P_{\rm orb}$, we can identify their presence from a clustering of flares in phase with the planet's orbital phase.
+Because they disturb the field as they move, they are expected to trigger \textcolor{red}{flares in the corona.
+Potential differences to the energies and morphologies of intrinsic flares are poorly constrained.} However, as we expect planet-induced flares to \textcolor{red}{correlate} with the planet's orbital period, we can identify \textcolor{red}{them} from a clustering of flares in phase with the planet's orbit.
 We used the excellent phase coverage from Kepler and the Transiting Exoplanet Survey Satellite to find flaring star-planet systems, compile a catalog of all their flares, and measure how much they cluster in orbital phase.
@@
 Most systems do not show any clustering, consistent with low expected power.
-Those we expect to show planet-induced flaring fall on two branches.
+Those we expect to show clustering fall on two branches.
 An inactive one, without any signs of clustering, and a tentative active one, where the clustering becomes more pronounced as the expected power of interaction increases.
-The flares in HIP 67522 are prominently clustered ($p<0.006$).
-This young Hot Jupiter system is the most promising candidate for magnetic star-planet interaction in our sample.
+\textcolor{red}{The flares in HIP 67522 are prominently clustered ($p<0.006$).
+This young Hot Jupiter system is the most promising candidate for magnetic star-planet interaction in our sample.}
 
@@
 One of the most surprising results in exoplanet research is the diversity of star-planet system architectures.
-The past two decades revealed that planets can occur in orbits of only a few stellar radii~\citep[e.g., ][]{sanchis-ojeda2014study} that they could almost be considered to live inside the stellar atmosphere.
+The past two decades revealed that planets can occur in orbits of only a few stellar radii~\citep[e.g., ][]{sanchis-ojeda2014study}, so that they could almost be considered to live inside the stellar atmosphere.
 At this proximity, the planet exerts force, tidal and magnetic, both short- and long-term, on its host -- a phenomenon largely unknown to the Solar System.
@@
 Beyond this radius, this plasma is disconnected from the star.
-Alfv\'en waves set off by the planet within the magnetic field they cross cannot propagate back to the star if the wind carries the plasma away faster than these waves can travel.
+Alfv\'en waves set off by \textcolor{red}{a planet that crosses the magnetic field} cannot propagate back to the star if the wind carries the plasma away faster than these waves can travel.
 In the sub-Alfv\'enic regime, the wave can reach the star, and deposit its energy in its atmosphere.
@@
 In the 2010s, a wealth of flare observations from space missions like Kepler~\citep{borucki2010kepler} and K2~\citep{howell2014k2} have been cataloged~\citep{davenport2016kepler, paudel2018k2, ilin2021flares}.
-We now have access to long-term stellar monitoring data available for flare hunting.
 Since 2018, the Transiting Exoplanet Survey Satellite~\citep{ricker2015transiting} is rapidly growing the archive~\citep{gunther2020stellar}.
@@
 We do not know how energetic planet-induced flares can be.
-The estimates for dissipated energy~\citep{lanza2018closeby} are in the ballpark of the regime of superflares\textcolor{red}{, with energies released at optical wavelengths $\geq10^{33}\,$erg~\citep{schaefer2000superflares},} observed by Kepler and TESS.
+The estimates for dissipated energy~\citep{lanza2018closeby} are in the ballpark of the regime of superflares\textcolor{red}{, with energies released at optical wavelengths $\geq10^{33}\,$erg~\citep{schaefer2000superflares}, that can be} observed by Kepler and TESS.
 However, on the one hand, the planet might be triggering flares prematurely, which would be of lower energy~\citep{loyd2023flares}, and end up below our detection threshold.
@@
 We will assume that, since they would be caused by magnetic reconnection triggered by the planet in the stellar corona, they should still have the same physics as intrinsic flares\textcolor{red}{.
-They should then approximalety follow the fast-rise-exponential-decay morphology.
-Individual flares can deviate from this template, yet still be classified as flares because flares remain the best explanation for a sudden rise and drop in stellar brightness in most main sequence dwarf stars.
+They should then approximalety follow the fast-rise-exponential-decay morphology~(see Fig.~\ref{fig:flares_and_fps} for an example).
+Individual intrinsic flares can deviate from this template, yet still be classified as flares because flares remain the best explanation for a sudden rise and drop in stellar brightness in most main sequence dwarf stars.
 Many of these deviations are unexplained today~\citep{howard2022no}, so that identifying SPI flares based on morphology is not possible without additional constraints.
@@
 In contrast to global SPI, local SPI effects are easier to tell apart from intrinsic stellar behavior because they are tied to the planet's orbital period.
-\textcolor{red}{Searches for star-planet interactions in polarized radio emission, i.e.
-at the wavelengths at which Jupiter-Io interaction is observed (scaled up to the high field strengths of stars) have produced promising, but tentative results.
-In some works, shorter radio wavelenths can still be confused with stellar activity~\citep{pineda2023coherent}.
-In others, the planet has not been detected (yet)~\citep{vedantham2020coherent}, the data do not cover multiple orbital periods to see the signal repeat~\citep{perez-torres2021monitoring}, or both \citep{callingham2021population}.} Phase-correlated activity, flaring and otherwise, has been searched for in individual systems.
+\textcolor{red}{Searches for an orbital modulation of polarized radio emission have produced promising, but tentative results.
+Close-in star-planet systems are expected to interact similarly to the Jupiter-Io system~\citep{bigg1964influence}, albeit scaled up to the high field strengths of stars~\citep{turnpenney2018exoplanetinduced}.
+In some detections, the planet has not been found (yet)~\citep{vedantham2020coherent}, or the data do not cover multiple orbital periods to see the signal repeat~\citep{perez-torres2021monitoring, pineda2023coherent}, or both \citep{callingham2021population}.} Phase-correlated activity, flaring and otherwise, has been searched for in individual systems.
 After eight years of monitoring of HD 189733, an active Hot Jupiter host, higher X-ray energy flares seem only marginally clustered in orbital phase than lower energy ones~\citep{pillitteri2022xray}.
@@
 We searched a total of 1811 systems and over 7200 light curves from both missions for flares.
-To calculate the clustering of in orbital phase, we further required the orbital periods of each system~(Section~\ref{sec:data:orbitalperiod}).
+To calculate the clustering of \textcolor{red}{flares} in orbital phase, we further required the orbital periods of each system~(Section~\ref{sec:data:orbitalperiod}).
 We then estimated the theoretically expected power of interaction for each system with at least three flares.
@@
 
-The Transiting Exoplanet Survey Satellite~\citep[TESS,][]{ricker2015transiting} is an all-sky mission that began operations in 2018, completed two sky scans until summer 2022.
+The Transiting Exoplanet Survey Satellite~\citep[TESS,][]{ricker2015transiting} is an all-sky mission that began operations in 2018, \textcolor{red}{and has} completed two sky scans in summer 2022.
 It is observing at the time of writing, collecting nearly continuous photometric time series in the $600-1000\,$nm band for $\sim 27\,$d in each observing Sector.
@@
 Eventually, we apply two Savitzky-Golay~\citep{savitzky1964smoothing} filters in sequence, with window sizes of 6h and 3h each.
-At this stage, we mask all data points above a $2.5 \sigma$ (or $1.5 \sigma$ for stars like AU Mic or Proxima Cen, which are very active or have very low noise levels, or both) threshold as flare candidates to prevent the filter from ironing out the flares.
+At this stage, we mask all data points above a $2.5 \sigma$ \textcolor{red}{threshold} (or $1.5 \sigma$ for stars like AU Mic or Proxima Cen, which are very active or have very low noise levels, or both) as flare candidates to prevent the filter from ironing out the flares.
 As a final step, we fit exponential functions to the edges of the light curves, if there are data points that deviate more than one standard deviation from the median value, while keeping the flare candidates masked.
@@
 In the de-trended light curves, we search for flares as series of at least three consecutive data points $3\sigma$ above the noise level using the \texttt{AltaiPony} method \texttt{find\_flares}.
-We estimate the noise level as the standard deviation in a rolling window of two hours, while masking deviation above $2.5\sigma$ (or $1.5\sigma$  for stars like AU Mic and Proxima Cen).
+We estimate the noise level as the standard deviation in a rolling window of two hours, while masking deviations above $2.5\sigma$ (or $1.5\sigma$  for stars like AU Mic and Proxima Cen).
 To capture the exponential tail of the flare, we use the \texttt{addtail} flag in the \texttt{find\_flares} method to continue adding data points to the end of the flare as long as they are $2\sigma$ above the noise threshold.
@@
 We vet all flare candidates by eye, and exclude instrumental and physical false positives, such as Solar System Objects passing by the field of view~(see Fig.~\ref{fig:flares_and_fps} in the Appendix for an example).
-For each confirmed flare candidate, we calculate the relative amplitude $a$ and equivalent duration $ED$, defined as the integrated flare flux $F_{\rm flare}$ over the duration of the flare, divided by the median flux $F_0$ of the star, integrated over the flare duration~\citep{gershberg1972results}:
+For each confirmed flare candidate, we calculate the relative amplitude $a$ and equivalent duration $ED$, defined as the flare flux $F_{\rm flare}$ over the duration of the flare, divided by the median flux $F_0$ of the star, integrated over the flare duration~\citep{gershberg1972results}:
 \begin{equation}
@@
 \end{equation}
-Equivalent duration is equal to the time during which the non-flaring star releases as much energy as the flare.
+\textcolor{red}{In other words, equivalent duration is }the time during which the non-flaring star releases as much energy as the flare.
 
@@
 With the phase coverage and base flare rate combined, we can tell how many flares we would expect to see in any given phase bin if flares were randomly distributed.
-We then aggregate this number of expected flares per time bin into one expected distribution by summing over all available light curves.
+We then aggregate this number of expected flares per \textcolor{red}{orbital phase} bin into one expected distribution \textcolor{red}{(blue curves in Figs.~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv})} by summing over all available light curves.
 As a last step, we compare the expected distribution to the observed one using an Anderson-Darling test.
-\textcolor{red}{For this, we sample 10000 times from the expected distribution the same number of flares we observe in each system, e.g., for HIP 67522, we sample 12 flares distributed according to the blue curve in Fig.~\ref{fig:cumdist_transiting}.
+\textcolor{red}{For this, we sample 10000 times from the expected distribution the same number of flares as we observe in each system.
+For instance, for HIP 67522, we sample 12 flares distributed according to its blue curve in Fig.~\ref{fig:cumdist_transiting}.
 For each of the 10000 samples, we compute the Anderson-Darling statistic $A^2$, which yields a distribution of $A^2$ values.
@@
            X-ray luminosity over bolometric luminosity compared to Rossby number (\textbf{upper panel}), and average surface magnetic field strength (\textbf{lower panel}).
-\textcolor{red}{Blue lines denote the error bars, grey lines point to the IDs of the corresponding stars.} Both relations follow those of stars not selected for hosting close-in planets, except for GJ 3082, which is underluminous for its Rossby number, and hence also its estimated magnetic field appears too strong for its $L_X/L_{\rm bol}$.
+\textcolor{red}{Blue lines denote the error bars, black lines point to the IDs of the corresponding stars.} Both relations follow those of stars not selected for hosting close-in planets, except for GJ 3082, which is underluminous for its Rossby number, and hence also its estimated magnetic field appears too strong for its $L_X/L_{\rm bol}$.
         }
@@
 First, we estimate the power of SPI generated by the stretch-and-break mechanism using the scaling relations in~\cite{lanza2012starplanet}.
-\textcolor{red}{We adopt their Eqn.
-45 for non-linear and axisymmetric magnetic fields, because the non-linear formulation does not assume a constant force-free parameter, and because only axisymmetric fields are able to produce modulation of flaring activity in phase with the planetary orbit.
-We note that the axisymmetry of stellar magnetic fields varies across stars~\citep[e.g.,][]{donati2009magnetic, donati2008largescale, morin2008largescale, morin2010largescale}, and also with the stellar activity cycle of individual stars~\citep[e.g.,][]{borosaikia2016solarlike, lehmann2021identifying} In Eqn.
-45,} $P_{\rm spi,sb}$ is proportional to
+\textcolor{red}{We adopt their Eqn.~45 for non-linear and axisymmetric magnetic fields, because the non-linear formulation does not assume a constant force-free parameter, and because only axisymmetric fields can produce modulation of flaring activity in phase with the planetary orbit.
+We note that the axisymmetry of stellar magnetic fields varies across stars~\citep[e.g.,][]{donati2009magnetic, donati2008largescale, morin2008largescale, morin2010largescale}, and also with the stellar activity cycle of individual stars~\citep[e.g.,][]{borosaikia2016solarlike, lehmann2021identifying}.
+In Eqn.
+45, the power of SPI, $P_{\rm spi,sb}$, is}
 
 \begin{equation}
-    P_{\rm spi,sb}=\underbrace{\frac{27\pi \lambda^2(n+1)}{16 \mu_0 n (\lambda^2 + n^2)^{1/3}}}_{\hat{C}} B_{\rm p}^{2/3} R_{\rm p}^2 B_*^{4/3}  v_{\rm rel} \left(\frac{R_*}{a}\right)^{\frac{n+11}{ 3}},
+\textcolor{red}{      P_{\rm spi,sb}=\underbrace{\frac{27\pi \lambda^2(n+1)}{16 \mu_0 n (\lambda^2 + n^2)^{1/3}}}_{\hat{C}} B_{\rm p}^{2/3} R_{\rm p}^2 B_*^{4/3}  v_{\rm rel} \left(\frac{R_*}{a}\right)^{\frac{n+11}{ 3}},}
 \end{equation}
 
-\textcolor{red}{where $\mu_0$ is the magnetic permeability of the vacuum, and $n$ and $\lambda$ are dimensionless constants, all of which we subsume under $\hat{C}$ together with other constant factors}.
+\textcolor{red}{where $\mu_0$ is the magnetic permeability of the vacuum, and $n$ and $\lambda$ are dimensionless constants, all of which we subsume under $\hat{C}$, together with other constant factors}.
 $B_{\rm p}$ and $B_*$ are the planetary and stellar field strengths at their poles, respectively; $v_{\rm rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis $a$; and $R_*$ and $R_{\rm p}$ are the stellar and planetary radii, respectively.
-\textcolor{red}{We choose $n=0.25$ ($\lambda^2 = 1.01203$, which best reproduces observations of SPI candidate systems HD~179949, $\tau$ Boo, and HD~189733 in~\citet{lanza2012starplanet} (except for $\upsilon$ And).
-Since the planetary fields are unknown, we adopt $B_{\rm p}=1\,$G for simplicity.} We also do not know the stellar field strength at the pole for the vast majority of the stars, so we adopt \textcolor{red}{an average value of 15 per cent of the} surface field strength~(see Section~\ref{sec:methods:bfield}) as a proxy.
+\textcolor{red}{We choose $n=0.25$ ($\lambda^2 = 1.01203$), which best reproduces observations of SPI candidate systems HD~179949, $\tau$ Boo, and HD~189733 in~\citet{lanza2012starplanet} (except for $\upsilon$ And).
+Since the planetary fields are unknown, we adopt $B_{\rm p}=1\,$G for simplicity.} We also do not know the stellar field strength at the pole for the vast majority of the stars, so we adopt \textcolor{red}{an average value of 15 per cent of the} surface field strength~(see Sections~\ref{sec:methods:bfield} and~\ref{sec:discussion:as}) as a proxy.
 
@@
 \begin{equation}
-    P_{\rm spi,sb0} =\hat{C} R_{\rm p}^2 B_*^2 v_{\rm rel}  \left(\frac{R_*}{a}\right)^{\frac{n+11}{ 3}}
+\textcolor{red}{      P_{\rm spi,sb0} =\hat{C} R_{\rm p}^2 B_*^2 v_{\rm rel}  \left(\frac{R_*}{a}\right)^{\frac{n+11}{ 3}}}
 \end{equation}
 
-Third, we estimate the power of SPI generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio}, \textcolor{red}{ combining Eqn.~8 for the power of interaction and Eqn.~11 for the magnetopause radius of the planet from\citet{kavanagh2022radio} to arrive at:}
+Third, we estimate the power of SPI generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio}, \textcolor{red}{ combining Eqn.~8 for the power of interaction and Eqn.~11 for the magnetopause radius of the planet from~\citet{kavanagh2022radio} to arrive at:}
 
 \begin{equation}
-    P_{\rm spi,aw} = \pi^{1/2} B_{\rm p}^{2/3} R_{p}^2  R_*^2  B_*^{1/3}  v_{\rm rel}^2 a^{-2} \rho_*^{1/2} \sin^2 \theta
+\textcolor{red}{    P_{\rm spi,aw} = \frac{\pi^{1/2}}{2^{2/3}} B_{\rm p}^{2/3} R_{p}^2  R_*^2  B_*^{1/3}  v_{\rm rel}^2 a^{-2} \rho_*^{1/2} \sin^2 \theta}
 \end{equation}
 
-\textcolor{red}{Here, we assume that the magnetopause radius extends to where the magnetic pressures of planet and stellar magnetic wind are equal, and the wind is dominated by the magnetic field in de sub-Alf\'enic regime.
+\textcolor{red}{Here, we assume that the magnetopause radius extends to where the magnetic pressures of planet and stellar magnetic wind are equal, and that the wind is dominated by the magnetic field in the sub-Alf\'enic regime.
 We approximate the stellar wind density $\rho_W$ with a proportionality to $\rho_* (R_* / a)^{2}$, where $\rho_*$ is the stellar wind density at the base of the corona.
-For the stellar wind magnetic field at the planetary radius $B_W$, we insert $B_* (R_* / a)^{3}$, i.e., the field strength decreasing radially outward from the surface as a dipole.
+For the stellar wind magnetic field at the planetary radius $B_W$, we insert $B_* (R_* / a)^{3}$, i.e., we assume that the field strength decreases radially outward from the surface as a dipole.
 This produces an upper bound on the field strength at the planet's distance because more complex fields would drop off more steeply.
 The last two replacements result in the total $R_*^2 a^{-2}$ factor in the above equation.
-Since $\rho_*$ is poorly constrained empirically~\citep{vidotto2021evolution}, we adopt $\rho_*=2\cdot10^{10}\rm{cm}^{-3}$, a value often used for the Sun~\citep{sokolov2013magnetohydrodynamic}, and for stellar simulations~\citep{alvarado-gomez2020tuning,kavanagh2021planetinduced}.
+Since $\rho_*$ is poorly constrained empirically~\citep{vidotto2021evolution}, we adopt $\rho_*=2\cdot10^{10}\rm{cm}^{-3}$, a value often used for the Sun~\citep{sokolov_magnetohydrodynamic_2013}, and for stellar simulations~\citep{alvarado-gomez2020tuning,kavanagh2021planetinduced}.
+The dependence on $\rho_*$ is stronger than that on $B_*$, so it may dominate the magnetic field dependence.
+However, it is also weaker than that on any other parameter in the scaling law.
 The angle between the wind magnetic field vector and the velocity vector of the planet $\theta$ is also unknown, so we set $\sin\theta=1$ to obtain an upper limit.
-In reality, $\theta$ will vary both between systems, and over time in any individual system.
-Omitting $\rho_*$ assumes that all stellar wind densities are the same in our sample, which is not true in reality.
-The dependence on $\rho_*$ is stronger than that on $B_*$, but weaker than on every other parameter, so it may dominate the magnetic field dependence.}
+In reality, $\theta$ will vary both between systems, and over time in any individual system.}
 
@@
 \begin{equation}
-    P_{\rm spi,aw0} \propto R_{\rm p}^2 R_*^4 B_*  v_{\rm rel}^2 a^{-4} \rho_*^{1/2} \sin^2 \theta
+\textcolor{red}{    P_{\rm spi,aw0} = \pi^{1/2} R_{\rm p}^2 R_*^4 B_*  v_{\rm rel}^2 a^{-4} \rho_*^{1/2} \sin^2 \theta}
 \end{equation}
@@
 Our goal was to measure magnetic SPI as the statistical clustering of flares in phase with the innermost planet's orbit.
-We searched all star-planet systems that were observed with Kepler and TESS at 1 or 2 min cadence, respectively, for flares.
+We searched for flares in all star-planet systems that were observed with Kepler and TESS at 1 or 2 min cadence, respectively.
 For the star-planet systems in the resulting flare catalog~(Section~\ref{sec:results:catalog}), we confirmed that the orbital phase could be known well enough for the entire observing baseline of the system~(Section~\ref{sec:results:coherence}).
@@
 In Table~\ref{tab:flares}, we list the flares and their characteristics.
-To identify each event, we provide the name of the system in which the flare was found, along with its TIC, whether it was observed with Kepler or TESS, and during what Quarter or Sector, respectively.
+To identify each event, we provide the name of the system in which the flare was found, its TIC, whether it was observed with Kepler or TESS, and during what Quarter or Sector, respectively.
 For each flare, we also give the start and finish time, relative amplitude $a$ and equivalent duration $ED$~(Eq.~\ref{eq:ED}).
@@
 is the Quarter or Sector number of the observation in Kepler or TESS, respectively.
-The first and last data point of the flare are denoted $t_s$ and $t_f$.
+The first and last data points of a flare are denoted $t_s$ and $t_f$.
 The orbital phase of the innermost planet is measured at $t_s$.
-Relative amplitude $a$, and equivalent duration $ED$ (see Eq.~\ref{eq:ED}) are given for each flare.} The full catalog is available online (see Data Availability Statement).
+We also give relative amplitude $a$, and equivalent duration $ED$ (see Eq.~\ref{eq:ED}) for each flare.} The full catalog is available online (see Data Availability Statement).
         }
@@
 If the orbital period is well-known, the resulting ratio $\Delta T/\tau$ should be $\ll 1$.
-\textcolor{red}{Here, we are not interested in the absolute orbital phase, but only in the relative one.
+\textcolor{red}{Here, we are not interested in the absolute orbital phase.
+We are only interested in how much uncertainty on the orbital phases of flares accumulates over the entire observing time after the first flare.
 Therefore, we can ignore that the uncertainty on phase zero at transit midtime increases with the time passed since the transit midtime was measured.
-For non-transiting systems, this time can amount to several years, and the midtime is unconstrained by the time of the observation with Kepler or TESS.
+For non-transiting systems, this time can amount to several years, so the midtime becomes unconstrained by the time of the observation with Kepler or TESS.
 For transiting systems, the midtime is usually very well known.
-So in the following, we set phsae zero to an arbitrary time in non-transiting systems, and to the reported transit midtime for the rest.} The bottom panel in Figure~\ref{fig:coherence_hist} shows a histogram of $\Delta T/\tau$ in our sample.
+So in the following, we set phsae zero to an arbitrary time in non-transiting systems, and to the reported transit midtime for the rest.}
+
+The bottom panel in Figure~\ref{fig:coherence_hist} shows a histogram of $\Delta T/\tau$ in our sample.
 The orbital period is known sufficiently well for our analysis in most cases with ratios $<0.02$, that is, the orbital phase of the last flare is at most $2\%$ off, compared to the first.
-The three cases where the ratio is highest with $0.05$, $0.12$, $0.24$ deviation are TAP 26, GJ 3082, and GJ 674, respectively.
+The three cases where the ratio is highest with \textcolor{red}{$\Delta T/\tau=$}$0.05$, $0.12$, $0.24$ are TAP 26, GJ 3082, and GJ 674, respectively.
 We keep these systems in our sample, but caution that the measured absence of flaring SPI might be partly due to the uncertain orbital period of the planet in these cases.
@@
 Figures~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv} show the flare phase distributions along with the corresponding expected distributions for transiting and non-transiting systems, respectively.
-The expected distributions usually deviate from a straight line because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different flare rates in each light curve, which arise due to varying noise levels between individual Quarter/Sectors, and Kepler and TESS.
+The expected distributions usually deviate from a straight line because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different flare rates in each light curve, which arise due to varying noise levels between individual Quarter/Sectors, and \textcolor{red}{between the two instruments}.
 
@@
 However, overall, the significance of the deviation increases with higher expected power $P_{\rm spi}$ of interaction, introduced in Section~\ref{sec:methods:pspi}.
-Table~\ref{tab:maintable_der} also lists the derived parameters required in these scaling laws, i.e., Rossby number $R$o, surface-average magnetic field strength $B$, and relative velocity between the planet and a co-rotating magnetic field $v_{\rm rel}$.
+Table~\ref{tab:maintable_der} also lists the derived parameters required in these scaling laws, i.e., Rossby number $R$o, surface-average magnetic field strength $B$, and relative velocity \textcolor{red}{$v_{\rm rel}$} between the planet and a co-rotating \textcolor{red}{stellar} magnetic field .
 
@@
 $P_{\rm spi,xx0}$ is the same, but assuming an unmagnetized planet.
-All powers are normalized to AU Mic.
 The $p$-value of the Anderson-Darling test is lower when the system shows a stronger clustering of flares in orbital phase.}
@@
 \textcolor{red}{The vertical and horizontal grey lines denote the uncertainties quoted in Table~\ref{tab:maintable_der}.} While no individual system amounts to a $>3\sigma$ detection, the global trend is intriguing: Systems with low expected power show no deviation from random intrinsic flaring (i.e.
-high $p$-values).
+high $p$-values \textcolor{red}{in the left half of the Figure}).
 In contrast, systems with high expected power show two branches.
@@
 We therefore excluded some systems due to documented contamination from nearby (bound or co-moving) companions~(Section~\ref{sec:results:individualstars:excluded}).
-One exception to this rule is Kepler-411, a binary system for which the flare contributions from each component could be separated, but which was excluded for other reasons.
+One exception to this rule is Kepler-411, a binary system for which the flare contributions from each component could be separated, but which was excluded \textcolor{red}{due to its flares' low $ED$}.
 We also dropped GJ 1061 from the final sample because its rotation period was unconstrained.
@@
 
-The bulk of the systems in our sample are neither expected to show high power of magnetic SPI, nor do they show any deviation from intrinsic stellar flaring.
+The bulk of the systems in our sample are neither expected to show high power of magnetic SPI, nor do they show any.
 In Section~\ref{sec:prominensystems}, in the subsample of stars with high expected power, of the order of AU Mic's and above, we first take a closer look at those that seem to follow an increase in measured flaring SPI with increasing expected power $P_{\rm spi}$, that is AU Mic itself, K2-25, TOI-540, and HIP 67522.
@@
 Depending on the phase of the activity cycle, Proxima Cen d may be in the sub-Alfv\'enic regime during Proxima Cen's activity maximum~\citep{alvarado-gomez2020earthlike}.
-However, the orbital period of the tentative planet is so uncertain at this point that its coherence time~(Section~\ref{sec:results:coherence}) is shorter than the roughly 2yr observing baseline of Proxima Cen, preventing us from accurately measuring the flare phases.
+However, the orbital period of the tentative planet is so uncertain at this point that its coherence time~(Section~\ref{sec:results:coherence}) is shorter than the roughly $2\,$yr observing baseline of Proxima Cen, preventing us from accurately measuring the flare phases.
 
@@
 
-In the scenario wherein the stretch-and-break mechanism drives the interaction, the three systems cluster together most distinctly~(Figure~\ref{fig:adtest_bp} and top panel in Figure~\ref{fig:adtest_bp_rest}).
-In the Alfv\'en wing scenario~(middle and bottom panels in Figure~\ref{fig:adtest_bp_rest}), the distinction is less clear.
+\textcolor{red}{In the stretch-and-break scenario, and the Alfv\'en wing scenario with a magnetized planet, the three systems cluster together distinctly~(Figure~\ref{fig:adtest_bp}, and top and middle panel in Figure~\ref{fig:adtest_bp_rest}).
+In the Alfv\'en wing scenario with an unmagnetized planet~(bottom panel in Figure~\ref{fig:adtest_bp_rest}),} the distinction is less clear.
 In both cases, the low level (or possible absence) of interaction could be due to the Alfv\'en radius being within the planetary orbit.
@@
 All else equal, a planet is more likely sub-Alfv\'enic if the stellar magnetic field is strong~(see Section~\ref{sec:discussion:as} to see that the three planets are likely sub-Alfv\'enic).
-Another explanation is the possible intermittency, or 'on-off nature' of the interaction~\citep{shkolnik2008nature}, which may be at play here, but particularly in cases where the expected power is very strong, such as in the comparison between HIP 67522 and TAP 26 that we address in the following two paragraphs.
+Another explanation is the possible intermittency, or 'on-off nature' of the interaction~\citep{shkolnik2008nature}, which may be at play, particularly in cases where the expected power is very strong, such as in the comparison between HIP 67522 and TAP 26 that we address in the following.
 
@@
 \label{sec:results:individualstars:koi12}
-KOI-12, also known as Kepler-448, is a two-planet system with an eccentric outer planet KOI-12 c, and an inner Warm Jupiter planet KOI-12 b in a $17.8\,$d orbit~\citep{masuda2017eccentric}.
+, also known as Kepler-448, is a two-planet system with an eccentric outer planet KOI-12 c, and an inner Warm Jupiter KOI-12 b in a $17.8\,$d orbit~\citep{masuda2017eccentric}.
 With respect to rotation rate, stellar and planetary radius, the KOI-12 system is similar to HIP~67522 and TAP~26 (although for the those young stars the radii are large because the stars are still contracting onto the main sequence).
@@
 The observed branching might also be explained by intermittent SPI~(Section~\ref{sec:discussion:intermittency}), but its possible causes are not well known.
-As an easier to test alternative explanation, we highlight the important influence of viewing geometry on the observability of flaring SPI, which might explain the absence of magnetic SPI in TAP~26~(Section~\ref{sec:discussion:viewing}).
+As an alternative explanation, we highlight the important influence of viewing geometry on the observability of flaring SPI, which might explain the absence of magnetic SPI in TAP~26~(Section~\ref{sec:discussion:viewing}).
 
@@
 Magnetic SPI can only take place if the planet spends at least a part of its orbit in the sub-Alfv\'enic regime~(see Section~\ref{sec:intro:mspi}).
-We estimated the average Alfv\'en surface size ($\overline{AS}_{R}$) using the power law established by \citet{chebly2023numerical}:
+We estimated the average Alfv\'en surface size ($\overline{AS}_{\rm R}$) using the power law established by \citet{chebly2023numerical}:
 
@@
 The size of the Alfv\'en surface depends strongly on this assumption.
-However, any variation in the value between different stars would lead to deviations from the law proposed in \citet{chebly2023numerical}, resulting in corresponding changes in the dimensions of the Alfvén surface.}
+As such, any variation in the value between different stars would lead to deviations from the law proposed in \citet{chebly2023numerical}, and change the dimensions of the Alfv\'en surface.
+Nevertheless, while the consistency in the Poynting flux appears as a very strong assumption, the numerical results of \citet{chebly2023numerical} fare relatively well when compared with our current observational knowledge of stellar winds in cool main-sequence stars~\citep{wood2021new}.
+For this reason, we consider that Eq.~\ref{AS_estimation} should be robust enough for our purposes.}
 
@@
 
-The second assumption is that $B_{\rm V}$ will match the maximum radial magnetic field in a ZDI reconstruction.
-Since $B_{\rm V}$ is integrated over the visible surface of the star, this assumption will only hold if for an observing phase containing the strongest large-scale radial magnetic region, the effect from cancellation of opposite polarities is small.
-At all other rotational phases, we expect $B_{\rm V} < B_{\rm r}^{\rm max}$.
-Therefore, by assuming $B_{\rm V} = B_{\rm r}^{\rm max}$ we are effectively taking an upper limit on the longitudinal magnetic field strength, which will be translated\footnote[3]{Naturally this will also depend on how good our $15$\% match between $B$ and $B_{\rm V}$ is to reality.} in our estimated values of $\overline{AS}_{R}$.
-
-We show the difference between star-planet distance and $\overline{AS}_{R}$ in Fig.~\ref{fig:as}.
+The second assumption is that $B_{\rm V}$ will match the maximum radial magnetic field \textcolor{red}{$B_{\rm r}^{\rm max}$} in a ZDI reconstruction.
+\textcolor{red}{$B_{\rm V}$ is integrated over the visible surface of the star.
+Only if the effect from cancellation of opposite polarities is small for an observing phase that contains the strongest large-scale radial magnetic region, will this assumption hold.} At all other rotational phases, we expect $B_{\rm V} < B_{\rm r}^{\rm max}$.
+Therefore, by assuming $B_{\rm V} = B_{\rm r}^{\rm max}$ we are effectively taking an upper limit on the longitudinal magnetic field strength, which will be translated\footnote[3]{Naturally this will also depend on how good our $15$\% match between $B$ and $B_{\rm V}$ is to reality.} in our estimated values of $\overline{AS}_{\rm R}$.
+
+We show the difference between star-planet distance and $\overline{AS}_{\rm R}$ in Fig.~\ref{fig:as}.
 HIP 67522 b falls most deeply into the sub-Alfv\'enic regime, consistent with the strongest signal of magnetic SPI in our sample.
@@
 From this follows that the absence of interaction is not caused by the planets orbiting outside the Alfv\'en radius.
-Location inside $\overline{AS}_{R}$ is a required but not sufficient condition for magnetic SPI, as we will see in the following subsections.
+Location inside $\overline{AS}_{\rm R}$ is a required but not sufficient condition for magnetic SPI, as we will see in the following subsections.
 %\textcolor{red}{JDAG: Thats a good point.
@@
 
-Most of our systems are transiting, and for those we can expect this scenario to be a minor problem unless the latitude of the footpoint is very high.
-Of the systems that have high expected power but do not show any excess flaring, only TAP 26 b is a planet detected in radial velocity, and has a relatively high orbital inclination of about $55\pm10$ deg inferred from photometry, spectroscopy, and Zeeman Doppler measurements in~\citet{yu2017hot}.
+Most of our systems are transiting\textcolor{red}{.
+F}or those we can expect this scenario to be a minor problem unless the latitude of the footpoint is very high.
+Of the systems that have high expected power but do not show any excess flaring, only TAP 26 \textcolor{red}{has }a planet detected in radial velocity \textcolor{red}{with} a relatively high orbital inclination of about $55\pm10$ deg inferred from photometry, spectroscopy, and Zeeman Doppler measurements in~\citet{yu2017hot}.
 Their ZD map reveals magnetic field concentrations close to the rotational pole, and the brightness maps also show a dark spot in the same location.
@@
 
-If the observed effects are due to the tidally interacting stellar companion, planetary companions should do the same, albeit at a smaller magnitude.
+If \textcolor{red}{it is the stellar companion that tidally causes} the observed effects, planetary companions should do the same, albeit at a smaller magnitude.
 Fortunately, spin and orbit are not synchronized in our sample, so confusion with intrinsic effects is less likely.
@@
 \newpage
-\section{Flaring finding in Kepler and TESS: False positives}
+\section{Finding flares in Kepler and TESS: False positives}
 \restartappendixnumbering
@@
     \caption{\textcolor{red}{True and false positive flare candidates in Kepler and TESS light curves.
-\textbf{Left panel}: A flare in the TESS 2-min cadence light curve of GJ 3323 in Sector 5, with its characteristic fast-rise-exponential-decay shape, with additional substructure around the peak.
+\textbf{Left panel}: A flare in the TESS 2-min cadence light curve of GJ 3323 in Sector 5, with its characteristic fast-rise-exponential-decay shape, and additional substructure around the peak.
 \textbf{Middle panel}: Kepler-235 with a possible argabrightening in the 1-min cadence light curve in  Quarter 14.
-Argabrightenings are few-minutes long reflections of light off debris and onto the detector~\citep{vancleve2016kepler}.
+Argabrightenings are few-minutes long reflections of light off of debris and onto the detector~\citep{vancleve2016kepler}.
 The reflections affect large parts of the detector, so that this event can be identified as a false positive by its common occurrence across many light curves.

### 2023-10-23 src/scripts/paper_example_ad_dist.py
added measured p value

@@ -201,15 +201,18 @@ if __name__ == "__main__":
 
 
     plt.figure(figsize=(6,5))
-    for perc, ls, sig in zip([68.27, 95.45, 99.75],[":", "--", "-"],[1,2,3]):
+    for perc, ls, sig in zip([68.27, 95.45, 99.75],[":", "--", "-."],[1,2,3]):
 
         adval = scoreatpercentile(ad, perc)
 
         plt.axvline(adval, label=fr"$p={((100-perc)/100):.3f}\;({sig}\sigma)$", linestyle=ls, color="k")
 
+
+    plt.axvline(4.5, label="HIP 67522, $p=0.0056$", linestyle="-", color="r")
+
     plt.hist(ad_, bins=100)
-    plt.xlim(0, adval+5)
-    plt.legend(loc=1, fontsize=13.5)
+    plt.xlim(0, adval+8)
+    plt.legend(loc=1, fontsize=12, frameon=False)
     plt.xlabel(r"$A^2$ statistic", fontsize=13)
     plt.ylabel("Number of samples", fontsize=13)
     plt.tight_layout()

### 2023-10-23 src/scripts/run_all.sh
added new fig to full script

@@ -15,5 +15,6 @@ python paper_lx_plots.py
 python paper_as_vs_ad.py
 python paper_correlation_coefficients.py
 python paper_aumic_table.py
+python paper_example_ad_dist.py
 
 

### 2023-10-23 src/tex/ms.tex
[showyourwork] overleaf sync

@@
     In many star-planet systems discovered so far, the innermost planet orbits within only a few stellar radii.
-In these systems, planets \textcolor{red}{could} become in-situ probes of the extended stellar magnetic field.
-Because they disturb the field as they move, they are expected to trigger \textcolor{red}{flares in the corona.
-Potential differences to the energies and morphologies of intrinsic flares are poorly constrained.} However, as we expect planet-induced flares to \textcolor{red}{correlate} with the planet's orbital period, we can identify \textcolor{red}{them} from a clustering of flares in phase with the planet's orbit.
+In these systems, planets could become in-situ probes of the extended stellar magnetic field.
+Because they disturb the field as they move, they are expected to trigger flares in the corona.
+Potential differences to the energies and morphologies of intrinsic flares are poorly constrained.
+However, as we expect planet-induced flares to correlate with the planet's orbital period, we can identify them from a clustering of flares in phase with the planet's orbit.
 We used the excellent phase coverage from Kepler and the Transiting Exoplanet Survey Satellite to find flaring star-planet systems, compile a catalog of all their flares, and measure how much they cluster in orbital phase.
@@
 An inactive one, without any signs of clustering, and a tentative active one, where the clustering becomes more pronounced as the expected power of interaction increases.
-\textcolor{red}{The flares in HIP 67522 are prominently clustered ($p<0.006$).
-This young Hot Jupiter system is the most promising candidate for magnetic star-planet interaction in our sample.}
+The flares in HIP 67522 are prominently clustered ($p<0.006$).
+This young Hot Jupiter system is the most promising candidate for magnetic star-planet interaction in our sample.
 
@@
 Beyond this radius, this plasma is disconnected from the star.
-Alfv\'en waves set off by \textcolor{red}{a planet that crosses the magnetic field} cannot propagate back to the star if the wind carries the plasma away faster than these waves can travel.
+Alfv\'en waves set off by a planet that crosses the magnetic field cannot propagate back to the star if the wind carries the plasma away faster than these waves can travel.
 In the sub-Alfv\'enic regime, the wave can reach the star, and deposit its energy in its atmosphere.
@@
 \label{sec:intro:global}
-\textcolor{red}{Even if the instrument's sensitivity is sufficiently high, measuring magnetic star planet-interaction remains notoriously difficult.
-In individual systems,} a non-detection may not mean an absence of the interaction, but merely a temporary cessation~\citep{shkolnik2005hot, shkolnik2008nature}.
+Even if the instrument's sensitivity is sufficiently high, measuring magnetic star planet-interaction remains notoriously difficult.
+In individual systems, a non-detection may not mean an absence of the interaction, but merely a temporary cessation~\citep{shkolnik2005hot, shkolnik2008nature}.
 Statistical studies searching for changes in global chromospheric and coronal activity indicators in star-planet systems with close-in planets relative to planet-less stars are inconclusive~\citep{kashyap2008extrasolar,scharf2010possible, shkolnik2013ultraviolet, france2018farultraviolet, viswanath2020statistical, krejcova2012evidence, miller2015comprehensive, poppenhaeger2010coronal}.
@@
 It is, for instance, easier to detect a planet around a magnetically inactive star, because both radial velocity and transit detections will be less affected by stellar variability~\citep{poppenhaeger2011correlation}, but that does not imply that SPI quenches activity.
-Further, tidal interactions can induce \textcolor{red}{a} global increase in activity~\citep{ilic2022tidal}, which adds a physical ambiguity to the interpretation~(see also Section~\ref{sec:discussion:tidal}).
+Further, tidal interactions can induce a global increase in activity~\citep{ilic2022tidal}, which adds a physical ambiguity to the interpretation~(see also Section~\ref{sec:discussion:tidal}).
 
@@
 We do not know how energetic planet-induced flares can be.
-The estimates for dissipated energy~\citep{lanza2018closeby} are in the ballpark of the regime of superflares\textcolor{red}{, with energies released at optical wavelengths $\geq10^{33}\,$erg~\citep{schaefer2000superflares}, that can be} observed by Kepler and TESS.
+The estimates for dissipated energy~\citep{lanza2018closeby} are in the ballpark of the regime of superflares, with energies released at optical wavelengths $\geq10^{33}\,$erg~\citep{schaefer2000superflares}, that can be observed by Kepler and TESS.
 However, on the one hand, the planet might be triggering flares prematurely, which would be of lower energy~\citep{loyd2023flares}, and end up below our detection threshold.
 On the other hand, the energy need not be dissipated continuously, particularly in the stretch-and-break mechanism proposed by~\citep{lanza2012starplanet}, so an individual flare's energy might be higher.
-We also do not know whether flares triggered by interactions with a companion would \textcolor{red}{unfold faster or slower than} intrinsic flares.
-We will assume that, since they would be caused by magnetic reconnection triggered by the planet in the stellar corona, they should still have the same physics as intrinsic flares\textcolor{red}{.
+We also do not know whether flares triggered by interactions with a companion would unfold faster or slower than intrinsic flares.
+We will assume that, since they would be caused by magnetic reconnection triggered by the planet in the stellar corona, they should still have the same physics as intrinsic flares.
 They should then approximalety follow the fast-rise-exponential-decay morphology~(see Fig.~\ref{fig:flares_and_fps} for an example).
@@
 Many of these deviations are unexplained today~\citep{howard2022no}, so that identifying SPI flares based on morphology is not possible without additional constraints.
-However, if we can statistically identify enough SPI flares, as we attempt in this work, we can infer the differences between intrinsic and SPI events from the two ensembles.}
-
-\textcolor{red}{In other words, s}ince planet-induced flares might not look any different from intrinsic flares, and we do not know how their energies will be distributed, we require a method to distinguish them without referring to their individual properties.
+However, if we can statistically identify enough SPI flares, as we attempt in this work, we can infer the differences between intrinsic and SPI events from the two ensembles.
+
+In other words, since planet-induced flares might not look any different from intrinsic flares, and we do not know how their energies will be distributed, we require a method to distinguish them without referring to their individual properties.
 Instead, we can look at the statistical distribution of flares in time:
@@
 In contrast to global SPI, local SPI effects are easier to tell apart from intrinsic stellar behavior because they are tied to the planet's orbital period.
-\textcolor{red}{Searches for an orbital modulation of polarized radio emission have produced promising, but tentative results.
+Searches for an orbital modulation of polarized radio emission have produced promising, but tentative results.
 Close-in star-planet systems are expected to interact similarly to the Jupiter-Io system~\citep{bigg1964influence}, albeit scaled up to the high field strengths of stars~\citep{turnpenney2018exoplanetinduced}.
-In some detections, the planet has not been found (yet)~\citep{vedantham2020coherent}, or the data do not cover multiple orbital periods to see the signal repeat~\citep{perez-torres2021monitoring, pineda2023coherent}, or both \citep{callingham2021population}.} Phase-correlated activity, flaring and otherwise, has been searched for in individual systems.
+In some detections, the planet has not been found (yet)~\citep{vedantham2020coherent}, or the data do not cover multiple orbital periods to see the signal repeat~\citep{perez-torres2021monitoring, pineda2023coherent}, or both \citep{callingham2021population}.
+Phase-correlated activity, flaring and otherwise, has been searched for in individual systems.
 After eight years of monitoring of HD 189733, an active Hot Jupiter host, higher X-ray energy flares seem only marginally clustered in orbital phase than lower energy ones~\citep{pillitteri2022xray}.
@@
 We searched a total of 1811 systems and over 7200 light curves from both missions for flares.
-To calculate the clustering of \textcolor{red}{flares} in orbital phase, we further required the orbital periods of each system~(Section~\ref{sec:data:orbitalperiod}).
+To calculate the clustering of flares in orbital phase, we further required the orbital periods of each system~(Section~\ref{sec:data:orbitalperiod}).
 We then estimated the theoretically expected power of interaction for each system with at least three flares.
@@
 % \rotate
- \caption{Flaring single star-planet system parameters. Obs. time is the total observing time with Kepler and TESS.}
+ \caption{Flaring single star-planet system parameters.
+Obs.
+time is the total observing time with Kepler and TESS.
+\textcolor{red}{The digits in square brackets refer to the uncertainties in the corresponding last digits shown, e.g., $0.051[1]$ is the same as $0.051\pm0.001$, and $98[12]$ is the same as $98\pm12$.}}
 \movetableright=-40mm
@@
 
-The Transiting Exoplanet Survey Satellite~\citep[TESS,][]{ricker2015transiting} is an all-sky mission that began operations in 2018, \textcolor{red}{and has} completed two sky scans in summer 2022.
+The Transiting Exoplanet Survey Satellite~\citep[TESS,][]{ricker2015transiting} is an all-sky mission that began operations in 2018, and has completed two sky scans in summer 2022.
 It is observing at the time of writing, collecting nearly continuous photometric time series in the $600-1000\,$nm band for $\sim 27\,$d in each observing Sector.
@@
 
-% \textcolor{red}{Mid-to-late M dwarfs follow this bimodal distribution }
+% Mid-to-late M dwarfs follow this bimodal distribution
 
@@
 Sections~\ref{sec:methods:relvel} and \ref{sec:methods:bfield}, respectively.
-We can then combine them with \textcolor{red}{the} stellar radius, planetary radius, and semi-major axis to estimate the power of SPI.
+We can then combine them with the stellar radius, planetary radius, and semi-major axis to estimate the power of SPI.
 We use the scaling laws for two different magnetic SPI models, which we introduce in Section~\ref{sec:methods:pspi}.
@@
 Eventually, we apply two Savitzky-Golay~\citep{savitzky1964smoothing} filters in sequence, with window sizes of 6h and 3h each.
-At this stage, we mask all data points above a $2.5 \sigma$ \textcolor{red}{threshold} (or $1.5 \sigma$ for stars like AU Mic or Proxima Cen, which are very active or have very low noise levels, or both) as flare candidates to prevent the filter from ironing out the flares.
+At this stage, we mask all data points above a $2.5 \sigma$ threshold (or $1.5 \sigma$ for stars like AU Mic or Proxima Cen, which are very active or have very low noise levels, or both) as flare candidates to prevent the filter from ironing out the flares.
 As a final step, we fit exponential functions to the edges of the light curves, if there are data points that deviate more than one standard deviation from the median value, while keeping the flare candidates masked.
@@
 \end{equation}
-\textcolor{red}{In other words, equivalent duration is }the time during which the non-flaring star releases as much energy as the flare.
+In other words, equivalent duration is the time during which the non-flaring star releases as much energy as the flare.
 
@@
 We use the same customized Anderson-Darling test as in \cite{ilin2022searching}, which is more sensitive to deviations at both ends of the distribution than the widely used Kolmogorov-Smirnov test~\citep{feigelson2012modern}.
-In \textcolor{red}{short}, we first take the number of flares observed in the TESS and Kepler data to calculate a base flare rate for each light curve.
+In short, we first take the number of flares observed in the TESS and Kepler data to calculate a base flare rate for each light curve.
 We then calculate how often each orbital phase has been observed, also for each light curve separately, to ensure that the different detection thresholds for TESS and Kepler do not bias the base rate.
 With the phase coverage and base flare rate combined, we can tell how many flares we would expect to see in any given phase bin if flares were randomly distributed.
-We then aggregate this number of expected flares per \textcolor{red}{orbital phase} bin into one expected distribution \textcolor{red}{(blue curves in Figs.~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv})} by summing over all available light curves.
+\textcolor{red}{The bin widths correspond to the distance between each consecutive detection of a flare in phase space.} We then aggregate this number of expected flares per orbital phase bin into one expected distribution (blue curves in Figs.~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv}) by summing over all available light curves.
 As a last step, we compare the expected distribution to the observed one using an Anderson-Darling test.
-\textcolor{red}{For this, we sample 10000 times from the expected distribution the same number of flares as we observe in each system.
+For this, we sample 10000 times from the expected distribution the same number of flares as we observe in each system.
 For instance, for HIP 67522, we sample 12 flares distributed according to its blue curve in Fig.~\ref{fig:cumdist_transiting}.
-For each of the 10000 samples, we compute the Anderson-Darling statistic $A^2$, which yields a distribution of $A^2$ values.
-In a last step, we compute $A^2$ for the observed distribution, and compute the $p$-value.} We repeat this test with different phase offsets to account for remaining biases in sensitivity of the test at different phases.
+For each of the 10000 samples, we compute the Anderson-Darling statistic $A^2$, which yields a distribution of $A^2$ values~\textcolor{red}{(see~Fig.~\ref{fig:ad_dist_hip} for the $A^2$ distribution derived for HIP~67522)}.
+In a last step, we compute $A^2$ for the observed distribution, and compute the $p$-value.
+We repeat this test with different phase offsets to account for remaining biases in sensitivity of the test at different phases.
 
@@
 \label{sec:methods:bfield}
-We derive the average magnetic field strength $B$ from \textcolor{red}{Rossby number} $R$o using the empirical relation derived in \citet{reiners2022magnetism},  Table 2, in the unsaturated and saturated regimes, respectively:
+We derive the average magnetic field strength $B$ from Rossby number $R$o using the empirical relation derived in \citet{reiners2022magnetism},  Table 2, in the unsaturated and saturated regimes, respectively:
 
@@
            X-ray luminosity over bolometric luminosity compared to Rossby number (\textbf{upper panel}), and average surface magnetic field strength (\textbf{lower panel}).
-\textcolor{red}{Blue lines denote the error bars, black lines point to the IDs of the corresponding stars.} Both relations follow those of stars not selected for hosting close-in planets, except for GJ 3082, which is underluminous for its Rossby number, and hence also its estimated magnetic field appears too strong for its $L_X/L_{\rm bol}$.
+Blue lines denote the error bars, black lines point to the IDs of the corresponding stars.
+Both relations follow those of stars not selected for hosting close-in planets, except for GJ 3082, which is underluminous for its Rossby number, and hence also its estimated magnetic field appears too strong for its $L_X/L_{\rm bol}$.
         }
@@
 First, we estimate the power of SPI generated by the stretch-and-break mechanism using the scaling relations in~\cite{lanza2012starplanet}.
-\textcolor{red}{We adopt their Eqn.~45 for non-linear and axisymmetric magnetic fields, because the non-linear formulation does not assume a constant force-free parameter, and because only axisymmetric fields can produce modulation of flaring activity in phase with the planetary orbit.
+We adopt their Eqn.~45 for non-linear and axisymmetric magnetic fields, because the non-linear formulation does not assume a constant force-free parameter, and because only axisymmetric fields can produce modulation of flaring activity in phase with the planetary orbit.
 We note that the axisymmetry of stellar magnetic fields varies across stars~\citep[e.g.,][]{donati2009magnetic, donati2008largescale, morin2008largescale, morin2010largescale}, and also with the stellar activity cycle of individual stars~\citep[e.g.,][]{borosaikia2016solarlike, lehmann2021identifying}.
 In Eqn.
-45, the power of SPI, $P_{\rm spi,sb}$, is}
+45, the power of SPI, $P_{\rm spi,sb}$, is
 
 \begin{equation}
-\textcolor{red}{      P_{\rm spi,sb}=\underbrace{\frac{27\pi \lambda^2(n+1)}{16 \mu_0 n (\lambda^2 + n^2)^{1/3}}}_{\hat{C}} B_{\rm p}^{2/3} R_{\rm p}^2 B_*^{4/3}  v_{\rm rel} \left(\frac{R_*}{a}\right)^{\frac{n+11}{ 3}},}
+      P_{\rm spi,sb}=\underbrace{\frac{27\pi \lambda^2(n+1)}{16 \mu_0 n (\lambda^2 + n^2)^{1/3}}}_{\hat{C}} B_{\rm p}^{2/3} R_{\rm p}^2 B_*^{4/3}  v_{\rm rel} \left(\frac{R_*}{a}\right)^{\frac{n+11}{ 3}},
 \end{equation}
 
-\textcolor{red}{where $\mu_0$ is the magnetic permeability of the vacuum, and $n$ and $\lambda$ are dimensionless constants, all of which we subsume under $\hat{C}$, together with other constant factors}.
+where $\mu_0$ is the magnetic permeability of the vacuum, and $n$ and $\lambda$ are dimensionless constants, all of which we subsume under $\hat{C}$, together with other constant factors.
 $B_{\rm p}$ and $B_*$ are the planetary and stellar field strengths at their poles, respectively; $v_{\rm rel}$ is the relative velocity between the stellar rotation and the planet's orbit at the semi-major axis $a$; and $R_*$ and $R_{\rm p}$ are the stellar and planetary radii, respectively.
-\textcolor{red}{We choose $n=0.25$ ($\lambda^2 = 1.01203$), which best reproduces observations of SPI candidate systems HD~179949, $\tau$ Boo, and HD~189733 in~\citet{lanza2012starplanet} (except for $\upsilon$ And).
-Since the planetary fields are unknown, we adopt $B_{\rm p}=1\,$G for simplicity.} We also do not know the stellar field strength at the pole for the vast majority of the stars, so we adopt \textcolor{red}{an average value of 15 per cent of the} surface field strength~(see Sections~\ref{sec:methods:bfield} and~\ref{sec:discussion:as}) as a proxy.
+We choose $n=0.25$ ($\lambda^2 = 1.01203$), which best reproduces observations of SPI candidate systems HD~179949, $\tau$ Boo, and HD~189733 in~\citet{lanza2012starplanet} (except for $\upsilon$ And).
+Since the planetary fields are unknown, we adopt $B_{\rm p}=1\,$G for simplicity.
+We also do not know the stellar field strength at the pole for the vast majority of the stars, so we adopt an average value of 15 per cent of the surface field strength~(see Sections~\ref{sec:methods:bfield} and~\ref{sec:discussion:as}) as a proxy.
 
@@
 \begin{equation}
-\textcolor{red}{      P_{\rm spi,sb0} =\hat{C} R_{\rm p}^2 B_*^2 v_{\rm rel}  \left(\frac{R_*}{a}\right)^{\frac{n+11}{ 3}}}
+      P_{\rm spi,sb0} =\hat{C} R_{\rm p}^2 B_*^2 v_{\rm rel}  \left(\frac{R_*}{a}\right)^{\frac{n+11}{ 3}}
 \end{equation}
 
-Third, we estimate the power of SPI generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio}, \textcolor{red}{ combining Eqn.~8 for the power of interaction and Eqn.~11 for the magnetopause radius of the planet from~\citet{kavanagh2022radio} to arrive at:}
+Third, we estimate the power of SPI generated by the Alfv\'en wing mechanism ~\citep{saur2013magnetic,kavanagh2022radio},  combining Eqn.~8 for the power of interaction and Eqn.~11 for the magnetopause radius of the planet from~\citet{kavanagh2022radio} to arrive at:
 
 \begin{equation}
-\textcolor{red}{    P_{\rm spi,aw} = \frac{\pi^{1/2}}{2^{2/3}} B_{\rm p}^{2/3} R_{p}^2  R_*^2  B_*^{1/3}  v_{\rm rel}^2 a^{-2} \rho_*^{1/2} \sin^2 \theta}
+    P_{\rm spi,aw} = \frac{\pi^{1/2}}{2^{2/3}} B_{\rm p}^{2/3} R_{p}^2  R_*^2  B_*^{1/3}  v_{\rm rel}^2 a^{-2} \rho_*^{1/2} \sin^2 \theta
 \end{equation}
 
-\textcolor{red}{Here, we assume that the magnetopause radius extends to where the magnetic pressures of planet and stellar magnetic wind are equal, and that the wind is dominated by the magnetic field in the sub-Alf\'enic regime.
+Here, we assume that the magnetopause radius extends to where the magnetic pressures of planet and stellar magnetic wind are equal, and that the wind is dominated by the magnetic field in the sub-Alf\'enic regime.
 We approximate the stellar wind density $\rho_W$ with a proportionality to $\rho_* (R_* / a)^{2}$, where $\rho_*$ is the stellar wind density at the base of the corona.
@@
 The angle between the wind magnetic field vector and the velocity vector of the planet $\theta$ is also unknown, so we set $\sin\theta=1$ to obtain an upper limit.
-In reality, $\theta$ will vary both between systems, and over time in any individual system.}
-
-And fourth, we also consider the case of an unmagnetized planet, \textcolor{red}{ where the magnetospheric radius is set equal to the planetary radius}, in which case Eq.~8 in \cite{kavanagh2022radio} reduces to
+In reality, $\theta$ will vary both between systems, and over time in any individual system.
+
+And fourth, we also consider the case of an unmagnetized planet,  where the magnetospheric radius is set equal to the planetary radius, in which case Eq.~8 in \cite{kavanagh2022radio} reduces to
 
 \begin{equation}
-\textcolor{red}{    P_{\rm spi,aw0} = \pi^{1/2} R_{\rm p}^2 R_*^4 B_*  v_{\rm rel}^2 a^{-4} \rho_*^{1/2} \sin^2 \theta}
+    P_{\rm spi,aw0} = \pi^{1/2} R_{\rm p}^2 R_*^4 B_*  v_{\rm rel}^2 a^{-4} \rho_*^{1/2} \sin^2 \theta
 \end{equation}
@@
 In transiting multi-planet systems, the orbital phase refers to the innermost planet, with the transit mid-time at phase zero.
-\textcolor{red}{Qua./Sec.
+Qua./Sec.
 is the Quarter or Sector number of the observation in Kepler or TESS, respectively.
@@
 The orbital phase of the innermost planet is measured at $t_s$.
-We also give relative amplitude $a$, and equivalent duration $ED$ (see Eq.~\ref{eq:ED}) for each flare.} The full catalog is available online (see Data Availability Statement).
+We also give relative amplitude $a$, and equivalent duration $ED$ (see Eq.~\ref{eq:ED}) for each flare.
+\textcolor{red}{The digits in square brackets refer to the uncertainties in the corresponding last digits shown, e.g., $0.051[1]$ is the same as $0.051\pm0.001$, and $98[12]$ is the same as $98\pm12$.} The full catalog is available online (see Data Availability Statement).
         }
@@
 If the orbital period is well-known, the resulting ratio $\Delta T/\tau$ should be $\ll 1$.
-\textcolor{red}{Here, we are not interested in the absolute orbital phase.
+Here, we are not interested in the absolute orbital phase.
 We are only interested in how much uncertainty on the orbital phases of flares accumulates over the entire observing time after the first flare.
@@
 For transiting systems, the midtime is usually very well known.
-So in the following, we set phsae zero to an arbitrary time in non-transiting systems, and to the reported transit midtime for the rest.}
+So in the following, we set phsae zero to an arbitrary time in non-transiting systems, and to the reported transit midtime for the rest.
 
@@
 The orbital period is known sufficiently well for our analysis in most cases with ratios $<0.02$, that is, the orbital phase of the last flare is at most $2\%$ off, compared to the first.
-The three cases where the ratio is highest with \textcolor{red}{$\Delta T/\tau=$}$0.05$, $0.12$, $0.24$ are TAP 26, GJ 3082, and GJ 674, respectively.
+The three cases where the ratio is highest with $\Delta T/\tau=$$0.05$, $0.12$, $0.24$ are TAP 26, GJ 3082, and GJ 674, respectively.
 We keep these systems in our sample, but caution that the measured absence of flaring SPI might be partly due to the uncertain orbital period of the planet in these cases.
@@
 Figures~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv} show the flare phase distributions along with the corresponding expected distributions for transiting and non-transiting systems, respectively.
-The expected distributions usually deviate from a straight line because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different flare rates in each light curve, which arise due to varying noise levels between individual Quarter/Sectors, and \textcolor{red}{between the two instruments}.
+The expected distributions usually deviate from a straight line because we take into account the coverage of the orbital phases by the Kepler and TESS observations, as well as the different flare rates in each light curve, which arise due to varying noise levels between individual Quarter/Sectors, and between the two instruments.
 
@@
 However, overall, the significance of the deviation increases with higher expected power $P_{\rm spi}$ of interaction, introduced in Section~\ref{sec:methods:pspi}.
-Table~\ref{tab:maintable_der} also lists the derived parameters required in these scaling laws, i.e., Rossby number $R$o, surface-average magnetic field strength $B$, and relative velocity \textcolor{red}{$v_{\rm rel}$} between the planet and a co-rotating \textcolor{red}{stellar} magnetic field .
+Table~\ref{tab:maintable_der} also lists the derived parameters required in these scaling laws, i.e., Rossby number $R$o, surface-average magnetic field strength $B$, and relative velocity $v_{\rm rel}$ between the planet and a co-rotating stellar magnetic field .
 
@@
 $P_{\rm spi,xx0}$ is the same, but assuming an unmagnetized planet.
-The $p$-value of the Anderson-Darling test is lower when the system shows a stronger clustering of flares in orbital phase.}
+The $p$-value of the Anderson-Darling test is lower when the system shows a stronger clustering of flares in orbital phase.
+\textcolor{red}{The digits in square brackets refer to the uncertainties in the corresponding last digits shown, e.g., $0.051[1]$ is the same as $0.051\pm0.001$, and $98[12]$ is the same as $98\pm12$.}}
 \input{output/table_der_vals.tex}
@@
 AD test results, assuming the stretch-and-break scenario with an unmagnetized planet.
-\textcolor{red}{The vertical and horizontal grey lines denote the uncertainties quoted in Table~\ref{tab:maintable_der}.} While no individual system amounts to a $>3\sigma$ detection, the global trend is intriguing: Systems with low expected power show no deviation from random intrinsic flaring (i.e.
-high $p$-values \textcolor{red}{in the left half of the Figure}).
+The vertical and horizontal grey lines denote the uncertainties quoted in Table~\ref{tab:maintable_der}.
+While no individual system amounts to a $>3\sigma$ detection, the global trend is intriguing: Systems with low expected power show no deviation from random intrinsic flaring (i.e.
+high $p$-values in the left half of the Figure).
 In contrast, systems with high expected power show two branches.
@@
 % \script{paper_aumic_table.py}
-% \caption{\textcolor{red}{Powers of star-planet interaction calculated for AU Mic in the four different scenarios introduced in Section~\ref{sec:methods:pspi}.}}
+% \caption{Powers of star-planet interaction calculated for AU Mic in the four different scenarios introduced in Section~\ref{sec:methods:pspi}.}
 % \input{output/aumic_spi.tex}
@@
 We therefore excluded some systems due to documented contamination from nearby (bound or co-moving) companions~(Section~\ref{sec:results:individualstars:excluded}).
-One exception to this rule is Kepler-411, a binary system for which the flare contributions from each component could be separated, but which was excluded \textcolor{red}{due to its flares' low $ED$}.
+One exception to this rule is Kepler-411, a binary system for which the flare contributions from each component could be separated, but which was excluded due to its flares' low $ED$.
 We also dropped GJ 1061 from the final sample because its rotation period was unconstrained.
@@
 
-\textcolor{red}{In the stretch-and-break scenario, and the Alfv\'en wing scenario with a magnetized planet, the three systems cluster together distinctly~(Figure~\ref{fig:adtest_bp}, and top and middle panel in Figure~\ref{fig:adtest_bp_rest}).
-In the Alfv\'en wing scenario with an unmagnetized planet~(bottom panel in Figure~\ref{fig:adtest_bp_rest}),} the distinction is less clear.
+In the stretch-and-break scenario, and the Alfv\'en wing scenario with a magnetized planet, the three systems cluster together distinctly~(Figure~\ref{fig:adtest_bp}, and top and middle panel in Figure~\ref{fig:adtest_bp_rest}).
+In the Alfv\'en wing scenario with an unmagnetized planet~(bottom panel in Figure~\ref{fig:adtest_bp_rest}), the distinction is less clear.
 In both cases, the low level (or possible absence) of interaction could be due to the Alfv\'en radius being within the planetary orbit.
@@
 
-\textcolor{red}{It is important to note that \citet{chebly2023numerical} assume a consistent Poynting flux per unit magnetic field strength for all stars, using the value of the Sun as a reference.
+It is important to note that \citet{chebly2023numerical} assume a consistent Poynting flux per unit magnetic field strength for all stars, using the value of the Sun as a reference.
 The size of the Alfv\'en surface depends strongly on this assumption.
@@
 Nevertheless, while the consistency in the Poynting flux appears as a very strong assumption, the numerical results of \citet{chebly2023numerical} fare relatively well when compared with our current observational knowledge of stellar winds in cool main-sequence stars~\citep{wood2021new}.
-For this reason, we consider that Eq.~\ref{AS_estimation} should be robust enough for our purposes.}
+For this reason, we consider that Eq.~\ref{AS_estimation} should be robust enough for our purposes.
 
@@
 
-The second assumption is that $B_{\rm V}$ will match the maximum radial magnetic field \textcolor{red}{$B_{\rm r}^{\rm max}$} in a ZDI reconstruction.
-\textcolor{red}{$B_{\rm V}$ is integrated over the visible surface of the star.
-Only if the effect from cancellation of opposite polarities is small for an observing phase that contains the strongest large-scale radial magnetic region, will this assumption hold.} At all other rotational phases, we expect $B_{\rm V} < B_{\rm r}^{\rm max}$.
+The second assumption is that $B_{\rm V}$ will match the maximum radial magnetic field $B_{\rm r}^{\rm max}$ in a ZDI reconstruction.
+$B_{\rm V}$ is integrated over the visible surface of the star.
+Only if the effect from cancellation of opposite polarities is small for an observing phase that contains the strongest large-scale radial magnetic region, will this assumption hold.
+At all other rotational phases, we expect $B_{\rm V} < B_{\rm r}^{\rm max}$.
 Therefore, by assuming $B_{\rm V} = B_{\rm r}^{\rm max}$ we are effectively taking an upper limit on the longitudinal magnetic field strength, which will be translated\footnote[3]{Naturally this will also depend on how good our $15$\% match between $B$ and $B_{\rm V}$ is to reality.} in our estimated values of $\overline{AS}_{\rm R}$.
@@
 Location inside $\overline{AS}_{\rm R}$ is a required but not sufficient condition for magnetic SPI, as we will see in the following subsections.
-%\textcolor{red}{JDAG: Thats a good point.
+%JDAG: Thats a good point.
 However, I think being inside the AS is a required but not sufficient condition for the type of SPI that you are looking for.
@@
 There's of course more to it than just field strength or accretion, with things like the torsion and helicity of the field among others (which is why the likelihood of a solar AR to host a flare is not only determined by field strength but also by its topology/complexity), but all of that is too complicated or even impossible to estimate here.
-The bottom line is that there are multiple reasons that could explain why those two stars that lie deep in the sub-Alfv\'enic regime show no signs of flaring SPI which, without a better characterization of each individual system + some 3D modelling, are very hard to ascertain.}
+The bottom line is that there are multiple reasons that could explain why those two stars that lie deep in the sub-Alfv\'enic regime show no signs of flaring SPI which, without a better characterization of each individual system + some 3D modelling, are very hard to ascertain.
 
@@
 
-Most of our systems are transiting\textcolor{red}{.
-F}or those we can expect this scenario to be a minor problem unless the latitude of the footpoint is very high.
-Of the systems that have high expected power but do not show any excess flaring, only TAP 26 \textcolor{red}{has }a planet detected in radial velocity \textcolor{red}{with} a relatively high orbital inclination of about $55\pm10$ deg inferred from photometry, spectroscopy, and Zeeman Doppler measurements in~\citet{yu2017hot}.
+Most of our systems are transiting.
+For those we can expect this scenario to be a minor problem unless the latitude of the footpoint is very high.
+Of the systems that have high expected power but do not show any excess flaring, only TAP 26 has a planet detected in radial velocity with a relatively high orbital inclination of about $55\pm10$ deg inferred from photometry, spectroscopy, and Zeeman Doppler measurements in~\citet{yu2017hot}.
 Their ZD map reveals magnetic field concentrations close to the rotational pole, and the brightness maps also show a dark spot in the same location.
@@
 
-If \textcolor{red}{it is the stellar companion that tidally causes} the observed effects, planetary companions should do the same, albeit at a smaller magnitude.
+If it is the stellar companion that tidally causes the observed effects, planetary companions should do the same, albeit at a smaller magnitude.
 Fortunately, spin and orbit are not synchronized in our sample, so confusion with intrinsic effects is less likely.
@@
 \section*{Acknowledgements}
-\textcolor{red}{The authors thank the anonymous referee for their thorough criticism of the manuscript, and numerous valuable suggestions. EI would like to thank Antonino Lanza for helpful advice.}
+The authors thank the anonymous referee for their thorough criticism of the manuscript, and numerous valuable suggestions. EI would like to thank Antonino Lanza for helpful advice.
 This paper includes data collected by the TESS mission, which are publicly available from the Mikulski Archive for Space Telescopes (MAST).
@@
     \includegraphics[width=\linewidth]{figures/systematics_false_positives.png}
-    \caption{\textcolor{red}{True and false positive flare candidates in Kepler and TESS light curves.
+    \caption{True and false positive flare candidates in Kepler and TESS light curves.
 \textbf{Left panel}: A flare in the TESS 2-min cadence light curve of GJ 3323 in Sector 5, with its characteristic fast-rise-exponential-decay shape, and additional substructure around the peak.
@@
 SSOs produce smooth and nearly symmetrical brightenings as they move in and out of the aperture of the star.
-They can also (partially) be identified with known SSOs~\citep{berthier2006skybot, berthier2016prediction}.}}
+They can also (partially) be identified with known SSOs~\citep{berthier2006skybot, berthier2016prediction}.}
     \label{fig:flares_and_fps}
@@
 
+\section{Anderson-Darling $A^2$ statistic}
+\restartappendixnumbering
+
+\begin{figure*}[ht!]
+    \script{paper_example_ad_dist.py}
+    \begin{centering}
+    \includegraphics[width=0.5\linewidth]{figures/example_ad_dist.png}
+\caption{\textcolor{red}{The distribution of 10000 samples of the $A^2$ statistic for HIP 67522.
+A value of $A^2$ is calculated by drawing a fixed number of flares \textit{at random orbital phases}.
+The fixed number has to be the same as the number of the flares that were observed in reality.
+Then, one takes the orbital phases of these observed flares, and compares their $A^2$ value to that of the distribution.
+An observed $A^2$ value in the tails of the distribution means that flares do not occur \textit{at random orbital phases}, but instead cluster in phase with the planetary orbit, suggesting that the planet triggers at least some of those flares.
+Here, we show the $A^2$ values that would correspond to $1$, $2$, and $3\sigma$ detections of clustering in orbital phase as vertical lines, along with the measured value for HIP 67522.}}
+    \label{fig:ad_dist_hip}
+        \end{centering}
+\end{figure*}
+
 \end{document}

### 2023-11-01 src/tex/ms.tex
[showyourwork] overleaf sync

@@
 \affiliation{Leibniz Insitute for Astrophysics Potsdam (AIP), An der Sternwarte 16, 14482 Potsdam, Germany}
+\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Oude Hoogeveensedijk 4, Dwingeloo, 7991 PD, The Netherlands}
 
@@
 \keywords{stars: flare, planet–star interactions, stars: magnetic field, stars: low-mass, stars: activity}
+
+\vspace{0.4cm}
+\textit{Accepted 2023 October 30. Received 2023 October 24; in original form 2023 July 04}
+
 \end{abstract}
@@
 time is the total observing time with Kepler and TESS.
-\textcolor{red}{The digits in square brackets refer to the uncertainties in the corresponding last digits shown, e.g., $0.051[1]$ is the same as $0.051\pm0.001$, and $98[12]$ is the same as $98\pm12$.}}
+The digits in square brackets refer to the uncertainties in the corresponding last digits shown, e.g., $0.051[1]$ is the same as $0.051\pm0.001$, and $98[12]$ is the same as $98\pm12$.}
 \movetableright=-40mm
@@
 With the phase coverage and base flare rate combined, we can tell how many flares we would expect to see in any given phase bin if flares were randomly distributed.
-\textcolor{red}{The bin widths correspond to the distance between each consecutive detection of a flare in phase space.} We then aggregate this number of expected flares per orbital phase bin into one expected distribution (blue curves in Figs.~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv}) by summing over all available light curves.
+The bin widths correspond to the distance between each consecutive detection of a flare in phase space.
+We then aggregate this number of expected flares per orbital phase bin into one expected distribution (blue curves in Figs.~\ref{fig:cumdist_transiting} and \ref{fig:cumdist_rv}) by summing over all available light curves.
 As a last step, we compare the expected distribution to the observed one using an Anderson-Darling test.
@@
 For instance, for HIP 67522, we sample 12 flares distributed according to its blue curve in Fig.~\ref{fig:cumdist_transiting}.
-For each of the 10000 samples, we compute the Anderson-Darling statistic $A^2$, which yields a distribution of $A^2$ values~\textcolor{red}{(see~Fig.~\ref{fig:ad_dist_hip} for the $A^2$ distribution derived for HIP~67522)}.
+For each of the 10000 samples, we compute the Anderson-Darling statistic $A^2$, which yields a distribution of $A^2$ values~(see~Fig.~\ref{fig:ad_dist_hip} for the $A^2$ distribution derived for HIP~67522).
 In a last step, we compute $A^2$ for the observed distribution, and compute the $p$-value.
@@
 We also give relative amplitude $a$, and equivalent duration $ED$ (see Eq.~\ref{eq:ED}) for each flare.
-\textcolor{red}{The digits in square brackets refer to the uncertainties in the corresponding last digits shown, e.g., $0.051[1]$ is the same as $0.051\pm0.001$, and $98[12]$ is the same as $98\pm12$.} The full catalog is available online (see Data Availability Statement).
+The digits in square brackets refer to the uncertainties in the corresponding last digits shown, e.g., $0.051[1]$ is the same as $0.051\pm0.001$, and $98[12]$ is the same as $98\pm12$.
+The full catalog is available online (see Data Availability Statement).
         }
@@
 The $p$-value of the Anderson-Darling test is lower when the system shows a stronger clustering of flares in orbital phase.
-\textcolor{red}{The digits in square brackets refer to the uncertainties in the corresponding last digits shown, e.g., $0.051[1]$ is the same as $0.051\pm0.001$, and $98[12]$ is the same as $98\pm12$.}}
+The digits in square brackets refer to the uncertainties in the corresponding last digits shown, e.g., $0.051[1]$ is the same as $0.051\pm0.001$, and $98[12]$ is the same as $98\pm12$.}
 \input{output/table_der_vals.tex}
@@
 \end{figure}
-
-% \begin{table}
-% \movetableright=-10mm
-% \script{paper_aumic_table.py}
-% \caption{Powers of star-planet interaction calculated for AU Mic in the four different scenarios introduced in Section~\ref{sec:methods:pspi}.}
-% \input{output/aumic_spi.tex}
-%     \label{tab:aumic}
-% \end{table}
 
@@
     \includegraphics[width=0.5\linewidth]{figures/example_ad_dist.png}
-\caption{\textcolor{red}{The distribution of 10000 samples of the $A^2$ statistic for HIP 67522.
+\caption{The distribution of 10000 samples of the $A^2$ statistic for HIP 67522.
 A value of $A^2$ is calculated by drawing a fixed number of flares \textit{at random orbital phases}.
@@
 An observed $A^2$ value in the tails of the distribution means that flares do not occur \textit{at random orbital phases}, but instead cluster in phase with the planetary orbit, suggesting that the planet triggers at least some of those flares.
-Here, we show the $A^2$ values that would correspond to $1$, $2$, and $3\sigma$ detections of clustering in orbital phase as vertical lines, along with the measured value for HIP 67522.}}
+Here, we show the $A^2$ values that would correspond to $1$, $2$, and $3\sigma$ detections of clustering in orbital phase as black vertical lines, along with the measured $A^2$ value for HIP 67522 as red vertical line.}
     \label{fig:ad_dist_hip}

### 2023-11-02 src/tex/ms.tex
[showyourwork] overleaf sync
final table upload to zenodo after acceptance

@@
 \citep{luger2021mappinga} to create all figures, format all tables, and compile the manuscript.
-Each figure links to the dataset stored on Zenodo (link to be added after acceptance), and to the script that produced the figure in the git repository~\href{https://github.com/ekaterinailin/flaring-spi-paper}{github.com/ekaterinailin/flaring-spi-paper}.
+Each figure links to the script that produced the figure in the git repository~\href{https://github.com/ekaterinailin/flaring-spi-paper}{github.com/ekaterinailin/flaring-spi-paper}.
 The git repository that produces the data stored on Zenodo is publicly available at \href{https://github.com/ekaterinailin/flaring-spi}{github.com/ekaterinailin/flaring-spi}.
+The almost 13000 de-trended light curves, and the full versions of all Tables in this work are available via Zenodo \href{https://doi.org/10.5281/zenodo.8355002}{10.5281/zenodo.8355002}.
 \bibliography{bib}

### 2023-11-02 src/scripts/paper_latex_flare_table.py

@@ -18,6 +18,42 @@ if __name__ == "__main__":
     # Sort the data by orbital phase
     flare_table = flare_table.sort_values(by="tstart", ascending=True)
 
+    # remove duplicates 
+    # Group by TIC and quarter_or_sector, then by timestamp and total_time_observed_in_lc_days, and remove all but first in each group
+    for l, g in flare_table.groupby(['TIC', 'quarter_or_sector']):
+        grouped = g.groupby(['timestamp', 'total_time_observed_in_lc_days'])
+
+        # now keep only the first group
+        flare_table = flare_table.drop(grouped.tail(len(grouped)-1).index)
+
+    print(flare_table[flare_table.ID == "HIP 67522"])
+
+    flare_table.to_csv(paths.data / "zenodo/Table_2_flares.csv", index=False)
+
+    # add text to the top of the written table with explanations of each column
+    top_text = ("# TIC and ID, star designations\n"
+                "# mission, TESS or Kepler\n"
+                "# quarter_or_sector, TESS sector or Kepler quarter\n"
+                "# timestamp, date when light curve was downloaded and analysed\n"
+                "# total_time_observed_in_lc_days, total time observed in this light curve, calculated by summing all valid data points times the cadence\n"
+                "# orbital_phase, orbital phase of the flare\n"
+                "# orbital_phase_err, uncertainty on the orbital phase, derived only for the stars in the final sample\n"
+                "# rel_amplitude, relative amplitude of the flare\n"
+                "# rel_amplitude_err, uncertainty on the relative amplitude\n"
+                "# tstart, start time of the flare\n"
+                "# tstop, stop time of the flare\n"
+                "# ED, equivalent duration of the flare in s\n"
+                "# ED_err, uncertainty on the equivalent duration\n"
+                "# abs_tstart, flare start time in BJD instead of with Kepler/TESS offsets\n")
+    
+    # add the top text to the top of the table in the zenodo folder
+    with open(paths.data / "zenodo/Table_2_flares.csv", "r") as f:
+        lines = f.readlines()
+    with open(paths.data / "zenodo/Table_2_flares.csv", "w") as f:
+        f.write(top_text)
+        f.writelines(lines)
+
+
     # Get ED with uncertainties in one expression
     # flare_table[r"$ED$ [s]"] = flare_table.apply(lambda x: fr"${x.ED:.2f} \pm {x.ED_err:.2f}$",
     #                                              axis=1)

### 2023-11-02 src/scripts/paper_main_table.py

@@ -208,6 +208,70 @@ if __name__ == "__main__":
     # convert st_spectype and st_spectype_bibkey to latex format
     singles.st_spectype = singles.st_spectype.fillna("")
     singles.st_spectype_bibkey = singles.st_spectype_bibkey.fillna("")
+
+    # delete some columns that are not needed
+    del singles["multiple_star"]
+    del singles["multiple_star_source"]
+    del singles["orbits_covered"]
+
+    s = singles.copy()
+
+    # drop all bibkey columns
+    for col in s.columns:
+        if "bibkey" in col:
+            del s[col]
+
+    # write the singles table to a csv file in the zenodo folder
+    s.to_csv(paths.data / "zenodo/Tables_1_3_star_planet_systems.csv", index=False)
+
+    # add text to the top of the table that explains the columns
+    top_text = ("# ID and TIC,star identifier\n"
+                "# obs. time, time span of the observations in days\n"
+                "# st_spectype, spectral type of the star\n"
+                "# st_rotp, rotation period of the star in days\n"
+                "# st_rotp_err, uncertainty on the rotation period\n"
+                "# orbper_d, orbital period of the planet in days\n"
+                "# orbper_d_err, uncertainty on the orbital period\n"
+                "# pl_orbeccen, orbital eccentricity of the innermost planet\n"
+                "# pl_orbeccenerr1, upper uncertainty on the orbital eccentricity\n"
+                "# pl_orbeccenerr2, lower uncertainty on the orbital eccentricity\n"
+                "# st_rad, stellar radius in solar radii\n"
+                "# st_rad_err1, upper uncertainty on the stellar radius\n"
+                "# pl_radj, planetary radius in Jupiter radii\n"
+                "# pl_radjerr1, upper uncertainty on the planetary radius\n"
+                "# pl_raderr2, lower uncertainty on the planetary radius\n"
+                "# Ro, Rossby number\n"
+                "# Ro_high, Ro + upper uncertainty on the Rossby number\n"
+                "# Ro_low, Ro - lower uncertainty on the Rossby number\n"
+                "# st_lum, stellar luminosity in solar luminosities\n"
+                "# st_lumerr1, upper uncertainty on the stellar luminosity\n"
+                "# st_lumerr2, lower uncertainty on the stellar luminosity\n"
+                "# a_au, planet-star distance in au\n"
+                "# a_au_err, uncertainty on the planet-star distance\n"
[…]

### 2023-11-02 src/scripts/paper_table_tidal.py

@@ -93,6 +93,46 @@ if __name__ == "__main__":
     # take neg value of pl_bmassjerr2
     df.M_pl_low_err = - df.M_pl_low_err
 
+    dfz = df.copy()
+
+    # select columns to go on zenodo
+    cols = ["TIC", "ID", "M_star", "M_star_up_err", "M_star_low_err",
+            "M_pl", "M_pl_up_err", "M_pl_low_err",	"grav_pert", 
+            "grav_pert_low_err", "grav_pert_up_err", "tidal_disip_timescale",
+            "tidal_disip_timescale_up_err", "tidal_disip_timescale_low_err",
+            "torque_conv", "torque_conv_up_err", "torque_conv_low_err", "mean", "std"]
+
+    # save table to file in the zenodo folder
+    dfz[cols].to_csv(paths.data / "zenodo/Table_4_tidal_interaction.csv", index=False)
+
+    # add text to the top of the written table with explanations of each column
+    top_text = ("# TIC and ID, star designations\n"
+                "# M_star, stellar mass in solar masses\n"
+                "# M_star_up_err, upper uncertainty on the stellar mass\n"
+                "# M_star_low_err, lower uncertainty on the stellar mass\n"
+                "# M_pl, planetary mass in Jupiter masses\n"
+                "# M_pl_up_err, upper uncertainty on the planetary mass\n"
+                "# M_pl_low_err, lower uncertainty on the planetary mass\n"
+                "# grav_pert, gravitational perturbation\n"
+                "# grav_pert_low_err, lower uncertainty on the gravitational perturbation\n"
+                "# grav_pert_up_err, upper uncertainty on the gravitational perturbation\n"
+                "# tidal_disip_timescale, tidal dissipation timescale in years\n"
+                "# tidal_disip_timescale_up_err, upper uncertainty on the tidal dissipation timescale\n"
+                "# tidal_disip_timescale_low_err, lower uncertainty on the tidal dissipation timescale\n"
+                "# torque_conv, convective torque in solar masses x (km/s)^2\n"
+                "# torque_conv_up_err, upper uncertainty on the convective torque\n"
+                "# torque_conv_low_err, lower uncertainty on the convective torque\n"
+                "# mean, mean of the Anderson-Darling test p-values\n"
+                "# std, standard deviation of the Anderson-Darling test p-values\n")
+    
[…]
